### 2013-01-26 paper/ms.tex
first commit of the paper source

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ Letters}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
%\bibliographystyle{apj}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

\newcommand{\kms}{\,km~s$^{-1}$}
\def\squig{\sim\!\!}
\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\Lsun}{\mbox{\,$L_{\odot}$}}
\newcommand{\like}{\mathscr{L}}
\newcommand{\bftheta}{\mathbf{\Theta}}
\newcommand{\degree}{\ensuremath{^\circ}}
\def\spose#1{\hbox to 0pt{#1\hss}}
\def\simlt{\mathrel{\spose{\lower 3pt\hbox{$\mathchar"218$}}
     \raise 2.0pt\hbox{$\mathchar"13C$}}}
\def\simgt{\mathrel{\spose{\lower 3pt\hbox{$\mathchar"218$}}
     \raise 2.0pt\hbox{$\mathchar"13E$}}}
\font\smcap=cmcsc10

\shorttitle{LAE halo host mass at z=3.1}
\shortauthors{Mej\'ia et al.}

\begin{document}
\title{Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance}

\author{
J. Mej\'ia \altaffilmark{2}, 
J. E.\ Forero-Romero\altaffilmark{1}, 
}

\altaffiltext{1}{XXX}
\altaffiltext{2}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia, \email{je.forero@uniandes.edu.co}}

\date{\today}

\begin{abstract}
-
\end{abstract}

\begin{keywords}
{galaxies: kinematics and dynamics, Local Group, methods:numerical}
\end{keywords}

\section{Introduction}
Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a central topic in studies of structure formation in the Universe. The reason is the diverse range of fields where they are helpful, LAEs can be used as probes of reionization, tracers of large scale structure, signposts for low metallicity stellar populations and markers of the the galaxy formation process through cosmic history.

At the same time, theoretical and observational developments have contributed to the emergence of a paradigm to describe structure formation in a cosmological context. In this context it is considered that dominant matter content of the Universe is to be found in dark matter, whereby each galaxy is hosted by larger dark matter structure known as a halo.

Most models of galaxy formation find that the mass of the halo largely determines key properties of the galaxy such as its stellar mass and star formation rate. Processes that regulate the star formation cycle are also though to be strongly dependent on its mass. Furthermore, the spatial clustering of galaxies on large scales is entirely dictated by the halo distribution.  For the reasons mentioned above, finding the typical dark matter halo mass hosting LAEs represents a significant step forward to understand the nature of this population in the context of LCDM.

Some theoretical approaches to this problem have been based on a forward modelling. Starting from the DM halo population, the corresponding intrinsic star formation properties are infered and statistics such as the luminosity function, the correlation function and the equivalent width distributions. Such modelling has been implemented from analytic considerations, semi-analytic models and full N-body hidrodynamical simulations.

Added to the uncertainties in the astrophysical processeses describing star formation in galactic populations, a highly debated steps in this approach is the calculation of the fraction of Lyman-$\alpha$ photons that escape the galaxy to the observer. Given the resonance nature of the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the density, temperature, topology and kinematics of the neutral Hydrogen in the interstellar medium (ISM).

This complexity makes the use of monte-carlo simulations for the radiative transfer a required tool to obtain physically sound results, although the degeneracy in the physical parameters involved in the problem makes it difficult to achieve a robust consensus on what is the theoretical expected value for the Lyman-$alpha$ escape fraction in high redshift.

Throughout this Letter we assume a $\Lambda$CDM cosmology with the following values for the cosmological parameters, $\Omega_{m}=0.27$, $\Omega_{\Lambda}=0.73$ and $h=0.70$, corresponding to the matter density, vacuum density and the Hubble constant in units of 100 km s$^{-1}$ Mpc$^{-1}$.

\section{Methodology}
In this paper we constrain the typical mass of dark matter halos hosting LAES at $z=3.1$. Our model is based on the number density information obtained in the recent large scale survey presented by XXX where XXX LAEs are detected over 7 fields of $\sim 46 \times 35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed fields of $XXX$ deg$^{2}$.

The diverse physical and astrophysical uncertainties in obtaining statistical prediction for the Lyman-alpha line are the largest impediment to consruct an ab-iitio model for LAEs. In this Letter we want to by-pass this approach by constructing models with the sole objective of reproducing the cosmic variance in the number density of LAEs. Afterwards we will interpret the implications of this result for physical models for Lyman-alpha emitting galaxies.

The model is based on the predictions of a large volume high resolution N-body simulation describing the gravitational dynamics of dark matter. We do not have an strong bias towards the theoretical expectation of what the mass of the dark matter halo hosting the galaxy should be.  Instead, we fully explore the parameter space of our simplified model. The only cut we impose is that observed LAEs do not reside in dark matter halos with masses less than 10$^{10}$hMsun [citation].

In the following subsections we describe the most relevant features of the observational data, the N-body simulation we use, our model and its parameters together with the method to compare its predictions against observations.

\subsection{The Observational Constraints}
We take as a reference the recently published results of a panoramic survey of LAES at z=3.1 by Yamada et al. 2012. This survey was conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera, which has a field of view covering $34\times 27$ arcmin, corresponding to a comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$. The narrow band filter is centered at $4977$ \AA with a $77$\AA width, corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc $h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line centered at $z=3.09$.

In this paper we only use the results of Yamada et al due to the homogenous conditions  to define their samples. We do this for homogeinity in the observation and data reduction techniques. There are other surveys by XXX an XXX that cover similar regions, but they use different criteria on the equivalent width (EW) cuts to construct the LAE samples. Different cuts in the EW can change the number of LAEs to be included in the catalog. This cuts have an impact on the fainter LAEs which are more abundante than brighter ones. Different definitions of the EW cuts can yield number densities different by a factor of two [REF, I think Yamada has some numbers].

The survey covered four independent fields. The first is the SSA22 field of $1.38$ deg$^2$ with $1394$ detected LAEs, this field has been known to harbor a region with a large density excess of galaxies. The second observed region is composed by the fields Subaru/{\it XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a total of $0.58$ deg$^2$ and $386$ LAEs. The third and fourth fields are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs, and the fild arotund the Great Observatory Optical Deep Survey North (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs. In Table 1 we summarize the values we use in throughout this paper for the each field, covered area, measured surface LAE number density and inferred number volume density.

\subsection{The Simulation and Halo Catalogs}
We use the Bolshoi simulation data available from their public database accessible via SQL query interface. The simulation was performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. It includes dark matter distribution is sampled using $2048^{3}$ particles, which translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.

The cosmological parameters are consistent with a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$, cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the power spectrum $\sigma_{8}=0.82$

We have used halo catalogs constructed with a Friend-of-Friends (FOF) algorithm with a linking lenght of 0.17 times the interparticle distance. We have veryfied that the main results we present in this paper also hold if instead we use halo catalogs constructed from a the Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are defined to have an density of 200 times the critical density.

The catalogs we have used here are obtained from a publicly available Multidark database \footnote{{\tt http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.

\subsection{Mock Catalogs: Populating Halos with LAEs}
\label{subsec:mocks}
We start from the Friends-of-Friends (FOF) catalog at $z=3.1$. The catalog is split into disjoint sub-volumes with the same geometry probed by Suprime-CAM and the narrow band filter of $46\times 35\times 41$ $h^{-3}Mpc^{3}$ . There are in total $5\times 7 \times 6=210$ of such sub-volumes in a snapshot of the Bolshoi simulation. We take the $z$ direction to correspond to the redshift direction in the survey. This corresponds to a total area of $880$ arcmin$^{2}$ for each projected sub-volume.

The model that creates a mock is based in a one-to-one correspondence of LAEs to DM halos: each halo can only host a single LAE. There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE. In what follows we will describe by the letter ${\mathcal M}$ a model spanning a set of mock catalogs calculated by fixed values of these three parameters.

\subsection{Model Sampling and Selection}
We generate a series of models ${\mathcal M}_{I}$, where $I$ corresponds to set of input values $I=\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$. We explore a wide range of values in the $I$ parameter space as follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 15 different values evenly spaced by $0.2$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.8$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.2$ up to $\log_{10}M_{\rm min}=13.0$ shifted by $0.2$ dex. The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$. In total the number of different sets of input parameters to be explored is $15\times 15\times 100 = 22500$.

For each model we generate 210 mock catalogs corresponding to each of the sub-volumes extracted in the box. For each volume we project along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$. Using the $210$ values for the surface density we perform a Kolmogorov-Smirnov test to compare it against the $12$ observational values and obtain the probability to reject the null hypothesis that the two data sets come from the same distribution.

We also boot-strap these 210 mocks for each model to construct sub-samples of 12 catalogs corresponding to the 12 observed fields. We do this boot-strapping in two different ways. First, by selecting the 12 catalogs in a random fashion without taking into account any spatial information. Second, by selecting sets of catalogs taking into account the spatial correlations present in observations. For instance, 7 out of the 12 catalogs are selected to be spatially contiguous as the SSA22 field, 3 fields correspond to the SXDS fields and 2 remaining catalogs are spatially uncorrelated to resemble the SDF and GOODS-North fields. We do this boot-straping 15 times and keep the median value for the KS test.

Summarizing, for each model $M_{\rm min}, M_{\rm max}, f_{\rm occ}$, there are three different ways to calculate a KS test, which is in turn used to select the models that best reproduce the observations: from the full 210 mock sample, from 20 boot-strapped sets of 12 catalogs and finally from the same kind of boot-strapped catalogs that take into account the correlation in neighboughring observed fields.

\section{Results}

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
\caption{ \label{figure:laes_dist} Cumulative mass function of dark matter haloes in the $210$ sub-volumes of $46\times 35\times 41$ $h^{-3}Mpc^{3}$. The variation in the total number of dark matter halos per sub-volume  evidences the effect of cosmic variance at such sub-volume scale. It is also appreciable the low population $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with $log(M/M_{\odot})>12.0$}.
\end{center} 
\end{figure}

\subsection{General Constraints on the Occupation Fraction}
The number density of dark matter halos per unit comoving volume is a well defined quantity for a given cosmological model, modulo the effects introduced by cosmic variance. The occupation fraction $f_{\rm occ}$ acts a renormalization factor of the halo number density to match the observational constrain of the surface density of LAEs.

In Fig. 1 we show the cumulative mass function of dark matter haloes in the $210$ sub-volumes extracted from the Bolshoi simulation. This mass function is expressed as a surface density by projecting the positions of all haloes along the $z$ direction and taking the surface of the rectangle in the $x$-$y$ plane as the nominal $880$ arcmin$^{2}$ we calculated in \S\ref{subsec:mocks}. The same figure shows as a vertical band the range of observed surface density of LAEs.

There is a characteristic halo mass $M_{\rm c}$ above which the halo mass functions are below the observational constraint, meaning that models with model parameters $I=\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ with $M_{\rm min}> M_{\rm c}$ have a number densiy that is already lower than the observational one, regardless of the value of $f_{\rm occ}$. Conversely, below for models with $M_{\rm min}<M_{\rm c}$ have a possibility of success if the occupation fraction $f_{\rm occ}$ is tuned as to lower the halo number density down to the observed value.

For the reasons explained above, the occupation fraction $f_{\rm occ}$ has a strong dependence on the mass parameters of the model $M_{\rm min}$ and $M_{\rm max}$. This allows us to focus in presenting the results of the best models in terms of these two parameters, knowing that the occupation fraction is already tightly constrained.

\subsection{Likelihood landscapes}

Figure \label{figure:landscape} presents the probability from the KS-tests that the observed and simulated surface densities can be considered as comming from similar distributions. For the reasons explained in the last section, we only show the results in the $M_{\rm min}-M_{\rm max}$ plane. The first panel show the results comming from using all the $210$ mocks for each model, the second and third panel from the boot-strapping of spatially uncorrelated and correlated fields, respectively.

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
\end{center} 
\caption{ \label{figure:landscape} 
}
\end{figure}

\subsection{Selection of the preferred halo mass}

\subsection{Estimating the Galaxy Bias from the Halo Masses}
Using the results from the previous sections it is possible to infre the bias of $z\sim 3$ LAEs. Considering a number of $N_{\rm fields}$ the expected number density of galaxies around the region located at $x_{i}$ is $n_{i}=\bar{n}[1+ b\delta_{\rm DM}(x_{i})]$, where $\bar{n}$ is the average galaxy number density and $\delta_{\rm DM}\equiv (\rho - \bar{\rho})/\bar{\rho}$ is the matter overdensity in the field [REF robertson].

We calculate the bias for each mock catalog in the best models using the corresponding dark matter overdensity in the simulation. This results in a distribution of bias values for each model. The results for this calculation are presented in Figure XX.  We compare this resul agains the following estimation $b^{2}\sim {\sigma_{N}^{2} - \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the average number counts in the $N_{fields}$, $\sigma_{N}$ is their dispersion and $\sigma_{DM}$ is the matter variance over many survey volumes.

\subsection{Prediction for the angular correlation function}

We calculate the angular correlation function (ACF) for the best models for a mock survey with a total surface area equal to the full survey by Yamada et al 2012. We compare these results with the observed ACF reported by Gawiser et al. XXX.

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/correlation_best_models_with_obs_comp.png}
\end{center} 
\caption{ \label{figure:landscape} 
}
\end{figure}

%\begin{figure}
% \input{plots/TCF}
%\end{figure}

\section{Conclusions}

\end{document}

### 2013-01-28 paper/ms.tex
updated text

@@
 \author{
+J. E.\ Forero-Romero\altaffilmark{1}, 
 J. Mej\'ia \altaffilmark{2}, 
-J. E.\ Forero-Romero\altaffilmark{1}, 
 }
 
-\altaffiltext{1}{XXX}
-\altaffiltext{2}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia, \email{je.forero@uniandes.edu.co}}
-
+\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia, \email{je.forero@uniandes.edu.co}}
+\altaffiltext{2}{XXX}
 \date{\today}
@@
 \section{Methodology}
-In this paper we constrain the typical mass of dark matter halos hosting LAES at $z=3.1$.
+In this Letter we constrain the typical mass of dark matter halos hosting LAES at $z=3.1$.
 Our model is based on the number density information obtained in the recent large scale survey presented by XXX where XXX LAEs are detected over 7 fields of $\sim 46 \times 35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed fields of $XXX$ deg$^{2}$.
 
-The diverse physical and astrophysical uncertainties in obtaining statistical prediction for the Lyman-alpha line are the largest impediment to consruct an ab-iitio model for LAEs.
-In this Letter we want to by-pass this approach by constructing models with the sole objective of reproducing the cosmic variance in the number density of LAEs.
+Both the spatial distribution and luminosities of the galaxies have, at least in a statistical sense, informatio to constrain theoretical model of LAEs.
+The most detailed theoretical models are also faced to diverse physical and astrophysical uncertainties in obtaining statistical prediction for the Lyman-alpha line.
+This uncertainties are largest impediment to consruct an ab-iitio model for LAEs.
+
+In this Letter we want to step back and reduce the complexity of our model, with the sole objective of reproducing the cosmic variance in the number density of LAEs.
 Afterwards we will interpret the implications of this result for physical models for Lyman-alpha emitting galaxies.
 
-The model is based on the predictions of a large volume high resolution N-body simulation describing the gravitational dynamics of dark matter.
+Our model is based on the predictions of a large volume high resolution N-body simulation describing the gravitational dynamics of dark matter.
 We do not have an strong bias towards the theoretical expectation of what the mass of the dark matter halo hosting the galaxy should be.
@@
 
-In this paper we only use the results of Yamada et al due to the homogenous conditions  to define their samples.
-We do this for homogeinity in the observation and data reduction techniques.
-There are other surveys by XXX an XXX that cover similar regions, but they use different criteria on the equivalent width (EW) cuts to construct the LAE samples.
+In this paper we only use the results of Yamada et al to constraint our model.
+This choice is made because their surveys is the largest in area with a set of homogenous conditions that define the LAE sample.
+Other surveys by XXX an XXX that cover similar regions, but they use different criteria on the equivalent width (EW) cuts to construct the LAE samples.
 Different cuts in the EW can change the number of LAEs to be included in the catalog.
@@
 \subsection{The Simulation and Halo Catalogs}
-We use the Bolshoi simulation data available from their public database accessible via SQL query interface.
-The simulation was performed in a cubic volume of 250 $h^{-1}$ Mpc on a side.
+
+The Bolshoi simulation was performed in a cubic volume of 250 $h^{-1}$ Mpc on a side.
 It includes dark matter distribution is sampled using $2048^{3}$ particles, which translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.
 
-The cosmological parameters are consistent with a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$, cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the power spectrum $\sigma_{8}=0.82$
+The cosmological parameters are consistent with a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$, cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the power spectrum $\sigma_{8}=0.82$ [REF].
 
@@
 We have veryfied that the main results we present in this paper also hold if instead we use halo catalogs constructed from a the Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are defined to have an density of 200 times the critical density.
+The minimum halo mass in the models we construct in this Letter correspond to groups of $\sim 75$ particles.
 
@@
 
-\subsection{Mock Catalogs: Populating Halos with LAEs}
+\subsection{Populating Halos with LAEs}
 \label{subsec:mocks}
-We start from the Friends-of-Friends (FOF) catalog at $z=3.1$.
-The catalog is split into disjoint sub-volumes with the same geometry probed by Suprime-CAM and the narrow band filter of $46\times 35\times 41$ $h^{-3}Mpc^{3}$ .
+
+The model that populates halos with LAEs is based one-to-one correspondence: each halo can only host a single LAE.
+There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE.
+In what follows we will describe by the letter ${\mathcal M}$ a model spanning a set of mock catalogs calculated by fixed values of these three parameters.
+
+We highlight that we do not intent to guess the luminosity of each LAE.
+We only care about its existence.
+Physically speaking we are interested in constraining the halo mass above which a LAE can be observed under the conditions defined by Yamada et al.
+
+\subsection{Making Mock Fields}
+
+We create LAEs mock fields from disjoing volumes in the simulation with the same geometry probed by Suprime-CAM and the narrow band filter of $46\times 35\times 41$ $h^{-3}Mpc^{3}$ .
 There are in total $5\times 7 \times 6=210$ of such sub-volumes in a snapshot of the Bolshoi simulation.
 We take the $z$ direction to correspond to the redshift direction in the survey.
-This corresponds to a total area of $880$ arcmin$^{2}$ for each projected sub-volume.
+This corresponds to a total area of $880$ arcmin$^{2}$ for each mock field.
 
-The model that creates a mock is based in a one-to-one correspondence of LAEs to DM halos: each halo can only host a single LAE.
-There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE.
-In what follows we will describe by the letter ${\mathcal M}$ a model spanning a set of mock catalogs calculated by fixed values of these three parameters.
+Next we group the mock fields in three different ways to construct the LAEs number density distribution The first way we fully take into account the observational constraints and constructs $30$ different mock surveys, each one composed of $12$ mock fields, out of which $7$ correspond to contiguous sub-boxes in the simulation to mimick XXX, $3$ are also contiguous between them but not to the first $7$ fields to mimick XXX and finally $2$ non-contiguous fields that correspond to the XXX data.
+
+From this set of sub-volumes we create groups of we create two different kinds of mock surveys.
+The first one is constructed to match the observatinal geometry of the observational fields included in this
 

### 2013-02-01 paper/ms.tex
updated text

@@
 \subsection{The Observational Constraints}
-We take as a reference the recently published results of a panoramic survey of LAES at z=3.1 by Yamada et al.
+
+Our observational reference are the recently published results of a panoramic survey of LAES at z=3.1 by Yamada et al.
 2012.
@@
 
-In this paper we only use the results of Yamada et al to constraint our model.
-This choice is made because their surveys is the largest in area with a set of homogenous conditions that define the LAE sample.
+The choice to have only one the data from Yamada et al 2012 as reference was  made because their surveys is the largest in area with a set of homogenous conditions that define the LAE sample.
 Other surveys by XXX an XXX that cover similar regions, but they use different criteria on the equivalent width (EW) cuts to construct the LAE samples.
@@
 It includes dark matter distribution is sampled using $2048^{3}$ particles, which translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.
-
 The cosmological parameters are consistent with a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$, cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the power spectrum $\sigma_{8}=0.82$ [REF].
 
-We have used halo catalogs constructed with a Friend-of-Friends (FOF) algorithm with a linking lenght of 0.17 times the interparticle distance.
+We use halo catalogs constructed with a Friend-of-Friends (FOF) algorithm with a linking lenght of 0.17 times the interparticle distance.
 We have veryfied that the main results we present in this paper also hold if instead we use halo catalogs constructed from a the Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are defined to have an density of 200 times the critical density.
 The minimum halo mass in the models we construct in this Letter correspond to groups of $\sim 75$ particles.
-
-The catalogs we have used here are obtained from a publicly available Multidark database \footnote{{\tt http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
+The catalogs were obtained from the publicly available Multidark database \footnote{{\tt http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
 
@@
 There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE.
-In what follows we will describe by the letter ${\mathcal M}$ a model spanning a set of mock catalogs calculated by fixed values of these three parameters.
+In what follows we will describe by the letter ${\mathcal M}$ a model defined by these three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.
 
-We highlight that we do not intent to guess the luminosity of each LAE.
-We only care about its existence.
-Physically speaking we are interested in constraining the halo mass above which a LAE can be observed under the conditions defined by Yamada et al.
+We stress that we do not intent to build a model for the luminosity of each LAE.
+Physically speaking we are primarely interested in constraining the halo mass above which there are detectable LAEs.
+under the conditions defined by Yamada et al.
 
-\subsection{Making Mock Fields}
+For each mode ${\mathcal M}$ we create mock field from disjoint volumes in the simulation with the same geometry probed by Suprime-CAM and the narrow band filter, namely $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where the last dinemsion goes in the redshift direction, corresponding to a total area of $880$ arcmin$^{2}$ for each mock field.
+There is a total $5\times 7 \times 6=210$ of such sub-volumes in a snapshot of the Bolshoi simulation.
 
-We create LAEs mock fields from disjoing volumes in the simulation with the same geometry probed by Suprime-CAM and the narrow band filter of $46\times 35\times 41$ $h^{-3}Mpc^{3}$ .
-There are in total $5\times 7 \times 6=210$ of such sub-volumes in a snapshot of the Bolshoi simulation.
-We take the $z$ direction to correspond to the redshift direction in the survey.
-This corresponds to a total area of $880$ arcmin$^{2}$ for each mock field.
+Next we group these $210$ mock fields in three different ways to construct the LAEs number density distribution.
+The first way we follow the observational setup and constructs $15$ different mock surveys, each one composed of $12$ mock fields, out of which $7$ correspond to contiguous sub-boxes in the simulation to mimick the whole SSA22, $3$ are also contiguous between them but not to the first $7$ fields to mimick the SXDS fields and finally $2$ non-contiguous fields that correspond to the SDF and GOODS-North fields.
+This will produce $15$ different distributions for the number density for a given model ${\mathrm M}$.
+The second is similar to the first one.
+There aare $15$ different mock surveys with $12$ mock fields each, but this time each field corresponds to uncorrelated sub-boxes in the simulation.
+The third way in only has $1$ mock survey containing all the $210$ mock fields, in this setup there is only one predicted number density distribution for each model ${\mathrm M}$
 
-Next we group the mock fields in three different ways to construct the LAEs number density distribution The first way we fully take into account the observational constraints and constructs $30$ different mock surveys, each one composed of $12$ mock fields, out of which $7$ correspond to contiguous sub-boxes in the simulation to mimick XXX, $3$ are also contiguous between them but not to the first $7$ fields to mimick XXX and finally $2$ non-contiguous fields that correspond to the XXX data.
-
-From this set of sub-volumes we create groups of we create two different kinds of mock surveys.
-The first one is constructed to match the observatinal geometry of the observational fields included in this
+The advantage of these three ways of sampling is that it allows us to explore the effects of both cosmic variance and the correlation between fields.
+Comparing the results of the first and second method will help us to quantify the effect of field correlation, while compating the first and the third method will serve us to gauge the impace of cosmic variance.
 
 \subsection{Model Sampling and Selection}
-We generate a series of models ${\mathcal M}_{I}$, where $I$ corresponds to set of input values $I=\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$.
-We explore a wide range of values in the $I$ parameter space as follows.
-$M_{\rm min}$ and $M_{\rm max}$ are allowed to take 15 different values evenly spaced by $0.2$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.8$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.2$ up to $\log_{10}M_{\rm min}=13.0$ shifted by $0.2$ dex.
+
+We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$.
+We explore a wide range of values in the parameter space as follows.
+$M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$.
 The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$.
-In total the number of different sets of input parameters to be explored is $15\times 15\times 100 = 22500$.
+In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 290000$.
 
-For each model we generate 210 mock catalogs corresponding to each of the sub-volumes extracted in the box.
+For each model we generate the number density distributions in three different ways as described in the previous section.
 For each volume we project along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$.
-Using the $210$ values for the surface density we perform a Kolmogorov-Smirnov test to compare it against the $12$ observational values and obtain the probability to reject the null hypothesis that the two data sets come from the same distribution.
-
-We also boot-strap these 210 mocks for each model to construct sub-samples of 12 catalogs corresponding to the 12 observed fields.
-We do this boot-strapping in two different ways.
-First, by selecting the 12 catalogs in a random fashion without taking into account any spatial information.
-Second, by selecting sets of catalogs taking into account the spatial correlations present in observations.
-For instance, 7 out of the 12 catalogs are selected to be spatially contiguous as the SSA22 field, 3 fields correspond to the SXDS fields and 2 remaining catalogs are spatially uncorrelated to resemble the SDF and GOODS-North fields.
-We do this boot-straping 15 times and keep the median value for the KS test.
+For each number density distributionwe perform a Kolmogorov-Smirnov test to compare it against the $12$ observational values.
+From this test we obtain the value $0<P<1$ to reject the null hypothesis that the two data sets come from the same distribution.
+In this paper we use values of $P<0.1$ to consider that the simulated and observed number densities do not come from the same distributions.
 

### 2013-02-03 paper/ms.tex
new changes

@@
 
-We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$.
-We explore a wide range of values in the parameter space as follows.
+We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as follows.
 $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$.
@@
 
-For each model we generate the number density distributions in three different ways as described in the previous section.
-For each volume we project along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$.
-For each number density distributionwe perform a Kolmogorov-Smirnov test to compare it against the $12$ observational values.
-From this test we obtain the value $0<P<1$ to reject the null hypothesis that the two data sets come from the same distribution.
-In this paper we use values of $P<0.1$ to consider that the simulated and observed number densities do not come from the same distributions.
-
-Summarizing, for each model $M_{\rm min}, M_{\rm max}, f_{\rm occ}$, there are three different ways to calculate a KS test, which is in turn used to select the models that best reproduce the observations: from the full 210 mock sample, from 20 boot-strapped sets of 12 catalogs and finally from the same kind of boot-strapped catalogs that take into account the correlation in neighboughring observed fields.
+For each model ${\mathcal M}$ we compute the LAE surface density distributions for the three different ways of grouping the mock fields, as described in the previous section.
+For each sub-volume we project the positions of the LAE hosting halos along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$.
+For each number density distribution we perform a Kolmogorov-Smirnov againsg the $12$ surface density observational values.
+From this test we obtain the value $0<P<1$ to reject the null hypothesis, namely that the two data sets come from the same distribution.
+In this paper we use values of $P>0.1$ to consider that the simulated and observed number densities come from the same distribution.
 
@@
 \begin{center}
-\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
+%\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
 \caption{ \label{figure:laes_dist} Cumulative mass function of dark matter haloes in the $210$ sub-volumes of $46\times 35\times 41$ $h^{-3}Mpc^{3}$.
@@
 
-\subsection{General Constraints on the Occupation Fraction}
-The number density of dark matter halos per unit comoving volume is a well defined quantity for a given cosmological model, modulo the effects introduced by cosmic variance.
-The occupation fraction $f_{\rm occ}$ acts a renormalization factor of the halo number density to match the observational constrain of the surface density of LAEs.
+\subsection{Dark Matter Halo Number Density}
+...
+We comment first on the intergrated dark matter halo surface density as a function of mass for each one o the 210 sub-volumes in the Bolshoi simulation.
+This will allows us to better understand the expected trends for the LAEs preferred mass and the occupation fraction.
+Figure \ref{fig:laes_dist} show these distributions.
 
-In Fig.
-1 we show the cumulative mass function of dark matter haloes in the $210$ sub-volumes extracted from the Bolshoi simulation.
-This mass function is expressed as a surface density by projecting the positions of all haloes along the $z$ direction and taking the surface of the rectangle in the $x$-$y$ plane as the nominal $880$ arcmin$^{2}$ we calculated in \S\ref{subsec:mocks}.
-The same figure shows as a vertical band the range of observed surface density of LAEs.
+The shadowed region in Figure \ref{fig:laes_dist} shows the surface density values allowed by the observations.
+This figure tells us by inspection which model parameters cannot reproduce the observations.
+The regions where the DM surface density values are below the observational constraint correspond to high masses.
+For a model ${\mathcal M}$ with a minimum mass in this high mass range, the observations present a surface density to high to be possible achieved.
 
-There is a characteristic halo mass $M_{\rm c}$ above which the halo mass functions are below the observational constraint, meaning that models with model parameters $I=\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ with $M_{\rm min}> M_{\rm c}$ have a number densiy that is already lower than the observational one, regardless of the value of $f_{\rm occ}$.
-Conversely, below for models with $M_{\rm min}<M_{\rm c}$ have a possibility of success if the occupation fraction $f_{\rm occ}$ is tuned as to lower the halo number density down to the observed value.
+Conversely the regions where the halo surface density is higher than the observational constraints correspond to models ${\mathcal M}$ with a minimum mass below this threshold.
+Models with this minimum mass hava a chance for successfuly reproducing observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to lower the halo number density down to the observed value.
 
-For the reasons explained above, the occupation fraction $f_{\rm occ}$ has a strong dependence on the mass parameters of the model $M_{\rm min}$ and $M_{\rm max}$.
-This allows us to focus in presenting the results of the best models in terms of these two parameters, knowing that the occupation fraction is already tightly constrained.
+\subsection{Selection of the preferred halo mass}
 
-\subsection{Likelihood landscapes}
-
-Figure \label{figure:landscape} presents the probability from the KS-tests that the observed and simulated surface densities can be considered as comming from similar distributions.
-For the reasons explained in the last section, we only show the results in the $M_{\rm min}-M_{\rm max}$ plane.
-The first panel show the results comming from using all the $210$ mocks for each model, the second and third panel from the boot-strapping of spatially uncorrelated and correlated fields, respectively.
+Figure \label{figure:landscape} presents the regions in the parameter space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of $P>0.1$.
+Each panel corresponds to the three different ways of grouping the mock fields.
+In the case of the methods {\tt{MatchObs}} and {\tt{RandomObs}} the color code indicates the fraction of these 15 mock surveys with with $P>0.1$.
+The third panel shows the result for the method {\tt{FullVolume}}, in this case the color code correspond to the value of $P$ for a given model.
 
@@
 \begin{center}
-\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
+%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
 \end{center} 
@@
 \end{figure}
-
-\subsection{Selection of the preferred halo mass}
 

### 2013-02-04 paper/ms.tex
3 paragraphs on the Results section

@@
 \section{Introduction}
-Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a central topic in studies of structure formation in the Universe.
+
+Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
+central topic in studies of structure formation in the Universe.
 The reason is the diverse range of fields where they are helpful, LAEs can be used as probes of reionization, tracers of large scale structure, signposts for low metallicity stellar populations and markers of the the galaxy formation process through cosmic history.
@@
 
-The model that populates halos with LAEs is based one-to-one correspondence: each halo can only host a single LAE.
+The model that populates halos with LAEs is based on a one-to-one correspondence: each halo can only host a single LAE.
 There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE.
@@
 
-The advantage of these three ways of sampling is that it allows us to explore the effects of both cosmic variance and the correlation between fields.
+The advantage of these three sampling ways is that they allow us to explore the effects of both cosmic variance and the correlation between fields.
 Comparing the results of the first and second method will help us to quantify the effect of field correlation, while compating the first and the third method will serve us to gauge the impace of cosmic variance.
@@
 The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$.
-In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 290000$.
+In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 9\times 10^{4}$.
 
@@
 
+\begin{figure}
+\begin{center}
+%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
+\end{center} 
+\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with $P>0.1$\label{figure:landscape}.}
+\end{figure}
+
 Figure \label{figure:landscape} presents the regions in the parameter space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of $P>0.1$.
@@
 
-\begin{figure}
-\begin{center}
-%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
-\end{center} 
-\caption{ \label{figure:landscape} 
-}
-\end{figure}
+These results distinguish three mass regimes.
+In the first regime, at high mass values, we find that LAE models with minimum mass of $M_{\rm min}>XXX$ are not compatible with observations as expected from the analysis in the previous subsection.
+Below this mass down to $M_{\rm min}=XXX$ any minium and maximum mass models are compatible with LAEs observations.
+In a thirds mass regime, for low mass values $M_{\rm min}<$ only a limited range of models with $M_{\rm max}$ is able to reproduce observations.
+
+In these three different mass regimes the occupation monotonically decreases as a function of the minimum halo mass $M_{\rm min}$.
+In Figure XXX we show this treend in three panels following the same correspondence as Figure XXX.
+From these results we interpret that the different mass regimes that were identified correspond to best fit models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm occ}\sim 0$, respectively.
+
+There are some models where the KS test yield values of $P\sim 1$.
+To illustrate the kind of success represented by these models, we have selected these best ones in the case of the method {\tt{MatchObs}}.
+Figure XXX shows in the main panel the spatial distribution of the mock surveys, the smaller panel shows the corresponding surface density distribution and the observational constraint.
 

### 2013-02-05 code/generate_mock_LAEs.py
pytho script to generate mock laes

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+
+import numpy as np
+import sys as sys
+
+def generate_all_models():
+    
+    log_m = np.arange(10.0, 13.1, 0.1)
+    box_size = 250.0
+    delta_x  = 46.0
+    delta_y = 35.0
+    delta_z = 41.0
+    n_i = int(box_size/delta_x)
+    n_j = int(box_size/delta_y)
+    n_k = int(box_size/delta_z)
+    
+    user = "/home/jeforero/"
+    repo_path="Dropbox/CosmicVarianceLAES/"
+    dmh_path=user+repo_path+"data/dark_matter/FOF/"
+    laes_path=user+repo_path+"data/laes/FOF/"
+
+    n_models = n_i * n_j * n_k
+    n_bins = log_m.size
+
+    model_numbers = np.zeros((n_i,n_j,n_k,n_bins))
+
+    for i in range(n_i):
+        for j in range(n_j):
+            for k in range(n_k):
+                id0 = k+n_k*(j + n_j*i) 
+                print i, j, k
+                dmh_filename=dmh_path+"halos_bolshoi_"+str(i)+"-"+str(j)+"-"+str(k)+".csv"
+                halos_prop=np.loadtxt(dmh_filename,delimiter=",",skiprows=12) 
+
+                halos_mass=halos_prop[:,4]
+                hist, edges = np.histogram(halos_mass, bins=log_m)
+                #print hist, edges, hist.size, edges.size, n_bins
+                for l in range(n_bins-1):
+                    model_numbers[i,j,k,l] = hist[l]
+    
+    for l in range(n_bins-1):
+        for m in range(l+1, n_bins):
+            model_name = 'model_{0}_{1}_{2}.dat'.format(log_m[l], log_m[m], 1.0)
+            print l, model_name
+            out = open(laes_path+model_name, "w")
+            for i in range(n_i):
+                for j in range(n_j):
+                    for k in range(n_k):
+                        id0 = k+n_k*(j + n_j*i) 
+                        value = sum(model_numbers[i,j,k,l:m])
+                        out.write("%d %d %d %d %d\n"%(id0, i, j, k, value))
+            out.close()
+generate_all_models()
+
+
+

### 2013-02-06 paper/ms.tex
2 new paragraphs. line breaks added

@@
 Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
-central topic in studies of structure formation in the Universe.
-The reason is the diverse range of fields where they are helpful, LAEs can be used as probes of reionization, tracers of large scale structure, signposts for low metallicity stellar populations and markers of the the galaxy formation process through cosmic history.
+central topic in studies of structure formation in the Universe. The
+reason is the diverse range of fields where they are helpful, LAEs can
+be used as probes of reionization, tracers of large scale structure,
+signposts for low metallicity stellar populations and markers of the
+the galaxy formation process through cosmic history.
 
-At the same time, theoretical and observational developments have contributed to the emergence of a paradigm to describe structure formation in a cosmological context.
-In this context it is considered that dominant matter content of the Universe is to be found in dark matter, whereby each galaxy is hosted by larger dark matter structure known as a halo.
+At the same time, theoretical and observational developments have
+contributed to the emergence of a paradigm to describe structure
+formation in a cosmological context. In this context it is considered
+that dominant matter content of the Universe is to be found in dark
+matter, whereby each galaxy is hosted by larger dark matter structure
+known as a halo.
 
-Most models of galaxy formation find that the mass of the halo largely determines key properties of the galaxy such as its stellar mass and star formation rate.
-Processes that regulate the star formation cycle are also though to be strongly dependent on its mass.
-Furthermore, the spatial clustering of galaxies on large scales is entirely dictated by the halo distribution.
-For the reasons mentioned above, finding the typical dark matter halo mass hosting LAEs represents a significant step forward to understand the nature of this population in the context of LCDM.
+Most models of galaxy formation find that the mass of the halo largely
+determines key properties of the galaxy such as its stellar mass and
+star formation rate. Processes that regulate the star formation cycle
+are also though to be strongly dependent on its mass. Furthermore, the
+spatial clustering of galaxies on large scales is entirely dictated by
+the halo distribution.  For the reasons mentioned above, finding the
+typical dark matter halo mass hosting LAEs represents a significant
+step forward to understand the nature of this population in the
+context of LCDM.
 
-Some theoretical approaches to this problem have been based on a forward modelling.
-Starting from the DM halo population, the corresponding intrinsic star formation properties are infered and statistics such as the luminosity function, the correlation function and the equivalent width distributions.
-Such modelling has been implemented from analytic considerations, semi-analytic models and full N-body hidrodynamical simulations.
+Some theoretical approaches to this problem have been based on a
+forward modelling. Starting from the DM halo population, the
+corresponding intrinsic star formation properties are infered and
+statistics such as the luminosity function, the correlation function
+and the equivalent width distributions. Such modelling has been
+implemented from analytic considerations, semi-analytic models and
+full N-body hidrodynamical simulations.
 
-Added to the uncertainties in the astrophysical processeses describing star formation in galactic populations, a highly debated steps in this approach is the calculation of the fraction of Lyman-$\alpha$ photons that escape the galaxy to the observer.
-Given the resonance nature of the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the density, temperature, topology and kinematics of the neutral Hydrogen in the interstellar medium (ISM).
+Added to the uncertainties in the astrophysical processeses describing
+star formation in galactic populations, a highly debated steps in this
+approach is the calculation of the fraction of Lyman-$\alpha$ photons
+that escape the galaxy to the observer. Given the resonance nature of
+the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the
+density, temperature, topology and kinematics of the neutral Hydrogen
+in the interstellar medium (ISM).
 
-This complexity makes the use of monte-carlo simulations for the radiative transfer a required tool to obtain physically sound results, although the degeneracy in the physical parameters involved in the problem makes it difficult to achieve a robust consensus on what is the theoretical expected value for the Lyman-$alpha$ escape fraction in high redshift.
+This complexity makes the use of monte-carlo simulations for the
+radiative transfer a required tool to obtain physically sound results,
+although the degeneracy in the physical parameters involved in the
+problem makes it difficult to achieve a robust consensus on what is
+the theoretical expected value for the Lyman-$alpha$ escape fraction
+in high redshift.
 
-Throughout this Letter we assume a $\Lambda$CDM cosmology with the following values for the cosmological parameters, $\Omega_{m}=0.27$, $\Omega_{\Lambda}=0.73$ and $h=0.70$, corresponding to the matter density, vacuum density and the Hubble constant in units of 100 km s$^{-1}$ Mpc$^{-1}$.
+Throughout this Letter we assume a $\Lambda$CDM cosmology with the
+following values for the cosmological parameters, $\Omega_{m}=0.27$,
+$\Omega_{\Lambda}=0.73$ and $h=0.70$, corresponding to the matter
+density, vacuum density and the Hubble constant in units of 100 km
+s$^{-1}$ Mpc$^{-1}$.
 
 \section{Methodology}
-In this Letter we constrain the typical mass of dark matter halos hosting LAES at $z=3.1$.
-Our model is based on the number density information obtained in the recent large scale survey presented by XXX where XXX LAEs are detected over 7 fields of $\sim 46 \times 35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed fields of $XXX$ deg$^{2}$.
+In this Letter we constrain the typical mass of dark matter halos
+hosting LAES at $z=3.1$. Our model is based on the number density
+information obtained in the recent large scale survey presented by XXX
+where XXX LAEs are detected over 7 fields of $\sim 46 \times
+35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed
+fields of $XXX$ deg$^{2}$.
 
-Both the spatial distribution and luminosities of the galaxies have, at least in a statistical sense, informatio to constrain theoretical model of LAEs.
-The most detailed theoretical models are also faced to diverse physical and astrophysical uncertainties in obtaining statistical prediction for the Lyman-alpha line.
-This uncertainties are largest impediment to consruct an ab-iitio model for LAEs.
+Both the spatial distribution and luminosities of the galaxies have,
+at least in a statistical sense, informatio to constrain theoretical
+model of LAEs. The most detailed theoretical models are also faced to
+diverse physical and astrophysical uncertainties in obtaining
+statistical prediction for the Lyman-alpha line. This uncertainties
+are largest impediment to consruct an ab-iitio model for LAEs.
 
-In this Letter we want to step back and reduce the complexity of our model, with the sole objective of reproducing the cosmic variance in the number density of LAEs.
-Afterwards we will interpret the implications of this result for physical models for Lyman-alpha emitting galaxies.
+In this Letter we want to step back and reduce the complexity of our
+model, with the sole objective of reproducing the cosmic variance in
+the number density of LAEs. Afterwards we will interpret the
+implications of this result for physical models for Lyman-alpha
+emitting galaxies.
 
-Our model is based on the predictions of a large volume high resolution N-body simulation describing the gravitational dynamics of dark matter.
-We do not have an strong bias towards the theoretical expectation of what the mass of the dark matter halo hosting the galaxy should be.
-Instead, we fully explore the parameter space of our simplified model.
-The only cut we impose is that observed LAEs do not reside in dark matter halos with masses less than 10$^{10}$hMsun [citation].
+Our model is based on the predictions of a large volume high
+resolution N-body simulation describing the gravitational dynamics of
+dark matter. We do not have an strong bias towards the theoretical
+expectation of what the mass of the dark matter halo hosting the
+galaxy should be.  Instead, we fully explore the parameter space of
+our simplified model. The only cut we impose is that observed LAEs do
+not reside in dark matter halos with masses less than 10$^{10}$hMsun
+[citation].
 
-In the following subsections we describe the most relevant features of the observational data, the N-body simulation we use, our model and its parameters together with the method to compare its predictions against observations.
+In the following subsections we describe the most relevant features of
+the observational data, the N-body simulation we use, our model and
+its parameters together with the method to compare its predictions
+against observations.
 
@@
 
-Our observational reference are the recently published results of a panoramic survey of LAES at z=3.1 by Yamada et al.
-2012.
-This survey was conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera, which has a field of view covering $34\times 27$ arcmin, corresponding to a comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.
-The narrow band filter is centered at $4977$ \AA with a $77$\AA width, corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc $h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line centered at $z=3.09$.
+Our observational reference are the recently published results of a
+panoramic survey of LAES at z=3.1 by Yamada et al. 2012. This survey
+was conducted with the Subaru 8.2m telescope and the Subaru Prime
+Focus Camera, which has a field of view covering $34\times 27$ arcmin,
+corresponding to a comoving scale of $46\times35$ Mpc $h^{-1}$ at
+$z=3.09$. The narrow band filter is centered at $4977$ \AA with a
+$77$\AA width, corresponding to the redshift range $z=3.062-3.125$ and
+$41$ Mpc $h^{-1}$ comoving scale for the detection of the
+Lyman-$\alpha$ line centered at $z=3.09$.
 
-The choice to have only one the data from Yamada et al 2012 as reference was  made because their surveys is the largest in area with a set of homogenous conditions that define the LAE sample.
-Other surveys by XXX an XXX that cover similar regions, but they use different criteria on the equivalent width (EW) cuts to construct the LAE samples.
-Different cuts in the EW can change the number of LAEs to be included in the catalog.
-This cuts have an impact on the fainter LAEs which are more abundante than brighter ones.
-Different definitions of the EW cuts can yield number densities different by a factor of two [REF, I think Yamada has some numbers].
+The choice to have only one the data from Yamada et al 2012 as
+reference was  made because their surveys is the largest in area with
+a set of homogenous conditions that define the LAE sample. Other
+surveys by XXX an XXX that cover similar regions, but they use
+different criteria on the equivalent width (EW) cuts to construct the
+LAE samples. Different cuts in the EW can change the number of LAEs to
+be included in the catalog. This cuts have an impact on the fainter
+LAEs which are more abundante than brighter ones. Different
+definitions of the EW cuts can yield number densities different by a
+factor of two [REF, I think Yamada has some numbers].
 
-The survey covered four independent fields.
-The first is the SSA22 field of $1.38$ deg$^2$ with $1394$ detected LAEs, this field has been known to harbor a region with a large density excess of galaxies.
-The second observed region is composed by the fields Subaru/{\it XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a total of $0.58$ deg$^2$ and $386$ LAEs.
-The third and fourth fields are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs, and the fild arotund the Great Observatory Optical Deep Survey North (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs.
-In Table 1 we summarize the values we use in throughout this paper for the each field, covered area, measured surface LAE number density and inferred number volume density.
+The survey covered four independent fields. The first is the SSA22
+field of $1.38$ deg$^2$ with $1394$ detected LAEs, this field has been
+known to harbor a region with a large density excess of galaxies. The
+second observed region is composed by the fields Subaru/{\it
+  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
+total of $0.58$ deg$^2$ and $386$ LAEs. The third and fourth fields
+are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs,
+and the fild arotund the Great Observatory Optical Deep Survey North
+(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs. In Table 1 we summarize
+the values we use in throughout this paper for the each field, covered
+area, measured surface LAE number density and inferred number volume
+density.
 
@@
 
-The Bolshoi simulation was performed in a cubic volume of 250 $h^{-1}$ Mpc on a side.
-It includes dark matter distribution is sampled using $2048^{3}$ particles, which translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.
-The cosmological parameters are consistent with a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$, cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the power spectrum $\sigma_{8}=0.82$ [REF].
+The Bolshoi simulation was performed in a cubic volume of 250 $h^{-1}$
+Mpc on a side. It includes dark matter distribution is sampled using
+$2048^{3}$ particles, which translates into a particle mass of $m_{\rm
+  p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.  The cosmological
+parameters are consistent with a WMAP5 and WMAP7 data with a matter
+density $\Omega_{\rm m} = 0.27$, cosmological constant
+$\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope
+of the power spectrum $n=0.95$ and normalization of the power spectrum
+$\sigma_{8}=0.82$ [REF].
 
-We use halo catalogs constructed with a Friend-of-Friends (FOF) algorithm with a linking lenght of 0.17 times the interparticle distance.
-We have veryfied that the main results we present in this paper also hold if instead we use halo catalogs constructed from a the Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are defined to have an density of 200 times the critical density.
-The minimum halo mass in the models we construct in this Letter correspond to groups of $\sim 75$ particles.
-The catalogs were obtained from the publicly available Multidark database \footnote{{\tt http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
+We use halo catalogs constructed with a Friend-of-Friends (FOF)
+algorithm with a linking lenght of 0.17 times the interparticle
+distance. We have veryfied that the main results we present in this
+paper also hold if instead we use halo catalogs constructed from a the
+Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are
+defined to have an density of 200 times the critical density. The
+minimum halo mass in the models we construct in this Letter correspond
+to groups of $\sim 75$ particles. The catalogs were obtained from the
+publicly available Multidark database \footnote{{\tt
+    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
 
@@
 
-The model that populates halos with LAEs is based on a one-to-one correspondence: each halo can only host a single LAE.
-There are three physical parameters in the model: the halo mass range $M_{\rm min}< M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that effectively host a LAE.
-In what follows we will describe by the letter ${\mathcal M}$ a model defined by these three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.
+The model that populates halos with LAEs is based on a one-to-one
+correspondence: each halo can only host a single LAE. There are three
+physical parameters in the model: the halo mass range $M_{\rm min}<
+M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
+  occ}$ of such halos that effectively host a LAE. In what follows we
+will describe by the letter ${\mathcal M}$ a model defined by these
+three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.
 
-We stress that we do not intent to build a model for the luminosity of each LAE.
-Physically speaking we are primarely interested in constraining the halo mass above which there are detectable LAEs.
-under the conditions defined by Yamada et al.
+We stress that we do not intent to build a model for the luminosity of
+each LAE. Physically speaking we are primarely interested in
+constraining the halo mass above which there are detectable
+LAEs. under the conditions defined by Yamada et al.
 
-For each mode ${\mathcal M}$ we create mock field from disjoint volumes in the simulation with the same geometry probed by Suprime-CAM and the narrow band filter, namely $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where the last dinemsion goes in the redshift direction, corresponding to a total area of $880$ arcmin$^{2}$ for each mock field.
-There is a total $5\times 7 \times 6=210$ of such sub-volumes in a snapshot of the Bolshoi simulation.
+For each mode ${\mathcal M}$ we create mock field from disjoint
+volumes in the simulation with the same geometry probed by Suprime-CAM
+and the narrow band filter, namely $46\times 35\times 41$
+$h^{-3}$Mpc$^{3}$ where the last dinemsion goes in the redshift
+direction, corresponding to a total area of $880$ arcmin$^{2}$ for
+each mock field. There is a total $5\times 7 \times 6=210$ of such
+sub-volumes in a snapshot of the Bolshoi simulation.
 
-Next we group these $210$ mock fields in three different ways to construct the LAEs number density distribution.
-The first way we follow the observational setup and constructs $15$ different mock surveys, each one composed of $12$ mock fields, out of which $7$ correspond to contiguous sub-boxes in the simulation to mimick the whole SSA22, $3$ are also contiguous between them but not to the first $7$ fields to mimick the SXDS fields and finally $2$ non-contiguous fields that correspond to the SDF and GOODS-North fields.
-This will produce $15$ different distributions for the number density for a given model ${\mathrm M}$.
-The second is similar to the first one.
-There aare $15$ different mock surveys with $12$ mock fields each, but this time each field corresponds to uncorrelated sub-boxes in the simulation.
-The third way in only has $1$ mock survey containing all the $210$ mock fields, in this setup there is only one predicted number density distribution for each model ${\mathrm M}$
+Next we group these $210$ mock fields in three different ways to
+construct the LAEs number density distribution. The first way we
+follow the observational setup and constructs $15$ different mock
+surveys, each one composed of $12$ mock fields, out of which $7$
+correspond to contiguous sub-boxes in the simulation to mimick the
+whole SSA22, $3$ are also contiguous between them but not to the first
+$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
+fields that correspond to the SDF and GOODS-North fields. This will
+produce $15$ different distributions for the number density for a
+given model ${\mathrm M}$. The second is similar to the first
+one. There aare $15$ different mock surveys with $12$ mock fields
+each, but this time each field corresponds to uncorrelated sub-boxes
+in the simulation. The third way in only has $1$ mock survey
+containing all the $210$ mock fields, in this setup there is only one
+predicted number density distribution for each model ${\mathrm M}$
 
-The advantage of these three sampling ways is that they allow us to explore the effects of both cosmic variance and the correlation between fields.
-Comparing the results of the first and second method will help us to quantify the effect of field correlation, while compating the first and the third method will serve us to gauge the impace of cosmic variance.
+The advantage of these three sampling ways is that they allow us to
+explore the effects of both cosmic variance and the correlation
+between fields. Comparing the results of the first and second method
+will help us to quantify the effect of field correlation, while
+compating the first and the third method will serve us to gauge the
+impace of cosmic variance.
 
@@
 
-We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as follows.
-$M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$.
-The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$.
-In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 9\times 10^{4}$.
+We generate a series of models ${\mathcal M}$ with different input
+parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as
+follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30
+different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from
+$\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while
+$M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to
+$\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$
+takes 100 different values from $0.01$ to $1.00$ regularly spaced by
+$0.01$. In total the number of different sets of input parameters to
+be explored is $30 \times 30\times 100 = 9\times 10^{4}$.
 
-For each model ${\mathcal M}$ we compute the LAE surface density distributions for the three different ways of grouping the mock fields, as described in the previous section.
-For each sub-volume we project the positions of the LAE hosting halos along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$.
-For each number density distribution we perform a Kolmogorov-Smirnov againsg the $12$ surface density observational values.
-From this test we obtain the value $0<P<1$ to reject the null hypothesis, namely that the two data sets come from the same distribution.
-In this paper we use values of $P>0.1$ to consider that the simulated and observed number densities come from the same distribution.
+For each model ${\mathcal M}$ we compute the LAE surface density
+distributions for the three different ways of grouping the mock
+fields, as described in the previous section. For each sub-volume we
+project the positions of the LAE hosting halos along the $z$ direction
+and calculate its surface number density in units of sources per
+arcmin$^{2}$. For each number density distribution we perform a
+Kolmogorov-Smirnov againsg the $12$ surface density observational
+values. From this test we obtain the value $0<P<1$ to reject the null
+hypothesis, namely that the two data sets come from the same
+distribution. In this paper we use values of $P>0.1$ to consider that
+the simulated and observed number densities come from the same
+distribution.
 
@@
 %\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
-\caption{ \label{figure:laes_dist} Cumulative mass function of dark matter haloes in the $210$ sub-volumes of $46\times 35\times 41$ $h^{-3}Mpc^{3}$.
-The variation in the total number of dark matter halos per sub-volume  evidences the effect of cosmic variance at such sub-volume scale.
-It is also appreciable the low population $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with $log(M/M_{\odot})>12.0$}.
+\caption{ \label{figure:laes_dist} Cumulative mass function of dark
+  matter haloes in the $210$ sub-volumes of $46\times 35\times 41$
+  $h^{-3}Mpc^{3}$. The variation in the total number of dark matter
+  halos per sub-volume  evidences the effect of cosmic variance at
+  such sub-volume scale. It is also appreciable the low population
+  $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with
+  $log(M/M_{\odot})>12.0$}. 
 \end{center} 
@@
 \subsection{Dark Matter Halo Number Density}
-...
-We comment first on the intergrated dark matter halo surface density as a function of mass for each one o the 210 sub-volumes in the Bolshoi simulation.
-This will allows us to better understand the expected trends for the LAEs preferred mass and the occupation fraction.
-Figure \ref{fig:laes_dist} show these distributions.
+... We comment first on the intergrated dark matter halo surface
+density as a function of mass for each one o the 210 sub-volumes in
+the Bolshoi simulation. This will allows us to better understand the
+expected trends for the LAEs preferred mass and the occupation
+fraction. Figure \ref{fig:laes_dist} show these distributions.
 
-The shadowed region in Figure \ref{fig:laes_dist} shows the surface density values allowed by the observations.
-This figure tells us by inspection which model parameters cannot reproduce the observations.
-The regions where the DM surface density values are below the observational constraint correspond to high masses.
-For a model ${\mathcal M}$ with a minimum mass in this high mass range, the observations present a surface density to high to be possible achieved.
+The shadowed region in Figure \ref{fig:laes_dist} shows the surface
+density values allowed by the observations. This figure tells us by
+inspection which model parameters cannot reproduce the
+observations. The regions where the DM surface density values are
+below the observational constraint correspond to high masses. For a
+model ${\mathcal M}$ with a minimum mass in this high mass range, the
+observations present a surface density to high to be possible
+achieved.
 
-Conversely the regions where the halo surface density is higher than the observational constraints correspond to models ${\mathcal M}$ with a minimum mass below this threshold.
-Models with this minimum mass hava a chance for successfuly reproducing observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to lower the halo number density down to the observed value.
+Conversely the regions where the halo surface density is higher than
+the observational constraints correspond to models ${\mathcal M}$ with
+a minimum mass below this threshold. Models with this minimum mass
+hava a chance for successfuly reproducing observations if the
+occupation fraction $f_{\rm occ}<1$ is tuned as to lower the halo
+number density down to the observed value.
 
@@
 \end{center} 
-\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with $P>0.1$\label{figure:landscape}.}
+\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
+  $P>0.1$\label{figure:landscape}.} 
 \end{figure}
 
-Figure \label{figure:landscape} presents the regions in the parameter space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of $P>0.1$.
-Each panel corresponds to the three different ways of grouping the mock fields.
-In the case of the methods {\tt{MatchObs}} and {\tt{RandomObs}} the color code indicates the fraction of these 15 mock surveys with with $P>0.1$.
-The third panel shows the result for the method {\tt{FullVolume}}, in this case the color code correspond to the value of $P$ for a given model.
+Figure \label{figure:landscape} presents the regions in the parameter
+space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of
+$P>0.1$. Each panel corresponds to the three different ways of
+grouping the mock fields. In the case of the methods {\tt{Match}}
+and {\tt{Random}} the color code indicates the fraction of these 15
+mock surveys with with $P>0.1$. The third panel shows the result for
+the method {\tt{Full}}, in this case the color code correspond
+to the value of $P$ for a given model.
 
-These results distinguish three mass regimes.
-In the first regime, at high mass values, we find that LAE models with minimum mass of $M_{\rm min}>XXX$ are not compatible with observations as expected from the analysis in the previous subsection.
-Below this mass down to $M_{\rm min}=XXX$ any minium and maximum mass models are compatible with LAEs observations.
-In a thirds mass regime, for low mass values $M_{\rm min}<$ only a limited range of models with $M_{\rm max}$ is able to reproduce observations.
+These results distinguish three mass regimes. In the first regime, at
+high mass values, we find that LAE models with minimum mass of $M_{\rm
+  min}>XXX$ are not compatible with observations as expected from the
+analysis in the previous subsection. Below this mass down to $M_{\rm
+  min}=XXX$ any minium and maximum mass models are compatible with
+LAEs observations. In a thirds mass regime, for low mass values
+$M_{\rm min}<$ only a limited range of models with $M_{\rm max}$ is
+able to reproduce observations.
 
-In these three different mass regimes the occupation monotonically decreases as a function of the minimum halo mass $M_{\rm min}$.
-In Figure XXX we show this treend in three panels following the same correspondence as Figure XXX.
-From these results we interpret that the different mass regimes that were identified correspond to best fit models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm occ}\sim 0$, respectively.
+In these three different mass regimes the occupation monotonically
+decreases as a function of the minimum halo mass $M_{\rm min}$. In
+Figure XXX we show this treend in three panels following the same
+correspondence as Figure XXX. From these results we interpret that the
+different mass regimes that were identified correspond to best fit
+models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm
+  occ}\sim 0$, respectively.
 
-There are some models where the KS test yield values of $P\sim 1$.
-To illustrate the kind of success represented by these models, we have selected these best ones in the case of the method {\tt{MatchObs}}.
-Figure XXX shows in the main panel the spatial distribution of the mock surveys, the smaller panel shows the corresponding surface density distribution and the observational constraint.
+The two {\tt match} and {\tt random} methods present the highest
+number of matching mock surveys in the medium mass regime. However, it
+is important to keep in mind that not all the mock surveys for a
+sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
+modest seems to be consistent with observations. This shows that the
+cosmic variance is still present on the physical scales probed by
+observations.
+
+... Figure presents the results for two mock fields for the same
+model, the two have extreme values for the KS test.
+
+Conversely here are different models where the KS test yield values of
+$P\sim 1$. To illustrate the kind of success represented by these
+models, we have selected these best ones in the case of the method
+{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
+distribution of the mock surveys, the smaller panel shows the
+corresponding surface density distribution and the observational
+constraint.
 
 \subsection{Estimating the Galaxy Bias from the Halo Masses}
-Using the results from the previous sections it is possible to infre the bias of $z\sim 3$ LAEs.
-Considering a number of $N_{\rm fields}$ the expected number density of galaxies around the region located at $x_{i}$ is $n_{i}=\bar{n}[1+ b\delta_{\rm DM}(x_{i})]$, where $\bar{n}$ is the average galaxy number density and $\delta_{\rm DM}\equiv (\rho - \bar{\rho})/\bar{\rho}$ is the matter overdensity in the field [REF robertson].
+Using the results from the previous sections it is possible to infre
+the bias of $z\sim 3$ LAEs. Considering a number of $N_{\rm fields}$
+the expected number density of galaxies around the region located at
+$x_{i}$ is $n_{i}=\bar{n}[1+ b\delta_{\rm DM}(x_{i})]$, where
+$\bar{n}$ is the average galaxy number density and $\delta_{\rm
+  DM}\equiv (\rho - \bar{\rho})/\bar{\rho}$ is the matter overdensity
+in the field [REF robertson].
 
-We calculate the bias for each mock catalog in the best models using the corresponding dark matter overdensity in the simulation.
-This results in a distribution of bias values for each model.
-The results for this calculation are presented in Figure XX.
-We compare this resul agains the following estimation $b^{2}\sim {\sigma_{N}^{2} - \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the average number counts in the $N_{fields}$, $\sigma_{N}$ is their dispersion and $\sigma_{DM}$ is the matter variance over many survey volumes.
+We calculate the bias for each mock catalog in the best models using
+the corresponding dark matter overdensity in the simulation. This
+results in a distribution of bias values for each model. The results
+for this calculation are presented in Figure XX.  We compare this
+resul agains the following estimation $b^{2}\sim {\sigma_{N}^{2} -
+  \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the
+average number counts in the $N_{fields}$, $\sigma_{N}$ is their
+dispersion and $\sigma_{DM}$ is the matter variance over many survey
+volumes.
 
@@
 
-We calculate the angular correlation function (ACF) for the best models for a mock survey with a total surface area equal to the full survey by Yamada et al 2012.
-We compare these results with the observed ACF reported by Gawiser et al.
-XXX.
+We calculate the angular correlation function (ACF) for the best
+models for a mock survey with a total surface area equal to the full
+survey by Yamada et al 2012. We compare these results with the
+observed ACF reported by Gawiser et al. XXX.
 
@@
 
-%\begin{figure}
-% \input{plots/TCF}
-%\end{figure}
+\section{Conclusions}
+In this letter we have presented new method to estimate preferred
+mass for dark matter halos hosting Lyman Alpha Emitters at
+$z=3.1$. The method is based on making an estimate of the cosmic
+variance from different observed fields. Based on a Nbody simulation,
+we select the range of halo masses, $M_{\rm min}<M_{\rm h}<M_{\rm
+  max}$, and the fraction of these halos, $f_{\rm occ}$, that could
+host LAEs being compatible witht the cosmic variance constraints.
 
-\section{Conclusions}
+We have used a large volume cosmological N-body simulation that allows
+us to extract $210$ sub-boxes each of which has a comparable
+volume to the field of view observed by Yamada et al. 2012. The
+comparison of the observed number density distribution against the
+results from our model is based on three different ways of
+constructing mock surveys. The first reproduces the spatial
+correlation between the $12$ observational fields, the second breaks
+this spatial correlation while keeping the number of fields and the
+third one simply includes all the $210$ sub-boxes.
 

### 2013-02-28 code/correlation/py_code/LAE_correlation.py
Code to select the best models and their respective catalog is done. Modules to compute correlation is also done. Waiting to check the codes and then compute correlation functions

@@ -1,24 +1,119 @@
 import numpy as np 
 import correlation_lib as corr
 
+D_z=6558.3
+
+def DD_histogram(X,Y,distance,th_min,th_max,theta_bins=10,cat_number=1):
+
+    n_points=len(X)
+    d_arr=[]
+    for i in range(n_points):
+        for j in range(i,n_points):
+            d=(X[i] - X[j])*(X[i] - X[j]) + (Y[i] - Y[j])*(Y[i] - Y[j])
+            d=np.sqrt(d)/distance
+            d_arr=np.append(d_arr,d)
+    
+           
+    DD=np.histogram(d_arr,bins=theta_bins, range=(th_min,th_max))
+    N=1.0*n_points*(1.0*n_points-1.0)/2.0
+    DD=DD/N
+    return DD
+
+def RR_histogram(X,Y,distance,cat_number=1000):
+    
+    n_points=len(X)
+    Xmin=1.0*np.floor( np.amin(X) )
+    Xmax=1.0*np.ceil( np.amin(X) )
+    Ymin=1.0*np.floor( np.amin(Y) )
+    Ymax=1.0*np.ceil( np.amin(Y) )
+    
+
+    Xr= Xmin +  ( Xmax - Xmin )*np.random.random_sample(n_points*cat_number)
+    Yr=Ymin +   ( Ymax - Ymin )*np.random.random_sample(n_points*cat_number)
+    d_arr=[]
+    for m in range(cat_number):
+        for i in range(n_points):
+            for j in range(i,n_points):
+                d=(Xr[i + n_points*m ] - Xr[j + n_points*m ])*(Xr[i + n_points*m ] - Xr[j + n_points*m ]) + (Yr[i + n_points*m ] - Yr[j + n_points*m ])*(Yr[i + n_points*m ] - Yr[j + n_points*m ])
+                d=np.sqrt(d)/distance
+                d_arr=np.append(d_arr,d)
+    RR=np.histogram(d_arr,bins=theta_bins, range=(th_min,th_max))
+    N=1.0*n_points*(1.0*n_points-1.0)/2.0
+    RR=RR/(N*cat_number)            
+    return RR
+
+def DR_histogram(X,Y,distance,cat_number=1000):
+        n_points=len(X)
+    Xmin=1.0*np.floor( np.amin(X) )
+    Xmax=1.0*np.ceil( np.amin(X) )
[…]

### 2013-02-28 paper/ms.tex

@@
 \subsection{Dark Matter Halo Number Density}
-... We comment first on the intergrated dark matter halo surface
-density as a function of mass for each one o the 210 sub-volumes in
-the Bolshoi simulation. This will allows us to better understand the
-expected trends for the LAEs preferred mass and the occupation
-fraction. Figure \ref{fig:laes_dist} show these distributions.
+We present first the results for  the intergrated dark matter halo surface
+density as a function of halos mass for each one o the 210 sub-volumes in
+the Bolshoi simulation. This result allowsus to better understand the
+expected trends for the LAEs' preferred mass and the occupation
+fraction. Figure \ref{fig:laes_dist} show these results. The continous lines
+correspond to the subvolumes. The shadowed area indicates the surface
+density values for LAEs allowed by the observations.
 
-The shadowed region in Figure \ref{fig:laes_dist} shows the surface
-density values allowed by the observations. This figure tells us by
-inspection which model parameters cannot reproduce the
-observations. The regions where the DM surface density values are
-below the observational constraint correspond to high masses. For a
-model ${\mathcal M}$ with a minimum mass in this high mass range, the
-observations present a surface density to high to be possible
-achieved.
+From this Figure we can read which models cannot reproduce the
+observations. Regions in the plot where the halo surface density
+values are below the observational constraint correspond to high
+masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
+$M_{\rm   min}$ located in that mass range, the surface density is too
+low compared with observations.
 
-Conversely the regions where the halo surface density is higher than
-the observational constraints correspond to models ${\mathcal M}$ with
-a minimum mass below this threshold. Models with this minimum mass
-hava a chance for successfuly reproducing observations if the
-occupation fraction $f_{\rm occ}<1$ is tuned as to lower the halo
-number density down to the observed value.
+Conversely, there are regions in the plot where the halo surface
+density can be higher than the observational constraints correspond to
+models ${\mathcal M}$ with a minimum mass below this threshold. Models
+with this minimum mass hava a chance for successfuly reproducing
+observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to
+lower the halo number density down to the observed value.
 
@@
 
-... Figure presents the results for two mock fields for the same
-model, the two have extreme values for the KS test.
+To illustrate this point, in Figure \ref{fig:mocks} we present the
+results for two mock fields for the {\tt{Match}} method for a model
+with the same parameters, but two extreme values for the KS test.
 
-Conversely here are different models where the KS test yield values of
+Conversely there are different models where the KS test yield values of
 $P\sim 1$. To illustrate the kind of success represented by these
@@
 \section{Conclusions}
-In this letter we have presented new method to estimate preferred
-mass for dark matter halos hosting Lyman Alpha Emitters at
-$z=3.1$. The method is based on making an estimate of the cosmic
+In this Letter we have constrained the preferred mass for dark matter
+halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
+method that matches the cosmic variance in the surface
+density number of LAEs from differente observed fields. From this we
+are able to constrain the mass range of dark matter halos hosting LAEs
+to be in the range $<M_{\rm h}<$ and a corresponding occupation fraction
+that escales as $f_{\rm occ} = M_{\rm min}$ with the minium halo mass
+defining the halo mass range.
+
+In this letter, this estimate is based on a large Nbody simulation
+where we select a range a fraction of halos in a given mass range to
+host LAEs. We explicitly construct mock observations to derive
+statistics that can be compared against observations.
+
+ The method is based on making an estimate of the cosmic
 variance from different observed fields. Based on a Nbody simulation,

### 2013-03-05 code/correlation/py_code/LAE_correlation.py
correlation module for project is complete but under test

@@ -3,7 +3,7 @@ import correlation_lib as corr
 
 D_z=6558.3
 
-def DD_histogram(X,Y,distance,th_min,th_max,theta_bins=10,cat_number=1):
+def DD_histogram(X,Y,distance,th_min,th_max,theta_bins):
 
     n_points=len(X)
     d_arr=[]
@@ -12,14 +12,15 @@ def DD_histogram(X,Y,distance,th_min,th_max,theta_bins=10,cat_number=1):
             d=(X[i] - X[j])*(X[i] - X[j]) + (Y[i] - Y[j])*(Y[i] - Y[j])
             d=np.sqrt(d)/distance
             d_arr=np.append(d_arr,d)
-    
-           
-    DD=np.histogram(d_arr,bins=theta_bins, range=(th_min,th_max))
+            
+
+    theta=d_arr/distance           
+    DD=np.histogram(theta,bins=theta_bins, range=(th_min,th_max))
     N=1.0*n_points*(1.0*n_points-1.0)/2.0
     DD=DD/N
     return DD
 
-def RR_histogram(X,Y,distance,cat_number=1000):
+def RR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=1000):
     
     n_points=len(X)
     Xmin=1.0*np.floor( np.amin(X) )
@@ -37,13 +38,14 @@ def RR_histogram(X,Y,distance,cat_number=1000):
                 d=(Xr[i + n_points*m ] - Xr[j + n_points*m ])*(Xr[i + n_points*m ] - Xr[j + n_points*m ]) + (Yr[i + n_points*m ] - Yr[j + n_points*m ])*(Yr[i + n_points*m ] - Yr[j + n_points*m ])
                 d=np.sqrt(d)/distance
                 d_arr=np.append(d_arr,d)
+    theta=d_arr/distance
     RR=np.histogram(d_arr,bins=theta_bins, range=(th_min,th_max))
     N=1.0*n_points*(1.0*n_points-1.0)/2.0
     RR=RR/(N*cat_number)            
     return RR
 
-def DR_histogram(X,Y,distance,cat_number=1000):
-        n_points=len(X)
+def DR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=1000):
+    n_points=len(X)
     Xmin=1.0*np.floor( np.amin(X) )
     Xmax=1.0*np.ceil( np.amin(X) )
[…]

### 2013-03-05 paper/ms.tex

@@
-\documentclass{emulateapj}
-\submitted{{\it Submitted for publication in ApJ Letters}}
-\usepackage{multirow,color,wrapfig,ulem}
-\usepackage {graphicx}
-%\bibliographystyle{apj}
+\documentclass[usenatbib]{mn2e} 
+\usepackage{amsmath} 
+\usepackage{amssymb} 
 \usepackage{graphics}
-\usepackage[dvips]{epsfig}
+\usepackage{graphicx}
+\usepackage{epsfig}  
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
+
+\newcommand{\apj}{ApJ}  
+\newcommand{\apjs}{ApJS}  
+\newcommand{\apjl}{ApJL}  
+\newcommand{\aj}{AJ}  
+\newcommand{\mnras}{MNRAS}  
+\newcommand{\mnrassub}{MNRAS accepted}  
+\newcommand{\aap}{A\&A}  
+\newcommand{\aaps}{A\&AS}  
+\newcommand{\araa}{ARA\&A}  
+\newcommand{\nat}{Nature}  
+\newcommand{\physrep}{PhR}
+\newcommand{\pasp}{PASP}    
+\newcommand{\pasj}{PASJ}
 
@@
 
-\shorttitle{LAE halo host mass at z=3.1}
-\shortauthors{Mej\'ia et al.}
+\begin{document}
 
-\begin{document}
-\title{Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance}
-
-\author{
-J. E.\ Forero-Romero\altaffilmark{1}, 
-J. Mej\'ia \altaffilmark{2}, 
+\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance}
+\author[J.E. Forero-Romero and J. Mejia]{
+\parbox[t]{\textwidth}{\raggedright Jaime E. Forero-Romero$^{1}$ and Julian Mejia$^{2}$}
+\vspace*{6pt}\\
+$^{1}$\\
+$^{2}$
 }
 
-\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia, \email{je.forero@uniandes.edu.co}}
-\altaffiltext{2}{XXX}
-\date{\today}
+\maketitle
 
@@
 \begin{center}
-%\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
+\includegraphics[width=1.00\linewidth,angle=0]{./plots/Fig1.pdf}
 \caption{ \label{figure:laes_dist} Cumulative mass function of dark

### 2013-03-08 code/LAE_correlation.py
correlation code update

@@ -270,20 +270,20 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
     for w in range( len(ID_arr) ):
         index=np.where( survey_ID == int(ID_arr[w]) )
         
-        print survey_ID[0], ID_arr[w], index
-        ID_ini=int(survey_ID[index[0]])
+        S_ID=survey_ID[index]
+        ID_ini=S_ID[0]
         ID_end=int(ID_ini+obs_surveys)
         m_min=best_models[w,0]
         m_max=best_models[w,1]
         f_occ=best_models[w,2]
-        
+        print m_min, m_max, f_occ
         i_s=i_field[ID_ini:ID_end]
         j_s=j_field[ID_ini:ID_end]
         k_s=k_field[ID_ini:ID_end]
         
         
         
-        corr=np.zeros(len(i_s)*len(js)*len(k_s),theta_bins)
+        corr=np.zeros( (len(i_s)*len(j_s)*len(k_s),theta_bins) )
         corr_laes=np.zeros(theta_bins)
         for i in i_s:
             for j in j_s:
@@ -292,17 +292,24 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
                     dmh_filename=dmh_path+"halos_bolshoi_"+str(i)+"-"+str(j)+"-"+str(k)+".csv"
                     halos_prop=np.loadtxt(dmh_filename,delimiter=",",skiprows=12)
                     
-                    halos_mass=halos_prop[:,4]
+                    halo_mass=halos_prop[:,4]
+                    print halo_mass
                     x_halos=halos_prop[:,0]
                     y_halos=halos_prop[:,1]
                     z_halos=halos_prop[:,2]
 
-                    halo_index=np.where( m_min <= halos_mass <= m_max )
-                    halo_index=np.random.shuffle(halo_cat_index)
-
-                    n_halos=np.size(halo_index)
-                    n_laes=f_occ*n_halos
-                    lae_index=halo_cat_index[0:n_laes]
+                    halo_index=np.where( (halo_mass< m_max) & (halo_mass> m_min) )
+                    halo_mass_sel=halo_mass[halo_index]
+                    print halo_index
+                    a=np.random.shuffle(halo_index)
+                    print halo_index,a
+                    x_sel=x_halos[halo_index]
+                    y_sel=y_halos[halo_index]
+                    
+                    n_halos=np.size(halo_mass_sel)
[…]

### 2013-03-11 paper/ms.tex
started the abstract

@@
 \begin{abstract}
--
+In this Letter we implement a new method to find the characteristic
+mass of dark matter halos hosting Lyman-Alpha Emitting (LAE)
+galaxies. The method is based on matching the statistics for the
+cosmic variance with the observations recently obtained by
+\cite{Yamada2012}. We build a model for LAEs on top of a large N-body
+cosmological simulation (Bolshoi). The basic principle is that a dark
+matter halo can host one LAE with a probability $f_{\rm occ}$ if its
+mass is found withing a certain range mass range delimited by two
+threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
+hundreds of mock catalogs in a thourough exploration of the parameter
+space of this model. These catalogs are constructed in such a way as
+to reproduce the spatial correlation between the different observed
+fields. We find that the models that best match the
+observed cosmic variance statistics are those with halo masses in the
+range $M_{\rm min}=$ and $M_{\rm max}=$ with and occupation fraction
+that scales as $f_{\rm occ}=$ with the minimum mass. We find that the
+angular correlation function is in agreement with the observational
+constraints. 
 \end{abstract}
@@
 Our observational reference are the recently published results of a
-panoramic survey of LAES at z=3.1 by Yamada et al. 2012. This survey
+panoramic survey of LAES at z=3.1 by \cite{Yamada2012}. This survey
 was conducted with the Subaru 8.2m telescope and the Subaru Prime
@@
 
+\section*{Acknowledgments}
+
+\bibliographystyle{mn2e}
+\bibliography{references}
+
 \end{document}

### 2013-03-11 code/mock_survey.py
deleted mocksurvey notebook

@@ -1,0 +1,196 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+import numpy as np
+
+def make_rectangle(width, height):
+    vertices = empty((5,2))
+    vertices[0,0] = 0.0
+    vertices[0,1] = 0.0
+    vertices[1,0] = width
+    vertices[1,1] = 0.0
+    vertices[2,0] = width
+    vertices[2,1] = height
+    vertices[3,0] = 0.0
+    vertices[3,1] = height
+    vertices[4,:] = vertices[0,:]
+    return vertices
+
+
+def plot_tile(tiles_x, tiles_y, i_tile, d_x, d_y, color='red'):
+    for i_field in range(7):
+        rec_base = make_rectangle(delta_x,delta_y)
+        plot(rec_base[:,0]+tiles_x[i_tile,i_field]*d_x, rec_base[:,1]+ tiles_y[i_tile,i_field]*d_y, color=color, linewidth=8, alpha=0.7)
+
+
+
+#finally dump all the IDs for the fields in the different surveys mimicking the observation
+def dump_match(data_path, all_tiles, all_tiles_x, all_tiles_z):
+    outputfile = data_path+'ID_match_surveys.dat'
+    print 'writing to', outputfile
+    out = open(outputfile, "w")
+    out.write("#ID_survey field_ID i j k\n")
+    ID_survey = 0
+    for i_z in range(3):    # loop over the slices in Z
+        for i_tile in range(5): # loop over the tiles defined in the X-Y plane
+        # define a unique ID for each field in the volume
+            for i_field in range(7): # these are the fields in the japanese surveys
+                index_i = all_tiles_x[i_z, i_tile, i_field]
+                index_j = all_tiles_y[i_z, i_tile, i_field]
+                index_k = i_z
+                field_ID = index_k + n_z*(index_j + (n_y * index_i))
+            #print ID_survey, field_ID, index_i, index_j, index_k
+                out.write("%d %d %d %d %d\n" % (ID_survey, field_ID, index_i, index_j, index_k))
+            for i_field in range(3): #tthree correlated fields
+                index_i = (all_tiles_x[i_z, i_tile, i_field] + 1)%n_x
[…]

### 2013-03-11 code/generate_mock_LAEs.py
minor modification to improve reproducibility

@@ -16,10 +16,8 @@ def generate_all_models():
     n_j = int(box_size/delta_y)
     n_k = int(box_size/delta_z)
     
-    user = "/home/jeforero/"
-    repo_path="Dropbox/CosmicVarianceLAES/"
-    dmh_path=user+repo_path+"data/dark_matter/FOF/"
-    laes_path=user+repo_path+"data/laes/FOF/"
+    dmh_path="../data/dark_matter/FOF/"
+    laes_path="../data/laes/FOF/"
 
     n_models = n_i * n_j * n_k
     n_bins = log_m.size
@@ -52,7 +50,10 @@ def generate_all_models():
                         value = sum(model_numbers[i,j,k,l:m])
                         out.write("%d %d %d %d %d\n"%(id0, i, j, k, value))
             out.close()
-generate_all_models()
+
+generate_data = True
+if generate_data:
+    generate_all_models()
 
 
 

### 2013-03-11 code/generate_mock_LAEs.py
last commit before new data generation

@@ -51,7 +51,7 @@ def generate_all_models():
                         out.write("%d %d %d %d %d\n"%(id0, i, j, k, value))
             out.close()
 
-generate_data = True
+generate_data = False
 if generate_data:
     generate_all_models()
 

### 2013-03-11 code/mock_survey.py

@@ -55,7 +55,7 @@ def dump_match(data_path, all_tiles, all_tiles_x, all_tiles_z):
                 field_ID = index_k + n_z*(index_j + (n_y * index_i))
             #print 'uncorr', ID_survey, field_ID, index_i, index_j, index_k
                 out.write("%d %d %d %d %d\n" % (ID_survey, field_ID, index_i, index_j, index_k))
-                ID_survey = ID_survey + 1        
+            ID_survey = ID_survey + 1        
     out.close()
     return 
         
@@ -177,7 +177,7 @@ all_tiles_z = np.arange(n_z)
 
 
 data_path="../data/mock_survey/"
-generate_data = True
+generate_data = False
 
 if generate_data:
     dump_random(data_path)

### 2013-03-11 code/LAE_correlation.py
Code to compute the correlation function for the best models: LAE_correlation.py. Working but slowly.

@@ -13,43 +13,54 @@ def DD_histogram(X,Y,distance,th_min,th_max,theta_bins):
     n_points=len(X)
     d_arr=[]
     for i in range(n_points):
-        for j in range(i,n_points):
+        for j in range(i+1,n_points):
             d=(X[i] - X[j])*(X[i] - X[j]) + (Y[i] - Y[j])*(Y[i] - Y[j])
             d=np.sqrt(d)/distance
             d_arr=np.append(d_arr,d)
             
-
-    theta=d_arr/distance           
-    DD=np.histogram(theta,bins=theta_bins, range=(th_min,th_max))
+            
+    theta=206265.0*d_arr         
+    
+    
+    DD,bins=np.histogram(theta,bins=theta_bins, range=(th_min,th_max))
+    
     N=1.0*n_points*(1.0*n_points-1.0)/2.0
     DD=DD/N
-    return DD
+    
+    return DD,bins
 
-def RR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=1000):
+def RR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=3):
     
     n_points=len(X)
     Xmin=1.0*np.floor( np.amin(X) )
-    Xmax=1.0*np.ceil( np.amin(X) )
+    Xmax=1.0*np.ceil( np.amax(X) )
     Ymin=1.0*np.floor( np.amin(Y) )
-    Ymax=1.0*np.ceil( np.amin(Y) )
+    Ymax=1.0*np.ceil( np.amax(Y) )
     
 
     Xr= Xmin +  ( Xmax - Xmin )*np.random.random_sample(n_points*cat_number)
     Yr=Ymin +   ( Ymax - Ymin )*np.random.random_sample(n_points*cat_number)
     d_arr=[]
+    
+    
     for m in range(cat_number):
         for i in range(n_points):
-            for j in range(i,n_points):
+            for j in range(i+1,n_points):
                 d=(Xr[i + n_points*m ] - Xr[j + n_points*m ])*(Xr[i + n_points*m ] - Xr[j + n_points*m ]) + (Yr[i + n_points*m ] - Yr[j + n_points*m ])*(Yr[i + n_points*m ] - Yr[j + n_points*m ])
                 d=np.sqrt(d)/distance
                 d_arr=np.append(d_arr,d)
-    theta=d_arr/distance
[…]

### 2013-03-11 code/LAE_correlation.py
"some cosmetic changes to LAE_correlation.py"

@@ -53,7 +53,7 @@ def RR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=3):
     theta=206265*d_arr 
     
     RR,bins=np.histogram(theta,bins=theta_bins, range=(th_min,th_max))
-    print RR
+    
     N=1.0*n_points*(1.0*n_points-1.0)/2.0
     N=N*cat_number
     RR=RR/N            

### 2013-03-11 code/p_value_distributions.py
added python code to get p_value distributions

@@ -1,0 +1,112 @@
+# -*- coding: utf-8 -*-
+# <nbformat>3.0</nbformat>
+
+from scipy import stats as st
+import numpy as np
+
+def ks_test_survey(ID_survey_filename, lae_obs, model_data, filling_fraction=1.0, area=1.0):
+    
+    #extracts the model data I care about
+    field_ID_model = np.int_(model_data[:,0])
+    int_i_model = np.int_(model_data[:,1])
+    int_j_model = np.int_(model_data[:,2])
+    int_k_model = np.int_(model_data[:,3])
+    n_halo_model = np.int_(model_data[:,4])
+    #field_ID_model = int_k_model + n_z * (int_j_model + (n_y * int_i_model))
+  
+    #load all data describing the fields that compose the different surveys 
+    survey_data = np.loadtxt(ID_survey_filename)
+    survey_ID_list = np.int_(survey_data[:,0])
+    #print survey_ID_list
+    
+    #count the total number of surveys included here
+    index = np.where(survey_ID_list==survey_ID_list[0])
+    n_surveys = survey_data.size/np.size(survey_data[0,:])/np.size(index)
+
+    p_value = np.zeros(n_surveys)
+    for survey_ID in range(n_surveys):        
+        #select the data for the fields with a given survey ID
+        index = np.where(survey_ID_list==survey_ID)
+        my_survey = survey_data[index[0],:]
+        field_ID_list = np.int_(my_survey[:,1])
+        field_i_list = np.int_(my_survey[:,2])
+        field_j_list = np.int_(my_survey[:,3])
+        field_k_list = np.int_(my_survey[:,4])
+    
+        #find the halo numbers for each field in all the fields of the survey
+        field_nhalo_list = np.zeros(field_ID_list.size)
+        for i_field in range(field_ID_list.size):
+            index = np.where(field_ID_model==field_ID_list[i_field])
+            #print index, field_ID_list[i_field]
+            index = index[0]
+            #print n_halo_model[index]
+            field_nhalo_list[i_field] = n_halo_model[index]
+            
+        n_lae_theory = filling_fraction * field_nhalo_list/area
+        distance,p_value[survey_ID]=st.ks_2samp(n_lae_theory, lae_obs)
+    return p_value
+
+# <codecell>
+# <codecell>
+
[…]

### 2013-03-12 code/LAE_correlation.py
bug correted in LAE_corelation.py

@@ -146,7 +146,7 @@ where  ks_prob>=p_threshold
 def best_model_sel(prob_treshold,survey_type="match", pro_path="/home/jemejia/CosmicVarianceLAES/"):
    
     ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
-    p_values_file= pro_path + "data/mock_survey/" + "p_values_ID_" + survey_type + "_surveys.dat"
+    p_values_file= pro_path + "data/mock_survey/" + "p_values_FOF_ID_" + survey_type + "_surveys.dat"
 
     ks_data=np.loadtxt(p_values_file) 
     
@@ -157,10 +157,10 @@ def best_model_sel(prob_treshold,survey_type="match", pro_path="/home/jemejia/Co
     ID_survey_arr = ks_data[:,3]
 
     model_prob_arr = ks_data[:,4]
-    
+    print np.size(m_min_arr)
     #choosing th models with ks test probabilities greater than prob_treshold
     index=np.where(model_prob_arr>=prob_treshold)
-    
+    print np.size(index)
     best_models=np.empty( [ np.size(index) , np.size( ks_data[0,:] ) ] )
     del(ks_data)
 
@@ -169,7 +169,7 @@ def best_model_sel(prob_treshold,survey_type="match", pro_path="/home/jemejia/Co
     best_models[:,2]=f_occ_arr[index]
     best_models[:,3]= ID_survey_arr[index] 
     best_models[:,4]=model_prob_arr[index]
-
+    print "the number of selected models are", np.size(best_models[:,0])
     return best_models
     
 
@@ -246,7 +246,7 @@ angles           -->  angels where the correlation function has been computed
 def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="match", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250, pro_path="/home/jemejia/CosmicVariance/"):
 
     
-    
+    print "computing correlation functions of the selected models"
     dmh_path=project_path+"data/dark_matter/FOF/"
     laes_path=project_path+"data/laes/FOF/"
     n_i= int( box_length/x_width)
@@ -294,54 +294,53 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
         m_min=best_models[w,0]
         m_max=best_models[w,1]
         f_occ=best_models[w,2]
-        print m_min, m_max, f_occ
[…]

### 2013-03-12 code/LAE_correlation.py
changes to LAE_correction.py

@@ -29,20 +29,19 @@ def DD_histogram(X,Y,distance,th_min,th_max,theta_bins):
     
     return DD,bins
 
-def RR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=3):
+def RR_histogram(X,Y,Xr,Yr,distance,th_min,th_max,theta_bins,cat_number=3):
     
     n_points=len(X)
-    Xmin=1.0*np.floor( np.amin(X) )
-    Xmax=1.0*np.ceil( np.amax(X) )
-    Ymin=1.0*np.floor( np.amin(Y) )
-    Ymax=1.0*np.ceil( np.amax(Y) )
+    #Xmin=1.0*np.floor( np.amin(X) )
+    #Xmax=1.0*np.ceil( np.amax(X) )
+    #Ymin=1.0*np.floor( np.amin(Y) )
+    #Ymax=1.0*np.ceil( np.amax(Y) )
     
 
-    Xr= Xmin +  ( Xmax - Xmin )*np.random.random_sample(n_points*cat_number)
-    Yr=Ymin +   ( Ymax - Ymin )*np.random.random_sample(n_points*cat_number)
+    #Xr= Xmin +  ( Xmax - Xmin )*np.random.random_sample(n_points*cat_number)
+    #Yr=Ymin +   ( Ymax - Ymin )*np.random.random_sample(n_points*cat_number)
     d_arr=[]
-    
-    
+
     for m in range(cat_number):
         for i in range(n_points):
             for j in range(i+1,n_points):
@@ -60,20 +59,20 @@ def RR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=3):
     
     return RR,bins
 
-def DR_histogram(X,Y,distance,th_min,th_max,theta_bins,cat_number=3):
+def DR_histogram(X,Y,Xr,Yr,distance,th_min,th_max,theta_bins,cat_number=3):
     n_points=len(X)
-    Xmin=1.0*np.floor( np.amin(X) )
-    Xmax=1.0*np.ceil( np.amin(X) )
-    Ymin=1.0*np.floor( np.amin(Y) )
-    Ymax=1.0*np.ceil( np.amin(Y) )
+    #Xmin=1.0*np.floor( np.amin(X) )
+    #Xmax=1.0*np.ceil( np.amax(X) )
+    #Ymin=1.0*np.floor( np.amin(Y) )
+    #Ymax=1.0*np.ceil( np.amax(Y) )
[…]

### 2013-03-13 code/LAE_correlation.py
final version of LAE_correlation.py

@@ -242,7 +242,7 @@ angles           -->  angels where the correlation function has been computed
 '''
 
 
-def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="match", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=4, pro_path="/home/jemejia/CosmicVariance/"):
+def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="match", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=1, pro_path="/home/jemejia/CosmicVariance/"):
 
     
     print "computing correlation functions of the selected models"
@@ -304,9 +304,9 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
         corr_peebles=np.zeros( (len(i_s),theta_bins) )
         corr_standard=np.zeros( (len(i_s),theta_bins) )
         corr_laes=np.zeros(theta_bins)
-        print "number of catalogs=",len(i_s)
+        print "number of sub-catalogs=",len(i_s)
         for i in range( np.size(i_s) ):
-            print "subcat",i_s[i],j_s[i],k_s[i]
+            print "subcat number:",i,"i_j_k=",i_s[i],j_s[i],k_s[i]
             dmh_filename=dmh_path+"halos_bolshoi_"+str(i_s[i])+"-"+str(j_s[i])+"-"+str(k_s[i])+".csv"
             halos_prop=np.loadtxt(dmh_filename,delimiter=",",skiprows=12)
             

### 2013-03-13 paper/ms.tex
100 new words into the paper

@@
 
-\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance}
+\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the
+  dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1
+  from cosmic variance} 
 \author[J.E. Forero-Romero and J. Mejia]{
@@
 to reproduce the spatial correlation between the different observed
-fields. We find that the models that best match the
-observed cosmic variance statistics are those with halo masses in the
-range $M_{\rm min}=$ and $M_{\rm max}=$ with and occupation fraction
-that scales as $f_{\rm occ}=$ with the minimum mass. We find that the
-angular correlation function is in agreement with the observational
-constraints. 
+fields. We find that the models that best match the observed cosmic
+variance statistics are those with halo masses in the range $M_{\rm
+  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales
+as $f_{\rm occ}=$ with the minimum mass. We find that the angular
+correlation function is in agreement with the observational
+constraints mostly due to the cosmic variance in the small angular
+fields where this statistics has been computed so far. We also present
+predictions for future measurements of the correlation function on
+larger continous fields. We make available the mock data for the best
+models in a public repository.  
 \end{abstract}
@@
 \subsection{Dark Matter Halo Number Density}
-We present first the results for  the intergrated dark matter halo surface
-density as a function of halos mass for each one o the 210 sub-volumes in
-the Bolshoi simulation. This result allowsus to better understand the
+In Figure \ref{fig:laes_dist} we present the results for  the intergrated dark matter halo surface
+density as a function of halos mass for each one of the 210 sub-volumes in
+the Bolshoi simulation. The continous lines correspond to the
+subvolumes. The shadowed area indicates the surface density values for
+LAEs allowed by the observations.
+
+This result allows us to better understand the
 expected trends for the LAEs' preferred mass and the occupation
-fraction. Figure \ref{fig:laes_dist} show these results. The continous lines
-correspond to the subvolumes. The shadowed area indicates the surface
-density values for LAEs allowed by the observations.
-
-From this Figure we can read which models cannot reproduce the
+fraction.  From this Figure we can read which models do not have a
+chance reproduce the
 observations. Regions in the plot where the halo surface density
@@
 masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
-$M_{\rm   min}$ located in that mass range, the surface density is too
-low compared with observations.
+$M_{\rm   min}> 3 \times 10^{11}$\hMsun located in that mass range,
+the surface density is too low compared with observations.
 
 Conversely, there are regions in the plot where the halo surface
-density can be higher than the observational constraints correspond to
-models ${\mathcal M}$ with a minimum mass below this threshold. Models
-with this minimum mass hava a chance for successfuly reproducing
-observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to
-lower the halo number density down to the observed value.
+density is always higher than the observational constraints correspond
+to models ${\mathcal M}$ with a minimum mass below $M_{\rm min}<
+3\times 10^{10}$\hMsun. Models with this minimum mass hava a chance
+for successfuly reproducing observations if the occupation fraction
+$f_{\rm occ}<1$ is tuned as to lower the halo number density down to
+the observed value.
 
@@
 high mass values, we find that LAE models with minimum mass of $M_{\rm
-  min}>XXX$ are not compatible with observations as expected from the
-analysis in the previous subsection. Below this mass down to $M_{\rm
-  min}=XXX$ any minium and maximum mass models are compatible with
-LAEs observations. In a thirds mass regime, for low mass values
-$M_{\rm min}<$ only a limited range of models with $M_{\rm max}$ is
-able to reproduce observations.
+  min}>3\times 10^{11}$\hMsun are not compatible with observations as
+expected from the analysis in the previous subsection. For masses below $M_{\rm
+  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
+can be made compatible with observations, provided that
+$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
+for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
+limited range of models with $M_{\rm max}$ with occupation fraction
+$f_{\rm occ}\sim 1$ is able to reproduce observations.
 

### 2013-03-13 code/LAE_correlation.py
correlation functions in ~/data/mock_survey/correlation_best_models/

@@ -43,8 +43,10 @@ def RR_histogram(X,Y,Xr,Yr,distance,th_min,th_max,theta_bins,cat_number=3):
     d_arr=[]
 
     for m in range(cat_number):
+        print "random cat=",m
         for i in range(n_points):
             for j in range(i+1,n_points):
+                
                 d=(Xr[i + n_points*m ] - Xr[j + n_points*m ])*(Xr[i + n_points*m ] - Xr[j + n_points*m ]) + (Yr[i + n_points*m ] - Yr[j + n_points*m ])*(Yr[i + n_points*m ] - Yr[j + n_points*m ])
                 d=np.sqrt(d)/distance
                 d_arr=np.append(d_arr,d)
@@ -142,7 +144,7 @@ where  ks_prob>=p_threshold
 
 
 
-def best_model_sel(prob_treshold,survey_type="match", pro_path="/home/jemejia/CosmicVarianceLAES/"):
+def best_model_sel(prob_treshold,survey_type="full", pro_path="/casiopea/jemejia/CosmicVarianceLAES/"):
    
     ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
     p_values_file= pro_path + "data/mock_survey/" + "p_values_FOF_ID_" + survey_type + "_surveys.dat"
@@ -242,7 +244,7 @@ angles           -->  angels where the correlation function has been computed
 '''
 
 
-def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="match", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=1, pro_path="/home/jemejia/CosmicVariance/"):
+def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="full", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=40, pro_path="/casiopea/jemejia/CosmicVariance/"):
 
     
     print "computing correlation functions of the selected models"
@@ -306,7 +308,7 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
         corr_laes=np.zeros(theta_bins)
         print "number of sub-catalogs=",len(i_s)
         for i in range( np.size(i_s) ):
[…]

### 2013-03-14 code/p_value_distributions.py
fixed bug for the full distributions

@@ -12,12 +12,11 @@ def ks_test_survey(ID_survey_filename, lae_obs, model_data, filling_fraction=1.0
     int_j_model = np.int_(model_data[:,2])
     int_k_model = np.int_(model_data[:,3])
     n_halo_model = np.int_(model_data[:,4])
-    #field_ID_model = int_k_model + n_z * (int_j_model + (n_y * int_i_model))
   
     #load all data describing the fields that compose the different surveys 
     survey_data = np.loadtxt(ID_survey_filename)
     survey_ID_list = np.int_(survey_data[:,0])
-    #print survey_ID_list
+#    print survey_ID_list
     
     #count the total number of surveys included here
     index = np.where(survey_ID_list==survey_ID_list[0])
@@ -44,6 +43,7 @@ def ks_test_survey(ID_survey_filename, lae_obs, model_data, filling_fraction=1.0
             
         n_lae_theory = filling_fraction * field_nhalo_list/area
         distance,p_value[survey_ID]=st.ks_2samp(n_lae_theory, lae_obs)
+#        print n_lae_theory, lae_obs
     return p_value
 
 # <codecell>
@@ -93,7 +93,7 @@ a_exp = 1.0/(3.1 +1.0)
 mock_area = (a_exp * x_width/h)*(a_exp * y_width/h) / ((D_angular) * (D_angular))
 mock_area = mock_area * (180.0/np.pi) * (180.0/np.pi) * (60.0 * 60.0) #arcmin^2
 
-generate_data = False
+generate_data = True
 
 if generate_data:
 
@@ -103,10 +103,10 @@ if generate_data:
     n_lae_obs = obs_prop[:,2]
 
     survey_filename= "ID_match_surveys.dat"
-    get_p_values(full_lae_data_path, full_data_path, survey_filename, filling_fraction, log_min_mass, log_max_mass, mock_area=mock_area, halo_finder=halo_finder)
+#    get_p_values(full_lae_data_path, full_data_path, survey_filename, filling_fraction, log_min_mass, log_max_mass, mock_area=mock_area, halo_finder=halo_finder)
 
     survey_filename="ID_random_surveys.dat"
-    get_p_values(full_lae_data_path, full_data_path, survey_filename, filling_fraction, log_min_mass, log_max_mass, mock_area=mock_area, halo_finder=halo_finder)
[…]

### 2013-03-15 paper/ms.tex
updated to include and construct Fig2

@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P99.pdf}\\
+\vspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_full_P5.pdf}
 \end{center} 
 \caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
-  $P>0.1$\label{figure:landscape}.} 
-\end{figure}
+  $P>0.05$\label{figure:landscape}.} 
+\end{figure*}
 

### 2013-03-19 code/LAE_correlation.py
correlation plots added to /data/mock_survey/correlation_best_models

@@ -1,4 +1,5 @@
 import numpy as np 
+import matplotlib.pyplot as P
 #import correlation_lib as corr
 
 D_z=6558.3
@@ -144,7 +145,7 @@ where  ks_prob>=p_threshold
 
 
 
-def best_model_sel(prob_treshold,survey_type="full", pro_path="/casiopea/jemejia/CosmicVarianceLAES/"):
+def best_model_sel(prob_treshold,survey_type="random", pro_path="/home/jemejia/CosmicVarianceLAES/"):
    
     ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
     p_values_file= pro_path + "data/mock_survey/" + "p_values_FOF_ID_" + survey_type + "_surveys.dat"
@@ -244,7 +245,7 @@ angles           -->  angels where the correlation function has been computed
 '''
 
 
-def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="full", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=40, pro_path="/casiopea/jemejia/CosmicVariance/"):
+def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="random", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=40, pro_path="/home/jemejia/CosmicVariance/"):
 
     
     print "computing correlation functions of the selected models"
@@ -341,7 +342,8 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
             del halo_mass
             
             #random cat histogram generation
-                    
+            P.xlabel(r'$\theta$', fontsize=16)
+            P.ylabel(r"$\xi(\theta)$",fontsize=16)
             if(w==0):
                 if(i==0):
                     print w,i
@@ -381,8 +383,9 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
         
         correlation_data=np.empty(( np.size(corr_laes) , 3 ) )
         
-        model_name = 'correlation_model_{0}_{1}_{2}.dat'.format(m_min, m_max, f_occ)
-        filename=pro_path + "data/mock_survey/" + "correlation_best_models/" + survey_type + "_" + model_name
[…]

### 2013-03-19 paper/ms.tex

@@
 \author[J.E. Forero-Romero and J. Mejia]{
-\parbox[t]{\textwidth}{\raggedright Jaime E. Forero-Romero$^{1}$ and Julian Mejia$^{2}$}
+\parbox[t]{\textwidth}{\raggedright 
+  Julian Mejia$^{2}$ and
+Jaime E. Forero-Romero$^{1}$}
 \vspace*{6pt}\\
 $^{1}$\\
-$^{2}$
+$^{2}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia
 }
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
+\end{center} 
+\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
+  $P>0.05$\label{figure:f_escape}.} 
+\end{figure*}
+
 Figure \label{figure:landscape} presents the regions in the parameter

### 2013-03-20 code/LAE_correlation.py
paper plots of correaltion function added in paper/plots

@@ -245,7 +245,7 @@ angles           -->  angels where the correlation function has been computed
 '''
 
 
-def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="random", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=40, pro_path="/home/jemejia/CosmicVariance/"):
+def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, survey_type="random", distance=6558.3, obs_surveys=12,x_width=46.0,y_width=35.0, z_depth=41.0 ,box_length=250,random_cat_number=16, pro_path="/home/jemejia/CosmicVariance/"):
 
     
     print "computing correlation functions of the selected models"
@@ -287,7 +287,9 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
     #choosing the subcatalogs of the best fields.
     best_correlation=np.empty([len(ID_arr),theta_bins])
     std_correlation=np.empty([len(ID_arr),theta_bins])
+    
     for w in range( len(ID_arr) ):
+    #for w in range( 3 ): 
         index=np.where( survey_ID == int(ID_arr[w]) )
         
         S_ID=survey_ID[index]
@@ -382,7 +384,7 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
         dtheta=(theta_max - theta_min)/theta_bins
         
         correlation_data=np.empty(( np.size(corr_laes) , 3 ) )
-        
+        model='{0}_{1}_{2}'.format(m_min, m_max, f_occ)
         model_name = 'model_{0}_{1}_{2}'.format(m_min, m_max, f_occ)
         filename=pro_path + "data/mock_survey/" + "correlation_best_models/" + survey_type + "_correlation_" + model_name + ".dat"
         
@@ -393,10 +395,11 @@ def best_model_correlation(best_model_array, theta_min,theta_max,theta_bins, sur
         
         np.savetxt(filename,correlation_data)
         
-        P.errorbar(correlation_data[:,0], correlation_data[:,1], correlation_data[:,2],label=model_name,elinewidth=2.0)
+        P.errorbar(correlation_data[:,0]+1.5*w, correlation_data[:,1], correlation_data[:,2],label=model,elinewidth=2.0)
         
[…]

### 2013-03-20 paper/ms.tex
new figure, updated text on obs contraints for the occupation fraction

@@
 
+\newcommand{\documentname}{paper~}
 \newcommand{\apj}{ApJ}  
@@
 
-\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the
-  dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1
-  from cosmic variance} 
-\author[J.E. Forero-Romero and J. Mejia]{
+\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Using cosmic
+  variance to constrain the
+  dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1}
+\author[~J.~E. Forero-Romero and J. Mejia]{
 \parbox[t]{\textwidth}{\raggedright 
-  Julian Mejia$^{2}$ and
+  Julian Mej\'ia$^{2}$ and
 Jaime E. Forero-Romero$^{1}$}
@@
 $^{1}$\\
-$^{2}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia
+$^{2}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia 
 }
@@
 \begin{abstract}
-In this Letter we implement a new method to find the characteristic
-mass of dark matter halos hosting Lyman-Alpha Emitting (LAE)
-galaxies. The method is based on matching the statistics for the
-cosmic variance with the observations recently obtained by
-\cite{Yamada2012}. We build a model for LAEs on top of a large N-body
-cosmological simulation (Bolshoi). The basic principle is that a dark
-matter halo can host one LAE with a probability $f_{\rm occ}$ if its
+We use simulations and recent observations to find the characteristic
+mass of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies
+at a redshift of $z=3.1$. The method is based on matching the
+statistics for the number density cosmic variance between different
+observed and mock fields. We build a model for LAEs on top of a large N-body
+cosmological simulation (Bolshoi) where the basic principle is that a dark
+matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
 mass is found withing a certain range mass range delimited by two
@@
 
-Throughout this Letter we assume a $\Lambda$CDM cosmology with the
+Throughout this \documentname we assume a $\Lambda$CDM cosmology with the
 following values for the cosmological parameters, $\Omega_{m}=0.27$,
@@
 \section{Methodology}
-In this Letter we constrain the typical mass of dark matter halos
+In this \documentname we constrain the typical mass of dark matter halos
 hosting LAES at $z=3.1$. Our model is based on the number density
@@
 
-In this Letter we want to step back and reduce the complexity of our
+In this \documentname we want to step back and reduce the complexity of our
 model, with the sole objective of reproducing the cosmic variance in
@@
 Our observational reference are the recently published results of a
-panoramic survey of LAES at z=3.1 by \cite{Yamada2012}. This survey
+panoramic survey of LAES at $z=3.1$ by \cite{Yamada2012}. This survey
 was conducted with the Subaru 8.2m telescope and the Subaru Prime
@@
 defined to have an density of 200 times the critical density. The
-minimum halo mass in the models we construct in this Letter correspond
+minimum halo mass in the models we construct in this \documentname correspond
 to groups of $\sim 75$ particles. The catalogs were obtained from the
@@
 \subsection{Dark Matter Halo Number Density}
-In Figure \ref{fig:laes_dist} we present the results for  the intergrated dark matter halo surface
-density as a function of halos mass for each one of the 210 sub-volumes in
-the Bolshoi simulation. The continous lines correspond to the
-subvolumes. The shadowed area indicates the surface density values for
-LAEs allowed by the observations.
+In Figure \ref{fig:laes_dist} we present the results for  the
+integrated dark matter halo surface density as a function of halos
+mass. Each line correspond to one of the 210 sub-volumes in the
+Bolshoi simulation. The shadowed area indicates the surface density
+values for LAEs allowed by the observations.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P99.pdf}\\
+\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}\\
 \vspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_full_P5.pdf}
+\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}\\
+\vspace{5mm}
+\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_full_P5.pdf}
 \end{center} 
 \caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
-  $P>0.05$\label{figure:landscape}.} 
-\end{figure*}
+  $P>0.05$ in the three different of grouping the mock fields. In the
+  case of the {\tt match} and {\tt random} methods the  color code
+  corresponds to the number of mock surveys that are found to
+  be compatible with observations. For the {\tt full} method the
+  colour code corresponds to the results of $100$ times the maximum $P$ value
+  resulting from the KS test. \label{figure:landscape}.}  
+\end{figure}
 
@@
 Figure \label{figure:landscape} presents the regions in the parameter
-space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of
-$P>0.1$. Each panel corresponds to the three different ways of
+space $M_{\rm min}$-$M_{\rm max}$ where the KS test yields values of
+$P>0.05$. We consider that for those models it is not possible to rule out the null
+hypothesis, namely that the number density in simulated data and the observations come
+from the same parent distribution. Each panel corresponds to the three different ways of
 grouping the mock fields. In the case of the methods {\tt{Match}}
@@
 the method {\tt{Full}}, in this case the color code correspond
-to the value of $P$ for a given model.
+to the value maximum value of $100\times P$ for a model with those
+mass ranges.
 
-These results distinguish three mass regimes. In the first regime, at
+These results clearly distinguish three mass regimes. In the first regime, at
 high mass values, we find that LAE models with minimum mass of $M_{\rm
-  min}>3\times 10^{11}$\hMsun are not compatible with observations as
-expected from the analysis in the previous subsection. For masses below $M_{\rm
+  min}>10^{11.5}$\hMsun are not compatible with observations. There is
+a second regime for masses below $M_{\rm
   min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
@@
 constraint.
+
+\subsection{Additional observational constraints on the occupation fraction}
+
+\cite{Hayes2010} constrained the value of $f_{\rm occ}$ at $z=2.2$ to
+be $f_{\rm occ}=0.10$. This estimation was based on blind surveys of
+the H$\alpha$ and Lyman alpha line with the European Southern
+Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
+extinction to obtain an estimate for the intrinsic H$\alpha$
+luminosity, and using values for the theoretical expectation of the
+ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
+the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
+esc}=(10.7\pm 2.8)$ if a different dust correction is used. From this
+results they derive that almost $90\%$ of the star forming galaxies
+emit insufficient Lyman-alpha to be detected, effectively setting the
+occupation fraction to be $f_{\rm occ}=0.10$. Obervations are
+consistent with these numbers are
+consistent with being constant for every galaxy regardless of its
+luminosity.
+
+For the cosmological parameters used in this \documentname the age of
+the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$ Gyr,
+it is reasonable to assume that the physical conditions that determine
+the escape fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm
+  occ}$ remain constant. This assumption allows us to further pick
+models that have an occupation fraction of $f_{\rm occ}=0.10$. Under
+this selection only $18$ models can be selected. Considering an
+occupation fraction $f_{\rm occ}=0.20$ another $39$ models can be
+considered. The minimum and maximum mass are found in the appendix in
+Table XX.
 
@@
 \section{Conclusions}
-In this Letter we have constrained the preferred mass for dark matter
+In this \documentname we have constrained the preferred mass for dark matter
 halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{ccc}\hline\hline
+10.1 & 10.2 & 0.1\\
+10.3 & 10.5 & 0.1\\
+10.4 & 10.7 & 0.1\\
+10.5 & 10.9 & 0.1\\
+10.6 & 11.2 & 0.1\\
+10.6 & 11.3 & 0.1\\
+10.6 & 11.4 & 0.1\\
+10.1 & 10.2 & 0.1\\
+10.3 & 10.5 & 0.1\\
+10.4 & 10.7 & 0.1\\
+10.5 & 10.9 & 0.1\\
+10.5 & 11.0 & 0.1\\
+10.6 & 11.2 & 0.1\\
+10.6 & 11.3 & 0.1\\
+10.6 & 11.4 & 0.1\\
+10.6 & 11.5 & 0.1\\
+10.6 & 11.6 & 0.1\\
+10.6 & 11.7 & 0.1\\\hline\hline
+
+10.4 & 10.5 & 0.2\\
+10.6 & 10.8 & 0.2\\
+10.7 & 11.0 & 0.2\\
+10.8 & 11.2 & 0.2\\
+10.8 & 11.3 & 0.2\\
+10.9 & 11.6 & 0.2\\
+10.9 & 11.7 & 0.2\\
+10.9 & 11.8 & 0.2\\
+10.9 & 11.9 & 0.2\\
+10.9 & 12.0 & 0.2\\
+10.9 & 12.1 & 0.2\\
+10.9 & 12.2 & 0.2\\
+10.9 & 12.3 & 0.2\\
+10.9 & 12.4 & 0.2\\
+10.9 & 12.5 & 0.2\\
+10.9 & 12.6 & 0.2\\
+10.9 & 12.7 & 0.2\\
+10.9 & 12.8 & 0.2\\
+10.9 & 12.9 & 0.2\\
+10.9 & 13.0 & 0.2\\
+10.6 & 10.8 & 0.2\\
+10.7 & 11.0 & 0.2\\
+10.8 & 11.2 & 0.2\\
+10.8 & 11.3 & 0.2\\
+10.8 & 11.4 & 0.2\\
+10.9 & 11.7 & 0.2\\
+10.9 & 11.8 & 0.2\\
+10.9 & 11.9 & 0.2\\
+10.9 & 12.0 & 0.2\\
+10.9 & 12.1 & 0.2\\
+10.9 & 12.2 & 0.2\\
+10.9 & 12.3 & 0.2\\
+10.9 & 12.4 & 0.2\\
+10.9 & 12.5 & 0.2\\
+10.9 & 12.6 & 0.2\\
+10.9 & 12.7 & 0.2\\
+10.9 & 12.8 & 0.2\\
+10.9 & 12.9 & 0.2\\
+10.9 & 13.0 & 0.2\\\hline\hline
+\end{tabular}
+\end{center}
+\end{table}
+
 \bibliographystyle{mn2e}

### 2013-03-26 paper/ms.tex
some changes in the correlation section and correlation plots were changed to pdf

@@
 Next we group these $210$ mock fields in three different ways to
-construct the LAEs number density distribution. The first way we
+construct the LAEs number density distribution. The first way (match method) we
 follow the observational setup and constructs $15$ different mock
@@
 produce $15$ different distributions for the number density for a
-given model ${\mathrm M}$. The second is similar to the first
+given model ${\mathrm M}$. The second (random method) is similar to the first
 one. There aare $15$ different mock surveys with $12$ mock fields
 each, but this time each field corresponds to uncorrelated sub-boxes
-in the simulation. The third way in only has $1$ mock survey
+in the simulation. The third (full method) way in only has $1$ mock survey
 containing all the $210$ mock fields, in this setup there is only one
@@
 \subsection{Estimating the Galaxy Bias from the Halo Masses}
-Using the results from the previous sections it is possible to infre
+Using the results from the previous sections it is possible to infer
 the bias of $z\sim 3$ LAEs. Considering a number of $N_{\rm fields}$
@@
 for this calculation are presented in Figure XX.  We compare this
-resul agains the following estimation $b^{2}\sim {\sigma_{N}^{2} -
+result against the following estimation $b^{2}\sim {\sigma_{N}^{2} -
   \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the
@@
 
-We calculate the angular correlation function (ACF) for the best
-models for a mock survey with a total surface area equal to the full
-survey by Yamada et al 2012. We compare these results with the
-observed ACF reported by Gawiser et al. XXX.
+We calculate the mean angular correlation function (ACF) for the best
+models for a mock survey using the match and random methods with 
+two different surface areas: $1)$ the full survey (12 subfields) and
+$2)$  e SSA22 field (7 subfields) reported by Yamada et al 2012 
+(see section XX) . The results for these calculations  are shown 
+in figure \ref{figure:correlation_match} (match) and figure
+\ref{figure:correlation_random} (random).  The error bars in these figure
+represent the standard deviation of the ACF over the subfields.
 
-\begin{figure}
+We compare these results with the observed ACF in the SSA22 field reported by Hayashino et al. 2004 .
+
+\begin{figure*}
 \begin{center}
-\includegraphics[width=1.00\linewidth,angle=0]{./plots/correlation_best_models_with_obs_comp.png} 
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plot/match_large_correlation_selected_models.pdf}\\
 \end{center} 
-\caption{ \label{figure:landscape} 
-}
-\end{figure}
+\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
+some selected models in different mass ranges. \label{figure:correlation_match} }
+
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plot/random_large_correlation_selected_models.pdf}\\
+\end{center} 
+\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
+some selected models in different mass ranges. \label{figure:correlation_match} }
+
+\end{figure*}
 

### 2013-03-30 paper/ms.tex
text added to the correlation fuction section

@@
 
-We calculate the mean angular correlation function (ACF) for the best
+As a prediction, we calculate the mean angular correlation function (ACF) for some of the best
 models for a mock survey using the match and random methods with 
@@
 in figure \ref{figure:correlation_match} (match) and figure
-\ref{figure:correlation_random} (random).  The error bars in these figure
+\ref{figure:correlation_random} (random).  The error bars in these figures
 represent the standard deviation of the ACF over the subfields. 
+We compare these results with the observed ACF in a field of the the SSA22 region
+reported by Hayashino et al in 2004.
 
-We compare these results with the observed ACF in the SSA22 field reported by Hayashino et al. 2004 .
+We can generally observe that the standard deviation of the computed ACF 
+in the subfields increase when  increasing $M_{min}$ following the same 
+trend as in figure \ref{figure:laes_dist}.Therefore, as the cosmic variance
+increase when increasing the halos mass the increment in the ACF standard 
+deviation when increasing $M_{min}$ is a direct consequence of cosmic variance.
+
+Given that the ACF reported by Hayashino et al en 2004 is taken over the densest 
+field oserved in the SSA22 region by  Yamada et el in 2012 it is expected that
+the predicted ACF in the SSA22 region should reproduce this observation. In the 
+left panel of figure \ref{figure:correlation_match} we can see the predicted ACFs 
+an their corresponding standard deviation over the seven fields that mock the SSA22 
+region. It can be seen that the model with $M_min=10.6$ seems to better reproduce the 
+Hayashino's ACF and that the corresponding field is in fact an overdense field in the
+SSA22 region covered by Yamada et al.
 
@@
 \begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
+\hspace{5mm}
 \includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plot/match_large_correlation_selected_models.pdf}\\
-\end{center} 
-\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
-some selected models in different mass ranges. \label{figure:correlation_match} }
+\end{center} f
+\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
+over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
+match configuration. \label{figure:correlation_match} }
 
@@
 \begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
+\hspace{5mm}
 \includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plot/random_large_correlation_selected_models.pdf}\\
 \end{center} 
-\caption{ mean ACFs over the 7 subfields of the SSA22 field and their correponding standard deviation (error bars)
-some selected models in different mass ranges. \label{figure:correlation_match} }
+\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
+over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
+random configuration. \label{figure:correlation_random} }
 

### 2013-04-05 code/field_correlation.py
added file to compute correlation funtion for a given model

@@ -1,0 +1,206 @@
+#!/usr/bin/env python
+
+import LAE_correlation as correlation
+import numpy as np
+import pylab as P
+
+field="full"
+survey_type="match"
+theta_max=1040
+theta_min=0
+theta_bins=13
+pro_path="/home/jemejia/CosmicVarianceLAES/"
+box_length=250.0
+x_width=46.0
+y_width=35.0
+z_depth=41.0
+obs_surveys=12
+random_cat_number=16
+distance=6558.3
+
+print "computing correlation functions of the selected models"
+dmh_path=pro_path+"data/dark_matter/FOF/"
+laes_path=pro_path+"data/laes/FOF/"
+n_i= int( box_length/x_width)
+n_j= int( box_length/y_width)
+n_k= int( box_length/z_depth)
+n_models = n_i * n_j * n_k
+    
+ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
+    
+
+
+model_info=np.loadtxt("./model_data.dat",skiprows=2)
+
+m_min_m=model_info[:,0] #_m refers to model
+m_max_m=model_info[:,1]
+f_occ_m=model_info[:,2]
+ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
+p_values_file= pro_path + "data/mock_survey/" + "p_values_FOF_ID_" + survey_type + "_surveys.dat"
+
+ID_data=np.loadtxt(ID_file,dtype='int')
+ks_data=np.loadtxt(p_values_file) 
+
+survey_ID=ID_data[:,0]
+field_ID=ID_data[:,1]
+i_field = ID_data[:,2]
+j_field = ID_data[:,3]
+k_field = ID_data[:,4]
+
+del ID_data
+
+m_min_arr = ks_data[:,0]
+m_max_arr =ks_data[:,1]
+f_occ_arr =ks_data[:,2]
+ID_survey_arr = ks_data[:,3]
+model_prob_arr = ks_data[:,4]
+
+
+del ks_data
+best_correlation=np.empty([len(m_min_m),theta_bins])
+std_correlation=np.empty([len(m_min_m),theta_bins])
+    
+for w in range( len(m_min_m) ):
+
+    model_index=np.where( ( m_min_arr == m_min_m[w] ) & ( m_max_arr == m_max_m[w] ) & ( f_occ_arr == f_occ_m[w] )  )  
[…]

### 2013-04-08 paper/ms.tex
removed bias section

@@
 
-\subsection{Estimating the Galaxy Bias from the Halo Masses}
-Using the results from the previous sections it is possible to infer
-the bias of $z\sim 3$ LAEs. Considering a number of $N_{\rm fields}$
-the expected number density of galaxies around the region located at
-$x_{i}$ is $n_{i}=\bar{n}[1+ b\delta_{\rm DM}(x_{i})]$, where
-$\bar{n}$ is the average galaxy number density and $\delta_{\rm
-  DM}\equiv (\rho - \bar{\rho})/\bar{\rho}$ is the matter overdensity
-in the field [REF robertson].
-
-We calculate the bias for each mock catalog in the best models using
-the corresponding dark matter overdensity in the simulation. This
-results in a distribution of bias values for each model. The results
-for this calculation are presented in Figure XX.  We compare this
-result against the following estimation $b^{2}\sim {\sigma_{N}^{2} -
-  \bar{N}}/\bar{N}^{2}\sigma_{\rm DM}^{2}$, where $\bar{N}$ is the
-average number counts in the $N_{fields}$, $\sigma_{N}$ is their
-dispersion and $\sigma_{DM}$ is the matter variance over many survey
-volumes.
-
 \subsection{Prediction for the angular correlation function}

### 2013-04-08 paper/ms.tex
new text on correlation functions

@@
 
-\subsection{Selection of the preferred halo mass}
+\subsection{Kolmogorov-Smirnov Tests}
 
@@
 
-\subsection{Additional observational constraints on the occupation fraction}
+\subsection{Constraints from the Angular Correlation Function}
+
+We calculate the mean angular correlation function (ACF) for all
+models with $P>0.05$ using the match and random methods. These
+correlation functions is calculated over the denseset subfield in all the
+mock surveys corresponding to the SSA22 region. These results are
+compared against the observations reported by Hayashino et al in 2004
+over the same region, which were also performed on the densest field.
+
+Figure \ref{figure:correlation_match} (match) and Figure
+\ref{figure:correlation_random} (random) present such comparison.  The
+error bars in these figures represent the standard deviation of the
+ACF over all the sub-fields.  In general, we observe that the standard
+deviation of the computed ACF in the subfields increases with
+$M_{min}$ following the same trend as in Figure
+\ref{figure:laes_dist}, as a direct consequence of cosmic variance.
+
+The comparison between the simulated and observed ACFs is also done using a
+$R^2$ statistic which includes the information on measurement uncertainties
+
+\begin{equation}
+R^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
+    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
+    sim}^2({\theta_i})}, 
+\end{equation}
+
+where the sum is done over all the angle values $\theta_i$ where the
+ACF has been computed. In Figure XX we plot the integrated
+distributions for this $R^{2}$ statistics
+
+Given that the ACF reported by Hayashino et al en 2004 is taken over the densest 
+field oserved in the SSA22 region by  Yamada et el in 2012 it is expected that
+the predicted ACF in the SSA22 region should reproduce this observation. In the 
+left panel of figure \ref{figure:correlation_match} we can see the predicted ACFs 
+an their corresponding standard deviation over the seven fields that mock the SSA22 
+region. It can be seen that the model with $M_min=10.6$ seems to better reproduce the 
+Hayashino's ACF and that the corresponding field is in fact an overdense field in the
+SSA22 region covered by Yamada et al.
+
+\subsection{Observational constraints on the occupation fraction}
 
@@
 
-As a prediction, we calculate the mean angular correlation function (ACF) for some of the best
-models for a mock survey using the match and random methods with 
-two different surface areas: $1)$ the full survey (12 subfields) and
-$2)$  e SSA22 field (7 subfields) reported by Yamada et al 2012 
-(see section XX) . The results for these calculations  are shown 
-in figure \ref{figure:correlation_match} (match) and figure
-\ref{figure:correlation_random} (random).  The error bars in these figures
-represent the standard deviation of the ACF over the subfields. 
-We compare these results with the observed ACF in a field of the the SSA22 region
-reported by Hayashino et al in 2004.
-
-We can generally observe that the standard deviation of the computed ACF 
-in the subfields increase when  increasing $M_{min}$ following the same 
-trend as in figure \ref{figure:laes_dist}.Therefore, as the cosmic variance
-increase when increasing the halos mass the increment in the ACF standard 
-deviation when increasing $M_{min}$ is a direct consequence of cosmic variance.
-
-Given that the ACF reported by Hayashino et al en 2004 is taken over the densest 
-field oserved in the SSA22 region by  Yamada et el in 2012 it is expected that
-the predicted ACF in the SSA22 region should reproduce this observation. In the 
-left panel of figure \ref{figure:correlation_match} we can see the predicted ACFs 
-an their corresponding standard deviation over the seven fields that mock the SSA22 
-region. It can be seen that the model with $M_min=10.6$ seems to better reproduce the 
-Hayashino's ACF and that the corresponding field is in fact an overdense field in the
-SSA22 region covered by Yamada et al.
+As a prediction,
 

### 2013-04-10 paper/ms.tex
added new text

@@
 at a redshift of $z=3.1$. The method is based on matching the
-statistics for the number density cosmic variance between different
-observed and mock fields. We build a model for LAEs on top of a large N-body
-cosmological simulation (Bolshoi) where the basic principle is that a dark
-matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
+statistics for the number density cosmic variance between observed and
+mock fields. We build a model for LAEs on top of a large N-body
+cosmological simulation (Bolshoi) where the basic principle is that a
+dark matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
 mass is found withing a certain range mass range delimited by two
@@
 
+\subsection{Observational constraints on the occupation fraction}
+
+\cite{Hayes2010} constrained the value of $f_{\rm occ}$ at $z=2.2$ to
+be $f_{\rm occ}=0.10$. This estimation was based on blind surveys of
+the H$\alpha$ and Lyman alpha line with the European Southern
+Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
+extinction to obtain an estimate for the intrinsic H$\alpha$
+luminosity, and using values for the theoretical expectation of the
+ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
+the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
+esc}=(10.7\pm 2.8)$ if a different dust correction is used. From this
+results they derive that almost $90\%$ of the star forming galaxies
+emit insufficient Lyman-alpha to be detected, effectively setting the
+occupation fraction to be $f_{\rm occ}=0.10$. Obervations are
+consistent with these numbers are
+consistent with being constant for every galaxy regardless of its
+luminosity.
+
+For the cosmological parameters used in this \documentname the age of
+the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$ Gyr,
+it is reasonable to assume that the physical conditions that determine
+the escape fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm
+  occ}$ remain constant. This assumption allows us to further pick
+models that have an occupation fraction of $f_{\rm occ}=0.10$. Under
+this selection only $18$ models can be selected. Considering an
+occupation fraction $f_{\rm occ}=0.20$ another $39$ models can be
+considered. The minimum and maximum mass are found in the appendix in
+Table XX.
+
 \subsection{Constraints from the Angular Correlation Function}
@@
 
-Given that the ACF reported by Hayashino et al en 2004 is taken over the densest 
-field oserved in the SSA22 region by  Yamada et el in 2012 it is expected that
-the predicted ACF in the SSA22 region should reproduce this observation. In the 
-left panel of figure \ref{figure:correlation_match} we can see the predicted ACFs 
-an their corresponding standard deviation over the seven fields that mock the SSA22 
-region. It can be seen that the model with $M_min=10.6$ seems to better reproduce the 
-Hayashino's ACF and that the corresponding field is in fact an overdense field in the
-SSA22 region covered by Yamada et al.
+Given that the ACF reported by Hayashino et al en 2004 is taken over
+the densest  field oserved in the SSA22 region by  Yamada et el in
+2012 it is expected that the predicted ACF in the SSA22 region should
+reproduce this observation. In the  left panel of figure
+\ref{figure:correlation_match} we can see the predicted ACFs  an their
+corresponding standard deviation over the seven fields that mock the
+SSA22  region. It can be seen that the model with $M_min=10.6$ seems
+to better reproduce the  Hayashino's ACF and that the corresponding
+field is in fact an overdense field in the SSA22 region covered by
+Yamada et al.
 
-\subsection{Observational constraints on the occupation fraction}
-
-\cite{Hayes2010} constrained the value of $f_{\rm occ}$ at $z=2.2$ to
-be $f_{\rm occ}=0.10$. This estimation was based on blind surveys of
-the H$\alpha$ and Lyman alpha line with the European Southern
-Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
-extinction to obtain an estimate for the intrinsic H$\alpha$
-luminosity, and using values for the theoretical expectation of the
-ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
-the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)$ if a different dust correction is used. From this
-results they derive that almost $90\%$ of the star forming galaxies
-emit insufficient Lyman-alpha to be detected, effectively setting the
-occupation fraction to be $f_{\rm occ}=0.10$. Obervations are
-consistent with these numbers are
-consistent with being constant for every galaxy regardless of its
-luminosity.
-
-For the cosmological parameters used in this \documentname the age of
-the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$ Gyr,
-it is reasonable to assume that the physical conditions that determine
-the escape fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm
-  occ}$ remain constant. This assumption allows us to further pick
-models that have an occupation fraction of $f_{\rm occ}=0.10$. Under
-this selection only $18$ models can be selected. Considering an
-occupation fraction $f_{\rm occ}=0.20$ another $39$ models can be
-considered. The minimum and maximum mass are found in the appendix in
-Table XX.
+From these tests we conclude that the ACF on small fields does not
+provide additional constraints to further select models for halos
+hosting LAEs. The reason is that cosmic variance is large and the
+statistical uncertainties on the ACF render almost any model
+compatible with the observational constraints.
 
@@
 
-As a prediction,
+We also present the ACF in the case of the full SSA22
+region which has been homogeneously observed by \citep{Yamada2012}. To
+this date the observational ACF has not been reported in the
+litereature, therefore our calculations can be considered as
+predictions.
+
+In Figure X we present the results for the models. The full list of
+these correlation functions can be found in the the data repository
+for this paper in \verb"github".
 
@@
 \end{center} f
-\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
-over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
-match configuration. \label{figure:correlation_match} }
+\caption{ mean ACFs   and their correponding standard deviation (error
+  bars)  of some selected models in different mass ranges over the 7
+  subfields  f the SSA22 field (left) and the entire 12 field sample
+  (rigth) using thematch
+  configuration. \label{figure:correlation_match} }
 
@@
 \section{Conclusions}
-In this \documentname we have constrained the preferred mass for dark matter
+In this \documentname we constrain the preferred mass for dark matter
 halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
 method that matches the cosmic variance in the surface
-density number of LAEs from differente observed fields. From this we
-are able to constrain the mass range of dark matter halos hosting LAEs
-to be in the range $<M_{\rm h}<$ and a corresponding occupation fraction
-that escales as $f_{\rm occ} = M_{\rm min}$ with the minium halo mass
-defining the halo mass range.
+density number of LAEs from differente observed fields to mock fields
+based on a simplified model with three basic parameters. The halo
+masses that define the halos where LAEs can be found, $M_{\rm
+  min}<M_{\rm h}<M_{\rm max}$, and the fraction of the halos in this
+range that are actully occupied, $f_{\rm occ}$. After a thorugh
+exploration of the paremeter space we are able to constrain the mass
+range of dark matter halos hosting LAEs to be in the range $<M_{\rm
+  h}<$ and a corresponding occupation fraction that escales as $f_{\rm
+  occ} = M_{\rm min}$.
 
-In this letter, this estimate is based on a large Nbody simulation
-where we select a range a fraction of halos in a given mass range to
-host LAEs. We explicitly construct mock observations to derive
-statistics that can be compared against observations.
+In this letter, our estimates are based on a large volume, high
+resolution, dark matter only Nbody simulation. From the halo catalogs
+in the simulation a fraction of halos in a given mass range to
+host LAEs. We use this information to construct mock observations to
+derive the statistics that can be compared against observations. The
+spatial information in this catalogs is also kept, which allows us to
+compute angular correlation functions and include these results in our
+analysis.
 
- The method is based on making an estimate of the cosmic
-variance from different observed fields. Based on a Nbody simulation,
-we select the range of halo masses, $M_{\rm min}<M_{\rm h}<M_{\rm
-  max}$, and the fraction of these halos, $f_{\rm occ}$, that could
-host LAEs being compatible witht the cosmic variance constraints.
+We simulation allows us to extract $210$ sub-boxes each of which has a
+comparable volume to the individual fields of view observed by
+\cite{Yamada2012}. The comparison of the observed number density
+distribution against the results from our model is based on three
+different ways of constructing mock surveys. The first reproduces the
+spatial correlation between the $12$ observational fields ({\texttt
+  match}), the second breaks this spatial correlation while keeping
+the number of fields ({\texttt random}) and the third one simply
+includes all the $210$ sub-boxes ({\texttt full}). We find that the
+methods {\texttt match} and {\texttt random} allow a larger set of
+models than the {{\texttt random}} method. We do not find a
+significant difference between the two first methods.
 
-We have used a large volume cosmological N-body simulation that allows
-us to extract $210$ sub-boxes each of which has a comparable
-volume to the field of view observed by Yamada et al. 2012. The
-comparison of the observed number density distribution against the
-results from our model is based on three different ways of
-constructing mock surveys. The first reproduces the spatial
-correlation between the $12$ observational fields, the second breaks
-this spatial correlation while keeping the number of fields and the
-third one simply includes all the $210$ sub-boxes.
+Including additional observational constraints on the occupation
+fraction allows us to reduce the range of allowed halo masses to be in
+a narrower range of $<M_{\rm h}<$. Including the information from the
+angular correlation function (ACF) does not allows us to impose
+further constraints. This is due to the scatter in the ACF due to the
+cosmic variance on the field observed by XXX
 

### 2013-04-10 code/model_correlation.py
bug fixed in model correlation

@@ -191,7 +191,7 @@ for w in range( len(m_min_m) ):
         DR,bins=correlation.DR_histogram(x_laes,y_laes,x_drand,y_drand,distance,theta_min,theta_max,theta_bins,cat_number=1)
         print "DR computed"
         
-        corr[j,:]=correlation.peebles_correlation(DD,RR,DR)
+        corr[j,:]=correlation.peebles_correlation(DD,DR)
 
         max_density_index=np.argmax(n_laes)
         number_laes=n_laes[max_density_index]
@@ -206,7 +206,7 @@ for w in range( len(m_min_m) ):
         #RR,bins=correlation.RR_histogram(x_laes_max,y_laes_max,x_random_max,y_random_max,distance,theta_min,theta_max,theta_bins,cat_number=random_cat_number)    
         DR,bins=correlation.DR_histogram(x_laes_max,y_laes_max,x_drand_max,y_drand_max,distance,theta_min,theta_max,theta_bins,cat_number=1)
         DD,bins=correlation.DD_histogram(x_laes_max,y_laes_max,distance,theta_min,theta_max,theta_bins)
-        corr_max_density[j,:]=correlation.peebles_correlation(DD,RR,DR)
+        corr_max_density[j,:]=correlation.peebles_correlation(DD,DR)
 
 
         print "CORR_landy=",corr[j,:]
@@ -224,18 +224,30 @@ for w in range( len(m_min_m) ):
     correlation_data=np.empty(( np.size(corr_laes) , 3 ) )
     model='(Mmin,Mmax,focc)=({0},{1},{2})'.format(m_min, m_max, f_occ)
     model_name = 'model_{0}_{1}_{2}'.format(m_min, m_max, f_occ)
-    filename=pro_path + "data/mock_survey/" + "correlation_best_models/" + survey_type + "_correlation_" + model_name + ".dat"
+    filename=pro_path + "data/mock_survey/" + "correlation_best_models/" + survey_type + "_correlation_" + str(w) + ".dat"
         
     angles = np.linspace( theta_min + dtheta/2.0 , theta_max - dtheta/2.0, theta_bins )
+    
+
     correlation_data[:,0]=angles
     correlation_data[:,1]=best_correlation[w,:]
     correlation_data[:,2]=std_correlation[w,:]
-        
+    
     np.savetxt(filename,correlation_data)
+    
     fig=P.figure()
     ax_mean=fig.add_subplot(111)
[…]

### 2013-04-12 paper/ms.tex
new sections in the paper, more structured

@@
 
+\section{Discussion}
+
+The raw results of our experiments yield a prefered range for
+halo masses hosting LAES is in the range $10^{10}\hMsun<M_{\rm
+  min}<10^{11.5}\hMsun$, without any limitation in the  maximum mass,
+plus an average occupation fraction as a function of the minimum mass
+$f_{occ}\approx 0.1 (M_{\rm min}/10^{10})^{XX}$. This exercise was
+useful to discard models that were nevertheless disfavored from the
+very beginning based on the results of the mass functions (see Figure 1.).
+
+In this discussion section we consider different ways to impose tighter
+constraints by making use of the results we have derived so far and
+using additional statistical and astrophysical constraints. We will
+consider three different constraints. The first is based on
+models with high fractions of mock surveys that are consistent with
+observations. The second uses observational results on the occupation
+fraction. The third exploits the observational information in the Angular
+Correlation Function.
+
+\subsection{Models with highest success rates}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
+\end{center} 
+\caption{ Number of models with a mininium number of mock survey
+  realizations that are consistent with observations.
+  \label{figure:high_success_rate}.}  
+\end{figure*}
+
+For each model there are 15 different realizations of mock surveys. In
+the loose constraints of the previous sections, each model has at
+least one (1) realization of mock survey with $P>0.05$. In Figure XX
+we show the number of models that have at least $n$ realizations with
+$P>0.05$ for the {\texttt match} and {\texttt random} methods.
+
+This Figure shows that there are around $550$ to $600$ different
+models that have at leaset one mock survey realization consistent with
+observations. At the other extreme, there are $80$ to $100$ models
+with all the 15 realizations with $P>0.05$. Here we focuse on the
+latter models.
+
 \subsection{Observational constraints on the occupation fraction}

### 2013-04-19 paper/ms.tex
udpated paper

--- 2013-04-10 paper/ms.tex
@@
 \title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Using cosmic
-  variance to constrain the
-  dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1}
+  variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1}
+
 \author[~J.~E. Forero-Romero and J. Mejia]{
@@
 \begin{abstract}
-We use simulations and recent observations to find the characteristic
-mass of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies
-at a redshift of $z=3.1$. The method is based on matching the
-statistics for the number density cosmic variance between observed and
-mock fields. We build a model for LAEs on top of a large N-body
-cosmological simulation (Bolshoi) where the basic principle is that a
-dark matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
+We use cosmological N-body simulations to find the characteristic
+mass of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a redshift of $z=3.1$.
+The method is based on matching the statistics for the number density between mock and observed fields.
+The mock catalogs are constructed using a simple model where the basic principle is that a dark matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
 mass is found withing a certain range mass range delimited by two
 threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
-hundreds of mock catalogs in a thourough exploration of the parameter
-space of this model. These catalogs are constructed in such a way as
-to reproduce the spatial correlation between the different observed
-fields. We find that the models that best match the observed cosmic
-variance statistics are those with halo masses in the range $M_{\rm
-  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales
-as $f_{\rm occ}=$ with the minimum mass. We find that the angular
-correlation function is in agreement with the observational
-constraints mostly due to the cosmic variance in the small angular
-fields where this statistics has been computed so far. We also present
-predictions for future measurements of the correlation function on
-larger continous fields. We make available the mock data for the best
+hundreds of mock catalogs in a thourough exploration of the parameter space of this model.
+These catalogs are constructed in such a way as o reproduce the observed areas and spatial correlations between the different observed fields.
+We find that the models that are consistent the observed cosmic variance statistics are those with halo masses in the range $M_{\rm
+  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales as $f_{\rm occ}=$ with the minimum mass.
+We explore three additional constraints to narrow these range.
+First we select the models with the highest possible number of mocks consistent with observations.
+Second we use observational constraints on the occupation fraction.
+Third, we compute the angular correlation function in the mocks against observational values.
+The first two conditions narrow down the space parameter to $M_{\rm min}=$ and $M_{\rm max}$, $f_{\rm occ}$.
+Although we find that the angular correlation function is in agreement with the observational constraints mostly due to the cosmic variance in the small angular fields where this statistics has been computed so far, this statistics does not allows us to put tighter constraints on the model parameters.
+We also present predictions for future measurements of the correlation function on larger continous fields.
+We make available the mock data for the best
 models in a public repository.  
+Implications for galaxy formation models?
 \end{abstract}
@@
 
+In what follows we will focus our discussion on the mocks constructed with the {\tt{Match}} and {\tt{Random}} methods.
+
+\section{Discussion}
+
+The raw results of our experiments yield a prefered range for
+halo masses hosting LAES is in the range $10^{10}\hMsun<M_{\rm
+  min}<10^{11.5}\hMsun$, without any limitation in the  maximum mass, with an average occupation fraction as a function of the minimum mass with an approximate dependence of the kind $f_{occ}\approx 0.1 (M_{\rm min}/10^{10})^{XX}$.
+These results discard models that were nevertheless disfavored from the very beginning based on the results of the mass functions (see Figure 1.).
+
+In this discussion section we consider three different ways to impose tighter constraints by making use of the results we have derived so far and using additional statistical and astrophysical constraints.
+The first is based on
+models with high fractions of mock surveys that are consistent with
+observations. The second uses observational results on the occupation
+fraction. The third exploits the observational information in the Angular
+Correlation Function (ACF).
+
+\subsection{Models with the highest success rates}
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
+\end{center} 
+\caption{ Number of models with a mininium number of mock survey
+  realizations that are consistent with observations.
+  \label{figure:high_success_rate}.}  
+\end{figure*}
+
+For each model there are 15 different mock survey realizations of mock. In
+the loose constraints of the previous sections, each model that had at
+least one (1) realization of mock survey with $P>0.05$ was considered as consistent with observations.
+
+In Figure XX we show the number of models that have at least $n$ realizations with $P>0.05$ for the {\texttt match} and {\texttt random} methods.
+This shows that there are around $550$ to $600$ different models that have at leaset one mock survey realization consistent with observations.
+At the other extreme, there are $80$ to $100$ models with all the 15 realizations with $P>0.05$.
+Here we focuse on the latter models.
+The best models represent $\sim 15\%$ of the number of initially considered good models.
+
+In Figure XX we present the locii of these models in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$.
+
 \subsection{Observational constraints on the occupation fraction}
 
-\cite{Hayes2010} constrained the value of $f_{\rm occ}$ at $z=2.2$ to
-be $f_{\rm occ}=0.10$. This estimation was based on blind surveys of
+We now impose a different restriction using the observational results by \cite{Hayes2010}.
+These authors constrained the value of $f_{\rm occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$.
+This estimation was based on blind surveys of
 the H$\alpha$ and Lyman alpha line with the European Southern
@@
 the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)$ if a different dust correction is used. From this
-results they derive that almost $90\%$ of the star forming galaxies
-emit insufficient Lyman-alpha to be detected, effectively setting the
-occupation fraction to be $f_{\rm occ}=0.10$. Obervations are
-consistent with these numbers are
-consistent with being constant for every galaxy regardless of its
-luminosity.
+esc}=(10.7\pm 2.8)$ if a different dust correction is used.
+The authors show that the luminosity function for LAEs at $z=2.2$ is consistent with the escape fraction being constant for every galaxy regardless of its luminosity.
+From this results they derive that almost $90\%$ of the star forming galaxies emit insufficient Lyman-alpha to be detected, effectively setting the occupation fraction to be $f_{\rm occ}=0.10$.
 
 For the cosmological parameters used in this \documentname the age of
-the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$ Gyr,
-it is reasonable to assume that the physical conditions that determine
-the escape fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm
-  occ}$ remain constant. This assumption allows us to further pick
-models that have an occupation fraction of $f_{\rm occ}=0.10$. Under
+the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical conditions that determine
+the escape fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$ remain constant over that time scale.
+This assumption allows us to further pick models that have an occupation fraction of $f_{\rm occ}=0.10$.
+Under
 this selection only $18$ models can be selected. Considering an
 occupation fraction $f_{\rm occ}=0.20$ another $39$ models can be
-considered. The minimum and maximum mass are found in the appendix in
-Table XX.
+considered. This constraint help us to select $\sim 10\%$ of the original models that were considered as consistent with observations in the previous section.
+
+Figure XX shows the prefered models in the planes $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$ for the {\tt match} and {\tt random} methods.
+The list for the model parameters is found in the appendix in Table XX.
+
+In terms of the constraints done in the previous sub-section, we find that the models in this region of parameter space have an average number of XX mock catalogs consistent with observations.
 
@@
 mock surveys corresponding to the SSA22 region. These results are
-compared against the observations reported by Hayashino et al in 2004
-over the same region, which were also performed on the densest field.
+compared against the observations reported by Hayashino et al in 2004 over the same region, which were also performed on the densest field.
 

### 2013-04-22 paper/ms.tex
small additions to the paper

@@
 \newcommand{\documentname}{paper~}
+\newcommand{\match}{{\tt match}~}
 \newcommand{\apj}{ApJ}  
@@
 \begin{abstract}
-We use cosmological N-body simulations to find the characteristic
-mass of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a redshift of $z=3.1$.
-The method is based on matching the statistics for the number density between mock and observed fields.
-The mock catalogs are constructed using a simple model where the basic principle is that a dark matter halo can only host one LAE with a probability $f_{\rm occ}$ if its
-mass is found withing a certain range mass range delimited by two
-threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
-hundreds of mock catalogs in a thourough exploration of the parameter space of this model.
-These catalogs are constructed in such a way as o reproduce the observed areas and spatial correlations between the different observed fields.
-We find that the models that are consistent the observed cosmic variance statistics are those with halo masses in the range $M_{\rm
-  min}=$ and $M_{\rm max}=$ with and occupation fraction that scales as $f_{\rm occ}=$ with the minimum mass.
-We explore three additional constraints to narrow these range.
-First we select the models with the highest possible number of mocks consistent with observations.
-Second we use observational constraints on the occupation fraction.
-Third, we compute the angular correlation function in the mocks against observational values.
-The first two conditions narrow down the space parameter to $M_{\rm min}=$ and $M_{\rm max}$, $f_{\rm occ}$.
-Although we find that the angular correlation function is in agreement with the observational constraints mostly due to the cosmic variance in the small angular fields where this statistics has been computed so far, this statistics does not allows us to put tighter constraints on the model parameters.
-We also present predictions for future measurements of the correlation function on larger continous fields.
-We make available the mock data for the best
-models in a public repository.  
-Implications for galaxy formation models?
+We use cosmological N-body simulations to find the characteristic mass
+of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
+redshift of $z=3.1$. The method is based on matching the statistics
+for the number density between mock and observed fields. The mock
+catalogs are constructed using a simple model where the basic
+principle is that a dark matter halo can only host one LAE with a
+probability $f_{\rm occ}$ if its mass is found withing a certain range
+mass range delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
+hundreds of mock catalogs in a thourough exploration of the parameter
+space of this model. These catalogs are constructed in such a way as o
+reproduce the observed areas and spatial correlations between the
+different observed fields. We find that the models that are consistent
+the observed cosmic variance statistics are those with halo masses in
+the range $M_{\rm  min}=$ and $M_{\rm max}=$ with and occupation
+fraction that scales as $f_{\rm occ}=$ with the minimum mass. We
+explore three additional constraints to narrow these range. First we
+select the models with the highest possible number of mocks consistent
+with observations. Second we use observational constraints on the
+occupation fraction. Third, we compute the angular correlation
+function in the mocks against observational values. The first two
+conditions narrow down the space parameter to $M_{\rm min}=$ and
+$M_{\rm max}$, $f_{\rm occ}$. Although we find that the angular
+correlation function is in agreement with the observational
+constraints mostly due to the cosmic variance in the small angular
+fields where this statistics has been computed so far, this statistics
+does not allows us to put tighter constraints on the model
+parameters. We also present predictions for future measurements of the
+correlation function on larger continous fields. We make available the
+mock data for the best models in a public repository. Implications for
+galaxy formation models? 
 \end{abstract}
@@
 central topic in studies of structure formation in the Universe. The
-reason is the diverse range of fields where they are helpful, LAEs can
+reason is the diverse range of fields where they are helpful. LAEs can
 be used as probes of reionization, tracers of large scale structure,
@@
 arcmin$^{2}$. For each number density distribution we perform a
-Kolmogorov-Smirnov againsg the $12$ surface density observational
+Kolmogorov-Smirnov against the $12$ surface density observational
 values. From this test we obtain the value $0<P<1$ to reject the null
@@
 integrated dark matter halo surface density as a function of halos
-mass. Each line correspond to one of the 210 sub-volumes in the
+mass. Each line corresponds to one of the 210 sub-volumes in the
 Bolshoi simulation. The shadowed area indicates the surface density
@@
 
-This result allows us to better understand the
-expected trends for the LAEs' preferred mass and the occupation
-fraction.  From this Figure we can read which models do not have a
-chance reproduce the
+This result allows us to better understand the expected trends for the
+LAEs' preferred mass and the occupation fraction.  From this Figure we
+can read which models do not have achance reproduce the
 observations. Regions in the plot where the halo surface density
@@
 masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
-$M_{\rm   min}> 3 \times 10^{11}$\hMsun located in that mass range,
-the surface density is too low compared with observations.
+$M_{\rm   min}> 3 \times 10^{11}$\hMsun located inthat mass range, the
+surface density is too low compared with observations.
 
@@
 sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
-modest seems to be consistent with observations. This shows that the
+modest fraction seems to be consistent with observations. This shows that the
 cosmic variance is still present on the physical scales probed by
-observations.
+observations. This will be considered in more detail in the discussion
+seccion.
 
@@
 
-In what follows we will focus our discussion on the mocks constructed with the {\tt{Match}} and {\tt{Random}} methods.
+In what follows we will focus our discussion on the mocks constructed
+with the {\tt{Match}} and {\tt{Random}} methods.
 
-\section{Discussion}
+\subsection{Additional Constraints}
 
 The raw results of our experiments yield a prefered range for
-halo masses hosting LAES is in the range $10^{10}\hMsun<M_{\rm
-  min}<10^{11.5}\hMsun$, without any limitation in the  maximum mass, with an average occupation fraction as a function of the minimum mass with an approximate dependence of the kind $f_{occ}\approx 0.1 (M_{\rm min}/10^{10})^{XX}$.
-These results discard models that were nevertheless disfavored from the very beginning based on the results of the mass functions (see Figure 1.).
+halo masses hosting LAES bounded by a minimum mass $10^{10}\hMsun<M_{\rm
+  min}<10^{11.5}\hMsun$ and without any limitation on the  maximum
+mass. In this regime the average occupation fraction varies with an
+approximate dependence of the kind $f_{occ}\approx 0.1 (M_{\rm
+  min}/10^{10})^{XX}$. These results discard models that were
+nevertheless disfavored from the very beginning based on the results
+of the mass functions (see Figure 1.).
 
-In this discussion section we consider three different ways to impose tighter constraints by making use of the results we have derived so far and using additional statistical and astrophysical constraints.
-The first is based on
-models with high fractions of mock surveys that are consistent with
-observations. The second uses observational results on the occupation
-fraction. The third exploits the observational information in the Angular
-Correlation Function (ACF).
+In this section we consider three different ways to impose
+tighter constraints on this mass range by making use of the results we
+have derived so far together with additional statistical and
+astrophysical constraints. In the first constraint we select the
+models where all the mock surveys present KS-test values consistent
+with observations. The second constraints uses recent observational
+results on the average occupation fraction for LAEs at high-z. The
+third exploits the information in the Angular Correlation Function
+(ACF).
 
-\subsection{Models with the highest success rates}
+\subsubsection{Models with the highest success rates}
 \begin{figure*}
@@
 
-For each model there are 15 different mock survey realizations of mock. In
-the loose constraints of the previous sections, each model that had at
-least one (1) realization of mock survey with $P>0.05$ was considered as consistent with observations.
+For each model there are 15 different mock survey realizations. In the
+previous section we presented the models that had at least one (1)
+mock survey realization with $P>0.05$.
 
-In Figure XX we show the number of models that have at least $n$ realizations with $P>0.05$ for the {\texttt match} and {\texttt random} methods.
-This shows that there are around $550$ to $600$ different models that have at leaset one mock survey realization consistent with observations.
-At the other extreme, there are $80$ to $100$ models with all the 15 realizations with $P>0.05$.
-Here we focuse on the latter models.
-The best models represent $\sim 15\%$ of the number of initially considered good models.
+In Figure \ref{figure:high_success_rate} we show the number of models
+that have at least $n$ realizations with $P>0.05$ for the {\texttt
+  match} and {\texttt random} methods.  This shows that there are
+around $550$ to $600$ different models that have at leaset one mock
+survey realization consistent with observations. At the other extreme,
+there are $80$ to $100$ models with all the 15 realizations with
+$P>0.05$. Here we focuse on the latter models. The best models
+represent $\sim 15\%$ of the number of initially considered good
+models.
 
-In Figure XX we present the locii of these models in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$.
+In Figure XX we present the locii of these models in the parameter
+space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$.
 
-\subsection{Observational constraints on the occupation fraction}
+\subsubsection{Observational constraints on the occupation fraction}
 
-We now impose a different restriction using the observational results by \cite{Hayes2010}.
-These authors constrained the value of $f_{\rm occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$.
-This estimation was based on blind surveys of
-the H$\alpha$ and Lyman alpha line with the European Southern
+We now impose a different restriction using the observational results
+by \cite{Hayes2010}. These authors constrained the value of $f_{\rm
+  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
+on blind surveys of the H$\alpha$ and Lyman alpha line with the European Southern
 Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
@@
 the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)$ if a different dust correction is used.
-The authors show that the luminosity function for LAEs at $z=2.2$ is consistent with the escape fraction being constant for every galaxy regardless of its luminosity.
-From this results they derive that almost $90\%$ of the star forming galaxies emit insufficient Lyman-alpha to be detected, effectively setting the occupation fraction to be $f_{\rm occ}=0.10$.
+esc}=(10.7\pm 2.8)$ if a different dust correction is used. The
+authors show that the luminosity function for LAEs at $z=2.2$ is
+consistent with the escape fraction being constant for every galaxy
+regardless of its luminosity. From this results they derive that
+almost $90\%$ of the star forming galaxies emit insufficient
+Lyman-alpha to be detected, effectively setting the occupation
+fraction to be $f_{\rm occ}=0.10$.
 
 For the cosmological parameters used in this \documentname the age of
-the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical conditions that determine
-the escape fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$ remain constant over that time scale.
-This assumption allows us to further pick models that have an occupation fraction of $f_{\rm occ}=0.10$.
-Under
-this selection only $18$ models can be selected. Considering an
-occupation fraction $f_{\rm occ}=0.20$ another $39$ models can be
-considered. This constraint help us to select $\sim 10\%$ of the original models that were considered as consistent with observations in the previous section.
+the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$
+Gyr. We assume that the physical conditions that determine the escape
+fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$
+remain constant over that time scale. This assumption allows us to
+further pick models that have an occupation fraction of $f_{\rm
+  occ}=0.10$. Under this selection only $18$ models can
+beselected. Considering an occupation fraction $f_{\rm occ}=0.20$
+another $39$ models can beconsidered. This constraint help us to
+select $\sim 10\%$ of theoriginal models that were considered as
+consistent with observations in the previous section.
 
-Figure XX shows the prefered models in the planes $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$ for the {\tt match} and {\tt random} methods.
-The list for the model parameters is found in the appendix in Table XX.
+Figure XX shows the prefered models in the planes $M_{\rm min}-M_{\rm
+  max}$ and $M_{\rm min}-f_{\rm occ}$ for the {\tt match} and {\tt
+  random} methods. The list for the model parameters is found in the
+appendix in Table XX.
 
-In terms of the constraints done in the previous sub-section, we find that the models in this region of parameter space have an average number of XX mock catalogs consistent with observations.
+In terms of the constraints done in the previous sub-section, we find
+that the models in this region of parameter space have an average
+number of XX mock catalogs consistent with observations.
 
-\subsection{Constraints from the Angular Correlation Function}
+\subsubsection{Constraints from the Angular Correlation Function}
 
@@
 mock surveys corresponding to the SSA22 region. These results are
-compared against the observations reported by Hayashino et al in 2004 over the same region, which were also performed on the densest field.
+compared against the observations reported by Hayashino et al in 2004
+over the same region, which were also performed on the densest field.
 
@@
 
-\subsection{Prediction for the angular correlation function}
-
 We also present the ACF in the case of the full SSA22
@@
 
+\section{Discussion}
+
+\subsection{Implications for galaxy formation models}
+
+... Intrinsic emission and escape fraction.
+
+... Star formation rate efficiency at this redshift.
+
+... Mass dependence of the escape fraction.
+
+\subsection{Implications for large LAEs surveys}
+
+... The bias for the preferred halo mass.
+
+... The scale at which cosmic variance drops.
+
+... This can be observationally tested with HETDEX.
+
+\subsection{On the reproducibility of our results}
+
+... All the software to produce the results in this paper is publicly
+available.
+
+... The raw catalogs can be obtained from the MultiDark database but
+can also be obtained in the repository of this paper on github.
+
 \section{Conclusions}
@@
 method that matches the cosmic variance in the surface
-density number of LAEs from differente observed fields to mock fields
-based on a simplified model with three basic parameters. The halo
-masses that define the halos where LAEs can be found, $M_{\rm
-  min}<M_{\rm h}<M_{\rm max}$, and the fraction of the halos in this
-range that are actully occupied, $f_{\rm occ}$. After a thorugh
-exploration of the paremeter space we are able to constrain the mass
-range of dark matter halos hosting LAEs to be in the range $<M_{\rm
-  h}<$ and a corresponding occupation fraction that escales as $f_{\rm
-  occ} = M_{\rm min}$.
+density number of LAEs between mock and real observations. The mock
+catalogs are based on a simplified model with three basic parameters: the halo
+mass range where LAEs can be found, $M_{\rm   min}<M_{\rm h}<M_{\rm
+  max}$, and the fraction of the halos in thisrange that are actully
+occupied, $f_{\rm occ}$. After a thorugh exploration of the parameter
+space we are able to constrain the mass range of dark matter halos
+hosting LAEs to be in the range $<M_{\rm   h}<$ and a corresponding
+occupation fraction that escales as $f_{\rm   occ} = M_{\rm min}$.
 
-In this letter, our estimates are based on a large volume, high
-resolution, dark matter only Nbody simulation. From the halo catalogs
-in the simulation a fraction of halos in a given mass range to
-host LAEs. We use this information to construct mock observations to
-derive the statistics that can be compared against observations. The
-spatial information in this catalogs is also kept, which allows us to
-compute angular correlation functions and include these results in our
-analysis.
+We use three additional constraints to reduce the allowed
+range of models. The first imposes a tighter criterion to consider a
+model succesful, namely that all the mock surveys for a given model
+must be consistent with observations. This restriction narrows down
+the allowed range of models to be.
+
+The second constraint is based on the observational results that high
+redshift LAEs have a bulk Lyman alpha escape fraction of $XX$ which
+can be also interepreted as an average occupation fraction of $XX$.
+
+Including additional observational constraints on the occupation
+fraction allows us to reduce the range of allowed halo masses to be in
+a narrower range of $<M_{\rm h}<$. Including the information from the
+angular correlation function (ACF) does not allows us to impose
+further constraints. This is due to the scatter in the ACF due to the
+cosmic variance on the field observed by XXX
 
@@
 significant difference between the two first methods.
-
-Including additional observational constraints on the occupation
-fraction allows us to reduce the range of allowed halo masses to be in
-a narrower range of $<M_{\rm h}<$. Including the information from the
-angular correlation function (ACF) does not allows us to impose
-further constraints. This is due to the scatter in the ACF due to the
-cosmic variance on the field observed by XXX
 

### 2013-04-22 code/LAE_correlation.py
plotting bugs solved

@@ -16,7 +16,9 @@ def DD_histogram(X,Y,distance,th_min,th_max,theta_bins):
     d_arr=[]
     print "number of LAEs=" + str(n_points)
     for i in range(n_points):
-        print "LAE_"+str(i)
+        
+        if(i%100==0):
+            print "LAE_"+str(i)
         for j in range(i+1,n_points):
             d=(X[i] - X[j])*(X[i] - X[j]) + (Y[i] - Y[j])*(Y[i] - Y[j])
             d=np.sqrt(d)/distance
@@ -79,7 +81,8 @@ def DR_histogram(X,Y,Xr,Yr,distance,th_min,th_max,theta_bins,cat_number=3):
     print "number of LAEs=" + str(n_points)
     for m in range(cat_number): 
         for i in range(n_points):
-            print "LAE_"+str(i)
+	    if(i%100==0):
+            	print "LAE_"+str(i)
             for j in range(n_points):
                 d=( X[i] - Xr[j + n_points*m] )*( X[i] - Xr[j + n_points*m] ) + ( Y[i] - Yr[j + n_points*m] )*( Y[i] - Yr[j + n_points*m] )
                 d=np.sqrt(d)/distance

### 2013-04-22 code/model_correlation.py

@@ -58,9 +58,18 @@ model_prob_arr = ks_data[:,4]
 
 del ks_data
 best_correlation=np.empty([len(m_min_m),theta_bins])
+best_corr_laes_max=np.empty([len(m_min_m),theta_bins])
 std_correlation=np.empty([len(m_min_m),theta_bins])
+std_correlation_max=np.empty([len(m_min_m),theta_bins])
+n_models=len(m_min_m)
+#n_models=1 #to delete
 
-for w in range( len(m_min_m) ):
+fig1=P.figure()
+fig2=P.figure()
+ax_mean=fig1.add_subplot(111)
+ax_max=fig2.add_subplot(111)
+
+for w in range( n_models ):
 
     model_index=np.where( ( m_min_arr == m_min_m[w] ) & ( m_max_arr == m_max_m[w] ) & ( f_occ_arr == f_occ_m[w] )  )  
     m_min_s=m_min_arr[model_index] #_s reffers to sorted
@@ -79,6 +88,7 @@ for w in range( len(m_min_m) ):
     ID_index=np.where(survey_ID==ID_survey_s[-1])
     S_ID=survey_ID[ID_index]
     n_mocks=np.size(S_ID)
+    print "n_mocks=" + str(n_mocks)
     corr=np.zeros( (n_mocks,theta_bins) )
     
     #corr_peebles=np.zeros( (n_mocks,theta_bins) )
@@ -88,7 +98,7 @@ for w in range( len(m_min_m) ):
     
     corr_max_density=np.zeros( (n_mocks,theta_bins) )
     corr_laes_max=np.zeros(theta_bins)
-
+    #n_mocks=1 #to delete
     for j in range( n_mocks ): 
         ID_ini=S_ID[j]
         ID_end=int(ID_ini+obs_surveys)
@@ -144,7 +154,9 @@ for w in range( len(m_min_m) ):
             del halo_mass_sel
         
             number_laes=int(f_occ*n_halos)
+            #number_laes=100 #to delete
             n_laes=np.append(n_laes, number_laes )    
+            
             lae_index=halo_index[0:number_laes]
             x_laes=np.append( x_laes, x_halos[lae_index] )
             y_laes=np.append( y_laes, y_halos[lae_index] )
@@ -218,10 +230,13 @@ for w in range( len(m_min_m) ):
     print "corr_landy=",corr_laes, "std_landy=",std_corr
[…]

### 2013-04-29 paper/ms.tex
minor updates
added spatial distribution plot in the paper

@@
 publicly available Multidark database \footnote{{\tt
-    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
+    http://www.multidark.org/MultiDark/}}
+\citep{2011arXiv1109.0003R}.
 
@@
 \subsubsection{Models with the highest success rates}
+
 \begin{figure*}
@@
   \label{figure:high_success_rate}.}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
+\end{center} 
+\caption{Spatial distribution for two mocks corresponding to the model
+  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
+  different mock  surveys for this model in the {\texttt match}
+  configuration are consistent with observations at the $P>0.05$
+  level. The full data for all the mocks can be found in the github
+  repository for this paper.
+  \label{figure:spatial_distro}.}
 \end{figure*}
@@
 In Figure XX we present the locii of these models in the parameter
-space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$.
+space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$. In
+Figure XX we show the spatial distribution for two mock surveys
+corresponding to one of such models.
 
@@
 \end{document}
+
+lun abr 29 07:38:58 COT 2013

### 2013-05-03 code/model_cat_gen.py
mock lae cat generator of some selected models. Catlogs will feed C code to compute the correlation function of the selected models

@@ -1,0 +1,211 @@
+#!/usr/bin/env python
+
+#import LAE_correlation as correlation
+import numpy as np
+import pylab as P
+
+field="large"
+survey_type="match"
+theta_max=1040
+theta_min=0
+theta_bins=13
+pro_path="/home/jemejia/CosmicVarianceLAES/"
+box_length=250.0
+x_width=46.0
+y_width=35.0
+z_depth=41.0
+obs_surveys=12
+random_cat_number=1
+distance=6558.3
+
+
+dmh_path=pro_path+"data/dark_matter/FOF/"
+laes_path=pro_path+"data/laes/FOF/"
+n_i= int( box_length/x_width)
+n_j= int( box_length/y_width)
+n_k= int( box_length/z_depth)
+n_models = n_i * n_j * n_k
+    
+ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
+    
+
+
+model_info=np.loadtxt("./model_data.dat",skiprows=2)
+
+m_min_m=model_info[:,0] #_m refers to model
+m_max_m=model_info[:,1]
+f_occ_m=model_info[:,2]
+ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
+p_values_file= pro_path + "data/mock_survey/" + "p_values_FOF_ID_" + survey_type + "_surveys.dat"
+
+
+
+
+
+ID_data=np.loadtxt(ID_file,dtype='int')
+
+
+
+
+ks_data=np.loadtxt(p_values_file) 
+
+survey_ID=ID_data[:,0]
+field_ID=ID_data[:,1]
+i_field = ID_data[:,2]
+j_field = ID_data[:,3]
+k_field = ID_data[:,4]
+
+del ID_data
+
+m_min_arr = ks_data[:,0]
+m_max_arr =ks_data[:,1]
+f_occ_arr =ks_data[:,2]
+ID_survey_arr = ks_data[:,3]
+model_prob_arr = ks_data[:,4]
+
+
+del ks_data
+best_correlation=np.empty([len(m_min_m),theta_bins])
+best_corr_laes_max=np.empty([len(m_min_m),theta_bins])
+std_correlation=np.empty([len(m_min_m),theta_bins])
+std_correlation_max=np.empty([len(m_min_m),theta_bins])
+n_models=len(m_min_m)
+#n_models=1 #to delete
+
+
+
+
[…]

### 2013-05-06 paper/ms.tex
some edits

@@
 for the number density between mock and observed fields. The mock
-catalogs are constructed using a simple model where the basic
-principle is that a dark matter halo can only host one LAE with a
-probability $f_{\rm occ}$ if its mass is found withing a certain range
-mass range delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. We generate
-hundreds of mock catalogs in a thourough exploration of the parameter
-space of this model. These catalogs are constructed in such a way as o
-reproduce the observed areas and spatial correlations between the
-different observed fields. We find that the models that are consistent
-the observed cosmic variance statistics are those with halo masses in
-the range $M_{\rm  min}=$ and $M_{\rm max}=$ with and occupation
-fraction that scales as $f_{\rm occ}=$ with the minimum mass. We
-explore three additional constraints to narrow these range. First we
-select the models with the highest possible number of mocks consistent
-with observations. Second we use observational constraints on the
-occupation fraction. Third, we compute the angular correlation
-function in the mocks against observational values. The first two
-conditions narrow down the space parameter to $M_{\rm min}=$ and
-$M_{\rm max}$, $f_{\rm occ}$. Although we find that the angular
-correlation function is in agreement with the observational
-constraints mostly due to the cosmic variance in the small angular
-fields where this statistics has been computed so far, this statistics
-does not allows us to put tighter constraints on the model
-parameters. We also present predictions for future measurements of the
-correlation function on larger continous fields. We make available the
-mock data for the best models in a public repository. Implications for
-galaxy formation models? 
+catalogs are constructed using a simple model where a dark matter halo
+can only host one LAE with a probability $f_{\rm occ}$ if its mass is
+found withing a certain range mass range delimited by two threshold
+values, $M_{\rm min}$ and $M_{\rm max}$. We find that the most of the models that
+are consistent the observed cosmic variance statistics are those with
+halo masses in the range $10.5 < \log_{10} M_{\rm  min}/hMsun < 11.5$
+and $\log_{10} M_{\rm max}/\hMsun < 13.5$ with and occupation fraction
+that scales as $f_{\rm occ}=$. We explore three additional constraints
+to narrow down these range: the number of mocks consistent with
+observations, observational constraints on the occupation fraction and
+the angular correlation function. The first two conditions narrow down
+the space parameter to $M_{\rm min}=$ and $M_{\rm max}$, $f_{\rm occ}$. The angular
+correlation function does not add a significant constraint due to the
+cosmic variance in the small angular fields where this statistics has
+been computed so far. We make available the mock data for the best
+models in a public repository. Implications for galaxy formation
+models? 
 \end{abstract}
@@
 
-Most models of galaxy formation find that the mass of the halo largely
-determines key properties of the galaxy such as its stellar mass and
-star formation rate. Processes that regulate the star formation cycle
-are also though to be strongly dependent on its mass. Furthermore, the
-spatial clustering of galaxies on large scales is entirely dictated by
-the halo distribution.  For the reasons mentioned above, finding the
-typical dark matter halo mass hosting LAEs represents a significant
-step forward to understand the nature of this population in the
-context of LCDM.
+Most models of galaxy formation find that the mass of the halo can be
+used to predict properties of the galaxy such as its stellar mass and
+star formation rate \citep{Behroozi2012}. Processes that regulate the
+star formation cycle are also though to be strongly dependent on its
+mass. Furthermore, the spatial clustering of galaxies on large scales
+is entirely dictated by the halo distribution.  For the reasons
+mentioned above, finding the typical dark matter halo mass hosting
+LAEs represents a significant step forward to understand the nature of
+this population in the context of Lambda Cold Dark Matter
+($\Lambda$CDM) paradigm.
 

### 2013-05-07 paper/ms.tex
adding references

@@
 \title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Using cosmic
-  variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1}
+  variance to constrain the dark matter halo mass of Lyman-alpha
+  emitting galaxies at $z$=3.1}
 
@@
 Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
-central topic in studies of structure formation in the Universe. The
-reason is the diverse range of fields where they are helpful. LAEs can
-be used as probes of reionization, tracers of large scale structure,
+central topic in studies of structure formation in the Universe. They 
+are helpful in a diverse range of fields. LAEs can
+be used as probes of reionization \citep{Dijkstra11}, tracers of
+large scale structure \citep{Koehler2007}, 
 signposts for low metallicity stellar populations and markers of the
-the galaxy formation process through cosmic history.
+the galaxy formation process through cosmic history \citep{ForeroRomero2012}.
 
@@
 implemented from analytic considerations, semi-analytic models and
-full N-body hidrodynamical simulations.
+full N-body hidrodynamical simulations \citep{ForeroRomero2011}.
 
@@
 our simplified model. The only cut we impose is that observed LAEs do
-not reside in dark matter halos with masses less than 10$^{10}$hMsun
-[citation].
+not reside in dark matter halos with masses less than 10$^{10}$
+\hMsun [citation].
 

### 2013-05-16 paper/ms.tex
added new references for the intro

@@
 Some theoretical approaches to this problem have been based on a
-forward modelling. Starting from the DM halo population, the
+forward modeling. Starting from the DM halo population, the
 corresponding intrinsic star formation properties are infered and
@@
 and the equivalent width distributions. Such modelling has been
-implemented from analytic considerations, semi-analytic models and
-full N-body hidrodynamical simulations \citep{ForeroRomero2011}.
+implemented from analytic considerations, semi-analytic models
+ and 
+full N-body hidrodynamical simulations
+\citep{Dayal2009, ForeroRomero2011, Yajima2012, ForeroRomero2012} .
 
@@
 density, temperature, topology and kinematics of the neutral Hydrogen
-in the interstellar medium (ISM).
+in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011,
+Laursen2013}.
 

### 2013-05-17 code/correlation/C_code/correlation.c
model_cat_gen.py actualizedto run with jaime's data

@@ -1,6 +1,6 @@
-#include<mass_min_max.h>
+#include<model_correlation.h>
 
-int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double Z_cat[],double histogram_cat[])
+int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double histogram_cat[])
 {
   
   double theta;
@@ -17,11 +17,11 @@ int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double Z_cat[],double h
   for(i=0;i<N_cat;i++)
     {
       
-      for(j=0;j<i;j++)
+      for(j=i+1;j<N_cat;j++)
 	{
 	  d1=sqrt(  (X_cat[i]-X_cat[j])*(X_cat[i]-X_cat[j]) + (Y_cat[i]-Y_cat[j])*(Y_cat[i]-Y_cat[j]) );	      
 	  theta=206265*d1/(D_z);
-          theta=log10(theta); 
+          //theta=log10(theta); 
 	  gsl_histogram_increment(hist_theta_cat,theta);
 	}
     }  
@@ -39,14 +39,10 @@ int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double Z_cat[],double h
 
 
 
-int RR_histogram(double histogram_rand[],int N_POINTS_RANDOM,double std[])
+int RR_histogram(double histogram_rand[],int random_points,double X[],double Y[],double std[])
 {
   
-  //  double X[N_POINTS_RANDOM*N_CATS_RANDOM],Y[N_POINTS_RANDOM*N_CATS_RANDOM],Z[N_POINTS_RANDOM*N_CATS_RANDOM];
-  double *X,*Y,*Z;
-  X=malloc( N_POINTS_RANDOM*N_CATS_RANDOM*sizeof(double) );
-  Y=malloc( N_POINTS_RANDOM*N_CATS_RANDOM*sizeof(double) );
-  Z=malloc( N_POINTS_RANDOM*N_CATS_RANDOM*sizeof(double) );
+  
   double *hist_all;
   hist_all=malloc( N_CATS_RANDOM*THETA_PARTITIONS*sizeof(double) );
   double theta;
@@ -54,7 +50,7 @@ int RR_histogram(double histogram_rand[],int N_POINTS_RANDOM,double std[])
[…]

### 2013-05-17 code/correlation/C_code/correlation.h

@@ -1,5 +1,6 @@
-int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double Z_cat[],double histogram_cat[]);
-int RR_histogram(double histogram_rand[],int N_POINTS_RANDOM,double std[]);
-int DR_histogram(int N_cat,int p,int q,int r,int N_cats_rand,double X_cat[],double Y_cat[],double Z_cat[],double histogram_dr[]);
+int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double histogram_cat[]);
+int RR_histogram(double histogram_rand[],int random_points,double X[], double Y[],double std[]);
+int DR_histogram(int N_cat,int N_cats_rand,double X_cat[],double Y_cat[],double X[],double Y[],double histogram_dr[]);
 int correlation_landy(double histogram_cat[],double histogram_rand[], double histogram_dr[],double correlation[]);
 int correlation_standard(double histogram_cat[],double histogram_rand[],double correlation[]);
+int correlation_peebles(double histogram_cat[],double histogram_dr[],double correlation[]);

### 2013-05-17 code/correlation/C_code/model_correlation.c

@@ -1,0 +1,100 @@
+#include<model_correlation.h>
+
+int main(int argc, char *argv[])
+{
+
+ 
+  
+  
+  int model, survey,i;
+  
+  double correlation[THETA_PARTITIONS];
+  double correlation_s[THETA_PARTITIONS];
+ double correlation_p[THETA_PARTITIONS];
+  char filename[100];
+  double theta;
+  double xc,yc,xr,yr;
+  double *x_cat,*y_cat,*x_rand,*y_rand;
+  double histogram_cat[THETA_PARTITIONS],histogram_rand[THETA_PARTITIONS],histogram_dr[THETA_PARTITIONS];
+  double std_rand[THETA_PARTITIONS];
+
+  FILE *file;
+  int ch;
+  int n_laes;
+  
+  for(model=0;model<N_MODELS;model++)
+    {
+      for(survey=0;survey<MOCK_SURVEYS;survey++)
+	{
+	  
+	  sprintf(filename,"/home/jemejia/CosmicVarianceLAES/data/laes/mock_cat/maxden_model_%d_mock_%d.txt",model,survey);
+	  file=fopen(filename,"r");
+	  
+	  n_laes=0;
+	  while(!feof(file))
+	    {
+	      fscanf(file,"%lf %lf %lf %lf",&xc,&yc,&xr,&yr);
+	      n_laes++;
+	    }
+	  
+	  fclose(file);
+	  
+  
+	  x_cat=malloc(n_laes*sizeof(double));
+	  y_cat=malloc(n_laes*sizeof(double));
+	  x_rand=malloc(n_laes*sizeof(double));
+	  y_rand=malloc(n_laes*sizeof(double));
+	  
+	  file=fopen(filename,"r");
+	  for(i=0;i<n_laes;i++)
+	    {
+	      fscanf(file,"%lf %lf %lf %lf",&xc,&yc,&xr,&yr);
+	      x_cat[i]=xc;
+	      y_cat[i]=yc;
+	      x_rand[i]=xr;
+	      y_rand[i]=yr;	       
+	      
+	    }
+	  printf("nlaes=%d\n",n_laes);
+	  fclose(file);
+	  printf("Computing RR \n");
+	  RR_histogram(histogram_rand,n_laes,x_rand,y_rand,std_rand);
+	  printf(" RR Computed model %d survey %d \n",model,survey);
+	  //	  for(i=0;i<THETA_PARTITIONS;i++)
+	  //{
[…]

### 2013-05-17 code/correlation/C_code/model_correlation.h

@@ -1,0 +1,56 @@
+//cabeceras del C
+#include <stdlib.h>
+#include<stdio.h>
+#include<math.h>
+#include <time.h>
+#include <gsl/gsl_roots.h>
+#include<string.h>
+
+
+
+
+//Cabeceras de gsl
+#include <gsl/gsl_errno.h>
+#include <gsl/gsl_math.h>
+#include <gsl/gsl_histogram.h>
+#include <gsl/gsl_rng.h>
+#include<gsl/gsl_sort_double.h>
+
+
+
+//Cabeceras propias
+
+#include<correlation.h>
+
+//VARIABLES GLOBALES
+#define RMIN 50.0
+#define RMAX 51.25
+#define N_CATS_RANDOM 1
+#define N_CATS_DR 1
+#define THETA_MIN 0.0 //arcsec
+#define THETA_MAX 1040.0 //arcsec
+#define THETA_PARTITIONS 13
+#define D_z 6558.3
+#define H 0.709
+#define PHO_M 3.7e10
+#define BOXSIZE 250.0
+#define GRID_SIZE 250.0
+
+//#define SUB_BOX_SIZE 40.0
+#define SUB_BOX_SIZE_X_OBS 46.0
+#define SUB_BOX_SIZE_Y_OBS 35.0
+#define SUB_BOX_SIZE_Z_OBS 41.0
+#define SUB_BOX_SIZE_X 46.0
+#define SUB_BOX_SIZE_Y 35.0
+#define SUB_BOX_SIZE_Z 41.0
+#define LOWEST_MASS 10.0
+#define HIGHEST_MASS 13.0
+#define MASS_STEP 0.10
+#define MOCK_SURVEYS 12
+#define N_MODELS 3
+#define HALO_MASS_DEV 0.127725e10
+
+
+
+
+

### 2013-05-17 code/model_cat_gen.py

@@ -29,8 +29,8 @@ n_models = n_i * n_j * n_k
 ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
     
 
-
-model_info=np.loadtxt("./model_data.dat",skiprows=2)
+models_file=pro_path + "data/mock_survey/" + "BestModels_match_mock.dat" 
+model_info=np.loadtxt(models_file)
 
 m_min_m=model_info[:,0] #_m refers to model
 m_max_m=model_info[:,1]
@@ -189,7 +189,19 @@ for w in range( n_models ):
             
         
         model_catalog_filename=pro_path +  "data/laes/mock_cat/model_"+str(w)+"_mock_"+str(j)+".txt"
-        np.savetxt(model_catalog_filename,(x_laes,y_laes,x_drand,y_drand))
+        
+
+
+
+
+
+
+        lae_cat=np.empty( [ np.size(x_laes) , 4 ] )
+        lae_cat[:,0]=x_laes
+        lae_cat[:,1]=y_laes
+        lae_cat[:,2]=x_drand
+        lae_cat[:,3]=y_drand
+        np.savetxt(model_catalog_filename,lae_cat)
         
         
         
@@ -206,6 +218,14 @@ for w in range( n_models ):
         x_drand_max = x_drand[lae_pos_ini:lae_pos_end]
         y_drand_max = y_drand[lae_pos_ini:lae_pos_end]
         
+        lae_max=np.empty( [ np.size(x_laes_max) , 4 ] )
+        lae_max[:,0]= x_laes_max
+        lae_max[:,1]= y_laes_max
+        lae_max[:,2]= x_drand_max
+        lae_max[:,3]= y_drand_max
+        
 
         model_catalog_filename=pro_path +  "data/laes/mock_cat/maxden_model_" + str(w) + "_mock_" + str(j) + ".txt"
-        np.savetxt(model_catalog_filename,(x_laes_max,y_laes_max,x_drand_max,y_drand_max))
+        
+        
+        np.savetxt(model_catalog_filename,lae_max)

### 2013-05-20 paper/ms.tex
starting the discussion section + new plots

@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}\\
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
 \vspace{5mm}
-\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}\\
-\vspace{5mm}
-\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig2_full_P5.pdf}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}\\
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
 \end{center} 
@@
   resulting from the KS test. \label{figure:landscape}.}  
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
-\end{center} 
-\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
-  $P>0.05$\label{figure:f_escape}.} 
 \end{figure*}
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
+\end{center} 
+\caption{ Number of models with a mininium number of mock survey
+  realizations that are consistent with observations.
+  \label{figure:high_success_rate}.}  
+\end{figure*}
+
 The raw results of our experiments yield a prefered range for
@@
 \subsubsection{Models with the highest success rates}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
-\end{center} 
-\caption{ Number of models with a mininium number of mock survey
-  realizations that are consistent with observations.
-  \label{figure:high_success_rate}.}  
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
-\end{center} 
-\caption{Spatial distribution for two mocks corresponding to the model
-  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
-  different mock  surveys for this model in the {\texttt match}
-  configuration are consistent with observations at the $P>0.05$
-  level. The full data for all the mocks can be found in the github
-  repository for this paper.
-  \label{figure:spatial_distro}.}
-\end{figure*}
 
@@
 number of XX mock catalogs consistent with observations.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
+\end{center} 
+\caption{Favored models when the constraints on the maximal number of
+  consistent mocks and the observational constrain on the occupation
+  fraction are included.
+  \label{figure:mock_and_f_occ}}  
+\end{figure*}
 
@@
   configuration. \label{figure:correlation_match} }  
-
   \end{figure*}
@@
 \end{center} 
-\caption{ mean ACFs   and their correponding standard deviation (error bars)  of some selected models in different mass ranges
-over the 7 subfields of the SSA22 field (left) and the entire 12 field sample (rigth) using the
-random configuration. \label{figure:correlation_random} }
+\caption{ mean ACFs   and their correponding standard deviation (error
+  bars)  of some selected models in different mass ranges over the 7
+  subfields of the SSA22 field (left) and the entire 12 field sample
+  (rigth) using the  random
+  configuration. \label{figure:correlation_random} }
 
@@
 \section{Discussion}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
+\end{center} 
+\caption{Spatial distribution for two mocks corresponding to the model
+  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
+  different mock  surveys for this model in the {\texttt match}
+  configuration are consistent with observations at the $P>0.05$
+  level. The full data for all the mocks can be found in the github
+  repository for this paper.
+  \label{figure:spatial_distro}.}
+\end{figure*}
+
+When we include the tightest constraints on the mock catalogs, we find
+that there are 30 set of parameters of our model, out of the original
+90000 initial models, that are consistent with the observational
+constraints at redshift $3.1$: the distribution of the number density,
+the inferred values for the average occupation fraction and the
+angular correlation function.
+
+The final 30 models can be distributed into two families of the same
+size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
+typically of less than $<1.0$ dex. While in the second familiy the
+extent $>1.0$ dex. In the first case the minimum halo mass is found to
+be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
+in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
+are compatible with the observational contraints. In what follows we
+discuss the implications of the existence of these two families of
+models.
 

### 2013-05-21 code/correlation_statistic.py
correlation_statistic.py created and correlation_stat.dat added: table with the chisquare of the mean correlation of the densest fields for the models where all the surveys are consistent with the observational density field

@@ -1,0 +1,63 @@
+import numpy as np
+import pylab as P
+
+n_models=101
+n_mocks=12
+theta_bins=13
+pro_path="/home/jemejia/CosmicVarianceLAES/"
+
+
+obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
+obs_correlation=np.loadtxt(obs_correlation_file,skiprows=4)
+models_file=pro_path + "data/mock_survey/" + "BestModels_match_mock.dat" 
+model_info=np.loadtxt(models_file)
+m_min_m=model_info[:,0] #_m refers to model
+m_max_m=model_info[:,1]
+f_occ_m=model_info[:,2]
+
+
+mean_correlation= np.zeros( [n_models,theta_bins] )
+std_correlation = np.zeros( [n_models,theta_bins] )
+chi_individual  = np.zeros( [n_models,n_mocks] )
+for i in range(n_models):
+    corr=np.zeros( (n_mocks,theta_bins) )
+    
+    for j in range(n_mocks):
+        model_correlation_filename=pro_path +  "data/laes/correlation/maxden_model_" + str(i) + "_mock_" + str(j) + ".txt"
+        
+        lae_correlation  = np.loadtxt(model_correlation_filename)
+        corr[j,:] = lae_correlation[:,1]
+        #chi_individual[i,j]= chi_individual[i,j] + (mean_correlation[i,j] - obs_correlation[j,1])*(mean_correlation[i,j] - obs_correlation[j,1])/(std_correlation[i,j]*std_correlation[i,j] + obs_correlation[j,2]*obs_correlation[j,2])
+    std_correlation[i,:]  = np.std(corr,axis=0)
+    mean_correlation[i,:] = np.mean(corr,axis=0)
+
+    chisquare=np.zeros([n_models,theta_bins])
+    chi=np.zeros(n_models)
+for i in range(n_models):
+    for j in range(theta_bins):
+        chisquare[i,j]= chisquare[i,j] + (mean_correlation[i,j] - obs_correlation[j,1])*(mean_correlation[i,j] - obs_correlation[j,1])/(std_correlation[i,j]*std_correlation[i,j] + obs_correlation[j,2]*obs_correlation[j,2])
+        chi[i]= chi[i] + chisquare[i,j] 
[…]

### 2013-05-21 paper/ms.tex
2 new paragraphs in the discussion section

@@
 
-The final 30 models can be distributed into two families of the same
+These 30 models can be classified into two families of the same
 size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
@@
 \subsection{Implications for galaxy formation models}
+
+In the case of a narrow of masses to host LAEs the upper masses are
+bound to be $M_{\rm max}< 10^{11.5}$\hMsun as it is show in Figure
+\ref{figure:mock_and_f_occ}. For halos more massive than this bound it
+is naturally expected that the galaxies can be observed as Lyman Break
+Galaxies (LBGs). This would imply that not all the bright LBGs can
+detected as a LAE.
+
+We have the opposite situation in the second familiy of models. If
+we have a wide range in halo masses, where the upper end of the halo
+masses can be considered as observed LAEs, one can expect that bright
+LBGs will have a correspondence as observed LAEs. The most interesting
+aspect is that there is a clear cut in the minimal mass that can be
+attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
+constraint on the relationship between the minimum star formation rate
+required to be observed as a LAE and this minimal halo mass.
 

### 2013-05-24 paper/ms.tex
minor updates in the paper

@@
 \parbox[t]{\textwidth}{\raggedright 
-  Julian Mej\'ia$^{2}$ and
-Jaime E. Forero-Romero$^{1}$}
+Jaime E. Forero-Romero$^{1}$ and
+Julian Mej\'ia$^{2}$ 
+}
 \vspace*{6pt}\\
-$^{1}$\\
-$^{2}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia 
-}
+$^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
+$^{2}$ --}
 
@@
 
-We calculate the mean angular correlation function (ACF) for all
-models with $P>0.05$ using the match and random methods. These
-correlation functions is calculated over the denseset subfield in all the
-mock surveys corresponding to the SSA22 region. These results are
-compared against the observations reported by Hayashino et al in 2004
-over the same region, which were also performed on the densest field.
+We calculate the mean angular correlation function (ACF) only for the
+models that showed that all of the 15 mock surveys are consistent
+at the $P>0.05$ level with observations. The ACF is computed only the
+denseset subfield in all the 15 mock surveys corresponding to the
+SSA22 region. These results are compared against the observations
+reported by Hayashino et al in 2004 over the same region, which were
+also performed on the densest field.
 
@@
 
+We also present the results for the angular correlation function in
+therms of the correlation lenght obtained by fitting the following
+function
+
+\begin{equation}
+\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
+\end{equation}
+
+The results are shown in Figure in a $r_{0}-\gamma$ plane where the
+average and standard deviation for each mock are shown in comparison
+with the result derived from observations.
+
 \begin{figure*}
@@
 constraints at redshift $3.1$: the distribution of the number density,
-the inferred values for the average occupation fraction and the
-angular correlation function.
+the inferred values for the average occupation fraction. The
+consistency with the angular correlation, in terms of the $\chi^2$
+statistics did not help to discard any additional models with a
+significant degree of confidence.
 

### 2013-05-27 paper/ms.tex
updated observational constraints section

@@
 \section{Methodology}
-In this \documentname we constrain the typical mass of dark matter halos
-hosting LAES at $z=3.1$. Our model is based on the number density
-information obtained in the recent large scale survey presented by XXX
-where XXX LAEs are detected over 7 fields of $\sim 46 \times
-35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed
-fields of $XXX$ deg$^{2}$.
 
-Both the spatial distribution and luminosities of the galaxies have,
-at least in a statistical sense, informatio to constrain theoretical
-model of LAEs. The most detailed theoretical models are also faced to
-diverse physical and astrophysical uncertainties in obtaining
-statistical prediction for the Lyman-alpha line. This uncertainties
-are largest impediment to consruct an ab-iitio model for LAEs.
+Our method to constrain the typical mass of a dark matter halos
+hosting LAEs at $z=3.1$ is based on the comparison of observational
+results on the surface number density and the predictions of a simple
+model that uses the outputs from cosmological N-body simulations.
 
-In this \documentname we want to step back and reduce the complexity of our
-model, with the sole objective of reproducing the cosmic variance in
-the number density of LAEs. Afterwards we will interpret the
-implications of this result for physical models for Lyman-alpha
-emitting galaxies.
+In the next subsections we describe in detail the four key elements of
+this workflow. First, we present the observations we take as a
+benchmark. Second, the N-body simulation and the halo catalogs we
+use. Third, the simplified model that allows us to translated halo
+catalogs into mock LAE observations. Fourth, the statistics we use to
+compare observational results against our theoretical predictions.
 
-Our model is based on the predictions of a large volume high
-resolution N-body simulation describing the gravitational dynamics of
-dark matter. We do not have an strong bias towards the theoretical
-expectation of what the mass of the dark matter halo hosting the
-galaxy should be.  Instead, we fully explore the parameter space of
-our simplified model. The only cut we impose is that observed LAEs do
-not reside in dark matter halos with masses less than 10$^{10}$
-\hMsun [citation].
+%In this \documentname we constrain the typical mass of dark matter halos
+%hosting LAES at $z=3.1$. Our model is based on the number density
+%information obtained in the recent large scale survey presented by XXX
+%where XXX LAEs are detected over 7 fields of $\sim 46 \times
+%35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed
+%fields of $XXX$ deg$^{2}$.
 
-In the following subsections we describe the most relevant features of
-the observational data, the N-body simulation we use, our model and
-its parameters together with the method to compare its predictions
-against observations.
+%Both the spatial distribution and luminosities of the galaxies have,
+%at least in a statistical sense, informatio to constrain theoretical
+%model of LAEs. The most detailed theoretical models are also faced to
+%diverse physical and astrophysical uncertainties in obtaining
+%statistical prediction for the Lyman-alpha line. This uncertainties
+%are largest impediment to consruct an ab-iitio model for LAEs.
+
+%In this \documentname we want to step back and reduce the complexity of our
+%model, with the sole objective of reproducing the cosmic variance in
+%the number density of LAEs. Afterwards we will interpret the
+%implications of this result for physical models for Lyman-alpha
+%emitting galaxies.
+
+%Our model is based on the predictions of a large volume high
+%resolution N-body simulation describing the gravitational dynamics of
+%dark matter. We do not have an strong bias towards the theoretical
+%expectation of what the mass of the dark matter halo hosting the
+%galaxy should be.  Instead, we fully explore the parameter space of
+%our simplified model. The only cut we impose is that observed LAEs do
+%not reside in dark matter halos with masses less than 10$^{10}$\hMsun
+%[citation].
+
+%In the following subsections we describe the most relevant features of
+%the observational data, the N-body simulation we use, our model and
+%its parameters together with the method to compare its predictions
+%against observations.
 
@@
 
-Our observational reference are the recently published results of a
-panoramic survey of LAES at $z=3.1$ by \cite{Yamada2012}. This survey
-was conducted with the Subaru 8.2m telescope and the Subaru Prime
+The observational benchamark we use in this paper is the LAE number
+density information at $z=3.1$ obtained by the panoramic narrow-band
+survey presented by \cite{Yamada2012} from a survey 
+%Our observational reference are the recently published results of a
+%panoramic survey of LAES at $z=3.1$ by \cite{Yamada2012}. 
+%This survey
+conducted with the Subaru 8.2m telescope and the Subaru Prime
 Focus Camera, which has a field of view covering $34\times 27$ arcmin,
@@
 $41$ Mpc $h^{-1}$ comoving scale for the detection of the
-Lyman-$\alpha$ line centered at $z=3.09$.
-
-The choice to have only one the data from Yamada et al 2012 as
-reference was  made because their surveys is the largest in area with
-a set of homogenous conditions that define the LAE sample. Other
-surveys by XXX an XXX that cover similar regions, but they use
-different criteria on the equivalent width (EW) cuts to construct the
-LAE samples. Different cuts in the EW can change the number of LAEs to
-be included in the catalog. This cuts have an impact on the fainter
-LAEs which are more abundante than brighter ones. Different
-definitions of the EW cuts can yield number densities different by a
-factor of two [REF, I think Yamada has some numbers].
+Lyman-$\alpha$ line centered at $z=3.09$. The authors report a total of
+$2161$ LAEs with an observed equivalent width larger than $190$\AA
+over a total survey area of $2.42$ deg$^{2}$, this corresponds to an
+averaga surface number density of $0.20\pm 0.01$ arcmin$^{-2}$.
 
@@
 and the fild arotund the Great Observatory Optical Deep Survey North
-(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs. In Table 1 we summarize
-the values we use in throughout this paper for the each field, covered
-area, measured surface LAE number density and inferred number volume
-density.
+(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs. 
+%In Table 1 we summarize
+%the values we use in throughout this paper for the each field, covered
+%area, measured surface LAE number density and inferred number volume
+%density.
+
+There is abundant observational work done on LAEs at redshift $z=3.1$
+\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
+However, we decide to focus on the data from \cite{Yamada2012} because
+it has the largest covered area with homogeneous intrumentational
+conditions (telescope, narrow band filter), data reduction pipeline
+and conditions to construct the LAE catalog. This ensures that the
+number density variations among fields are due only to
+astrophysical reasons and not different observational conditions or
+criteria to construct the catalogs.
+
+%For instance, having
+%different selection criteria on the equivalent width (EW) can change
+%the number of LAEs included in the catalog, yielding number densities
+%different by a factor of two   
+%different criteria on the equivalent width (EW) cuts to construct the
+%LAE samples. Different cuts in the EW can change the number of LAEs to
+%be included in the catalog. This cuts have an impact on the fainter
+%LAEs which are more abundante than brighter ones. Different
+%definitions of the EW cuts can yield number densities different by a
+%factor of two [REF, I think Yamada has some numbers].
+
+%Other
+%surveys by XXX an XXX that cover similar regions, but they use
+%different criteria on the equivalent width (EW) cuts to construct the
+%LAE samples. Different cuts in the EW can change the number of LAEs to
+%be included in the catalog. This cuts have an impact on the fainter
+%LAEs which are more abundante than brighter ones. Different
+%definitions of the EW cuts can yield number densities different by a
+%factor of two [REF, I think Yamada has some numbers].
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_selected_models.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_selected_models.pdf}
-\end{center} f
-\caption{ mean ACFs   and their correponding standard deviation (error
-  bars)  of some selected models in different mass ranges over the 7
-  subfields  f the SSA22 field (left) and the entire 12 field sample
-  (rigth) using thematch
-  configuration. \label{figure:correlation_match} }  
-  \end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_%selected_models.pdf}
+%\hspace{5mm}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_s%elected_models.pdf}
+%\end{center} f
+%\caption{ mean ACFs   and their correponding standard deviation (error
+%  bars)  of some selected models in different mass ranges over the 7
+%  subfields  f the SSA22 field (left) and the entire 12 field sample
+%  (rigth) using thematch
+%  configuration. \label{figure:correlation_match} }  
+%  \end{figure*}
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
-\end{center} 
-\caption{ mean ACFs   and their correponding standard deviation (error
-  bars)  of some selected models in different mass ranges over the 7
-  subfields of the SSA22 field (left) and the entire 12 field sample
-  (rigth) using the  random
-  configuration. \label{figure:correlation_random} }
-
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
+%\hspace{5mm}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
+%\end{center} 
+%\caption{ mean ACFs   and their correponding standard deviation (error
+%  bars)  of some selected models in different mass ranges over the 7
+%  subfields of the SSA22 field (left) and the entire 12 field sample
+%  (rigth) using the  random
+%  configuration. \label{figure:correlation_random} }   
+%\end{figure*}
 

### 2013-05-27 paper/ms.tex
updated the section on simulation and halo catalog

@@
 
-The Bolshoi simulation was performed in a cubic volume of 250 $h^{-1}$
-Mpc on a side. It includes dark matter distribution is sampled using
-$2048^{3}$ particles, which translates into a particle mass of $m_{\rm
-  p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.  The cosmological
-parameters are consistent with a WMAP5 and WMAP7 data with a matter
-density $\Omega_{\rm m} = 0.27$, cosmological constant
-$\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope
-of the power spectrum $n=0.95$ and normalization of the power spectrum
-$\sigma_{8}=0.82$ [REF].
+The Bolshoi simulation \citep{Bolshoi} we use in this paper was
+performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. It includes
+dark matter distribution is sampled using $2048^{3}$ particles, which
+translates into a particle mass of $m_{\rm   p}=1.35\times 10^{8}$
+$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
+a WMAP5 and WMAP7 data with a  density $\Omega_{\rm m} = 0.27$,
+cosmological  $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
+$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
+power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.
 
@@
 algorithm with a linking lenght of 0.17 times the interparticle
-distance. We have veryfied that the main results we present in this
-paper also hold if instead we use halo catalogs constructed from a the
-Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are
-defined to have an density of 200 times the critical density. The
-minimum halo mass in the models we construct in this \documentname correspond
-to groups of $\sim 75$ particles. The catalogs were obtained from the
-publicly available Multidark database \footnote{{\tt
-    http://www.multidark.org/MultiDark/}}
-\citep{2011arXiv1109.0003R}.
+distance. 
+%We have veryfied that the main results we present in this
+%paper also hold if instead we use halo catalogs constructed from a the
+%Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are
+%defined to have an density of 200 times the critical density. 
+The minimum halo mass in the models we construct in this \documentname
+correspond to groups of $\sim 75$ particles. The catalogs were
+obtained from the publicly available Multidark database \footnote{{\tt
+    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
+We focus our work on halos more massive than $1\times 10^{10}$\hMsun
+that are resolved with at least $70$ particles.
 

### 2013-05-27 paper/ms.tex
updated section on mock catalog construction

@@
 
-\subsection{The Observational Constraints}
+\subsection{Observational Constraints}
 
@@
 
-\subsection{The Simulation and Halo Catalogs}
+\subsection{Simulation and Halo Catalogs}
 
@@
 
-\subsection{Populating Halos with LAEs}
+\subsection{A Model to Populate Halos with LAEs}
 \label{subsec:mocks}
 
-The model that populates halos with LAEs is based on a one-to-one
-correspondence: each halo can only host a single LAE. There are three
-physical parameters in the model: the halo mass range $M_{\rm min}<
+In our model a dark matter halo can only host one or zero LAE. 
+There are three parameters in the model that decide whether a halo can host a
+galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
 M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
-  occ}$ of such halos that effectively host a LAE. In what follows we
-will describe by the letter ${\mathcal M}$ a model defined by these
-three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.
+  occ}$ of such halos that effectively host a LAE. We do not assign a
+luminosity to each each LAE. We are primaraly interested in
+constraining the halo mass range hosting detectable LAEs under the
+conditions defined by \cite{Yamada2012}. In what follows will describe by
+the letter ${\mathcal M}$ a model defined by an specific choice of the
+three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.
 
-We stress that we do not intent to build a model for the luminosity of
-each LAE. Physically speaking we are primarely interested in
-constraining the halo mass above which there are detectable
-LAEs. under the conditions defined by Yamada et al.
+For each model ${\mathcal M}$ we create a set of mock fields from
+disjoint volumes in the simulation. Each volume has the same geometry
+probed by Suprime-CAM and the narrow band filter, namely rectangular
+cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
+the last dinemsion goes in the redshift direction. This corresponds to
+a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
+$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
+simulation.
 
-For each mode ${\mathcal M}$ we create mock field from disjoint
-volumes in the simulation with the same geometry probed by Suprime-CAM
-and the narrow band filter, namely $46\times 35\times 41$
-$h^{-3}$Mpc$^{3}$ where the last dinemsion goes in the redshift
-direction, corresponding to a total area of $880$ arcmin$^{2}$ for
-each mock field. There is a total $5\times 7 \times 6=210$ of such
-sub-volumes in a snapshot of the Bolshoi simulation.
-
-Next we group these $210$ mock fields in three different ways to
-construct the LAEs number density distribution. The first way (match method) we
-follow the observational setup and constructs $15$ different mock
-surveys, each one composed of $12$ mock fields, out of which $7$
-correspond to contiguous sub-boxes in the simulation to mimick the
-whole SSA22, $3$ are also contiguous between them but not to the first
-$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
-fields that correspond to the SDF and GOODS-North fields. This will
-produce $15$ different distributions for the number density for a
-given model ${\mathrm M}$. The second (random method) is similar to the first
-one. There aare $15$ different mock surveys with $12$ mock fields
-each, but this time each field corresponds to uncorrelated sub-boxes
-in the simulation. The third (full method) way in only has $1$ mock survey
-containing all the $210$ mock fields, in this setup there is only one
-predicted number density distribution for each model ${\mathrm M}$
-
-The advantage of these three sampling ways is that they allow us to
-explore the effects of both cosmic variance and the correlation
-between fields. Comparing the results of the first and second method
-will help us to quantify the effect of field correlation, while
-compating the first and the third method will serve us to gauge the
-impace of cosmic variance.
+Next we construct mock surveys by making groups of $11$ mock fields
+out of the $210$ available volumes. In total $15$ mock surveys are
+constructed for each model $\mathcal{M}$.
+%mock fields into
+%sets of $11$ different ways to
+%construct the LAEs. The first way (match method) we
+The grouping is done in two different ways. In the first way, called
+{\texttt match}, we follow
+the clustering of the observed fields. From the $11$ mock fields, $7$
+are constructed from contigous fields in the simulation to mimic the
+SSA22 region, $3$ are also contiguous between them but not to the first
+$7$ fields to mimic the SXDS fields and finally $2$ non-contigous
+fields to imitate the SDF and GOODS-North field. Our main goal with
+this selection is to test the impact on the final statistics of having
+$7$ clustered fields. The second way to group the mock fields is called {\texttt
+  random}, whereby all the $11$ fields are selected in such a way as
+to avoid that any two volumes are contigous.
+%follow the observational setup and constructs $15$ different mock
+%surveys, each one composed of $12$ mock fields, out of which $7$
+%correspond to contiguous sub-boxes in the simulation to mimick the
+%whole SSA22, $3$ are also contiguous between them but not to the first
+%$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
+%fields that correspond to the SDF and GOODS-North fields. This will
+%produce $15$ different distributions for the number density for a
+%given model ${\mathrm M}$. The second (random method) is similar to the first
+%one. There aare $15$ different mock surveys with $12$ mock fields
+%each, but this time each field corresponds to uncorrelated sub-boxes
+%in the simulation. The third (full method) way in only has $1$ mock survey
+%containing all the $210$ mock fields, in this setup there is only one
+%predicted number density distribution for each model ${\mathrm M}$ 
+%We create the mock surveys in two different ways. First we follow 
+%The advantage of these three sampling ways is that they allow us to
+%explore the effects of both cosmic variance and the correlation
+%between fields. Comparing the results of the first and second method
+%will help us to quantify the effect of field correlation, while
+%compating the first and the third method will serve us to gauge the
+%impace of cosmic variance.
 

### 2013-05-27 paper/ms.tex
finished whole Methodology section

@@
 galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
-M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
+M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
   occ}$ of such halos that effectively host a LAE. We do not assign a
@@
 $5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
-simulation.
+simulation. In each mock field a LAE is assigned to the position of a
+dark matter halo if the halo mass is in the range allowed by the model
+$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
+an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
+fraction $\xi<f_{\rm occ}$.
 
@@
 
-\subsection{Model Sampling and Selection}
+\subsection{Sampling and Selecting Models}
 
-We generate a series of models ${\mathcal M}$ with different input
-parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as
-follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30
-different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from
-$\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while
-$M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to
-$\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$
-takes 100 different values from $0.01$ to $1.00$ regularly spaced by
-$0.01$. In total the number of different sets of input parameters to
-be explored is $30 \times 30\times 100 = 9\times 10^{4}$.
+We make a thorough exploration of the parameter space for the models
+${\mathcal M}$. $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
+to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
+takes values in the same range as $\log_{10}M_{\rm min}$ only with a
+displacement of $0.1$ dex in the whole range. The occupation fraction
+$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regulary
+spaced by $0.1$. In total the number of different models ${\mathcal
+  M}$ that are explored is $30 \times 30 \times 10 = 9000$.
 
-For each model ${\mathcal M}$ we compute the LAE surface density
-distributions for the three different ways of grouping the mock
-fields, as described in the previous section. For each sub-volume we
-project the positions of the LAE hosting halos along the $z$ direction
-and calculate its surface number density in units of sources per
-arcmin$^{2}$. For each number density distribution we perform a
-Kolmogorov-Smirnov against the $12$ surface density observational
-values. From this test we obtain the value $0<P<1$ to reject the null
-hypothesis, namely that the two data sets come from the same
-distribution. In this paper we use values of $P>0.1$ to consider that
-the simulated and observed number densities come from the same
+For each mock survey generated in a given model ${\mathcal M}$ we
+compute the surface density in the $12$ mock fields. We perform a
+Kolmogorov-Smirnov (KS) to compare this mock date against the $12$
+observational values. From this test we obtain a value $0<P<1$ to
+reject the null hypotesis, namely that two data sets come from the
+same distribution. In this paper we consider that for values $P>0.05$
+the two distributions can be thought as coming from the same
 distribution.
+
+In this paper we consider that a model
+${\mathcal M}$ that has at least one (1) mock survey (out of 15)
+consistent with the observed distribution of LAE number densities has
+viable parameters thatdeserve to be considered for further analysis.
+
+%For each mock survey generated in a given model ${\mathcal M}$ we compute the LAE surface density
+%distributions for the three different ways of grouping the mock
+%fields, as described in the previous section. For each sub-volume we
+%project the positions of the LAE hosting halos along the $z$ direction
+%and calculate its surface number density in units of sources per
+%arcmin$^{2}$. For each number density distribution we perform a
+%Kolmogorov-Smirnov against the $12$ surface density observational
+%values. From this test we obtain the value $0<P<1$ to reject the null
+%hypothesis, namely that the two data sets come from the same
+%distribution. In this paper we use values of $P>0.1$ to consider that
+%the simulated and observed number densities come from the same
+%distribution.
+
+%We generate a series of models ${\mathcal M}$ with different input
+%parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as
+%follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30
+%different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from
+%$\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while
+%$M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to
+%$\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$
+%takes 100 different values from $0.01$ to $1.00$ regularly spaced by
+%$0.01$. In total the number of different sets of input parameters to
+%be explored is $30 \times 30\times 100 = 9\times 10^{4}$.
 
@@
 \begin{center}
-\includegraphics[width=1.00\linewidth,angle=0]{./plots/Fig1.pdf}
-\caption{ \label{figure:laes_dist} Cumulative mass function of dark
-  matter haloes in the $210$ sub-volumes of $46\times 35\times 41$
-  $h^{-3}Mpc^{3}$. The variation in the total number of dark matter
-  halos per sub-volume  evidences the effect of cosmic variance at
-  such sub-volume scale. It is also appreciable the low population
-  $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with
-  $log(M/M_{\odot})>12.0$}. 
+\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
+\caption{ \label{figure:laes_dist} Surface density of dark
+  matter halos as a function of a minimum halo mass to count the
+  total number of elements in a volume. Each line represents on of the
+  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
+  in the Bolshoi simulation. The horizontal grey band represents the
+  range of surface densities observed for LAEs at $z=3.1$ as reported
+  by \citep{Yamada2012}.}
 \end{center} 
@@
 
-\subsection{Additional Constraints}
+\section{Additional Constraints}
 

### 2013-05-27 paper/ms.tex
in the middle of the Results section

@@
 
-\section{Results}
+\section{Basic Results}
 
@@
 \includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
-\caption{ \label{figure:laes_dist} Surface density of dark
+\caption{ \label{fig:laes_dist} Surface density of dark
   matter halos as a function of a minimum halo mass to count the
@@
 \subsection{Dark Matter Halo Number Density}
+
 In Figure \ref{fig:laes_dist} we present the results for  the
-integrated dark matter halo surface density as a function of halos
+integrated dark matter halo surface density as a function of halo
 mass. Each line corresponds to one of the 210 sub-volumes in the
-Bolshoi simulation. The shadowed area indicates the surface density
-values for LAEs allowed by the observations.
+Bolshoi simulation. The gray band indicates the surface density
+values for LAEs allowed reported in observations \citep{Yamada2012}.
 
-This result allows us to better understand the expected trends for the
-LAEs' preferred mass and the occupation fraction.  From this Figure we
-can read which models do not have achance reproduce the
-observations. Regions in the plot where the halo surface density
-values are below the observational constraint correspond to high
-masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
-$M_{\rm   min}> 3 \times 10^{11}$\hMsun located inthat mass range, the
-surface density is too low compared with observations.
+This result provides the basis to understand why a range of models
+${\mathcal M}$ can be expected to be consistent with
+observations. In Figure \ref{fig:laes_dist} we can read that models
+with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
+surface number density lower than the observational
+constrain. The oppossite is true in models with $\log_{10} M_{\rm min}<10.5$
+that will show surface number density larger than observations, this
+implies that in such models the occupation fraction has to be tuned
+$f_{\rm occ}<1.0$ as to lower the halo numeber density to match the
+gray band values.
+
+%This basic result provides the basis to understand the range of models
+%${\mathcal M}$ expected trends for the
+%LAEs' preferred mass and the occupation fraction.  
+%From this Figure we
+%can read which models do not have achance reproduce the
+%observations. Regions in the plot where the halo surface density
+%values are below the observational constraint correspond to high
+%masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
+%$M_{\rm   min}> 3 \times 10^{11}$\hMsun located inthat mass range, the
+%surface density is too low compared with observations.
 
@@
 
-\subsection{Kolmogorov-Smirnov Tests}
+In the next subsection we quantify this intuition by means of the KS
+tests between mock surveys and observations.
+
+\subsection{Three Regions in Parameter Space}
 
@@
 \end{center} 
-\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
-  $P>0.05$ in the three different of grouping the mock fields. In the
-  case of the {\tt match} and {\tt random} methods the  color code
-  corresponds to the number of mock surveys that are found to
-  be compatible with observations. For the {\tt full} method the
-  colour code corresponds to the results of $100$ times the maximum $P$ value
-  resulting from the KS test. \label{figure:landscape}.}  
+\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
+    min}-f_{\rm occ}$ (right) planes for all models with
+  $P>0.05$ in two different ways used to construct the mock
+  surveys. The color code corresponds to the number of mock surveys
+  that are found to be compatible with observations in terms of the KS
+  test with $P>0.05$. Only regions of parameter space with at least
+  one (1) consistent mock survey are included. \label{fig:landscape}}   
 \end{figure*}
 
-Figure \label{figure:landscape} presents the regions in the parameter
-space $M_{\rm min}$-$M_{\rm max}$ where the KS test yields values of
-$P>0.05$. We consider that for those models it is not possible to rule out the null
-hypothesis, namely that the number density in simulated data and the observations come
-from the same parent distribution. Each panel corresponds to the three different ways of
-grouping the mock fields. In the case of the methods {\tt{Match}}
-and {\tt{Random}} the color code indicates the fraction of these 15
-mock surveys with with $P>0.1$. The third panel shows the result for
-the method {\tt{Full}}, in this case the color code correspond
-to the value maximum value of $100\times P$ for a model with those
-mass ranges.
+Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
+min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
+values of $P>0.05$ at least for one mock survey. For those models it
+is not possible reject the hypothesis that the simulated and observed
+data for the surface number density come from the same parent
+distribution.
 
-These results clearly distinguish three mass regimes. In the first regime, at
-high mass values, we find that LAE models with minimum mass of $M_{\rm
-  min}>10^{11.5}$\hMsun are not compatible with observations. There is
-a second regime for masses below $M_{\rm
-  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
-can be made compatible with observations, provided that
-$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
-for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
-limited range of models with $M_{\rm max}$ with occupation fraction
-$f_{\rm occ}\sim 1$ is able to reproduce observations.
+The upper (lower) panels correspond to the {\texttt match} ({\texttt
+  random}) method to build the mock surveys from individual
+fields. The color code shows the number of mock surveys consistent
+with observations. In both cases there are three regions of parameter
+space that can be clearly distinguised.
 
-In these three different mass regimes the occupation monotonically
-decreases as a function of the minimum halo mass $M_{\rm min}$. In
-Figure XXX we show this treend in three panels following the same
-correspondence as Figure XXX. From these results we interpret that the
-different mass regimes that were identified correspond to best fit
-models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm
-  occ}\sim 0$, respectively.
+The first region corresponds to models where the minimum mass is high
+$\log_{10}M_{\rm min}> 11.5$. None of this models is compatible with
+observations as expected from the results in the previous section. For
+these models the number density of LAEs is too low.
 
-The two {\tt match} and {\tt random} methods present the highest
-number of matching mock surveys in the medium mass regime. However, it
-is important to keep in mind that not all the mock surveys for a
-sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
-modest fraction seems to be consistent with observations. This shows that the
-cosmic variance is still present on the physical scales probed by
-observations. This will be considered in more detail in the discussion
-seccion.
+The second region corresponds to an intermediate range for the minimum
+mass $10.5<\log_{10}M_{\rm min}<11.5$ where regardless of the value of
+the maximum mass $M_{\rm max}$ it is possible to tune the occupation
+fraction $f_{\rm occ}$ to bring some of the mock observations into
+good agreement with observations. In this region in parameter space
+one can thus find two extreme kinds of models.  One kind where the
+mass interval is very narrow with sizes smaller than $<0.3$ dex (a
+factor of two in mass) and others where the mass interval is very
+extended, larger than $1.0$ dex, going up to the maximum halo mass
+present in the simulation at that redshift.
 
-To illustrate this point, in Figure \ref{fig:mocks} we present the
-results for two mock fields for the {\tt{Match}} method for a model
-with the same parameters, but two extreme values for the KS test.
+The third region in parameter space corresponds to $\log_{10}M_{\rm
+  min}<10.5$. In this case only models with a narrow mass interval of
+at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
+occupation fractions $f_{\rm occ}<0.3$ are allowed.
 
-Conversely there are different models where the KS test yield values of
-$P\sim 1$. To illustrate the kind of success represented by these
-models, we have selected these best ones in the case of the method
-{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
-distribution of the mock surveys, the smaller panel shows the
-corresponding surface density distribution and the observational
-constraint.
+%Figure \label{figure:landscape} presents the regions in the parameter
+%space $M_{\rm min}$-$M_{\rm max}$ where the KS test yields values of
+%$P>0.05$. We consider that for those models it is not possible to rule out the null
+%hypothesis, namely that the number density in simulated data and the observations come
+%from the same parent distribution. Each panel corresponds to the three different ways of
+%grouping the mock fields. In the case of the methods {\tt{Match}}
+%and {\tt{Random}} the color code indicates the fraction of these 15
+%mock surveys with with $P>0.1$. The third panel shows the result for
+%the method {\tt{Full}}, in this case the color code correspond
+%to the value maximum value of $100\times P$ for a model with those
+%mass ranges.
 
-In what follows we will focus our discussion on the mocks constructed
-with the {\tt{Match}} and {\tt{Random}} methods.
+%These results clearly distinguish three mass regimes. In the first regime, at
+%high mass values, we find that LAE models with minimum mass of $M_{\rm
+%  min}>10^{11.5}$\hMsun are not compatible with observations. There is
+%a second regime for masses below $M_{\rm
+%  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
+%can be made compatible with observations, provided that
+%$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
+%for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
+%limited range of models with $M_{\rm max}$ with occupation fraction
+%$f_{\rm occ}\sim 1$ is able to reproduce observations.
+
+%In these three different mass regimes the occupation monotonically
+%decreases as a function of the minimum halo mass $M_{\rm min}$. In
+%Figure XXX we show this treend in three panels following the same
+%correspondence as Figure XXX. From these results we interpret that the
+%different mass regimes that were identified correspond to best fit
+%models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm
+%  occ}\sim 0$, respectively.
+
+%The two {\tt match} and {\tt random} methods present the highest
+%number of matching mock surveys in the medium mass regime. However, it
+%is important to keep in mind that not all the mock surveys for a
+%sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
+%modest fraction seems to be consistent with observations. This shows that the
+%cosmic variance is still present on the physical scales probed by
+%observations. This will be considered in more detail in the discussion
+%seccion.
+
+%To illustrate this point, in Figure \ref{fig:mocks} we present the
+%results for two mock fields for the {\tt{Match}} method for a model
+%with the same parameters, but two extreme values for the KS test.
+
+%Conversely there are different models where the KS test yield values of
+%$P\sim 1$. To illustrate the kind of success represented by these
+%models, we have selected these best ones in the case of the method
+%{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
+%distribution of the mock surveys, the smaller panel shows the
+%corresponding surface density distribution and the observational
+%constraint.
+
+%In what follows we will focus our discussion on the mocks constructed
+%with the {\tt{Match}} and {\tt{Random}} methods.
 
@@
 
+... Discuss all this in terms of the star formation efficiency in
+Behroozi et al.
+
 \subsection{Implications for large LAEs surveys}

### 2013-05-28 paper/ms.tex
almost done with section 4

@@
 \includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
-\caption{ \label{fig:laes_dist} Surface density of dark
+\caption{ \label{fig:halos} Surface density of dark
   matter halos as a function of a minimum halo mass to count the
@@
 
-In Figure \ref{fig:laes_dist} we present the results for  the
+In Figure \ref{fig:halos} we present the results for  the
 integrated dark matter halo surface density as a function of halo
@@
 ${\mathcal M}$ can be expected to be consistent with
-observations. In Figure \ref{fig:laes_dist} we can read that models
+observations. In Figure \ref{fig:halos} we can read that models
 with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
@@
   random}) method to build the mock surveys from individual
-fields. The color code shows the number of mock surveys consistent
-with observations. In both cases there are three regions of parameter
-space that can be clearly distinguised.
+fields. The plot shows number of mock surveys consistent
+with observations. There are between $550$ to $600$ models out of the
+original $9000$ models that have at least one (1) mock survey
+consistent with observations.
 
-The first region corresponds to models where the minimum mass is high
-$\log_{10}M_{\rm min}> 11.5$. None of this models is compatible with
-observations as expected from the results in the previous section. For
-these models the number density of LAEs is too low.
+In Figure \ref{fig:landscale} there are three regions of parameter
+space that can be clearly distinguised. The first region corresponds
+to models where the minimum mass is high $\log_{10}M_{\rm min}>
+11.5$. None of this models is compatible with observations as expected
+from the results in the previous section. For these models the number
+density of LAEs is too low.
 
@@
 occupation fractions $f_{\rm occ}<0.3$ are allowed.
+
+Without any additional information our method allows us to infer that
+most of the succesful models are found in the second and third region of
+parameter space where. This result was already expected from halo
+abundance calculations shown in Figure \ref{fig:halos}. In the next
+section we reduce the size of this region by using more stringent
+constraints to define the agreement with observations and including
+additional observational information onpossible values for the
+occupation fraction at $z\sim 3$.
+
+%The raw results of our experiments yield a prefered range for
+%halo masses hosting LAES bounded by a minimum mass $10.5<\log_{10}M_{\rm
+%  min}<11.5$ and without any limitation on the  maximum
+%mass. In this regime the average occupation fraction tends to increase
+%with $M_{\rm min}$. These results discard models that were
+%nevertheless disfavored from the very beginning based on the results
+%of the mass functions (see Figure 1.).
 
@@
   realizations that are consistent with observations.
-  \label{figure:high_success_rate}.}  
+  \label{fig:high_success_rate}.}  
 \end{figure*}
 
-The raw results of our experiments yield a prefered range for
-halo masses hosting LAES bounded by a minimum mass $10^{10}\hMsun<M_{\rm
-  min}<10^{11.5}\hMsun$ and without any limitation on the  maximum
-mass. In this regime the average occupation fraction varies with an
-approximate dependence of the kind $f_{occ}\approx 0.1 (M_{\rm
-  min}/10^{10})^{XX}$. These results discard models that were
-nevertheless disfavored from the very beginning based on the results
-of the mass functions (see Figure 1.).
+In this section we consider two additional constraints on the models
+we accept as succesul. First by taking models with the
+highest possible number of mock surveys consistent with
+observations. Second by including additional observational constraints
+on the occupation fraction for high redshift LAEs.
 
-In this section we consider three different ways to impose
-tighter constraints on this mass range by making use of the results we
-have derived so far together with additional statistical and
-astrophysical constraints. In the first constraint we select the
-models where all the mock surveys present KS-test values consistent
-with observations. The second constraints uses recent observational
-results on the average occupation fraction for LAEs at high-z. The
-third exploits the information in the Angular Correlation Function
-(ACF).
+%In this section we consider three different ways to impose
+%tighter constraints on this mass range by making use of the results we
+%have derived so far together with additional statistical and
+%astrophysical constraints. In the first constraint we select the
+%models where all the mock surveys present KS-test values consistent
+%with observations. The second constraints uses recent observational
+%results on the average occupation fraction for LAEs at high-z. The
+%third exploits the information in the Angular Correlation Function
+%(ACF).
 
-\subsubsection{Models with the highest success rates}
+\subsection{Models with the highest success rates}
 
-For each model there are 15 different mock survey realizations. In the
+For each model ${\mathcal M}$there are 15 different mock surveys. In the
 previous section we presented the models that had at least one (1)
-mock survey realization with $P>0.05$.
+mock survey with $P>0.05$.
 
-In Figure \ref{figure:high_success_rate} we show the number of models
-that have at least $n$ realizations with $P>0.05$ for the {\texttt
+Figure \ref{fig:high_success_rate} shows the number of models
+that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for the {\texttt
   match} and {\texttt random} methods.  This shows that there are
-around $550$ to $600$ different models that have at leaset one mock
-survey realization consistent with observations. At the other extreme,
-there are $80$ to $100$ models with all the 15 realizations with
-$P>0.05$. Here we focuse on the latter models. The best models
-represent $\sim 15\%$ of the number of initially considered good
-models.
+here are between $80$ to $100$ models with all the 15 realizations with
+$P>0.05$. This a reduction of a factor of $\sim 6$ with repect to the
+total number of mocks with at least one consistent mock. 
+%Here we focuse on the latter models. 
+%The best models
+%represent $\sim 15\%$ of the number of initially considered good
+%models.
 
-In Figure XX we present the locii of these models in the parameter
-space $M_{\rm min}-M_{\rm max}$ and $M_{\rm min}-f_{\rm occ}$. In
-Figure XX we show the spatial distribution for two mock surveys
-corresponding to one of such models.
+Figure \ref{fig:restriction_mock} presents the locii of these models
+in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
+  min}-f_{\rm occ}$ for the {\texttt match} method, the results for
+the {\texttt random} method are similar. In this case the models with
+$\log_{10}M_{\rm min}< 11.7$ are greatly reduced. This corresponds to
+the regions in the parameter space in Figure \ref{fig:landscape} that
+already had a low number of consistent mock surveys. From the right
+panel in Figure \ref{fig:restriction_mock} one can see that there is
+not a strong selection effect on the occupation fraction $f_{\rm
+  occ}$.
 
-\subsubsection{Observational constraints on the occupation fraction}
+\subsection{Observational constraints on the occupation fraction}
 
-We now impose a different restriction using the observational results
+We impose a different restriction using the observational results
 by \cite{Hayes2010}. These authors constrained the value of $f_{\rm
   occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
-on blind surveys of the H$\alpha$ and Lyman alpha line with the European Southern
+on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
 Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
@@
 almost $90\%$ of the star forming galaxies emit insufficient
-Lyman-alpha to be detected, effectively setting the occupation
+Lyman $\alpha$ to be detected, effectively setting the occupation
 fraction to be $f_{\rm occ}=0.10$.
@@
 fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$
-remain constant over that time scale. This assumption allows us to
-further pick models that have an occupation fraction of $f_{\rm
-  occ}=0.10$. Under this selection only $18$ models can
-beselected. Considering an occupation fraction $f_{\rm occ}=0.20$
-another $39$ models can beconsidered. This constraint help us to
-select $\sim 10\%$ of theoriginal models that were considered as
-consistent with observations in the previous section.
+remain constant over that time scale. We limits the escape fraction to
+be in the range further pick models that have an occupation fraction of $f_{\rm
+  occ}\leq 0.2$ to allow for some flexibility. With this additional
+constraint between $35$ to $40$ models are consistent with
+observations. 
+%Considering an occupation fraction $f_{\rm occ}=0.20$
+%another $39$This constraint help us to
+%select $\sim 10\%$ of theoriginal models that were considered as
+%consistent with observations in the previous section.
 
-Figure XX shows the prefered models in the planes $M_{\rm min}-M_{\rm
-  max}$ and $M_{\rm min}-f_{\rm occ}$ for the {\tt match} and {\tt
-  random} methods. The list for the model parameters is found in the
-appendix in Table XX.
+Figure  \ref{fig:restriction_mock_and_f_occ}   shows the prefered
+models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
+  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random}
+methods. The list for the parameters in these models is found in the appendix in
+Table XX.
 
-In terms of the constraints done in the previous sub-section, we find
-that the models in this region of parameter space have an average
-number of XX mock catalogs consistent with observations.
+%In terms of the constraints done in the previous sub-section, we find
+%that the models in this region of parameter space have an average
+%number of XX mock catalogs consistent with observations.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
+\end{center} 
+\caption{Favored regions in parameter space when the constraints on
+  the maximal number of consistent mocks is imposed. The results for
+  the {\texttt random} methodology area very similar to the ones
+  presented here for the {\texttt match} method.
+  \label{fig:restriction_mock}}  
+\end{figure*}
 
@@
   fraction are included.
-  \label{figure:mock_and_f_occ}}  
+  \label{fig:restriction_mock_and_f_occ}}  
 \end{figure*}
 
-\subsubsection{Constraints from the Angular Correlation Function}
+\section{Results for the Angular Correlation Function}
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
-\end{center} 
-\caption{Spatial distribution for two mocks corresponding to the model
-  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
-  different mock  surveys for this model in the {\texttt match}
-  configuration are consistent with observations at the $P>0.05$
-  level. The full data for all the mocks can be found in the github
-  repository for this paper.
-  \label{figure:spatial_distro}.}
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
+%\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
+%\end{center} 
+%\caption{Spatial distribution for two mocks corresponding to the model
+%  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
+%  different mock  surveys for this model in the {\texttt match}
+%  configuration are consistent with observations at the $P>0.05$
+%  level. The full data for all the mocks can be found in the github
+%  repository for this paper.
+%  \label{figure:spatial_distro}.}
+%\end{figure*}
 

### 2013-05-28 paper/ms.tex
finished section 4

@@
 
-\subsection{Observational constraints on the occupation fraction}
-
-We impose a different restriction using the observational results
-by \cite{Hayes2010}. These authors constrained the value of $f_{\rm
+\subsection{Additional  Constraints on the Occupation Fraction}
+
+We impose an additional restriction using the observational results
+by \cite{Hayes2010}. They constrained the value of $f_{\rm
   occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
@@
 the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)$ if a different dust correction is used. The
+esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
 authors show that the luminosity function for LAEs at $z=2.2$ is
@@
 Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$.
-
-For the cosmological parameters used in this \documentname the age of
-the universe between $z=3.1$ and $z=2.2$ has changed by $\sim 1$
-Gyr. We assume that the physical conditions that determine the escape
-fraction $f_{\rm esc}$ and the occupation fraction $f_{\rm  occ}$
-remain constant over that time scale. We limits the escape fraction to
-be in the range further pick models that have an occupation fraction of $f_{\rm
-  occ}\leq 0.2$ to allow for some flexibility. With this additional
-constraint between $35$ to $40$ models are consistent with
-observations. 
+fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
+used in this \documentname the age of the universe between $z=3.1$ and
+$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
+conditions that determine the escape fraction $f_{\rm esc}$ and the
+occupation fraction $f_{\rm  occ}$ remain similar over that time
+scale.
+
+We limit the occupation fraction to
+be in the range 
+%further pick models that have an occupation fract
+$f_{\rm
+  occ}\leq 0.2$ to allow for some flexibility on the time evolution
+and the uncertainty in the dust correction used to infer the escape fraction. 
 %Considering an occupation fraction $f_{\rm occ}=0.20$
@@
 %consistent with observations in the previous section. 
-
 Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
-  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random}
-methods. The list for the parameters in these models is found in the appendix in
-Table XX.
+  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
+With this additional constraint between $35$ to $40$ models are
+consistent with observations, this represents a factor of $\sim 2$
+reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
+excluded and the best models are now clustered around a narrow region
+in parameter space. The list for the model parameters is in the
+Appendix in Table \ref{table:models_match}.
 
@@
   the maximal number of consistent mocks is imposed. The results for
-  the {\texttt random} methodology area very similar to the ones
+  the {\texttt random} methodology (not shown here) are very similar to the ones
   presented here for the {\texttt match} method.
@@
 \end{center} 
-\caption{Favored models when the constraints on the maximal number of
-  consistent mocks and the observational constrain on the occupation
-  fraction are included.
-  \label{fig:restriction_mock_and_f_occ}}  
+\caption{Best models when both the constraints on the maximal number
+  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
+  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
 \end{figure*}
@@
 \begin{tabular}{ccc}\hline\hline
-10.1 & 10.2 & 0.1\\
-10.3 & 10.5 & 0.1\\
-10.4 & 10.7 & 0.1\\
-10.5 & 10.9 & 0.1\\
-10.6 & 11.2 & 0.1\\
-10.6 & 11.3 & 0.1\\
-10.6 & 11.4 & 0.1\\
-10.1 & 10.2 & 0.1\\
-10.3 & 10.5 & 0.1\\
-10.4 & 10.7 & 0.1\\
-10.5 & 10.9 & 0.1\\
-10.5 & 11.0 & 0.1\\
-10.6 & 11.2 & 0.1\\
-10.6 & 11.3 & 0.1\\
-10.6 & 11.4 & 0.1\\
-10.6 & 11.5 & 0.1\\
-10.6 & 11.6 & 0.1\\
-10.6 & 11.7 & 0.1\\\hline\hline
-
-10.4 & 10.5 & 0.2\\
-10.6 & 10.8 & 0.2\\
-10.7 & 11.0 & 0.2\\
-10.8 & 11.2 & 0.2\\
-10.8 & 11.3 & 0.2\\
-10.9 & 11.6 & 0.2\\
-10.9 & 11.7 & 0.2\\
-10.9 & 11.8 & 0.2\\
-10.9 & 11.9 & 0.2\\
-10.9 & 12.0 & 0.2\\
-10.9 & 12.1 & 0.2\\
-10.9 & 12.2 & 0.2\\
-10.9 & 12.3 & 0.2\\
-10.9 & 12.4 & 0.2\\
-10.9 & 12.5 & 0.2\\
-10.9 & 12.6 & 0.2\\
-10.9 & 12.7 & 0.2\\
-10.9 & 12.8 & 0.2\\
-10.9 & 12.9 & 0.2\\
-10.9 & 13.0 & 0.2\\
-10.6 & 10.8 & 0.2\\
-10.7 & 11.0 & 0.2\\
-10.8 & 11.2 & 0.2\\
-10.8 & 11.3 & 0.2\\
-10.8 & 11.4 & 0.2\\
-10.9 & 11.7 & 0.2\\
-10.9 & 11.8 & 0.2\\
-10.9 & 11.9 & 0.2\\
-10.9 & 12.0 & 0.2\\
-10.9 & 12.1 & 0.2\\
-10.9 & 12.2 & 0.2\\
-10.9 & 12.3 & 0.2\\
-10.9 & 12.4 & 0.2\\
-10.9 & 12.5 & 0.2\\
-10.9 & 12.6 & 0.2\\
-10.9 & 12.7 & 0.2\\
-10.9 & 12.8 & 0.2\\
-10.9 & 12.9 & 0.2\\
-10.9 & 13.0 & 0.2\\\hline\hline
+$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
+10.1& 10.2& 0.1\\
+10.3& 10.5& 0.1\\
+10.4& 10.7& 0.1\\
+10.5& 10.9& 0.1\\
+10.5& 11.0& 0.1\\
+10.6& 11.2& 0.1\\
+10.6& 11.3& 0.1\\
+10.6& 11.4& 0.1\\
+10.6& 11.5& 0.1\\
+10.6& 11.6& 0.1\\
+10.6& 11.7& 0.1\\
+10.6& 10.8& 0.2\\
+10.7& 11.0& 0.2\\
+10.8& 11.2& 0.2\\
+10.8& 11.3& 0.2\\
+10.8& 11.4& 0.2\\
+10.9& 11.7& 0.2\\
+10.9& 11.8& 0.2\\
+10.9& 11.9& 0.2\\
+10.9& 12.0& 0.2\\
+10.9& 12.1& 0.2\\
+10.9& 12.2& 0.2\\
+10.9& 12.3& 0.2\\
+10.9& 12.4& 0.2\\
+10.9& 12.5& 0.2\\
+10.9& 12.6& 0.2\\
+10.9& 12.7& 0.2\\
+10.9& 12.8& 0.2\\
+10.9& 12.9& 0.2\\
+10.9& 13.0& 0.2\\\hline\hline
 \end{tabular}
 \end{center}
+\caption{List of model parameters for the best models that have all
+  mock surveys consistent with observations and an occupation
+  fraction $f_{\rm occ}\leq 0.2$. This corresponds to the {\texttt
+    match} method to construct the mock surveys. \label{table:models_match}. }
 \end{table}

### 2013-05-28 paper/ms.tex
working on the correlation function section

@@
 
-We calculate the mean angular correlation function (ACF) only for the
-models that showed that all of the 15 mock surveys are consistent
-at the $P>0.05$ level with observations. The ACF is computed only the
-denseset subfield in all the 15 mock surveys corresponding to the
-SSA22 region. These results are compared against the observations
-reported by Hayashino et al in 2004 over the same region, which were
-also performed on the densest field.
+we calculate the angular correlation function
+(ACF) for all the models having the $15$ mock surveys consistent with
+observations. We perform this calculation as a sanity check and
+potential additional constraint. The ACF is computed only the densest
+subfield in all the 15 mock surveys corresponding to the SSA22
+region. These results are compared against the observations reported
+by \citep{Hayashino2004} which were also performed on the densest
+field of SSA22.
+
+It is important to keep in mind that there are some differences
+between this work and \citep{Yamada2012}. The color selection by
+\cite{Yamada2012} is less stringent compared to the one by
+\cite{Hayashino2004}. Also the EW threshold is different,
+\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
+used by \citep{Yamada2012}
+
+The comparison between the simulated and observed ACFs is also done using a
+$\chi^2$ statistic which includes the information on the measurement
+uncertainties and the statistical dispersio from the $15$ mock surveys
+in the simulation
+
+\begin{equation}
+\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
+    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
+    sim}^2({\theta_i})}, 
+\end{equation}
+
+where the sum is done over all the $13$ angle values $\theta_i$ where the
+ACF has been computed. In Figure XX we plot this statistic for all the
+models considered. In all cases $\chi^{2}<7$ which is not sufficient
+to consider that the correlation functions from the simulations are
+statistically different from the observational one. The constribution
+of cosmic variance in the simulations together with the statistical
+uncertainties make all tested models compatible with the observational
+constraints.
+
+%From these tests we conclude that the ACF on small fields does not
+%provide additional constraints to further select models for halos
+%hosting LAEs. The reason is that
+
+We also present the ACF in the case of the full SSA22
+region which has been homogeneously observed by \citep{Yamada2012}. To
+this date the observational ACF has not been reported in the
+litereature, therefore our calculations can be considered as
+predictions.
+
+In Figure X we present the results for the models. The full list of
+these correlation functions can be found in the the data repository
+for this paper in \verb"github".
+
+%Given that the ACF reported by Hayashino et al en 2004 is taken over
+%the densest  field oserved in the SSA22 region by  Yamada et el in
+%2012 it is expected that the predicted ACF in the SSA22 region should
+%reproduce this observation. In the  left panel of figure
+%\ref{figure:correlation_match} we can see the predicted ACFs  an their
+%corresponding standard deviation over the seven fields that mock the
+%SSA22  region. It can be seen that the model with $M_min=10.6$ seems
+%to better reproduce the  Hayashino's ACF and that the corresponding
+%field is in fact an overdense field in the SSA22 region covered by
+%Yamada et al.
+
+We also present the results for the angular correlation function in
+therms of the correlation lenght obtained by fitting the following
+function
+\begin{equation}
+\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
+\end{equation}
+
+The results are shown in Figure in a $r_{0}-\gamma$ plane where the
+average and standard deviation for each mock are shown in comparison
+with the result derived from observations.
+
+%We calculate the mean angular correlation function (ACF) only for the
+%models that showed that all of the 15 mock surveys are consistent
+%at the $P>0.05$ level with observations.
 
@@
 \ref{figure:laes_dist}, as a direct consequence of cosmic variance.
-
-The comparison between the simulated and observed ACFs is also done using a
-$R^2$ statistic which includes the information on measurement uncertainties
-
-\begin{equation}
-R^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
-    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
-    sim}^2({\theta_i})}, 
-\end{equation}
-
-where the sum is done over all the angle values $\theta_i$ where the
-ACF has been computed. In Figure XX we plot the integrated
-distributions for this $R^{2}$ statistics
-
-Given that the ACF reported by Hayashino et al en 2004 is taken over
-the densest  field oserved in the SSA22 region by  Yamada et el in
-2012 it is expected that the predicted ACF in the SSA22 region should
-reproduce this observation. In the  left panel of figure
-\ref{figure:correlation_match} we can see the predicted ACFs  an their
-corresponding standard deviation over the seven fields that mock the
-SSA22  region. It can be seen that the model with $M_min=10.6$ seems
-to better reproduce the  Hayashino's ACF and that the corresponding
-field is in fact an overdense field in the SSA22 region covered by
-Yamada et al.
-
-From these tests we conclude that the ACF on small fields does not
-provide additional constraints to further select models for halos
-hosting LAEs. The reason is that cosmic variance is large and the
-statistical uncertainties on the ACF render almost any model
-compatible with the observational constraints.
-
-We also present the ACF in the case of the full SSA22
-region which has been homogeneously observed by \citep{Yamada2012}. To
-this date the observational ACF has not been reported in the
-litereature, therefore our calculations can be considered as
-predictions.
-
-In Figure X we present the results for the models. The full list of
-these correlation functions can be found in the the data repository
-for this paper in \verb"github".
-
-We also present the results for the angular correlation function in
-therms of the correlation lenght obtained by fitting the following
-function
-
-\begin{equation}
-\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
-\end{equation}
-
-The results are shown in Figure in a $r_{0}-\gamma$ plane where the
-average and standard deviation for each mock are shown in comparison
-with the result derived from observations.
 

### 2013-05-28 paper/ms.tex
removed comments from text

@@
 
-%In this \documentname we constrain the typical mass of dark matter halos
-%hosting LAES at $z=3.1$. Our model is based on the number density
-%information obtained in the recent large scale survey presented by XXX
-%where XXX LAEs are detected over 7 fields of $\sim 46 \times
-%35$Mpc$^{2}h^{-2}$ in area comoving in area corresponding to observed
-%fields of $XXX$ deg$^{2}$.
-
-%Both the spatial distribution and luminosities of the galaxies have,
-%at least in a statistical sense, informatio to constrain theoretical
-%model of LAEs. The most detailed theoretical models are also faced to
-%diverse physical and astrophysical uncertainties in obtaining
-%statistical prediction for the Lyman-alpha line. This uncertainties
-%are largest impediment to consruct an ab-iitio model for LAEs.
-
-%In this \documentname we want to step back and reduce the complexity of our
-%model, with the sole objective of reproducing the cosmic variance in
-%the number density of LAEs. Afterwards we will interpret the
-%implications of this result for physical models for Lyman-alpha
-%emitting galaxies.
-
-%Our model is based on the predictions of a large volume high
-%resolution N-body simulation describing the gravitational dynamics of
-%dark matter. We do not have an strong bias towards the theoretical
-%expectation of what the mass of the dark matter halo hosting the
-%galaxy should be.  Instead, we fully explore the parameter space of
-%our simplified model. The only cut we impose is that observed LAEs do
-%not reside in dark matter halos with masses less than 10$^{10}$\hMsun
-%[citation].
-
-%In the following subsections we describe the most relevant features of
-%the observational data, the N-body simulation we use, our model and
-%its parameters together with the method to compare its predictions
-%against observations.
-
 \subsection{Observational Constraints}
@@
 density information at $z=3.1$ obtained by the panoramic narrow-band
-survey presented by \cite{Yamada2012} from a survey 
-%Our observational reference are the recently published results of a
-%panoramic survey of LAES at $z=3.1$ by \cite{Yamada2012}. 
-%This survey
-conducted with the Subaru 8.2m telescope and the Subaru Prime
-Focus Camera, which has a field of view covering $34\times 27$ arcmin,
-corresponding to a comoving scale of $46\times35$ Mpc $h^{-1}$ at
-$z=3.09$. The narrow band filter is centered at $4977$ \AA with a
-$77$\AA width, corresponding to the redshift range $z=3.062-3.125$ and
-$41$ Mpc $h^{-1}$ comoving scale for the detection of the
-Lyman-$\alpha$ line centered at $z=3.09$. The authors report a total of
-$2161$ LAEs with an observed equivalent width larger than $190$\AA
-over a total survey area of $2.42$ deg$^{2}$, this corresponds to an
-averaga surface number density of $0.20\pm 0.01$ arcmin$^{-2}$.
+survey presented by \cite{Yamada2012} from a survey  conducted with
+the Subaru 8.2m telescope and the Subaru Prime Focus Camera, which has
+a field of view covering $34\times 27$ arcmin, corresponding to a
+comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$. The narrow
+band filter is centered at $4977$ \AA with  $77$\AA width,
+corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
+$h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
+centered at $z=3.09$. The authors report a total  $2161$ LAEs with an
+observed equivalent width larger than $190$\ over a total survey area
+of $2.42$ deg$^{2}$, this corresponds to  averaga surface number
+density of $0.20\pm 0.01$ arcmin$^{-2}$.
 
@@
 (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs.
-%In Table 1 we summarize
-%the values we use in throughout this paper for the each field, covered
-%area, measured surface LAE number density and inferred number volume
-%density.
 
@@
 criteria to construct the catalogs.
-
-%For instance, having
-%different selection criteria on the equivalent width (EW) can change
-%the number of LAEs included in the catalog, yielding number densities
-%different by a factor of two   
-%different criteria on the equivalent width (EW) cuts to construct the
-%LAE samples. Different cuts in the EW can change the number of LAEs to
-%be included in the catalog. This cuts have an impact on the fainter
-%LAEs which are more abundante than brighter ones. Different
-%definitions of the EW cuts can yield number densities different by a
-%factor of two [REF, I think Yamada has some numbers].
-
-%Other
-%surveys by XXX an XXX that cover similar regions, but they use
-%different criteria on the equivalent width (EW) cuts to construct the
-%LAE samples. Different cuts in the EW can change the number of LAEs to
-%be included in the catalog. This cuts have an impact on the fainter
-%LAEs which are more abundante than brighter ones. Different
-%definitions of the EW cuts can yield number densities different by a
-%factor of two [REF, I think Yamada has some numbers].
 
@@
 algorithm with a linking lenght of 0.17 times the interparticle
-distance. 
-%We have veryfied that the main results we present in this
-%paper also hold if instead we use halo catalogs constructed from a the
-%Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are
-%defined to have an density of 200 times the critical density. 
-The minimum halo mass in the models we construct in this \documentname
+distance. The minimum halo mass in the models we construct in this \documentname
 correspond to groups of $\sim 75$ particles. The catalogs were
@@
 out of the $210$ available volumes. In total $15$ mock surveys are
-constructed for each model $\mathcal{M}$. 
-%mock fields into
-%sets of $11$ different ways to
-%construct the LAEs. The first way (match method) we
-The grouping is done in two different ways. In the first way, called
-{\texttt match}, we follow
+constructed for each model $\mathcal{M}$. The grouping is done in two
+different ways. In the first way, called {\texttt match}, we follow
 the clustering of the observed fields. From the $11$ mock fields, $7$
@@
 to avoid that any two volumes are contigous.
-%follow the observational setup and constructs $15$ different mock
-%surveys, each one composed of $12$ mock fields, out of which $7$
-%correspond to contiguous sub-boxes in the simulation to mimick the
-%whole SSA22, $3$ are also contiguous between them but not to the first
-%$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
-%fields that correspond to the SDF and GOODS-North fields. This will
-%produce $15$ different distributions for the number density for a
-%given model ${\mathrm M}$. The second (random method) is similar to the first
-%one. There aare $15$ different mock surveys with $12$ mock fields
-%each, but this time each field corresponds to uncorrelated sub-boxes
-%in the simulation. The third (full method) way in only has $1$ mock survey
-%containing all the $210$ mock fields, in this setup there is only one
-%predicted number density distribution for each model ${\mathrm M}$ 
-%We create the mock surveys in two different ways. First we follow 
-%The advantage of these three sampling ways is that they allow us to
-%explore the effects of both cosmic variance and the correlation
-%between fields. Comparing the results of the first and second method
-%will help us to quantify the effect of field correlation, while
-%compating the first and the third method will serve us to gauge the
-%impace of cosmic variance.
 
@@
 viable parameters thatdeserve to be considered for further analysis.
-
-%For each mock survey generated in a given model ${\mathcal M}$ we compute the LAE surface density
-%distributions for the three different ways of grouping the mock
-%fields, as described in the previous section. For each sub-volume we
-%project the positions of the LAE hosting halos along the $z$ direction
-%and calculate its surface number density in units of sources per
-%arcmin$^{2}$. For each number density distribution we perform a
-%Kolmogorov-Smirnov against the $12$ surface density observational
-%values. From this test we obtain the value $0<P<1$ to reject the null
-%hypothesis, namely that the two data sets come from the same
-%distribution. In this paper we use values of $P>0.1$ to consider that
-%the simulated and observed number densities come from the same
-%distribution.
-
-%We generate a series of models ${\mathcal M}$ with different input
-%parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as
-%follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30
-%different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from
-%$\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while
-%$M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to
-%$\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$
-%takes 100 different values from $0.01$ to $1.00$ regularly spaced by
-%$0.01$. In total the number of different sets of input parameters to
-%be explored is $30 \times 30\times 100 = 9\times 10^{4}$.
 
@@
 gray band values.
-
-%This basic result provides the basis to understand the range of models
-%${\mathcal M}$ expected trends for the
-%LAEs' preferred mass and the occupation fraction.  
-%From this Figure we
-%can read which models do not have achance reproduce the
-%observations. Regions in the plot where the halo surface density
-%values are below the observational constraint correspond to high
-%masses halo masses. For a LAE model ${\mathcal M}$ with a minimum mass
-%$M_{\rm   min}> 3 \times 10^{11}$\hMsun located inthat mass range, the
-%surface density is too low compared with observations.
 
@@
 
-%The raw results of our experiments yield a prefered range for
-%halo masses hosting LAES bounded by a minimum mass $10.5<\log_{10}M_{\rm
-%  min}<11.5$ and without any limitation on the  maximum
-%mass. In this regime the average occupation fraction tends to increase
-%with $M_{\rm min}$. These results discard models that were
-%nevertheless disfavored from the very beginning based on the results
-%of the mass functions (see Figure 1.).
-
-%Figure \label{figure:landscape} presents the regions in the parameter
-%space $M_{\rm min}$-$M_{\rm max}$ where the KS test yields values of
-%$P>0.05$. We consider that for those models it is not possible to rule out the null
-%hypothesis, namely that the number density in simulated data and the observations come
-%from the same parent distribution. Each panel corresponds to the three different ways of
-%grouping the mock fields. In the case of the methods {\tt{Match}}
-%and {\tt{Random}} the color code indicates the fraction of these 15
-%mock surveys with with $P>0.1$. The third panel shows the result for
-%the method {\tt{Full}}, in this case the color code correspond
-%to the value maximum value of $100\times P$ for a model with those
-%mass ranges.
-
-%These results clearly distinguish three mass regimes. In the first regime, at
-%high mass values, we find that LAE models with minimum mass of $M_{\rm
-%  min}>10^{11.5}$\hMsun are not compatible with observations. There is
-%a second regime for masses below $M_{\rm
-%  min}=3\times 10^{10}$ any values for $M_{\rm min}$ and $M_{\rm max}$
-%can be made compatible with observations, provided that
-%$f_{\rm occ}$ is fine tuned to do it. In an intermediate mass regime,
-%for minimum mass values $3\times 10^{10}\hMsun < M_{\rm min}< 3\times 10^{11}\hMsun$ only a
-%limited range of models with $M_{\rm max}$ with occupation fraction
-%$f_{\rm occ}\sim 1$ is able to reproduce observations.
-
-%In these three different mass regimes the occupation monotonically
-%decreases as a function of the minimum halo mass $M_{\rm min}$. In
-%Figure XXX we show this treend in three panels following the same
-%correspondence as Figure XXX. From these results we interpret that the
-%different mass regimes that were identified correspond to best fit
-%models with $f_{\rm occ}\sim 1$, $0<f_{\rm occ}<1$ and $f_{\rm
-%  occ}\sim 0$, respectively.
-
-%The two {\tt match} and {\tt random} methods present the highest
-%number of matching mock surveys in the medium mass regime. However, it
-%is important to keep in mind that not all the mock surveys for a
-%sucessful model ${\mathrm M}$ present a high value $P>0.1$, only a
-%modest fraction seems to be consistent with observations. This shows that the
-%cosmic variance is still present on the physical scales probed by
-%observations. This will be considered in more detail in the discussion
-%seccion.
-
-%To illustrate this point, in Figure \ref{fig:mocks} we present the
-%results for two mock fields for the {\tt{Match}} method for a model
-%with the same parameters, but two extreme values for the KS test.
-
-%Conversely there are different models where the KS test yield values of
-%$P\sim 1$. To illustrate the kind of success represented by these
-%models, we have selected these best ones in the case of the method
-%{\tt{MatchObs}}. Figure XXX shows in the main panel the spatial
-%distribution of the mock surveys, the smaller panel shows the
-%corresponding surface density distribution and the observational
-%constraint.
-
-%In what follows we will focus our discussion on the mocks constructed
-%with the {\tt{Match}} and {\tt{Random}} methods.
-
 \section{Additional Constraints}
@@
 
-%In this section we consider three different ways to impose
-%tighter constraints on this mass range by making use of the results we
-%have derived so far together with additional statistical and
-%astrophysical constraints. In the first constraint we select the
-%models where all the mock surveys present KS-test values consistent
-%with observations. The second constraints uses recent observational
-%results on the average occupation fraction for LAEs at high-z. The
-%third exploits the information in the Angular Correlation Function
-%(ACF).
-
 \subsection{Models with the highest success rates}
@@
 total number of mocks with at least one consistent mock.
-%Here we focuse on the latter models. 
-%The best models
-%represent $\sim 15\%$ of the number of initially considered good
-%models.
 
@@
 We limit the occupation fraction to
-be in the range 
-%further pick models that have an occupation fract
-$f_{\rm
-  occ}\leq 0.2$ to allow for some flexibility on the time evolution
+be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
 and the uncertainty in the dust correction used to infer the escape fraction. 
-%Considering an occupation fraction $f_{\rm occ}=0.20$
-%another $39$This constraint help us to
-%select $\sim 10\%$ of theoriginal models that were considered as
-%consistent with observations in the previous section. 
 Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
@@
 Appendix in Table \ref{table:models_match}.
-
-%In terms of the constraints done in the previous sub-section, we find
-%that the models in this region of parameter space have an average
-%number of XX mock catalogs consistent with observations.
 
@@
 \end{document}
-
-lun abr 29 07:38:58 COT 2013

### 2013-05-31 paper/ms.tex
minor updates

@@
 
-In this section we consider two additional constraints on the models
+In this section we consider three additional constraints on the models
 we accept as succesul. First by taking models with the
@@
 observations. Second by including additional observational constraints
-on the occupation fraction for high redshift LAEs.
+on the occupation fraction for high redshift LAEs. Third by comparing
+the angular correlation function against observational constraints by
+\cite{Hayashino2004}.
 
@@
 
-\section{Results for the Angular Correlation Function}
+\subsection{Consitency with the Angular Correlation Function}
+
+The measurementens presented in \citep{Yamada2012} do not present a
+new measurement of the angular correlation function (ACF). However
+\citep{Hayashino2004} performed such calculation on the LAEs observed
+inthe densest field of SSA22.
 
@@
 subfield in all the 15 mock surveys corresponding to the SSA22
-region. These results are compared against the observations reported
-by \citep{Hayashino2004} which were also performed on the densest
-field of SSA22.
+region.
 

### 2013-06-03 paper/ms.tex
correlation plots added and changes in the paper in the correlation section added

@@
 excluded and the best models are now clustered around a narrow region
-in parameter space. The list for the model parameters is in the
-Appendix in Table \ref{table:models_match}.
+in parameter space. %The list for the model parameters is in the
+%Appendix in Table \ref{table:models_match}.
 
@@
 
-We also present the ACF in the case of the full SSA22
-region which has been homogeneously observed by \citep{Yamada2012}. To
-this date the observational ACF has not been reported in the
-litereature, therefore our calculations can be considered as
-predictions.
-
-In Figure X we present the results for the models. The full list of
-these correlation functions can be found in the the data repository
-for this paper in \verb"github".
-
 %Given that the ACF reported by Hayashino et al en 2004 is taken over
@@
 
-We also present the results for the angular correlation function in
-therms of the correlation lenght obtained by fitting the following
-function
+We also present the results for the mean angular correlation function in
+therms of the angular correlation lenght obtained  by fitting to a power-law
+function:
+
 \begin{equation}
-\xi(r) = \left(\frac{r}{r_{0}}\right)^{-\gamma}
+\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
 \end{equation}
 
-The results are shown in Figure in a $r_{0}-\gamma$ plane where the
-average and standard deviation for each mock are shown in comparison
-with the result derived from observations.
+The fitting is done to both the mean ACF and the observational
+ACF reported by \cite{Hayashino2004} .  The results are shown 
+in Figure  \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$ 
+plane where the average and standard deviation for each mock 
+are shown in comparison with the result derived from observations. 
+Error bars in these figures represents the standard deviation of the
+ACF over all the sub-fields.
 
-%We calculate the mean angular correlation function (ACF) only for the
-%models that showed that all of the 15 mock surveys are consistent
-%at the $P>0.05$ level with observations.
+It can be seen in the left panel figure \ref{figure:correlation_parameters} that
+The observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
+constrains on the parameters models. Only models with angular-correlation lenght within  
+$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models.
 
-Figure \ref{figure:correlation_match} (match) and Figure
-\ref{figure:correlation_random} (random) present such comparison.  The
-error bars in these figures represent the standard deviation of the
-ACF over all the sub-fields.  In general, we observe that the standard
-deviation of the computed ACF in the subfields increases with
-$M_{min}$ following the same trend as in Figure
-\ref{figure:laes_dist}, as a direct consequence of cosmic variance.
+In order to identify the models that are consistent with observation we
+plot if the right panel of figure \ref{figure:correlation_parameters} 
+$\theta_{0}$ vs $M_{\rm min}$ and divide the plots into two sets: Those models
+with $\log \frac{M_{\rm max}}{M_{\odot}}<12$ (blue dots) and those with 
+$\log \frac{M_{\rm max}}{M_{\odot}}>12$ (green dots). The red rectangle includes
+the parameter region wich is consistent with the observational constraint in $\theta_{0}$.
+With this restriction we find that models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and
+$\log \frac{M_{\rm min}}{M_{\odot}}>11.1$can be ruled out.
 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_large_correlation_%selected_models.pdf}
-%\hspace{5mm}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/match_full_correlation_s%elected_models.pdf}
-%\end{center} f
-%\caption{ mean ACFs   and their correponding standard deviation (error
-%  bars)  of some selected models in different mass ranges over the 7
-%  subfields  f the SSA22 field (left) and the entire 12 field sample
-%  (rigth) using thematch
-%  configuration. \label{figure:correlation_match} }  
-%  \end{figure*}
+%In general, we observe that the standard
+%deviation of the computed ACF in the subfields increases with
+%$M_{min}$ following the same trend as in Figure
+%\ref{figure:laes_dist}, as a direct consequence of cosmic variance.
+
+Finally, we also present the ACF in the case of the full SSA22
+region which has been homogeneously observed by \citep{Yamada2012}. To
+this date the observational ACF has not been reported in the
+litereature, therefore our calculations can be considered as
+predictions.
+
+In Figure X we present the results for the models. The full list of
+these correlation functions can be found in the the data repository
+for this paper in \verb"github".
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}
+\end{center}
+\caption{Left: The fitted parameters  ($\theta_{0}$ vs $\gamma$) of the 
+mean ACF  assuming a powerlaw behavior. Each blue dot corresponds to a
+match-model while the green dot represent the powerlaw fit of the observational
+ACF reported by \cite{Hayashino2004}.  The error bars represents the dispersion
+in each parameter over all the mock surveys for a given model and dispersion due
+to the observational error for the measured ACF by \cite{Hayashino2004}. Rigth: 
+$\theta_{0}$ vs $M_{min}$. The date is subdivided into two blocks $M_{max}<12.0$ 
+(blue) and $M_{max}>12.0$ (green). The red rectangle includes the region within
+models are consisted with the observational angular-correlation lenght
+($15<\theta_{0}<23$) as it can be deduced from the left panel. \label{figure:correlation_parameters} }  
+\end{figure*}
 
@@
 models.
+
+When we additional include the ACF constraint we find that only models with 
+$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
+are now consistent with observations.
+
+Including all the observational constraints we find that only between $15$ to $20$ 
+models reproduces observations. The list for the model parameters is in the
+Appendix in Table \ref{table:models_match}.
 
@@
 10.9& 11.9& 0.2\\
-10.9& 12.0& 0.2\\
-10.9& 12.1& 0.2\\
-10.9& 12.2& 0.2\\
-10.9& 12.3& 0.2\\
-10.9& 12.4& 0.2\\
-10.9& 12.5& 0.2\\
-10.9& 12.6& 0.2\\
-10.9& 12.7& 0.2\\
-10.9& 12.8& 0.2\\
-10.9& 12.9& 0.2\\
-10.9& 13.0& 0.2\\\hline\hline
+%10.9& 12.0& 0.2\\
+%10.9& 12.1& 0.2\\
+%10.9& 12.2& 0.2\\
+%10.9& 12.3& 0.2\\
+%10.9& 12.4& 0.2\\
+%10.9& 12.5& 0.2\\
+%10.9& 12.6& 0.2\\
+%10.9& 12.7& 0.2\\
+%10.9& 12.8& 0.2\\
+%10.9& 12.9& 0.2\\
+%10.9& 13.0& 0.2\\\hline\hline
 \end{tabular}

### 2013-06-04 paper/ms.tex
small changes to abstract and mispelling errors

@@
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
-$^{2}$ --}
+$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile}
 
@@
 observations, observational constraints on the occupation fraction and
-the angular correlation function. The first two conditions narrow down
-the space parameter to $M_{\rm min}=$ and $M_{\rm max}$, $f_{\rm occ}$. The angular
-correlation function does not add a significant constraint due to the
-cosmic variance in the small angular fields where this statistics has
-been computed so far. We make available the mock data for the best
-models in a public repository. Implications for galaxy formation
-models? 
+the angular correlation function. These three conditions narrow down
+the space parameter to $10.1\leq M_{\rm min}\leq11.0$ and
+$10.2\leq M_{\rm max}\leq12.0$, $0.1\leq_{\rm occ}\leq 0.2 $. 
+ We make available the mock data for the best models in a public repository. 
+ Implications for galaxy formation models? 
 \end{abstract}
@@
 There are three parameters in the model that decide whether a halo can host a
-galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
+galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
 M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
   occ}$ of such halos that effectively host a LAE. We do not assign a
-luminosity to each each LAE. We are primaraly interested in
+luminosity to each LAE. We are primaraly interested in
 constraining the halo mass range hosting detectable LAEs under the
@@
 \citep{Hayashino2004} performed such calculation on the LAEs observed
-inthe densest field of SSA22.
+in the densest field of SSA22.
 

### 2013-06-04 code/correlation_statistic.py

@@ -1,14 +1,47 @@
 import numpy as np
 import pylab as P
+import matplotlib.collections as collections
+from scipy import stats
+from scipy import optimize as op
+
+#defining the power-law function to fit
+powerlaw = lambda x, amp, index: (x/amp)**(index)
+fitfunc = lambda p, x: (x/p[0])**p[1]
+errfunc = lambda p, x, y,err: (y - fitfunc(p, x))/err
+
+pinit = [1.0, -1.0] 
 
 n_models=101
 n_mocks=12
 theta_bins=13
 pro_path="/home/jemejia/CosmicVarianceLAES/"
 
-
 obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
 obs_correlation=np.loadtxt(obs_correlation_file,skiprows=4)
+theta=obs_correlation[0:theta_bins,0]
+correlation=obs_correlation[0:theta_bins,1]
+std=obs_correlation[0:theta_bins,2]
+out = op.leastsq(errfunc, pinit,args=(theta, correlation,std), full_output=1)
+
+pfinal = out[0]
+covar = out[1]
+
+    
+print pfinal
+print "covariance matriz \n\n", covar, "\n\n"
+
+ro_obs=pfinal[0]
+ro_err_obs=np.sqrt(covar[0][0])
+slope_obs=pfinal[1]
+slope_err_obs=np.sqrt(covar[1][1])
+ro_min=ro_obs - ro_err_obs
+ro_max=ro_obs + ro_err_obs
+slope_min=slope_obs - slope_err_obs
+slope_max=slope_obs + slope_err_obs
+print "ro=",ro_obs,"+-" ,ro_err_obs, "\n"
+print "slope=",slope_obs,"+-" ,slope_err_obs, "\n"
+
+theta=obs_correlation[0:theta_bins,0]
 models_file=pro_path + "data/mock_survey/" + "BestModels_match_mock.dat" 
 model_info=np.loadtxt(models_file)
 m_min_m=model_info[:,0] #_m refers to model
@@ -19,6 +52,11 @@ f_occ_m=model_info[:,2]
 mean_correlation= np.zeros( [n_models,theta_bins] )
 std_correlation = np.zeros( [n_models,theta_bins] )
 chi_individual  = np.zeros( [n_models,n_mocks] )
+slope = np.zeros( n_models )
+slope_err = np.zeros( n_models )
[…]

### 2013-06-04 paper/ms.tex
minor updates to the abstract

@@
 \begin{abstract}
-We use cosmological N-body simulations to find the characteristic mass
-of dark matter halos hosting Lyman-Alpha Emitting (LAE) galaxies at a
-redshift of $z=3.1$. The method is based on matching the statistics
-for the number density between mock and observed fields. The mock
-catalogs are constructed using a simple model where a dark matter halo
-can only host one LAE with a probability $f_{\rm occ}$ if its mass is
-found withing a certain range mass range delimited by two threshold
-values, $M_{\rm min}$ and $M_{\rm max}$. We find that the most of the models that
-are consistent the observed cosmic variance statistics are those with
-halo masses in the range $10.5 < \log_{10} M_{\rm  min}/hMsun < 11.5$
-and $\log_{10} M_{\rm max}/\hMsun < 13.5$ with and occupation fraction
-that scales as $f_{\rm occ}=$. We explore three additional constraints
-to narrow down these range: the number of mocks consistent with 
-observations, observational constraints on the occupation fraction and
-the angular correlation function. These three conditions narrow down
-the space parameter to $10.1\leq M_{\rm min}\leq11.0$ and
-$10.2\leq M_{\rm max}\leq12.0$, $0.1\leq_{\rm occ}\leq 0.2 $. 
- We make available the mock data for the best models in a public repository. 
- Implications for galaxy formation models? 
+We use cosmological N-body dark matter only simulations to constrain the
+characteristic mass of dark matter halos hosting Lyman-Alpha Emitting
+(LAE) galaxies at a redshift of $z=3.1$. The method is based on
+matching the statistics for the number density between mock and
+observed fields. The mock fields are constructed using a simple model
+where a dark matter halo can only host one LAE with a probability
+$f_{\rm occ}$ if its mass is found withing a certain range mass range
+delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. 
+We also maximize the number of mocks surveys consistent with
+observations and impose consistency with the angular correlation
+function. Under these conditions we find that LAEs are preferentially
+hosted by halos in very narrow mass ranges less than 0.5 dex in width,
+with the minimum mass $10\leq \log_{10}M_{\rm min}\leq 10.9$ and the
+occupation fraction $f_{\rm   occ}\leq 0.2$.  Our finding suggest that
+the most massive dark matter halos at that epoch do not host the
+brightest LAEs. This also gives support to observational evidence that
+says that only a small fraction of star forming galaxies can be
+actually detected as LAEs.
 \end{abstract}
@@
 match-model while the green dot represent the powerlaw fit of the observational
-ACF reported by \cite{Hayashino2004}.  The error bars represents the dispersion
+ACF reported by \citet{Hayashino2004}.  The error bars represents the dispersion
 in each parameter over all the mock surveys for a given model and dispersion due
-to the observational error for the measured ACF by \cite{Hayashino2004}. Rigth: 
+to the observational error for the measured ACF by \citet{Hayashino2004}. Rigth: 
 $\theta_{0}$ vs $M_{min}$. The date is subdivided into two blocks $M_{max}<12.0$ 
@@
 models are consisted with the observational angular-correlation lenght
-($15<\theta_{0}<23$) as it can be deduced from the left panel. \label{figure:correlation_parameters} }  
+($15<\theta_{0}<23$) as it can be deduced from the left
+panel. \label{figure:correlation_parameters}} 
 \end{figure*}

### 2013-06-06 paper/ms.tex
new plots

@@
 
+In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
+models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rmmin}-f_{\rm occ}$
+for the {\tt match} method after applying the observational constraints 
+in the occupation fraction and the ACF.
+
 Finally, we also present the ACF in the case of the full SSA22
@@
 models are consisted with the observational angular-correlation lenght
-($15<\theta_{0}<23$) as it can be deduced from the left
-panel. \label{figure:correlation_parameters}} 
+($15<\theta_{0}<23$) as it can be deduced from the left panel. \label{figure:correlation_parameters}} 
 \end{figure*}
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
+\end{center}
+\caption{Best models when both the constraints on the maximal number
+  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
+  0.2$ are included. \label{fig:restriction_mock_and_f_occ_corr}} 
+\end{figure*} 
 %\begin{figure*}

### 2013-06-11 code/correlation_statistic.py
paper updated in correlation function section and occupation fraction discussion

@@ -4,7 +4,7 @@ import matplotlib.collections as collections
 from scipy import stats
 from scipy import optimize as op
 
-#defining the power-law function to fit
+#defining the power-law function to fit the correlation function
 powerlaw = lambda x, amp, index: (x/amp)**(index)
 fitfunc = lambda p, x: (x/p[0])**p[1]
 errfunc = lambda p, x, y,err: (y - fitfunc(p, x))/err
@@ -47,7 +47,7 @@ model_info=np.loadtxt(models_file)
 m_min_m=model_info[:,0] #_m refers to model
 m_max_m=model_info[:,1]
 f_occ_m=model_info[:,2]
-
+model_numbers=np.arange(len(f_occ_m))
 
 mean_correlation= np.zeros( [n_models,theta_bins] )
 std_correlation = np.zeros( [n_models,theta_bins] )
@@ -66,16 +66,12 @@ for i in range(n_models):
         lae_correlation  = np.loadtxt(model_correlation_filename)
         corr[j,:] = lae_correlation[:,1]
 
-        #slope[i,j], intercept, r_value, p_value, std_err = stats.linregress( log_theta[corr_index] , np.log10(correlation[corr_index]) )
-        #log_ro[i,j]=-1*intercept
-        #print log_theta, corr[j,:]
-        #print slope[i,j] , np.power(10,log_ro[i,j]), r_value
-        #chi_individual[i,j]= chi_individual[i,j] + (mean_correlation[i,j] - obs_correlation[j,1])*(mean_correlation[i,j] - obs_correlation[j,1])/(std_correlation[i,j]*std_correlation[i,j] + obs_correlation[j,2]*obs_correlation[j,2])
+        
     std_correlation[i,:]  = np.std(corr,axis=0)
     mean_correlation[i,:] = np.mean(corr,axis=0)
 
-    chisquare=np.zeros([n_models,theta_bins])
-    chi=np.zeros(n_models)
+chisquare=np.zeros([n_models,theta_bins])
+chi=np.zeros(n_models)
 for i in range(n_models):
     correlation= mean_correlation[i,:]
     std= std_correlation[i,:]
@@ -85,10 +81,7 @@ for i in range(n_models):
[…]

### 2013-06-13 paper/ms.tex
starting to res-structure the final draft

--- 2013-06-04 paper/ms.tex
@@
 
-\subsection{Additional  Constraints on the Occupation Fraction}
-
-We impose an additional restriction using the observational results
-by \cite{Hayes2010}. They constrained the value of $f_{\rm
-  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
-on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
-Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
-extinction to obtain an estimate for the intrinsic H$\alpha$
-luminosity, and using values for the theoretical expectation of the
-ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
-the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
-authors show that the luminosity function for LAEs at $z=2.2$ is
-consistent with the escape fraction being constant for every galaxy
-regardless of its luminosity. From this results they derive that
-almost $90\%$ of the star forming galaxies emit insufficient
-Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
-used in this \documentname the age of the universe between $z=3.1$ and
-$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
-conditions that determine the escape fraction $f_{\rm esc}$ and the
-occupation fraction $f_{\rm  occ}$ remain similar over that time
-scale.
-
-We limit the occupation fraction to
-be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
-and the uncertainty in the dust correction used to infer the escape fraction. 
-Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
-models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
-  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
-With this additional constraint between $35$ to $40$ models are
-consistent with observations, this represents a factor of $\sim 2$
-reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
-excluded and the best models are now clustered around a narrow region
-in parameter space. %The list for the model parameters is in the
-%Appendix in Table \ref{table:models_match}.
-
 \begin{figure*}
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
-\end{center} 
-\caption{Best models when both the constraints on the maximal number
-  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
-  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
+%\hspace{5mm}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
+%\end{center} 
+%\caption{Best models when both the constraints on the maximal number
+%  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
+%  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
+%\end{figure*}
 
@@
 
+In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
+models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
+for the {\tt match} method after applying the observational constraints 
+in the occupation fraction and the ACF.
+
 Finally, we also present the ACF in the case of the full SSA22
@@
 Appendix in Table \ref{table:models_match}.
+
+\subsection{Observational estimates for the occupation fraction}
+
+Observations by  \cite{Hayes2010} constrained the occupation fraction of $f_{\rm 
+  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
+on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
+European Southern 
+Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
+extinction to obtain an estimate for the intrinsic H$\alpha$
+luminosity, and using values for the theoretical expectation of the
+ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
+the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
+esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
+authors show that the luminosity function for LAEs at $z=2.2$ is
+consistent with the escape fraction being constant for every galaxy
+regardless of its luminosity. From this results they derive that
+almost $90\%$ of the star forming galaxies emit insufficient
+Lyman $\alpha$ to be detected, effectively setting the occupation
+fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
+used in this \documentname the age of the universe between $z=3.1$ and
+$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
+conditions that determine the escape fraction $f_{\rm esc}$ and the
+occupation fraction $f_{\rm  occ}$ remain similar over that time
+scale.
+
+We limit the occupation fraction to
+be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
+and the uncertainty in the dust correction used to infer the escape fraction. 
+Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
+models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
+  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
+With this additional constraint between $35$ to $40$ models are
+consistent with observations, this represents a factor of $\sim 2$
+reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
+excluded and the best models are now clustered around a narrow region
+in parameter space. %The list for the model parameters is in the
+%Appendix in Table \ref{table:models_match}.
 

### 2013-06-15 paper/ms.tex
re-structure

@@
 
-When we include the tightest constraints on the mock catalogs, we find
-that there are 30 set of parameters of our model, out of the original
-90000 initial models, that are consistent with the observational
-constraints at redshift $3.1$: the distribution of the number density,
-the inferred values for the average occupation fraction. The
-consistency with the angular correlation, in terms of the $\chi^2$
-statistics did not help to discard any additional models with a
-significant degree of confidence.
+Considering the tightest constraints on the mock catalogs 
+with the angular correlation function and the maximal
+number of consistent mock surveys we end up with 50 models out of the
+original 90000 models.
 
-These 30 models can be classified into two families of the same
+We find that most of the models with an occupation fraction $f_{\rm
+  occ}\leq 0.2$ are those with mean correlation lenghts within the
+observational uncertainty. Most of the models with $f_{\rm occ}$ are
+those that are consistent only when the statistical uncertainty from
+the mock cosmic variance is taken into account.
+
+This slight preference towards low occupations fractions is remarkably
+close to  the observational constraint $f_{\rm occ}$ derived at
+$z=2.2$ by \cite{Hayes2010}.  This estimation was based
+on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
+European Southern  Observatorio (ESO) Very Large Telescope
+(VLT). Using corrections by extinction to obtain an estimate for the
+intrinsic H$\alpha$ luminosity, and using values for the theoretical
+expectation of the ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
+the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
+esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
+authors show that the luminosity function for LAEs at $z=2.2$ is
+consistent with the escape fraction being constant for every galaxy
+regardless of its luminosity. From this results they derive that
+almost $90\%$ of the star forming galaxies emit insufficient
+Lyman $\alpha$ to be detected, effectively setting the occupation
+fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
+used in this \documentname the age of the universe between $z=3.1$ and
+$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
+conditions that determine the escape fraction $f_{\rm esc}$ and the
+occupation fraction $f_{\rm  occ}$ remain similar over that time
+scale.
+
+%that there are 60 set of parameters of our model, out of the original
+%90000 initial models, that are consistent with the observational
+%constraints at redshift $3.1$: the distribution of the number density,
+%the inferred values for the average occupation fraction. The
+%consistency with the angular correlation, in terms of the $\chi^2$
+%statistics did not help to discard any additional models with a
+%significant degree of confidence.
+
+These 50 models can be classified into two families of the same
 size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
@@
 \subsection{Observational estimates for the occupation fraction}
-
-Observations by  \cite{Hayes2010} constrained the occupation fraction of $f_{\rm 
-  occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
-on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
-European Southern 
-Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
-extinction to obtain an estimate for the intrinsic H$\alpha$
-luminosity, and using values for the theoretical expectation of the
-ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
-the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
-authors show that the luminosity function for LAEs at $z=2.2$ is
-consistent with the escape fraction being constant for every galaxy
-regardless of its luminosity. From this results they derive that
-almost $90\%$ of the star forming galaxies emit insufficient
-Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
-used in this \documentname the age of the universe between $z=3.1$ and
-$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
-conditions that determine the escape fraction $f_{\rm esc}$ and the
-occupation fraction $f_{\rm  occ}$ remain similar over that time
-scale.
 

### 2013-06-16 paper/ms.tex
editting ACF section

@@
 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
-%\hspace{5mm}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
-%\end{center} 
-%\caption{Best models when both the constraints on the maximal number
-%  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
-%  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
-%\end{figure*}
-
 \subsection{Consitency with the Angular Correlation Function}
 
-The measurementens presented in \citep{Yamada2012} do not present a
-new measurement of the angular correlation function (ACF). However
-\citep{Hayashino2004} performed such calculation on the LAEs observed
-in the densest field of SSA22.
-
-we calculate the angular correlation function
-(ACF) for all the models having the $15$ mock surveys consistent with
-observations. We perform this calculation as a sanity check and
-potential additional constraint. The ACF is computed only the densest
-subfield in all the 15 mock surveys corresponding to the SSA22
-region.
+We impose an additional constraint by requiring that the models
+selected in the previous section to be also compatible with the
+observational ACF. The measurementens presented in \citep{Yamada2012}
+do not present a new measurement of the angular correlation function
+(ACF). Instead we use the measurements performed by
+\citep{Hayashino2004} on the LAEs observed in the densest field of
+SSA22.
 
@@
 
-The comparison between the simulated and observed ACFs is also done using a
-$\chi^2$ statistic which includes the information on the measurement
-uncertainties and the statistical dispersio from the $15$ mock surveys
-in the simulation
-
-\begin{equation}
-\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
-    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
-    sim}^2({\theta_i})}, 
-\end{equation}
-
-where the sum is done over all the $13$ angle values $\theta_i$ where the
-ACF has been computed. In Figure XX we plot this statistic for all the
-models considered. In all cases $\chi^{2}<7$ which is not sufficient
-to consider that the correlation functions from the simulations are
-statistically different from the observational one. The constribution
-of cosmic variance in the simulations together with the statistical
-uncertainties make all tested models compatible with the observational
-constraints.
-
-%From these tests we conclude that the ACF on small fields does not
-%provide additional constraints to further select models for halos
-%hosting LAEs. The reason is that
-
-%Given that the ACF reported by Hayashino et al en 2004 is taken over
-%the densest  field oserved in the SSA22 region by  Yamada et el in
-%2012 it is expected that the predicted ACF in the SSA22 region should
-%reproduce this observation. In the  left panel of figure
-%\ref{figure:correlation_match} we can see the predicted ACFs  an their
-%corresponding standard deviation over the seven fields that mock the
-%SSA22  region. It can be seen that the model with $M_min=10.6$ seems
-%to better reproduce the  Hayashino's ACF and that the corresponding
-%field is in fact an overdense field in the SSA22 region covered by
-%Yamada et al.
-
-We also present the results for the mean angular correlation function in
+The comparison between the theoretical and observational ACF is done in
 therms of the angular correlation lenght obtained  by fitting to a power-law
@@
 
-The fitting is done to both the mean ACF and the observational
-ACF reported by \cite{Hayashino2004} .  The results are shown 
-in Figure  \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$ 
-plane where the average and standard deviation for each mock 
-are shown in comparison with the result derived from observations. 
-Error bars in these figures represents the standard deviation of the
-ACF over all the sub-fields.
+The procedure is a done through a least square minimizatio is done to
+both the mean ACF and the observational ACF reported by
+\cite{Hayashino2004} .  The results are shown  in Figure
+\ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$  plane
+where the average and standard deviation for each mock  are shown in
+comparison with the resut derived from observations.  Error bars in
+these figures represents the standard deviation of the ACF over all
+the sub-fields. These error bars are larger than the statistical
+uncertainty from the fitting procedure on a single field.
 
-It can be seen in the left panel figure \ref{figure:correlation_parameters} that
-The observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
+We see in the left panel Figure \ref{figure:correlation_parameters} that
+the observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
 constrains on the parameters models. Only models with angular-correlation lenght within  
@@
 for this paper in \verb"github".
+
+%The comparison between the simulated and observed ACFs is also done using
+%$\chi^2$ statistic which includes the information on the measurement
+%uncertainties and the statistical dispersio from the $15$ mock surveys
+%in the simulation
+
+%\begin{equation}
+%\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
+%    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
+%    sim}^2({\theta_i})}, 
+%\end{equation}
+
+%where the sum is done over all the $13$ angle values $\theta_i$ where the
+%ACF has been computed. In Figure XX we plot this statistic for all the
+%models considered. In all cases $\chi^{2}<7$ which is not sufficient
+%to consider that the correlation functions from the simulations are
+%statistically different from the observational one. The constribution
+%of cosmic variance in the simulations together with the statistical
+%uncertainties make all tested models compatible with the observational
+%constraints.
+
+%From these tests we conclude that the ACF on small fields does not
+%provide additional constraints to further select models for halos
+%hosting LAEs. The reason is that
+
+%Given that the ACF reported by Hayashino et al en 2004 is taken over
+%the densest  field oserved in the SSA22 region by  Yamada et el in
+%2012 it is expected that the predicted ACF in the SSA22 region should
+%reproduce this observation. In the  left panel of figure
+%\ref{figure:correlation_match} we can see the predicted ACFs  an their
+%corresponding standard deviation over the seven fields that mock the
+%SSA22  region. It can be seen that the model with $M_min=10.6$ seems
+%to better reproduce the  Hayashino's ACF and that the corresponding
+%field is in fact an overdense field in the SSA22 region covered by
+%Yamada et al.
 

### 2013-06-16 paper/ms.tex
few changes in paper

--- 2013-06-13 paper/ms.tex
@@
 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
-%\hspace{5mm}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
-%\end{center} 
-%\caption{Best models when both the constraints on the maximal number
-%  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
-%  0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
-%\end{figure*}
-
 \subsection{Consitency with the Angular Correlation Function}
@@
 where the sum is done over all the $13$ angle values $\theta_i$ where the
-ACF has been computed. In Figure XX we plot this statistic for all the
-models considered. In all cases $\chi^{2}<7$ which is not sufficient
-to consider that the correlation functions from the simulations are
-statistically different from the observational one. The constribution
-of cosmic variance in the simulations together with the statistical
-uncertainties make all tested models compatible with the observational
-constraints.
+ACF has been computed. We found that 35 out of 100 models  has statistical significance 
+greater that $10\%$ ($\chi^{2}<18$ that for 12 degrees). Therefore, 
+in spite of the effect of cosmic variance and statistical we can rule out about
+$70\%$ of the consistent models with the ACF observational constraint.
 
@@
 Error bars in these figures represents the standard deviation of the
-ACF over all the sub-fields.
 
@@
 $\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models. 
+It is important to note that the compatible models that have been found by this power
+approach are in accordance with the models found using the $\chi^{2}$ statistic.
 
@@
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
-for the {\tt match} method after applying the observational constraints 
-in the occupation fraction and the ACF.
+for the {\tt match} method after applying the observational constraint
+in the ACF. We also plot in different colors models with $f_{occ}\leq0.2$ and
+models with $f_{occ} > 0.2$.
 
-Finally, we also present the ACF in the case of the full SSA22
-region which has been homogeneously observed by \citep{Yamada2012}. To
+Finally, in figure \ref{fig:ACF_prediction} we also present the ACF 
+in the case of the full SSA22 region which has been homogeneously
+observed by \citep{Yamada2012}. To
 this date the observational ACF has not been reported in the
 litereature, therefore our calculations can be considered as
-predictions.
+predictions.  The full list ofthese correlation functions can
+be found in the the data repository for this paper in \verb"github".
 
-In Figure X we present the results for the models. The full list of
-these correlation functions can be found in the the data repository
-for this paper in \verb"github".
+%In Figure X we present the results for the models. The full list of
+%these correlation functions can be found in the the data repository
+%for this paper in \verb"github".
 
@@
 \includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
 \end{center}
@@
 
-When we include the tightest constraints on the mock catalogs, we find
-that there are 30 set of parameters of our model, out of the original
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/power_law_correlation_prediction.pdf}
+%\hspace{5mm}
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/mean_correlation_prediction.pdf}
+\end{center}
+\caption{Predited ACF parameters (left panel) and ACF (rigth panel) in the full SSA22
+field for the models that are consistent with observations \label{fig:ACF_prediction}} 
+\end{figure*}
+
+When we include the tightest constraints on the mock catalogs: : the
+distribution of the number density and the  consistency with 
+the angular correlation, we find
+that there are 40 set of parameters of our model, out of the original
 90000 initial models, that are consistent with the observational
-constraints at redshift $3.1$: the distribution of the number density,
-the inferred values for the average occupation fraction. The
-consistency with the angular correlation, in terms of the $\chi^2$
-statistics did not help to discard any additional models with a
-significant degree of confidence.
+constraints at redshift $3.1$. The parameter space of these models
+is constraint on $M_{\rm min}$ and $M_{\rm max}$ where
+$\log_{10}M_{\rm min}\leq 11.3$ and $\log_{10}M_{\rm max}\leq 12.0$ 
+are now consistent with observations.
 
-These 30 models can be classified into two families of the same
+These 40 models can be classified into two families of the same
 size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
-typically of less than $<1.0$ dex. While in the second familiy the
-extent $>1.0$ dex. In the first case the minimum halo mass is found to
-be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
+typically of less than $<0.5$ dex. While in the second familiy the
+extent $>0.5$ dex. In the first case the minimum halo mass is found to
+be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.3}\hMsun$ while
 in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
-are compatible with the observational contraints. In what follows we
+are compatible with the observational contraints. In the next section we
 discuss the implications of the existence of these two families of
@@
 
-When we additional include the ACF constraint we find that only models with 
-$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
-are now consistent with observations.
+\subsection{Additional  Constraints on the Occupation Fraction}
 
-Including all the observational constraints we find that only between $15$ to $20$ 
-models reproduces observations. The list for the model parameters is in the
-Appendix in Table \ref{table:models_match}.
-
-\subsection{Observational estimates for the occupation fraction}
-
-Observations by  \cite{Hayes2010} constrained the occupation fraction of $f_{\rm 
+We impose an additional restriction using the observational results
+by \cite{Hayes2010}. They constrained the value of $f_{\rm
   occ}$ at $z=2.2$ to be $f_{\rm occ}=0.10$. This estimation was based
-on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
-European Southern 
+on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the European Southern
 Observatorio (ESO) Very Large Telescope (VLT). Using corrections by
@@
 and the uncertainty in the dust correction used to infer the escape fraction. 
-Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
-models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
-  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
-With this additional constraint between $35$ to $40$ models are
-consistent with observations, this represents a factor of $\sim 2$
-reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
-excluded and the best models are now clustered around a narrow region
-in parameter space. %The list for the model parameters is in the
+Figure  \ref{fig:restriction_mock_and_f_occ_corr}  shows the prefered
+models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$ 
+for the {\tt match} method after applying the observational constraint
+in the ACF. We also plot in different colors models with $f_{occ}\leq0.2$ and
+models with $f_{occ} > 0.2$.
+
+ With this additional constraint between $15$ to $20$ models are
+consistent with observations, this represents an aditional factor of $\sim 2$
+reduction. The list for the model parameters is in the Appendix 
+in Table \ref{table:models_match}.
+%All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
+%excluded and the best models are now clustered around a narrow region
+%in parameter space.
+
+In addition to this, we can also see in Figure \ref{fig:restriction_mock_and_f_occ_corr}
+ that all the models excluded with  the occupation fraction  constraint ($f_{\rm occ}>0.2$)
+ has $\log_{10}M_{\rm min}\geq 11.0$ and  belongs to the family 
+where the range $M_{\rm min}-M_{\rm max}$ is narrow (typically of less than $<0.5$ dex).
+Consequentely, our models predict that LAEs tend to live in a broad mass range
+(typically of greater than $<0.5$ dex).
+
+% In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
+% models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rmmin}-f_{\rm occ}$
+% for the {\tt match} method after applying the observational constraint
+% in the ACF. We also plot in different colors models with $f_{occ}\leq0.2$ and
+% models with $f_{occ}\gt0.2$.
+
+Finally, in figure \ref{fig:ACF_prediction} we also present the ACF 
+in the case of the full SSA22 region which has been homogeneously
+observed by \citep{Yamada2012}. To
+this date the observational ACF has not been reported in the
+litereature, therefore our calculations can be considered as
+predictions that could help us to make additional constrainst to our model
+. The full list ofthese correlation functions can
+be found in the the data repository for this paper in \verb"github".
+
+%The list for the model parameters is in the
 %Appendix in Table \ref{table:models_match}.
+
+% 
+% \begin{figure*}
+% \begin{center}
+% \includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock_and_f_occ.pdf}
+% \hspace{5mm}
+% \includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_random_mass_mock_and_f_occ.pdf}
+% \end{center} 
+% \caption{Best models when both the constraints on the maximal number
+%   of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
+%   0.2$ are included.  \label{fig:restriction_mock_and_f_occ}}   
+% \end{figure*}
 

### 2013-06-18 paper/ms.tex
jaime's version recovered

--- 2013-06-16 paper/ms.tex
@@
 Jaime E. Forero-Romero$^{1}$ and
-Julian Mej\'ia$^{2}$ 
+Julian Mej\'ia-Restrepo$^{2}$ 
 }
@@
 \includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
 \end{center}
-\caption{Best models when both the constraints on the maximal number
+\caption{Best models paramter space when both the constraints on the maximal number
   of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
-  0.2$ are included. \label{fig:restriction_mock_and_f_occ_corr}} 
+  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth)
+  \label{fig:restriction_mock_and_f_occ_corr}} 
 \end{figure*} 

### 2013-06-20 paper/ms.tex
making quantitative statements

@@
 \newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
-\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
 \newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
@@
 
-In this section we consider three additional constraints on the models
-we accept as succesul. First by taking models with the
+In this section we consider two additional constraints on the models
+we accept as succesul. First we take models with the
 highest possible number of mock surveys consistent with
-observations. Second by including additional observational constraints
-on the occupation fraction for high redshift LAEs. Third by comparing
-the angular correlation function against observational constraints by
-\cite{Hayashino2004}.
+observations. Second by comparing the angular correlation function
+against observational constraints by \cite{Hayashino2004}.
 
@@
 
-For each model ${\mathcal M}$there are 15 different mock surveys. In the
+For each model ${\mathcal M}$ there are 15 different mock surveys. In the
 previous section we presented the models that had at least one (1)
@@
 Figure \ref{fig:high_success_rate} shows the number of models
-that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for the {\texttt
-  match} and {\texttt random} methods.  This shows that there are
-here are between $80$ to $100$ models with all the 15 realizations with
-$P>0.05$. This a reduction of a factor of $\sim 6$ with repect to the
-total number of mocks with at least one consistent mock.
+that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
+{\texttt  match} and {\texttt random} methods.  This shows that there
+are between $80$ to $100$ models with all the 15 realizations with
+$P>0.05$. Selction of these models as successful represents a
+reduction of a factor of $\sim 6$ with repect to the total number of
+mocks with at least one consistent mock.
 
@@
 in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
-  min}-f_{\rm occ}$ for the {\texttt match} method, the results for
-the {\texttt random} method are similar. In this case the models with
-$\log_{10}M_{\rm min}< 11.7$ are greatly reduced. This corresponds to
-the regions in the parameter space in Figure \ref{fig:landscape} that
-already had a low number of consistent mock surveys. From the right
-panel in Figure \ref{fig:restriction_mock} one can see that there is
-not a strong selection effect on the occupation fraction $f_{\rm
-  occ}$.
+  min}-f_{\rm occ}$. The results are very similar between the {\texttt
+  match} and {\texttt random} methods. With this constraints the
+number of consistent models with  $\log_{10}M_{\rm min}< 11.7$ are
+greatly reduced. This corresponds to the regions in the parameter
+space in Figure \ref{fig:landscape} that already had a low number of
+consistent mock surveys. On the other hand, from the right panel in
+Figure \ref{fig:restriction_mock} one can see that there is not a
+strong selection effect on the occupation fraction $f_{\rm occ}$.
 
@@
 
-We impose an additional constraint by requiring that the models
-selected in the previous section to be also compatible with the
-observational ACF. The measurementens presented in \citep{Yamada2012}
-do not present a new measurement of the angular correlation function
-(ACF). Instead we use the measurements performed by
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
+\hspace{5mm}  
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
+\end{center}
+\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) of the 
+mean angular correlation function of the 15 mock surveys for each
+model. Blue dots corresponds to simulations and the green cross to
+observations by \citet{Hayashino2004}. The error bars in the
+theoretical data correspond to the starndard deviation from the
+different mocks. Right: Same results as before in the
+$\theta_{0}$-$M_{\rm min}$ plane. This time the observational
+constraints are represented by the red rectangle. Blue squares
+represent models with $\log_{10} M_{\rm  max}<12.0$, green circles are
+models with $\log_{10} M_{\rm max}>12.0$.
+\label{figure:correlation_parameters}}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
+\end{center}
+\caption{Best models paramter space when both the constraints on the
+  maximal number of  consistent mocks and the occupation  fraction
+  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
+  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
+  \label{fig:restriction_mock_and_f_occ_corr}} 
+\end{figure*}
+
+As an additional observational constraint we requiring that the models
+selected in the previous section must be compatible with the
+observational angular correlation function (ACF). The measurementens
+presented in \citep{Yamada2012} do not report an ACF
+measurement. Instead we use the results reported by
 \citep{Hayashino2004} on the LAEs observed in the densest field of
@@
 It is important to keep in mind that there are some differences
-between this work and \citep{Yamada2012}. The color selection by
+between this work and \citep{Yamada2012}. First, the color selection by
 \cite{Yamada2012} is less stringent compared to the one by
@@
 
-The procedure is a done through a least square minimizatio is done to
-both the mean ACF and the observational ACF reported by
-\cite{Hayashino2004} .  The results are shown  in Figure
+Both the theoretical and observational ACF are derived by a least
+square minimization procedure. The results are shown  in Figure
 \ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$  plane
-where the average and standard deviation for each mock  are shown in
-comparison with the resut derived from observations.  Error bars in
+where the average and standard deviation for each mock is shown in
+comparison with the resut derived from observations.  The Error bars in
 these figures represents the standard deviation of the ACF over all
-the sub-fields. These error bars are larger than the statistical
-uncertainty from the fitting procedure on a single field.
+the sub-fields in the 15 mock observations. These error bars are
+larger than the statistical uncertainty from the fitting procedure on
+a single field..
 
 We see in the left panel Figure \ref{figure:correlation_parameters} that
-the observational ACF measured by \cite{Hayashino2004} (green dot) set aditional 
-constrains on the parameters models. Only models with angular-correlation lenght within  
-$\theta_{0}\sim[15,23]arcsec$ reproduces observations and this rule out several models.
+the observational ACF measured by \cite{Hayashino2004} (green dot) is
+succesul in reducing the total number of possible models. Only those
+with angular-correlation length within
+$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are consideret to
+reproduce observations.
 
-In order to identify the models that are consistent with observation we
-plot if the right panel of figure \ref{figure:correlation_parameters} 
-$\theta_{0}$ vs $M_{\rm min}$ and divide the plots into two sets: Those models
-with $\log \frac{M_{\rm max}}{M_{\odot}}<12$ (blue dots) and those with 
-$\log \frac{M_{\rm max}}{M_{\odot}}>12$ (green dots). The red rectangle includes
-the parameter region wich is consistent with the observational constraint in $\theta_{0}$.
-With this restriction we find that models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and
-$\log \frac{M_{\rm min}}{M_{\odot}}>11.1$can be ruled out.
+In order to interpret the results from this test we
+show in the right panel of Figure \ref{figure:correlation_parameters} 
+the plane $\theta_{0}$-$M_{\rm min}$ for all models. There we divide
+the models into two disjoint sents: those with $\log \frac{M_{\rm
+    max}}{M_{\odot}}<12$ (blue dots) and $\log \frac{M_{\rm
+    max}}{M_{\odot}}>12$ (green dots). The colored rectangle includes
+the parameter region wich is consistent with the observational
+constraint in $\theta_{0}$. With this restriction we find that most
+models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and  $\log
+\frac{M_{\rm     min}}{M_{\odot}}>11.1$can be safely ruled out.
 
-%In general, we observe that the standard
-%deviation of the computed ACF in the subfields increases with
-%$M_{min}$ following the same trend as in Figure
-%\ref{figure:laes_dist}, as a direct consequence of cosmic variance.
-
-In figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
+In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
 for the {\tt match} method after applying the observational constraints 
-in the occupation fraction and the ACF.
-
-Finally, we also present the ACF in the case of the full SSA22
-region which has been homogeneously observed by \citep{Yamada2012}. To
-this date the observational ACF has not been reported in the
-litereature, therefore our calculations can be considered as
-predictions.
-
-In Figure X we present the results for the models. The full list of
-these correlation functions can be found in the the data repository
-for this paper in \verb"github".
-
-%The comparison between the simulated and observed ACFs is also done using
-%$\chi^2$ statistic which includes the information on the measurement
-%uncertainties and the statistical dispersio from the $15$ mock surveys
-%in the simulation
-
-%\begin{equation}
-%\chi^{2} = \sum_{\theta_i} \frac{(\xi_{\rm obs}(\theta_i) - \xi_{\rm
-%    sim}(\theta_i))^2}{\sigma_{\rm obs}^2(\theta_i) + \sigma_{\rm
-%    sim}^2({\theta_i})}, 
-%\end{equation}
-
-%where the sum is done over all the $13$ angle values $\theta_i$ where the
-%ACF has been computed. In Figure XX we plot this statistic for all the
-%models considered. In all cases $\chi^{2}<7$ which is not sufficient
-%to consider that the correlation functions from the simulations are
-%statistically different from the observational one. The constribution
-%of cosmic variance in the simulations together with the statistical
-%uncertainties make all tested models compatible with the observational
-%constraints.
-
-%From these tests we conclude that the ACF on small fields does not
-%provide additional constraints to further select models for halos
-%hosting LAEs. The reason is that
-
-%Given that the ACF reported by Hayashino et al en 2004 is taken over
-%the densest  field oserved in the SSA22 region by  Yamada et el in
-%2012 it is expected that the predicted ACF in the SSA22 region should
-%reproduce this observation. In the  left panel of figure
-%\ref{figure:correlation_match} we can see the predicted ACFs  an their
-%corresponding standard deviation over the seven fields that mock the
-%SSA22  region. It can be seen that the model with $M_min=10.6$ seems
-%to better reproduce the  Hayashino's ACF and that the corresponding
-%field is in fact an overdense field in the SSA22 region covered by
-%Yamada et al.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}
-\end{center}
-\caption{Left: The fitted parameters  ($\theta_{0}$ vs $\gamma$) of the 
-mean ACF  assuming a powerlaw behavior. Each blue dot corresponds to a
-match-model while the green dot represent the powerlaw fit of the observational
-ACF reported by \citet{Hayashino2004}.  The error bars represents the dispersion
-in each parameter over all the mock surveys for a given model and dispersion due
-to the observational error for the measured ACF by \citet{Hayashino2004}. Rigth: 
-$\theta_{0}$ vs $M_{min}$. The date is subdivided into two blocks $M_{max}<12.0$ 
-(blue) and $M_{max}>12.0$ (green). The red rectangle includes the region within
-models are consisted with the observational angular-correlation lenght
-($15<\theta_{0}<23$) as it can be deduced from the left panel. \label{figure:correlation_parameters}} 
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
-\end{center}
-\caption{Best models paramter space when both the constraints on the maximal number
-  of  consistent mocks and the occupation  fraction $f_{\rm occ}\leq
-  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth)
-  \label{fig:restriction_mock_and_f_occ_corr}} 
-\end{figure*} 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_large_correlation_selected_models.pdf}
-%\hspace{5mm}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/random_full_correlation_selected_models.pdf}
-%\end{center} 
-%\caption{ mean ACFs   and their correponding standard deviation (error
-%  bars)  of some selected models in different mass ranges over the 7
-%  subfields of the SSA22 field (left) and the entire 12 field sample
-%  (rigth) using the  random
-%  configuration. \label{figure:correlation_random} }   
-%\end{figure*}
+in the occupation fraction and the ACF. Here we consider a model
+consistent if there is an overlap of $1-sigma$ in its values for the
+correlation length $\theta_0$ and the power $\gamma$ in the
+correlation function.
 
@@
 
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
-%\includegraphics[width=0.49\linewidth,angle=0]{./plots/mytest.pdf}
-%\end{center} 
-%\caption{Spatial distribution for two mocks corresponding to the model
-%  $M_{\rm min}=$, $M_{\rm max}=$ and $f_{\rm occ}=$. All the 15
-%  different mock  surveys for this model in the {\texttt match}
-%  configuration are consistent with observations at the $P>0.05$
-%  level. The full data for all the mocks can be found in the github
-%  repository for this paper.
-%  \label{figure:spatial_distro}.}
-%\end{figure*}
+Imposing additional constraints with the maximal number of consistent
+mock surveys and the angular correlation function we end up with 50
+models out of the original 90000 models. In what follows we discuss
+the implications of the selection of these models on the escape
+fraction of Lyman $\alpha$ radiation, the stellar abundance and the
+star formation efficiency in LAEs at $z=3.1$.
 
-Considering the tightest constraints on the mock catalogs 
-with the angular correlation function and the maximal
-number of consistent mock surveys we end up with 50 models out of the
-original 90000 models.
+\subsection{Escape fraction}
 
-We find that most of the models with an occupation fraction $f_{\rm
-  occ}\leq 0.2$ are those with mean correlation lenghts within the
-observational uncertainty. Most of the models with $f_{\rm occ}$ are
-those that are consistent only when the statistical uncertainty from
-the mock cosmic variance is taken into account.
+We find that the majority ($80\%$) of the best models have a low
+ocacupation fraction $f_{\rm occ}\leq 0.4$. This preference goes in
+the same direction as the observational constraint on $f_{\rm occ}\sim
+0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}.
 
-This slight preference towards low occupations fractions is remarkably
-close to  the observational constraint $f_{\rm occ}$ derived at
-$z=2.2$ by \cite{Hayes2010}.  This estimation was based
-on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
+Their estimation was based on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
 European Southern  Observatorio (ESO) Very Large Telescope
@@
 
-%that there are 60 set of parameters of our model, out of the original
-%90000 initial models, that are consistent with the observational
-%constraints at redshift $3.1$: the distribution of the number density,
-%the inferred values for the average occupation fraction. The
-%consistency with the angular correlation, in terms of the $\chi^2$
-%statistics did not help to discard any additional models with a
-%significant degree of confidence.
+Including the information of the halo mass range size allows us
 
 These 50 models can be classified into two families of the same
-size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
+size.
+
+The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
 typically of less than $<1.0$ dex. While in the second familiy the
@@
 Appendix in Table \ref{table:models_match}.
-
-\subsection{Observational estimates for the occupation fraction}
-
-We limit the occupation fraction to
-be in the range $f_{\rm  occ}\leq 0.2$ to allow for some flexibility on the time evolution
-and the uncertainty in the dust correction used to infer the escape fraction. 
-Figure  \ref{fig:restriction_mock_and_f_occ}  shows the prefered
-models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm
-  min}-f_{\rm occ}$ for the {\tt match} and {\tt   random} methods.
-With this additional constraint between $35$ to $40$ models are
-consistent with observations, this represents a factor of $\sim 2$
-reduction. All the models with $\log_{10}M_{\rm min}\geq 11.0$ are now
-excluded and the best models are now clustered around a narrow region
-in parameter space. %The list for the model parameters is in the
-%Appendix in Table \ref{table:models_match}.
 

### 2013-06-21 code/model_cat_gen.py
bug corrected model_cat_gen.py

@@ -84,6 +84,7 @@ for w in range( n_models ):
     print m_min_s[0], m_max_s[0], f_occ_s[0]
     ID_survey_s=ID_survey_arr[model_index]
     model_prob_s=model_prob_arr[model_index]
+    print "number of mocks=",np.size(model_prob_s)
     index_prob=np.argsort(model_prob_s)
     m_min_s=m_min_s[index_prob]
     m_max_s=m_max_s[index_prob]
@@ -93,12 +94,15 @@ for w in range( n_models ):
     
     ID_index=np.where(survey_ID==ID_survey_s[-1])
     S_ID=survey_ID[ID_index]
-    n_mocks=np.size(S_ID)
+    #n_mocks=np.size(S_ID)
+    n_mocks=np.size(model_prob_s)
+    print n_mocks
     print "n_mocks=" + str(n_mocks)
     
     #n_mocks=1 #to delete
     for j in range( n_mocks ): 
-        ID_ini=S_ID[j]
+        
+        ID_ini=j*obs_surveys
         ID_end=int(ID_ini+obs_surveys)
         m_min=m_min_s[-1]
         m_max=m_max_s[-1]

### 2013-06-21 paper/ms.tex
additional paragraphs

@@
 mock surveys and the angular correlation function we end up with 50
-models out of the original 90000 models. In what follows we discuss
+models out of the initial 90000 models. In what follows we discuss
 the implications of the selection of these models on the escape
@@
 
-\subsection{Escape fraction}
+\subsection{Escape fraction and allowed halo mass range}
 
-We find that the majority ($80\%$) of the best models have a low
-ocacupation fraction $f_{\rm occ}\leq 0.4$. This preference goes in
+We find that the majority ($70\%$) of the best models have a low
+ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
 the same direction as the observational constraint on $f_{\rm occ}\sim
-0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}.
+0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
+study of observational data in a wide redshift range $0<z<6$ by
+\cite{Dijkstra2013}.
 
-Their estimation was based on blind surveys of the H$\alpha$ and Lyman $\alpha$ line with the
-European Southern  Observatorio (ESO) Very Large Telescope
-(VLT). Using corrections by extinction to obtain an estimate for the
-intrinsic H$\alpha$ luminosity, and using values for the theoretical
-expectation of the ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
+The observational estimation by \cite{Hayes2012} was based on blind
+surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
+extinction to obtain an estimate for the intrinsic H$\alpha$
+luminosity, and using values for the theoretical expectation of the
+ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
 the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-esc}=(10.7\pm 2.8)\%$ if a different dust correction is used. The
-authors show that the luminosity function for LAEs at $z=2.2$ is
+  esc}=(10.7\pm 2.8)\%$ if a different dust correction is used.
+
+They also showed that that the luminosity function for LAEs at $z=2.2$ is
 consistent with the escape fraction being constant for every galaxy
@@
 Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$. For the cosmological parameters
-used in this \documentname the age of the universe between $z=3.1$ and
-$z=2.2$ has changed by $\sim 1$ Gyr. We assume that the physical
-conditions that determine the escape fraction $f_{\rm esc}$ and the
-occupation fraction $f_{\rm  occ}$ remain similar over that time
-scale.
+fraction to be $f_{\rm occ}=0.10$.
 
-Including the information of the halo mass range size allows us
+The results by \cite{Dijkstra2013} use a similar principle. They
+compared observationally dereived star formation functions to LAE
+luminosity functions. At $z\sim 3.0$ they derive an affective escape
+fraction of $f_{\rm esc}=(17\pm 5)\%$, which in turn using the same
+arguments in \cite{Hayes2010} could be interpreted as an occupation
+fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of our method
+the fact that we find that most of the consistent models show a low
+occupation fraction.
 
-These 50 models can be classified into two families of the same
-size.
+The study of the escape farction is also complementary to the size of
+the halo mass range $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm
+  min}$for LAEs. All the successful model we have found can be 
+split into three families. 
+\begin{itemize}
+\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
+  dex: 24 models.
+\item[(2)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
+\item[(3)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
+  models
+\end{itemize}
 
-The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
-typically of less than $<1.0$ dex. While in the second familiy the
-extent $>1.0$ dex. In the first case the minimum halo mass is found to
-be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
-in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
-are compatible with the observational contraints. In what follows we
-discuss the implications of the existence of these two families of
-models.
+There is a clear majority of models with a narrow $\Delta M\leq
+1$, such models imply that there is a cut for lower and higher halo masses
+that render inefficient the presence and/or detection of LAEs.  A cut
+a lower masses can be readily interepreted in terms of the minimal halo star
+formation rate needed to produce the necessary \lya luminosity to be
+above a given detection threshold.
 
-When we additional include the ACF constraint we find that only models with 
-$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
-are now consistent with observations.
+The cut at higher halo masses requires a different explanation. A
+possible interpretation can be made in terms of a lower escape
+fraction of \ly radiation in massive systems. There are detailed models for
+radiative transfer that support the idea that massive galaxies with
+higher metallicities have larger dust contents than lower mass
+systems, which due to the resonant nature of the \ly line are enough
+to produce high absorption of \ly photons but not of continuum or
+other non-resonant lines.
 
-Including all the observational constraints we find that only between $15$ to $20$ 
-models reproduces observations. The list for the model parameters is in the
-Appendix in Table \ref{table:models_match}.
+This preference for narrow $\Delta M$ ranges for hosting LAEs together
+with the total absence of reasonable models with $M_{\rm max}>
+10^{12}$\hMsun shows that our models supports theoretical insights
+where the most massive systems are not bright \ly sources.
 
-\subsection{Implications for galaxy formation models}
+%The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
+%typically of less than $<1.0$ dex. While in the second familiy th
+%extent $>1.0$ dex. In the first case the minimum halo mass is found to
+%be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
+%in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
+%are compatible with the observational contraints. In what follows we
+%discuss the implications of the existence of these two families of
+%models.  
+%When we additional include the ACF constraint we find that only models with 
+%$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
+%are now consistent with observations.
+
+%Including all the observational constraints we find that only between $15$ to $20$ 
+%models reproduces observations. The list for the model parameters is in the
+%Appendix in Table \ref{table:models_match}.
+
+\subsection{Models in the context of abundance matching}
+
+The abundance matching methods, whereby a stellar mass is associated
+to a halo mass in order to reproduce various luminosity functions, can
+be used to interpret the results we have obtained so far.
 

### 2013-06-21 paper/ms.tex
discussion in terms of abundance matching

@@
 
-\subsection{Models in the context of abundance matching}
+\subsection{In the context of abundance matching models}
 
-The abundance matching methods, whereby a stellar mass is associated
-to a halo mass in order to reproduce various luminosity functions, can
-be used to interpret the results we have obtained so far.
+Using abundance matching methods throughout cosmic time from redshifts
+$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
+formation efficiency (star formation rate divided by the stellar mass)
+presents a clear maximum around $10^{11.7}$\Msun at all redshifts
+$z<4$.
 
-In the case of a narrow of masses to host LAEs the upper masses are
-bound to be $M_{\rm max}< 10^{11.5}$\hMsun as it is show in Figure
-\ref{figure:mock_and_f_occ}. For halos more massive than this bound it
-is naturally expected that the galaxies can be observed as Lyman Break
-Galaxies (LBGs). This would imply that not all the bright LBGs can
-detected as a LAE.
+This mass scale is strictly superior to the all the $M_{\rm max}$
+values allowed in the consistent models. Using the results published
+in \cite{Behroozi2013a} we find that the typical stellar mass in halos
+of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
+their star formion rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$. These halo
+masses actually correspond to the lower bound of what is computed in
+the abundance matching model in order to fit the observational data
+for the stellar mass function.
 

### 2013-06-21 code/correlation_statistic.py
correlation_statistic.py updated- plot saved directly in pdf format an in paper/plots dir

@@ -3,6 +3,7 @@ import pylab as P
 import matplotlib.collections as collections
 from scipy import stats
 from scipy import optimize as op
+plot_dir="../paper/plots/"
 
 #defining the power-law function to fit the correlation function
 powerlaw = lambda x, amp, index: (x/amp)**(index)
@@ -112,11 +113,11 @@ ro_plot.set_xlabel(r'$\theta_{0}$', fontsize=20)
 ro_plot.set_ylabel(r"$\gamma$",fontsize=20)
 ro_plot.set_title("Angular Correlation parameters. Full SSA22 field",fontsize=20)
 ro_plot.set_title("Angular Correlation parameters. Match survey",fontsize=20)
-plot_name="power_law_correlation.png"
+plot_name=plot_dir +"power_law_correlation.pdf"
 ro_plot.legend(shadow=False,loc=2)
 
 
-fig2.savefig(plot_name)
+fig2.savefig(plot_name,format="pdf")
 
 
 fig3=P.figure()
@@ -130,11 +131,11 @@ mmin_plot.set_xlabel(r"$M_{min}$",fontsize=20)
 mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Full SSA22 Field",fontsize=20)
 mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Match Survey",fontsize=20)
 
-plot_name="mmin_vs_correlation.png"
+plot_name=plot_dir +"mmin_vs_correlation.pdf"
 mmin_plot.legend(shadow=False,loc=2)
 collection = collections.BrokenBarHCollection.span_where(m_min_m, ymin=15, ymax=23, where=ro>0,  facecolor='red', alpha=0.5)
 mmin_plot.add_collection(collection)
-fig3.savefig(plot_name)
+fig3.savefig(plot_name,format="pdf")
 
 
 corr_index=np.where(( (ro_max>(ro-ro_err)) & ((ro+ro_err)>ro_min) ) & ( ((slope+slope_err)>slope_min) & ((slope-slope_err)<slope_max) )== True) #and ro<ro_max) #and slope_min<slope<slope_max)
@@ -174,9 +175,9 @@ mass_plot.set_title(r"Observationally consistent models. Full Field",fontsize=20
 mass_plot.set_title(r"$\log M_{min}$ vs $\Delta log M$. Observationally consistent models",fontsize=20)
[…]

### 2013-06-23 paper/ms.tex
thinking

@@
 
-\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Using cosmic
-  variance to constrain the dark matter halo mass of Lyman-alpha
-  emitting galaxies at $z$=3.1}
+\title[Halo mass and occupation fraction for LAEs at $z=3.1$]{Using cosmic
+  variance to constrain the dark matter halo mass and occupation
+  fraction of Lyman-alpha emitting galaxies at $z$=3.1}
 
@@
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
-$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile}
+$^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el
+Observatorio 1515, Santiago, Chile}
 
@@
 of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-their star formion rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$. These halo
-masses actually correspond to the lower bound of what is computed in
-the abundance matching model in order to fit the observational data
-for the stellar mass function.
+their star formion rate is in the range $0.6\pm 0.2$ Msun
+yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
+lower bound of what is computed in the abundance matching model in
+order to fit the observational data for the stellar mass function
+based on the obervations of Lyman Break Galaxies.
 
@@
 
-... Intrinsic emission and escape fraction.
+%... Intrinsic emission and escape fraction.
 
-... Star formation rate efficiency at this redshift.
+%... Star formation rate efficiency at this redshift.
 
-... Mass dependence of the escape fraction.
+%... Mass dependence of the escape fraction.
 
-... Discuss all this in terms of the star formation efficiency in
+%... Discuss all this in terms of the star formation efficiency in
 Behroozi et al.

### 2013-06-24 paper/ms.tex
advances

@@
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
-\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$~}\fi}}
 \newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
@@
 We also maximize the number of mocks surveys consistent with
+Our most important results is that, unlike previous studies, a pure
+clustering analysis cannot fully constraint the halo occupation
+fraction for LAEs.
+
+Most of the models have a narrow mass range $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}< 1.0$ dex and a low
+occupation fraction $f_{\rm occ}\leq 0.3$.
+
 observations and impose consistency with the angular correlation
@@
 
-We find that the majority ($70\%$) of the best models have a low
+We find that $70\%$ of the best models have a low
 ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
@@
 0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
-study of observational data in a wide redshift range $0<z<6$ by
-\cite{Dijkstra2013}.
+study of observational data in a wide redshift range $0<z<6$ 
+\citep{Dijkstra2013}.
 
-The observational estimation by \cite{Hayes2012} was based on blind
+The observational estimation by \cite{Hayes2010} was based on blind
 surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
@@
 
-The results by \cite{Dijkstra2013} use a similar principle. They
-compared observationally dereived star formation functions to LAE
+\cite{Dijkstra2013} use a similar principle to derive their results. They
+compared observationally derived star formation functions to LAE
 luminosity functions. At $z\sim 3.0$ they derive an affective escape
-fraction of $f_{\rm esc}=(17\pm 5)\%$, which in turn using the same
-arguments in \cite{Hayes2010} could be interpreted as an occupation
-fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of our method
-the fact that we find that most of the consistent models show a low
-occupation fraction.
+fraction of $f_{\rm esc}=(17\pm 5)\%$ could be interpreted as an
+occupation fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of
+our method the fact that we find that most of the consistent models
+show a low occupation fraction.
 
-The study of the escape farction is also complementary to the size of
-the halo mass range $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm
-  min}$for LAEs. All the successful model we have found can be 
-split into three families. 
+A complementary perspective to the range of the allowed values for the
+escape fraction is the quantification of the allowed halo mass range
+$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$for LAEs. In this
+respect, we find that all the successful models can be  split into
+three families:
+
 \begin{itemize}
@@
   dex: 24 models.
-\item[(2)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
-\item[(3)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
+\item[(2)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
   models
+\item[(3)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
 \end{itemize}
@@
 There is a clear majority of models with a narrow $\Delta M\leq
-1$, such models imply that there is a cut for lower and higher halo masses
+1$. Such models imply that there is a cut for lower and higher halo masses
 that render inefficient the presence and/or detection of LAEs.  A cut
-a lower masses can be readily interepreted in terms of the minimal halo star
+at the low mass end can be readily interepreted in terms of the minimal halo star
 formation rate needed to produce the necessary \lya luminosity to be
-above a given detection threshold.
+above a given detection threshold.  However, under the reasonable assumption of star formation rate
+increainsng with halo mass, the cut at higher halo masses requires a
+different explanation.
 
-The cut at higher halo masses requires a different explanation. A
-possible interpretation can be made in terms of a lower escape
+A possible interpretation can be made in terms of a drecreasing escape
 fraction of \ly radiation in massive systems. There are detailed models for
@@
 10^{12}$\hMsun shows that our models supports theoretical insights
-where the most massive systems are not bright \ly sources.
+where the most massive systems are not bright \ly sources \citep{ForeroRomero2012}.
 
-%The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
-%typically of less than $<1.0$ dex. While in the second familiy th
-%extent $>1.0$ dex. In the first case the minimum halo mass is found to
-%be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
-%in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
-%are compatible with the observational contraints. In what follows we
-%discuss the implications of the existence of these two families of
-%models.  
-%When we additional include the ACF constraint we find that only models with 
-%$\log_{10}M_{\rm min}\leq 11.0$ and $\log_{10}M_{\rm max}\leq 12.0$ 
-%are now consistent with observations.
+\subsection{Comparison to other clustering estimates}
 
-%Including all the observational constraints we find that only between $15$ to $20$ 
-%models reproduces observations. The list for the model parameters is in the
-%Appendix in Table \ref{table:models_match}.
+Since the observational estimates based on the ACF infered from photometric
+measurements in the Extended Chandra Deep Field South
+\citep{Gawiser07} it is a well accepted fact that the median dark
+matter masses of halos hosting LAEs is $\log_{10}M_{\rm
+  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
+fraction of $1-10\%$.  Our results are in a good agrement with those estimates for the
+host mass. This is not unexepected given that we have also
+required consistency with ACF measurements.
 
-\subsection{In the context of abundance matching models}
+The novelty in our approach is that we have a detailed estimate for 
+host halo mass range. Following the numbers shown for the three
+families in the previous section, we see that two thirds of the best models
+have a narrow mass range, less than $<1.0$ dex, out of the $2.5$ dex
+spanned by dark matter halos at that redshift. Only one fourth of the
+models indicate a wide mass range with $>1.0$dex.
 
-Using abundance matching methods throughout cosmic time from redshifts
-$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
-formation efficiency (star formation rate divided by the stellar mass)
-presents a clear maximum around $10^{11.7}$\Msun at all redshifts
-$z<4$.
+As a byproduct of our results, we are now able to demonstrate that a
+simple clustering analysis is not enough to rule out models with a
+high occupation fraction $f_{\rm occ}>0.3$, they represent almost
+one fourth of our best models, coinciding with a wide range in halo
+masses $\Delta M>1.0$ dex.
 
-This mass scale is strictly superior to the all the $M_{\rm max}$
-values allowed in the consistent models. Using the results published
-in \cite{Behroozi2013a} we find that the typical stellar mass in halos
-of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-their star formion rate is in the range $0.6\pm 0.2$ Msun
-yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
-lower bound of what is computed in the abundance matching model in
-order to fit the observational data for the stellar mass function
-based on the obervations of Lyman Break Galaxies.
+%\subsection{In the context of abundance matching models}
 
-We have the opposite situation in the second familiy of models. If
-we have a wide range in halo masses, where the upper end of the halo
-masses can be considered as observed LAEs, one can expect that bright
-LBGs will have a correspondence as observed LAEs. The most interesting
-aspect is that there is a clear cut in the minimal mass that can be
-attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
-constraint on the relationship between the minimum star formation rate
-required to be observed as a LAE and this minimal halo mass.
+%Using abundance matching methods throughout cosmic time from redshifts
+%$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
+%formation efficiency (star formation rate divided by the stellar mass)
+%presents a clear maximum around $10^{11.7}$\Msun at all redshifts
+%$z<4$.
 
-%... Intrinsic emission and escape fraction.
+%This mass scale is strictly superior to the all the $M_{\rm max}$
+%values allowed in the consistent models. Using the results published
+%in \cite{Behroozi2013a} we find that the typical stellar mass in halos
+%of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
+%their star formation rate is in the range $0.6\pm 0.2$ Msun
+%yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
+%lower bound of what is computed in the abundance matching model in
+%order to fit the observational data for the stellar mass function
+%based on the obervations of Lyman Break Galaxies.
 
-%... Star formation rate efficiency at this redshift.
+%Most of the prefered models have a halo mass range with $M_{\rm
+%  max}<10^{11.4}$\hMsun. This suggests that a detailed and careful
+%study of the spectral properties of LAEs coupled to the kind of
+%analysis performed in this paper can be a guide in the study of the
+%properties of low mass dark matter halos at $z=3.1$, extending the
+%capabilities of abundance matching methods.
 
-%... Mass dependence of the escape fraction.
-
-%... Discuss all this in terms of the star formation efficiency in
-Behroozi et al.
-
-\subsection{Implications for large LAEs surveys}
-
-... The bias for the preferred halo mass.
-
-... The scale at which cosmic variance drops.
-
-... This can be observationally tested with HETDEX.
+%we have a wide range in halo masses, where the upper end of the halo
+%masses can be considered as observed LAEs, one can expect that bright
+%LBGs will have a correspondence as observed LAEs. The most interesting
+%aspect is that there is a clear cut in the minimal mass that can be
+%attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
+%constraint on the relationship between the minimum star formation rate
+%required to be observed as a LAE and this minimal halo mass.
 
@@
 \section{Conclusions}
-In this \documentname we constrain the preferred mass for dark matter
-halos hosting Lyman Alpha Emitters at a redshift $z=3.1$. We use a
-method that matches the cosmic variance in the surface
-density number of LAEs between mock and real observations. The mock
-catalogs are based on a simplified model with three basic parameters: the halo
-mass range where LAEs can be found, $M_{\rm   min}<M_{\rm h}<M_{\rm
-  max}$, and the fraction of the halos in thisrange that are actully
-occupied, $f_{\rm occ}$. After a thorugh exploration of the parameter
-space we are able to constrain the mass range of dark matter halos
-hosting LAEs to be in the range $<M_{\rm   h}<$ and a corresponding
-occupation fraction that escales as $f_{\rm   occ} = M_{\rm min}$.
 
-We use three additional constraints to reduce the allowed
-range of models. The first imposes a tighter criterion to consider a
-model succesful, namely that all the mock surveys for a given model
-must be consistent with observations. This restriction narrows down
-the allowed range of models to be.
+In this \documentname we constrain the preferred dark matter mass
+and occupation fraction for halos hosting Lyman Alpha Emitters at
+redshift $z=3.1$. We use a method that matches the cosmic variance in the surface
+density number of LAEs between mock and real observations and provides
+consistent results with observational estimates for the angular
+correlation function. The mock catalogs are based on a simplified
+model with three basic parameters: the halo mass range where LAEs can
+be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
+the halos in this range that are actully occupied, $f_{\rm occ}$. After
+a thorough exploration of the parameter space we find that wide
+variety of models are consistent with the observational constraints,
+where only a minority has been considered so far in the
+literature. Out of $9000$ initial combinations for the model
+parameters we end up with $49$ sucessful arrangement of parameters.
 
-The second constraint is based on the observational results that high
-redshift LAEs have a bulk Lyman alpha escape fraction of $XX$ which
-can be also interepreted as an average occupation fraction of $XX$.
+These parameter sets can be split into three families depending the mass range
+$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
+occupation fraction $f_{\rm occ}$. The first family is narrow both in
+$\Delta M$ and $f_{\rm occ}$, a second familiy is only narrow in
+$\Delta M$ and the third is only narrow in $f_{\rm occ}$.
 
-Including additional observational constraints on the occupation
-fraction allows us to reduce the range of allowed halo masses to be in
-a narrower range of $<M_{\rm h}<$. Including the information from the
-angular correlation function (ACF) does not allows us to impose
-further constraints. This is due to the scatter in the ACF due to the
-cosmic variance on the field observed by XXX
+Analysis based in observations have been only able to describe models
+in the third family, but have so far missed the possibility of the first
+two: a narrow mass range and any value for the escape fraction.
 
-We simulation allows us to extract $210$ sub-boxes each of which has a
-comparable volume to the individual fields of view observed by
-\cite{Yamada2012}. The comparison of the observed number density
-distribution against the results from our model is based on three
-different ways of constructing mock surveys. The first reproduces the
-spatial correlation between the $12$ observational fields ({\texttt
-  match}), the second breaks this spatial correlation while keeping
-the number of fields ({\texttt random}) and the third one simply
-includes all the $210$ sub-boxes ({\texttt full}). We find that the
-methods {\texttt match} and {\texttt random} allow a larger set of
-models than the {{\texttt random}} method. We do not find a
-significant difference between the two first methods.
+Many different observational estimates on the occupation fraction of
+LAEs at $z=3$ suggest that the occupation fraction must be low $f_{\rm
+  occ}<0.2$. We find that the first and most numerous family of models
+is consistent with this suggestion, where also a narrow range for the
+halo mass $\Delta M<1.0$ is prefered.
 
@@
 10.4& 10.7& 0.1\\
+10.5& 10.6& 0.3\\
 10.5& 10.9& 0.1\\
 10.5& 11.0& 0.1\\
+10.6& 10.8& 0.2\\
 10.6& 11.2& 0.1\\
@@
 10.6& 11.6& 0.1\\
-10.6& 11.7& 0.1\\
-10.6& 10.8& 0.2\\
 10.7& 11.0& 0.2\\
@@
 10.8& 11.4& 0.2\\
+10.9& 11.3& 0.3\\
 10.9& 11.7& 0.2\\
@@
 10.9& 11.9& 0.2\\
-%10.9& 12.0& 0.2\\
-%10.9& 12.1& 0.2\\
-%10.9& 12.2& 0.2\\
-%10.9& 12.3& 0.2\\
-%10.9& 12.4& 0.2\\
-%10.9& 12.5& 0.2\\
-%10.9& 12.6& 0.2\\
-%10.9& 12.7& 0.2\\
-%10.9& 12.8& 0.2\\
-%10.9& 12.9& 0.2\\
-%10.9& 13.0& 0.2\\\hline\hline
+11.0& 11.6& 0.3\\
+11.0& 11.7& 0.3\\
+11.0& 11.8& 0.3\\
+11.0& 12.0& 0.3\\\hline\hline
 \end{tabular}
 \end{center}
-\caption{List of model parameters for the best models that have all
-  mock surveys consistent with observations and an occupation
-  fraction $f_{\rm occ}\leq 0.2$. This corresponds to the {\texttt
-    match} method to construct the mock surveys. \label{table:models_match}. }
+\caption{\label{table:thirdfamily}List of parameters for the first family of models. Narrow
+  mass range $\Delta M\leq 1.0$dex and low occupation fraction $f_{\rm occ}\leq 0.3$.}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{ccc}\hline\hline
+$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
+10.6& 10.7& 0.4\\
+10.7& 10.8& 0.5\\
+10.8& 10.9& 0.6\\
+10.8& 11.0& 0.4\\
+10.9& 11.0& 0.8\\
+10.9& 11.0& 0.9\\
+10.9& 11.1& 0.5\\
+11.0& 11.1& 1.0\\
+11.0& 11.4& 0.4\\
+11.1& 11.3& 0.7\\
+11.1& 11.7& 0.4\\
+11.2& 11.5& 0.7\\
+11.2& 11.6& 0.6\\
+11.2& 11.9& 0.5\\\hline\hline
+\end{tabular}
+\end{center}
+\caption{\label{table:secondfamily}List of parameters for the second family of models. Narrow
+  mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{ccc}\hline\hline
+$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
+10.6& 11.7& 0.1\\
+10.9& 12.1& 0.2\\
+10.9& 12.2& 0.2\\
+10.9& 12.3& 0.2\\
+10.9& 12.4& 0.2\\
+10.9& 12.5& 0.2\\
+10.9& 12.6& 0.2\\
+10.9& 12.7& 0.2\\
+10.9& 12.8& 0.2\\
+10.9& 12.9& 0.2\\
+10.9& 13.&0 0.2\\\hline\hline
+\end{tabular}
+\end{center}
+\caption{\label{table:thirdfamily}List of parameters for the third family of models. Broad
+  mass range $\Delta M >1.0$dex and low occupation fraction $f_{\rm occ}\leq0.3$.}
 \end{table}

### 2013-06-25 paper/ms.tex
reordering, shaping up the conclusions

@@
 
-\section{Additional Constraints}
-
 \begin{figure*}
@@
 
-In this section we consider two additional constraints on the models
-we accept as succesul. First we take models with the
-highest possible number of mock surveys consistent with
-observations. Second by comparing the angular correlation function
-against observational constraints by \cite{Hayashino2004}.
+In this next subsections we consider two additional constraints on the models
+we accept as succesul. First we take models with the highest possible
+number of mock surveys consistent with observations. Second by
+comparing the angular correlation function against observational
+results by \cite{Hayashino2004}.
 
@@
 
-As an additional observational constraint we requiring that the models
-selected in the previous section must be compatible with the
+We now make a further selection to the models compatible with the
 observational angular correlation function (ACF). The measurementens
@@
 
-Imposing additional constraints with the maximal number of consistent
-mock surveys and the angular correlation function we end up with 50
-models out of the initial 90000 models. In what follows we discuss
-the implications of the selection of these models on the escape
-fraction of Lyman $\alpha$ radiation, the stellar abundance and the
-star formation efficiency in LAEs at $z=3.1$.
+From the matching of number density statistics we find that all
+the succesful models have halos in the range
+$10^{10}-10^{12}$. Including strict criteria and the information from
+the angular correlation function does not narrow this mass range, but
+help us nevertheless to narrow down the number of good models.
 
-\subsection{Escape fraction and allowed halo mass range}
+matter masses of halos hosting LAEs is $\log_{10}M_{\rm
+  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
+fraction of $1-10\%$.  Our results are in a good agrement with those estimates for the
+host mass. This is not unexepected given that we have also
+required consistency with ACF measurements.
+
+Together with the escape fraction $f_{\rm occ}$, quantifying the halo mass range
+$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$ for the succesful
+models help us to classify them into three families:
+
+\begin{itemize}
+\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
+  dex: 24 models.
+\item[(2)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
+  models
+\item[(3)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
+\end{itemize}
+
+There is a clear majority of models with a narrow $\Delta M\leq
+1$. Such models imply that there is a cut for lower and higher halo
+masses that render inefficient the presence and/or detection of LAEs.
+A cut at the low mass end can be readily interepreted in terms of the
+minimal halo star formation rate needed to produce the necessary \lya
+luminosity to be above a given detection threshold.  However, under the reasonable assumption of star formation rate
+increainsng with halo mass, the cut at higher halo masses requires a
+different explanation.
+
+A possible interpretation can be made in terms of a drecreasing escape
+fraction of \ly radiation in massive systems. There are detailed models for
+radiative transfer that support the idea that massive galaxies with
+higher metallicities have larger dust contents than lower mass
+systems, which due to the resonant nature of the \ly line are enough
+to produce high absorption of \ly photons but not of continuum or
+other non-resonant lines.
+
+This preference for narrow $\Delta M$ ranges for hosting LAEs together
+with the total absence of reasonable models with $M_{\rm max}>
+10^{12}$\hMsun shows that our models supports theoretical insights
+where the most massive systems are not bright \ly sources \citep{ForeroRomero2012}.
 
 We find that $70\%$ of the best models have a low
-ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
+occupation fraction $f_{\rm occ}\leq 0.3$.
+
+With all the observational constraints we we end up with 50
+models out of the initial 90000 combination of parameters. In what
+follows we classify the resulting models into three families and
+discuss them under the light of previous observational analysis from
+blind galaxy surveys and other LAEs clustering analysis.
+
+\subsection{Constraints from blind surveys}
+
+This preference goes in
 the same direction as the observational constraint on $f_{\rm occ}\sim
@@
 show a low occupation fraction.
-
-A complementary perspective to the range of the allowed values for the
-escape fraction is the quantification of the allowed halo mass range
-$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$for LAEs. In this
-respect, we find that all the successful models can be  split into
-three families:
-
-\begin{itemize}
-\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
-  dex: 24 models.
-\item[(2)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
-  models
-\item[(3)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
-\end{itemize}
-
-There is a clear majority of models with a narrow $\Delta M\leq
-1$. Such models imply that there is a cut for lower and higher halo masses
-that render inefficient the presence and/or detection of LAEs.  A cut
-at the low mass end can be readily interepreted in terms of the minimal halo star
-formation rate needed to produce the necessary \lya luminosity to be
-above a given detection threshold.  However, under the reasonable assumption of star formation rate
-increainsng with halo mass, the cut at higher halo masses requires a
-different explanation.
-
-A possible interpretation can be made in terms of a drecreasing escape
-fraction of \ly radiation in massive systems. There are detailed models for
-radiative transfer that support the idea that massive galaxies with
-higher metallicities have larger dust contents than lower mass
-systems, which due to the resonant nature of the \ly line are enough
-to produce high absorption of \ly photons but not of continuum or
-other non-resonant lines.
-
-This preference for narrow $\Delta M$ ranges for hosting LAEs together
-with the total absence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun shows that our models supports theoretical insights
-where the most massive systems are not bright \ly sources \citep{ForeroRomero2012}.
 
@@
 $\Delta M$ and $f_{\rm occ}$, a second familiy is only narrow in
-$\Delta M$ and the third is only narrow in $f_{\rm occ}$.
+$\Delta M$ and the third is narrow in $f_{\rm occ}$ and broad in
+$\Delta M$.
 
-Analysis based in observations have been only able to describe models
-in the third family, but have so far missed the possibility of the first
-two: a narrow mass range and any value for the escape fraction.
+All the halo mass ranges in the best models fall into the broad
+results based in observations, which have been able to describe models
+in the third family, but have so far missed all the possible
+models. In particular, previous analysis did not consider the first
+two families: a narrow mass range and any value for the escape fraction.
 
-Many different observational estimates on the occupation fraction of
-LAEs at $z=3$ suggest that the occupation fraction must be low $f_{\rm
-  occ}<0.2$. We find that the first and most numerous family of models
-is consistent with this suggestion, where also a narrow range for the
-halo mass $\Delta M<1.0$ is prefered.
+In the case of narrow mass models there are various cases with $\Delta
+M=0.1$dex. Taken at face value, a possible confirmation of these kind of models
+can be considered a challenge to explain relatively high star
+formation ratesm
 

### 2013-06-26 paper/ms.tex
in better shape for the discussion

@@
 
-From the matching of number density statistics we find that all
-the succesful models have halos in the range
-$10^{10}-10^{12}$. Including strict criteria and the information from
-the angular correlation function does not narrow this mass range, but
-help us nevertheless to narrow down the number of good models.
+Matching the galaxy surface number density statistics sets the median
+mass of all succesful models in the range $10^{10}-10^{12}$
+\hMsun. Including more strict criteria on the number of mock surveys
+that must be consistent with those observations and additional
+information from the angular correlation function greatly reduces the
+number of possible models. We end up with $\sim 50$ models out of the
+initial 90000 possible combination of parameters.
 
-matter masses of halos hosting LAEs is $\log_{10}M_{\rm
-  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
-fraction of $1-10\%$.  Our results are in a good agrement with those estimates for the
-host mass. This is not unexepected given that we have also
-required consistency with ACF measurements.
-
-Together with the escape fraction $f_{\rm occ}$, quantifying the halo mass range
-$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$ for the succesful
-models help us to classify them into three families:
+We find that for the physical interpretation of these models it is
+useful to do it in terms of the size of halo mass range, using the
+variable $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$, together
+with the escape fraction $f_{\rm occ}$. These two variables help us
+build a classification of all the successful models into three families:
 
@@
 There is a clear majority of models with a narrow $\Delta M\leq
-1$. Such models imply that there is a cut for lower and higher halo
+1$, compared to the $2.5$dex of halo mass available for occupation at
+that redshift. Such models imply that there is a cut at lower and higher halo
 masses that render inefficient the presence and/or detection of LAEs.
-A cut at the low mass end can be readily interepreted in terms of the
+
+At the low mass end, such cut can be readily interepreted in terms of the
 minimal halo star formation rate needed to produce the necessary \lya
-luminosity to be above a given detection threshold.  However, under the reasonable assumption of star formation rate
-increainsng with halo mass, the cut at higher halo masses requires a
-different explanation.
+luminosity to be above a given detection threshold.  However, under
+the reasonable assumption of star formation rate increainsng with halo
+mass, the cut at higher halo masses requires a different explanation.
 
-A possible interpretation can be made in terms of a drecreasing escape
+One possible interpretation can be made in terms of a drecreasing escape
 fraction of \ly radiation in massive systems. There are detailed models for
@@
 
-This preference for narrow $\Delta M$ ranges for hosting LAEs together
+The preference for narrow $\Delta M$ ranges to hosting LAEs together
 with the total absence of reasonable models with $M_{\rm max}>
 10^{12}$\hMsun shows that our models supports theoretical insights
-where the most massive systems are not bright \ly sources \citep{ForeroRomero2012}.
+where the most massive systems are not bright \ly sources
+\citep{ForeroRomero2012}.
 
-We find that $70\%$ of the best models have a low
-occupation fraction $f_{\rm occ}\leq 0.3$.
+\subsection{Comparison against results from blind surveys}
 
-With all the observational constraints we we end up with 50
-models out of the initial 90000 combination of parameters. In what
-follows we classify the resulting models into three families and
-discuss them under the light of previous observational analysis from
-blind galaxy surveys and other LAEs clustering analysis.
-
-\subsection{Constraints from blind surveys}
-
-This preference goes in
-the same direction as the observational constraint on $f_{\rm occ}\sim
-0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
-study of observational data in a wide redshift range $0<z<6$ 
-\citep{Dijkstra2013}.
+We also find that $70\%$ of the best models are found in families (1)
+and (2), with a low occupation fraction $f_{\rm occ}\leq 0.3$. This
+preference goes in the same direction as the observational constraint
+on $f_{\rm occ}\sim 0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}
+and recent theoretical study of observational data in a wide redshift
+range $0<z<6$  \citep{Dijkstra2013}.
 
@@
 
-\cite{Dijkstra2013} use a similar principle to derive their results. They
+\cite{Dijkstra2013} used a similar principle to derive their results. They
 compared observationally derived star formation functions to LAE
@@
 
-Since the observational estimates based on the ACF infered from photometric
-measurements in the Extended Chandra Deep Field South
-\citep{Gawiser07} it is a well accepted fact that the median dark
-matter masses of halos hosting LAEs is $\log_{10}M_{\rm
+Observational based on the ACF infered from photometric measurements
+in the Extended Chandra Deep Field South have shown that the median
+dark matter masses of h los hosting LAEs is $\log_{10}M_{\rm
   med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
-fraction of $1-10\%$.  Our results are in a good agrement with those estimates for the
-host mass. This is not unexepected given that we have also
-required consistency with ACF measurements.
+fraction of $1-10\%$  \citep{Gawiser07}.  Our results are in a general
+good agrement with those estimates for the host mass. This is not
+completeley unexepected given that we have also required consistency
+with ACF measurements.
 
 The novelty in our approach is that we have a detailed estimate for 
-host halo mass range. Following the numbers shown for the three
-families in the previous section, we see that two thirds of the best models
-have a narrow mass range, less than $<1.0$ dex, out of the $2.5$ dex
-spanned by dark matter halos at that redshift. Only one fourth of the
-models indicate a wide mass range with $>1.0$dex.
+host halo mass range together with the escape fraction. This allows us
+to demonstrate that the halo mass range could be very narrow $\Delta M <
+0.2$dex, something that cannot be inferred from ACF analysis
+alone.
 
-As a byproduct of our results, we are now able to demonstrate that a
-simple clustering analysis is not enough to rule out models with a
-high occupation fraction $f_{\rm occ}>0.3$, they represent almost
-one fourth of our best models, coinciding with a wide range in halo
-masses $\Delta M>1.0$ dex.
+WE also find interesting that ACF analsys is also not enough to rule
+out models with a high occupation fraction $f_{\rm occ}>0.3$, which
+represent almost one fourth of our best models, coinciding with a wide
+range in halo masses $\Delta M>1.0$ dex. These models can only be
+considered unfavorable based on a different set of observations as we
+have described in the previous subsection.
 
-%\subsection{In the context of abundance matching models}
+\subsection{In the context of abundance matching models}
 
-%Using abundance matching methods throughout cosmic time from redshifts
-%$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
-%formation efficiency (star formation rate divided by the stellar mass)
-%presents a clear maximum around $10^{11.7}$\Msun at all redshifts
-%$z<4$.
+Considering the additional evidence for a low escape fraction we can
+say that the prefered models are in families (1) and (2) with a
+clear majority composed by those with narrow mass range and low occupation
+fraction.
 
-%This mass scale is strictly superior to the all the $M_{\rm max}$
-%values allowed in the consistent models. Using the results published
-%in \cite{Behroozi2013a} we find that the typical stellar mass in halos
-%of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-%their star formation rate is in the range $0.6\pm 0.2$ Msun
-%yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
-%lower bound of what is computed in the abundance matching model in
-%order to fit the observational data for the stellar mass function
-%based on the obervations of Lyman Break Galaxies.
+Using abundance matching methods throughout cosmic time from redshifts
+$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
+formation efficiency (star formation rate divided by the stellar mass)
+presents a clear maximum around $10^{11.7}$\Msun at all redshifts
+$z<4$.
 
-%Most of the prefered models have a halo mass range with $M_{\rm
-%  max}<10^{11.4}$\hMsun. This suggests that a detailed and careful
-%study of the spectral properties of LAEs coupled to the kind of
-%analysis performed in this paper can be a guide in the study of the
-%properties of low mass dark matter halos at $z=3.1$, extending the
-%capabilities of abundance matching methods.
+This mass scale is strictly superior to the great majority of  $M_{\rm max}$
+values allowed in the models with low escape fraction. Using the results published
+in \cite{Behroozi2013a} we find that the typical stellar mass in halos
+of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
+their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$.
+This halo mass range around $10^{11.4}$ \hMsun is the lower bound of
+what is computed in the abundance matching model in order to fit the
+observational data for the stellar mass function based on the
+obervations of Lyman Break Galaxies.
 
-%we have a wide range in halo masses, where the upper end of the halo
-%masses can be considered as observed LAEs, one can expect that bright
-%LBGs will have a correspondence as observed LAEs. The most interesting
-%aspect is that there is a clear cut in the minimal mass that can be
-%attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
-%constraint on the relationship between the minimum star formation rate
-%required to be observed as a LAE and this minimal halo mass.
+All of the prefered models have a halo mass range with $M_{\rm
+  min}<10^{11.4}$\hMsun. This suggests that a detailed and careful
+study of the spectral properties of LAEs coupled to the kind of
+analysis performed in this paper can be a guide in the study of the
+properties of low mass dark matter halos at $z=3.1$, extending the
+capabilities of abundance matching methods.
 

### 2013-06-26 paper/ms.tex
abstract + conclusions

@@
 
-\title[Halo mass and occupation fraction for LAEs at $z=3.1$]{Using cosmic
-  variance to constrain the dark matter halo mass and occupation
-  fraction of Lyman-alpha emitting galaxies at $z$=3.1}
-
+\title[Halo mass and occupation fraction for LAEs at
+  $z=3.1$]{Constraints on the mass and occupation
+  fraction of dark matter halos hosting Lyman-alpha emitters
+  at $z$=3.1}    
 \author[~J.~E. Forero-Romero and J. Mejia]{
@@
 \begin{abstract}
-We use cosmological N-body dark matter only simulations to constrain the
-characteristic mass of dark matter halos hosting Lyman-Alpha Emitting
-(LAE) galaxies at a redshift of $z=3.1$. The method is based on
-matching the statistics for the number density between mock and
-observed fields. The mock fields are constructed using a simple model
-where a dark matter halo can only host one LAE with a probability
-$f_{\rm occ}$ if its mass is found withing a certain range mass range
-delimited by two threshold values, $M_{\rm min}$ and $M_{\rm max}$. 
-We also maximize the number of mocks surveys consistent with
-Our most important results is that, unlike previous studies, a pure
-clustering analysis cannot fully constraint the halo occupation
-fraction for LAEs.
+%
+We derive constraints on the mass and occupation fraction of dark
+matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
+$z=3.1$, by comparing the  number density and the angular
+correlation function between mock and observed fields. The mock fields
+are constructed in a large cosmological N-body simulation using a
+model where a dark matter halo can only host one LAE with a
+probability $f_{\rm occ}$ if its mass is found within the mass range
+delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
+conclude that the number density and spatial clustering information
+available are not sufficient to derive a unique and narrow set of
+values for the parameter in the model. We find three different
+families of models based on their mass range $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}< 1.0$ dex and occupation
+fraction $f_{\rm occ}$.  The dominant familiy is composed by models with a narrow
+mass range $\Delta M<1.0$ dex, a low occupation fraction $f_{\rm occ}\leq 0.3$
+and a maximum mass $M_{\rm max}< 10^{12}$\hMsun.  This finding
+suggests that the most massive dark matter halos at that epoch do not
+host the brightest LAEs. This also gives support to observational evidence
+concluding that only a small fraction of star forming galaxies can be
+actually detected as LAEs. We provide tables and mock catalogs for the
+succesful models.
 
-Most of the models have a narrow mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}< 1.0$ dex and a low
-occupation fraction $f_{\rm occ}\leq 0.3$.
-
-observations and impose consistency with the angular correlation
-function. Under these conditions we find that LAEs are preferentially
-hosted by halos in very narrow mass ranges less than 0.5 dex in width,
-with the minimum mass $10\leq \log_{10}M_{\rm min}\leq 10.9$ and the
-occupation fraction $f_{\rm   occ}\leq 0.2$.  Our finding suggest that
-the most massive dark matter halos at that epoch do not host the
-brightest LAEs. This also gives support to observational evidence that
-says that only a small fraction of star forming galaxies can be
-actually detected as LAEs.
 \end{abstract}
@@
 
-\subsection{Three Regions in Parameter Space}
+\subsection{Three halo mass ranges}
 
@@
 section we reduce the size of this region by using more stringent
-constraints to define the agreement with observations and including
-additional observational information onpossible values for the
-occupation fraction at $z\sim 3$.
+constraints to define the agreement with observations and the
+inclusion of the angular correlation function information by
+\cite{Hayashino2004}.
 
@@
 \end{figure*}
-
-In this next subsections we consider two additional constraints on the models
-we accept as succesul. First we take models with the highest possible
-number of mock surveys consistent with observations. Second by
-comparing the angular correlation function against observational
-results by \cite{Hayashino2004}.
 
@@
 
-All of the prefered models have a halo mass range with $M_{\rm
+All the prefered models have a halo mass range with $M_{\rm
   min}<10^{11.4}$\hMsun. This suggests that a detailed and careful
-study of the spectral properties of LAEs coupled to the kind of
+study of the spectral and photometric properties of LAEs coupled to the kind of
 analysis performed in this paper can be a guide in the study of the
@@
 and occupation fraction for halos hosting Lyman Alpha Emitters at
-redshift $z=3.1$. We use a method that matches the cosmic variance in the surface
-density number of LAEs between mock and real observations and provides
-consistent results with observational estimates for the angular
-correlation function. The mock catalogs are based on a simplified
+redshift $z=3.1$ in a $\Lambda$CDM cosmology. We use a method that
+matches the cosmic variance of the surface 
+density number of LAEs between mock and real observations and is also
+consistent with observational estimates for the angular
+correlation function. The mock catalogs are constructed using a 
 model with three basic parameters: the halo mass range where LAEs can
@@
 
-These parameter sets can be split into three families depending the mass range
+The most important conclusion of this work is that available
+observational information for the clustering properties of LAEs at
+$z=3.1$ does not provide enough constraints to uniquely narrow the range of masses
+and occupation fraction of dark matter halos hosting those galaxies. In our
+model, the hosting halos can be split into three families depending the mass range
 $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
@@
 All the halo mass ranges in the best models fall into the broad
-results based in observations, which have been able to describe models
-in the third family, but have so far missed all the possible
-models. In particular, previous analysis did not consider the first
-two families: a narrow mass range and any value for the escape fraction.
+range obtained in previous analysis \citep{Gawiser2007}. The
+improvement of our method is being able to describe in high detail
+all the possible models consistent with observations, including the
+discovery of models previously overlooked like those with a high
+occupation fraction $f_{\rm occ}>0.3$.
 
-In the case of narrow mass models there are various cases with $\Delta
-M=0.1$dex. Taken at face value, a possible confirmation of these kind of models
-can be considered a challenge to explain relatively high star
-formation ratesm
+A central result in this exploration of paremter espace is the
+existence of a large number of models with a very
+narrow mass range $\Delta M< 0.1$ dex that are consistent in every
+aspect with the spatial distribution of observed LAEs. In order to
+have these characteristics it is required that halos around the mass
+$M_{\rm max}$ for each model become ineffecient in hosting detectable
+galaxies. One way to achieve this is having LAEs with a decreasing \ly
+escape fraction with increasing mass.
+
+All the models also present a range of masses where the halos are
+below the imass scale of $10^{11.4}$\hMsun infered as a lower
+threshold for the LBGs used in halo abundace matching
+studies. Detailed study of high-z LAES will have a possitive impact on
+our undertading of the connection of low mass halos to star forming
+galaxies.
+
+We forsee that the new observations with new instruments (such as MUSE,
+Hyper SuprimeCam and HETDEX) covering larger fields and a wider range
+of luminosities will be key in imposing tighter constraints on the
+properties of dark matter halos hosting LAEs.
 
 \section*{Acknowledgments} 
+J.E.F-R thanks the hospitality of Changbom Park and the Korea
+Institute for Advance Studies where the first full draft of this paper
+was completed.
 
@@
 \end{center}
-\caption{\label{table:thirdfamily}List of parameters for the first family of models. Narrow
-  mass range $\Delta M\leq 1.0$dex and low occupation fraction $f_{\rm occ}\leq 0.3$.}
+\caption{\label{table:thirdfamily}List of parameters for the first
+  family of models. Narrow   mass range $\Delta M\leq 1.0$dex and low
+  occupation fraction $f_{\rm occ}\leq 0.3$.} 
 \end{table}

### 2013-06-26 paper/ms.tex
first full draft version

@@
   fraction of dark matter halos hosting Lyman-alpha emitters
-  at $z$=3.1}    
+  at $z\sim 3$}    
 \author[~J.~E. Forero-Romero and J. Mejia]{
@@
 model where a dark matter halo can only host one LAE with a
-probability $f_{\rm occ}$ if its mass is found within the mass range
+probability $f_{\rm occ}$ if its mass is within the mass range
 delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
 conclude that the number density and spatial clustering information
-available are not sufficient to derive a unique and narrow set of
-values for the parameter in the model. We find three different
+available from observations is not sufficient to derive a unique and narrow set of
+values for the parameters in the model. We find three different
 families of models based on their mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}< 1.0$ dex and occupation
-fraction $f_{\rm occ}$.  The dominant familiy is composed by models with a narrow
-mass range $\Delta M<1.0$ dex, a low occupation fraction $f_{\rm occ}\leq 0.3$
-and a maximum mass $M_{\rm max}< 10^{12}$\hMsun.  This finding
-suggests that the most massive dark matter halos at that epoch do not
-host the brightest LAEs. This also gives support to observational evidence
-concluding that only a small fraction of star forming galaxies can be
-actually detected as LAEs. We provide tables and mock catalogs for the
-succesful models.
-
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
+fraction $f_{\rm occ}$.  However, there is a dominant familiy composed
+by models with a narrow mass range $\Delta M<1.0$ dex, a low
+occupation fraction $f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm
+  max}< 10^{12}$\hMsun.  This finding suggests that the most massive
+dark matter halos at that epoch do not host the brightest LAEs. This
+also gives support to observational evidence concluding that only a
+small fraction of star forming galaxies can be actually detected as
+LAEs. We provide tables and mock catalogs for the successful models. 
 \end{abstract}
@@
 \begin{keywords}
-{galaxies: kinematics and dynamics, Local Group, methods:numerical}
+{cosmology: theory – cosmology: large-scale structure of universe –
+  galaxies: formation – galaxies: high-redshift – galaxies: statistics
+  – galaxy: haloes} 
 \end{keywords}
@@
 
-Some theoretical approaches to this problem have been based on a
-forward modeling. Starting from the DM halo population, the
-corresponding intrinsic star formation properties are infered and
-statistics such as the luminosity function, the correlation function
-and the equivalent width distributions. Such modelling has been
-implemented from analytic considerations, semi-analytic models
- and 
-full N-body hidrodynamical simulations
-\citep{Dayal2009, ForeroRomero2011, Yajima2012, ForeroRomero2012} .
+Some theoretical approaches to this problem have been based on
+ab-initio approach modeling. Starting from the DM halo population, the
+corresponding intrinsic star formation properties are inferred
+together with other statistics such as the luminosity function, the
+correlation function and the equivalent width distributions. Such
+modelling has been implemented from analytic considerations,
+semi-analytic models  and  full N-body hidrodynamical simulations
+\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012}.
 
-Added to the uncertainties in the astrophysical processeses describing
-star formation in galactic populations, a highly debated steps in this
-approach is the calculation of the fraction of Lyman-$\alpha$ photons
-that escape the galaxy to the observer. Given the resonance nature of
-the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the
+Added to the uncertainties in the astrophysical processes describing
+star formation in galactic populations, a highly debated step in this
+approach is the calculation of the fraction of \ly photons
+that escape the galaxy to the observer. Given the resonant nature of
+the \lya line, the radiative transfer of \ly is sensitive to the
 density, temperature, topology and kinematics of the neutral Hydrogen
-in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011,
+in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011, Dijkstra2012,
 Laursen2013}.
@@
 problem makes it difficult to achieve a robust consensus on what is
-the theoretical expected value for the Lyman-$alpha$ escape fraction
-in high redshift.
+the theoretical expected value for the \ly escape fraction
+at high redshift.
+
+Our objective in the present \documentname is to use a method to
+bypass all the complexity involved in the estimation of the \ly escape
+fraction to infer information relevant to the understanding of LAEs in
+a cosmological context. The analysis we present is thus based on one
+of the most robust prediction of $\Lambda$CDM, namely the clustering
+and abudance of dark matter halos. We construct a simple model that
+allow us to construct mock catalogs and explore a wide range of
+parameters to narrow the mass interval of halos hosting LAEs together
+with its occupation fraction.
+
+Another central point in our study is the explicit inclusion of cosmic
+variance effects by using large volume cosmological simulations. This
+allows us to go closer to the space of observables and directly
+explore the compatibility of a model with observations.
+
+This paper is structured as follows. In the next section we present
+the simulation and model used to produce the mock catalogs and the criteria
+used to compare them against observations. In \SS \ref{sec:results} we
+present the main results in terms of the parameters of our model. We
+continue with a discussion of these results under the light of other
+observational results for LAEs and abundance matching models for
+galaxy formation before presenting our conclusions in \SS
+\ref{sec:conclusions}.
 
@@
 
-Our method to constrain the typical mass of a dark matter halos
-hosting LAEs at $z=3.1$ is based on the comparison of observational
-results on the surface number density and the predictions of a simple
-model that uses the outputs from cosmological N-body simulations.
-
-In the next subsections we describe in detail the four key elements of
-this workflow. First, we present the observations we take as a
-benchmark. Second, the N-body simulation and the halo catalogs we
+Our method is based on the comparison of observatios and mock
+catalogs on the surface number density and the angular correlation
+function.  In the next subsections we describe in detail the four key
+elements of this workflow. First, we present the observations we take
+as a benchmark. Second, the N-body simulation and the halo catalogs we
 use. Third, the simplified model that allows us to translated halo
@@
 
-The observational benchamark we use in this paper is the LAE number
+One of the main observational benchmarks we use in this paper is the LAE number
 density information at $z=3.1$ obtained by the panoramic narrow-band
@@
 observed equivalent width larger than $190$\ over a total survey area
-of $2.42$ deg$^{2}$, this corresponds to  averaga surface number
+of $2.42$ deg$^{2}$, this corresponds to  average surface number
 density of $0.20\pm 0.01$ arcmin$^{-2}$.
@@
 are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs,
-and the fild arotund the Great Observatory Optical Deep Survey North
+and the field around the Great Observatory Optical Deep Survey North
 (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs.
@@
 However, we decide to focus on the data from \cite{Yamada2012} because
-it has the largest covered area with homogeneous intrumentational
+it has the largest covered area with homogeneous instrumentation
 conditions (telescope, narrow band filter), data reduction pipeline
@@
 We use halo catalogs constructed with a Friend-of-Friends (FOF)
-algorithm with a linking lenght of 0.17 times the interparticle
+algorithm with a linking length of 0.17 times the inter-particle
 distance. The minimum halo mass in the models we construct in this \documentname
@@
   occ}$ of such halos that effectively host a LAE. We do not assign a
-luminosity to each LAE. We are primaraly interested in
+luminosity to each LAE. We are primarily interested in
 constraining the halo mass range hosting detectable LAEs under the
@@
 cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
-the last dinemsion goes in the redshift direction. This corresponds to
+the last dimension goes in the redshift direction. This corresponds to
 a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
@@
 the clustering of the observed fields. From the $11$ mock fields, $7$
-are constructed from contigous fields in the simulation to mimic the
+are constructed from contiguous fields in the simulation to mimic the
 SSA22 region, $3$ are also contiguous between them but not to the first
-$7$ fields to mimic the SXDS fields and finally $2$ non-contigous
+$7$ fields to mimic the SXDS fields and finally $2$ non-contiguous
 fields to imitate the SDF and GOODS-North field. Our main goal with
@@
   random}, whereby all the $11$ fields are selected in such a way as
-to avoid that any two volumes are contigous.
+to avoid that any two volumes are contiguous.
+
+The second benchmark is the angular correlation function (ACF). The
+measurements presented in \citep{Yamada2012} do not report an ACF
+measurement. Instead we use the results reported by
+\citep{Hayashino2004} on the LAEs observed in the densest field of
+SSA22. It is important to keep in mind that there are some differences
+between this work and \citep{Yamada2012}. First, the color selection by
+\cite{Yamada2012} is less stringent compared to the one by
+\cite{Hayashino2004}. Also the EW threshold is different,
+\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
+used by \citep{Yamada2012}
 
@@
 displacement of $0.1$ dex in the whole range. The occupation fraction
-$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regulary
+$f_{\rm occ}$ takes $10$ different values from $0.1$ to $1$ regularly
 spaced by $0.1$. In total the number of different models ${\mathcal
@@
 observational values. From this test we obtain a value $0<P<1$ to
-reject the null hypotesis, namely that two data sets come from the
+reject the null hypothesis, namely that two data sets come from the
 same distribution. In this paper we consider that for values $P>0.05$
@@
 
-In this paper we consider that a model
-${\mathcal M}$ that has at least one (1) mock survey (out of 15)
-consistent with the observed distribution of LAE number densities has
-viable parameters thatdeserve to be considered for further analysis.
+We begin by considering that  a model ${\mathcal M}$ that has at least
+one (1) mock survey (out of 15) consistent with the observed
+distribution of LAE number densities has viable parameters that
+deserve to be considered for further analysis. Later on we impose
+harder constraints to reduce the number of models by asking that all
+the 15 mocks to be consistent with observations.
 
-\section{Basic Results}
+The comparison between the theoretical and observational ACF is done
+in therms of the angular correlation length obtained  by fitting to a power-law
+function:
+
+\begin{equation}
+\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
+\label{eq:fitting}
+\end{equation}
+
+Both the theoretical and observational ACF are derived by a least
+square minimization procedure. We consider that a model is consistent
+with observations if the two parameters $\gamma$ and $\theta_0$ are
+equal within a $1$-$\sigma$ range.
+
+\section{Results}
+\label{sec:results}
 
@@
   $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
-  in the Bolshoi simulation. The horizontal grey band represents the
+  in the Bolshoi simulation. The horizontal gray band represents the
   range of surface densities observed for LAEs at $z=3.1$ as reported
@@
 
-This result provides the basis to understand why a range of models
+This result provides the basis to understand why only a specific range of models
 ${\mathcal M}$ can be expected to be consistent with
-observations. In Figure \ref{fig:halos} we can read that models
+observations. From Figure \ref{fig:halos} we can read that models
 with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
 surface number density lower than the observational
-constrain. The oppossite is true in models with $\log_{10} M_{\rm min}<10.5$
+constrain. This makes impossible that models with that minimum mass
+can be compatible with observations.
+
+The opposite is true in models with $\log_{10} M_{\rm min}<10.5$
 that will show surface number density larger than observations, this
 implies that in such models the occupation fraction has to be tuned
-$f_{\rm occ}<1.0$ as to lower the halo numeber density to match the
+$f_{\rm occ}<1.0$ as to lower the halo number density to match the
 gray band values.
 
-Conversely, there are regions in the plot where the halo surface
-density is always higher than the observational constraints correspond
-to models ${\mathcal M}$ with a minimum mass below $M_{\rm min}<
-3\times 10^{10}$\hMsun. Models with this minimum mass hava a chance
-for successfuly reproducing observations if the occupation fraction
-$f_{\rm occ}<1$ is tuned as to lower the halo number density down to
-the observed value.
-
-In the next subsection we quantify this intuition by means of the KS
-tests between mock surveys and observations.
+In the next subsection we quantify this intuition by means of the
+Kolmogorov-Smirnov tests between mock surveys and observations.
 
@@
 
-In Figure \ref{fig:landscale} there are three regions of parameter
-space that can be clearly distinguised. The first region corresponds
+In Figure \ref{fig:landscape} there are three regions of parameter
+space that can be clearly distinguished. The first region corresponds
 to models where the minimum mass is high $\log_{10}M_{\rm min}>
 11.5$. None of this models is compatible with observations as expected
-from the results in the previous section. For these models the number
-density of LAEs is too low.
+from the results in the previous subsection. For these models the number
+density of LAEs is too low compared to observations.
 
@@
 mass interval is very narrow with sizes smaller than $<0.3$ dex (a
-factor of two in mass) and others where the mass interval is very
+factor of two in mass) and others where the mass interval is 
 extended, larger than $1.0$ dex, going up to the maximum halo mass
@@
 The third region in parameter space corresponds to $\log_{10}M_{\rm
-  min}<10.5$. In this case only models with a narrow mass interval of
+  min}<10.5$. In this case only models with a very narrow mass interval of
 at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
@@
 Without any additional information our method allows us to infer that
-most of the succesful models are found in the second and third region of
+most of the successful models are found in the second and third region of
 parameter space where. This result was already expected from halo
 abundance calculations shown in Figure \ref{fig:halos}. In the next
-section we reduce the size of this region by using more stringent
-constraints to define the agreement with observations and the
-inclusion of the angular correlation function information by
-\cite{Hayashino2004}.
+section we reduce the size of this region by imposing tighter
+constraints on the KS tests and consistency with the angular
+correlation function.
 
@@
 \end{center} 
-\caption{ Number of models with a mininium number of mock survey
+\caption{ Number of models with a minimum number of mock survey
   realizations that are consistent with observations.
@@
 are between $80$ to $100$ models with all the 15 realizations with
-$P>0.05$. Selction of these models as successful represents a
-reduction of a factor of $\sim 6$ with repect to the total number of
+$P>0.05$. Selection of these models as successful represents a
+reduction of a factor of $\sim 6$ with respect to the total number of
 mocks with at least one consistent mock.
@@
 
-\subsection{Consitency with the Angular Correlation Function}
+\subsection{Consistency with the Angular Correlation Function}
 
@@
 \end{center}
-\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) of the 
-mean angular correlation function of the 15 mock surveys for each
-model. Blue dots corresponds to simulations and the green cross to
+\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) 
+in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
+correlation function. Blue dots correspond to simulations and the green cross to
 observations by \citet{Hayashino2004}. The error bars in the 
-theoretical data correspond to the starndard deviation from the
-different mocks. Right: Same results as before in the
-$\theta_{0}$-$M_{\rm min}$ plane. This time the observational
+theoretical data correspond to the standard deviation from the
+different mocks surveys. Right: Same results as before in the shown in
+the $\theta_{0}$-$M_{\rm min}$ plane. This time the observational
 constraints are represented by the red rectangle. Blue squares
-represent models with $\log_{10} M_{\rm  max}<12.0$, green circles are
-models with $\log_{10} M_{\rm max}>12.0$.
+represent models with $\log_{10} M_{\rm  max}<12.0$, green circles
+correspond to models with $\log_{10} M_{\rm max}>12.0$. 
 \label{figure:correlation_parameters}}
@@
 \end{center}
-\caption{Best models paramter space when both the constraints on the
+\caption{Best models parameter space when both the constraints on the
   maximal number of  consistent mocks and the occupation  fraction
@@
 
-We now make a further selection to the models compatible with the
-observational angular correlation function (ACF). The measurementens
-presented in \citep{Yamada2012} do not report an ACF
-measurement. Instead we use the results reported by
-\citep{Hayashino2004} on the LAEs observed in the densest field of
-SSA22.
+Figure \ref{figure:correlation_parameters} shows the main results in a
+$\theta_{0}-\gamma$  plane where the average and standard deviation
+for each mock is shown in comparison with the result derived from
+observations.  The error bars in this Figure represents the standard
+deviation of the ACF over all the sub-fields in the 15 mock
+observations. These error bars are larger than the statistical
+uncertainty from the fitting procedure on a single field.
 
-It is important to keep in mind that there are some differences
-between this work and \citep{Yamada2012}. First, the color selection by
-\cite{Yamada2012} is less stringent compared to the one by
-\cite{Hayashino2004}. Also the EW threshold is different,
-\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
-used by \citep{Yamada2012}
-
-The comparison between the theoretical and observational ACF is done in
-therms of the angular correlation lenght obtained  by fitting to a power-law
-function:
-
-\begin{equation}
-\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
-\end{equation}
-
-Both the theoretical and observational ACF are derived by a least
-square minimization procedure. The results are shown  in Figure
-\ref{figure:correlation_parameters}  in a $\theta_{0}-\gamma$  plane
-where the average and standard deviation for each mock is shown in
-comparison with the resut derived from observations.  The Error bars in
-these figures represents the standard deviation of the ACF over all
-the sub-fields in the 15 mock observations. These error bars are
-larger than the statistical uncertainty from the fitting procedure on
-a single field..
-
-We see in the left panel Figure \ref{figure:correlation_parameters} that
+In the left panel Figure \ref{figure:correlation_parameters} we see how
 the observational ACF measured by \cite{Hayashino2004} (green dot) is
-succesul in reducing the total number of possible models. Only those
+successful in reducing the total number of possible models. Only those
 with angular-correlation length within
-$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are consideret to
+$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
 reproduce observations.
 
-In order to interpret the results from this test we
+In order to better illustrate the results from this test we
 show in the right panel of Figure \ref{figure:correlation_parameters} 
 the plane $\theta_{0}$-$M_{\rm min}$ for all models. There we divide
-the models into two disjoint sents: those with $\log \frac{M_{\rm
+the models into two disjoint sets: those with $\log \frac{M_{\rm
     max}}{M_{\odot}}<12$ (blue dots) and $\log \frac{M_{\rm
     max}}{M_{\odot}}>12$ (green dots). The colored rectangle includes
-the parameter region wich is consistent with the observational
+the parameter region which is consistent with the observational
 constraint in $\theta_{0}$. With this restriction we find that most
 models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and  $\log
-\frac{M_{\rm     min}}{M_{\odot}}>11.1$can be safely ruled out.
+\frac{M_{\rm     min}}{M_{\odot}}>11.1$ can be safely ruled out.
 
-In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the prefered
+In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
@@
 Matching the galaxy surface number density statistics sets the median
-mass of all succesful models in the range $10^{10}-10^{12}$
+mass of all successful models in the range $10^{10}-10^{12}$
 \hMsun. Including more strict criteria on the number of mock surveys
@@
 
-We find that for the physical interpretation of these models it is
-useful to do it in terms of the size of halo mass range, using the
+We find that to make a physical interpretation of these models it is
+useful to do it in terms of the size of halo mass range. We now use the
 variable $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$, together
-with the escape fraction $f_{\rm occ}$. These two variables help us
-build a classification of all the successful models into three families:
+with the escape fraction $f_{\rm occ}$ to help us build a classification
+of all the successful models into three families:
 
@@
 
-At the low mass end, such cut can be readily interepreted in terms of the
+At the low mass end, such cut can be readily interpreted in terms of the
 minimal halo star formation rate needed to produce the necessary \lya
 luminosity to be above a given detection threshold.  However, under
-the reasonable assumption of star formation rate increainsng with halo
+the reasonable assumption of star formation rate increasing with halo
 mass, the cut at higher halo masses requires a different explanation.
 
-One possible interpretation can be made in terms of a drecreasing escape
+One possible interpretation can be made in terms of a decreasing escape
 fraction of \ly radiation in massive systems. There are detailed models for
@@
 with the total absence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun shows that our models supports theoretical insights
+10^{12}$\hMsun shows that our models support theoretical insights
 where the most massive systems are not bright \ly sources
@@
 compared observationally derived star formation functions to LAE
-luminosity functions. At $z\sim 3.0$ they derive an affective escape
+luminosity functions. At $z\sim 3.0$ they derive an effective escape
 fraction of $f_{\rm esc}=(17\pm 5)\%$ could be interpreted as an
-occupation fraction $f_{\rm occ}\sim 0.2$.  We consider a sucess of
+occupation fraction $f_{\rm occ}\sim 0.2$.  We consider a success of
 our method the fact that we find that most of the consistent models
@@
 
-Observational based on the ACF infered from photometric measurements
+Observational based on the ACF inferred from photometric measurements
 in the Extended Chandra Deep Field South have shown that the median
@@
 fraction of $1-10\%$  \citep{Gawiser07}.  Our results are in a general
-good agrement with those estimates for the host mass. This is not
-completeley unexepected given that we have also required consistency
+good agreement with those estimates for the host mass. This is not
+completely unexpected given that we have also required consistency
 with ACF measurements.
@@
 
-WE also find interesting that ACF analsys is also not enough to rule
+We also find interesting that our ACF analysis is also not enough to rule
 out models with a high occupation fraction $f_{\rm occ}>0.3$, which
@@
 Considering the additional evidence for a low escape fraction we can
-say that the prefered models are in families (1) and (2) with a
+say that the preferred models are in families (1) and (2) with a
 clear majority composed by those with narrow mass range and low occupation
@@
 observational data for the stellar mass function based on the
-obervations of Lyman Break Galaxies.
+observations of Lyman Break Galaxies.
 
-All the prefered models have a halo mass range with $M_{\rm
+All the preferred models have a halo mass range with $M_{\rm
   min}<10^{11.4}$\hMsun. This suggests that a detailed and careful
@@
 \section{Conclusions}
+\label{sec:conclusions}
 
@@
 be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
-the halos in this range that are actully occupied, $f_{\rm occ}$. After
+the halos in this range that are actually occupied, $f_{\rm occ}$. After
 a thorough exploration of the parameter space we find that wide
@@
 literature. Out of $9000$ initial combinations for the model
-parameters we end up with $49$ sucessful arrangement of parameters.
+parameters we end up with $49$ successful arrangement of parameters.
 
@@
 occupation fraction $f_{\rm occ}$. The first family is narrow both in
-$\Delta M$ and $f_{\rm occ}$, a second familiy is only narrow in
+$\Delta M$ and $f_{\rm occ}$, a second family is only narrow in
 $\Delta M$ and the third is narrow in $f_{\rm occ}$ and broad in
@@
 
-A central result in this exploration of paremter espace is the
+A central result in this exploration of parameter esp ace is the
 existence of a large number of models with a very
@@
 have these characteristics it is required that halos around the mass
-$M_{\rm max}$ for each model become ineffecient in hosting detectable
+$M_{\rm max}$ for each model become inefficient in hosting detectable
 galaxies. One way to achieve this is having LAEs with a decreasing \ly
@@
 All the models also present a range of masses where the halos are
-below the imass scale of $10^{11.4}$\hMsun infered as a lower
-threshold for the LBGs used in halo abundace matching
-studies. Detailed study of high-z LAES will have a possitive impact on
-our undertading of the connection of low mass halos to star forming
+below the mass scale of $10^{11.4}$\hMsun inferred as a lower
+threshold for the LBGs used in halo abundance matching
+studies. Detailed study of high-z LAES will have a positive impact on
+our understanding of the connection of low mass halos to star forming
 galaxies.
 
-We forsee that the new observations with new instruments (such as MUSE,
+We foresee that the new observations with new instruments (such as MUSE,
 Hyper SuprimeCam and HETDEX) covering larger fields and a wider range
@@
 J.E.F-R thanks the hospitality of Changbom Park and the Korea
-Institute for Advance Studies where the first full draft of this paper
+Institute for Advanced Study where the first full draft of this paper
 was completed.

### 2013-06-26 paper/ms.tex
little changes to the paper

@@
 semi-analytic models  and  full N-body hidrodynamical simulations
-\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012}.
+\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012, Soler2012}.
 
@@
 in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011, Dijkstra2012,
-Laursen2013}.
+Laursen2013,Orsi2012}.
 
@@
 constraining the halo mass range hosting detectable LAEs under the
-conditions defined by \cite{Yamada2012}. In what follows will describe by
+conditions defined by \cite{Yamada2012}. In what follows we will describe by
 the letter ${\mathcal M}$ a model defined by an specific choice of the
@@
 \cite{Hayashino2004}. Also the EW threshold is different,
-\cite{Hayashino2004} uses a cut around $154$\AA instead of $190$\AA
-used by \citep{Yamada2012}
+\cite{Hayashino2004} uses a cut around $154$\AA \ instead of $190$\AA
+\ used by \citep{Yamada2012}
 
@@
 \begin{equation}
-\xi(\theta) = \left(\frac{r}{\theta_{0}}\right)^{-\gamma}
+\xi(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\gamma}
 \label{eq:fitting}
@@
 observations. From Figure \ref{fig:halos} we can read that models
-with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
+with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun \ will always have a
 surface number density lower than the observational
@@
   match} and {\texttt random} methods. With this constraints the
-number of consistent models with  $\log_{10}M_{\rm min}< 11.7$ are
+number of consistent models with  $\log_{10}M_{\rm min}< 11.5$ are
 greatly reduced. This corresponds to the regions in the parameter
@@
 the plane $\theta_{0}$-$M_{\rm min}$ for all models. There we divide
-the models into two disjoint sets: those with $\log \frac{M_{\rm
-    max}}{M_{\odot}}<12$ (blue dots) and $\log \frac{M_{\rm
-    max}}{M_{\odot}}>12$ (green dots). The colored rectangle includes
+the models into two disjoint sets: those with $\log_{10} M_{\rm
+    max}<12$ (blue dots) and $\log_{10} M_{\rm
+    max}>12$ (green dots). The colored rectangle includes
 the parameter region which is consistent with the observational
 constraint in $\theta_{0}$. With this restriction we find that most
-models with $\log \frac{M_{\rm max}}{M_{\odot}}>12$ and  $\log
-\frac{M_{\rm     min}}{M_{\odot}}>11.1$ can be safely ruled out.
+models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.1$ 
+%can be safely ruled out.
 
@@
 useful to do it in terms of the size of halo mass range. We now use the
-variable $\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$, together
+variable $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, together
 with the escape fraction $f_{\rm occ}$ to help us build a classification
@@
 with the total absence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun shows that our models support theoretical insights
+10^{12}$\hMsun \  shows that our models support theoretical insights
 where the most massive systems are not bright \ly sources
@@
 formation efficiency (star formation rate divided by the stellar mass)
-presents a clear maximum around $10^{11.7}$\Msun at all redshifts
+presents a clear maximum around $10^{11.7}$\Msun \ at all redshifts
 $z<4$.
@@
 in \cite{Behroozi2013a} we find that the typical stellar mass in halos
-of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
+of $10^{11.4}$\hMsun \ is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
 their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$.
-This halo mass range around $10^{11.4}$ \hMsun is the lower bound of
+This halo mass range around $10^{11.4}$ \hMsun \ is the lower bound of
 what is computed in the abundance matching model in order to fit the
@@
 All the models also present a range of masses where the halos are
-below the mass scale of $10^{11.4}$\hMsun inferred as a lower
+below the mass scale of $10^{11.4}$\hMsun \  inferred as a lower
 threshold for the LBGs used in halo abundance matching

### 2013-06-27 paper/ms.tex
minor modifications: first draft to be sent to friends

@@
 delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
-conclude that the number density and spatial clustering information
-available from observations is not sufficient to derive a unique and narrow set of
-values for the parameters in the model. We find three different
-families of models based on their mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
-fraction $f_{\rm occ}$.  However, there is a dominant familiy composed
+find three different families of parameters based on their mass range
+$\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
+fraction $f_{\rm occ}$.  From this we  conclude that the number
+density and spatial clustering information available from observations
+is not sufficient to derive a unique and narrow set of values for the
+parameters in the model.  However, there is a dominant familiy composed
 by models with a narrow mass range $\Delta M<1.0$ dex, a low
 occupation fraction $f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm
-  max}< 10^{12}$\hMsun.  This finding suggests that the most massive
-dark matter halos at that epoch do not host the brightest LAEs. This
-also gives support to observational evidence concluding that only a
-small fraction of star forming galaxies can be actually detected as
-LAEs. We provide tables and mock catalogs for the successful models. 
+  max}< 10^{12}$\hMsun.  This suggests that the most massive
+dark matter halos at that epoch do not host the brightest LAEs, also
+giving support to some observational evidence indicating that only a small
+fraction of star forming galaxies can be actually detected as LAEs. We
+provide tables and mock catalogs for the successful models.  
 \end{abstract}
@@
 \begin{equation}
-\xi(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\gamma}
+\xi(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{\gamma}
 \label{eq:fitting}
@@
 in the occupation fraction and the ACF. Here we consider a model
-consistent if there is an overlap of $1-sigma$ in its values for the
+consistent if there is an overlap of $1-\sigma$ in its values for the
 correlation length $\theta_0$ and the power $\gamma$ in the
@@
 Matching the galaxy surface number density statistics sets the median
-mass of all successful models in the range $10^{10}-10^{12}$
+mass of all successful models in the range $(10^{10}-10^{12})$
 \hMsun. Including more strict criteria on the number of mock surveys
@@
 say that the preferred models are in families (1) and (2) with a
-clear majority composed by those with narrow mass range and low occupation
-fraction.
+clear majority composed by those with narrow mass range.
 
-Using abundance matching methods throughout cosmic time from redshifts
-$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} report that the instantaneous star
-formation efficiency (star formation rate divided by the stellar mass)
-presents a clear maximum around $10^{11.7}$\Msun \ at all redshifts
-$z<4$.
+Abundance matching methods throughout cosmic time from redshifts
+$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} work based on observational
+results for Lyman Break Galaxies. In thos studies the minimum halo
+mass considered to be relevant in their analysis is
+$10^{11.4}$\hMsun. For that mass, \cite{Behroozi2013a} report a
+stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$
+\hMsun, while their star formation rate is in the range $0.6\pm 0.2$
+Msun yr$^{-1}$, which nevertheless are close to the lower bound of
+values inferred for LAEs at high redshift
+\citep{Gawiser2007,Nilsson2009,Pentericci2009}.
 
-This mass scale is strictly superior to the great majority of  $M_{\rm max}$
-values allowed in the models with low escape fraction. Using the results published
-in \cite{Behroozi2013a} we find that the typical stellar mass in halos
-of $10^{11.4}$\hMsun \ is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$.
-This halo mass range around $10^{11.4}$ \hMsun \ is the lower bound of
-what is computed in the abundance matching model in order to fit the
-observational data for the stellar mass function based on the
-observations of Lyman Break Galaxies.
-
-All the preferred models have a halo mass range with $M_{\rm
-  min}<10^{11.4}$\hMsun. This suggests that a detailed and careful
-study of the spectral and photometric properties of LAEs coupled to the kind of
-analysis performed in this paper can be a guide in the study of the
+In our results, all the preferred models have a halo mass range lower
+than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considerend in
+abundance matching at $z=3$. This mass scale is also strictly superior to
+the great majority of  $M_{\rm max}$ values allowed in the models with
+low escape fraction.   This suggests that a detailed and careful study
+of the s ectral and photometric properties of LAEs coupled to the kind
+of analysis performed in this paper can be a guide in the study of the
 properties of low mass dark matter halos at $z=3.1$, extending the

### 2013-06-27 paper/ms.tex
minor update

@@
 The preference for narrow $\Delta M$ ranges to hosting LAEs together
-with the total absence of reasonable models with $M_{\rm max}>
+with the minor presence of reasonable models with $M_{\rm max}>
 10^{12}$\hMsun \  shows that our models support theoretical insights

### 2013-06-27 paper/ms.tex
little spelling corrections on paper

@@
 $0<z<8$ \cite{Behroozi2013a,Behroozi2013b} work based on observational
-results for Lyman Break Galaxies. In thos studies the minimum halo
+results for Lyman Break Galaxies. In those studies the minimum halo
 mass considered to be relevant in their analysis is
@@
 low escape fraction.   This suggests that a detailed and careful study
-of the s ectral and photometric properties of LAEs coupled to the kind
+of the spectral and photometric properties of LAEs coupled to the kind
 of analysis performed in this paper can be a guide in the study of the

### 2013-07-08 paper/ms.tex
paragraph on the parameters selected for the model

--- 2013-06-27 paper/ms.tex
@@
   M}$ that are explored is $30 \times 30 \times 10 = 9000$.
+
+The lower limit for the parameter $M_{\rm min}$ IS set by the
+observational constraints on the stellar mass $M_{
+\rm star}>2\times 10^{9}$\hMsun \citep{Gawiser07}. Considering a
+extreme case where all baryonic mass is in the form of stars an under
+the assumption that the baryon to dark matter ratio cannot be larger
+than the cosmological value $\Omega_{\rm b}/Omega_{\rm dm}\sim 0.2$,
+the minimum value for the dark matter halo that we should consider is
+precisely $\sim 10^{10}$\hMsun. In turn, this limit help us impose the
+minimum value of $f_{\rm occ}=0.1$. Lower values for the occupation
+fraction would produce a halo number density well below the observational
+constraints.
 

### 2013-07-09 paper/ms.tex
included all the comments from Peter Laursen

@@
 delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
-find three different families of parameters based on their mass range
+define three different families of parameters consistent with
+observations based on their mass range
 $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
@@
 is not sufficient to derive a unique and narrow set of values for the
-parameters in the model.  However, there is a dominant familiy composed
-by models with a narrow mass range $\Delta M<1.0$ dex, a low
-occupation fraction $f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm
-  max}< 10^{12}$\hMsun.  This suggests that the most massive
-dark matter halos at that epoch do not host the brightest LAEs, also
-giving support to some observational evidence indicating that only a small
-fraction of star forming galaxies can be actually detected as LAEs. We
-provide tables and mock catalogs for the successful models.  
+parameters in the model. In particular, it is always possible to find a 
+a model with any desired occupation fraction in the range $0.1\leq
+f_{\rm occ}\leq 1.0$.  However, there is a dominant family composed by
+models with a narrow mass range $\Delta M<1.0$ dex, a low occupation fraction
+$f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm   max}<
+10^{12}$\hMsun.  This suggests that the most massive dark matter halos
+at that epoch do not host the brightest LAEs, also giving support to
+some observational evidence indicating that only a small fraction of
+star forming galaxies can be actually detected as LAEs. We provide
+tables and mock catalogs for the successful models.   
 \end{abstract}
@@
 
-Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
-central topic in studies of structure formation in the Universe. They 
-are helpful in a diverse range of fields. LAEs can
-be used as probes of reionization \citep{Dijkstra11}, tracers of
-large scale structure \citep{Koehler2007}, 
-signposts for low metallicity stellar populations and markers of the
-the galaxy formation process through cosmic history \citep{ForeroRomero2012}.
+Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade
+a  central topic in studies of structure formation in the Universe. They 
+are helpful in a diverse range of fields. LAEs can be used as probes
+of reionization \citep{Dijkstra11}, tracers of large scale structure
+\citep{Koehler2007},  signposts for low metallicity stellar
+populations and markers of thethe galaxy formation process through
+cosmic history \citep{ForeroRomero2012}.
 
@@
 M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
-  occ}$ of such halos that effectively host a LAE. We do not assign a
+  occ}$ of such halos that host a \emph{detectable LAE}. The reader
+must keep in mind that the physical interpreation of the occupation
+fraction $f_{\rm occ}$ convolves two things: the presence of a star
+forming galaxy in a halos and its detectability as a LAE. We do not assign a
 luminosity to each LAE. We are primarily interested in
@@
 We begin by considering that  a model ${\mathcal M}$ that has at least
-one (1) mock survey (out of 15) consistent with the observed
+one mock survey (out of 15) consistent with the observed
 distribution of LAE number densities has viable parameters that
@@
 \label{sec:results}
+
+The main purpose of this section is to show how different
+observational constraints narrow down the parameters space of allowed
+models. In each one of the four sub-sections we add a new
+constraint. First we consider the average halo number density, then we
+consider the surface density distributions for all the mock fields in
+a given mock survey. From this result we move to narrower constraints
+by requiring a high number of mock surveys with consistent surface
+density distributions to finally consider the impact of the angular
+correlation function.
 
@@
 
-\subsection{Three halo mass ranges}
+\subsection{Surface density distributions}
 
@@
   test with $P>0.05$. Only regions of parameter space with at least
-  one (1) consistent mock survey are included. \label{fig:landscape}}   
+  one consistent mock survey are included. \label{fig:landscape}}   
 \end{figure*}
@@
 with observations. There are between $550$ to $600$ models out of the
-original $9000$ models that have at least one (1) mock survey
+original $9000$ models that have at least one mock survey
 consistent with observations.
@@
 For each model ${\mathcal M}$ there are 15 different mock surveys. In the
-previous section we presented the models that had at least one (1)
+previous section we presented the models that had at least one
 mock survey with $P>0.05$.
@@
 number of possible models. We end up with $\sim 50$ models out of the
-initial 90000 possible combination of parameters.
+initial 9000 possible combination of parameters.
 
@@
 variable $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, together
-with the escape fraction $f_{\rm occ}$ to help us build a classification
+with the occupation fraction $f_{\rm occ}$ to help us build a classification
 of all the successful models into three families:
@@
 the reasonable assumption of star formation rate increasing with halo
-mass, the cut at higher halo masses requires a different explanation.
+mass, the cut at higher halo masses requires a different
+explanation. There are two different physical scenarios to explain
+this.
 
@@
 radiative transfer that support the idea that massive galaxies with
-higher metallicities have larger dust contents than lower mass
-systems, which due to the resonant nature of the \ly line are enough
-to produce high absorption of \ly photons but not of continuum or
-other non-resonant lines.
+higher metallicities have larger dust contents and less concentrated
+ISM than lower mass systems, which due to the resonant nature of the
+\ly line are enough to produce high absorption of \ly photons but not of continuum or
+other non-resonant lines \citep{ForeroRomero2011,Laursen2009}.
+
+A second scenario is that larger systems have more extended gaseous
+envelopes which, due to resonance effects of the \ly line, leading to
+a low surface brightness and a broader line, making these systems less
+observable in narrow band filter surveys \citep{Zheng2010}.
 
@@
 have described in the previous subsection.
+
+\citep{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.
 
@@
 Institute for Advanced Study where the first full draft of this paper
-was completed.
+was completed. J.E.F-R also thanks Peter Laursen for helpful comments
+on the physical interpretation and the presentation of our results.
 

### 2013-07-09 paper/ms.tex
minor changes before lunch :)

@@
 
-\citep{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.
+... \cite{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.
 
@@
 
-In this \documentname we constrain the preferred dark matter mass
-and occupation fraction for halos hosting Lyman Alpha Emitters at
+In this \documentname we constrain the preferred mass
+and occupation fraction of dark matter halos hosting Lyman Alpha Emitters at
 redshift $z=3.1$ in a $\Lambda$CDM cosmology. We use a method that
@@
 density number of LAEs between mock and real observations and is also
-consistent with observational estimates for the angular
+consistent with estimations of the angular
 correlation function. The mock catalogs are constructed using a 
@@
 be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
-the halos in this range that are actually occupied, $f_{\rm occ}$. After
-a thorough exploration of the parameter space we find that wide
+the halos in this range that host a detectable LAE, $f_{\rm occ}$. After
+a thorough exploration of the parameter space we find that a wide
 variety of models are consistent with the observational constraints,
@@
 $z=3.1$ does not provide enough constraints to uniquely narrow the range of masses
-and occupation fraction of dark matter halos hosting those galaxies. In our
-model, the hosting halos can be split into three families depending the mass range
-$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
-occupation fraction $f_{\rm occ}$. The first family is narrow both in
+and occupation fraction of dark matter halos hosting those
+galaxies. In particular we are not able to put a stringent constraint
+on the occupation fraction $f_{\rm occ}$.
+
+In our results the models can be split into three families
+depending the mass range $\Delta M=\log_{10}M_{\rm max} -
+\log_{10}M_{\rm min}$ and the occupation fraction $f_{\rm occ}$. The first family is narrow both in
 $\Delta M$ and $f_{\rm occ}$, a second family is only narrow in

### 2013-07-12 paper/ms.tex
Paulina comments partially added

@@
 
-This complexity makes the use of monte-carlo simulations for the
+This complexity can be tackeld with monte-carlo simulations for the
 radiative transfer a required tool to obtain physically sound results,
@@
 catalogs on the surface number density and the angular correlation
-function.  In the next subsections we describe in detail the four key
+function of LAEs.  In the next subsections we describe in detail the four key
 elements of this workflow. First, we present the observations we take
@@
 density information at $z=3.1$ obtained by the panoramic narrow-band
-survey presented by \cite{Yamada2012} from a survey  conducted with
-the Subaru 8.2m telescope and the Subaru Prime Focus Camera, which has
-a field of view covering $34\times 27$ arcmin, corresponding to a
+survey presented by \cite{Yamada2012} from a survey
+conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
+which has a field of view covering $34\times 27$ arcmin, corresponding to a
 comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
@@
 $h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
-centered at $z=3.09$. The authors report a total  $2161$ LAEs with an
-observed equivalent width larger than $190$\ over a total survey area
-of $2.42$ deg$^{2}$, this corresponds to  average surface number
-density of $0.20\pm 0.01$ arcmin$^{-2}$.
+centered at $z=3.09$. The authors reported a
+total  $2161$  LAEs with an observed equivalent width larger than $190$\AA 
+over a total survey area of $2.42$ deg$^{2}$ that includes 12 subfields, 
+this corresponds to average surface number density of $0.20\pm 0.01$ arcmin$^{-2}$.
 
 The survey covered four independent fields. The first is the SSA22
-field of $1.38$ deg$^2$ with $1394$ detected LAEs, this field has been
+field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 subfields), this field has been
 known to harbor a region with a large density excess of galaxies. The
@@
   XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a 
-total of $0.58$ deg$^2$ and $386$ LAEs. The third and fourth fields
-are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs,
+total of $0.58$ deg$^2$ and $386$ LAEs (3 subfields). The third and fourth fields
+are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs (1 subfield),
 and the field around the Great Observatory Optical Deep Survey North
-(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs.
+(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1 subfield).
 
@@
 and conditions to construct the LAE catalog. This ensures that the
-number density variations among fields are due only to
-astrophysical reasons and not different observational conditions or
-criteria to construct the catalogs.
+number density variations among fields are \emph{not} due to different observational
+conditions or criteria to construct the catalogs.
+
+The second constraint is the angular correlation function (ACF). The
+measurements presented in \citep{Yamada2012} do not report an ACF
+measurement. Instead we use the results reported by
+\citep{Hayashino2004} on the LAEs observed in the densest field of
+SSA22. It is important to keep in mind that there are some differences
+between this work and \citep{Yamada2012}. First, the color selection by
+\cite{Yamada2012} is less stringent compared to the one by
+\cite{Hayashino2004}. Also the EW threshold is different,
+\cite{Hayashino2004} uses a cut around $154$\AA \ instead of $190$\AA
+\ used by \citep{Yamada2012}
 
@@
 We focus our work on halos more massive than $1\times 10^{10}$\hMsun
-that are resolved with at least $70$ particles.
+that are resolved with at least $70$ particles (REFF????)
 
@@
 fraction $f_{\rm occ}$ convolves two things: the presence of a star
-forming galaxy in a halos and its detectability as a LAE. We do not assign a
+forming galaxy in a halo and its detectability as a LAE. We do not assign a
 luminosity to each LAE. We are primarily interested in
@@
 the letter ${\mathcal M}$ a model defined by an specific choice of the
-three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.
+three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ and $f_{\rm occ}$.
 
@@
 to avoid that any two volumes are contiguous.
-
-The second benchmark is the angular correlation function (ACF). The
-measurements presented in \citep{Yamada2012} do not report an ACF
-measurement. Instead we use the results reported by
-\citep{Hayashino2004} on the LAEs observed in the densest field of
-SSA22. It is important to keep in mind that there are some differences
-between this work and \citep{Yamada2012}. First, the color selection by
-\cite{Yamada2012} is less stringent compared to the one by
-\cite{Hayashino2004}. Also the EW threshold is different,
-\cite{Hayashino2004} uses a cut around $154$\AA \ instead of $190$\AA
-\ used by \citep{Yamada2012}
 
@@
 factor of two in mass) and others where the mass interval is 
-extended, larger than $1.0$ dex, going up to the maximum halo mass
-present in the simulation at that redshift.
+extended (larger than $1.0$ dex) going up to the maximum halo mass
+present in the simulation at that redshift (up to $2.5$ dex).
 
@@
 most of the successful models are found in the second and third region of
-parameter space where. This result was already expected from halo
+parameter space where this result was already expected from halo
 abundance calculations shown in Figure \ref{fig:halos}. In the next
@@
 Figure \ref{fig:restriction_mock} one can see that there is not a
-strong selection effect on the occupation fraction $f_{\rm occ}$.
+strong constraint on the occupation fraction $f_{\rm occ}$.
 
@@
 models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.1$ 
-%can be safely ruled out.
+can be safely ruled out.
 
@@
 
-Matching the galaxy surface number density statistics sets the median
+Matching the galaxy surface number density statistics to
+our mock  data sets the median
 mass of all successful models in the range $(10^{10}-10^{12})$
@@
 higher metallicities have larger dust contents and less concentrated
-ISM than lower mass systems, which due to the resonant nature of the
-\ly line are enough to produce high absorption of \ly photons but not of continuum or
-other non-resonant lines \citep{ForeroRomero2011,Laursen2009}.
+ISM than lower mass systems which, due to the resonant nature of the
+\ly line that increase the probability of absortion  of\ly photons, produce
+high absorption of \ly photons but not of continuum or
+other n-resonant lines \citep{ForeroRomero2011,Laursen2009}.
 
@@
 with the minor presence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun \  shows that our models support theoretical insights
-where the most massive systems are not bright \ly sources
-\citep{ForeroRomero2012}.
+10^{12}$\hMsun \  shows that our models support theoretical and observational
+insights where the most massive systems are not bright \ly sources
+\citep{ForeroRomero2012}, \citep{Shapley2003}
 

### 2013-07-17 paper/ms.tex
paragraph update in the model description

@@
 
-The lower limit for the parameter $M_{\rm min}$ IS set by the
-observational constraints on the stellar mass $M_{
-\rm star}>2\times 10^{9}$\hMsun \citep{Gawiser07}. Considering a
-extreme case where all baryonic mass is in the form of stars an under
-the assumption that the baryon to dark matter ratio cannot be larger
-than the cosmological value $\Omega_{\rm b}/Omega_{\rm dm}\sim 0.2$,
-the minimum value for the dark matter halo that we should consider is
-precisely $\sim 10^{10}$\hMsun. In turn, this limit help us impose the
-minimum value of $f_{\rm occ}=0.1$. Lower values for the occupation
-fraction would produce a halo number density well below the observational
-constraints.
+The lower limit for the parameter $M_{\rm min}$ is set by the minium
+occupation fraction we are able to consider. At $M_{\rm
+  min}=10^{10}$\hMsun the halo number density is already $\sim 10$
+times higher than the observational constraints for LAEs. This means
+that models in that mass range and an occupation fraction $f_{\rm
+  occ}$ have the possibility to be compatible with observations. Lower
+values for $M_{\rm min}$ require $f_{\rm occ}<0.1$, which are not
+considered in this \documentname.
 

### 2013-07-24 paper/ms.tex
ACF calculation described, paulina's comments added

@@
   at $z\sim 3$}    
-\author[~J.~E. Forero-Romero and J. Mejia]{
+\author[~J.~E. Forero-Romero and ~J.~E Mejia-Restreo]{
 \parbox[t]{\textwidth}{\raggedright 
 Jaime E. Forero-Romero$^{1}$ and
-Julian Mej\'ia-Restrepo$^{2}$ 
+Julian E. Mej\'ia-Restrepo$^{2}$ 
 }
@@
 \citep{Koehler2007},  signposts for low metallicity stellar
-populations and markers of thethe galaxy formation process through
-cosmic history \citep{ForeroRomero2012}.
+populations, markers of the galaxy formation process through
+cosmic history \citep{ForeroRomero2012}. and tracers of active star formation 
+\citep{Guaita2013}
 
@@
 matter, whereby each galaxy is hosted by larger dark matter structure
-known as a halo.
+known as a halo. \citep{Peebles1980}
 
@@
 \cite{Hayashino2004} uses a cut around $154$\AA \ instead of $190$\AA
-\ used by \citep{Yamada2012}
+\ used by \citep{Yamada2012}. These differences  translates
+in only two more detected objects in the Hayashino survey (283 LAEs) than in 
+Yamada et al (281 LAEs).
 
@@
 We focus our work on halos more massive than $1\times 10^{10}$\hMsun
-that are resolved with at least $70$ particles (REFF????)
+that are resolved with at least $70$ particles ({\bf REFF???? or support???})
 
@@
 
-The comparison between the theoretical and observational ACF is done
-in therms of the angular correlation length obtained  by fitting to a power-law
-function:
+We then calculate the  angular correlation function (ACF)
+for all the models having the $15$ mock surveys consistent with
+observations . The ACF is computed  ( using 
+the Davis \& Peebles  estimator \citep{Davis1983} ) only on the densest
+subfield in all the 15 mock surveys corresponding to the SSA22
+region. We then take the mean ACF over the 15  mock surveys  for
+each model as well as its the standard deviation to include
+the effect of cosmic variance.
+
+We finally compare the observational ACF and the mean mock  ACF of the models   
+in therms of the angular correlation lenght ($\theta_{0}$) by fitting 
+them to a power-law function:
 
@@
 
-Both the theoretical and observational ACF are derived by a least
-square minimization procedure. We consider that a model is consistent
-with observations if the two parameters $\gamma$ and $\theta_0$ are
+Both mock and observational ACF are derived by a least
+square minimization procedure. The observational errors of 
+the ACF as well as the standard deviation of the mean modelled ACFs  are
+considered to compute the error in the fitted parameters to ensure ourselves
+to include poissionian and cosmic-variance errors. 
+We consider that a model is consistent with observations if the two parameters $\gamma$ and $\theta_0$ are
 equal within a $1$-$\sigma$ range.
@@
   matter halos as a function of a minimum halo mass to count the
-  total number of elements in a volume. Each line represents on of the
+  total number of elements in a volume. Each line represents one of the
   $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
@@
 correlation length $\theta_0$ and the power $\gamma$ in the
-correlation function.
+correlation function.  As before, we found similar results using the {\tt random} method
 
@@
 preference goes in the same direction as the observational constraint
-on $f_{\rm occ}\sim 0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}
+on the escape fraction $f_{\rm esc}\sim 0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}
 and recent theoretical study of observational data in a wide redshift
@@
 range in halo masses $\Delta M>1.0$ dex. These models can only be
-considered unfavorable based on a different set of observations as we
-have described in the previous subsection.
+considered unfavorable based on the density and abundance observations
+as we have described in the previous subsection.
 
@@
 
-Considering the additional evidence for a low escape fraction we can
+Considering the additional evidence for a low escape fraction and 
+assuming a direct relation between $f_{esc}$ and $f_{occ}$ we can
 say that the preferred models are in families (1) and (2) with a
@@
 
-A central result in this exploration of parameter esp ace is the
+A central result in this exploration of parameter espace is the
 existence of a large number of models with a very

### 2013-07-29 paper/ms.tex
updated section on ACF

@@
 and conditions to construct the LAE catalog. This ensures that the
-number density variations among fields are \emph{not} due to different observational
-conditions or criteria to construct the catalogs.
+number density variations among fields are \emph{not} due to different
+observational conditions or criteria to construct the catalogs.
 
-The second constraint is the angular correlation function (ACF). The
-measurements presented in \citep{Yamada2012} do not report an ACF
-measurement. Instead we use the results reported by
-\citep{Hayashino2004} on the LAEs observed in the densest field of
-SSA22. It is important to keep in mind that there are some differences
-between this work and \citep{Yamada2012}. First, the color selection by
-\cite{Yamada2012} is less stringent compared to the one by
-\cite{Hayashino2004}. Also the EW threshold is different,
-\cite{Hayashino2004} uses a cut around $154$\AA \ instead of $190$\AA
-\ used by \citep{Yamada2012}. These differences  translates
-in only two more detected objects in the Hayashino survey (283 LAEs) than in 
-Yamada et al (281 LAEs).
+The second constraint is the angular correlation function
+(ACF). \cite{Yamada2012} does not report an ACF measurement. Instead
+we use the results by \cite{Hayashino2004} and
+\cite{Ouchi2008,Ouchi2010}.
+
+\cite{Hayashino2004} observed in the densest field of
+SSA22 while \cite{Ouchi2008} observed on a 1 deg$^2$ sky of the
+Subaru/XMM-Newton Deep Survey (SXDS) Field.  There are some
+differences between these observations and those iby
+\cite{Yamada2012}. The details in the color selection, corresponding
+limiting luminosities and EW thresholds are different in these
+references. Nevertheless we use these observations as additional
+constraints in spite of the fact that the first selected models are
+based only on the surface density statistics by \citep{Yamada2012}.
 
@@
 The Bolshoi simulation \citep{Bolshoi} we use in this paper was
-performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. It includes
+performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. The
 dark matter distribution is sampled using $2048^{3}$ particles, which
@@
 $h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
-a WMAP5 and WMAP7 data with a  density $\Omega_{\rm m} = 0.27$,
-cosmological  $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
+a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$,
+cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
 $h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
@@
 algorithm with a linking length of 0.17 times the inter-particle
-distance. The minimum halo mass in the models we construct in this \documentname
-correspond to groups of $\sim 75$ particles. The catalogs were
-obtained from the publicly available Multidark database \footnote{{\tt
-    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
-We focus our work on halos more massive than $1\times 10^{10}$\hMsun
-that are resolved with at least $70$ particles ({\bf REFF???? or support???})
+distance. The catalogs were obtained from the publicly available
+Multidark database \footnote{{\tt
+    http://www.multidark.org/MultiDark/}}
+\citep{2011arXiv1109.0003R}. We focus our work on halos more massive
+than $1\times 10^{10}$\hMsun that are resolved with at least $70$
+particles, the reasons for this choice are explained in the next
+section.
 
@@
 
-In our model a dark matter halo can only host one or zero LAE. 
+In our model a dark matter halo can only host one LAE at most. 
 There are three parameters in the model that decide whether a halo can host a
@@
   random}, whereby all the $11$ fields are selected in such a way as
-to avoid that any two volumes are contiguous.
+to avoid that any two volumes are contiguous. In this \documentname we
+only report the results obtained by the {\texttt match} method that
+are also obtained in the {\texttt random} selection.
 
@@
 \begin{equation}
-\xi(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{\gamma}
+\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}
 \label{eq:fitting}
@@
 to include poissionian and cosmic-variance errors. 
-We consider that a model is consistent with observations if the two parameters $\gamma$ and $\theta_0$ are
+We consider that a model is consistent with observations if the two parameters $\beta$ and $\theta_0$ are
 equal within a $1$-$\sigma$ range.
@@
 
-\subsection{Surface density distributions}
+\subsection{Models consistent with the surface density distributions}
 
@@
 \end{center}
-\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\gamma$) 
+\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
 in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_mmax.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_focc.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_f_occ.pdf}
 \end{center}
@@
 Figure \ref{figure:correlation_parameters} shows the main results in a
-$\theta_{0}-\gamma$  plane where the average and standard deviation
+$\theta_{0}-\beta$  plane where the average and standard deviation
 for each mock is shown in comparison with the result derived from
@@
 consistent if there is an overlap of $1-\sigma$ in its values for the
-correlation length $\theta_0$ and the power $\gamma$ in the
+correlation length $\theta_0$ and the power $\beta$ in the
 correlation function.  As before, we found similar results using the {\tt random} method
@@
 
-... \cite{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.
+\cite{Ouchi2010} presents an analysis of LAE observations in the
+redshift interval $3.1<z<7.0$. At $z=3.1$ They get to an average
+mass for the host dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times
+10^{10}$ \hMsun with a corresponding duty cycle of $0.008\pm
+0.03$. This broadly matches the expectations from the first family of
+models, also summarized in Table \ref{table:firstfamily}. In
+particular it seems to favor only the very low occupations fractions.
 
@@
 \end{center}
-\caption{\label{table:thirdfamily}List of parameters for the first
+\caption{\label{table:firstfamily}List of parameters for the first
   family of models. Narrow   mass range $\Delta M\leq 1.0$dex and low

### 2013-07-29 paper/ms.tex
minor abstract changes

@@
 are constructed in a large cosmological N-body simulation using a
-model where a dark matter halo can only host one LAE with a
-probability $f_{\rm occ}$  if its mass is within the mass range
-delimited by two threshold values  $M_{\rm min}$ and $M_{\rm max}$. We
-define three different families of parameters consistent with
-observations based on their mass range
+model where a dark matter halo with mass in the range $M_{\rm
+  min}<M_{\rm h}<M_{\rm max}$ can only host one LAE with a
+probability $f_{\rm occ}$. We define three different families of
+parameters consistent with observations based on their mass range
 $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
@@
 $f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm   max}<
-10^{12}$\hMsun.  This suggests that the most massive dark matter halos
-at that epoch do not host the brightest LAEs, also giving support to
-some observational evidence indicating that only a small fraction of
-star forming galaxies can be actually detected as LAEs. We provide
-tables and mock catalogs for the successful models.   
+10^{12}$\hMsun.  The existence of this dominant family gives support
+to the idea that the most massive dark matter halos at that epoch do
+not host the brightest LAEs and that only a small fraction of star
+forming galaxies can be actually detected as LAEs.
+
 \end{abstract}

### 2013-07-30 paper/ms.tex
new title, different abstract and improved intro

@@
 \title[Halo mass and occupation fraction for LAEs at
-  $z=3.1$]{Constraints on the mass and occupation
-  fraction of dark matter halos hosting Lyman-alpha emitters
-  at $z\sim 3$}    
+  $z=3.1$]{Mass and occupation
+  fraction of dark matter halos hosting Lyman-$\alpha$ emitters
+  at $z\sim 3$: limitations imposed by cosmic variance}    
 \author[~J.~E. Forero-Romero and ~J.~E Mejia-Restreo]{
@@
 matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
-$z=3.1$, by comparing the number density and the angular
-correlation function between mock and observed fields. The mock fields
-are constructed in a large cosmological N-body simulation using a
-model where a dark matter halo with mass in the range $M_{\rm
-  min}<M_{\rm h}<M_{\rm max}$ can only host one LAE with a
-probability $f_{\rm occ}$. We define three different families of
-parameters consistent with observations based on their mass range
-$\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ dex and occupation
-fraction $f_{\rm occ}$.  From this we conclude that the number
-density and spatial clustering information available from observations
-is not sufficient to derive a unique and narrow set of values for the
-parameters in the model. In particular, it is always possible to find a 
-a model with any desired occupation fraction in the range $0.1\leq
-f_{\rm occ}\leq 1.0$.  However, there is a dominant family composed by
-models with a narrow mass range $\Delta M<1.0$ dex, a low occupation fraction
+$z=3.1$ by matching the number density and the angular
+correlation function between mock and observed fields. We explicitly
+take into account the cosmic variance on the typical observed field size by
+constructing mock fields from a large cosmological N-body
+simulation matching observational geometries. To populate the
+halos in the simulation we use a model where a dark matter halo with
+mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host one LAE with a
+probability $f_{\rm occ}$. We find that the large scatter in the mocks, induced by
+cosmic variance, makes the number density and spatial clustering
+information insufficient to derive a
+unique and narrow set of values for the parameters in the model. In
+particular, it is always possible to find a consistent model with any
+desired occupation fraction in the range $0.1\leq f_{\rm occ}\leq
+1.0$.  Nevertheless, in the models we can define three
+different families of parameters based on their mass range $\Delta M
+\equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ and occupation
+fraction $f_{\rm occ}$. The dominant family is composed by models with
+a narrow mass range $\Delta M<1.0$ dex, a low occupation fraction
 $f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm  max}<
@@
 populations, markers of the galaxy formation process through
-cosmic history \citep{ForeroRomero2012}. and tracers of active star formation 
-\citep{Guaita2013}
+cosmic history \citep{ForeroRomero2012} and tracers of active star
+formation  \citep{Guaita2013}
 
@@
 that dominant matter content of the Universe is to be found in dark
-matter, whereby each galaxy is hosted by larger dark matter structure
+matter (DM), whereby each galaxy is hosted by larger dark matter structure
 known as a halo. \citep{Peebles1980}
@@
 star formation cycle are also though to be strongly dependent on its
-mass. Furthermore, the spatial clustering of galaxies on large scales
-is entirely dictated by the halo distribution.  For the reasons
-mentioned above, finding the typical dark matter halo mass hosting
-LAEs represents a significant step forward to understand the nature of
-this population in the context of Lambda Cold Dark Matter
-($\Lambda$CDM) paradigm.
+mass.  For the reasons mentioned above finding the typical dark matter
+halo mass hosting LAEs represents a significant step forward to
+understand the nature of this population in the context of Lambda Cold
+Dark Matter ($\Lambda$CDM) paradigm.
 
@@
 density, temperature, topology and kinematics of the neutral Hydrogen
-in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011, Dijkstra2012,
-Laursen2013,Orsi2012}.
+in the interstellar medium (ISM) \citep{Neufeld1991,ForeroRomero2011,
+  Dijkstra2012,Laursen2013,Orsi2012}.
 
@@
 
-Our objective in the present \documentname is to use a method to
-bypass all the complexity involved in the estimation of the \ly escape
-fraction to infer information relevant to the understanding of LAEs in
-a cosmological context. The analysis we present is thus based on one
-of the most robust prediction of $\Lambda$CDM, namely the clustering
-and abudance of dark matter halos. We construct a simple model that
-allow us to construct mock catalogs and explore a wide range of
-parameters to narrow the mass interval of halos hosting LAEs together
-with its occupation fraction.
+Another approach uses the spatial information to infer the typical
+mass of the hosting dark matter halo. This uses the fact that in cold
+dark matter cosmologies the spatial clustering of galaxies on large
+scales is entirely dictated by the halo distribution
+\citep{Colberg00}, which in turn has a strong dependence on halo
+mass. Using measurements of the angular correlation function of LAEs,
+observers have put constraints on the typical mass and occupation
+fraction of the putative halos hosting these galaxies
+\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In this
+studies the observations were done on single fields of $\sim 1$
+deg$^{2}$ and the conclusions derived on the halo host mass from
+clustering information do not delve to deeply into the impact of
+cosmic variance.
 
-Another central point in our study is the explicit inclusion of cosmic
-variance effects by using large volume cosmological simulations. This
-allows us to go closer to the space of observables and directly
-explore the compatibility of a model with observations.
+Recently \cite{Yamada2012} observed a wide area a bit more than ten
+times the sky area covered so far, all of it with the same instrument
+and the same criteria to reduce the observational data and produce LAE
+catalogs. This large data-set allows a first observational study on the
+expected cosmic variance effects in LAEs at $z=3.1$. This motivate us
+to perform such a study from a theoretical persepective and study the
+effects of the explicit inclusion of cosmica variance effects by using
+a large N-body cosmological simulation. This
+allows us to build mock fields resembling the observational geometry
+and and directly expore the compatibility of a model with
+observations.
 
-This paper is structured as follows. In the next section we present
+In this \documentname, besides studying the impact of cosmic variance,
+we implement a method to populate the DM halos with LAEs that bypasses
+all the uncertainty involved in the estimation of star formation rates
+and \ly escape fraction. Our model only defines whether a DM hosts a
+detectable LAE or not. It does not predict a \lya luminosity. By using
+this model we want to define the preferred mass range of DM halos
+hosting these galaxies and the fraction of such halos that actually
+can host a LAE.  Once the mock catalogs are constructed in this model
+we proceed with a direct comparison against the statistics derived
+from observations.
+
+This \documentname is structured as follows. In the next section we present
 the simulation and model used to produce the mock catalogs and the criteria

### 2013-07-31 paper/ms.tex
abstract + intro

@@
 \newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\lya}{{Lyman$\alpha$~}}
 \newcommand{\clara}{{\texttt{CLARA}}~}
@@
 constructing mock fields from a large cosmological N-body
-simulation matching observational geometries. To populate the
+simulation matching the observational geometries. To populate the
 halos in the simulation we use a model where a dark matter halo with
@@
 cosmic variance, makes the number density and spatial clustering
-information insufficient to derive a
-unique and narrow set of values for the parameters in the model. In
-particular, it is always possible to find a consistent model with any
-desired occupation fraction in the range $0.1\leq f_{\rm occ}\leq
-1.0$.  Nevertheless, in the models we can define three
-different families of parameters based on their mass range $\Delta M
-\equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ and occupation
-fraction $f_{\rm occ}$. The dominant family is composed by models with
-a narrow mass range $\Delta M<1.0$ dex, a low occupation fraction
-$f_{\rm occ}\leq 0.3$ and a maximum mass $M_{\rm  max}<
-10^{12}$\hMsun.  The existence of this dominant family gives support
-to the idea that the most massive dark matter halos at that epoch do
-not host the brightest LAEs and that only a small fraction of star
-forming galaxies can be actually detected as LAEs.
+information insufficient to derive a unique and narrow set of values
+for the parameters in the model. In particular, it is always possible
+to find a model that is consistent with observations and has any
+desired occupation fraction in the range $0.1\leq f_{\rm occ}\leq 1.0$
+.  Nevertheless, in the models we can define three different families
+of parameters based on their mass range $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ and occupation fraction
+$f_{\rm occ}$. The dominant family is composed by models with a narrow
+mass range $\Delta M<1.0$ dex, a low occupation fraction $f_{\rm
+  occ}\leq 0.3$ and a maximum mass $M_{\rm  max}< 10^{12}$\hMsun.  The
+existence of this dominant family gives support to the idea that the
+most massive dark matter halos at that epoch do not host the brightest
+LAEs and that only a small fraction of star forming galaxies can be
+actually detected as LAEs.
 
@@
 matter (DM), whereby each galaxy is hosted by larger dark matter structure
-known as a halo. \citep{Peebles1980}
+known as a halo. \citep{Peebles1980,SpringelNature05}.
 
-Most models of galaxy formation find that the mass of the halo can be
-used to predict properties of the galaxy such as its stellar mass and
+Most models of galaxy formation find that halo mass can be
+used to predict galaxy properties such as the stellar mass and
 star formation rate \citep{Behroozi2012}. Processes that regulate the
 star formation cycle are also though to be strongly dependent on its
-mass.  For the reasons mentioned above finding the typical dark matter
-halo mass hosting LAEs represents a significant step forward to
-understand the nature of this population in the context of Lambda Cold
-Dark Matter ($\Lambda$CDM) paradigm.
+mass.  For these reasons, finding the typical dark matter halo mass
+hosting LAEs represents a significant step forward to understand the
+nature of this galaxy population in the context of Lambda Cold Dark
+Matter ($\Lambda$CDM) paradigm.
 
 Some theoretical approaches to this problem have been based on
-ab-initio approach modeling. Starting from the DM halo population, the
+ab-initio approach. Starting from the DM halo population, the
 corresponding intrinsic star formation properties are inferred
@@
 
-Added to the uncertainties in the astrophysical processes describing
-star formation in galactic populations, a highly debated step in this
-approach is the calculation of the fraction of \ly photons
-that escape the galaxy to the observer. Given the resonant nature of
-the \lya line, the radiative transfer of \ly is sensitive to the
+In addition to the uncertainties in the astrophysical processes describing
+star formation in galactic populations, is the calculation of the fraction of \ly photons
+that escape the galaxy to the observer is another debated step. Given the resonant nature of
+the \ly line, the radiative transfer of \ly is sensitive to the
 density, temperature, topology and kinematics of the neutral Hydrogen
-in the interstellar medium (ISM) \citep{Neufeld1991,ForeroRomero2011,
+in the interstellar medium (ISM). \citep{Neufeld1991,ForeroRomero2011,
   Dijkstra2012,Laursen2013,Orsi2012}.
 
-This complexity can be tackeld with monte-carlo simulations for the
-radiative transfer a required tool to obtain physically sound results,
-although the degeneracy in the physical parameters involved in the
-problem makes it difficult to achieve a robust consensus on what is
+This problem can be tackeld with Monte Carlo simulations for the
+radiative transfer, however the complexity of the relevant physical
+processes makes it difficult to achieve a robust consensus on what is
 the theoretical expected value for the \ly escape fraction
@@
 
-Another approach uses the spatial information to infer the typical
-mass of the hosting dark matter halo. This uses the fact that in cold
+Another approach to infer the typical DM halo mass of halos hosting
+LAEs is based on the spatial information. This uses the fact that in cold
 dark matter cosmologies the spatial clustering of galaxies on large
@@
 Recently \cite{Yamada2012} observed a wide area a bit more than ten
-times the sky area covered so far, all of it with the same instrument
-and the same criteria to reduce the observational data and produce LAE
-catalogs. This large data-set allows a first observational study on the
-expected cosmic variance effects in LAEs at $z=3.1$. This motivate us
-to perform such a study from a theoretical persepective and study the
-effects of the explicit inclusion of cosmica variance effects by using
-a large N-body cosmological simulation. This
-allows us to build mock fields resembling the observational geometry
-and and directly expore the compatibility of a model with
-observations.
+times the sky area covered so far by individual campaigns. The
+observations were done with the same instrument and same criteria to
+reduce the observational data and produce LAE catalogs. This large
+data-set allows us to make the first study on the expected cosmic
+variance effects in LAEs at $z=3.1$ and its impact on the
+determination of the halo mass and occupation fraction.
 
-In this \documentname, besides studying the impact of cosmic variance,
-we implement a method to populate the DM halos with LAEs that bypasses
-all the uncertainty involved in the estimation of star formation rates
-and \ly escape fraction. Our model only defines whether a DM hosts a
-detectable LAE or not. It does not predict a \lya luminosity. By using
-this model we want to define the preferred mass range of DM halos
-hosting these galaxies and the fraction of such halos that actually
-can host a LAE.  Once the mock catalogs are constructed in this model
-we proceed with a direct comparison against the statistics derived
-from observations.
+In this \documentname to study the impact of cosmic variance,
+we implement a method to populate the DM halos in cosmological
+simulations with LAEs. This approach bypasses all the uncertainty
+involved in the estimation of star formation rates and \ly escape
+fraction. The model only considers whether a DM can host a
+detectable LAE or not. It does not predict a \ly  luminosity. Once the
+mock catalogs are constructed  we proceed with a direct comparison
+against the statistics derived from observations. This allows us 
+to find the preferred mass range of DM halos hosting these galaxies
+and its occupation fraction.
 
@@
 the simulation and model used to produce the mock catalogs and the criteria
-used to compare them against observations. In \SS \ref{sec:results} we
-present the main results in terms of the parameters of our model. We
+we use to compare them against observations. In \SS \ref{sec:results} we
+present the main results for the halo mass and occupation fraction. We
 continue with a discussion of these results under the light of other
-observational results for LAEs and abundance matching models for
-galaxy formation before presenting our conclusions in \SS
+observational and theoretical results. Finally, we present our
+conclusions in \SS
 \ref{sec:conclusions}.
@@
 At the low mass end, such cut can be readily interpreted in terms of the
-minimal halo star formation rate needed to produce the necessary \lya
+minimal halo star formation rate needed to produce the necessary \ly 
 luminosity to be above a given detection threshold.  However, under

### 2013-07-31 paper/ms.tex
conclusions

@@
 \title[Halo mass and occupation fraction for LAEs at
-  $z=3.1$]{Mass and occupation
+  $z=3.1$]{Finding the mass and occupation
   fraction of dark matter halos hosting Lyman-$\alpha$ emitters
-  at $z\sim 3$: limitations imposed by cosmic variance}    
+  at $z\sim 3$: the importance of cosmic variance}    
 \author[~J.~E. Forero-Romero and ~J.~E Mejia-Restreo]{
@@
 .  Nevertheless, in the models we can define three different families
-of parameters based on their mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ and occupation fraction
+of parameters based on their mass range, $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, and occupation fraction,
 $f_{\rm occ}$. The dominant family is composed by models with a narrow
@@
 high absorption of \ly photons but not of continuum or
-other n-resonant lines \citep{ForeroRomero2011,Laursen2009}.
+other n-resonant lines \citep{Laursen2009,ForeroRomero2011}.
 
@@
 
-In this \documentname we constrain the preferred mass
+In this \documentname we look for constraints on the preferred mass
 and occupation fraction of dark matter halos hosting Lyman Alpha Emitters at
-redshift $z=3.1$ in a $\Lambda$CDM cosmology. We use a method that
-matches the cosmic variance of the surface 
-density number of LAEs between mock and real observations and is also
-consistent with estimations of the angular
-correlation function. The mock catalogs are constructed using a 
-model with three basic parameters: the halo mass range where LAEs can
-be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
-the halos in this range that host a detectable LAE, $f_{\rm occ}$. After
-a thorough exploration of the parameter space we find that a wide
-variety of models are consistent with the observational constraints,
-where only a minority has been considered so far in the
-literature. Out of $9000$ initial combinations for the model
-parameters we end up with $49$ successful arrangement of parameters.
+redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform this study
+paying attention to the impact of cosmic variance in these results. We
+build a large number of mock catalogs matching observational
+geometries. The mocks are constructed from a N-body simulation
+following a simple recipe to assign a single LAE to each halo. Only
+a fraction $f_{\rm occ}$ of halos with a mass range  $M_{\rm
+  min}<M_{\rm h}<M_{\rm   max}$ can host a LAE. We proceed with a
+thourough exploration of the space of free parameters $M_{\rm min},
+M_{\rm max}$ and $f_{\rm occ}$ to find mocks that are consistent with
+two observational constraints: the surface number density and the
+angular correlation function. Out of the initial $9000$ initial
+combinations of parameters in the model we find $49$ arrangements
+consistent with observations.
 
-The most important conclusion of this work is that available
-observational information for the clustering properties of LAEs at
-$z=3.1$ does not provide enough constraints to uniquely narrow the range of masses
-and occupation fraction of dark matter halos hosting those
-galaxies. In particular we are not able to put a stringent constraint
-on the occupation fraction $f_{\rm occ}$.
+The most relevant result from our study is the following. The 
+successful parameter arrangements present a wide range of possibilities for
+DM hosting LAE hosts at $z=3.1$. This means that the available LAEs' spatial
+information is not sufficient to put a tight constraint on the mass
+and occupation fraction of DM halos hosting LAEs. In particular it is
+not possible to put a strong constraint on the occupation
+fraction. Such a wide range in solutions is facilitated by the large
+dispersion in the statistics derived from the mocks. All the halo mass
+ranges and occupation fractions deduced in previous analysis in
+previous analysis \citep[i.e.][]{Gawiser2007} are a subset of the
+models we find in this \documentname.
 
-In our results the models can be split into three families
+Nevertheless, the sucessful models can be split into three families
 depending the mass range $\Delta M=\log_{10}M_{\rm max} -
-\log_{10}M_{\rm min}$ and the occupation fraction $f_{\rm occ}$. The first family is narrow both in
-$\Delta M$ and $f_{\rm occ}$, a second family is only narrow in
-$\Delta M$ and the third is narrow in $f_{\rm occ}$ and broad in
-$\Delta M$.
+\log_{10}M_{\rm min}$ and the occupation fraction $f_{\rm occ}$. The
+first family is narrow both in $\Delta M$ and $f_{\rm occ}$, a second
+family is only narrow in $\Delta M$ and the third is narrow in $f_{\rm
+  occ}$ and broad in $\Delta M$.
 
-All the halo mass ranges in the best models fall into the broad
-range obtained in previous analysis \citep{Gawiser2007}. The
-improvement of our method is being able to describe in high detail
-all the possible models consistent with observations, including the
-discovery of models previously overlooked like those with a high
-occupation fraction $f_{\rm occ}>0.3$.
+A second results from our investigation is the existence
+of a large number of models with a very narrow mass range $\Delta M<
+0.1$ dex that are consistent in every aspect with the spatial
+distribution of observed LAEs. In order to have these characteristics
+it is required that halos around the mass $M_{\rm   max}$ for each
+model become inefficient in hosting detectable LAEs. Two possible
+ways to achieve this is having LAEs with a decreasing \ly escape
+fraction with increasing mass or increasing screening effects by
+neutral Hydrogen around the most massive systems
+\citep{Laursen2009,ForeroRomero2011}.
 
-A central result in this exploration of parameter espace is the
-existence of a large number of models with a very
-narrow mass range $\Delta M< 0.1$ dex that are consistent in every
-aspect with the spatial distribution of observed LAEs. In order to
-have these characteristics it is required that halos around the mass
-$M_{\rm max}$ for each model become inefficient in hosting detectable
-galaxies. One way to achieve this is having LAEs with a decreasing \ly
-escape fraction with increasing mass.
-
-All the models also present a range of masses where the halos are
-below the mass scale of $10^{11.4}$\hMsun \  inferred as a lower
-threshold for the LBGs used in halo abundance matching
-studies. Detailed study of high-z LAES will have a positive impact on
-our understanding of the connection of low mass halos to star forming
-galaxies.
+A third aspect that stands out is the existence of a dominant family
+of models with narrow $\Delta M<0.1$, as described before, and also a
+low occupation fraction $f_{\rm occ}<0.3$. This gives support to the
+common wisdom stating that only a small fraction of star forming
+galaxies can be detected as strong LAEs.
 
@@
 Institute for Advanced Study where the first full draft of this paper
-was completed. J.E.F-R also thanks Peter Laursen for helpful comments
-on the physical interpretation and the presentation of our results.
+was completed. The authors also thank Peter Laursen, Paulina Lira and
+Alvaro Orsi for helpful comments on the physical interpretation and
+the presentation of our results.
 

### 2013-08-01 paper/ms.tex
updating the methodology

@@
 \title[Halo mass and occupation fraction for LAEs at
-  $z=3.1$]{Finding the mass and occupation
+  $z=3.1$]{Mass and occupation
   fraction of dark matter halos hosting Lyman-$\alpha$ emitters
-  at $z\sim 3$: the importance of cosmic variance}    
+  at $z\sim 3$}    
 \author[~J.~E. Forero-Romero and ~J.~E Mejia-Restreo]{
@@
 actually detected as LAEs.
-
 \end{abstract}
@@
 
-Our method is based on the comparison of observatios and mock
-catalogs on the surface number density and the angular correlation
-function of LAEs.  In the next subsections we describe in detail the four key
+Our method is based on the comparison of observations and mock
+catalogs. We use two different kinds of statistics to perform the
+comparison: (i) the distribution of the surface number density
+across fields fields and (ii) the angular correlation function measured in
+some fields.
+
+In the next subsections we describe in detail the four key
 elements of this workflow. First, we present the observations we take
-as a benchmark. Second, the N-body simulation and the halo catalogs we
-use. Third, the simplified model that allows us to translated halo
-catalogs into mock LAE observations. Fourth, the statistics we use to
-compare observational results against our theoretical predictions.
+as a benchmark. Second, we describe the main characteristics of the
+N-body simulation and the halo catalogs we use. Third, we recount the
+important parameters of the simplified model that we use to populate
+the halo catalogs with LAEs. Finally we describe some of the
+statistical tests we adopt to compare observations and mocks.
 
@@
 
-One of the main observational benchmarks we use in this paper is the LAE number
+The first observational constraint we use in this paper is the LAE number
 density information at $z=3.1$ obtained by the panoramic narrow-band
@@
 comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
-band filter is centered at $4977$ \AA with  $77$\AA width,
+band filter used in the survey is centered at $4977$ \AA with  $77$\AA width,
 corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
@@
 over a total survey area of $2.42$ deg$^{2}$ that includes 12 subfields, 
-this corresponds to average surface number density of $0.20\pm 0.01$ arcmin$^{-2}$.
+this corresponds to average surface number density of $0.20\pm 0.01$
+arcmin$^{-2}$.
 
@@
 we use the results by \cite{Hayashino2004} and
-\cite{Ouchi2008,Ouchi2010}.
-
-\cite{Hayashino2004} observed in the densest field of
-SSA22 while \cite{Ouchi2008} observed on a 1 deg$^2$ sky of the
-Subaru/XMM-Newton Deep Survey (SXDS) Field.  There are some
-differences between these observations and those iby
-\cite{Yamada2012}. The details in the color selection, corresponding
-limiting luminosities and EW thresholds are different in these
-references. Nevertheless we use these observations as additional
-constraints in spite of the fact that the first selected models are
-based only on the surface density statistics by \citep{Yamada2012}.
+\cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
+densest field of SSA22 while \cite{Ouchi2008} observed on a 1 deg$^2$
+sky of the SXDS Field.  There are some differences between these
+observations and those by \cite{Yamada2012}. The details in the color
+selection, corresponding limiting luminosities and EW thresholds are
+different in these references. Nevertheless we use these observations
+as additional constraints in spite of the fact that the first selected
+models are based only on the surface density statistics by
+\citep{Yamada2012}.
 
@@
     http://www.multidark.org/MultiDark/}}
-\citep{2011arXiv1109.0003R}. We focus our work on halos more massive
-than $1\times 10^{10}$\hMsun that are resolved with at least $70$
-particles, the reasons for this choice are explained in the next
-section.
+\citep{2011arXiv1109.0003R}. For each halo in the box we store its
+position in the box (3-D coordinates) and FOF mass. We focus our work
+on halos more massive than $1\times 10^{10}$\hMsun that are resolved
+with at least $70$ particles, the reasons for this choice are
+explained in the next sub-section.
 
@@
 
-In our model a dark matter halo can only host one LAE at most. 
-There are three parameters in the model that decide whether a halo can host a
-galaxy or not: the lower and upper bounds for the mass range $M_{\rm min}<
+We assume that a dark matter halo can only host one
+detectable LAE at most.  There are three parameters that
+decide whether a halo host a LAE: the lower and upper bounds for the mass range $M_{\rm min}<
 M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
-  occ}$ of such halos that host a \emph{detectable LAE}. The reader
+  occ}$ of such halos that host a detectable LAE. The reader
 must keep in mind that the physical interpreation of the occupation
-fraction $f_{\rm occ}$ convolves two things: the presence of a star
-forming galaxy in a halo and its detectability as a LAE. We do not assign a
-luminosity to each LAE. We are primarily interested in
-constraining the halo mass range hosting detectable LAEs under the
-conditions defined by \cite{Yamada2012}. In what follows we will describe by
-the letter ${\mathcal M}$ a model defined by an specific choice of the
-three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ and $f_{\rm occ}$.
+fraction $f_{\rm occ}$ convolves two phenomena: the presence of a star
+forming galaxy in a halo and its detectability as a LAE.  We do not
+peform a explicit modeling for LAE detectability. Our model does not
+assign a luminosity or escape fraction to each LAE.  We are only
+interested in constraining the halo mass range hosting detectable LAEs
+under the conditions defined by \cite{Yamada2012}.
 
-For each model ${\mathcal M}$ we create a set of mock fields from
-disjoint volumes in the simulation. Each volume has the same geometry
-probed by Suprime-CAM and the narrow band filter, namely rectangular
-cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
-the last dimension goes in the redshift direction. This corresponds to
-a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
-$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
+In what follows we note by the letter ${\mathcal M}$ a model
+defined by a particular choice of the three scalar parameters $M_{\rm
+  min}$, $M_{\rm  max}$ and $f_{\rm occ}$. For each model ${\mathcal
+  M}$ we create a set of mock fields from disjoint volumes in the
+simulation. Each volume has the same geometry probed by Suprime-CAM
+and the narrow band filter, namely rectangular cuboids of dimensions
+$46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$ where the last dimension goes
+in the redshift direction. This corresponds to a total area of $880$
+arcmin$^{2}$ in each mock field. We construct a total $5\times 7
+\times 6=210$ of such volumes from a snapshot in the Bolshoi
 simulation. In each mock field a LAE is assigned to the position of a
@@
 
-Next we construct mock surveys by making groups of $11$ mock fields
+Next we construct mock surveys by making groups of $12$ mock fields
 out of the $210$ available volumes. In total $15$ mock surveys are
-constructed for each model $\mathcal{M}$. The grouping is done in two
-different ways. In the first way, called {\texttt match}, we follow
-the clustering of the observed fields. From the $11$ mock fields, $7$
-are constructed from contiguous fields in the simulation to mimic the
-SSA22 region, $3$ are also contiguous between them but not to the first
-$7$ fields to mimic the SXDS fields and finally $2$ non-contiguous
-fields to imitate the SDF and GOODS-North field. Our main goal with
-this selection is to test the impact on the final statistics of having
-$7$ clustered fields. The second way to group the mock fields is called {\texttt
-  random}, whereby all the $11$ fields are selected in such a way as
-to avoid that any two volumes are contiguous. In this \documentname we
-only report the results obtained by the {\texttt match} method that
-are also obtained in the {\texttt random} selection.
+constructed for each model $\mathcal{M}$. The grouping of the $11$
+mock fields into a mock catalog is done in two different ways. The
+first is called {\texttt match}, it follows the clustering of the
+observational fields. From the $12$ mock fields, $7$ are constructed
+from contiguous fields in the simulation to mimic the SSA22 region,
+$3$ are also contiguous between them but not to the first $7$ fields
+to mimic the SXDS fields and finally $2$ non-contiguous fields to
+imitate the SDF and GOODS-North field.  The second way to group the
+mock fields is called {\texttt   random}, whereby all the $11$ fields
+are selected in such a way as to avoid that any two volumes are
+contiguous. In this \documentname we only report the results obtained
+by the {\texttt match} method and mention explicitly differences
+observed with the {\texttt random} selection.
 
-\subsection{Sampling and Selecting Models}
+\subsection{Exploring and Selecting Good Models}
 
@@
 that models in that mass range and an occupation fraction $f_{\rm
-  occ}$ have the possibility to be compatible with observations. Lower
+  occ}=0.1$ have the possibility to be compatible with observations. Lower
 values for $M_{\rm min}$ require $f_{\rm occ}<0.1$, which are not
@@
 compute the surface density in the $12$ mock fields. We perform a
-Kolmogorov-Smirnov (KS) to compare this mock date against the $12$
+Kolmogorov-Smirnov (KS) to compare this mock data against the $12$
 observational values. From this test we obtain a value $0<P<1$ to
@@
 
-We then calculate the  angular correlation function (ACF)
+The second constraint  comes from the angular correlation function (ACF)
 for all the models having the $15$ mock surveys consistent with
@@
 to include poissionian and cosmic-variance errors. 
-We consider that a model is consistent with observations if the two parameters $\beta$ and $\theta_0$ are
-equal within a $1$-$\sigma$ range.
+We consider that a model is consistent with observations if the two
+parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$ range.
 

### 2013-08-02 paper/ms.tex
updated subsection on the dark matter halo number density

@@
 
-In addition to the uncertainties in the astrophysical processes describing
-star formation in galactic populations, is the calculation of the fraction of \ly photons
-that escape the galaxy to the observer is another debated step. Given the resonant nature of
-the \ly line, the radiative transfer of \ly is sensitive to the
-density, temperature, topology and kinematics of the neutral Hydrogen
-in the interstellar medium (ISM). \citep{Neufeld1991,ForeroRomero2011,
-  Dijkstra2012,Laursen2013,Orsi2012}.
+In addition to the uncertainties in the astrophysical processes
+describing star formation in galactic populations, is the calculation
+of the fraction of \ly photons that escape the galaxy to the observer
+is another debated step. Given the resonant nature of the \ly line,
+the radiative transfer of \ly is sensitive to the density,
+temperature, topology and kinematics of the neutral Hydrogen in the
+interstellar medium
+(ISM). \citep{Neufeld1991,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
 
@@
 observational constraints narrow down the parameters space of allowed
-models. In each one of the four sub-sections we add a new
-constraint. First we consider the average halo number density, then we
-consider the surface density distributions for all the mock fields in
-a given mock survey. From this result we move to narrower constraints
-by requiring a high number of mock surveys with consistent surface
-density distributions to finally consider the impact of the angular
-correlation function.
+models. Each sub-sections presents the effect of adding new pieces of
+observational or statistical evidence.
 
@@
 ${\mathcal M}$ can be expected to be consistent with
-observations. From Figure \ref{fig:halos} we can read that models
-with a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun \ will always have a
+observations. From Figure \ref{fig:halos} we can read that models with
+a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
 surface number density lower than the observational
-constrain. This makes impossible that models with that minimum mass
-can be compatible with observations.
+constrain. This makes impossible that models in that range can be
+compatible with observations, there are simply to few halos compared
+to observed LAEs.
 
-The opposite is true in models with $\log_{10} M_{\rm min}<10.5$
-that will show surface number density larger than observations, this
-implies that in such models the occupation fraction has to be tuned
-$f_{\rm occ}<1.0$ as to lower the halo number density to match the
-gray band values.
+The opposite is true in models with $\log_{10} M_{\rm min}<10.5$ that
+have a surface number density larger than observations. In those cases
+the occupation fraction $f_{\rm occ}<1.0$ can be tuned in order to
+lower the halo number density to match observations.
 
-In the next subsection we quantify this intuition by means of the
-Kolmogorov-Smirnov tests between mock surveys and observations.
+Figure \ref{fig:halos} also illustrates the impact of cosmic
+variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
+mass range $10^{10}\hMsun < M_{\rm  min}<10^{11}\hMsun$.  A consequence of
+this variation is that models with the same mass range and occupation
+fraction can have mock fields with number densities varying up to a
+factor of $\sim 2-5$. Also, the scatter in mocks across the simulation
+is comparable to the $0.3$ dex scatter in observations.
+
+In the same Figure \ref{fig:halos} we see that at fixed number
+density, around the range allowed by observations, there is an scatter
+in the masses of $0.4-0.5$ dex. This intrinsic scatter in the masses
+with a given number density adds is also included in the mock
+construction process, enlarging the range of possible models
+consistent with observations.
 

### 2013-08-05 paper/ms.tex
updated until subsection 3.3 (models with highest nmock consistent with observations)

@@
 \vspace{5mm}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}\\
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
-\hspace{5mm}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
+\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
+%\hspace{5mm}
+%\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
 \end{center} 
-\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
-    min}-f_{\rm occ}$ (right) planes for all models with
-  $P>0.05$ in two different ways used to construct the mock
-  surveys. The color code corresponds to the number of mock surveys
-  that are found to be compatible with observations in terms of the KS
-  test with $P>0.05$. Only regions of parameter space with at least
-  one consistent mock survey are included. \label{fig:landscape}}   
+\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}-f_{\rm
+    occ}$ (right) planes for all models with  KS test values
+  $P>0.05$. The color code corresponds to the number of  mock surveys
+  compatible with observations. Only regions of parameter  space with
+  at least one consistent mock survey are  included. \label{fig:landscape}}     
 \end{figure*}
@@
 data for the surface number density come from the same parent
-distribution.
-
-The upper (lower) panels correspond to the {\texttt match} ({\texttt
-  random}) method to build the mock surveys from individual
-fields. The plot shows number of mock surveys consistent
-with observations. There are between $550$ to $600$ models out of the
-original $9000$ models that have at least one mock survey
+distribution. In total, there are between $550$ to $600$ models out of
+the original $9000$ models that have at least one mock survey
 consistent with observations.
@@
 to models where the minimum mass is high $\log_{10}M_{\rm min}>
-11.5$. None of this models is compatible with observations as expected
-from the results in the previous subsection. For these models the number
-density of LAEs is too low compared to observations.
+11.5$. None of these models is compatible with observations as expected
+from the arguments presented in the previous subsection. For these
+models the number density of LAEs is too low compared to observations.
 
 The second region corresponds to an intermediate range for the minimum
-mass $10.5<\log_{10}M_{\rm min}<11.5$ where regardless of the value of
-the maximum mass $M_{\rm max}$ it is possible to tune the occupation
+mass $10.5<\log_{10}M_{\rm min}<11.5$ where, regardless of the value of
+the maximum mass $M_{\rm max}$, it is possible to tune the occupation
 fraction $f_{\rm occ}$ to bring some of the mock observations into
-good agreement with observations. In this region in parameter space
-one can thus find two extreme kinds of models.  One kind where the
-mass interval is very narrow with sizes smaller than $<0.3$ dex (a
-factor of two in mass) and others where the mass interval is 
-extended (larger than $1.0$ dex) going up to the maximum halo mass
-present in the simulation at that redshift (up to $2.5$ dex).
+good agreement with observations. In this region of parameter space
+one can tfind two extreme kinds of models.  One kind where the
+mass interval $\Delta M\equiv \log_{10} M_{\rm max} - \log_{10}M_{\rm
+  min}$ is narrow with $\Delta M<1.0$ dex, others where the mass interval is 
+extended $\Delta M>1.0$dex going up to the maximum halo mass
+present in the simulation at that redshift, up to $\Delta M = 2.5$ dex
+in some cases.
 
@@
 Without any additional information our method allows us to infer that
-most of the successful models are found in the second and third region of
-parameter space where this result was already expected from halo
-abundance calculations shown in Figure \ref{fig:halos}. In the next
-section we reduce the size of this region by imposing tighter
-constraints on the KS tests and consistency with the angular
-correlation function.
+most of the successful models are found in the second and third regions of
+parameter space. This result was already expected from halo
+abundance calculations shown in Figure \ref{fig:halos} and discussed
+in the previous subsection.
 
-\begin{figure*}
+However, the additional information we gain with this test is the
+relative abundance of models in the parameter space. Not all the
+models in the second region have an equal abundance. By inspection of
+Figure \ref{fig:landscape} it seems that models with $\log_{10}M_{\rm
+  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}<0.3$
+are preferred.  In the next sub-section we explore in detail the
+models in this region, imposing tighter constraints on the KS test
+results and exploring the mocks' consistency with the angular correlation
+function.
+
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
+\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
+%\hspace{5mm}
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
 \end{center} 
-\caption{ Number of models with a minimum number of mock survey
-  realizations that are consistent with observations.
+\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
+  consistent with the observed surface number density
+  distribution in terms of the KS-test values $P>0.05$. Only $\sim
+  100$ models have all their mocks consistent with observations. 
   \label{fig:high_success_rate}.}  
-\end{figure*}
+\end{figure}
 
-\subsection{Models with the highest success rates}
+\subsection{Models with the largest number of consistent mock surveys}
 
@@
 previous section we presented the models that had at least one
-mock survey with $P>0.05$.
-
-Figure \ref{fig:high_success_rate} shows the number of models
+mock survey with $P>0.05$. Figure \ref{fig:high_success_rate} shows the number of models
 that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
 {\texttt  match} and {\texttt random} methods.  This shows that there
-are between $80$ to $100$ models with all the 15 realizations with
-$P>0.05$. Selection of these models as successful represents a
-reduction of a factor of $\sim 6$ with respect to the total number of
-mocks with at least one consistent mock.
+are $\sim 100$ models with all the 15 mock survey realizations with
+$P>0.05$.
+
+We discard the models that have 14 mocks or less consistent with observations.
+This cut represents a reduction by a factor of $\sim 6$ with respect
+to the total number of models with at least one (1) consistent mock.
 
@@
 in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
-  min}-f_{\rm occ}$. The results are very similar between the {\texttt
-  match} and {\texttt random} methods. With this constraints the
-number of consistent models with  $\log_{10}M_{\rm min}< 11.5$ are
+  min}-f_{\rm occ}$. With this constraints the
+number of consistent models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are
 greatly reduced. This corresponds to the regions in the parameter
@@
 Figure \ref{fig:restriction_mock} one can see that there is not a
-strong constraint on the occupation fraction $f_{\rm occ}$.
+strong reduction on the favored values for the occupation fraction
+$f_{\rm occ}$.
 

### 2013-08-08 paper/ms.tex
edits on the consistency with the ACF

@@
 \caption{Favored regions in parameter space when the constraints on
-  the maximal number of consistent mocks is imposed. The results for
-  the {\texttt random} methodology (not shown here) are very similar to the ones
-  presented here for the {\texttt match} method.
+  the maximal number of consistent mocks is imposed. Only the results
+  for the {\texttt match} method are shown.
   \label{fig:restriction_mock}}  
@@
 \hspace{5mm}  
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf} 
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
+%\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
 \end{center}
 \caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
-in the fitting formula (Eq. \ref{eq:fitting}) for the mean angular
-correlation function. Blue dots correspond to simulations and the green cross to
-observations by \citet{Hayashino2004}. The error bars in the 
-theoretical data correspond to the standard deviation from the
-different mocks surveys. Right: Same results as before in the shown in
-the $\theta_{0}$-$M_{\rm min}$ plane. This time the observational
-constraints are represented by the red rectangle. Blue squares
-represent models with $\log_{10} M_{\rm  max}<12.0$, green circles
-correspond to models with $\log_{10} M_{\rm max}>12.0$. 
-\label{figure:correlation_parameters}}
+in the fitting formula (Eq. \ref{eq:fitting}) for the angular
+correlation function. Blue dots correspond to simulations and the
+green cross to observations by \citet{Hayashino2004} and
+\citet{Ouchi2010}. The error bars in the   theoretical data correspond
+to the standard deviation from the different mocks surveys. 
+%Right:
+%Same results in the $\theta_{0}$-$M_{\rm min}$ plane, with the
+%observational constraint on $\theta_{0}$ epresented by the red
+%rectangle. Blue  squares represent models with $\log_{10} M_{\rm
+%  max}<12.0$, green circles correspond to models with $\log_{10}
+%M_{\rm max}>12.0$. 
+\label{fig:correlation_parameters}}
 \end{figure*}
@@
 \end{center}
-\caption{Best models parameter space when both the constraints on the
-  maximal number of  consistent mocks and the occupation  fraction
-  $f_{\rm occ}\leq  0.2$ are included. $M_{\rm min}$ vs $M_{\rm max}$
-  (left), $M_{\rm min}$ vs $f_{\rm occ}$ (rigth).
+\caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
+  vs $f_{\rm occ}$ (rigth). The squares represent the models when both
+  th constraints on the maximal number of  consistent mocks and the
+  angular correlation function are included. 
   \label{fig:restriction_mock_and_f_occ_corr}} 
@@
 
-Figure \ref{figure:correlation_parameters} shows the main results in a
+Figure \ref{fig:correlation_parameters} shows the main results in a
 $\theta_{0}-\beta$  plane where the average and standard deviation
-for each mock is shown in comparison with the result derived from
+over the mocks is shown in comparison with the result derived from
 observations.  The error bars in this Figure represents the standard
@@
 
-In the left panel Figure \ref{figure:correlation_parameters} we see how
-the observational ACF measured by \cite{Hayashino2004} (green dot) is
-successful in reducing the total number of possible models. Only those
-with angular-correlation length within
+In the left panel Figure \ref{figure:correlation_parameters} we see
+how the observational ACF measured by \cite{Hayashino2004} (green dot)
+is successful in reducing the total number of possible models. Only
+those with angular-correlation length within
 $15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
-reproduce observations.
-
-In order to better illustrate the results from this test we
-show in the right panel of Figure \ref{figure:correlation_parameters} 
-the plane $\theta_{0}$-$M_{\rm min}$ for all models. There we divide
-the models into two disjoint sets: those with $\log_{10} M_{\rm
-    max}<12$ (blue dots) and $\log_{10} M_{\rm
-    max}>12$ (green dots). The colored rectangle includes
-the parameter region which is consistent with the observational
-constraint in $\theta_{0}$. With this restriction we find that most
-models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.1$ 
-can be safely ruled out.
+reproduce observations.     {\bf Cual es el resultsdo de Hayashino
+  para $\theta_0$?}
 
@@
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
-for the {\tt match} method after applying the observational constraints 
-in the occupation fraction and the ACF. Here we consider a model
-consistent if there is an overlap of $1-\sigma$ in its values for the
-correlation length $\theta_0$ and the power $\beta$ in the
-correlation function.  As before, we found similar results using the {\tt random} method
+for the {\tt match} method. To make this selection we consider a that
+a model is consistent with observations if there is a $1-\sigma$
+overlap between both the correlation length $\theta_0$ and the power
+$\beta$ in the correlation function. Comparing this Figure with the
+results shown in Figure \ref{fig:restriction_mock} we see that the
+models that were removed were those with highest minimal masses
+$M_{\rm min}>10^{11.2}$, for all the values of $M_{\rm max}$, which
+had preferentially high occupation fractions of $f_{\rm occ}> 0.5$.
+
+%In order to better illustrate the results from this test we
+%show in the right panel of Figure \ref{figure:correlation_parameters} 
+%the plane $\theta_{0}$-$M_{\rm min}$ for all models divided in two
+%disjoint sets. The first are the models $\log_{10} M_{\rm
+%    max}<12$ (blue dots), the second corresponds to $\log_{10} M_{\rm
+%    max}>12$ (green dots). The colored rectangle includes
+%the parameter region which is consistent with the observational
+%constraint in $\theta_{0}$.  With this restriction we find that most
+
+%models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.s$ 
+%can be safely ruled out.
 

### 2013-08-09 paper/ms.tex
dicussion section to 90%

@@
 The survey covered four independent fields. The first is the SSA22
-field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 subfields), this field has been
-known to harbor a region with a large density excess of galaxies. The
-second observed region is composed by the fields Subaru/{\it
+field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 subfields), this
+field has been known to harbor a region with a large density excess of
+galaxies. The second observed region is composed by the fields Subaru/{\it
   XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
-total of $0.58$ deg$^2$ and $386$ LAEs (3 subfields). The third and fourth fields
-are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and $196$ LAEs (1 subfield),
-and the field around the Great Observatory Optical Deep Survey North
-(GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1 subfield).
+total of $0.58$ deg$^2$ and $386$ LAEs (3 subfields). The third and
+fourth fields are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
+$196$ LAEs (1 subfield), and the field around the Great Observatory
+Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
+subfield).
 
@@
 detectable LAE at most.  There are three parameters that
-decide whether a halo host a LAE: the lower and upper bounds for the mass range $M_{\rm min}<
-M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
-  occ}$ of such halos that host a detectable LAE. The reader
+decide whether a halo host a LAE: the lower and upper bounds for the
+mass range $M_{\rm min}< M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
 must keep in mind that the physical interpreation of the occupation
@@
 observations.  The error bars in this Figure represents the standard
-deviation of the ACF over all the sub-fields in the 15 mock
-observations. These error bars are larger than the statistical
+deviation of the ACF over all the 15 mock fields used to make the
+computation.  These error bars are larger than the statistical
 uncertainty from the fitting procedure on a single field.
@@
 $15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
-reproduce observations.     {\bf Cual es el resultsdo de Hayashino
+reproduce observations. {\bf Cual es el resultsdo de Ouchi
   para $\theta_0$?}
@@
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
-for the {\tt match} method. To make this selection we consider a that
+for the {\tt match} method. To make this selection we consider that
 a model is consistent with observations if there is a $1-\sigma$
 overlap between both the correlation length $\theta_0$ and the power
-$\beta$ in the correlation function. Comparing this Figure with the
-results shown in Figure \ref{fig:restriction_mock} we see that the
-models that were removed were those with highest minimal masses
-$M_{\rm min}>10^{11.2}$, for all the values of $M_{\rm max}$, which
-had preferentially high occupation fractions of $f_{\rm occ}> 0.5$.
+$\beta$ . Comparing this Figure with the results shown in Figure
+\ref{fig:restriction_mock} we see that the models that were removed
+were those with highest minimal masses $M_{\rm min}>10^{11.2}$, for
+all the values of $M_{\rm max}$, with preferentially high
+occupation fractions of $f_{\rm occ}> 0.5$.
 
@@
 
-Matching the galaxy surface number density statistics to
-our mock  data sets the median
-mass of all successful models in the range $(10^{10}-10^{12})$
-\hMsun. Including more strict criteria on the number of mock surveys
-that must be consistent with those observations and additional
-information from the angular correlation function greatly reduces the
-number of possible models. We end up with $\sim 50$ models out of the
-initial 9000 possible combination of parameters.
+In the Results Section we start by matching the rough numbers for the
+galaxy surface number density. This sets the median mass of all
+successful models to the broad range $(10^{10}-10^{12})$ \hMsun for
+$M_{\rm min}$ and $M_{\rm max}$. We include additional criteria on the
+number of mock surveys that must be consistent observations
+and the information from the angular correlation function, reducing
+the number of feasible models. We end up with $\sim 50$ models out of
+the initial $9000$ possible combination of parameters.
 
-We find that to make a physical interpretation of these models it is
-useful to do it in terms of the size of halo mass range. We now use the
-variable $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, together
-with the occupation fraction $f_{\rm occ}$ to help us build a classification
-of all the successful models into three families:
+In order to make a physical interpretation of these models we use 
+the halo mass range, defined as $\Delta M=\log_{10}M_{\rm max} -
+\log_{10}M_{\rm  min}$, together with the occupation fraction $f_{\rm
+  occ}$ to classify all the successful models into three families:
 
@@
 At the low mass end, such cut can be readily interpreted in terms of the
-minimal halo star formation rate needed to produce the necessary \ly 
+minimal halo star formation rate needed to produce the minimal \ly 
 luminosity to be above a given detection threshold.  However, under
@@
 mass, the cut at higher halo masses requires a different
-explanation. There are two different physical scenarios to explain
-this.
+justification. There are two complementary physical scenarios that can
+provide an explanation.
 
-One possible interpretation can be made in terms of a decreasing escape
+One sceneario can be presented in terms of a decreasing escape
 fraction of \ly radiation in massive systems. There are detailed models for
@@
 higher metallicities have larger dust contents and less concentrated
-ISM than lower mass systems which, due to the resonant nature of the
-\ly line that increase the probability of absortion  of\ly photons, produce
-high absorption of \ly photons but not of continuum or
-other n-resonant lines \citep{Laursen2009,ForeroRomero2011}.
+ISM than lower mass systems. Due to the resonant nature of the
+\ly line the probability of absortion  of \ly photons increases in
+massive systems, producing high absorption of \ly photons but not of
+continuum or other non-resonant lines
+\citep{Laursen2009,ForeroRomero2011}.
 
 A second scenario is that larger systems have more extended gaseous
-envelopes which, due to resonance effects of the \ly line, leading to
-a low surface brightness and a broader line, making these systems less
-observable in narrow band filter surveys \citep{Zheng2010}.
+envelopes which. Again, due to resonance effects of the \ly line,
+these systems can present a low surface brightness and a broader line,
+making these systems less observable in narrow band filter surveys
+\citep{Laursen2009,Zheng2010}.
 
-The preference for narrow $\Delta M$ ranges to hosting LAEs together
-with the minor presence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun \  shows that our models support theoretical and observational
+The preference for narrow $\Delta M$ ranges to host LAEs 
+and the minoritary presence of reasonable models with $M_{\rm max}>
+10^{12}$\hMsun follows theoretical and observational
 insights where the most massive systems are not bright \ly sources
-\citep{ForeroRomero2012}, \citep{Shapley2003}
+\citep{ForeroRomero2012,Shapley2003}.
 
-\subsection{Comparison against results from blind surveys}
+\subsection{Comparison against results from galaxy surveys}
 
@@
 preference goes in the same direction as the observational constraint
-on the escape fraction $f_{\rm esc}\sim 0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010}
-and recent theoretical study of observational data in a wide redshift
-range $0<z<6$  \citep{Dijkstra2013}.
+on the escape fraction $f_{\rm esc}\sim 0.1-0.2$ derived at $z=2.2$ by
+\cite{Hayes2010} and recent theoretical study of observational data in
+a wide redshift range $0<z<6$  \citep{Dijkstra2013}.
 
@@
 to demonstrate that the halo mass range could be very narrow $\Delta M <
-0.2$dex, something that cannot be inferred from ACF analysis
-alone.
+0.2$dex, something that cannot be inferred from ACF analysis alone.
 
-We also find interesting that our ACF analysis is also not enough to rule
+We also find that an ACF analysis on a single dataset is not enough to rule
 out models with a high occupation fraction $f_{\rm occ}>0.3$, which
 represent almost one fourth of our best models, coinciding with a wide
-range in halo masses $\Delta M>1.0$ dex. These models can only be
-considered unfavorable based on the density and abundance observations
-as we have described in the previous subsection.
+range in halo masses $\Delta M>1.0$ dex. These models cannot be
+considered unfavorable based on a clustering analysis only.
 
@@
 
-Considering the additional evidence for a low escape fraction and 
-assuming a direct relation between $f_{esc}$ and $f_{occ}$ we can
-say that the preferred models are in families (1) and (2) with a
-clear majority composed by those with narrow mass range.
-
 Abundance matching methods throughout cosmic time from redshifts
 $0<z<8$ \cite{Behroozi2013a,Behroozi2013b} work based on observational
-results for Lyman Break Galaxies. In those studies the minimum halo
+results for Lyman Break Galaxies (LBG). In those studies the minimum halo
 mass considered to be relevant in their analysis is
@@
 than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considerend in
-abundance matching at $z=3$. This mass scale is also strictly superior to
-the great majority of  $M_{\rm max}$ values allowed in the models with
-low escape fraction.   This suggests that a detailed and careful study
-of the spectral and photometric properties of LAEs coupled to the kind
-of analysis performed in this paper can be a guide in the study of the
-properties of low mass dark matter halos at $z=3.1$, extending the
-capabilities of abundance matching methods.
+abundance matching at $z=3$. This shows that our results also confirm
+the expectations of LAEs to be hosted by less massive halos than LBGs.
+A detaile analysis of the spectral and photometric properties of LAEs
+coupled to the kind of analysis performed in this paper can be a guide
+in the study of the properties of low mass dark matter halos at
+$z=3.1$, extending the capabilities of abundance matching methods.
+
+\subsection{Possible caveats to our method}
+
+... Single LAE in a halo.
+
+... Mass definition for different halo finders.
 
@@
 
-... All the software to produce the results in this paper is publicly
-available.
-
-... The raw catalogs can be obtained from the MultiDark database but
-can also be obtained in the repository of this paper on github.
+All the software, raw data and processed data to produce the results
+and plots in this paper are publicly available in a github
+repository \footnote{https://github.com/forero/CosmicVarianceLAES}. Most
+of the code to produce the plots can be found as an Ipython notebook
+\citep{IPython} in the same repository.
 

### 2013-08-11 code/correlation/C_code/model_correlation.c
model_cat_gen.py modified to create mean density catalogs and model_correlation.c modified to adjust it to ouchi

@@ -10,7 +10,7 @@ int main(int argc, char *argv[])
   
   double correlation[THETA_PARTITIONS];
   double correlation_s[THETA_PARTITIONS];
- double correlation_p[THETA_PARTITIONS];
+  double correlation_all[THETA_PARTITIONS*NRAND];
   char filename[100];
   double theta;
   double xc,yc,xr,yr;
@@ -20,7 +20,7 @@ int main(int argc, char *argv[])
 
   FILE *file;
   int ch;
-  int n_laes;
+  int n_laes,n_total;
   
   for(model=0;model<N_MODELS;model++)
     {
@@ -31,12 +31,13 @@ int main(int argc, char *argv[])
 	  file=fopen(filename,"r");
 	  
 	  n_laes=0;
+	  n_total=0
 	  while(!feof(file))
 	    {
 	      fscanf(file,"%lf %lf %lf %lf",&xc,&yc,&xr,&yr);
-	      n_laes++;
+	      n_total++;
 	    }
-	  
+	  n_laes=n_total/NRAND
 	  fclose(file);
 	  
   
@@ -44,37 +45,57 @@ int main(int argc, char *argv[])
 	  y_cat=malloc(n_laes*sizeof(double));
 	  x_rand=malloc(n_laes*sizeof(double));
 	  y_rand=malloc(n_laes*sizeof(double));
-	  
+	  printf("nlaes=%d\n",n_laes);
 	  file=fopen(filename,"r");
-	  for(i=0;i<n_laes;i++)
+	  for(i=0;i<THETA_PARTITIONS;i++)
 	    {
-	      fscanf(file,"%lf %lf %lf %lf",&xc,&yc,&xr,&yr);
-	      x_cat[i]=xc;
-	      y_cat[i]=yc;
-	      x_rand[i]=xr;
-	      y_rand[i]=yr;	       
+	      correlation[i]=0;
+	      correlation_s[i]=0;
+	    }
+	  for(l=0;l<NRAND;l++)
+	    {
+	      for(i=0;i<n_laes;i++)
+		{
+		  fscanf(file,"%lf %lf %lf %lf",&xc,&yc,&xr,&yr);
+		  x_cat[i]=xc;
+		  y_cat[i]=yc;
+		  x_rand[i]=xr;
+		  y_rand[i]=yr;	       
+		}
+	  
+	      printf("Computing RR \n");
+	      RR_histogram(histogram_rand,n_laes,x_rand,y_rand,std_rand);
[…]

### 2013-08-11 code/correlation/C_code/model_correlation.h

@@ -1,4 +1,4 @@
-//cabeceras del C
+ //cabeceras del C
 #include <stdlib.h>
 #include<stdio.h>
 #include<math.h>
@@ -48,6 +48,7 @@
 #define MASS_STEP 0.10
 #define MOCK_SURVEYS 15
 #define N_MODELS 101
+#define NRAND 16
 #define HALO_MASS_DEV 0.127725e10
 
 

### 2013-08-11 code/model_cat_gen.py

@@ -17,6 +17,7 @@ z_depth=41.0
 obs_surveys=12
 random_cat_number=1
 distance=6558.3
+randcats=16
 
 
 dmh_path=pro_path+"data/dark_matter/FOF/"
@@ -148,55 +149,37 @@ for w in range( n_models ):
             halo_index=np.where( (halo_mass< m_max) & (halo_mass> m_min) )
             halo_mass_sel=halo_mass[halo_index]
             halo_index=numbers[halo_index]
-                    
-            np.random.shuffle(halo_index)
-            
-            
-            n_halos=np.size(halo_mass_sel)
-            del halo_mass_sel
-        
             number_laes=int(f_occ*n_halos)
-            #number_laes=100 #to delete
             n_laes=np.append(n_laes, number_laes )    
+            for l in range(randcats): 
+                np.random.shuffle(halo_index)
+                n_halos=np.size(halo_mass_sel)
+                lae_index=halo_index[0:number_laes]
+                x_laes=np.append( x_laes, x_halos[lae_index] )
+                y_laes=np.append( y_laes, y_halos[lae_index] )
             
-            lae_index=halo_index[0:number_laes]
-            x_laes=np.append( x_laes, x_halos[lae_index] )
-            y_laes=np.append( y_laes, y_halos[lae_index] )
-            
-
+            del halo_mass_sel
             del x_halos
             del y_halos
             del z_halos
             del halo_mass
             
-            #random cat histogram generation
-
-        
-        
-        
-            #print "random catalog generator
-            #x_random=np.append( x_random, x_width*np.random.random_sample(number_laes*random_cat_number) )
-            #y_random=np.append( y_random, y_width*np.random.random_sample(number_laes*random_cat_number) )
-        
-        
-             
             print "subcat number ",i,"i j k=",i_s[i],j_s[i],k_s[i]
 
             #random-survey catalog generation
             Xmin=x_width*i_s[i]
             Xmax=Xmin + x_width
             Ymin=y_width*j_s[i]
-            Ymax=Ymin + y_width          
[…]

### 2013-08-11 code/model_cat_gen.py
model_cat_gen.py bugs fixed

@@ -148,12 +148,12 @@ for w in range( n_models ):
             numbers=np.arange(len(halo_mass))
             halo_index=np.where( (halo_mass< m_max) & (halo_mass> m_min) )
             halo_mass_sel=halo_mass[halo_index]
-            halo_index=numbers[halo_index]
+            n_halos=np.size(halo_mass_sel)
             number_laes=int(f_occ*n_halos)
             n_laes=np.append(n_laes, number_laes )    
+            halo_index=numbers[halo_index]
             for l in range(randcats): 
                 np.random.shuffle(halo_index)
-                n_halos=np.size(halo_mass_sel)
                 lae_index=halo_index[0:number_laes]
                 x_laes=np.append( x_laes, x_halos[lae_index] )
                 y_laes=np.append( y_laes, y_halos[lae_index] )
@@ -221,7 +221,7 @@ for w in range( n_models ):
 
 
         n_mean=np.mean(n_laes)    
-        mean_density_index=np.argmin( np.abs( n_laes-m_mean ) )
+        mean_density_index=np.argmin( np.abs( n_laes-n_mean ) )
         number_laes=n_laes[mean_density_index]
         lae_pos_ini=randcats*np.sum( n_laes[ 0 : mean_density_index ] )
         lae_pos_end=lae_pos_ini + randcats*number_laes
@@ -233,7 +233,7 @@ for w in range( n_models ):
         y_drand_mean = y_drand[lae_pos_ini:lae_pos_end]
 
 
-        lae_mean=np.empty( [ np.size(x_laes_max) , 4 ] )
+        lae_mean=np.empty( [ np.size(x_laes_mean) , 4 ] )
         lae_mean[:,0]= x_laes_mean
         lae_mean[:,1]= y_laes_mean
         lae_mean[:,2]= x_drand_mean

### 2013-08-12 paper/ms.tex
new full version

@@
 
-This problem can be tackeld with Monte Carlo simulations for the
+This problem can be tackled with Monte Carlo simulations for the
 radiative transfer, however the complexity of the relevant physical
@@
 In the next subsections we describe in detail the four key
-elements of this workflow. First, we present the observations we take
+elements of this work-flow. First, we present the observations we take
 as a benchmark. Second, we describe the main characteristics of the
@@
 conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
-which has a field of view covering $34\times 27$ arcmin, corresponding to a
+which has a field of view covering $34\times 27$ arc-min, corresponding to a
 comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
@@
 total  $2161$  LAEs with an observed equivalent width larger than $190$\AA 
-over a total survey area of $2.42$ deg$^{2}$ that includes 12 subfields, 
+over a total survey area of $2.42$ deg$^{2}$ that includes 12 sub-fields, 
 this corresponds to average surface number density of $0.20\pm 0.01$
@@
 The survey covered four independent fields. The first is the SSA22
-field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 subfields), this
+field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
 field has been known to harbor a region with a large density excess of
@@
   XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
-total of $0.58$ deg$^2$ and $386$ LAEs (3 subfields). The third and
+total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields). The third and
 fourth fields are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
-$196$ LAEs (1 subfield), and the field around the Great Observatory
+$196$ LAEs (1 sub-field), and the field around the Great Observatory
 Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
-subfield).
+sub-field).
 
@@
 mass range $M_{\rm min}< M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
-must keep in mind that the physical interpreation of the occupation
+must keep in mind that the physical interpretation of the occupation
 fraction $f_{\rm occ}$ convolves two phenomena: the presence of a star
@@
 the Davis \& Peebles  estimator \citep{Davis1983} ) only on the densest
-subfield in all the 15 mock surveys corresponding to the SSA22
+sub-field in all the 15 mock surveys corresponding to the SSA22
 region. We then take the mean ACF over the 15  mock surveys  for
@@
 We finally compare the observational ACF and the mean mock  ACF of the models   
-in therms of the angular correlation lenght ($\theta_{0}$) by fitting 
+in therms of the angular correlation length ($\theta_{0}$) by fitting 
 them to a power-law function:
@@
 square minimization procedure. The observational errors of 
-the ACF as well as the standard deviation of the mean modelled ACFs  are
+the ACF as well as the standard deviation of the mean modeled ACFs  are
 considered to compute the error in the fitted parameters to ensure ourselves
-to include poissionian and cosmic-variance errors. 
+to include poissonian and cosmic-variance errors. 
 We consider that a model is consistent with observations if the two
@@
 good agreement with observations. In this region of parameter space
-one can tfind two extreme kinds of models.  One kind where the
+one can find two extreme kinds of models.  One kind where the
 mass interval $\Delta M\equiv \log_{10} M_{\rm max} - \log_{10}M_{\rm
@@
 \caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
-  vs $f_{\rm occ}$ (rigth). The squares represent the models when both
-  th constraints on the maximal number of  consistent mocks and the
+  vs $f_{\rm occ}$ (right). The squares represent the models when both
+   constraints on the maximal number of  consistent mocks and the
   angular correlation function are included. 
@@
 
-One sceneario can be presented in terms of a decreasing escape
+One scenario can be presented in terms of a decreasing escape
 fraction of \ly radiation in massive systems. There are detailed models for
@@
 ISM than lower mass systems. Due to the resonant nature of the
-\ly line the probability of absortion  of \ly photons increases in
+\ly line the probability of absorption  of \ly photons increases in
 massive systems, producing high absorption of \ly photons but not of
@@
 The preference for narrow $\Delta M$ ranges to host LAEs 
-and the minoritary presence of reasonable models with $M_{\rm max}>
+and the small presence of reasonable models with $M_{\rm max}>
 10^{12}$\hMsun follows theoretical and observational
@@
 
-We also find that an ACF analysis on a single dataset is not enough to rule
+We also find that an ACF analysis on a single data-set is not enough to rule
 out models with a high occupation fraction $f_{\rm occ}>0.3$, which
@@
 \cite{Ouchi2010} presents an analysis of LAE observations in the
-redshift interval $3.1<z<7.0$. At $z=3.1$ They get to an average
+redshift interval $3.1<z<7.0$. At $z=3.1$ They quote an average
 mass for the host dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times
@@
 models, also summarized in Table \ref{table:firstfamily}. In
-particular it seems to favor only the very low occupations fractions.
+particular it seems to favor only the very low occupations
+fractions.
+
+We conclude this section by noting that the uncertainties on
+the preferred masses in \citep{Gawiser07} and \cite{Ouchi2010} are
+found with in the intervals $M_{\rm min}$ and $M_{\rm max}$ of our
+models. Under the light of our model, this implies that detected LAEs
+must be absent from the most massive dark matter halos at that
+redshift.
 
@@
 
-Abundance matching methods throughout cosmic time from redshifts
-$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} work based on observational
-results for Lyman Break Galaxies (LBG). In those studies the minimum halo
-mass considered to be relevant in their analysis is
-$10^{11.4}$\hMsun. For that mass, \cite{Behroozi2013a} report a
-stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$
-\hMsun, while their star formation rate is in the range $0.6\pm 0.2$
-Msun yr$^{-1}$, which nevertheless are close to the lower bound of
-values inferred for LAEs at high redshift
-\citep{Gawiser2007,Nilsson2009,Pentericci2009}.
+The abundance matching methods are based on observational results for Lyman Break Galaxies
+\citep{Behroozi2013a,Behroozi2013b}  (LBG).  In the case of
+\cite{Behroozi2013a} the minimum halo mass considered to be relevant
+in their analysis is $10^{11.4}$\hMsun. They report  stellar mass mass
+around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while their star formation
+rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$, which nevertheless
+are close to the lower bound of values inferred for LAEs at high
+redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.
 
 In our results, all the preferred models have a halo mass range lower
-than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considerend in
-abundance matching at $z=3$. This shows that our results also confirm
-the expectations of LAEs to be hosted by less massive halos than LBGs.
-A detaile analysis of the spectral and photometric properties of LAEs
+than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
+abundance matching at $z=3$. Thus confirming the expectations of LAEs
+to be found in less massive halos than those for LBGs.
+
+A detailed analysis of the spectral and photometric properties of LAEs
 coupled to the kind of analysis performed in this paper can be a guide
@@
 
-\subsection{Possible caveats to our method}
+\subsection{Caveats of our method}
 
-... Single LAE in a halo.
+There are two important caveats for the work presented here. The first is the
+assumption of a single LAE per dark matter halo. It is expected
+for sub-halos in the simulation to host satellited galaxies. However,
+it has been found in analysis based on the shape of the correlation
+function [citation needed] that satellite galaxies are not a dominant
+population, making our initial approximation a reasonable one.
 
-... Mass definition for different halo finders.
+The second caveat are the precise values for the mass intervals. These
+numbers are defined from the halos defined in using the BDM halo
+finder with a density threshold of 200 times the critical
+density. Different halo finders and definitions for the detection
+density threshold can yield different masses up to a factor of 2
+[citation needed].
 
@@
   min}<M_{\rm h}<M_{\rm   max}$ can host a LAE. We proceed with a
-thourough exploration of the space of free parameters $M_{\rm min},
+thorough exploration of the space of free parameters $M_{\rm min},
 M_{\rm max}$ and $f_{\rm occ}$ to find mocks that are consistent with
 two observational constraints: the surface number density and the
-angular correlation function. Out of the initial $9000$ initial
+angular correlation function. Out of the initial $9000$ 
 combinations of parameters in the model we find $49$ arrangements
@@
 
-The most relevant result from our study is the following. The 
-successful parameter arrangements present a wide range of possibilities for
+The successful parameter arrangements present a wide range of possibilities for
 DM hosting LAE hosts at $z=3.1$. This means that the available LAEs' spatial
@@
 ranges and occupation fractions deduced in previous analysis in
-previous analysis \citep[i.e.][]{Gawiser2007} are a subset of the
+previous analysis \citep[i.e.][]{Gawiser2007,Ouchi2010} are a subset of the
 models we find in this \documentname.
 
-Nevertheless, the sucessful models can be split into three families
+Nevertheless, the successful models can be split into three families
 depending the mass range $\Delta M=\log_{10}M_{\rm max} -
@@
 
-A second results from our investigation is the existence
-of a large number of models with a very narrow mass range $\Delta M<
-0.1$ dex that are consistent in every aspect with the spatial
-distribution of observed LAEs. In order to have these characteristics
+We find a large number of models with a narrow mass range
+$\Delta M<1.0$ dex that are consistent in every aspect with the
+spatial distribution of observed LAEs. In order to have this characteristic
 it is required that halos around the mass $M_{\rm   max}$ for each
-model become inefficient in hosting detectable LAEs. Two possible
-ways to achieve this is having LAEs with a decreasing \ly escape
-fraction with increasing mass or increasing screening effects by
-neutral Hydrogen around the most massive systems
+model become inefficient in hosting detectable LAEs. Two conditions
+can explain this. The first is having LAEs with a decreasing \ly
+escape fraction with increasing mass, the second is having larger screening
+effects by neutral Hydrogen around the most massive systems
 \citep{Laursen2009,ForeroRomero2011}.
@@
 A third aspect that stands out is the existence of a dominant family
-of models with narrow $\Delta M<0.1$, as described before, and also a
+of models with narrow $\Delta M<1.0$, as described before, and also a
 low occupation fraction $f_{\rm occ}<0.3$. This gives support to the
@@
 
-We foresee that the new observations with new instruments (such as MUSE,
-Hyper SuprimeCam and HETDEX) covering larger fields and a wider range
-of luminosities will be key in imposing tighter constraints on the
-properties of dark matter halos hosting LAEs.
+However, there are extreme cases with a very narrow $\Delta M<0.3$, meaning that
+there is barely a factor of $\sim 2$ between the minimum and halo
+mass. If these models turn out to be confirmed, this would be a great
+challenge for galaxy formation models to explain how is that LAEs can
+be hosted in such a narrow range of halo mass.
+
+In summary, we show how current observations of LAEs cannot
+put a tight constraint on the physical models. We  foresee that the
+new observations with new instruments (such as MUSE, Hyper SuprimeCam
+and HETDEX) covering larger fields and a wider range of luminosities
+will be key in imposing tighter constraints on the properties of dark
+matter halos hosting LAEs.
 
@@
 Alvaro Orsi for helpful comments on the physical interpretation and
-the presentation of our results.
+presentation of our results.
 

### 2013-08-13 paper/ms.tex
caveats

@@
 it has been found in analysis based on the shape of the correlation
-function [citation needed] that satellite galaxies are not a dominant
+function \citep{Jose2013b} that satellite galaxies are not a dominant
 population, making our initial approximation a reasonable one.
@@
 density. Different halo finders and definitions for the detection
-density threshold can yield different masses up to a factor of 2
-[citation needed].
+density threshold can yield different masses up to a factor. For
+instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
+times the average interparticle distance finds halos on average $1.4$
+times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
+values for $M_{\rm min}$ and $M_{\rm max}$ must be considered exact
+within $\sim 0.2$ dex.
 

### 2013-08-20 paper/ms.tex
starting to include Mark's comments

@@
 centered at $z=3.09$. The authors reported a
-total  $2161$  LAEs with an observed equivalent width larger than $190$\AA 
+total  $2161$  LAEs with an observed equivalent width, in the observer
+frame, larger than $190$\AA 
 over a total survey area of $2.42$ deg$^{2}$ that includes 12 sub-fields, 
@@
 \label{subsec:mocks}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\linewidth,angle=0]{./plots/Figure0.pdf}
+\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
+  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
+    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt match}
+  method. The larger panel shows $7$ mock
+  fields together mimicking the SSA22 region. The intermediate panel
+  shows $3$ mock fields corresponding to the SXDS region. The lower
+  panels represent the SDF and GOODS-North fields. The same model has
+  another 14 associated mock surveys build from different regions in
+  the simulation, but constructed following the same pattern in the
+  {\texttt match} method.}
+\end{center} 
+\end{figure*}
 
@@
 out of the $210$ available volumes. In total $15$ mock surveys are
-constructed for each model $\mathcal{M}$. The grouping of the $11$
+constructed for each model $\mathcal{M}$. The grouping of the $12$
 mock fields into a mock catalog is done in two different ways. The
@@
 imitate the SDF and GOODS-North field.  The second way to group the
-mock fields is called {\texttt   random}, whereby all the $11$ fields
+mock fields is called {\texttt   random}, whereby all the $12$ fields
 are selected in such a way as to avoid that any two volumes are
@@
 observed with the {\texttt random} selection.
+
+We note that we use $15\times 12=144$ mock fields out of the total of $210$
+available sub-volumes. The reason is that the {\texttt match}
+method imposes constraints on the way the $7$ fields mimicking the
+SSA22 can be distributed, making unusuable some of the
+sub-volumes in the box. We decide to keep the number of mock surveys
+fixed to $15$ also for the {\texttt random} method in order to allow a
+fair comparison between the two methods.
 

### 2013-08-23 paper/ms.tex
more text on the results section

@@
 min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
-values of $P>0.05$ at least for one mock survey. For those models it
+values of $P>0.05$ at least for one mock survey, which is the most
+conservative assumption for agreement between a model and observations. For those models it
 is not possible reject the hypothesis that the simulated and observed
@@
 the original $9000$ models that have at least one mock survey
-consistent with observations.
+consistent with observations. By inspection of Figure
+\ref{fig:landscape} we see that the halo number abundance is able to
+constraint the minimum mass $M_{\rm min}$ to a narrow range, while
+$M_{\rm max}$ and $f_{\rm occ}$ remain unconstrained.
 
@@
 from the arguments presented in the previous subsection. For these
-models the number density of LAEs is too low compared to observations.
+models the number density of LAEs is too low compared to
+observations.
 
@@
 
-For each model ${\mathcal M}$ there are 15 different mock surveys. In the
-previous section we presented the models that had at least one
-mock survey with $P>0.05$. Figure \ref{fig:high_success_rate} shows the number of models
-that have at least $N_{\rm high-P}$ mocks with $P>0.05$ for both the
-{\texttt  match} and {\texttt random} methods.  This shows that there
-are $\sim 100$ models with all the 15 mock survey realizations with
-$P>0.05$.
-
-We discard the models that have 14 mocks or less consistent with observations.
-This cut represents a reduction by a factor of $\sim 6$ with respect
-to the total number of models with at least one (1) consistent mock.
+In the previous Section we present a conservative criterion of
+agreement by selecting the models that had at least one mock survey
+with $P>0.05$ in the KS test. Now we turn to a more strict selection
+by requiring all constructed mock surveys to be consistent with
+observations.
+
+Figure \ref{fig:high_success_rate} shows the number of models
+that have at least $N_{\rm high-P}$ mocks with $P>0.05$. For each
+model ${\mathcal M}$ there are 15 different mock surveys.  We discard
+the models that have 14 mocks or less consistent with
+observations. With this cut we find $\sim 100$ models with all the 15
+mock survey realizations with $P>0.05$.  This cut represents a
+reduction by a factor of $\sim 6$ with respect to the total number of
+models with at least one consistent mock.
 
@@
 $f_{\rm occ}$.
+
+We conclude that conditions on the number density statistics, even if they are
+very strict, only put strong constraints on the minimum mass $M_{\rm
+  min}$ but not on the other two parameter of the model $M_{\rm max}$
+and $f_{\rm occ}$. In the next section we use additional observational
+information to constrain these paremeters.
 
@@
 occupation fractions of $f_{\rm occ}> 0.5$.
+
+We conclude that the clustering information is able to put meaningful
+constraints on the values of the maxium mass parameters $M_{\rm max}$
+and the occupation fraction $f_{\rm occ}$.
 

### 2013-08-23 code/correlation_statistic.py
new version of correlation_statistic.py . Now each mock field ACF is fitted instead of the mean ACF

@@ -1,23 +1,35 @@
 import numpy as np
 import pylab as P
 import matplotlib.collections as collections
+import matplotlib 
 from scipy import stats
 from scipy import optimize as op
+import sys
+#plot_dir="../paper/plots/"
 plot_dir="../paper/plots/"
 
+matplotlib.use('pdf')
 #defining the power-law function to fit the correlation function
 powerlaw = lambda x, amp, index: (x/amp)**(index)
-fitfunc = lambda p, x: (x/p[0])**p[1]
+fitfunc = lambda p, x: (x/p[0])**(p[1])
 errfunc = lambda p, x, y,err: (y - fitfunc(p, x))/err
 
-pinit = [1.0, -1.0] 
+pinit = [2.0,-1.0] 
 
 n_models=101
-n_mocks=12
+n_mocks=15
 theta_bins=13
-pro_path="/home/jemejia/CosmicVarianceLAES/"
+pro_path="/Users/jemejia/CosmisVarianceLAES/"
 
 obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
+obs=np.loadtxt(obs_correlation_file,skiprows=4)
+theta1=obs[0:theta_bins,0]
+if(sys.argv[1]=="maxden"):
+    obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
+if(sys.argv[1]=="meanden"):
+    obs_correlation_file=pro_path + "data/obs/ouchi2010.txt"
+
+
 obs_correlation=np.loadtxt(obs_correlation_file,skiprows=4)
 theta=obs_correlation[0:theta_bins,0]
 correlation=obs_correlation[0:theta_bins,1]
@@ -33,7 +45,7 @@ print "covariance matriz \n\n", covar, "\n\n"
 
 ro_obs=pfinal[0]
 ro_err_obs=np.sqrt(covar[0][0])
-slope_obs=pfinal[1]
+slope_obs=-pfinal[1]
 slope_err_obs=np.sqrt(covar[1][1])
 ro_min=ro_obs - ro_err_obs
 ro_max=ro_obs + ro_err_obs
@@ -53,6 +65,14 @@ model_numbers=np.arange(len(f_occ_m))
 mean_correlation= np.zeros( [n_models,theta_bins] )
 std_correlation = np.zeros( [n_models,theta_bins] )
 chi_individual  = np.zeros( [n_models,n_mocks] )
+
[…]

### 2013-08-25 paper/ms.tex
model correlation files and correlation_statistic.py

@@
 observations . The ACF is computed  ( using 
-the Davis \& Peebles  estimator \citep{Davis1983} ) only on the densest
-sub-field in all the 15 mock surveys corresponding to the SSA22
-region. We then take the mean ACF over the 15  mock surveys  for
-each model as well as its the standard deviation to include
-the effect of cosmic variance.
-
-We finally compare the observational ACF and the mean mock  ACF of the models   
+the Landy \&  Szalay  estimator \citep{Landy1993} )  on $1$ the densest
+and $2)$ a mean sub-field of each of the 15 mock surveys. This is done to 
+compare the predicted ACFs with the \cite{Hayashino2004}  and \cite{Ouchi2010}
+ACFs respectively.
+
+The observational ACF and the  mock  ACF of the models are compared   
 in therms of the angular correlation length ($\theta_{0}$) by fitting 
@@
 Both mock and observational ACF are derived by a least
-square minimization procedure. The observational errors of 
-the ACF as well as the standard deviation of the mean modeled ACFs  are
-considered to compute the error in the fitted parameters to ensure ourselves
-to include poissonian and cosmic-variance errors. 
+square minimization procedure to the previous equation. The  errors of 
+the ACF  are considered to compute the error in the fitted parameters to ensure ourselves
+to include poissonian. At the same time, for each model ${\mathcal M}$ we 
+compute the mean and standard deviation on the fitted parameters over
+each mock survey to account for cosmic-variance errors. 
 We consider that a model is consistent with observations if the two

### 2013-08-25 code/correlation_statistic.py

@@ -94,7 +94,7 @@ for i in range(n_models):
         #pinit=pfinal
         covar = out[1]
         
-        if( covar is None ):
+        if( covar is None ): 
             ro_ind[i,j]=ro_ind[i,j-1]
             slope_ind[i,j]=slope_ind[i,j-1]
             ro_err_ind[i,j]=ro_err_ind[i,j-1]
@@ -244,96 +244,8 @@ plot_name=plot_dir +"mmin_vs_focc_"  + sys.argv[1] + ".pdf"
 f_occ_plot.legend(shadow=False,loc=2)
 fig5.savefig(plot_name,format="pdf")
 
-#---------prediction on the ACF for the best models-------------------------------------------
 
 
-focc_index=np.where(((f_occ<=0.2) & (m_max<12.0) ) == True)
-model_numbers=model_numbers[focc_index]
-n_models=np.size(model_numbers)
-n_mocks=12
-
-mean_correlation= np.zeros( [n_models,theta_bins] )
-std_correlation = np.zeros( [n_models,theta_bins] )
-chi_individual  = np.zeros( [n_models,n_mocks] )
-slope = np.zeros( n_models )
-slope_err = np.zeros( n_models )
-ro = np.zeros( n_models )
-ro_err = np.zeros( n_models )
-n=0
-for i in model_numbers:
-    corr=np.zeros( (n_mocks,theta_bins) )
-    
-    for j in range(n_mocks):
-        model_correlation_filename=pro_path +  "data/laes/correlation/model_" + str(i) + "_mock_" + str(j) + ".txt"
-        
-        lae_correlation  = np.loadtxt(model_correlation_filename)
-        corr[j,:] = lae_correlation[:,1]
-
-        
-    std_correlation[n,:]  = np.std(corr,axis=0)
-    mean_correlation[n,:] = np.mean(corr,axis=0)
-    n=n+1
-
-chisquare=np.zeros([n_models,theta_bins])
-chi=np.zeros(n_models)
-
-for i in range(n_models):
-    correlation= mean_correlation[i,:]
-    std= std_correlation[i,:]
-    
-    salida = op.leastsq(errfunc, pinit,args=(lae_correlation[:,0], correlation,std), full_output=1)
-    
-    pfinal = salida[0]
-    covar = salida[1]
-
[…]

### 2013-08-27 code/correlation_statistic.py
cosmetic changes in correlation_statistic.py and plots. Best models files added as : data/mock_survey/powerlaw_bestmodels_maxden.dat and  data/mock_survey/powerlaw_bestmodels_meanden.dat

@@ -156,17 +156,19 @@ fig2=P.figure()
 ro_plot=fig2.add_subplot(111)
 ro_index=np.where(slope_err<2.0)
 ro_plot.errorbar(ro[ro_index],slope[ro_index], yerr=slope_err[ro_index], xerr=ro_err[ro_index], label="Models",elinewidth=1.5,fmt="o")
-ro_plot.errorbar(ro_obs,slope_obs, yerr=slope_err_obs, xerr=ro_err_obs, label="Hayashino et al 2004",elinewidth=4.5)
+
+if sys.argv[1]=="maxden" :
+    ro_plot.errorbar(ro_obs,slope_obs, yerr=slope_err_obs, xerr=ro_err_obs, label="Hayashino et al 2004",elinewidth=4.5)
+if sys.argv[1]=="meanden":
+    ro_plot.errorbar(ro_obs,slope_obs, yerr=slope_err_obs, xerr=ro_err_obs, label="Ouchi et al 2010",elinewidth=4.5)
+
 ro_plot.set_xlabel(r'$\theta_{0}$', fontsize=20)
 ro_plot.set_ylabel(r"$\gamma$",fontsize=20)
-ro_plot.set_title("Angular Correlation parameters. Full SSA22 field",fontsize=20)
 ro_plot.set_title("Angular Correlation parameters. Match survey",fontsize=20)
-plot_name=plot_dir +"power_law_correlation_" + sys.argv[1] + ".pdf"
+plot_name=plot_dir + "power_law_correlation_" + sys.argv[1] + ".pdf"
 ro_plot.legend(shadow=False,loc=2)
 
-
 fig2.savefig(plot_name,format="pdf")
-
 
 fig3=P.figure()
 mmin_plot=fig3.add_subplot(111)
@@ -176,8 +178,12 @@ mmax_index=np.where(m_max_m>12.0) #and ro<ro_max) #and slope_min<slope<slope_max
 mmin_plot.errorbar(m_min_m[mmax_index]+0.01,ro[mmax_index], yerr=ro_err[mmax_index],label=r"$\log M_{max}>12.0$",elinewidth=1.5,fmt="o")
 mmin_plot.set_ylabel(r'$\theta_{0}$', fontsize=20)
 mmin_plot.set_xlabel(r"$M_{min}$",fontsize=20)
-mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Full SSA22 Field",fontsize=20)
[…]

### 2013-08-28 paper/ms.tex
there is evidence for two families, not three

--- 2013-08-23 paper/ms.tex
@@
 observations . The ACF is computed  ( using 
-the Davis \& Peebles  estimator \citep{Davis1983} ) only on the densest
-sub-field in all the 15 mock surveys corresponding to the SSA22
-region. We then take the mean ACF over the 15  mock surveys  for
-each model as well as its the standard deviation to include
-the effect of cosmic variance.
-
-We finally compare the observational ACF and the mean mock  ACF of the models   
-in therms of the angular correlation length ($\theta_{0}$) by fitting 
+the Landy \&  Szalay  estimator \citep{Landy1993} )  on two kinds of
+fields in the mock survey: the densest and one corresponding to the
+average density. The first with the \cite{Hayashino2004}  and \cite{Ouchi2010}
+ACFs respectively.
+
+The observational ACF and the  mock  ACF of the models are compared   
+in terms of the correlation length ($\theta_{0}$) by fitting 
 them to a power-law function:
@@
 
-Both mock and observational ACF are derived by a least
-square minimization procedure. The observational errors of 
-the ACF as well as the standard deviation of the mean modeled ACFs  are
-considered to compute the error in the fitted parameters to ensure ourselves
-to include poissonian and cosmic-variance errors. 
-We consider that a model is consistent with observations if the two
-parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$ range.
+Both mock and observational ACF are derived by a least square
+minimization procedure. For each mock we obtain a covariance matrix
+that gives us the uncertainty in the parameters $\beta$ and
+$\theta_0$. We compute a mean value for the parameters and its
+associated uncertainty as the cuadratic average of the uncertainties in
+the fitting procedure. We consider that a model is consistent with
+observations if the two parameters $\beta$ and $\theta_0$ are equal
+within a $1$-$\sigma$ range.
 
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_maxden.pdf} 
 \hspace{5mm}  
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation.pdf} 
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
 %\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_mass.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_f_occ.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_f_occ.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_mass.pdf}
+\hspace{5mm}
+\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_f_occ.pdf}
 \end{center}
@@
    constraints on the maximal number of consistent mocks and the
-  angular correlation function are included. 
+  angular correlation function are included. Upper panels correspond
+  checks the consistency against the observational data of
+  \citet{Ouchi2010}, while lower panels show results for \citet{Hayashino2004}
   \label{fig:restriction_mock_and_f_occ_corr}} 
@@
 $\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
-10.1& 10.2& 0.1\\
-10.3& 10.5& 0.1\\
-10.4& 10.7& 0.1\\
-10.5& 10.6& 0.3\\
-10.5& 10.9& 0.1\\
-10.5& 11.0& 0.1\\
-10.6& 10.8& 0.2\\
-10.6& 11.2& 0.1\\
-10.6& 11.3& 0.1\\
-10.6& 11.4& 0.1\\
-10.6& 11.5& 0.1\\
-10.6& 11.6& 0.1\\
-10.7& 11.0& 0.2\\
-10.8& 11.2& 0.2\\
-10.8& 11.3& 0.2\\
-10.8& 11.4& 0.2\\
-10.9& 11.3& 0.3\\
-10.9& 11.7& 0.2\\
-10.9& 11.8& 0.2\\
-10.9& 11.9& 0.2\\
-11.0& 11.6& 0.3\\
-11.0& 11.7& 0.3\\
-11.0& 11.8& 0.3\\
-11.0& 12.0& 0.3\\\hline\hline
+10.1 &10.2 & 0.1\\
+10.3 &10.5 & 0.1\\
+10.4 &10.7 & 0.1\\
+10.5 &10.6 & 0.3\\
+10.5 &10.9 & 0.1\\
+10.5 &11.0 & 0.1\\
+10.6 &11.2 & 0.1\\
+10.6 &11.4 & 0.1\\
+10.6 &11.7 & 0.1\\
+10.7 &11.0 & 0.2\\
+10.8 &11.2 & 0.2\\
+10.8 &11.3 & 0.2\\\hline
 \end{tabular}
@@
 $\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
-10.6& 10.7& 0.4\\
-10.7& 10.8& 0.5\\
-10.8& 10.9& 0.6\\
-10.8& 11.0& 0.4\\
-10.9& 11.0& 0.8\\
-10.9& 11.0& 0.9\\
-10.9& 11.1& 0.5\\
-11.0& 11.1& 1.0\\
-11.0& 11.4& 0.4\\
-11.1& 11.3& 0.7\\
-11.1& 11.7& 0.4\\
-11.2& 11.5& 0.7\\
-11.2& 11.6& 0.6\\
-11.2& 11.9& 0.5\\\hline\hline
+10.6 &10.7 &0.4\\
+10.8 &10.9 &0.6\\
+10.8 &11.0 &0.4\\
+10.9 &11.0 &0.8\\
+10.9 &11.0 &0.9\\
+10.9 &11.1 &0.5\\
+11.0 &11.1 &1.0\\
+11.1 &11.3 &0.8\\
+11.2 &11.6 &0.6\\
+11.2 &12.2 &0.5\\
+11.3 &11.7 &0.9\\\hline
 \end{tabular}
 \end{center}
-\caption{\label{table:secondfamily}List of parameters for the second family of models. Narrow
-  mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccc}\hline\hline
-$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
-10.6& 11.7& 0.1\\
-10.9& 12.1& 0.2\\
-10.9& 12.2& 0.2\\
-10.9& 12.3& 0.2\\
-10.9& 12.4& 0.2\\
-10.9& 12.5& 0.2\\
-10.9& 12.6& 0.2\\
-10.9& 12.7& 0.2\\
-10.9& 12.8& 0.2\\
-10.9& 12.9& 0.2\\
-10.9& 13.&0 0.2\\\hline\hline
-\end{tabular}
-\end{center}
-\caption{\label{table:thirdfamily}List of parameters for the third family of models. Broad
-  mass range $\Delta M >1.0$dex and low occupation fraction $f_{\rm occ}\leq0.3$.}
+\caption{\label{table:secondfamily}List of parameters for the second
+  family of models. Narrow mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
 \end{table}

### 2013-08-28 paper/ms.tex
abstract+results sections are updated

@@
 halos in the simulation we use a model where a dark matter halo with
-mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host one LAE with a
-probability $f_{\rm occ}$. We find that the large scatter in the mocks, induced by
-cosmic variance, makes the number density and spatial clustering
-information insufficient to derive a unique and narrow set of values
-for the parameters in the model. In particular, it is always possible
-to find a model that is consistent with observations and has any
-desired occupation fraction in the range $0.1\leq f_{\rm occ}\leq 1.0$
-.  Nevertheless, in the models we can define three different families
-of parameters based on their mass range, $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, and occupation fraction,
-$f_{\rm occ}$. The dominant family is composed by models with a narrow
-mass range $\Delta M<1.0$ dex, a low occupation fraction $f_{\rm
-  occ}\leq 0.3$ and a maximum mass $M_{\rm  max}< 10^{12}$\hMsun.  The
-existence of this dominant family gives support to the idea that the
-most massive dark matter halos at that epoch do not host the brightest
-LAEs and that only a small fraction of star forming galaxies can be
-actually detected as LAEs.
+mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
+one LAE with a probability $f_{\rm occ}$.  We find that the observational information on the number density restricts the minimum mass to a
+range $10^{10}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ leaving all the
+other parameters unrestricted, while the clustering information puts a
+tight constraint of $M_{\rm   max}<10^{12}\hMsun$. This gives support
+to the idea that the most massive dark matter halos at that epoch do
+not host the brightest LAEs.  However, none of these observations is
+able to constrain the occupation fraction. It is always possible to
+find a model that is consistent with observations and has any desired
+occupation fraction in the range $0.1\leq f_{\rm occ}\leq
+1.0$. Furthermore, all models have a mass range $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex. 
+We divide the best models into families of low and high occupation
+fraction with a transition around $f_{\rm occ}\leq 0.3$. These two
+families are almost disjoint in their values of $M_{\rm min}$. Low
+occupation fraction occurs below a threshold of $M_{\rm th}=
+10^{10.8}\Msun$, while high occupation fractions are present in
+$M_{\rm min}>M_{\rm the}$. These two families of models are
+similar in size, giving an unconclusive response as to which is the
+occupation fraction of LAEs at $z=3.1$. A conclusive answer requires
+a detailed physical model for the  connection between dark matter,
+star formation and the escape of \ly radiation. That kind of modelling
+should also provide a plausible explanation for the narrow range in
+mass $\Delta M<1.0$ dex derived here for the halos hosting LAEs at
+$z=3.1$.
+
 \end{abstract}
@@
 semi-analytic models  and  full N-body hidrodynamical simulations
-\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012, Soler2012}.
+\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012,
+  Soler2012}.
 
@@
 the simulation and model used to produce the mock catalogs and the criteria
-we use to compare them against observations. In \SS \ref{sec:results} we
+we use to compare them against observations. In \S \ref{sec:results} we
 present the main results for the halo mass and occupation fraction. We
@@
 observational and theoretical results. Finally, we present our
-conclusions in \SS
-\ref{sec:conclusions}.
+conclusions in \S \ref{sec:conclusions}.
 
@@
 \includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/mmin_vs_correlation.pdf}  
 \end{center}
@@
 to the standard deviation from the different mocks surveys. 
-%Right:
-%Same results in the $\theta_{0}$-$M_{\rm min}$ plane, with the
-%observational constraint on $\theta_{0}$ epresented by the red
-%rectangle. Blue  squares represent models with $\log_{10} M_{\rm
-%  max}<12.0$, green circles correspond to models with $\log_{10}
-%M_{\rm max}>12.0$. 
 \label{fig:correlation_parameters}}
@@
 $15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
-reproduce observations. {\bf Cual es el resultsdo de Ouchi
-  para $\theta_0$?}
+reproduce observations. The right panel of Figure
+\ref{figure:correlation_parameters} shows the results for fields in
+the mock catalog that have an average number density that are compared
+against the fit of the data reported by \cite{Ouchi2010}. In this case
+we find that there are large uncertainties in the observational data,
+however it is possible to discard a fraction of the models.
 
@@
 models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
-for the {\tt match} method. To make this selection we consider that
+both for the comparisong against \cite{Hayashino2004} and
+\cite{Ouchi2010}. To make this selection we consider that
 a model is consistent with observations if there is a $1-\sigma$
 overlap between both the correlation length $\theta_0$ and the power
-$\beta$ . Comparing this Figure with the results shown in Figure
-\ref{fig:restriction_mock} we see that the models that were removed
-were those with highest minimal masses $M_{\rm min}>10^{11.2}$, for
-all the values of $M_{\rm max}$, with preferentially high
-occupation fractions of $f_{\rm occ}> 0.5$.
-
-We conclude that the clustering information is able to put meaningful
-constraints on the values of the maxium mass parameters $M_{\rm max}$
-and the occupation fraction $f_{\rm occ}$.
+$\beta$. We clearly see from this Figure that the conditions imposed
+by \cite{Hayashino2004} are the tightest. Comparing this Figure with
+the results shown in Figure \ref{fig:restriction_mock} we see that
+practically all models with $M_{\rm max}>10^{12}$ are removed. On the
+other hand the comparison against \cite{Ouchi2010} does not succeed in
+greatly reducing the number of models.
+
+At this point we keep the models that are consistent with both
+observational constraints. This basically reduces the selection to the
+models already restricted by the data in \cite{Hayashino2004} as
+presented in the lower panels of Figure
+\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
+this comparison is that clustering information is able to put
+meaningful constraints on the values of $M_{\rm max}$. However, the
+possible values for the occupation fraction are still in the initial
+range $0.1\leq f_{\rm occ}\leq 1$.
 

### 2013-08-29 code/correlation_statistic.py
power law * plots modified

@@ -161,15 +161,18 @@ if sys.argv[1]=="maxden" :
     ro_plot.errorbar(ro_obs,slope_obs, yerr=slope_err_obs, xerr=ro_err_obs, label="Hayashino et al 2004",elinewidth=4.5)
 if sys.argv[1]=="meanden":
     ro_plot.errorbar(ro_obs,slope_obs, yerr=slope_err_obs, xerr=ro_err_obs, label="Ouchi et al 2010",elinewidth=4.5)
-
-ro_plot.set_xlabel(r'$\theta_{0}$', fontsize=20)
-ro_plot.set_ylabel(r"$\gamma$",fontsize=20)
-ro_plot.set_title("Angular Correlation parameters. Match survey",fontsize=20)
+P.xlim(0,50)
+P.ylim(0.5,3.5)
+ro_plot.set_xlabel(r'$\theta_{0}(arcsec)$', fontsize=20)
+ro_plot.set_ylabel(r"$\beta$",fontsize=20)
+##ro_plot.set_title("Angular Correlation parameters. Match survey",fontsize=20)
 plot_name=plot_dir + "power_law_correlation_" + sys.argv[1] + ".pdf"
 ro_plot.legend(shadow=False,loc=2)
 
 fig2.savefig(plot_name,format="pdf")
 
+P.xlim()
+P.ylim()
 fig3=P.figure()
 mmin_plot=fig3.add_subplot(111)
 mmax_index=np.where(m_max_m<12.0) #and ro<ro_max) #and slope_min<slope<slope_max)

### 2013-08-29 paper/ms.tex
udpated discussion

@@
 occupation fraction in the range $0.1\leq f_{\rm occ}\leq
-1.0$. Furthermore, all models have a mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex. 
-We divide the best models into families of low and high occupation
+1.0$. We also find that all models have a narrow mass range $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex,
+with the vast majority in the range $\Delta M<0.5$ dex, meaning that
+there is only a factor of $3$ in mass between the minimum and maximum
+halo mass. We divide the best models into families of low and high occupation
 fraction with a transition around $f_{\rm occ}\leq 0.3$. These two
@@
 10^{10.8}\Msun$, while high occupation fractions are present in
-$M_{\rm min}>M_{\rm the}$. These two families of models are
-similar in size, giving an unconclusive response as to which is the
-occupation fraction of LAEs at $z=3.1$. A conclusive answer requires
-a detailed physical model for the  connection between dark matter,
-star formation and the escape of \ly radiation. That kind of modelling
-should also provide a plausible explanation for the narrow range in
-mass $\Delta M<1.0$ dex derived here for the halos hosting LAEs at
-$z=3.1$.
+models with $M_{\rm min}>M_{\rm th}$. This represents an unconclusive response as
+to which is the occupation fraction for LAEs at $z=3.1$. A definite
+answer requires a detailed physical model for the  connection between
+dark matter, star formation and the escape of \ly radiation. That kind
+of modelling should also provide a plausible explanation for the
+narrow range in mass $\Delta M<1.0$ dex derived here for the halos
+hosting LAEs at $z=3.1$.
 
@@
 method imposes constraints on the way the $7$ fields mimicking the
-SSA22 can be distributed, making unusuable some of the
+SSA22 can be distributed. This restriction makes unusuable some of the
 sub-volumes in the box. We decide to keep the number of mock surveys
@@
 practically all models with $M_{\rm max}>10^{12}$ are removed. On the
-other hand the comparison against \cite{Ouchi2010} does not succeed in
-greatly reducing the number of models.
-
-At this point we keep the models that are consistent with both
-observational constraints. This basically reduces the selection to the
-models already restricted by the data in \cite{Hayashino2004} as
-presented in the lower panels of Figure
+other hand the comparison against \cite{Ouchi2010} does not
+substantially reduce the number of models.
+
+At this point we take the most strict selection criterio and keep the
+models that are consistent with both observational constraints. This
+basically reduces the selection to the models already restricted by
+the data in \cite{Hayashino2004} as presented in the lower panels of Figure
 \ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
@@
 range $0.1\leq f_{\rm occ}\leq 1$.
-
-%In order to better illustrate the results from this test we
-%show in the right panel of Figure \ref{figure:correlation_parameters} 
-%the plane $\theta_{0}$-$M_{\rm min}$ for all models divided in two
-%disjoint sets. The first are the models $\log_{10} M_{\rm
-%    max}<12$ (blue dots), the second corresponds to $\log_{10} M_{\rm
-%    max}>12$ (green dots). The colored rectangle includes
-%the parameter region which is consistent with the observational
-%constraint in $\theta_{0}$.  With this restriction we find that most
-
-%models with $\log_{10} M_{\rm max}>12$ and  $\log_{10} M_{\rm min}>11.s$ 
-%can be safely ruled out.
 
@@
 and the information from the angular correlation function, reducing
-the number of feasible models. We end up with $\sim 50$ models out of
+the number of feasible models. We end up with $\sim 25$ models out of
 the initial $9000$ possible combination of parameters.
@@
 \log_{10}M_{\rm  min}$, together with the occupation fraction $f_{\rm
-  occ}$ to classify all the successful models into three families:
+  occ}$ to classify all the successful models into two families:
 
 \begin{itemize}
-\item[(1)] Low $f_{\rm occ}\leq 0.3$ and low $\Delta M\leq 1.0$
-  dex: 24 models.
-\item[(2)] Low $f_{\rm occ}\leq 0.3$ and high $\Delta M > 1.0$dex: 11
-  models
-\item[(3)] High $f_{\rm occ}> 0.3$ and low $\Delta M\leq 1.0$: 14 models
+\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
+  dex: 12 models. 
+\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
+  low $\Delta M\leq 1.0$: 11 models 
 \end{itemize}
 
-There is a clear majority of models with a narrow $\Delta M\leq
-1$, compared to the $2.5$dex of halo mass available for occupation at
-that redshift. Such models imply that there is a cut at lower and higher halo
-masses that render inefficient the presence and/or detection of LAEs.
-
-At the low mass end, such cut can be readily interpreted in terms of the
-minimal halo star formation rate needed to produce the minimal \ly 
-luminosity to be above a given detection threshold.  However, under
-the reasonable assumption of star formation rate increasing with halo
-mass, the cut at higher halo masses requires a different
-justification. There are two complementary physical scenarios that can
-provide an explanation.
-
-One scenario can be presented in terms of a decreasing escape
-fraction of \ly radiation in massive systems. There are detailed models for
+The full list of paramenter in the two families is summarized in Table
+\ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
+have a clear majority of any family. This leads us to the following
+two conclusions. First, the occupation fraction cannot be constrained
+based on clustering anaylsis. Second, the halos hosting LAEs have a
+narrow mass range.
+
+The existence of a narrow mass rango for halo masses has different
+possible explanations. A cut at the low mass end $M_{\rm min}$ can be
+interpreted in terms of the minimal halo star formation rate needed to
+produce the minimal \ly  luminosity to be above a given detection
+threshold.  However, under the reasonable assumption of star formation
+rate increasing with halo mass, the cut at higher halo masses requires
+a different justification. There are two complementary physical
+scenarios that can provide it.
+
+One scenario can be presented in terms of a decreasing escape fraction
+of \ly radiation in massive systems. There are detailed models for
 radiative transfer that support the idea that massive galaxies with
 higher metallicities have larger dust contents and less concentrated
-ISM than lower mass systems. Due to the resonant nature of the
-\ly line the probability of absorption  of \ly photons increases in
+ISM than lower mass systems. Due to the resonant nature of the \ly
+line the probability of absorption  of \ly photons increases in
 massive systems, producing high absorption of \ly photons but not of
-continuum or other non-resonant lines
-\citep{Laursen2009,ForeroRomero2011}.
+continuum or other non-resonant lines \citep{Laursen2009,ForeroRomero2011}.
 
 A second scenario is that larger systems have more extended gaseous
-envelopes which. Again, due to resonance effects of the \ly line,
-these systems can present a low surface brightness and a broader line,
-making these systems less observable in narrow band filter surveys
+envelopes which due to resonance effects of the \ly line, can induce a
+low surface brightness and a broader line, making these systems less
+observable in narrow band filter surveys
 \citep{Laursen2009,Zheng2010}.
@@
 and the small presence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun follows theoretical and observational
-insights where the most massive systems are not bright \ly sources
-\citep{ForeroRomero2012,Shapley2003}.
+10^{12}$\hMsun also follows theoretical and observational
+insights for high-z galaxies where the most massive systems are not
+bright \ly sources \citep{ForeroRomero2012,Shapley2003}.
 
@@
 
-We also find that $70\%$ of the best models are found in families (1)
-and (2), with a low occupation fraction $f_{\rm occ}\leq 0.3$. This
-preference goes in the same direction as the observational constraint
-on the escape fraction $f_{\rm esc}\sim 0.1-0.2$ derived at $z=2.2$ by
-\cite{Hayes2010} and recent theoretical study of observational data in
-a wide redshift range $0<z<6$  \citep{Dijkstra2013}.
-
-The observational estimation by \cite{Hayes2010} was based on blind
-surveys of the H$\alpha$ and Lyman $\alpha$ line. Using corrections by
-extinction to obtain an estimate for the intrinsic H$\alpha$
-luminosity, and using values for the theoretical expectation of the
-ratio Lyman$\alpha$/H$\alpha$ they derive an bulk escape fraction for
-the Lyman$\alpha$ radiation of $f_{\rm esc}=(5.3\pm 3.8)\%$ or $f_{\rm
-  esc}=(10.7\pm 2.8)\%$ if a different dust correction is used.
-
-They also showed that that the luminosity function for LAEs at $z=2.2$ is
-consistent with the escape fraction being constant for every galaxy
-regardless of its luminosity. From this results they derive that
-almost $90\%$ of the star forming galaxies emit insufficient
+Theoretical intepretations of blind galaxy surveys at $z=2.2$ find a
+volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
+\cite{Hayes2010}, similar results are obtained in a recent theoretical
+study of observational data in a wide redshift range $0<z<6$
+\citep{Dijkstra2013}.
+
+\cite{Hayes2010} showed that the luminosity function for
+LAEs at $z=2.2$ is consistent with the escape fraction being constant
+for every galaxy regardless of its luminosity. From this results they
+derive that almost $90\%$ of the star forming galaxies emit insufficient
 Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$.
-
-\cite{Dijkstra2013} used a similar principle to derive their results. They
-compared observationally derived star formation functions to LAE
-luminosity functions. At $z\sim 3.0$ they derive an effective escape
-fraction of $f_{\rm esc}=(17\pm 5)\%$ could be interpreted as an
-occupation fraction $f_{\rm occ}\sim 0.2$.  We consider a success of
-our method the fact that we find that most of the consistent models
-show a low occupation fraction.
+fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} uses similar
+methods to find an average \ly escape fraction in high-z galaxies,
+they conclude that there is a range in luminosity where the escape
+fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
+be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$.
+
+We consider a success that our model indeed includes such low
+occupation fraction models. The observational evidence from galaxy
+surveys seem to disfavor the second family of models with high
+occupation fractions. Nevertheless, it remains a task for galaxy
+formation models to explain the mass range $\Delta M<0.5$ in the models.
 
@@
 out models with a high occupation fraction $f_{\rm occ}>0.3$, which
-represent almost one fourth of our best models, coinciding with a wide
-range in halo masses $\Delta M>1.0$ dex. These models cannot be
-considered unfavorable based on a clustering analysis only.
+represent half of our best models. These models cannot be
+considered unfavorable based on a clustering analysis only, it
+requires additional information from galaxy surveys, as we have
+presented in the previous section.
 
@@
 found with in the intervals $M_{\rm min}$ and $M_{\rm max}$ of our
-models. Under the light of our model, this implies that detected LAEs
-must be absent from the most massive dark matter halos at that
-redshift.
+models.
 
@@
 
-The abundance matching methods are based on observational results for Lyman Break Galaxies
-\citep{Behroozi2013a,Behroozi2013b}  (LBG).  In the case of
-\cite{Behroozi2013a} the minimum halo mass considered to be relevant
-in their analysis is $10^{11.4}$\hMsun. They report  stellar mass mass
-around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while their star formation
-rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$, which nevertheless
-are close to the lower bound of values inferred for LAEs at high
-redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.
+The abundance matching methods are based on observational results for
+Lyman Break Galaxies \citep{Behroozi2013a,Behroozi2013b}  (LBG).  In
+the case of \cite{Behroozi2013a} the minimum halo mass considered to
+be relevant in their analysis is $10^{11.4}$\hMsun. They report
+stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
+their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$,
+which nevertheless are close to the lower bound of values inferred for
+LAEs at high redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.
 
@@
 than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
-abundance matching at $z=3$. Thus confirming the expectations of LAEs
-to be found in less massive halos than those for LBGs.
-
-A detailed analysis of the spectral and photometric properties of LAEs
+abundance matching at $z=3$. This confirms once more the expectations
+that most of  LAEs are to be found in less massive halos LBG hosts.A
+detailed analysis of the spectral and photometric properties of LAEs
 coupled to the kind of analysis performed in this paper can be a guide
@@
 There are two important caveats for the work presented here. The first is the
-assumption of a single LAE per dark matter halo. It is expected
-for sub-halos in the simulation to host satellited galaxies. However,
-it has been found in analysis based on the shape of the correlation
-function \citep{Jose2013b} that satellite galaxies are not a dominant
-population, making our initial approximation a reasonable one.
+assumption of a single LAE per dark matter halo. This contradicts the
+general expectation of dark matter sub-halos in the simulation to host
+satellite galaxies. However, it has been found in analysis based on
+the shape of the correlation function \citep{Jose2013b} that satellite
+galaxies are not a dominant population, making our initial
+approximation a reasonable one. Therefore we think that it is not
+crucial to include the effect of satellites in the model.
 
@@
 times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
-values for $M_{\rm min}$ and $M_{\rm max}$ must be considered exact
-within $\sim 0.2$ dex.
+values for $M_{\rm min}$ and $M_{\rm max}$ should not be considered exact
+within less than $\sim 0.2$ dex.
 
@@
 
-All the software, raw data and processed data to produce the results
+All the software, raw and processed data to produce the results
 and plots in this paper are publicly available in a github
@@
 Institute for Advanced Study where the first full draft of this paper
-was completed. The authors also thank Peter Laursen, Paulina Lira and
-Alvaro Orsi for helpful comments on the physical interpretation and
-presentation of our results.
+was completed. The authors also thank Peter Laursen, Paulina Lira, 
+Alvaro Orsi and Mark Dijkstra for helpful comments on the physical
+interpretation and presentation of our results.
 
@@
 \begin{center}
-\begin{tabular}{ccc}\hline\hline
-$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
-10.1 &10.2 & 0.1\\
-10.3 &10.5 & 0.1\\
-10.4 &10.7 & 0.1\\
-10.5 &10.6 & 0.3\\
-10.5 &10.9 & 0.1\\
-10.5 &11.0 & 0.1\\
-10.6 &11.2 & 0.1\\
-10.6 &11.4 & 0.1\\
-10.6 &11.7 & 0.1\\
-10.7 &11.0 & 0.2\\
-10.8 &11.2 & 0.2\\
-10.8 &11.3 & 0.2\\\hline
+\begin{tabular}{cccc}\hline\hline
+$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
+10.1 &10.2 & 0.1 & 0.1\\
+10.3 &10.5 & 0.1 & 0.2\\
+10.4 &10.7 & 0.1 & 0.3\\
+10.5 &10.6 & 0.3 & 0.1\\
+10.5 &10.9 & 0.1 & 0.4\\
+10.5 &11.0 & 0.1 & 0.5\\
+10.6 &11.2 & 0.1 & 0.6\\
+10.6 &11.4 & 0.1 & 0.8\\
+10.6 &11.7 & 0.1 & 1.1\\
+10.7 &11.0 & 0.2 & 0.3\\
+10.8 &11.2 & 0.2 & 0.4\\
+10.8 &11.3 & 0.2 & 0.5\\\hline
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{ccc}\hline\hline
-$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$\\\hline
-10.6 &10.7 &0.4\\
-10.8 &10.9 &0.6\\
-10.8 &11.0 &0.4\\
-10.9 &11.0 &0.8\\
-10.9 &11.0 &0.9\\
-10.9 &11.1 &0.5\\
-11.0 &11.1 &1.0\\
-11.1 &11.3 &0.8\\
-11.2 &11.6 &0.6\\
-11.2 &12.2 &0.5\\
-11.3 &11.7 &0.9\\\hline
+\begin{tabular}{cccc}\hline\hline
+$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
+10.6 &10.7 &0.4 & 0.1\\
+10.8 &10.9 &0.6 & 0.1\\
+10.8 &11.0 &0.4 & 0.2\\
+10.9 &11.0 &0.8 & 0.1\\
+10.9 &11.0 &0.9 & 0.1\\
+10.9 &11.1 &0.5 & 0.2\\
+11.0 &11.1 &1.0 & 0.1\\
+11.1 &11.3 &0.8 & 0.2\\
+11.2 &11.6 &0.6 & 0.4\\
+11.2 &12.2 &0.5 & 1.0\\
+11.3 &11.7 &0.9 & 0.4\\\hline
 \end{tabular}

### 2013-08-30 paper/ms.tex
new abstract, new conclusions

@@
 constructing mock fields from a large cosmological N-body
-simulation matching the observational geometries. To populate the
+simulation matching the geometries of observed fields. To populate the
 halos in the simulation we use a model where a dark matter halo with
 mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
-one LAE with a probability $f_{\rm occ}$.  We find that the observational information on the number density restricts the minimum mass to a
-range $10^{10}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ leaving all the
-other parameters unrestricted, while the clustering information puts a
-tight constraint of $M_{\rm   max}<10^{12}\hMsun$. This gives support
-to the idea that the most massive dark matter halos at that epoch do
-not host the brightest LAEs.  However, none of these observations is
-able to constrain the occupation fraction. It is always possible to
-find a model that is consistent with observations and has any desired
-occupation fraction in the range $0.1\leq f_{\rm occ}\leq
-1.0$. We also find that all models have a narrow mass range $\Delta M \equiv
+one LAE with a probability $f_{\rm occ}$. This main motivation to
+build such a model is to avoid the large uncertainties in the estimation of
+\ly luminosities. We find that the clustering and number density information are
+insufficient to impose a tight constraint on the escape fraction. On
+the other hand the minium mass and maximum mass are tightly
+constrained to be $M_{\rm max}<10^{12}$\hMsun and
+$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
+that all models have a narrow mass range $\Delta M \equiv
 \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex,
-with the vast majority in the range $\Delta M<0.5$ dex, meaning that
-there is only a factor of $3$ in mass between the minimum and maximum
-halo mass. We divide the best models into families of low and high occupation
-fraction with a transition around $f_{\rm occ}\leq 0.3$. These two
-families are almost disjoint in their values of $M_{\rm min}$. Low
-occupation fraction occurs below a threshold of $M_{\rm th}=
-10^{10.8}\Msun$, while high occupation fractions are present in
-models with $M_{\rm min}>M_{\rm th}$. This represents an unconclusive response as
-to which is the occupation fraction for LAEs at $z=3.1$. A definite
-answer requires a detailed physical model for the  connection between
+with the vast majority in the range $\Delta M<0.5$ dex. All previous
+constraints on the mass range and occupation fraction are a sub-set of
+the models we report in this paper. This represents an unconclusive response as
+to which is the occupation fraction for LAEs at $z=3.1$. A more
+precise answer requires physical models for the connection between
 dark matter, star formation and the escape of \ly radiation. That kind
-of modelling should also provide a plausible explanation for the
-narrow range in mass $\Delta M<1.0$ dex derived here for the halos
-hosting LAEs at $z=3.1$.
+of modeling should also provide a plausible explanation for the narrow
+ ange in mass $\Delta M<1.0$ dex derived here for the halos hosting
+ LAEs at $z=3.1$.
 
@@
     http://www.multidark.org/MultiDark/}}
-\citep{2011arXiv1109.0003R}. For each halo in the box we store its
+\citep{MultiDark}. For each halo in the box we store its
 position in the box (3-D coordinates) and FOF mass. We focus our work
@@
 models.
-
-\subsection{In the context of abundance matching models}
-
-The abundance matching methods are based on observational results for
-Lyman Break Galaxies \citep{Behroozi2013a,Behroozi2013b}  (LBG).  In
-the case of \cite{Behroozi2013a} the minimum halo mass considered to
-be relevant in their analysis is $10^{11.4}$\hMsun. They report
-stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$,
-which nevertheless are close to the lower bound of values inferred for
-LAEs at high redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.
-
-In our results, all the preferred models have a halo mass range lower
-than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
-abundance matching at $z=3$. This confirms once more the expectations
-that most of  LAEs are to be found in less massive halos LBG hosts.A
-detailed analysis of the spectral and photometric properties of LAEs
-coupled to the kind of analysis performed in this paper can be a guide
-in the study of the properties of low mass dark matter halos at
-$z=3.1$, extending the capabilities of abundance matching methods.
-
-\subsection{Caveats of our method}
-
-There are two important caveats for the work presented here. The first is the
-assumption of a single LAE per dark matter halo. This contradicts the
-general expectation of dark matter sub-halos in the simulation to host
-satellite galaxies. However, it has been found in analysis based on
-the shape of the correlation function \citep{Jose2013b} that satellite
-galaxies are not a dominant population, making our initial
-approximation a reasonable one. Therefore we think that it is not
-crucial to include the effect of satellites in the model.
-
-The second caveat are the precise values for the mass intervals. These
-numbers are defined from the halos defined in using the BDM halo
-finder with a density threshold of 200 times the critical
-density. Different halo finders and definitions for the detection
-density threshold can yield different masses up to a factor. For
-instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
-times the average interparticle distance finds halos on average $1.4$
-times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
-values for $M_{\rm min}$ and $M_{\rm max}$ should not be considered exact
-within less than $\sim 0.2$ dex.
-
-\subsection{On the reproducibility of our results}
-
-All the software, raw and processed data to produce the results
-and plots in this paper are publicly available in a github
-repository \footnote{https://github.com/forero/CosmicVarianceLAES}. Most
-of the code to produce the plots can be found as an Ipython notebook
-\citep{IPython} in the same repository.
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-In this \documentname we look for constraints on the preferred mass
-and occupation fraction of dark matter halos hosting Lyman Alpha Emitters at
-redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform this study
-paying attention to the impact of cosmic variance in these results. We
-build a large number of mock catalogs matching observational
-geometries. The mocks are constructed from a N-body simulation
-following a simple recipe to assign a single LAE to each halo. Only
-a fraction $f_{\rm occ}$ of halos with a mass range  $M_{\rm
-  min}<M_{\rm h}<M_{\rm   max}$ can host a LAE. We proceed with a
-thorough exploration of the space of free parameters $M_{\rm min},
-M_{\rm max}$ and $f_{\rm occ}$ to find mocks that are consistent with
-two observational constraints: the surface number density and the
-angular correlation function. Out of the initial $9000$ 
-combinations of parameters in the model we find $49$ arrangements
-consistent with observations.
-
-The successful parameter arrangements present a wide range of possibilities for
-DM hosting LAE hosts at $z=3.1$. This means that the available LAEs' spatial
-information is not sufficient to put a tight constraint on the mass
-and occupation fraction of DM halos hosting LAEs. In particular it is
-not possible to put a strong constraint on the occupation
-fraction. Such a wide range in solutions is facilitated by the large
-dispersion in the statistics derived from the mocks. All the halo mass
-ranges and occupation fractions deduced in previous analysis in
-previous analysis \citep[i.e.][]{Gawiser2007,Ouchi2010} are a subset of the
-models we find in this \documentname.
-
-Nevertheless, the successful models can be split into three families
-depending the mass range $\Delta M=\log_{10}M_{\rm max} -
-\log_{10}M_{\rm min}$ and the occupation fraction $f_{\rm occ}$. The
-first family is narrow both in $\Delta M$ and $f_{\rm occ}$, a second
-family is only narrow in $\Delta M$ and the third is narrow in $f_{\rm
-  occ}$ and broad in $\Delta M$.
-
-We find a large number of models with a narrow mass range
-$\Delta M<1.0$ dex that are consistent in every aspect with the
-spatial distribution of observed LAEs. In order to have this characteristic
-it is required that halos around the mass $M_{\rm   max}$ for each
-model become inefficient in hosting detectable LAEs. Two conditions
-can explain this. The first is having LAEs with a decreasing \ly
-escape fraction with increasing mass, the second is having larger screening
-effects by neutral Hydrogen around the most massive systems
-\citep{Laursen2009,ForeroRomero2011}.
-
-A third aspect that stands out is the existence of a dominant family
-of models with narrow $\Delta M<1.0$, as described before, and also a
-low occupation fraction $f_{\rm occ}<0.3$. This gives support to the
-common wisdom stating that only a small fraction of star forming
-galaxies can be detected as strong LAEs.
-
-However, there are extreme cases with a very narrow $\Delta M<0.3$, meaning that
-there is barely a factor of $\sim 2$ between the minimum and halo
-mass. If these models turn out to be confirmed, this would be a great
-challenge for galaxy formation models to explain how is that LAEs can
-be hosted in such a narrow range of halo mass.
-
-In summary, we show how current observations of LAEs cannot
-put a tight constraint on the physical models. We  foresee that the
-new observations with new instruments (such as MUSE, Hyper SuprimeCam
-and HETDEX) covering larger fields and a wider range of luminosities
-will be key in imposing tighter constraints on the properties of dark
-matter halos hosting LAEs.
-
-\section*{Acknowledgments} 
-J.E.F-R thanks the hospitality of Changbom Park and the Korea
-Institute for Advanced Study where the first full draft of this paper
-was completed. The authors also thank Peter Laursen, Paulina Lira, 
-Alvaro Orsi and Mark Dijkstra for helpful comments on the physical
-interpretation and presentation of our results.
 
@@
 
+\subsection{In the context of abundance matching models}
+
+The abundance matching methods are based on observational results for
+Lyman Break Galaxies \citep{Behroozi2013a,Behroozi2013b}  (LBG).  In
+the case of \cite{Behroozi2013a} the minimum halo mass considered to
+be relevant in their analysis is $10^{11.4}$\hMsun. They report
+stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
+their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$,
+which nevertheless are close to the lower bound of values inferred for
+LAEs at high redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.
+
+In our results, all the preferred models have a halo mass range lower
+than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
+abundance matching at $z=3$. This confirms once more the expectations
+that most of  LAEs are to be found in less massive halos LBG hosts.A
+detailed analysis of the spectral and photometric properties of LAEs
+coupled to the kind of analysis performed in this paper can be a guide
+in the study of the properties of low mass dark matter halos at
+$z=3.1$, extending the capabilities of abundance matching methods.
+
+\subsection{Caveats of our method}
+
+There are two important caveats for the work presented here. The first is the
+assumption of a single LAE per dark matter halo. This contradicts the
+general expectation of dark matter sub-halos in the simulation to host
+satellite galaxies. However, it has been found in analysis based on
+the shape of the correlation function \citep{Jose2013b} that satellite
+galaxies are not a dominant population, making our initial
+approximation a reasonable one. Therefore we think that it is not
+crucial to include the effect of satellites in the model.
+
+The second caveat are the precise values for the mass intervals. These
+numbers are defined from the halos defined in using the BDM halo
+finder with a density threshold of 200 times the critical
+density. Different halo finders and definitions for the detection
+density threshold can yield different masses up to a factor. For
+instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
+times the average interparticle distance finds halos on average $1.4$
+times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
+values for $M_{\rm min}$ and $M_{\rm max}$ should not be considered exact
+within less than $\sim 0.2$ dex.
+
+\subsection{On the reproducibility of our results}
+
+All the software, raw and processed data to produce the results
+and plots in this paper are publicly available in a github
+repository \footnote{https://github.com/forero/CosmicVarianceLAES}. Most
+of the code to produce the plots can be found as an Ipython notebook
+\citep{IPython} in the same repository.
+
+\section{Conclusions}
+\label{sec:conclusions}
+
+In this \documentname we look for constraints on the preferred mass
+and occupation fraction of dark matter halos hosting Lyman Alpha Emitters at
+redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform this study
+paying special attention to the impact of cosmic variance on these
+results. To this end we build a large number of mock catalogs matching
+observational geometries. The mocks are constructed from a N-body simulation
+following a simple recipe to assign a single LAE to each halo. Only
+a fraction $f_{\rm occ}$ of halos with a mass range  $M_{\rm
+  min}<M_{\rm h}<M_{\rm   max}$ can host a LAE. We proceed with a
+thorough exploration of the space of free parameters $M_{\rm min},
+M_{\rm max}$ and $f_{\rm occ}$ to find mocks that are consistent with
+two observational constraints: the surface number density and the
+angular correlation function. Out of the initial $9000$ 
+combinations of parameters in the model we find $23$ arrangements
+consistent with observations.
+
+We find that the observational information we use is insufficient to
+impose a tight constraint on the escape fraction. On the other hand
+the minium mass and maximum mass are tightly constrained as follows
+$M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
+10^{11.5}\hMsun$. Furthermore, we find that the mass range defined as
+$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is always
+$\Delta M\leq 1.0$.
+
+The wide range in solutions is facilitated by the large dispersion in
+the statistics derived from the mocks. Nevertheless, all the halo mass
+ranges and occupation fractions deduced previous analysis
+\citep[i.e.][]{Gawiser2007,Ouchi2010} are a subset of the models we
+find in this \documentname. All of our models support the notion that
+the most massive halos at $z=3.1$ do not host the brightest LAEs.
+
+The existence of a narrow mass range for halos hosting LAEs, $\Delta
+M\leq 1.0$ dex, has two different explanations at least. The
+first is having LAEs with a decreasing \ly escape fraction with
+increasing mass, the second is having larger screening effects by
+neutral Hydrogen around the most massive systems
+\citep{Laursen2009,ForeroRomero2011}.
+
+However, there are extreme cases with a very narrow $\Delta M<0.3$, meaning that
+there is barely a factor of $\sim 2$ between the minimum and halo
+mass. If these models turn out to be confirmed, this would be a great
+challenge for galaxy formation models to explain how is that LAEs can
+be hosted in such a narrow range of halo mass.
+
+In summary, we show how spatial information of LAEs cannot
+put a tight constraint on their host halos and occupation fraction. We
+foresee that the new observations with new instruments (such as MUSE,
+Hyper SuprimeCam and HETDEX) covering larger fields and a wider range
+of luminosities will be key in imposing tighter constraints on the
+properties of dark matter halos hosting LAEs. At the same time,
+additional modeling for \ly radiation transfer, is needed to put a
+tighter constrain on the \ly escape fraction in high redshift
+galaxies.
+
+\section*{Acknowledgments} 
+J.E.F-R thanks the hospitality of Changbom Park and the Korea
+Institute for Advanced Study where the first full draft of this paper
+was completed. The authors also thank Peter Laursen, Paulina Lira, 
+Alvaro Orsi and Mark Dijkstra for helpful comments on the physical
+interpretation and presentation of our results. J.E.F-R was
+supported by the FAPA grant by Vicerrector\'ia de Investigaciones at
+Universidad de los Andes.
+
+The MultiDark Database used in this paper and the web application
+providing online access to it were constructed as part of the
+activities of the German Astrophysical Virtual Observatory as result
+of a collaboration between the Leibniz-Institute for Astrophysics
+Potsdam (AIP) and the Spanish MultiDark Consolider Project
+CSD2009-00064. The Bolshoi and MultiDark simulations were run on the
+NASA's Pleiades supercomputer at the NASA Ames Research Center.
+
 \bibliographystyle{mn2e}

### 2013-08-30 paper/ms.tex
new introduction done

@@
 
-\title[Halo mass and occupation fraction for LAEs at
-  $z=3.1$]{Mass and occupation
-  fraction of dark matter halos hosting Lyman-$\alpha$ emitters
-  at $z\sim 3$}    
-\author[~J.~E. Forero-Romero and ~J.~E Mejia-Restreo]{
+\title[Halo mass and occupation fraction of LAEs at$z=3.1$]{Mass and
+  occupation fraction of dark matter halos hosting Lyman-$\alpha$
+  emitters at $z\sim 3$}      
+\author[~J.~E. Forero-Romero and ~J.~E. Mejia-Restreo]{
 \parbox[t]{\textwidth}{\raggedright 
@@
 mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
-one LAE with a probability $f_{\rm occ}$. This main motivation to
+one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
 build such a model is to avoid the large uncertainties in the estimation of
@@
 that all models have a narrow mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than 1.0 dex,
-with the vast majority in the range $\Delta M<0.5$ dex. All previous
-constraints on the mass range and occupation fraction are a sub-set of
-the models we report in this paper. This represents an unconclusive response as
-to which is the occupation fraction for LAEs at $z=3.1$. A more
-precise answer requires physical models for the connection between
-dark matter, star formation and the escape of \ly radiation. That kind
-of modeling should also provide a plausible explanation for the narrow
- ange in mass $\Delta M<1.0$ dex derived here for the halos hosting
- LAEs at $z=3.1$.
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
+with the vast majority in the range $\Delta M<0.5$ dex. Already
+published constraints on the mass range and occupation fraction are a sub-set of
+the models we report in this \documentname. Our results present an
+inconclusive response as to which is the occupation fraction for LAEs
+at $z=3.1$. A precise answer requires robust physical models for the
+connection between dark matter, star formation and the escape of \ly
+radiation. That kind of modelling should also be able to provide a
+plausible explanation for the narrow ange in mass $\Delta M<1.0$ dex
+derived here for the halos hosting LAEs at $z=3.1$.
 
@@
 \citep{Koehler2007},  signposts for low metallicity stellar
-populations, markers of the galaxy formation process through
-cosmic history \citep{ForeroRomero2012} and tracers of active star
-formation  \citep{Guaita2013}
+populations, markers of the galaxy formation process at high redshift
+\citep{Dayal2009,ForeroRomero2012} and tracers of active star formation
+\citep{Guaita2013}
 
@@
 formation in a cosmological context. In this context it is considered
-that dominant matter content of the Universe is to be found in dark
+that the dominant matter content of the Universe is to be found in dark
 matter (DM), whereby each galaxy is hosted by larger dark matter structure
@@
 star formation cycle are also though to be strongly dependent on its
-mass.  For these reasons, finding the typical dark matter halo mass
+halo mass.  For these reasons, finding the typical dark matter halo mass
 hosting LAEs represents a significant step forward to understand the
@@
 modelling has been implemented from analytic considerations,
-semi-analytic models  and  full N-body hidrodynamical simulations
-\citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012, Orsi2012,
-  Soler2012}.
+semi-analytic models \citep{Garel2012, Orsi2012}and  full N-body
+hydrodynamical simulations \citep{Laursen2007, Dayal2009,
+  ForeroRomero2011, Yajima2012, Soler2012}.
 
 In addition to the uncertainties in the astrophysical processes
-describing star formation in galactic populations, is the calculation
+describing star formation in galactic populations,the calculation
 of the fraction of \ly photons that escape the galaxy to the observer
@@
 interstellar medium
-(ISM). \citep{Neufeld1991,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
-
-This problem can be tackled with Monte Carlo simulations for the
+(ISM). This problem can be tackled with Monte Carlo simulations for the
 radiative transfer, however the complexity of the relevant physical
@@
 the theoretical expected value for the \ly escape fraction
-at high redshift.
+at high redshift
+\citep{Neufeld1991,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
 
 Another approach to infer the typical DM halo mass of halos hosting
-LAEs is based on the spatial information. This uses the fact that in cold
+LAEs is based on the clustering information. This uses the fact that in cold
 dark matter cosmologies the spatial clustering of galaxies on large
@@
 
-In this \documentname to study the impact of cosmic variance,
-we implement a method to populate the DM halos in cosmological
-simulations with LAEs. This approach bypasses all the uncertainty
-involved in the estimation of star formation rates and \ly escape
+In this \documentname we implement a method to populate the DM halos
+in cosmological simulations with LAEs that bypasses all the
+uncertainty involved in the estimation of star formation rates and \ly escape
 fraction. The model only considers whether a DM can host a
-detectable LAE or not. It does not predict a \ly  luminosity. Once the
+detectable LAE or not without predicting a \ly  luminosity. Once the
 mock catalogs are constructed  we proceed with a direct comparison

### 2013-08-30 paper/ms.tex
updated methodology

@@
 comparison: (i) the distribution of the surface number density
-across fields fields and (ii) the angular correlation function measured in
+across fields and (ii) the angular correlation function measured in
 some fields.
@@
 
-\subsection{Observational Constraints}
+\subsection{Observational constraints}
 
@@
 comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
-band filter used in the survey is centered at $4977$ \AA with  $77$\AA width,
-corresponding to the redshift range $z=3.062-3.125$ and $41$ Mpc
-$h^{-1}$ comoving scale for the detection of the Lyman-$\alpha$ line
-centered at $z=3.09$. The authors reported a
-total  $2161$  LAEs with an observed equivalent width, in the observer
-frame, larger than $190$\AA 
-over a total survey area of $2.42$ deg$^{2}$ that includes 12 sub-fields, 
-this corresponds to average surface number density of $0.20\pm 0.01$
-arcmin$^{-2}$.
+band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
+corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
+centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
+an observed equivalent width, in the observer frame, larger than $190$
+\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
+sub-fields,  this corresponds to average surface number density of
+$0.20\pm 0.01$ arcmin$^{-2}$.
 
@@
 \cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
-densest field of SSA22 while \cite{Ouchi2008} observed on a 1 deg$^2$
-sky of the SXDS Field.  There are some differences between these
+densest field of SSA22 while \cite{Ouchi2008} observed on a $\sim 0.5$
+deg$^2$ field.  There are some differences between these
 observations and those by \cite{Yamada2012}. The details in the color
 selection, corresponding limiting luminosities and EW thresholds are
-different in these references. Nevertheless we use these observations
-as additional constraints in spite of the fact that the first selected
-models are based only on the surface density statistics by
-\citep{Yamada2012}.
+different in these references. Nevertheless we use the ACF from these
+observations as additional constraints in spite of the fact that the
+first selected models are based only on the surface density statistics by
+\cite{Yamada2012}.
 
-\subsection{Simulation and Halo Catalogs}
+\subsection{Simulation and halo catalogs}
 
@@
 \citep{MultiDark}. For each halo in the box we store its
-position in the box (3-D coordinates) and FOF mass. We focus our work
+comoving position in the box (3-D coordinates) and FOF mass. We focus our work
 on halos more massive than $1\times 10^{10}$\hMsun that are resolved
@@
 
-\subsection{A Model to Populate Halos with LAEs}
+\subsection{A model to populate halos with LAEs}
 \label{subsec:mocks}
@@
   survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
-    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt match}
+    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
   method. The larger panel shows $7$ mock
@@
   the simulation, but constructed following the same pattern in the
-  {\texttt match} method.}
+  {\texttt{match}} method.}
 \end{center} 
@@
 decide whether a halo host a LAE: the lower and upper bounds for the
-mass range $M_{\rm min}< M_{\rm h} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
+mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
 must keep in mind that the physical interpretation of the occupation
-fraction $f_{\rm occ}$ convolves two phenomena: the presence of a star
+fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
 forming galaxy in a halo and its detectability as a LAE.  We do not
@@
 mock fields into a mock catalog is done in two different ways. The
-first is called {\texttt match}, it follows the clustering of the
+first is called {\texttt{match}}, it follows the clustering of the
 observational fields. From the $12$ mock fields, $7$ are constructed
@@
 imitate the SDF and GOODS-North field.   The second way to group the
-mock fields is called {\texttt   random}, whereby all the $12$ fields
+mock fields is called {\texttt{random}}, whereby all the $12$ fields
 are selected in such a way as to avoid that any two volumes are
 contiguous. In this \documentname we only report the results obtained
-by the {\texttt match} method and mention explicitly differences
-observed with the {\texttt random} selection.
+by the {\texttt{match}} method and mention explicitly differences
+observed with the {\texttt{random}} selection.
 
-We note that we use $15\times 12=144$ mock fields out of the total of $210$
-available sub-volumes. The reason is that the {\texttt match}
+Figure \ref{fig:distros} shows the spatial distribution for one mock
+survey constructed using the {\texttt{match}} method. Each field
+corresponds to one of the observational fields. The model parameters
+to build it are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
+  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. It is only one out of
+the $15$ different mock surveys that are constructed for each
+model. We note that we use $15\times 12=180$ mock fields out of the
+total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
 method imposes constraints on the way the $7$ fields mimicking the
@@
 sub-volumes in the box. We decide to keep the number of mock surveys
-fixed to $15$ also for the {\texttt random} method in order to allow a
+fixed to $15$ also for the {\texttt{random}} method in order to allow a
 fair comparison between the two methods.
 
-\subsection{Exploring and Selecting Good Models}
+\subsection{Exploring and selecting good models}
 
 We make a thorough exploration of the parameter space for the models
-${\mathcal M}$. $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
+${\mathcal M}$ where $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
 to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
@@
 
-The lower limit for the parameter $M_{\rm min}$ is set by the minium
+The lower limit for the parameter $M_{\rm min}$ is set by the minimum
 occupation fraction we are able to consider. At $M_{\rm
@@
 for all the models having the $15$ mock surveys consistent with
-observations . The ACF is computed  ( using 
-the Landy \&  Szalay  estimator \citep{Landy1993} )  on two kinds of
-fields in the mock survey: the densest and one corresponding to the
-average density. The first with the \cite{Hayashino2004}  and \cite{Ouchi2010}
-ACFs respectively.
+observations . The ACF is computed using 
+the Landy \&  Szalay estimator \citep{Landy1993}  on two different 
+fields in the mock survey. The first field is the densest to be compared
+against the results of \cite{Hayashino2004}. The second field
+has an average number density and is compared against \cite{Ouchi2010}.
 
-The observational ACF and the  mock  ACF of the models are compared   
-in terms of the correlation length ($\theta_{0}$) by fitting 
-them to a power-law function:
-
+The observed and mock ACF are fit to a power-law function:
 \begin{equation}
-\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}
+\omega(\theta) = \left(\frac{\theta}{\theta_{0}}\right)^{-\beta}, 
 \label{eq:fitting}
 \end{equation}
-
-Both mock and observational ACF are derived by a least square
-minimization procedure. For each mock we obtain a covariance matrix
-that gives us the uncertainty in the parameters $\beta$ and
-$\theta_0$. We compute a mean value for the parameters and its
-associated uncertainty as the cuadratic average of the uncertainties in
-the fitting procedure. We consider that a model is consistent with
-observations if the two parameters $\beta$ and $\theta_0$ are equal
-within a $1$-$\sigma$ range.
+where $\theta_0$ and $\beta$ are free parametres. The fit is donde
+using a least square minimization procedure. For each mock field we obtain a
+covariance matrix that gives us the uncertainty in the parameters $\beta$ and
+$\theta_0$. Using the $15$ mock fields in a mock survey, we compute a
+mean value for the parameters and its associated uncertainty as the
+cuadratic average of the uncertainties in the fitting procedure. We
+consider that a model is consistent with observations if the two
+parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
+range.
 

### 2013-08-30 paper/ms.tex
new results section

@@
 observational constraints narrow down the parameters space of allowed
-models. Each sub-sections presents the effect of adding new pieces of
+models. Each sub-section presents the effect of adding new pieces of
 observational or statistical evidence.
@@
 In Figure \ref{fig:halos} we present the results for  the
-integrated dark matter halo surface density as a function of halo
-mass. Each line corresponds to one of the 210 sub-volumes in the
-Bolshoi simulation. The gray band indicates the surface density
-values for LAEs allowed reported in observations \citep{Yamada2012}.
+integrated dark matter halo surface density as a function of the
+minimum halo mass $M_{\rm min}$. Each line corresponds to one of the
+210 sub-volumes in the Bolshoi simulation. The gray band indicates the
+surface density values for LAEs allowed by observations
+\citep{Yamada2012}.
 
-This result provides the basis to understand why only a specific range of models
-${\mathcal M}$ can be expected to be consistent with
+This result allows us to understand why only a specific range of
+models ${\mathcal M}$ can be expected to be consistent with
 observations. From Figure \ref{fig:halos} we can read that models with
-a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
-surface number density lower than the observational
-constrain. This makes impossible that models in that range can be
-compatible with observations, there are simply to few halos compared
-to observed LAEs.
-
-The opposite is true in models with $\log_{10} M_{\rm min}<10.5$ that
-have a surface number density larger than observations. In those cases
-the occupation fraction $f_{\rm occ}<1.0$ can be tuned in order to
-lower the halo number density to match observations.
+a minimum mass $M_{\rm min}>10^{11.5}$\hMsun will always have a
+surface number density lower than the observational constrain. This
+makes impossible that models in that range can be compatible with
+observations, there are simply to few halos compared to observed
+LAEs. The opposite is true in models with $M_{\rm
+  min}<10^{10.5}$\hMsun that have a surface number density larger
+observations. In those cases the occupation fraction $f_{\rm occ}<1.0$
+can be tuned in order to lower the halo number density to match
+observations.
 
@@
 variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
-mass range $10^{10}\hMsun < M_{\rm  min}<10^{11}\hMsun$.  A consequence of
-this variation is that models with the same mass range and occupation
-fraction can have mock fields with number densities varying up to a
-factor of $\sim 2-5$. Also, the scatter in mocks across the simulation
-is comparable to the $0.3$ dex scatter in observations.
+number density abudance.  A consequence of this variation is that
+models with the same mass range and occupation fraction can have mock
+fields with number densities varying up to a factor of $\sim
+2-5$. This scatter is comparable to the $0.3$ dex scatter coming from 
+observations. In the same Figure \ref{fig:halos} we see that at fixed
+number density, around the range allowed by observations, there is an
+scatter in the masses of $0.4-0.5$ dex.
 
-In the same Figure \ref{fig:halos} we see that at fixed number
-density, around the range allowed by observations, there is an scatter
-in the masses of $0.4-0.5$ dex. This intrinsic scatter in the masses
-with a given number density adds is also included in the mock
-construction process, enlarging the range of possible models
-consistent with observations.
+This scatter induced by cosmic variance is naturally included in the
+mock construction process. This will allows us to have a wider range
+of models compatible with observations, as compared with a model that
+neglects cosmic variance.
 
@@
 Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
-min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
+min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test yields
 values of $P>0.05$ at least for one mock survey, which is the most
@@
 constraint the minimum mass $M_{\rm min}$ to a narrow range, while
-$M_{\rm max}$ and $f_{\rm occ}$ remain unconstrained.
+$M_{\rm max}$ and $f_{\rm occ}$ remain largely unconstrained.
 
 In Figure \ref{fig:landscape} there are three regions of parameter
-space that can be clearly distinguished. The first region corresponds
-to models where the minimum mass is high $\log_{10}M_{\rm min}>
-11.5$. None of these models is compatible with observations as expected
-from the arguments presented in the previous subsection. For these
-models the number density of LAEs is too low compared to
-observations.
+space that can be clearly distinguished. The first corresponds to
+models where the minimum mass is high $M_{\rm min}>
+10^{11.5}\hMsun$. None of these models is compatible with observations
+as expected from the arguments presented in the previous
+subsection. For these models the number density of LAEs is too low
+compared to observations.
 
 The second region corresponds to an intermediate range for the minimum
-mass $10.5<\log_{10}M_{\rm min}<11.5$ where, regardless of the value of
-the maximum mass $M_{\rm max}$, it is possible to tune the occupation
-fraction $f_{\rm occ}$ to bring some of the mock observations into
-good agreement with observations. In this region of parameter space
-one can find two extreme kinds of models.  One kind where the
-mass interval $\Delta M\equiv \log_{10} M_{\rm max} - \log_{10}M_{\rm
-  min}$ is narrow with $\Delta M<1.0$ dex, others where the mass interval is 
-extended $\Delta M>1.0$dex going up to the maximum halo mass
-present in the simulation at that redshift, up to $\Delta M = 2.5$ dex
-in some cases.
+mass $10^{10.5}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ where,
+regardless of the value of the maximum mass $M_{\rm max}$, it is
+possible to tune the occupation fraction $f_{\rm occ}$ to bring some
+of the mock surveys into good agreement with observations. In this
+region of parameter space one can find two extreme kinds of models.
+One kind where the mass interval $\Delta M\equiv \log_{10} M_{\rm max}
+- \log_{10}M_{\rm  min}$ is narrow with $\Delta M<1.0$ dex, others
+where the mass interval is  extended $\Delta M>1.0$ dex going up to
+the maximum halo mass present in the simulation at that redshift, with
+$\Delta M = 2.5$ dex in those cases.
 
-The third region in parameter space corresponds to $\log_{10}M_{\rm
-  min}<10.5$. In this case only models with a very narrow mass interval of
-at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
-occupation fractions $f_{\rm occ}<0.3$ are allowed.
+The third region in parameter space corresponds to $M_{\rm
+  min}<10^{10.5}\hMsun$. In this case only models with a very narrow
+mass interval of at most $0.5$ dex ($M_{\rm max}<10^{11.0}\hMsun$) and low
+occupation fractions $f_{\rm occ}\leq 0.3$ are allowed.
 
@@
 However, the additional information we gain with this test is the
-relative abundance of models in the parameter space. Not all the
+relative abundance of models in the parameter space. Not all 
 models in the second region have an equal abundance. By inspection of
 Figure \ref{fig:landscape} it seems that models with $\log_{10}M_{\rm
-  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}<0.3$
-are preferred.  In the next sub-section we explore in detail the
+  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}\leq 0.3$
+are preferred.  In the next sub-sections we explore in detail the
 models in this region, imposing tighter constraints on the KS test
@@
 
-In the previous Section we present a conservative criterion of
+In the previous sub-section we presented a conservative criterion of
 agreement by selecting the models that had at least one mock survey
@@
 consistent mock surveys. On the other hand, from the right panel in
-Figure \ref{fig:restriction_mock} one can see that there is not a
-strong reduction on the favored values for the occupation fraction
-$f_{\rm occ}$.
+Figure \ref{fig:restriction_mock} one can see that the reduction of
+favored values for the occupation fraction $f_{\rm occ}$ is not strong.
 
@@
 over the mocks is shown in comparison with the result derived from
-observations.  The error bars in this Figure represents the standard
-deviation of the ACF over all the 15 mock fields used to make the
-computation.  These error bars are larger than the statistical
-uncertainty from the fitting procedure on a single field.
-
-In the left panel Figure \ref{figure:correlation_parameters} we see
-how the observational ACF measured by \cite{Hayashino2004} (green dot)
-is successful in reducing the total number of possible models. Only
-those with angular-correlation length within
-$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
-reproduce observations. The right panel of Figure
-\ref{figure:correlation_parameters} shows the results for fields in
-the mock catalog that have an average number density that are compared
-against the fit of the data reported by \cite{Ouchi2010}. In this case
-we find that there are large uncertainties in the observational data,
-however it is possible to discard a fraction of the models.
+observations. In the left panel Figure \ref{fig:correlation_parameters} we see
+how the observational ACF measured by \cite{Hayashino2004} 
+can be successful in reducing the total number of possible models. The
+right panel shows the results for fields in the mock catalog with an
+average number density compared against the fit of the data
+reported by \cite{Ouchi2010}. In this case we find that there are
+large uncertainties coming from the observational data, and only a reduced
+fraction of the modesl can be discartded.
 
 In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
-models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
-both for the comparisong against \cite{Hayashino2004} and
+models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
+both for the comparisons against \cite{Hayashino2004} and
 \cite{Ouchi2010}. To make this selection we consider that
-a model is consistent with observations if there is a $1-\sigma$
+a model is consistent with observations if there is a $1$-$\sigma$
 overlap between both the correlation length $\theta_0$ and the power
@@
 
-At this point we take the most strict selection criterio and keep the
-models that are consistent with both observational constraints. This
-basically reduces the selection to the models already restricted by
+At this point we take the most strict decision to keep 
+models consistent with both observational constraints. This
+reduces the selection to the models already restricted by
 the data in \cite{Hayashino2004} as presented in the lower panels of Figure
@@
 meaningful constraints on the values of $M_{\rm max}$. However, the
-possible values for the occupation fraction are still in the initial
-range $0.1\leq f_{\rm occ}\leq 1$.
+possible values for the occupation fraction, despite having a strong correlation
+with $M_{\rm min}$, still are in the initial range $0.1\leq f_{\rm
+  occ}\leq 1$.
 

### 2013-08-30 paper/ms.tex
MNRAS version

@@
 insufficient to impose a tight constraint on the escape fraction. On
-the other hand the minium mass and maximum mass are tightly
+the other hand the minimum mass and maximum mass are tightly
 constrained to be $M_{\rm max}<10^{12}$\hMsun and
@@
 radiation. That kind of modelling should also be able to provide a
-plausible explanation for the narrow ange in mass $\Delta M<1.0$ dex
+plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
 derived here for the halos hosting LAEs at $z=3.1$.
@@
 used to predict galaxy properties such as the stellar mass and
-star formation rate \citep{Behroozi2012}. Processes that regulate the
+star formation rate \citep{Behroozi2013a}. Processes that regulate the
 star formation cycle are also though to be strongly dependent on its
@@
 at high redshift
-\citep{Neufeld1991,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
+\citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
 
@@
 \begin{center}
-\includegraphics[width=0.8\linewidth,angle=0]{./plots/Figure0.pdf}
+\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
 \caption{ \label{fig:distros} Spatial distribution of a LAEs mock
@@
 forming galaxy in a halo and its detectability as a LAE.  We do not
-peform a explicit modeling for LAE detectability. Our model does not
+perform a explicit modeling for LAE detectability. Our model does not
 assign a luminosity or escape fraction to each LAE.  We are only
@@
 method imposes constraints on the way the $7$ fields mimicking the
-SSA22 can be distributed. This restriction makes unusuable some of the
+SSA22 can be distributed. This restriction makes unable some of the
 sub-volumes in the box. We decide to keep the number of mock surveys
@@
 \end{equation}
-where $\theta_0$ and $\beta$ are free parametres. The fit is donde
+where $\theta_0$ and $\beta$ are free parameters. The fit is done
 using a least square minimization procedure. For each mock field we obtain a
@@
 mean value for the parameters and its associated uncertainty as the
-cuadratic average of the uncertainties in the fitting procedure. We
+quadratic average of the uncertainties in the fitting procedure. We
 consider that a model is consistent with observations if the two
@@
 \begin{center}
-\includegraphics[width=1.10\linewidth,angle=0]{./plots/Fig1.pdf}
+\includegraphics[width=1.10\linewidth,angle=0]{Fig1.pdf}
 \caption{ \label{fig:halos} Surface density of dark
@@
   total number of elements in a volume. Each line represents one of the
-  $210$ volumes of dimensions $46\times 35\times 41$ h${-3}$Mpc$^{3}$
+  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
   in the Bolshoi simulation. The horizontal gray band represents the
@@
 variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
-number density abudance.  A consequence of this variation is that
+number density abundance.  A consequence of this variation is that
 models with the same mass range and occupation fraction can have mock
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_match_P5.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
 \vspace{5mm}
-\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig2_random_P5.pdf}
-%\hspace{5mm}
-%\includegraphics[width=0.49\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
+\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
 \end{center} 
-\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}-f_{\rm
+\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
     occ}$ (right) planes for all models with  KS test values
@@
 \begin{center}
-\includegraphics[width=0.95\linewidth,angle=0]{./plots/Fig4_match_P5.pdf}
-%\hspace{5mm}
-%\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig4_random_P5.pdf}
+\includegraphics[width=0.95\linewidth,angle=0]{Fig4_match_P5.pdf}
 \end{center} 
@@
 and $f_{\rm occ}$. In the next section we use additional observational
-information to constrain these paremeters.
+information to constrain these parameters.
 
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_mass_mock.pdf} 
+\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_mass_mock.pdf} 
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig5_match_f_occ_mock.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_f_occ_mock.pdf}
 \end{center}  
@@
   the maximal number of consistent mocks is imposed. Only the results
-  for the {\texttt match} method are shown.
+  for the {\texttt{match}} method are shown.
   \label{fig:restriction_mock}}  
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_maxden.pdf} 
+\includegraphics[width=0.46\linewidth,angle=0]{power_law_correlation_maxden.pdf} 
 \hspace{5mm}  
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/power_law_correlation_meanden.pdf} 
+\includegraphics[width=0.46\linewidth,angle=0]{power_law_correlation_meanden.pdf} 
 \end{center}
-\caption{Left: Values for the free parameters ($\theta_{0}$ vs $\beta$) 
+\caption{Values for the free parameters $\theta_{0}$ and $\beta$
 in the fitting formula (Eq. \ref{eq:fitting}) for the angular
 correlation function. Blue dots correspond to simulations and the
-green cross to observations by \citet{Hayashino2004} and
-\citet{Ouchi2010}. The error bars in the   theoretical data correspond
-to the standard deviation from the different mocks surveys. 
+green cross to observations by \citet{Hayashino2004} (left) and
+\citet{Ouchi2010} (right). The error bars in the theoretical data correspond
+to the quadratic average of the fitting errors for each mock survey
 \label{fig:correlation_parameters}}
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_mass.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_meanden_f_occ.pdf}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_mass.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_f_occ.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig6_maxden_f_occ.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_f_occ.pdf}
 \end{center}
-\caption{Planes $M_{\rm min}$ vs $M_{\rm max}$ (left), $M_{\rm min}$
-  vs $f_{\rm occ}$ (right). The squares represent the models when both
+\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
+    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
    constraints on the maximal number of consistent mocks and the
-  angular correlation function are included. Upper panels correspond
-  checks the consistency against the observational data of
-  \citet{Ouchi2010}, while lower panels show results for \citet{Hayashino2004}
+  angular correlation function. Upper panels correspond
+  checks the consistency with the observational data of
+  \citet{Ouchi2010}. Lower panels show results after comparison
+  against \citet{Hayashino2004}
   \label{fig:restriction_mock_and_f_occ_corr}} 
@@
 large uncertainties coming from the observational data, and only a reduced
-fraction of the modesl can be discartded.
+fraction of the models can be discarded.
 
@@
 
-In the Results Section we start by matching the rough numbers for the
+In the previous Section we started by matching the rough numbers for the
 galaxy surface number density. This sets the median mass of all
-successful models to the broad range $(10^{10}-10^{12})$ \hMsun for
-$M_{\rm min}$ and $M_{\rm max}$. We include additional criteria on the
+successful models to the broad range $(10^{10}$-$10^{12})$ \hMsun for
+$M_{\rm min}$ and $M_{\rm max}$. Then we included additional criteria on the
 number of mock surveys that must be consistent observations
 and the information from the angular correlation function, reducing
-the number of feasible models. We end up with $\sim 25$ models out of
+the number of feasible models. We ended up with $23$ models out of
 the initial $9000$ possible combination of parameters.
 
-In order to make a physical interpretation of these models we use 
-the halo mass range, defined as $\Delta M=\log_{10}M_{\rm max} -
-\log_{10}M_{\rm  min}$, together with the occupation fraction $f_{\rm
-  occ}$ to classify all the successful models into two families:
+Now we define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
+\log_{10}M_{\rm  min}$, to use it together with the occupation
+fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ to
+classify all the successful models into two families:
 
@@
 \end{itemize}
-
-The full list of paramenter in the two families is summarized in Table
+%
+The full list of parameter in the two families is summarized in Table
 \ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
@@
 two conclusions. First, the occupation fraction cannot be constrained
-based on clustering anaylsis. Second, the halos hosting LAEs have a
+based on clustering analysis. Second, the halos hosting LAEs have a
 narrow mass range.
 
-The existence of a narrow mass rango for halo masses has different
-possible explanations. A cut at the low mass end $M_{\rm min}$ can be
+The existence of a narrow mass range for halo masses has different
+possible explanations. A cut at the low mass end, $M_{\rm min}$, can be
 interpreted in terms of the minimal halo star formation rate needed to
-produce the minimal \ly  luminosity to be above a given detection
+produce the \ly luminosity needed to be above a given detection
 threshold.  However, under the reasonable assumption of star formation
-rate increasing with halo mass, the cut at higher halo masses requires
-a different justification. There are two complementary physical
-scenarios that can provide it.
+rate increasing with halo mass, the cut at higher halo masses $M_{\rm
+  max}$requires a different justification. There are two complementary physical
+scenarios that could provide it.
 
 One scenario can be presented in terms of a decreasing escape fraction
-of \ly radiation in massive systems. There are detailed models for
-radiative transfer that support the idea that massive galaxies with
-higher metallicities have larger dust contents and less concentrated
-ISM than lower mass systems. Due to the resonant nature of the \ly
-line the probability of absorption  of \ly photons increases in
-massive systems, producing high absorption of \ly photons but not of
-continuum or other non-resonant lines \citep{Laursen2009,ForeroRomero2011}.
-
-A second scenario is that larger systems have more extended gaseous
-envelopes which due to resonance effects of the \ly line, can induce a
-low surface brightness and a broader line, making these systems less
-observable in narrow band filter surveys
-\citep{Laursen2009,Zheng2010}.
-
-The preference for narrow $\Delta M$ ranges to host LAEs 
-and the small presence of reasonable models with $M_{\rm max}>
-10^{12}$\hMsun also follows theoretical and observational
-insights for high-z galaxies where the most massive systems are not
-bright \ly sources \citep{ForeroRomero2012,Shapley2003}.
+of \ly radiation in massive systems. Detailed galaxy formation models
+support the idea that massive galaxies with higher metallicities have
+larger dust contents and less concentrated ISM than lower mass
+systems. Due to the resonant nature of the \ly line the probability of
+absorption  of \ly photons increases in massive systems, producing
+high absorption of the \ly line but not of UV continuum or other
+non-resonant lines \citep{Laursen2009,ForeroRomero2011}. In a second
+scenario larger systems have more extended gaseous envelopes which due
+to resonance effects of the \ly line, induces a low surface brightness
+and a broader line, making these systems less observable in narrow
+band filter surveys \citep{Laursen2009,Zheng2010}.
 
@@
 
-Theoretical intepretations of blind galaxy surveys at $z=2.2$ find a
+Theoretical interpretations of blind galaxy surveys at $z=2.2$ find a
 volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
@@
 Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} uses similar
+fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} use similar
 methods to find an average \ly escape fraction in high-z galaxies,
-they conclude that there is a range in luminosity where the escape
+they conclude that there is a range in \ly luminosity where the escape
 fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
-be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$.
-
-We consider a success that our model indeed includes such low
-occupation fraction models. The observational evidence from galaxy
-surveys seem to disfavor the second family of models with high
-occupation fractions. Nevertheless, it remains a task for galaxy
-formation models to explain the mass range $\Delta M<0.5$ in the models.
+be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$. We
+consider a success that our model indeed includes such low occupation
+fraction models. The observational evidence from galaxy surveys seem
+to disfavor the second family of models with high occupation
+fractions. Nevertheless, it remains an open task to explain the narrow
+mass range $\Delta M<0.5$ in most of the models.
 
@@
 
-Observational based on the ACF inferred from photometric measurements
-in the Extended Chandra Deep Field South have shown that the median
-dark matter masses of h los hosting LAEs is $\log_{10}M_{\rm
-  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
-fraction of $1-10\%$  \citep{Gawiser07}.  Our results are in a general
-good agreement with those estimates for the host mass. This is not
-completely unexpected given that we have also required consistency
-with ACF measurements.
-
-The novelty in our approach is that we have a detailed estimate for 
+Observational evidence based on the ACF inferred from photometric
+measurements in the Extended Chandra Deep Field South has shown that
+the median dark matter masses of h los hosting LAEs is
+$\log_{10}M_{\rm  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding
+occupation fraction of $1-10\%$  \citep{Gawiser07}.  \cite{Ouchi2010}
+presents analysis of LAE observations in the redshift interval
+$3.1<z<7.0$ and at $z=3.1$ They quote an average mass for the host
+dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times 10^{10}$ \hMsun
+with a corresponding duty cycle of $0.008\pm 0.03$.
+
+Our results are in a general good agreement with those estimates for
+the host mass. This is not completely unexpected given that we have
+also required consistency with ACF measurements. These expectations
+are matched by the first family of models, also summarized in Table
+\ref{table:firstfamily}. These models, which favor only the very
+low occupations fractions, are also consistent in that regards with
+the observational expectations.
+
+The novelty in our results is that we have a detailed estimate for 
 host halo mass range together with the escape fraction. This allows us
-to demonstrate that the halo mass range could be very narrow $\Delta M <
-0.2$dex, something that cannot be inferred from ACF analysis alone.
-
-We also find that an ACF analysis on a single data-set is not enough to rule
+to demonstrate that the halo mass range can in some cases be narrow $\Delta M <
+0.3$dex, something that cannot be inferred from ACF analysis alone.
+Furthermore, In contrast to \citep{Gawiser07} and \citep{Ouchi2010} we
+find that an ACF analysis on a single data-set is not enough to rule
 out models with a high occupation fraction $f_{\rm occ}>0.3$, which
-represent half of our best models. These models cannot be
-considered unfavorable based on a clustering analysis only, it
-requires additional information from galaxy surveys, as we have
-presented in the previous section.
-
-\cite{Ouchi2010} presents an analysis of LAE observations in the
-redshift interval $3.1<z<7.0$. At $z=3.1$ They quote an average
-mass for the host dark matter halos of $M_{h}=2.9^{+24.0}_{-2.9}\times
-10^{10}$ \hMsun with a corresponding duty cycle of $0.008\pm
-0.03$.  This broadly matches the expectations from the first family of
-models, also summarized in Table \ref{table:firstfamily}. In
-particular it seems to favor only the very low occupations
-fractions.
-
-We conclude this section by noting that the uncertainties on
-the preferred masses in \citep{Gawiser07} and \cite{Ouchi2010} are
-found with in the intervals $M_{\rm min}$ and $M_{\rm max}$ of our
-models.
+represent half of our best models.
 
@@
 \caption{\label{table:firstfamily}List of parameters for the first
-  family of models. Narrow mass range $\Delta M\leq 1.0$dex and low
+  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
   occupation fraction $f_{\rm occ}\leq 0.3$.} 
@@
 \caption{\label{table:secondfamily}List of parameters for the second
-  family of models. Narrow mass range $\Delta M\leq 1.0$dex and high occupation fraction $f_{\rm occ}>0.3$.}
+  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and high occupation fraction $f_{\rm occ}>0.3$.}
 \end{table}
@@
 The abundance matching methods are based on observational results for
-Lyman Break Galaxies \citep{Behroozi2013a,Behroozi2013b}  (LBG).  In
+Lyman Break Galaxies (LBGs) \citep{Behroozi2013a,Behroozi2013b}.  In
 the case of \cite{Behroozi2013a} the minimum halo mass considered to
@@
 stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-their star formation rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$,
+their star formation rate is in the range $0.6\pm 0.2$ \Msun yr$^{-1}$,
 which nevertheless are close to the lower bound of values inferred for
@@
 than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
-abundance matching at $z=3$. This confirms once more the expectations
-that most of  LAEs are to be found in less massive halos LBG hosts.A
+abundance matching at $z=3$. Our results confirm the expectations
+that most of  LAEs are to be found in less massive halos LBG hosts. A
 detailed analysis of the spectral and photometric properties of LAEs
@@
 galaxies are not a dominant population, making our initial
-approximation a reasonable one. Therefore we think that it is not
-crucial to include the effect of satellites in the model.
+approximation a reasonable one. Therefore we conclude that including
+the effect of satellite galaxies won't change the main results
+reported in this \documentname.
 
 The second caveat are the precise values for the mass intervals. These
-numbers are defined from the halos defined in using the BDM halo
-finder with a density threshold of 200 times the critical
-density. Different halo finders and definitions for the detection
+values are defined from the halos defined in using the FOF halo
+finder. Different halo finders and definitions for the detection
 density threshold can yield different masses up to a factor. For
-instance a Friends-of-Friends algorithm with linking lenght $l=0.20$
-times the average interparticle distance finds halos on average $1.4$
-times more massive than BDM halos \citep{Bolshoi}. Therefore, the mass
-values for $M_{\rm min}$ and $M_{\rm max}$ should not be considered exact
-within less than $\sim 0.2$ dex.
+instance a Friends-of-Friends algorithm with linking length $l=0.20$
+times the average inter-particle distance finds halos on average $1.4$
+times less massive than halos defined  with an spherical overdensity
+algorithm halos \citep{Bolshoi}. Therefore, the mass values for
+$M_{\rm min}$ and $M_{\rm max}$ should not be considered exact within
+less than $\sim 0.2$ dex.
 
@@
 impose a tight constraint on the escape fraction. On the other hand
-the minium mass and maximum mass are tightly constrained as follows
+the minimum mass and maximum mass are tightly constrained as follows
 $M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
@@
 properties of dark matter halos hosting LAEs. At the same time,
-additional modeling for \ly radiation transfer, is needed to put a
+additional modeling for \ly radiation transfer , is needed to put a
 tighter constrain on the \ly escape fraction in high redshift
-galaxies.
+galaxies, also paying attention to newly framed physical phenomena, such as the
+stochasticity \citep{ForeroRomero2013} in the star formation process,
+which might play a role in inducing detection biases in high redshift LAEs.
 
@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
+  et~al.}{2013a}]{Behroozi2013b}
+{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013a, \apjl, 762, L31
+
+\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
+  et~al.}{2013b}]{Behroozi2013a}
+{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013b, \apj, 770, 57
+
+\bibitem[\protect\citeauthoryear{{Colberg}, {White}, {Yoshida}, {MacFarland},
+  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
+  {Thomas} \& {Virgo Consortium}}{{Colberg} et~al.}{2000}]{Colberg00}
+{Colberg} J.~M.,  {White} S.~D.~M.,  {Yoshida} N.,  {MacFarland} T.~J.,
+  {Jenkins} A.,  {Frenk} C.~S.,  {Pearce} F.~R.,  {Evrard} A.~E.,  {Couchman}
+  H.~M.~P.,  {Efstathiou} G.,  {Peacock} J.~A.,  {Thomas} P.~A.,    {Virgo
+  Consortium} 2000, \mnras, 319, 209
+
+\bibitem[\protect\citeauthoryear{{Dayal}, {Ferrara}, {Saro}, {Salvaterra},
+  {Borgani} \& {Tornatore}}{{Dayal} et~al.}{2009}]{Dayal2009}
+{Dayal} P.,  {Ferrara} A.,  {Saro} A.,  {Salvaterra} R.,  {Borgani} S.,
+  {Tornatore} L.,  2009, \mnras, 400, 2000
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Jeeson-Daniel}}{{Dijkstra} \&
+  {Jeeson-Daniel}}{2013}]{Dijkstra2013}
+{Dijkstra} M.,  {Jeeson-Daniel} A.,  2013, ArXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
+  {Kramer}}{2012}]{Dijkstra2012}
+{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Mesinger} \& {Wyithe}}{{Dijkstra}
+  et~al.}{2011}]{Dijkstra11}
+{Dijkstra} M.,  {Mesinger} A.,    {Wyithe} J.~S.~B.,  2011, \mnras, 414, 2139
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero} \& {Dijkstra}}{{Forero-Romero}
+  \& {Dijkstra}}{2013}]{ForeroRomero2013}
+{Forero-Romero} J.~E.,  {Dijkstra} M.,  2013, \mnras, 428, 2163
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero}
+  et~al.}{2011}]{ForeroRomero2011}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber} \&
+  {Prada}}{{Forero-Romero} et~al.}{2012}]{ForeroRomero2012}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,    {Prada} F.,  2012,
+  \mnras, 419, 952
+
+\bibitem[\protect\citeauthoryear{{Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
+  {Verhamme} \& {Hayes}}{{Garel} et~al.}{2012}]{Garel2012}
+{Garel} T.,  {Blaizot} J.,  {Guiderdoni} B.,  {Schaerer} D.,  {Verhamme} A.,
+  {Hayes} M.,  2012, \mnras, 422, 310
+
+\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
+  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio} \&
+  {Feldmeier}}{{Gawiser} et~al.}{2007}]{Gawiser2007}
+{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
+  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
+  G.~A.,  {Fazio} G.,    {Feldmeier} J.~J.,  2007, \apj, 671, 278
+
+\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
+  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio},
+  {Feldmeier}, {Huang}, {Infante}, {Lira} \& {Padilla}}{{Gawiser}
+  et~al.}{2007}]{Gawiser07}
+{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
+  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
+  G.~A.,  {Fazio} G.,  {Feldmeier} J.~J.,  {Huang} J.-s.,  {Infante} L.,
+  {Lira} P.,    {Padilla} N.,  2007, \apj, 671, 278
+
+\bibitem[\protect\citeauthoryear{{Guaita}, {Francke}, {Gawiser}, {Bauer},
+  {Hayes}, {{\"O}stlin} \& {Padilla}}{{Guaita} et~al.}{2013}]{Guaita2013}
+{Guaita} L.,  {Francke} H.,  {Gawiser} E.,  {Bauer} F.~E.,  {Hayes} M.,
+  {{\"O}stlin} G.,    {Padilla} N.,  2013, \aap, 551, A93
+
+\bibitem[\protect\citeauthoryear{{Hayashino}, {Matsuda}, {Tamura}, {Yamauchi},
+  {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi},
+  {Shimasaku}, {Shioya} \& {Taniguchi}}{{Hayashino}
+  et~al.}{2004}]{Hayashino2004}
+{Hayashino} T.,  {Matsuda} Y.,  {Tamura} H.,  {Yamauchi} R.,  {Yamada} T.,
+  {Ajiki} M.,  {Fujita} S.~S.,  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,
+  {Okamura} S.,  {Ouchi} M.,  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,
+  2004, \aj, 128, 2073
+
+\bibitem[\protect\citeauthoryear{{Hayes}, {{\"O}stlin}, {Schaerer},
+  {Mas-Hesse}, {Leitherer}, {Atek}, {Kunth}, {Verhamme}, {de Barros} \&
+  {Melinder}}{{Hayes} et~al.}{2010}]{Hayes2010}
+{Hayes} M.,  {{\"O}stlin} G.,  {Schaerer} D.,  {Mas-Hesse} J.~M.,  {Leitherer}
+  C.,  {Atek} H.,  {Kunth} D.,  {Verhamme} A.,  {de Barros} S.,    {Melinder}
+  J.,  2010, \nat, 464, 562
+
+\bibitem[\protect\citeauthoryear{{Jarosik}, {Bennett}, {Dunkley}, {Gold},
+  {Greason}, {Halpern}, {Hill}, {Hinshaw}, {Kogut}, {Komatsu}, {Larson} \&
+  {Limon}}{{Jarosik} et~al.}{2011}]{Jarosik2011}
+{Jarosik} N.,  {Bennett} C.~L.,  {Dunkley} J.,  {Gold} B.,  {Greason} M.~R.,
+  {Halpern} M.,  {Hill} R.~S.,  {Hinshaw} G.,  {Kogut} A.,  {Komatsu} E.,
+  {Larson} D.,    {Limon} M.,  2011, \apjs, 192, 14
+
+\bibitem[\protect\citeauthoryear{{Jose}, {Srianand} \& {Subramanian}}{{Jose}
+  et~al.}{2013}]{Jose2013b}
+{Jose} C.,  {Srianand} R.,    {Subramanian} K.,  2013, ArXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
+  {Primack}}{{Klypin} et~al.}{2011}]{Bolshoi}
+{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102
+
+\bibitem[\protect\citeauthoryear{{Koehler}, {Schuecker} \&
+  {Gebhardt}}{{Koehler} et~al.}{2007}]{Koehler2007}
+{Koehler} R.~S.,  {Schuecker} P.,    {Gebhardt} K.,  2007, \aap, 462, 7
+
+\bibitem[\protect\citeauthoryear{{Komatsu}, {Dunkley}, {Nolta}, {Bennett},
+  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Limon}, {Page}, {Spergel} \&
+  {Halpern}}{{Komatsu} et~al.}{2009}]{Komatsu2009}
+{Komatsu} E.,  {Dunkley} J.,  {Nolta} M.~R.,  {Bennett} C.~L.,  {Gold} B.,
+  {Hinshaw} G.,  {Jarosik} N.,  {Larson} D.,  {Limon} M.,  {Page} L.,
+  {Spergel} D.~N.,    {Halpern} M.,  2009, \apjs, 180, 330
+
+\bibitem[\protect\citeauthoryear{{Kudritzki}, {M{\'e}ndez}, {Feldmeier},
+  {Ciardullo}, {Jacoby}, {Freeman}, {Arnaboldi}, {Capaccioli}, {Gerhard} \&
+  {Ford}}{{Kudritzki} et~al.}{2000}]{Kudritzki2000}
+{Kudritzki} R.-P.,  {M{\'e}ndez} R.~H.,  {Feldmeier} J.~J.,  {Ciardullo} R.,
+  {Jacoby} G.~H.,  {Freeman} K.~C.,  {Arnaboldi} M.,  {Capaccioli} M.,
+  {Gerhard} O.,    {Ford} H.~C.,  2000, \apj, 536, 19
+
+\bibitem[\protect\citeauthoryear{{Landy} \& {Szalay}}{{Landy} \&
+  {Szalay}}{1993}]{Landy1993}
+{Landy} S.~D.,  {Szalay} A.~S.,  1993, \apj, 412, 64
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013}
+{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Razoumov} \&
+  {Sommer-Larsen}}{{Laursen} et~al.}{2009}]{Laursen2009}
+{Laursen} P.,  {Razoumov} A.~O.,    {Sommer-Larsen} J.,  2009, \apj, 696, 853
+
+\bibitem[\protect\citeauthoryear{{Laursen} \& {Sommer-Larsen}}{{Laursen} \&
+  {Sommer-Larsen}}{2007}]{Laursen2007}
+{Laursen} P.,  {Sommer-Larsen} J.,  2007, \apjl, 657, L69
+
+\bibitem[\protect\citeauthoryear{{Matsuda}, {Yamada}, {Hayashino}, {Tamura},
+  {Yamauchi}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi}, {Shimasaku},
+  {Shioya} \& {Taniguchi}}{{Matsuda} et~al.}{2005}]{Matsuda2005}
+{Matsuda} Y.,  {Yamada} T.,  {Hayashino} T.,  {Tamura} H.,  {Yamauchi} R.,
+  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,  {Okamura} S.,  {Ouchi} M.,
+  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,  2005, \apjl, 634, L125
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{Neufeld1991}
+{Neufeld} D.~A.,  1991, \apjl, 370, L85
+
+\bibitem[\protect\citeauthoryear{{Nilsson}, {M{\o}ller}, {M{\"o}ller}, {Fynbo},
+  {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen} \&
+  {Grove}}{{Nilsson} et~al.}{2007}]{Nilsson2007}
+{Nilsson} K.~K.,  {M{\o}ller} P.,  {M{\"o}ller} O.,  {Fynbo} J.~P.~U.,
+  {Micha{\l}owski} M.~J.,  {Watson} D.,  {Ledoux} C.,  {Rosati} P.,  {Pedersen}
+  K.,    {Grove} L.~F.,  2007, \aap, 471, 71
+
+\bibitem[\protect\citeauthoryear{{Nilsson}, {Tapken}, {M{\o}ller}, {Freudling},
+  {Fynbo}, {Meisenheimer}, {Laursen} \& {{\"O}stlin}}{{Nilsson}
+  et~al.}{2009}]{Nilsson2009}
+{Nilsson} K.~K.,  {Tapken} C.,  {M{\o}ller} P.,  {Freudling} W.,  {Fynbo}
+  J.~P.~U.,  {Meisenheimer} K.,  {Laursen} P.,    {{\"O}stlin} G.,  2009, \aap,
+  498, 13
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
+  et~al.}{2012}]{Orsi2012}
+{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87
+
+\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
+  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
+  {Okamura}, {Iye}, {Takata}, {Yoshida} \& {Yoshida}}{{Ouchi}
+  et~al.}{2008}]{Ouchi2008}
+{Ouchi} M.,  {Shimasaku} K.,  {Akiyama} M.,  {Simpson} C.,  {Saito} T.,  {Ueda}
+  Y.,  {Furusawa} H.,  {Sekiguchi} K.,  {Yamada} T.,  {Kodama} T.,  {Kashikawa}
+  N.,  {Okamura} S.,  {Iye} M.,  {Takata} T.,  {Yoshida} M.,    {Yoshida} M.,
+  2008, \apjs, 176, 301
+
+\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
+  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
+  {Okamura}, {Simpson} \& {Yoshida}}{{Ouchi} et~al.}{2010}]{Ouchi2010}
+{Ouchi} M.,  {Shimasaku} K.,  {Furusawa} H.,  {Saito} T.,  {Yoshida} M.,
+  {Akiyama} M.,  {Ono} Y.,  {Yamada} T.,  {Ota} K.,  {Kashikawa} N.,  {Iye} M.,
+   {Kodama} T.,  {Okamura} S.,  {Simpson} C.,    {Yoshida} M.,  2010, \apj,
+  723, 869
+
+\bibitem[\protect\citeauthoryear{{Peebles}}{{Peebles}}{1980}]{Peebles1980}
+{Peebles} P.~J.~E.,  1980, {The large-scale structure of the universe}
+
+\bibitem[\protect\citeauthoryear{{Pentericci}, {Grazian}, {Fontana},
+  {Castellano}, {Giallongo}, {Salimbeni} \& {Santini}}{{Pentericci}
+  et~al.}{2009}]{Pentericci2009}
+{Pentericci} L.,  {Grazian} A.,  {Fontana} A.,  {Castellano} M.,  {Giallongo}
+  E.,  {Salimbeni} S.,    {Santini} P.,  2009, \aap, 494, 553
+
+\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
+  Granger}{2007}]{IPython}
+P\'erez F.,  Granger B.~E.,  2007, {C}omput. {S}ci. {E}ng., 9, 21
+
+\bibitem[\protect\citeauthoryear{Riebe, Partl, Enke, Forero-Romero, Gottlöber,
+  Klypin, Lemson, Prada, Primack, Steinmetz \& Turchaninov}{Riebe
+  et~al.}{2013}]{MultiDark}
+Riebe K.,  Partl A.~M.,  Enke H.,  Forero-Romero J.,  Gottlöber S.,  Klypin
+  A.,  Lemson G.,  Prada F.,  Primack J.~R.,  Steinmetz M.,    Turchaninov V.,
+  2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[\protect\citeauthoryear{{Springel}, {White}, {Jenkins}, {Frenk},
+  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
+  {Thomas}, {Couchman}, {Evrard}, {Colberg} \& {Pearce}}{{Springel}
+  et~al.}{2005}]{SpringelNature05}
+{Springel} V.,  {White} S.~D.~M.,  {Jenkins} A.,  {Frenk} C.~S.,  {Yoshida} N.,
+   {Gao} L.,  {Navarro} J.,  {Thacker} R.,  {Croton} D.,  {Helly} J.,
+  {Peacock} J.~A.,  {Cole} S.,  {Thomas} P.,  {Couchman} H.,  {Evrard} A.,
+  {Colberg} J.,    {Pearce} F.,  2005, \nat, 435, 629
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
+  {Maselli}}{{Verhamme} et~al.}{2006}]{Verhamme2006}
+{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397
+
+\bibitem[\protect\citeauthoryear{{Walker-Soler}, {Gawiser}, {Bond}, {Padilla}
+  \& {Francke}}{{Walker-Soler} et~al.}{2012}]{Soler2012}
+{Walker-Soler} J.~P.,  {Gawiser} E.,  {Bond} N.~A.,  {Padilla} N.,    {Francke}
+  H.,  2012, \apj, 752, 160
+
+\bibitem[\protect\citeauthoryear{{Yajima}, {Choi} \& {Nagamine}}{{Yajima}
+  et~al.}{2012}]{Yajima2012}
+{Yajima} H.,  {Choi} J.-H.,    {Nagamine} K.,  2012, \mnras, 427, 2889
+
+\bibitem[\protect\citeauthoryear{{Yamada}, {Nakamura}, {Matsuda}, {Hayashino},
+  {Yamauchi}, {Morimoto}, {Kousai} \& {Umemura}}{{Yamada}
+  et~al.}{2012}]{Yamada2012}
+{Yamada} T.,  {Nakamura} Y.,  {Matsuda} Y.,  {Hayashino} T.,  {Yamauchi} R.,
+  {Morimoto} N.,  {Kousai} K.,    {Umemura} M.,  2012, \aj, 143, 79
+
+\bibitem[\protect\citeauthoryear{{Zheng}, {Cen}, {Trac} \&
+  {Miralda-Escud{\'e}}}{{Zheng} et~al.}{2010}]{Zheng2010}
+{Zheng} Z.,  {Cen} R.,  {Trac} H.,    {Miralda-Escud{\'e}} J.,  2010, \apj,
+  716, 574
+
+\end{thebibliography}
+
+%\bibliography{references}
 

### 2013-10-21 paper/ms.tex
some updates in the paper

@@
 \ly luminosities. We find that the clustering and number density information are
-insufficient to impose a tight constraint on the escape fraction. On
+insufficient to impose a tight constraint on the {\bf occupation} fraction. On
 the other hand the minimum mass and maximum mass are tightly
@@
 The second constraint is the angular correlation function
-(ACF). \cite{Yamada2012} does not report an ACF measurement. Instead
+(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement}. Instead
 we use the results by \cite{Hayashino2004} and
 \cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
-densest field of SSA22 while \cite{Ouchi2008} observed on a $\sim 0.5$
-deg$^2$ field.  There are some differences between these
-observations and those by \cite{Yamada2012}. The details in the color
-selection, corresponding limiting luminosities and EW thresholds are
-different in these references. Nevertheless we use the ACF from these
-observations as additional constraints in spite of the fact that the
-first selected models are based only on the surface density statistics by
-\cite{Yamada2012}.
+densest field of SSA22 while \cite{Ouchi2008} observed a 1 deg$^2$
+over the SXDS field, which is twice as large as the SXDS region
+observed by \cite{Yamada2012}.
+
+There are some differences between these observations and those by
+\cite{Yamada2012}. The details in the color selection, corresponding
+limiting luminosities and EW thresholds are different in these
+references. Nevertheless we use the ACF from these observations as
+additional constraints in spite of the fact that the first selected
+models are based only on the surface density statistics by \cite{Yamada2012}.
+
+{\bf The LAEs number density inferred by \cite{Hayashino2004} is
+  $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
+by \cite{Yamada2012}. In the case of \cite{Ouchi2008} the number
+density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
+inferred by \cite{Yamada2012} for a portion of the same region.}
 

### 2013-10-22 paper/ms.tex
new subsection on the SSA22 field

@@
 correlation function between mock and observed fields. We explicitly
-take into account the cosmic variance on the typical observed field size by
-constructing mock fields from a large cosmological N-body
+take into account the cosmic variance on the typical observed field
+size by constructing mock fields from a large cosmological N-body
 simulation matching the geometries of observed fields. To populate the
@@
 band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
-corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
-centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
-an observed equivalent width, in the observer frame, larger than $190$
+corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc
+comoving scale for the detection of the Lyman-$\alpha$ line centered
+at $z=3.09$. The authors reported a total  $2161$  LAEs with an
+observed equivalent width, in the observer frame, larger than $190$
 \AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
@@
 inferred by \cite{Yamada2012} for a portion of the same region.}
+
+\subsection{The adequacy of using SSA22 as an observational test}
+
+{\bf The field centered on SSA22 has been known to harbor a 
+  galaxy overdensity. Measurements of Lyman Break Galaxies show that
+  the densest sub-field presents an overdensity 6 times the one present in a
+  blank field \cite{XXX}. Using the data of \cite{Yamada2012}, we
+  compute that for LAEs the whole region is only 1.4 times more dense than
+  the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
+  in SSA22 is only 2 times denser than the average of the blank
+  fields.}
+
+{\bf This shows that the bias factor of LBGs is higher
+  than LAEs. In a LCDM cosmology this implies that LAEs are, on average,
+  hosted by halos less massive than those hosting LBGs. The
+  interpretation of how rare is this subfield in terms of the number
+  densities of dark matter halos has to assume a defined model for
+  galaxy formation[...]}
+
+{\bf Excluding the densest region in the SSA222, all the fields have a
+similar number densisty as the blank fields and cannot be considered
+as rare. Therefore we expect that a comparison between different
+distributions for the number densities will fail at reproducing the
+high density tail of the densest field in SSA22.}
 

### 2013-10-23 paper/ms.tex
updated discussion in the new section and new panel

@@
 similar number densisty as the blank fields and cannot be considered
-as rare. Therefore we expect that a comparison between different
-distributions for the number densities will fail at reproducing the
-high density tail of the densest field in SSA22.}
+as rare. The left panel in Figure \ref{fig:halos} shows the integrated
+distritbution of LAEs number density in all the fields reported in
+\cite{Yamada2012}.
+
+From this figure it is clear that the highest density
+sub-fields is the only outlier in the distribution. Therefore, using
+as a benchmark the number density distribution that includes the
+sub-fields in the SSA22 region does not impose a strong bias to select
+very rare regions in a cosmological simulation. However, on has to
+keep in mind that only very rarely the full number density distribution from a
+simulation will include a very dense field as an outlier. We will not
+require the presence of such field to judge a mock distribution as
+successful. [..]}
 
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
+\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
+\caption{ \label{fig:halos} Left panel. Distribution of LAE number
+  densities in all the fields observed by \citet{Yamada2012}. The
+  point with the highest surface density corresponds to the densest
+  sub-field in the SSA22 field. Right panel. Surface density of dark 
+  matter halos as a function of a minimum halo mass to count the
+  total number of elements in a volume. Each line represents one of the
+  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
+  in the Bolshoi simulation. The horizontal gray band represents the
+  range of surface densities observed for LAEs at $z=3.1$ as reported
+  by \citep{Yamada2012}.}
+\end{center} 
+\end{figure*}
+
 We make a thorough exploration of the parameter space for the models
@@
 observational or statistical evidence.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=1.10\linewidth,angle=0]{Fig1.pdf}
-\caption{ \label{fig:halos} Surface density of dark
-  matter halos as a function of a minimum halo mass to count the
-  total number of elements in a volume. Each line represents one of the
-  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
-  in the Bolshoi simulation. The horizontal gray band represents the
-  range of surface densities observed for LAEs at $z=3.1$ as reported
-  by \citep{Yamada2012}.}
-\end{center} 
-\end{figure}
 

### 2013-10-26 paper/ms.tex
minor change
explanation for using hayashinos ACF

@@
 band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
-corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc
-comoving scale for the detection of the Lyman-$\alpha$ line centered
-at $z=3.09$. The authors reported a total  $2161$  LAEs with an
-observed equivalent width, in the observer frame, larger than $190$
+corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
+centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
+an observed equivalent width, in the observer frame, larger than $190$
 \AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
@@
 
-The survey covered four independent fields. The first is the SSA22
+The survey covered four independent fields:
+
+\begin{enumerate}
+\item The first is the SSA22
 field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
 field has been known to harbor a region with a large density excess of
-galaxies. The second observed region is composed by the fields Subaru/{\it
+galaxies. {\bf It is important to note  that the first sub-field of this sample  is
+exactly the same that are reported by \cite{Hayashino2004} } as it is reported 
+by as by \cite{Yamada2012}  in section $2.1$.
+
+\item The second observed region is composed by the fields Subaru/{\it
   XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
-total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields). The third and
-fourth fields are the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
-$196$ LAEs (1 sub-field), and the field around the Great Observatory
+total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).
+
+\item The third  field si the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
+$196$ LAEs (1 sub-field), and
+
+\item The fourth one is the field around the Great Observatory
 Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
 sub-field).  
+\end{enumerate}
 
@@
 
-The second constraint is the angular correlation function
-(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement}. Instead
-we use the results by \cite{Hayashino2004} and
-\cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
-densest field of SSA22 while \cite{Ouchi2008} observed a 1 deg$^2$
-over the SXDS field, which is twice as large as the SXDS region
-observed by \cite{Yamada2012}.
-
-There are some differences between these observations and those by
+{\bf The second constraint is the angular correlation function
+(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for the entire field}. Instead
+we use the results by \cite{Hayashino2004} who has reported the ACF for the
+first and at the same time the densest sub-field of  SSSA22 as we have mention 
+before.
+
+In adition to Hayashino's ACF we use as a matter of comparison the
+ACF reported by  \cite{Ouchi2008}. This ACF is computer over
+an observed field of 1 deg$^2$ over the SXDS field, which is twice
+ as large as the SXDS region observed by \cite{Yamada2012}.
+
+There are some differences between \cite{Ouchi2008} observations and those by
 \cite{Yamada2012}. The details in the color selection, corresponding
 limiting luminosities and EW thresholds are different in these
-references. Nevertheless we use the ACF from these observations as
-additional constraints in spite of the fact that the first selected
-models are based only on the surface density statistics by \cite{Yamada2012}.
-
-{\bf The LAEs number density inferred by \cite{Hayashino2004} is
-  $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
-by \cite{Yamada2012}. In the case of \cite{Ouchi2008} the number
+references. Nevertheless we use the ACF from this particular to 
+get a sense of a mean ACF but do not use it to constrain our parameter space. }
+
+%{\bf The LAEs number density inferred by \cite{Hayashino2004} is
+ % $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
+%by \cite{Yamada2012}. 
+In the case of \cite{Ouchi2008} the number
 density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
@@
 require the presence of such field to judge a mock distribution as
-successful. [..]}
+successful. [...]}
 

### 2013-10-26 paper/ms.tex
Discusion on the Walker-Soler paper in the introduction section

@@
 
+{\bf \cite{Soler2012} has derived the median mass of $z=0$ the $z=3.1$ LAE 
+descendat.  In order to construct their  LAE mock catalogs 
+they impose their model to reproduced, whitin the observational errors,
+ the number density  as well as  the minimal and median mass reported 
+ by \cite{Gawiser07} that has been derived from observations
+ over one single field. }
+
 Recently \cite{Yamada2012} observed a wide area a bit more than ten
@@
 mock catalogs are constructed  we proceed with a direct comparison
-against the statistics derived from observations. This allows us 
+against the statistics on the number density distribution derived from
+ the observations over the 12 fields of \cite{Yamada2012}. This allows us 
 to find the preferred mass range of DM halos hosting these galaxies

### 2013-11-06 paper/ms.tex
new updates in reply to the referee

@@
 {\bf The second constraint is the angular correlation function
-(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for the entire field}. Instead
-we use the results by \cite{Hayashino2004} who has reported the ACF for the
-first and at the same time the densest sub-field of  SSSA22 as we have mention 
-before.
+(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for
+    the entire field. Instead we use the results by
+  \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
+  including its densest subfield.}
 
@@
 %by \cite{Yamada2012}.
-In the case of \cite{Ouchi2008} the number
+
+{\bf In the case of \cite{Ouchi2008} the number
 density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
@@
 
-\subsection{The adequacy of using SSA22 as an observational test}
+\subsection{The adequacy of including SSA22 as an observational benchmark}
 
@@
   the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
-  in SSA22 is only 2 times denser than the average of the blank
+  in SSA22 is 2 times denser than the average of the blank
   fields.}
 
-{\bf This shows that the bias factor of LBGs is higher
-  than LAEs. In a LCDM cosmology this implies that LAEs are, on average,
-  hosted by halos less massive than those hosting LBGs. The
-  interpretation of how rare is this subfield in terms of the number
-  densities of dark matter halos has to assume a defined model for
-  galaxy formation[...]}
-
-{\bf Excluding the densest region in the SSA222, all the fields have a
-similar number densisty as the blank fields and cannot be considered
+{\bf Excluding the densest region in the SSA22, all the fields have a
+similar number density as the blank fields and cannot be considered
 as rare. The left panel in Figure \ref{fig:halos} shows the integrated
-distritbution of LAEs number density in all the fields reported in
-\cite{Yamada2012}.
-
-From this figure it is clear that the highest density
-sub-fields is the only outlier in the distribution. Therefore, using
+distribution of LAEs number density in all the fields reported in
+\cite{Yamada2012}. It is evident that there is only one sub-field that
+stands out as an outlier in the distribution (it corresponds to the
+densest field in SSA22), the central message of this distribution is
+that all the other fields form a continous distribution in number density.}
+
+{\bf Therefore, using
 as a benchmark the number density distribution that includes the
@@
 require the presence of such field to judge a mock distribution as
-successful. [...]}
+successful. In terms of the ACF the results that include the densest
+field in SSA22 \citep{Hayashino2004} are consistent, within the
+uncertainties, with the results of other fields \citep{Ouchi2008}.}
+
+{\bf Finally, two very different number densities in LBGs versus LAEs evidences
+  that the two populations have different biases. In a $\Lambda$ CDM
+  cosmology this implies that LAEs are, on average, hosted by halos
+  less massive than those hosting LBGs. The interpretation of how rare
+  is this subfield in terms of the number densities of dark matter
+  halos has to assume a defined model for galaxy formation;
+  i.e. defining the link between halo mass, star formation rate, \ly
+  luminosity and \ly escape fraction.}
+
+{\bf The purpose of our work is to avoid any loose of generality by
+  assuming a defined halo-LAE connection and instead explore all the
+  possible halo populations to host LAEs.}
 

### 2013-11-08 paper/ms.tex
minor updates

@@
 field has been known to harbor a region with a large density excess of
-galaxies. {\bf It is important to note  that the first sub-field of this sample  is
-exactly the same that are reported by \cite{Hayashino2004} } as it is reported 
-by as by \cite{Yamada2012}  in section $2.1$.
+galaxies. {\bf The first sub-field of is taken around the same region
+  observed in \cite{Hayashino2004} } as it is reported  by as by
+\cite{Yamada2012} in section $2.1$.
 
@@
 
-{\bf The second constraint is the angular correlation function
-(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement for
+{\bf A secondary benchmark is the angular correlation function
+(ACF). \cite{Yamada2012} does not report an ACF measurement for
   the entire field. Instead we use the results by
   \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
-  including its densest subfield.}
-
-In adition to Hayashino's ACF we use as a matter of comparison the
-ACF reported by  \cite{Ouchi2008}. This ACF is computer over
-an observed field of 1 deg$^2$ over the SXDS field, which is twice
- as large as the SXDS region observed by \cite{Yamada2012}.
-
-There are some differences between \cite{Ouchi2008} observations and those by
-\cite{Yamada2012}. The details in the color selection, corresponding
-limiting luminosities and EW thresholds are different in these
-references. Nevertheless we use the ACF from this particular to 
-get a sense of a mean ACF but do not use it to constrain our parameter space. }
-
-%{\bf The LAEs number density inferred by \cite{Hayashino2004} is
- % $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
-%by \cite{Yamada2012}.
-
-{\bf In the case of \cite{Ouchi2008} the number
-density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
-inferred by \cite{Yamada2012} for a portion of the same region.}
+  including its densest subfield. In adition to Hayashino's ACF we use
+  as a matter of comparison the ACF reported by
+  \cite{Ouchi2008}. This ACF is computer over an observed field of 1
+  deg$^2$ over the SXDS field.}
+
+{\bf There are some differences between \cite{Ouchi2008} observations
+  and those by \cite{Yamada2012}. The details in the color selection,
+  corresponding limiting luminosities and EW thresholds are different
+  in these references. The average LAEs number density inferred by
+  \cite{Hayashino2004} is   $0.37$ arcmin$^{-2}$, which is $15\%$
+  lower than the new measurement by \cite{Yamada2012}. In the case of
+  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
+  is $\sim 50\%$ higher than the value inferred by \cite{Yamada2012}
+  for a portion of the same region.}
+
+{\bf In spite of being different fields, we find that the parameters
+  describing this
+
+the parameters in their
+  correlation function are consistent with each other Nevertheless we use the ACF from this
+  particular to  get a sense of a mean ACF.
 
@@
 
-{\bf The field centered on SSA22 has been known to harbor a 
-  galaxy overdensity. Measurements of Lyman Break Galaxies show that
-  the densest sub-field presents an overdensity 6 times the one present in a
-  blank field \cite{XXX}. Using the data of \cite{Yamada2012}, we
-  compute that for LAEs the whole region is only 1.4 times more dense than
-  the blank fields of SXDS, SDF and GOODS-N. The densest sub-field
-  in SSA22 is 2 times denser than the average of the blank
-  fields.}
-
-{\bf Excluding the densest region in the SSA22, all the fields have a
-similar number density as the blank fields and cannot be considered
-as rare. The left panel in Figure \ref{fig:halos} shows the integrated
-distribution of LAEs number density in all the fields reported in
+{\bf The field SSA22 has been known to harbor a significant
+  galaxy overdensity. \cite{Yamada2012} estimates that the densest
+  subfield is likely to be a rare density peak with $3-4\sigma$
+  significance on the scale of $\sim 60$\hMpc.}
+
+{\bf Excluding that high density sub-field in SSA22, all the fields
+  are average with a similar number density as the blank fields
+  rare. The left panel in Figure \ref{fig:halos} shows the integrated distribution of LAEs number density in all the fields reported in
   \cite{Yamada2012}. It is evident that there is only one sub-field that
   stands out as an outlier in the distribution (it corresponds to the
-densest field in SSA22), the central message of this distribution is
-that all the other fields form a continous distribution in number density.}
-
-{\bf Therefore, using
-as a benchmark the number density distribution that includes the
-sub-fields in the SSA22 region does not impose a strong bias to select
-very rare regions in a cosmological simulation. However, on has to
-keep in mind that only very rarely the full number density distribution from a
-simulation will include a very dense field as an outlier. We will not
+  densest field in SSA22). All the other fields form a continous
+  distribution in number density.}
+
+{\bf Therefore, using the whole SSA22 region as a benchmark in the
+  number density distribution does not impose any bias. However, on
+  has to  keep in mind that is not plausible that the full number
+  density distribution from a simulation will include a very dense
+  field. The statistical test we perform to compare mock distributions against
+  observations does not require such a perfect match.
+
+We will not
   require the presence of such field to judge a mock distribution as
@@
 for all the models having the $15$ mock surveys consistent with
-observations . The ACF is computed using 
-the Landy \&  Szalay estimator \citep{Landy1993}  on two different 
-fields in the mock survey. The first field is the densest to be compared
-against the results of \cite{Hayashino2004}. The second field
-has an average number density and is compared against \cite{Ouchi2010}.
+observations .
+
+{\bf The ACF is computed using  the Landy \&  Szalay estimator
+  \citep{Landy1993}  on two different  fields in the mock survey. The
+  first field is the densest to be compared against the results of
+  \cite{Hayashino2004}. The second field has an average number density and is compared against \cite{Ouchi2010}.}
 

### 2013-11-13 paper/ms.tex
edits in the abstract and introduction

@@
 one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
-build such a model is to avoid the large uncertainties in the estimation of
-\ly luminosities. We find that the clustering and number density information are
-insufficient to impose a tight constraint on the {\bf occupation} fraction. On
-the other hand the minimum mass and maximum mass are tightly
-constrained to be $M_{\rm max}<10^{12}$\hMsun and
-$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
-that all models have a narrow mass range $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
-with the vast majority in the range $\Delta M<0.5$ dex. Already
-published constraints on the mass range and occupation fraction are a sub-set of
-the models we report in this \documentname. Our results present an
-inconclusive response as to which is the occupation fraction for LAEs
-at $z=3.1$. A precise answer requires robust physical models for the
-connection between dark matter, star formation and the escape of \ly
-radiation. That kind of modelling should also be able to provide a
+build such a model is to avoid the large uncertainties in the
+estimation of \ly luminosities. Our main result is that the clustering
+and number density information are insufficient to impose a tight
+constraint on the {\bf occupation} fraction. On the other hand the
+minimum mass and maximum mass can be tightly constrained to the range
+$M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
+10^{11.5}\hMsun$.  We also find that all models have a narrow mass
+range $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$
+smaller than $1.0$ dex, with the vast majority in the range $\Delta
+M<0.5$ dex. Already published constraints on the mass range and
+occupation fraction are a sub-set of the models we report in this
+\documentname. Our results present an inconclusive response as to
+which is the occupation fraction for LAEs at $z=3.1$. A precise answer
+requires observations on larger fields and robust physical models for
+the connection between dark matter, star formation and the escape of
+\ly radiation. That kind of modelling should also be able to provide a
 plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
@@
 
-Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade
-a  central topic in studies of structure formation in the Universe. They 
-are helpful in a diverse range of fields. LAEs can be used as probes
-of reionization \citep{Dijkstra11}, tracers of large scale structure
-\citep{Koehler2007},  signposts for low metallicity stellar
-populations, markers of the galaxy formation process at high redshift
-\citep{Dayal2009,ForeroRomero2012} and tracers of active star formation
-\citep{Guaita2013}
-
-At the same time, theoretical and observational developments have
-contributed to the emergence of a paradigm to describe structure
-formation in a cosmological context. In this context it is considered
-that the dominant matter content of the Universe is to be found in dark
-matter (DM), whereby each galaxy is hosted by larger dark matter structure
-known as a halo. \citep{Peebles1980,SpringelNature05}.
-
-Most models of galaxy formation find that halo mass can be
-used to predict galaxy properties such as the stellar mass and
-star formation rate \citep{Behroozi2013a}. Processes that regulate the
-star formation cycle are also though to be strongly dependent on its
-halo mass.  For these reasons, finding the typical dark matter halo mass
-hosting LAEs represents a significant step forward to understand the
+Lyman-$\alpha$ emitting galaxies (LAEs) are helpful in a diverse range
+of subjects in extragalactic astronomy. LAEs can be
+used as probes of reionization \citep{Dijkstra11}, tracers of large
+scale structure \citep{Koehler2007},  signposts for low metallicity
+stellar populations, markers of the galaxy formation process at high
+redshift \citep{Dayal2009,ForeroRomero2012} and tracers of active star
+formation \citep{Guaita2013}.
+
+Capitalizing LAEs observations requires an understanding of
+their place in the context of a given structure formarion model in a
+cosmological context. Under the current paradigm the dominant matter
+content of the Universe is to be found in dark matter (DM) and each
+galaxy is thought to be hosted by larger dark matter structure known
+as a halo. \citep{Peebles1980,SpringelNature05}.
+
+Galaxy formation models find that halo mass predicts with high
+accuracy galaxy properties such as stellar mass and star formation
+rate \citep{Behroozi2013a}. This suggests that the
+physical processes that regulate the star formation cycle are 
+dependent on halo mass.  For that reason, finding the typical dark
+matter halo mass hosting LAEs represents an advance to understand the
 nature of this galaxy population in the context of Lambda Cold Dark
@@
 
-Some theoretical approaches to this problem have been based on
-ab-initio approach. Starting from the DM halo population, the
-corresponding intrinsic star formation properties are inferred
-together with other statistics such as the luminosity function, the
-correlation function and the equivalent width distributions. Such
-modelling has been implemented from analytic considerations,
-semi-analytic models \citep{Garel2012, Orsi2012}and  full N-body
+Some theoretical attempts to solve this problem using an  ab-initio
+approach. They start from the DM halo population to infer the
+intrinsic star formation rates and \ly a luminosities. From these
+values they estimate the amount of \ly photons that
+escape each galaxy and compute the observed luminosity for each
+galaxy. These models can predict different observables including: the
+luminosity function, correlation function and the equivalent width
+distributions. Such modelling has been implemented in semi-analytic
+models \citep{Garel2012,   Orsi2012, Solre2012} and  full N-body
 hydrodynamical simulations \citep{Laursen2007, Dayal2009,
-  ForeroRomero2011, Yajima2012, Soler2012}.
-
-In addition to the uncertainties in the astrophysical processes
-describing star formation in galactic populations,the calculation
-of the fraction of \ly photons that escape the galaxy to the observer
-is another debated step. Given the resonant nature of the \ly line,
-the radiative transfer of \ly is sensitive to the density,
-temperature, topology and kinematics of the neutral Hydrogen in the
-interstellar medium
-(ISM). This problem can be tackled with Monte Carlo simulations for the
-radiative transfer, however the complexity of the relevant physical
-processes makes it difficult to achieve a robust consensus on what is
-the theoretical expected value for the \ly escape fraction
-at high redshift
+  ForeroRomero2011, Yajima2012}.
+
+However, there are many uncertain steps in these calculations. The
+usual ones are the astrophysical processes describing star formation in galactic
+populations. But the dominant uncertainty is estimating the
+fraction of \ly photons that escape the galaxy, a number known as the escape
+fraction. Given the resonant nature of the \ly line, the escape
+fraction is sensitive to  the density, temperature, topology and
+kinematics of the neutral Hydrogen in the interstellar medium
+(ISM), besides the amount of dust that absorb the \ly photons. The
+complex radiative transfer of \ly photons in the ISM requires Monte
+Carlo simulations to be solved. Until now it has been dificult to
+achieve a consensus on the expected value for the \ly escape fraction
+in high redshift galaxies
 \citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
@@
   for a portion of the same region.}
-
-{\bf In spite of being different fields, we find that the parameters
-  describing this
-
-the parameters in their
-  correlation function are consistent with each other Nevertheless we use the ACF from this
-  particular to  get a sense of a mean ACF.
 

### 2013-11-13 paper/ms.tex
introduction rewritten

@@
 distributions. Such modelling has been implemented in semi-analytic
-models \citep{Garel2012,   Orsi2012, Solre2012} and  full N-body
+models \citep{Garel2012,Orsi2012, Solre2012} and  full N-body
 hydrodynamical simulations \citep{Laursen2007, Dayal2009,
@@
 
-Another approach to infer the typical DM halo mass of halos hosting
-LAEs is based on the clustering information. This uses the fact that in cold
-dark matter cosmologies the spatial clustering of galaxies on large
+A different approach to infer the typical mass of halos hosting
+LAEs is based on clustering information. This method uses the fact
+that in CDM cosmologies the spatial clustering of galaxies on large
 scales is entirely dictated by the halo distribution
@@
 fraction of the putative halos hosting these galaxies
-\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In this
-studies the observations were done on single fields of $\sim 1$
-deg$^{2}$ and the conclusions derived on the halo host mass from
-clustering information do not delve to deeply into the impact of
-cosmic variance.
-
-{\bf \cite{Soler2012} has derived the median mass of $z=0$ the $z=3.1$ LAE 
-descendat.  In order to construct their  LAE mock catalogs 
-they impose their model to reproduced, whitin the observational errors,
- the number density  as well as  the minimal and median mass reported 
- by \cite{Gawiser07} that has been derived from observations
- over one single field. }
-
-Recently \cite{Yamada2012} observed a wide area a bit more than ten
-times the sky area covered so far by individual campaigns. The
-observations were done with the same instrument and same criteria to
-reduce the observational data and produce LAE catalogs. This large
-data-set allows us to make the first study on the expected cosmic
-variance effects in LAEs at $z=3.1$ and its impact on the
-determination of the halo mass and occupation fraction.
-
-In this \documentname we implement a method to populate the DM halos
-in cosmological simulations with LAEs that bypasses all the
-uncertainty involved in the estimation of star formation rates and \ly escape
-fraction. The model only considers whether a DM can host a
-detectable LAE or not without predicting a \ly  luminosity. Once the
-mock catalogs are constructed  we proceed with a direct comparison
-against the statistics on the number density distribution derived from
- the observations over the 12 fields of \cite{Yamada2012}. This allows us 
-to find the preferred mass range of DM halos hosting these galaxies
-and its occupation fraction.
+\citep{Hayashino2004,Gawiser07,Nilsson2007,Ouchi2010}. In these
+studies the observations are done on fields of $\sim 1$ deg$^{2}$ and
+the conclusions derived on the halo host mass do not delve too deeply
+into the possible impact of cosmic variance.
+
+Recently \cite{Yamada2012} observed a wide area of $2.4$ deg$^{2}$
+under homogeneous instrumental and data reduction conditions. This data
+set is constructed from 12 different sub-fields. This large and
+homogeneous data-set allows us to use clustering statistics and cosmic
+variance to constraint the mass and occupation fraction of halos hosting
+LAEs.
+
+Our method first populates DM halos in cosmological simulations with
+LAEs. We only consider whether a DM can host a detectable LAE or not
+without predicting a \ly  luminosity. This is constructed to bypass
+all the physical uncertainties involved in the estimation of observed
+\ly luminosities.  Once we have the mock LAE catalogs, we compare them
+against the statistics on the number density distribution derived from the
+observations over the 12 fields of \cite{Yamada2012}. Additionally, we
+use measurements of the angular correlation function to improve these
+constraints. This method allows us to find the preferred mass range of
+DM halos hosting these galaxies and its occupation fraction.
 
 This \documentname is structured as follows. In the next section we present
-the simulation and model used to produce the mock catalogs and the criteria
-we use to compare them against observations. In \S \ref{sec:results} we
-present the main results for the halo mass and occupation fraction. We
-continue with a discussion of these results under the light of other
-observational and theoretical results. Finally, we present our
-conclusions in \S \ref{sec:conclusions}.
+the simulation and the model used to produce the mock catalogs. We
+also list the criteria used to compare the mocks against
+observations. In \S \ref{sec:results} we present the main results for
+the halo mass and occupation fraction. We continue with a discussion
+of these results under the light of other observational and
+theoretical results. Finally, we present our conclusions in \S
+\ref{sec:conclusions}.
 

### 2013-11-13 paper/ms.tex
introduction rewritten

@@
 Galaxy formation models find that halo mass predicts with high
-accuracy galaxy properties such as stellar mass and star formation
+accuracy galactic properties such as stellar mass and star formation
 rate \citep{Behroozi2013a}. This suggests that the

### 2013-11-13 paper/ms.tex
new methodology section

@@
 distributions. Such modelling has been implemented in semi-analytic
-models \citep{Garel2012,Orsi2012, Solre2012} and  full N-body
+models \citep{Garel2012,Orsi2012,Soler2012} and  full N-body
 hydrodynamical simulations \citep{Laursen2007, Dayal2009,
@@
 
-However, there are many uncertain steps in these calculations. The
-usual ones are the astrophysical processes describing star formation in galactic
-populations. But the dominant uncertainty is estimating the
-fraction of \ly photons that escape the galaxy, a number known as the escape
-fraction. Given the resonant nature of the \ly line, the escape
-fraction is sensitive to  the density, temperature, topology and
+These calculations involve many uncertain steps, such as the treatment
+of astrophysical processes describing star formation. However, in the
+context of LAEs, the dominant uncertainty is the estimation of the
+escape fraction, that is the fraction of \ly photons that escape the
+galaxy to the observer. Given the resonant nature of the \ly line, the escape
+fraction is sensitive to  the dust contents, density, temperature, topology and
 kinematics of the neutral Hydrogen in the interstellar medium
-(ISM), besides the amount of dust that absorb the \ly photons. The
-complex radiative transfer of \ly photons in the ISM requires Monte
-Carlo simulations to be solved. Until now it has been dificult to
-achieve a consensus on the expected value for the \ly escape fraction
-in high redshift galaxies
+(ISM). Solving the radiative transfer of \ly photons in the ISM requires Monte
+Carlo simulations. The process of finding a consensus on the expected
+value for the \ly escape fraction in high redshift galaxies is still
+matter of ongoing research
 \citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
@@
 A different approach to infer the typical mass of halos hosting
-LAEs is based on clustering information. This method uses the fact
+LAEs is based on the spatial clustering information. This approach uses the fact
 that in CDM cosmologies the spatial clustering of galaxies on large
@@
 under homogeneous instrumental and data reduction conditions. This data
-set is constructed from 12 different sub-fields. This large and
-homogeneous data-set allows us to use clustering statistics and cosmic
-variance to constraint the mass and occupation fraction of halos hosting
-LAEs.
+set is constructed from 12 different sub-fields that allows us to use
+clustering statistics and cosmic variance to constraint the mass and
+occupation fraction of halos hosting LAEs.
 
@@
 LAEs. We only consider whether a DM can host a detectable LAE or not
-without predicting a \ly  luminosity. This is constructed to bypass
-all the physical uncertainties involved in the estimation of observed
-\ly luminosities.  Once we have the mock LAE catalogs, we compare them
-against the statistics on the number density distribution derived from the
-observations over the 12 fields of \cite{Yamada2012}. Additionally, we
-use measurements of the angular correlation function to improve these
-constraints. This method allows us to find the preferred mass range of
-DM halos hosting these galaxies and its occupation fraction.
+without predicting a \ly  luminosity. This bypasses all the physical
+uncertainties involved in the estimation of observed \ly luminosities.
+Once we have the mock LAE catalogs, we compare them against
+observations in terms of the  statistics on the number density
+distribution derived from the observations over the 12 fields of
+\cite{Yamada2012}. We also use measurements of the angular
+correlation function to improve these constraints. This method allows
+us to constraint the preferred mass range and occupation fraction of DM
+halos hosting LAEs.
 
@@
 comparison: (i) the distribution of the surface number density
-across fields and (ii) the angular correlation function measured in
-some fields.
+across fields and (ii) the angular correlation function.
 
 In the next subsections we describe in detail the four key
-elements of this work-flow. First, we present the observations we take
-as a benchmark. Second, we describe the main characteristics of the
-N-body simulation and the halo catalogs we use. Third, we recount the
-important parameters of the simplified model that we use to populate
-the halo catalogs with LAEs. Finally we describe some of the
-statistical tests we adopt to compare observations and mocks.
+elements int our work-flow. First we present (in two sub-sections) the
+observations we take as a benchmark. Second, we describe the main
+characteristics of the N-body simulation and the halo catalogs we
+use. Third, we recount the important parameters of the simplified
+model that we use to populate the halo catalogs with LAEs. Finally, we
+describe some of the statistical tests we adopt to compare
+observations and mocks .
 
 \subsection{Observational constraints}
-
-The first observational constraint we use in this paper is the LAE number
-density information at $z=3.1$ obtained by the panoramic narrow-band
-survey presented by \cite{Yamada2012} from a survey
-conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
-which has a field of view covering $34\times 27$ arc-min, corresponding to a
-comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
-band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
-corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
-centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
-an observed equivalent width, in the observer frame, larger than $190$
-\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
-sub-fields,  this corresponds to average surface number density of
-$0.20\pm 0.01$ arcmin$^{-2}$.
-
-The survey covered four independent fields:
-
-\begin{enumerate}
-\item The first is the SSA22
-field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
-field has been known to harbor a region with a large density excess of
-galaxies. {\bf The first sub-field of is taken around the same region
-  observed in \cite{Hayashino2004} } as it is reported  by as by
-\cite{Yamada2012} in section $2.1$.
-
-\item The second observed region is composed by the fields Subaru/{\it
-  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
-total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).
-
-\item The third  field si the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
-$196$ LAEs (1 sub-field), and
-
-\item The fourth one is the field around the Great Observatory
-Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
-sub-field).  
-\end{enumerate}
-
-There is abundant observational work done on LAEs at redshift $z=3.1$
-\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
-However, we decide to focus on the data from \cite{Yamada2012} because
-it has the largest covered area with homogeneous instrumentation
-conditions (telescope, narrow band filter), data reduction pipeline
-and conditions to construct the LAE catalog. This ensures that the
-number density variations among fields are \emph{not} due to different
-observational conditions or criteria to construct the catalogs.
-
-{\bf A secondary benchmark is the angular correlation function
-(ACF). \cite{Yamada2012} does not report an ACF measurement for
-  the entire field. Instead we use the results by
-  \cite{Hayashino2004} who has reported the ACF in the SSA22 region,
-  including its densest subfield. In adition to Hayashino's ACF we use
-  as a matter of comparison the ACF reported by
-  \cite{Ouchi2008}. This ACF is computer over an observed field of 1
-  deg$^2$ over the SXDS field.}
-
-{\bf There are some differences between \cite{Ouchi2008} observations
-  and those by \cite{Yamada2012}. The details in the color selection,
-  corresponding limiting luminosities and EW thresholds are different
-  in these references. The average LAEs number density inferred by
-  \cite{Hayashino2004} is   $0.37$ arcmin$^{-2}$, which is $15\%$
-  lower than the new measurement by \cite{Yamada2012}. In the case of
-  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
-  is $\sim 50\%$ higher than the value inferred by \cite{Yamada2012}
-  for a portion of the same region.}
-
-\subsection{The adequacy of including SSA22 as an observational benchmark}
-
-{\bf The field SSA22 has been known to harbor a significant
-  galaxy overdensity. \cite{Yamada2012} estimates that the densest
-  subfield is likely to be a rare density peak with $3-4\sigma$
-  significance on the scale of $\sim 60$\hMpc.}
-
-{\bf Excluding that high density sub-field in SSA22, all the fields
-  are average with a similar number density as the blank fields
-  rare. The left panel in Figure \ref{fig:halos} shows the integrated distribution of LAEs number density in all the fields reported in
-  \cite{Yamada2012}. It is evident that there is only one sub-field that
-  stands out as an outlier in the distribution (it corresponds to the
-  densest field in SSA22). All the other fields form a continous
-  distribution in number density.}
-
-{\bf Therefore, using the whole SSA22 region as a benchmark in the
-  number density distribution does not impose any bias. However, on
-  has to  keep in mind that is not plausible that the full number
-  density distribution from a simulation will include a very dense
-  field. The statistical test we perform to compare mock distributions against
-  observations does not require such a perfect match.
-
-We will not
-  require the presence of such field to judge a mock distribution as
-  successful. In terms of the ACF the results that include the densest
-  field in SSA22 \citep{Hayashino2004} are consistent, within the
-  uncertainties, with the results of other fields \citep{Ouchi2008}.}
-
-{\bf Finally, two very different number densities in LBGs versus LAEs evidences
-  that the two populations have different biases. In a $\Lambda$ CDM
-  cosmology this implies that LAEs are, on average, hosted by halos
-  less massive than those hosting LBGs. The interpretation of how rare
-  is this subfield in terms of the number densities of dark matter
-  halos has to assume a defined model for galaxy formation;
-  i.e. defining the link between halo mass, star formation rate, \ly
-  luminosity and \ly escape fraction.}
-
-{\bf The purpose of our work is to avoid any loose of generality by
-  assuming a defined halo-LAE connection and instead explore all the
-  possible halo populations to host LAEs.}
-
-\subsection{Simulation and halo catalogs}
-
-The Bolshoi simulation \citep{Bolshoi} we use in this paper was
-performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. The
-dark matter distribution is sampled using $2048^{3}$ particles, which
-translates into a particle mass of $m_{\rm   p}=1.35\times 10^{8}$
-$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
-a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$,
-cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
-$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
-power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.
-
-We use halo catalogs constructed with a Friend-of-Friends (FOF)
-algorithm with a linking length of 0.17 times the inter-particle
-distance. The catalogs were obtained from the publicly available
-Multidark database \footnote{{\tt
-    http://www.multidark.org/MultiDark/}}
-\citep{MultiDark}. For each halo in the box we store its
-comoving position in the box (3-D coordinates) and FOF mass. We focus our work
-on halos more massive than $1\times 10^{10}$\hMsun that are resolved
-with at least $70$ particles, the reasons for this choice are
-explained in the next sub-section.
-
-\subsection{A model to populate halos with LAEs}
-\label{subsec:mocks}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
-\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
-  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
-    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
-  method. The larger panel shows $7$ mock
-  fields together mimicking the SSA22 region. The intermediate panel
-  shows $3$ mock fields corresponding to the SXDS region. The lower
-  panels represent the SDF and GOODS-North fields. The same model has
-  another 14 associated mock surveys build from different regions in
-  the simulation, but constructed following the same pattern in the
-  {\texttt{match}} method.}
-\end{center} 
-\end{figure*}
-
-We assume that a dark matter halo can only host one
-detectable LAE at most.  There are three parameters that
-decide whether a halo host a LAE: the lower and upper bounds for the
-mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
-must keep in mind that the physical interpretation of the occupation
-fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
-forming galaxy in a halo and its detectability as a LAE.  We do not
-perform a explicit modeling for LAE detectability. Our model does not
-assign a luminosity or escape fraction to each LAE.  We are only
-interested in constraining the halo mass range hosting detectable LAEs
-under the conditions defined by \cite{Yamada2012}.
-
-In what follows we note by the letter ${\mathcal M}$ a model
-defined by a particular choice of the three scalar parameters $M_{\rm
-  min}$, $M_{\rm  max}$ and $f_{\rm occ}$. For each model ${\mathcal
-  M}$ we create a set of mock fields from disjoint volumes in the
-simulation. Each volume has the same geometry probed by Suprime-CAM
-and the narrow band filter, namely rectangular cuboids of dimensions
-$46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$ where the last dimension goes
-in the redshift direction. This corresponds to a total area of $880$
-arcmin$^{2}$ in each mock field. We construct a total $5\times 7
-\times 6=210$ of such volumes from a snapshot in the Bolshoi
-simulation. In each mock field a LAE is assigned to the position of a
-dark matter halo if the halo mass is in the range allowed by the model
-$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
-an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
-fraction $\xi<f_{\rm occ}$.
-
-Next we construct mock surveys by making groups of $12$ mock fields
-out of the $210$ available volumes. In total $15$ mock surveys are
-constructed for each model $\mathcal{M}$. The grouping of the $12$
-mock fields into a mock catalog is done in two different ways. The
-first is called {\texttt{match}}, it follows the clustering of the
-observational fields. From the $12$ mock fields, $7$ are constructed
-from contiguous fields in the simulation to mimic the SSA22 region,
-$3$ are also contiguous between them but not to the first $7$ fields
-to mimic the SXDS fields and finally $2$ non-contiguous fields to
-imitate the SDF and GOODS-North field.   The second way to group the
-mock fields is called {\texttt{random}}, whereby all the $12$ fields
-are selected in such a way as to avoid that any two volumes are
-contiguous. In this \documentname we only report the results obtained
-by the {\texttt{match}} method and mention explicitly differences
-observed with the {\texttt{random}} selection.
-
-Figure \ref{fig:distros} shows the spatial distribution for one mock
-survey constructed using the {\texttt{match}} method. Each field
-corresponds to one of the observational fields. The model parameters
-to build it are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
-  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. It is only one out of
-the $15$ different mock surveys that are constructed for each
-model. We note that we use $15\times 12=180$ mock fields out of the
-total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
-method imposes constraints on the way the $7$ fields mimicking the
-SSA22 can be distributed. This restriction makes unable some of the
-sub-volumes in the box. We decide to keep the number of mock surveys
-fixed to $15$ also for the {\texttt{random}} method in order to allow a
-fair comparison between the two methods.
-
-\subsection{Exploring and selecting good models}
 
@@
 
+The primary observational constraint we use in this paper is the LAE number
+density information at $z=3.1$ obtained by the panoramic narrow-band
+survey presented by \cite{Yamada2012} from a survey
+conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
+which has a field of view covering $34\times 27$ arc-min, corresponding to a
+comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
+band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
+corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
+centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
+an observed equivalent width, in the observer frame, larger than $190$
+\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
+sub-fields,  this corresponds to average surface number density of
+$0.24\pm 0.01$ arcmin$^{-2}$.
+
+The survey covered four independent fields:
+
+\begin{enumerate}
+\item The first is the SSA22
+field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
+field has been known to harbor a region with a large density excess of
+galaxies. {\bf The first sub-field of is taken around the same region
+  observed in \cite{Hayashino2004}.}
+
+\item The second observed region is composed by the fields Subaru/{\it
+  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
+total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).
+
+\item The third  field is the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
+$196$ LAEs (1 sub-field), and
+
+\item The fourth one is the field around the Great Observatory
+Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
+sub-field).  
+\end{enumerate}
+
+There is abundant observational work done on LAEs at redshift $z=3.1$
+\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
+However, we decide to focus on the data from \cite{Yamada2012} because
+it has the largest covered area with homogeneous instrumentation
+conditions (telescope, narrow band filter), data reduction pipeline
+and conditions to construct the LAE catalog. This ensures that the
+number density variations among fields are \emph{not} due to different
+observational conditions or criteria to construct the catalogs.
+
+{\bf A secondary benchmark is the angular correlation function
+(ACF). \cite{Yamada2012} does not report an ACF measurement for
+  their fields. Instead we use the results by   \cite{Ouchi2008} who
+  reported the ACF is over a region of $1$ deg$^2$ over the SXDS
+  field.  We also keep track of the results by \cite{Hayashino2004}
+  who reported the ACF in the SSA22 region, including its densest
+  subfield.}
+
+{\bf There are some differences between \cite{Ouchi2008} observations
+  and those by \cite{Yamada2012}. The details in the color selection,
+  corresponding limiting luminosities and EW thresholds are different
+  in these references. The average LAEs number density inferred by
+  \cite{Hayashino2004} is  $0.37$ arcmin$^{-2}$, which is $30\%$
+  higher than the new measurement by \cite{Yamada2012}. In the case of
+  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
+  is $\sim 50\%$ lower than the value inferred by \cite{Yamada2012}
+  for a portion of the same region.}
+
+\subsection{The adequacy of including SSA22 as an observational benchmark}
+
+{\bf The field SSA22 has been known to harbor a significant
+  galaxy overdensity. \cite{Yamada2012} estimates that the densest
+  subfield is likely to be a rare density peak with $3-4\sigma$
+  significance on the scale of $\sim 60$\hMpc. }
+
+{\bf All the other sub-fields in SSA22 are average. They have a similar
+  number density as other blank fields. The left panel in Figure
+  \ref{fig:halos} shows the integrated distribution of LAEs number
+  density in all the fields reported in  \cite{Yamada2012}. It is
+  evident that there is only one sub-field  that stands out as an
+  outlier in the distribution (it corresponds to  the densest field in
+  SSA22). All the other fields form a continous  distribution in
+  number density.}
+
+{\bf Therefore, using the whole SSA22 region as a benchmark in the
+  number density distribution does not impose any bias. However, on
+  has to  keep in mind that is not plausible that the full number
+  density distribution from a simulation will include a very dense
+  field. We do not require the presence of such field to judge a mock
+  distribution as successful. The statistical test we perform to
+  compare mock distributions   against   observations does not require
+  such a perfect match.
+
+  In terms of the ACF the results that include the densest
+  field in SSA22 \citep{Hayashino2004} are consistent, within 
+  uncertainties, with the results of other fields
+  \citep{Ouchi2008}. In spite of this consistency we will focus on the
+  results from \citep{Ouchi2008}.}
+
+\subsection{Simulation and halo catalogs}
+
+The Bolshoi simulation \citep{Bolshoi} we use in this paper was
+performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. The
+dark matter distribution is sampled using $2048^{3}$ particles, which
+translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$
+$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
+a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$,
+cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
+$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
+power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.
+
+We use halo catalogs constructed with a Friend-of-Friends (FOF)
+algorithm with a linking length of 0.17 times the inter-particle
+distance. The catalogs were obtained from the publicly available
+Multidark database \footnote{{\tt
+    http://www.multidark.org/MultiDark/}}
+\citep{MultiDark}. For each halo in the box we store its
+comoving position in the box (3-D coordinates) and FOF mass. We focus our work
+on halos more massive than $1\times 10^{10}$\hMsun that are resolved
+with at least $70$ particles, the reasons for this choice are
+explained in the next sub-section.
+
+\subsection{A model to populate halos with LAEs}
+\label{subsec:mocks}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
+\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
+  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
+    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
+  method. The larger panel shows $7$ mock
+  fields together mimicking the SSA22 region. The intermediate panel
+  shows $3$ mock fields corresponding to the SXDS region. The lower
+  panels represent the SDF and GOODS-North fields. The same model has
+  another 14 associated mock surveys build from different regions in
+  the simulation, but constructed following the same pattern.}
+\end{center} 
+\end{figure*}
+
+We assume that a dark matter halo can only host one
+detectable LAE at most.  There are three parameters that
+decide whether a halo host a LAE: the lower and upper bounds for the
+mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
+must keep in mind that the physical interpretation of the occupation
+fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
+forming galaxy in a halo and its detectability as a LAE.
+
+{\bf We recall that we do not perform a explicit modeling for LAE
+detectability. Our model does not assign a luminosity or escape
+fraction for each LAE. We are interested in constraining the halo
+mass range hosting detectable LAEs commonly used in photometric
+narrow-band surveys. We also want to explore a wide range of
+possible masses for the host halos without any strong theoretical
+prejudice regarding the details of star formation in high-redshift
+galaxies. }
+
+In what follows we note by the letter ${\mathcal M}$ a model
+defined by a particular choice of the three scalar parameters $M_{\rm
+  min}$, $M_{\rm  max}$ and $f_{\rm occ}$. For each model ${\mathcal
+  M}$ we create a set of mock fields from disjoint volumes in the
+simulation. Each volume has the same geometry probed by Suprime-CAM
+and the narrow band filter, namely rectangular cuboids of dimensions
+$46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$ where the last dimension goes
+in the redshift direction. This corresponds to a total area of $880$
+arcmin$^{2}$ in each mock field. We construct a total $5\times 7
+\times 6=210$ of such volumes from a snapshot in the Bolshoi
+simulation. In each mock field a LAE is assigned to the position of a
+dark matter halo if the halo mass is in the range allowed by the model
+$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
+an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
+fraction $\xi<f_{\rm occ}$.
+
+Next we construct mock surveys by making groups of $12$ mock fields
+out of the $210$ available volumes. In total $15$ mock surveys are
+constructed for each model $\mathcal{M}$. The grouping of the $12$
+mock fields into a mock catalog is done in two different ways. The
+first is called {\texttt{match}}, it follows the clustering of the
+observational fields. From the $12$ mock fields, $7$ are constructed
+from contiguous fields in the simulation to mimic the SSA22 region,
+$3$ are also contiguous between them but not to the first $7$ fields
+to mimic the SXDS fields and finally $2$ non-contiguous fields to
+imitate the SDF and GOODS-North field.   The second way to group the
+mock fields is called {\texttt{random}}, whereby all the $12$ fields
+are selected in such a way as to avoid that any two volumes are
+contiguous. In this \documentname we only report the results obtained
+by the {\texttt{match}} method and mention explicitly differences
+observed with the {\texttt{random}} selection.
+
+Figure \ref{fig:distros} shows the spatial distribution for one mock
+survey constructed using the {\texttt{match}} method. Each field
+corresponds to one of the observational fields. The model parameters
+to build the mock are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
+  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
+one out of the $15$ different mock surveys that are constructed for
+each model. We note that we only use $15\times 12=180$ mock fields out of the
+total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
+method imposes constraints on the way the $7$ fields mimicking the
+SSA22 can be distributed. This restriction makes unable some of the
+sub-volumes in the box. We decide to keep the number of mock surveys
+fixed to $15$ also for the {\texttt{random}} method in order to allow a
+fair comparison between the two methods.
+
+\subsection{Exploring and selecting good models}
+
 We make a thorough exploration of the parameter space for the models
@@
 The lower limit for the parameter $M_{\rm min}$ is set by the minimum
-occupation fraction we are able to consider. At $M_{\rm
-  min}=10^{10}$\hMsun the halo number density is already $\sim 10$
-times higher than the observational constraints for LAEs. This means
-that models in that mass range and an occupation fraction $f_{\rm
-  occ}=0.1$ have the possibility to be compatible with observations. Lower
-values for $M_{\rm min}$ require $f_{\rm occ}<0.1$, which are not
-considered in this \documentname.
+occupation fraction we decide to consider. At $M_{\rm
+  min}=10^{10}$\hMsun the halo number density around that mass range
+is $\sim 10$ times higher than the observational constraints
+for LAEs. This means that models in that mass range and an occupation fraction $f_{\rm  occ}=0.1$ have the possibility to be compatible with
+observations. Lower values for $M_{\rm min}$ require $f_{\rm
+  occ}<0.1$, which are not considered in this \documentname.  {\bf In
+  turn exploring occupation fractions on the order of $f_{\rm occ}=0.01$ requires
+  only makes sense for halo populations in the mass range of
+  $10^{9}$\hMsun which are abundant enough to fit observations with a
+  low occupation fraction. In our case that mass range is not resolved
+  by the Bolshoi simulation an are not considered here.}
 
 For each mock survey generated in a given model ${\mathcal M}$ we
-compute the surface density in the $12$ mock fields. We perform a
-Kolmogorov-Smirnov (KS) to compare this mock data against the $12$
-observational values. From this test we obtain a value $0<P<1$ to
+compute the surface density in its $12$ mock fields. We perform a
+Kolmogorov-Smirnov (KS) to compare these values against the $12$
+observational values. This tests gives us a value $0<P<1$ to
 reject the null hypothesis, namely that two data sets come from the
@@
 
-We begin by considering that  a model ${\mathcal M}$ that has at least
-one mock survey (out of 15) consistent with the observed
-distribution of LAE number densities has viable parameters that
-deserve to be considered for further analysis. Later on we impose
-harder constraints to reduce the number of models by asking that all
-the 15 mocks to be consistent with observations.
-
-The second constraint  comes from the angular correlation function (ACF)
-for all the models having the $15$ mock surveys consistent with
-observations .
+We begin by considering that  a model ${\mathcal M}$ with at least one
+mock survey (out of 15) consistent with observations has viable
+parameters to host LAEs. From that we consider a stronger constraints
+to reduce the number of models by asking that all the 15 mocks to be
+consistent with observations and analyze again the properties of the
+resulting models. Finally we add the ACF as an additional constraint
+and consider all the models having their $15$ mocks consistent with
+observations.
 
 {\bf The ACF is computed using  the Landy \&  Szalay estimator
-  \citep{Landy1993}  on two different  fields in the mock survey. The
-  first field is the densest to be compared against the results of
-  \cite{Hayashino2004}. The second field has an average number density and is compared against \cite{Ouchi2010}.}
+  \citep{Landy1993}  on fields of size $1$ deg$^2$ to be compared
+  against the results reported by \cite{Ouchi2010}.}
 
@@
 where $\theta_0$ and $\beta$ are free parameters. The fit is done
-using a least square minimization procedure. For each mock field we obtain a
-covariance matrix that gives us the uncertainty in the parameters $\beta$ and
-$\theta_0$. Using the $15$ mock fields in a mock survey, we compute a
-mean value for the parameters and its associated uncertainty as the
-quadratic average of the uncertainties in the fitting procedure. We
-consider that a model is consistent with observations if the two
-parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
-range.
+using a least square minimization procedure. For each mock field we
+obtain a covariance matrix that gives us the uncertainty in the
+parameters $\beta$ and $\theta_0$. {\bf We consider that a mock field is
+consistent with observations if the two parameters $\beta$ and
+$\theta_0$ are equal within a $1$-$\sigma$ range.}
 
@@
 \bibliographystyle{mn2e}
-\begin{thebibliography}{}
-
-\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
-  et~al.}{2013a}]{Behroozi2013b}
-{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013a, \apjl, 762, L31
-
-\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
-  et~al.}{2013b}]{Behroozi2013a}
-{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013b, \apj, 770, 57
-
-\bibitem[\protect\citeauthoryear{{Colberg}, {White}, {Yoshida}, {MacFarland},
-  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
-  {Thomas} \& {Virgo Consortium}}{{Colberg} et~al.}{2000}]{Colberg00}
-{Colberg} J.~M.,  {White} S.~D.~M.,  {Yoshida} N.,  {MacFarland} T.~J.,
-  {Jenkins} A.,  {Frenk} C.~S.,  {Pearce} F.~R.,  {Evrard} A.~E.,  {Couchman}
-  H.~M.~P.,  {Efstathiou} G.,  {Peacock} J.~A.,  {Thomas} P.~A.,    {Virgo
-  Consortium} 2000, \mnras, 319, 209
-
-\bibitem[\protect\citeauthoryear{{Dayal}, {Ferrara}, {Saro}, {Salvaterra},
-  {Borgani} \& {Tornatore}}{{Dayal} et~al.}{2009}]{Dayal2009}
-{Dayal} P.,  {Ferrara} A.,  {Saro} A.,  {Salvaterra} R.,  {Borgani} S.,
-  {Tornatore} L.,  2009, \mnras, 400, 2000
-
-\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Jeeson-Daniel}}{{Dijkstra} \&
-  {Jeeson-Daniel}}{2013}]{Dijkstra2013}
-{Dijkstra} M.,  {Jeeson-Daniel} A.,  2013, ArXiv e-prints
-
-\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
-  {Kramer}}{2012}]{Dijkstra2012}
-{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672
-
-\bibitem[\protect\citeauthoryear{{Dijkstra}, {Mesinger} \& {Wyithe}}{{Dijkstra}
-  et~al.}{2011}]{Dijkstra11}
-{Dijkstra} M.,  {Mesinger} A.,    {Wyithe} J.~S.~B.,  2011, \mnras, 414, 2139
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero} \& {Dijkstra}}{{Forero-Romero}
-  \& {Dijkstra}}{2013}]{ForeroRomero2013}
-{Forero-Romero} J.~E.,  {Dijkstra} M.,  2013, \mnras, 428, 2163
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
-  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero}
-  et~al.}{2011}]{ForeroRomero2011}
-{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
-  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber} \&
-  {Prada}}{{Forero-Romero} et~al.}{2012}]{ForeroRomero2012}
-{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,    {Prada} F.,  2012,
-  \mnras, 419, 952
-
-\bibitem[\protect\citeauthoryear{{Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
-  {Verhamme} \& {Hayes}}{{Garel} et~al.}{2012}]{Garel2012}
-{Garel} T.,  {Blaizot} J.,  {Guiderdoni} B.,  {Schaerer} D.,  {Verhamme} A.,
-  {Hayes} M.,  2012, \mnras, 422, 310
-
-\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
-  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio} \&
-  {Feldmeier}}{{Gawiser} et~al.}{2007}]{Gawiser2007}
-{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
-  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
-  G.~A.,  {Fazio} G.,    {Feldmeier} J.~J.,  2007, \apj, 671, 278
-
-\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
-  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio},
-  {Feldmeier}, {Huang}, {Infante}, {Lira} \& {Padilla}}{{Gawiser}
-  et~al.}{2007}]{Gawiser07}
-{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
-  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
-  G.~A.,  {Fazio} G.,  {Feldmeier} J.~J.,  {Huang} J.-s.,  {Infante} L.,
-  {Lira} P.,    {Padilla} N.,  2007, \apj, 671, 278
-
-\bibitem[\protect\citeauthoryear{{Guaita}, {Francke}, {Gawiser}, {Bauer},
-  {Hayes}, {{\"O}stlin} \& {Padilla}}{{Guaita} et~al.}{2013}]{Guaita2013}
-{Guaita} L.,  {Francke} H.,  {Gawiser} E.,  {Bauer} F.~E.,  {Hayes} M.,
-  {{\"O}stlin} G.,    {Padilla} N.,  2013, \aap, 551, A93
-
-\bibitem[\protect\citeauthoryear{{Hayashino}, {Matsuda}, {Tamura}, {Yamauchi},
-  {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi},
-  {Shimasaku}, {Shioya} \& {Taniguchi}}{{Hayashino}
-  et~al.}{2004}]{Hayashino2004}
-{Hayashino} T.,  {Matsuda} Y.,  {Tamura} H.,  {Yamauchi} R.,  {Yamada} T.,
-  {Ajiki} M.,  {Fujita} S.~S.,  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,
-  {Okamura} S.,  {Ouchi} M.,  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,
-  2004, \aj, 128, 2073
-
-\bibitem[\protect\citeauthoryear{{Hayes}, {{\"O}stlin}, {Schaerer},
-  {Mas-Hesse}, {Leitherer}, {Atek}, {Kunth}, {Verhamme}, {de Barros} \&
-  {Melinder}}{{Hayes} et~al.}{2010}]{Hayes2010}
-{Hayes} M.,  {{\"O}stlin} G.,  {Schaerer} D.,  {Mas-Hesse} J.~M.,  {Leitherer}
-  C.,  {Atek} H.,  {Kunth} D.,  {Verhamme} A.,  {de Barros} S.,    {Melinder}
-  J.,  2010, \nat, 464, 562
-
-\bibitem[\protect\citeauthoryear{{Jarosik}, {Bennett}, {Dunkley}, {Gold},
-  {Greason}, {Halpern}, {Hill}, {Hinshaw}, {Kogut}, {Komatsu}, {Larson} \&
-  {Limon}}{{Jarosik} et~al.}{2011}]{Jarosik2011}
-{Jarosik} N.,  {Bennett} C.~L.,  {Dunkley} J.,  {Gold} B.,  {Greason} M.~R.,
-  {Halpern} M.,  {Hill} R.~S.,  {Hinshaw} G.,  {Kogut} A.,  {Komatsu} E.,
-  {Larson} D.,    {Limon} M.,  2011, \apjs, 192, 14
-
-\bibitem[\protect\citeauthoryear{{Jose}, {Srianand} \& {Subramanian}}{{Jose}
-  et~al.}{2013}]{Jose2013b}
-{Jose} C.,  {Srianand} R.,    {Subramanian} K.,  2013, ArXiv e-prints
-
-\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
-  {Primack}}{{Klypin} et~al.}{2011}]{Bolshoi}
-{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102
-
-\bibitem[\protect\citeauthoryear{{Koehler}, {Schuecker} \&
-  {Gebhardt}}{{Koehler} et~al.}{2007}]{Koehler2007}
-{Koehler} R.~S.,  {Schuecker} P.,    {Gebhardt} K.,  2007, \aap, 462, 7
-
-\bibitem[\protect\citeauthoryear{{Komatsu}, {Dunkley}, {Nolta}, {Bennett},
-  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Limon}, {Page}, {Spergel} \&
-  {Halpern}}{{Komatsu} et~al.}{2009}]{Komatsu2009}
-{Komatsu} E.,  {Dunkley} J.,  {Nolta} M.~R.,  {Bennett} C.~L.,  {Gold} B.,
-  {Hinshaw} G.,  {Jarosik} N.,  {Larson} D.,  {Limon} M.,  {Page} L.,
-  {Spergel} D.~N.,    {Halpern} M.,  2009, \apjs, 180, 330
-
-\bibitem[\protect\citeauthoryear{{Kudritzki}, {M{\'e}ndez}, {Feldmeier},
-  {Ciardullo}, {Jacoby}, {Freeman}, {Arnaboldi}, {Capaccioli}, {Gerhard} \&
-  {Ford}}{{Kudritzki} et~al.}{2000}]{Kudritzki2000}
-{Kudritzki} R.-P.,  {M{\'e}ndez} R.~H.,  {Feldmeier} J.~J.,  {Ciardullo} R.,
-  {Jacoby} G.~H.,  {Freeman} K.~C.,  {Arnaboldi} M.,  {Capaccioli} M.,
-  {Gerhard} O.,    {Ford} H.~C.,  2000, \apj, 536, 19
-
-\bibitem[\protect\citeauthoryear{{Landy} \& {Szalay}}{{Landy} \&
-  {Szalay}}{1993}]{Landy1993}
-{Landy} S.~D.,  {Szalay} A.~S.,  1993, \apj, 412, 64
-
-\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
-  et~al.}{2013}]{Laursen2013}
-{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124
-
-\bibitem[\protect\citeauthoryear{{Laursen}, {Razoumov} \&
-  {Sommer-Larsen}}{{Laursen} et~al.}{2009}]{Laursen2009}
-{Laursen} P.,  {Razoumov} A.~O.,    {Sommer-Larsen} J.,  2009, \apj, 696, 853
-
-\bibitem[\protect\citeauthoryear{{Laursen} \& {Sommer-Larsen}}{{Laursen} \&
-  {Sommer-Larsen}}{2007}]{Laursen2007}
-{Laursen} P.,  {Sommer-Larsen} J.,  2007, \apjl, 657, L69
-
-\bibitem[\protect\citeauthoryear{{Matsuda}, {Yamada}, {Hayashino}, {Tamura},
-  {Yamauchi}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi}, {Shimasaku},
-  {Shioya} \& {Taniguchi}}{{Matsuda} et~al.}{2005}]{Matsuda2005}
-{Matsuda} Y.,  {Yamada} T.,  {Hayashino} T.,  {Tamura} H.,  {Yamauchi} R.,
-  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,  {Okamura} S.,  {Ouchi} M.,
-  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,  2005, \apjl, 634, L125
-
-\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{Neufeld1991}
-{Neufeld} D.~A.,  1991, \apjl, 370, L85
-
-\bibitem[\protect\citeauthoryear{{Nilsson}, {M{\o}ller}, {M{\"o}ller}, {Fynbo},
-  {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen} \&
-  {Grove}}{{Nilsson} et~al.}{2007}]{Nilsson2007}
-{Nilsson} K.~K.,  {M{\o}ller} P.,  {M{\"o}ller} O.,  {Fynbo} J.~P.~U.,
-  {Micha{\l}owski} M.~J.,  {Watson} D.,  {Ledoux} C.,  {Rosati} P.,  {Pedersen}
-  K.,    {Grove} L.~F.,  2007, \aap, 471, 71
-
-\bibitem[\protect\citeauthoryear{{Nilsson}, {Tapken}, {M{\o}ller}, {Freudling},
-  {Fynbo}, {Meisenheimer}, {Laursen} \& {{\"O}stlin}}{{Nilsson}
-  et~al.}{2009}]{Nilsson2009}
-{Nilsson} K.~K.,  {Tapken} C.,  {M{\o}ller} P.,  {Freudling} W.,  {Fynbo}
-  J.~P.~U.,  {Meisenheimer} K.,  {Laursen} P.,    {{\"O}stlin} G.,  2009, \aap,
-  498, 13
-
-\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
-  et~al.}{2012}]{Orsi2012}
-{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87
-
-\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
-  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
-  {Okamura}, {Iye}, {Takata}, {Yoshida} \& {Yoshida}}{{Ouchi}
-  et~al.}{2008}]{Ouchi2008}
-{Ouchi} M.,  {Shimasaku} K.,  {Akiyama} M.,  {Simpson} C.,  {Saito} T.,  {Ueda}
-  Y.,  {Furusawa} H.,  {Sekiguchi} K.,  {Yamada} T.,  {Kodama} T.,  {Kashikawa}
-  N.,  {Okamura} S.,  {Iye} M.,  {Takata} T.,  {Yoshida} M.,    {Yoshida} M.,
-  2008, \apjs, 176, 301
-
-\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
-  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
-  {Okamura}, {Simpson} \& {Yoshida}}{{Ouchi} et~al.}{2010}]{Ouchi2010}
-{Ouchi} M.,  {Shimasaku} K.,  {Furusawa} H.,  {Saito} T.,  {Yoshida} M.,
-  {Akiyama} M.,  {Ono} Y.,  {Yamada} T.,  {Ota} K.,  {Kashikawa} N.,  {Iye} M.,
-   {Kodama} T.,  {Okamura} S.,  {Simpson} C.,    {Yoshida} M.,  2010, \apj,
-  723, 869
-
-\bibitem[\protect\citeauthoryear{{Peebles}}{{Peebles}}{1980}]{Peebles1980}
-{Peebles} P.~J.~E.,  1980, {The large-scale structure of the universe}
-
-\bibitem[\protect\citeauthoryear{{Pentericci}, {Grazian}, {Fontana},
-  {Castellano}, {Giallongo}, {Salimbeni} \& {Santini}}{{Pentericci}
-  et~al.}{2009}]{Pentericci2009}
-{Pentericci} L.,  {Grazian} A.,  {Fontana} A.,  {Castellano} M.,  {Giallongo}
-  E.,  {Salimbeni} S.,    {Santini} P.,  2009, \aap, 494, 553
-
-\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
-  Granger}{2007}]{IPython}
-P\'erez F.,  Granger B.~E.,  2007, {C}omput. {S}ci. {E}ng., 9, 21
-
-\bibitem[\protect\citeauthoryear{Riebe, Partl, Enke, Forero-Romero, Gottlöber,
-  Klypin, Lemson, Prada, Primack, Steinmetz \& Turchaninov}{Riebe
-  et~al.}{2013}]{MultiDark}
-Riebe K.,  Partl A.~M.,  Enke H.,  Forero-Romero J.,  Gottlöber S.,  Klypin
-  A.,  Lemson G.,  Prada F.,  Primack J.~R.,  Steinmetz M.,    Turchaninov V.,
-  2013, Astronomische Nachrichten, 334, 691
-
-\bibitem[\protect\citeauthoryear{{Springel}, {White}, {Jenkins}, {Frenk},
-  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
-  {Thomas}, {Couchman}, {Evrard}, {Colberg} \& {Pearce}}{{Springel}
-  et~al.}{2005}]{SpringelNature05}
-{Springel} V.,  {White} S.~D.~M.,  {Jenkins} A.,  {Frenk} C.~S.,  {Yoshida} N.,
-   {Gao} L.,  {Navarro} J.,  {Thacker} R.,  {Croton} D.,  {Helly} J.,
-  {Peacock} J.~A.,  {Cole} S.,  {Thomas} P.,  {Couchman} H.,  {Evrard} A.,
-  {Colberg} J.,    {Pearce} F.,  2005, \nat, 435, 629
-
-\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
-  {Maselli}}{{Verhamme} et~al.}{2006}]{Verhamme2006}
-{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397
-
-\bibitem[\protect\citeauthoryear{{Walker-Soler}, {Gawiser}, {Bond}, {Padilla}
-  \& {Francke}}{{Walker-Soler} et~al.}{2012}]{Soler2012}
-{Walker-Soler} J.~P.,  {Gawiser} E.,  {Bond} N.~A.,  {Padilla} N.,    {Francke}
-  H.,  2012, \apj, 752, 160
-
-\bibitem[\protect\citeauthoryear{{Yajima}, {Choi} \& {Nagamine}}{{Yajima}
-  et~al.}{2012}]{Yajima2012}
-{Yajima} H.,  {Choi} J.-H.,    {Nagamine} K.,  2012, \mnras, 427, 2889
-
-\bibitem[\protect\citeauthoryear{{Yamada}, {Nakamura}, {Matsuda}, {Hayashino},
-  {Yamauchi}, {Morimoto}, {Kousai} \& {Umemura}}{{Yamada}
-  et~al.}{2012}]{Yamada2012}
-{Yamada} T.,  {Nakamura} Y.,  {Matsuda} Y.,  {Hayashino} T.,  {Yamauchi} R.,
-  {Morimoto} N.,  {Kousai} K.,    {Umemura} M.,  2012, \aj, 143, 79
-
-\bibitem[\protect\citeauthoryear{{Zheng}, {Cen}, {Trac} \&
-  {Miralda-Escud{\'e}}}{{Zheng} et~al.}{2010}]{Zheng2010}
-{Zheng} Z.,  {Cen} R.,  {Trac} H.,    {Miralda-Escud{\'e}} J.,  2010, \apj,
-  716, 574
-
-\end{thebibliography}
-
-%\bibliography{references}
+\bibliography{references}
 

### 2013-11-18 paper/ms.tex
editing the discussion

@@
 
-In the previous Section we started by matching the rough numbers for the
-galaxy surface number density. This sets the median mass of all
-successful models to the broad range $(10^{10}$-$10^{12})$ \hMsun for
-$M_{\rm min}$ and $M_{\rm max}$. Then we included additional criteria on the
-number of mock surveys that must be consistent observations
-and the information from the angular correlation function, reducing
-the number of feasible models. We ended up with $23$ models out of
-the initial $9000$ possible combination of parameters.
-
-Now we define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
+We end up with $XX$ models, out of $9000$ initial guesses, consistent
+with observations. In order to discuss these results we now
+define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
 \log_{10}M_{\rm  min}$, to use it together with the occupation
@@
 \item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
-  dex: 12 models. 
+  dex: XX models. 
 \item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
-  low $\Delta M\leq 1.0$: 11 models 
+  low $\Delta M\leq 1.0$: XX models 
 \end{itemize}
 %
-The full list of parameter in the two families is summarized in Table
-\ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
-have a clear majority of any family. This leads us to the following
-two conclusions. First, the occupation fraction cannot be constrained
-based on clustering analysis. Second, the halos hosting LAEs have a
-narrow mass range.
-
-The existence of a narrow mass range for halo masses has different
-possible explanations. A cut at the low mass end, $M_{\rm min}$, can be
+A complete parameter list is presented in Table
+\ref{table:firstfamily} and Table \ref{table:secondfamily}. There are
+two interesting feature in these families. First, the occupation
+fraction can take any value from $0.1$ to $1.0$. Second, the halos
+hosting LAEs all have a narrow mass range $\Delta M\leq 1.0$.
+
+{\bf The existence of models with high occupation fractions $f_{\rm
+    occ}>0.3$ is unexpected from previous clustering analysis that do
+  not take  account the effect of cosmic variance in the same way we
+  propose in this \documentname. It seems that taking explicitly into
+  account  effect hinders the possibility of constraining the LAEs
+  occupation fraction.}
+
+{\bf This challenge can be tracked to the uncertainty in the minimum
+  halo mass. Within out framework, high occupation fraction are
+  allowed because there are models where the minimum mass for hosting
+  observable LAEs is larger than $10^{10.8}$\hMsun, which are fully
+  consistent with the observational constraints.}
+
+{\bf On the other hand, a robust conclusion is that all
+possible models have narrow mass range regardless of the occupation
+fraction.}
+
+...A cut at the low mass end, $M_{\rm min}$, can be
 interpreted in terms of the minimal halo star formation rate needed to

### 2013-11-19 paper/ms.tex
more editing in the paper

@@
 
-The main purpose of this section is to show how different
-observational constraints narrow down the parameters space of allowed
-models. Each sub-section presents the effect of adding new pieces of
-observational or statistical evidence.
-
-\subsection{Dark Matter Halo Number Density}
-
-In Figure \ref{fig:halos} we present the results for  the
-integrated dark matter halo surface density as a function of the
-minimum halo mass $M_{\rm min}$. Each line corresponds to one of the
-210 sub-volumes in the Bolshoi simulation. The gray band indicates the
-surface density values for LAEs allowed by observations
-\citep{Yamada2012}.
-
-This result allows us to understand why only a specific range of
-models ${\mathcal M}$ can be expected to be consistent with
-observations. From Figure \ref{fig:halos} we can read that models with
-a minimum mass $M_{\rm min}>10^{11.5}$\hMsun will always have a
-surface number density lower than the observational constrain. This
-makes impossible that models in that range can be compatible with
-observations, there are simply to few halos compared to observed
-LAEs. The opposite is true in models with $M_{\rm
-  min}<10^{10.5}$\hMsun that have a surface number density larger
-observations. In those cases the occupation fraction $f_{\rm occ}<1.0$
-can be tuned in order to lower the halo number density to match
-observations.
-
-Figure \ref{fig:halos} also illustrates the impact of cosmic
-variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
-number density abundance.  A consequence of this variation is that
-models with the same mass range and occupation fraction can have mock
-fields with number densities varying up to a factor of $\sim
-2-5$. This scatter is comparable to the $0.3$ dex scatter coming from 
-observations. In the same Figure \ref{fig:halos} we see that at fixed
-number density, around the range allowed by observations, there is an
-scatter in the masses of $0.4-0.5$ dex.
-
-This scatter induced by cosmic variance is naturally included in the
-mock construction process. This will allows us to have a wider range
-of models compatible with observations, as compared with a model that
-neglects cosmic variance.
-
-\subsection{Models consistent with the surface density distributions}
-
 \begin{figure*}
@@
   compatible with observations. Only regions of parameter  space with
-  at least one consistent mock survey are  included. \label{fig:landscape}}     
+  at least one consistent mock survey are
+  included. \label{fig:landscape}}      
 \end{figure*}
 
+The main purpose of this section is to show how different
+observational constraints narrow down the parameters space of allowed
+models. Each sub-section presents the effect of adding a new piece of 
+observational or statistical evidence.
+
+\subsection{Dark Matter Halo Number Density}
+
+The right panel in Figure \ref{fig:halos} shows the  integrated dark matter halo surface
+density as a function of  minimum halo mass $M_{\rm min}$. Each line
+corresponds to one of the 210 sub-volumes in the Bolshoi
+simulation. The gray band indicates the surface density values for
+LAEs allowed by observations \citep{Yamada2012}. The dashed lines
+represent the average values in the fields observed by
+\citep{Hayashino2004,Ouchi08}.
+
+This plot allows us to understand why only a specific range of
+models ${\mathcal M}$ can be expected to be consistent with
+observations. From Figure \ref{fig:halos} we can read that models with
+a minimum mass $M_{\rm min}>10^{12}$\hMsun always have a
+surface number density lower than the observational constrain, making
+them incompatible with observations; there are simply to few halos compared to observed
+LAEs. The opposite is true in models with $M_{\rm
+  min}<10^{11.0}$\hMsun that have a surface number density larger
+observations. In those cases the maximum mass $M_{\rm max}$ and the
+occupation fraction $f_{\rm occ}<1.0$  can be tuned in order to lower
+the halo number density to match observations.
+
+Figure \ref{fig:halos} also illustrates the impact of cosmic
+variance. At fixed minimum mass there is an scatter of $0.3-0.6$ dex
+in the number density abundance, which is of the same order of
+magnitude as the scatter in the observational data.  As a consequence, the variation in
+the number density in mocks for models with the same mass range and occupation
+fraction can be by factors of $\sim 2-5$.  This scatter induced by
+cosmic variance is naturally included in the mock construction
+process. This variance will explain that very different models can be
+made compatible with observations.
+
+\subsection{Models consistent with the surface density distributions}
+
 Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
-min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test yields
-values of $P>0.05$ at least for one mock survey, which is the most
-conservative assumption for agreement between a model and observations. For those models it
+min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test
+between the mocks and observations yields values of $P>0.05$ for at
+least one mock survey in each model. For those models it
 is not possible reject the hypothesis that the simulated and observed
 data for the surface number density come from the same parent
-distribution. In total, there are between $550$ to $600$ models out of
-the original $9000$ models that have at least one mock survey
-consistent with observations. By inspection of Figure
-\ref{fig:landscape} we see that the halo number abundance is able to
-constraint the minimum mass $M_{\rm min}$ to a narrow range, while
-$M_{\rm max}$ and $f_{\rm occ}$ remain largely unconstrained.
+distribution.
+
+In total, there are between $550$ to $600$ models out of the original
+$9000$ models that have at least one mock survey consistent with
+observations. By inspection of Figure \ref{fig:landscape} we see that
+the halo number abundance is able to constraint the minimum mass
+$M_{\rm min}$ to a narrow range, while $M_{\rm max}$ and $f_{\rm occ}$
+remain largely unconstrained.
 
@@
 models where the minimum mass is high $M_{\rm min}>
-10^{11.5}\hMsun$. None of these models is compatible with observations
-as expected from the arguments presented in the previous
-subsection. For these models the number density of LAEs is too low
-compared to observations.
+10^{11.5}\hMsun$.  For these models the number density of LAEs is too low
+to be compatible with observations.
 
@@
 of the mock surveys into good agreement with observations. In this
-region of parameter space one can find two extreme kinds of models.
-One kind where the mass interval $\Delta M\equiv \log_{10} M_{\rm max}
-- \log_{10}M_{\rm  min}$ is narrow with $\Delta M<1.0$ dex, others
-where the mass interval is  extended $\Delta M>1.0$ dex going up to
-the maximum halo mass present in the simulation at that redshift, with
-$\Delta M = 2.5$ dex in those cases.
+region we find two extreme kinds of models. One extreme are models
+with a narrow mass interval $\Delta M\equiv \log_{10} M_{\rm max}
+- \log_{10}M_{\rm  min} <1.0$ dex. The other extreme are models with a
+large mass interval $\Delta M>1.0$ dex going up to the maximum halo
+mass present in the simulation at that redshift, with $\Delta M = 2.5$
+dex in some cases.
 
@@
 most of the successful models are found in the second and third regions of
-parameter space. This result was already expected from halo
+parameter space. This result was expected from halo
 abundance calculations shown in Figure \ref{fig:halos} and discussed
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.95\linewidth,angle=0]{Fig4_match_P5.pdf}
-\end{center} 
-\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
-  consistent with the observed surface number density
-  distribution in terms of the KS-test values $P>0.05$. Only $\sim
-  100$ models have all their mocks consistent with observations. 
-  \label{fig:high_success_rate}.}  
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.95\linewidth,angle=0]{Fig4_match_P5.pdf}
+%\end{center} 
+%\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
+%  consistent with the observed surface number density
+%  distribution in terms of the KS-test values $P>0.05$. Only $\sim
+%  100$ models have all their mocks consistent with observations. 
+%  \label{fig:high_success_rate}.}  
+%\end{figure}
 
 \subsection{Models with the largest number of consistent mock surveys}
-
-In the previous sub-section we presented a conservative criterion of
-agreement by selecting the models that had at least one mock survey
-with $P>0.05$ in the KS test. Now we turn to a more strict selection
-by requiring all constructed mock surveys to be consistent with
-observations.
-
-Figure \ref{fig:high_success_rate} shows the number of models
-that have at least $N_{\rm high-P}$ mocks with $P>0.05$. For each
-model ${\mathcal M}$ there are 15 different mock surveys.  We discard
-the models that have 14 mocks or less consistent with
-observations. With this cut we find $\sim 100$ models with all the 15
-mock survey realizations with $P>0.05$.  This cut represents a
-reduction by a factor of $\sim 6$ with respect to the total number of
-models with at least one consistent mock.
-
-Figure \ref{fig:restriction_mock} presents the locii of these models
-in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
-  min}-f_{\rm occ}$. With this constraints the
-number of consistent models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are
-greatly reduced. This corresponds to the regions in the parameter
-space in Figure \ref{fig:landscape} that already had a low number of
-consistent mock surveys. On the other hand, from the right panel in
-Figure \ref{fig:restriction_mock} one can see that the reduction of
-favored values for the occupation fraction $f_{\rm occ}$ is not strong.
-
-We conclude that conditions on the number density statistics, even if they are
-very strict, only put strong constraints on the minimum mass $M_{\rm
-  min}$ but not on the other two parameter of the model $M_{\rm max}$
-and $f_{\rm occ}$. In the next section we use additional observational
-information to constrain these parameters.
 
@@
 
+In the previous sub-section we use a conservative criterion of
+agreement by selecting the models that had at least one mock survey
+with $P>0.05$ in the KS test. Now we turn to a more strict selection
+by requiring all the 15 constructed mock surveys to be consistent with
+observations.
+
+%Figure \ref{fig:high_success_rate} shows the number of models that
+%have at least $N_{\rm high-P}$ mocks with $P>0.05$. For each model
+%${\mathcal M}$ there are 15 different mock surveys.  We discard the
+%models that have 14 mocks or less consistent with observations.
+
+With
+this cut we find $\sim 100$ models with all the 15 mock survey
+realizations with $P>0.05$.  This cut represents a reduction by a
+factor of $\sim 6$ with respect to the total number of models with at
+least one consistent mock.
+
+Figure \ref{fig:restriction_mock} presents the locii of these models
+in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
+  min}-f_{\rm occ}$. With this constraints the number of consistent
+models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are reduced. This 
+corresponds to the regions in the parameter space in
+Figure \ref{fig:landscape} that already had a low number of 
+consistent mock surveys. On the other hand, from the right panel in
+Figure \ref{fig:restriction_mock} one can see that the favored
+occupation fraction  values are still in a range $0\leq f_{\rm
+  occ}\leq 1.0$.
+
+We conclude that conditions on the number density statistics, even if they are
+very strict, only put strong constraints on the minimum mass $M_{\rm
+  min}$ but not on the other two parameter of the model $M_{\rm max}$
+and $f_{\rm occ}$.
+
 \subsection{Consistency with the Angular Correlation Function}
 
-\begin{figure*}
+Figure \ref{fig:correlation_parameters} shows the main results for the
+best estimates of $\theta_{0}-\beta$ in the parameterization of the
+ACF. Blue circles represent the results from the mocks and the crosses
+from observations. In the left panel Figure \ref{fig:correlation_parameters} we see
+how the observational ACF measured by \cite{Hayashino2004} 
+can be successful in reducing the total number of possible models. The
+right panel shows the results for fields in the mock catalog with an
+average number density compared against the fit of the data
+reported by \cite{Ouchi2010}. In this case we find that there are
+large uncertainties coming from the observational data, and only a reduced
+fraction of the models can be discarded.
+
+In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
+models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
+both for the comparisons against \cite{Hayashino2004} and
+\cite{Ouchi2010}. To make this selection we consider that
+a model is consistent with observations if there is a $1$-$\sigma$
+overlap between both the correlation length $\theta_0$ and the power
+$\beta$. We clearly see from this Figure that the conditions imposed
+by \cite{Hayashino2004} are the tightest. Comparing this Figure with
+the results shown in Figure \ref{fig:restriction_mock} we see that
+practically all models with $M_{\rm max}>10^{12}$ are removed. On the
+other hand the comparison against \cite{Ouchi2010} does not
+substantially reduce the number of models.
+
+At this point we take the most strict decision to keep 
+models consistent with both observational constraints. This
+reduces the selection to the models already restricted by
+the data in \cite{Hayashino2004} as presented in the lower panels of Figure
+\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
+this comparison is that clustering information is able to put
+meaningful constraints on the values of $M_{\rm max}$. However, the
+possible values for the occupation fraction, despite having a strong correlation
+with $M_{\rm min}$, still are in the initial range $0.1\leq f_{\rm
+  occ}\leq 1$.
+
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{power_law_correlation_maxden.pdf} 
-\hspace{5mm}  
-\includegraphics[width=0.46\linewidth,angle=0]{power_law_correlation_meanden.pdf} 
+\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_meanden.pdf} 
 \end{center}
@@
 correlation function. Blue dots correspond to simulations and the
-green cross to observations by \citet{Hayashino2004} (left) and
-\citet{Ouchi2010} (right). The error bars in the theoretical data correspond
-to the quadratic average of the fitting errors for each mock survey
+green cross to observations by \citet{Ouchi2010} (right). The error
+bars in the theoretical data correspond to the quadratic average of
+the fitting errors for each mock survey 
 \label{fig:correlation_parameters}}
-\end{figure*}
+\end{figure}
+
+\section{Discussion}
 
@@
 
-Figure \ref{fig:correlation_parameters} shows the main results in a
-$\theta_{0}-\beta$  plane where the average and standard deviation
-over the mocks is shown in comparison with the result derived from
-observations. In the left panel Figure \ref{fig:correlation_parameters} we see
-how the observational ACF measured by \cite{Hayashino2004} 
-can be successful in reducing the total number of possible models. The
-right panel shows the results for fields in the mock catalog with an
-average number density compared against the fit of the data
-reported by \cite{Ouchi2010}. In this case we find that there are
-large uncertainties coming from the observational data, and only a reduced
-fraction of the models can be discarded.
-
-In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
-models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
-both for the comparisons against \cite{Hayashino2004} and
-\cite{Ouchi2010}. To make this selection we consider that
-a model is consistent with observations if there is a $1$-$\sigma$
-overlap between both the correlation length $\theta_0$ and the power
-$\beta$. We clearly see from this Figure that the conditions imposed
-by \cite{Hayashino2004} are the tightest. Comparing this Figure with
-the results shown in Figure \ref{fig:restriction_mock} we see that
-practically all models with $M_{\rm max}>10^{12}$ are removed. On the
-other hand the comparison against \cite{Ouchi2010} does not
-substantially reduce the number of models.
-
-At this point we take the most strict decision to keep 
-models consistent with both observational constraints. This
-reduces the selection to the models already restricted by
-the data in \cite{Hayashino2004} as presented in the lower panels of Figure
-\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
-this comparison is that clustering information is able to put
-meaningful constraints on the values of $M_{\rm max}$. However, the
-possible values for the occupation fraction, despite having a strong correlation
-with $M_{\rm min}$, still are in the initial range $0.1\leq f_{\rm
-  occ}\leq 1$.
-
-\section{Discussion}
-
 We end up with $XX$ models, out of $9000$ initial guesses, consistent
@@
 to disfavor the second family of models with high occupation
-fractions. Nevertheless, it remains an open task to explain the narrow
-mass range $\Delta M<0.5$ in most of the models.
+fractions.
 
@@
 measurements in the Extended Chandra Deep Field South has shown that
-the median dark matter masses of h los hosting LAEs is
+the median dark matter masses of halos hosting LAEs is
 $\log_{10}M_{\rm  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding

### 2013-11-19 code/correlation/C_code/correlation.c
angular correlation calculus updated

@@ -10,9 +10,10 @@ int DD_histogram(int N_cat,double X_cat[],double Y_cat[],double histogram_cat[])
   int i,j,w;
   double scale_cat=2.0/(1.0*N_cat*(N_cat-1));
   
-  
+  double ranges=[0.0,3.4,5.0,15.0,40.0,70.0,100.0,180.0,300.0,500.0,800.0]
   hist_theta_cat=gsl_histogram_alloc(THETA_PARTITIONS);
-  gsl_histogram_set_ranges_uniform(hist_theta_cat,THETA_MIN,THETA_MAX);
+  //gsl_histogram_set_ranges_uniform(hist_theta_cat,THETA_MIN,THETA_MAX);
+  gsl_histogram_set_ranges(hist_theta_cat,ranges,11);
   
   for(i=0;i<N_cat;i++)
     {
@@ -51,6 +52,7 @@ int RR_histogram(double histogram_rand[],int random_points,double X[],double Y[]
   
   int i,j,k,w,m;
   double scale_rand=2.0/(1.0*random_points*(random_points-1));
+  
   
   
   hist_theta_rand=gsl_histogram_alloc(THETA_PARTITIONS);

### 2013-11-19 code/correlation/C_code/model_correlation.h

@@ -29,7 +29,7 @@
 #define N_CATS_DR 1
 #define THETA_MIN 0.0 //arcsec
 #define THETA_MAX 1040.0 //arcsec
-#define THETA_PARTITIONS 13
+#define THETA_PARTITIONS 12
 #define D_z 6558.3
 #define H 0.709
 #define PHO_M 3.7e10

### 2013-11-19 code/correlation_statistic.py

@@ -1,41 +1,45 @@
 import numpy as np
 import pylab as P
-import matplotlib.collections as collections
 import matplotlib 
+matplotlib.use('Agg')
+import matplotlib.collections as collections
+
 from scipy import stats
 from scipy import optimize as op
 import sys
 #plot_dir="../paper/plots/"
-plot_dir="../paper/plots/"
+plot_dir="./plots/"
 
 matplotlib.use('pdf')
 #defining the power-law function to fit the correlation function
 powerlaw = lambda x, amp, index: (x/amp)**(index)
-fitfunc = lambda p, x: (x/p[0])**(p[1])
+fitfunc = lambda p, x: (x/p[0])**p[1]
+fit_f= lambda p, x: (x/p[0])**(-0.8)
+err_f= lambda p, x, y,err: (y - fit_f(p, x))/err
 errfunc = lambda p, x, y,err: (y - fitfunc(p, x))/err
 
-pinit = [2.0,-1.0] 
+pinit = [12.0] 
 
 n_models=101
 n_mocks=15
-theta_bins=13
-pro_path="/Users/jemejia/CosmisVarianceLAES/"
+theta_bins=11
+pro_path="/Users/jemejia/CosmicVarianceLAES/"
 
 obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
 obs=np.loadtxt(obs_correlation_file,skiprows=4)
-theta1=obs[0:theta_bins,0]
+#theta1=obs[0:theta_bins,0]
 if(sys.argv[1]=="maxden"):
     obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
-if(sys.argv[1]=="meanden"):
-    obs_correlation_file=pro_path + "data/obs/ouchi2010.txt"
+if(sys.argv[1]=="degree2"):
+     obs_correlation_file=pro_path + "data/obs/ouchi2010.txt"
+     print "hola"
 
-
-obs_correlation=np.loadtxt(obs_correlation_file,skiprows=4)
-theta=obs_correlation[0:theta_bins,0]
-correlation=obs_correlation[0:theta_bins,1]
-std=obs_correlation[0:theta_bins,2]
-out = op.leastsq(errfunc, pinit,args=(theta, correlation,std), full_output=1)
-
[…]

### 2013-11-19 code/model_cat_gen.py

@@ -4,12 +4,12 @@
 import numpy as np
 import pylab as P
 
-field="large"
+field="degree"
 survey_type="match"
 theta_max=1040
 theta_min=0
 theta_bins=13
-pro_path="/home/jemejia/CosmicVarianceLAES/"
+pro_path="/casiopea/jemejia/CosmicVarianceLAES/"
 box_length=250.0
 x_width=46.0
 y_width=35.0
@@ -36,7 +36,7 @@ model_info=np.loadtxt(models_file)
 m_min_m=model_info[:,0] #_m refers to model
 m_max_m=model_info[:,1]
 f_occ_m=model_info[:,2]
-ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_surveys.dat"
+ID_file=pro_path + "data/mock_survey/" + "ID_" + survey_type + "_square_surveys.dat"
 p_values_file= pro_path + "data/mock_survey/" + "p_values_FOF_ID_" + survey_type + "_surveys.dat"
 
 
@@ -103,8 +103,8 @@ for w in range( n_models ):
     #n_mocks=1 #to delete
     for j in range( n_mocks ): 
         
-        ID_ini=j*obs_surveys
-        ID_end=int(ID_ini+obs_surveys)
+        ID_ini=j*4
+        ID_end=int(ID_ini+4)
         m_min=m_min_s[-1]
         m_max=m_max_s[-1]
         f_occ=f_occ_s[-1]
@@ -125,7 +125,7 @@ for w in range( n_models ):
         
     
         if(field=="large"):
-            i_range=7
+            i_range=4
             print "large field"
             
         else:
@@ -178,7 +178,7 @@ for w in range( n_models ):
             
             
         
-        model_catalog_filename=pro_path +  "data/laes/mock_cat/model_"+str(w)+"_mock_"+str(j)+".txt"
+        model_catalog_filename=pro_path +  "data/laes/mock_cat/degree2_"+str(w)+"_mock_"+str(j)+".txt"
     
 
 
@@ -191,7 +191,7 @@ for w in range( n_models ):
         np.savetxt(model_catalog_filename,lae_cat)
         
         
-        
+        """
         
 
         max_density_index=np.argmax(n_laes)
@@ -244,3 +244,4 @@ for w in range( n_models ):
         
         
         np.savetxt(model_catalog_filename,lae_mean)
+        """

### 2013-11-20 paper/ms.tex
new figures in the paper

@@
 best estimates of $\theta_{0}-\beta$ in the parameterization of the
-ACF. Blue circles represent the results from the mocks and the crosses
-from observations. In the left panel Figure \ref{fig:correlation_parameters} we see
-how the observational ACF measured by \cite{Hayashino2004} 
-can be successful in reducing the total number of possible models. The
-right panel shows the results for fields in the mock catalog with an
-average number density compared against the fit of the data
-reported by \cite{Ouchi2010}. In this case we find that there are
-large uncertainties coming from the observational data, and only a reduced
-fraction of the models can be discarded.
-
-In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
+ACF. Blue circles with error bars represent the results from the mocks
+and the horizontal line the result from observations reported by
+\cite{Ouchi2010} over a field with average number density. The
+observational result does not have an uncertainty associated with
+$\beta$ because the parameter was fixed in the fit. Only $40$ models
+are consistent with the new constraints.
+
+Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
 models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_meanden.pdf} 
+\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
 \end{center}
@@
 correlation function. Blue dots correspond to simulations and the
-green cross to observations by \citet{Ouchi2010} (right). The error
+green cross to observations by \citet{Ouchi2010} . The error
 bars in the theoretical data correspond to the quadratic average of
-the fitting errors for each mock survey 
-\label{fig:correlation_parameters}}
+the fitting errors for each mock
+survey \label{fig:correlation_parameters}} 
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_mass.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_f_occ.pdf}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_mass.pdf}
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_f_occ.pdf}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
 \end{center}
@@
    constraints on the maximal number of consistent mocks and the
-  angular correlation function. Upper panels correspond
-  checks the consistency with the observational data of
-  \citet{Ouchi2010}. Lower panels show results after comparison
-  against \citet{Hayashino2004}
+  angular correlation function. The observational data correspods to
+  \citet{Ouchi2010}.   
   \label{fig:restriction_mock_and_f_occ_corr}} 
@@
 $\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
-10.1 &10.2 & 0.1 & 0.1\\
-10.3 &10.5 & 0.1 & 0.2\\
-10.4 &10.7 & 0.1 & 0.3\\
-10.5 &10.6 & 0.3 & 0.1\\
-10.5 &10.9 & 0.1 & 0.4\\
-10.5 &11.0 & 0.1 & 0.5\\
-10.6 &11.2 & 0.1 & 0.6\\
-10.6 &11.4 & 0.1 & 0.8\\
-10.6 &11.7 & 0.1 & 1.1\\
-10.7 &11.0 & 0.2 & 0.3\\
-10.8 &11.2 & 0.2 & 0.4\\
-10.8 &11.3 & 0.2 & 0.5\\\hline
+10.4 &10.7 & 0.1\\
+ 10.5 &10.6 & 0.3\\
+ 10.5 &10.9 & 0.1\\
+ 10.5 &11.0 & 0.1\\
+ 10.6 &10.8 & 0.2\\
+ 10.6 &11.2 & 0.1\\
+ 10.6 &11.3 & 0.1\\
+ 10.6 &11.4 & 0.1\\
+ 10.6 &11.5 & 0.1\\
+ 10.6 &11.6 & 0.1\\
+ 10.6 &11.7 & 0.1\\
+ 10.7 &11.0 & 0.2\\
+ 10.8 &11.2 & 0.2\\
+ 10.8 &11.3 & 0.2\\
+ 10.8 &11.4 & 0.2\\
+ 10.9 &11.3 & 0.3\\
+ 10.9 &11.7 & 0.2\\
+ 10.9 &11.8 & 0.2\\
+ 10.9 &11.9 & 0.2\\
+ 10.9 &12.0 & 0.2\\
+ 10.9 &12.1 & 0.2\\
+ 10.9 &12.2 & 0.2\\
+ 10.9 &12.3 & 0.2\\
+ 10.9 &12.6 & 0.2\\
+ 10.9 &12.8 & 0.2\\\hline
 \end{tabular}
@@
 $\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
-10.6 &10.7 &0.4 & 0.1\\
-10.8 &10.9 &0.6 & 0.1\\
-10.8 &11.0 &0.4 & 0.2\\
-10.9 &11.0 &0.8 & 0.1\\
-10.9 &11.0 &0.9 & 0.1\\
-10.9 &11.1 &0.5 & 0.2\\
-11.0 &11.1 &1.0 & 0.1\\
-11.1 &11.3 &0.8 & 0.2\\
-11.2 &11.6 &0.6 & 0.4\\
-11.2 &12.2 &0.5 & 1.0\\
-11.3 &11.7 &0.9 & 0.4\\\hline
+10.6 &10.700 & 0.4\\
+ 10.7 &10.8 & 0.5\\
+ 10.8 &10.9 & 0.6\\
+ 10.8 &11.0 & 0.4\\
+ 10.9 &11.0 & 0.8\\
+ 10.9 &11.0 & 0.9\\
+ 10.9 &11.1 & 0.5\\
+ 11.0 &11.1 & 1.0\\
+ 11.0 &11.2 & 0.6\\
+ 11.0 &11.4 & 0.4\\
+ 11.1 &11.3 & 0.7\\
+ 11.1 &11.3 & 0.8\\
+ 11.1 &11.4 & 0.6\\
+ 11.2 &11.4 & 0.9\\
+ 11.2 &11.4 & 1.0\\\hline
 \end{tabular}

### 2013-11-20 paper/ms.tex
continue editing of the results section

@@
 
-Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
-models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
-both for the comparisons against \cite{Hayashino2004} and
-\cite{Ouchi2010}. To make this selection we consider that
+Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the selected models
+models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm
+  min}$-$f_{\rm occ}$. To make this selection we consider that
 a model is consistent with observations if there is a $1$-$\sigma$
 overlap between both the correlation length $\theta_0$ and the power
-$\beta$. We clearly see from this Figure that the conditions imposed
-by \cite{Hayashino2004} are the tightest. Comparing this Figure with
-the results shown in Figure \ref{fig:restriction_mock} we see that
-practically all models with $M_{\rm max}>10^{12}$ are removed. On the
-other hand the comparison against \cite{Ouchi2010} does not
-substantially reduce the number of models.
-
-At this point we take the most strict decision to keep 
-models consistent with both observational constraints. This
-reduces the selection to the models already restricted by
-the data in \cite{Hayashino2004} as presented in the lower panels of Figure
-\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
-this comparison is that clustering information is able to put
-meaningful constraints on the values of $M_{\rm max}$. However, the
-possible values for the occupation fraction, despite having a strong correlation
-with $M_{\rm min}$, still are in the initial range $0.1\leq f_{\rm
-  occ}\leq 1$.
+$\beta$. Comparing this Figure
+\ref{fig:restriction_mock_and_f_occ_corr} with the results shown in Figure
+\ref{fig:restriction_mock} we see that the new constraint disfavors
+practically all models with $M_{\rm max}>10^{12}$.
+
+Our main conclusions after this comparison is that clustering
+information is able to put meaningful constraints on the values of
+$M_{\rm max}$. However, the possible values for the occupation
+fraction, despite having a strong correlation with $M_{\rm min}$
+remain unconstrained.
 
@@
 $\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
-10.4 &10.7 & 0.1\\
- 10.5 &10.6 & 0.3\\
- 10.5 &10.9 & 0.1\\
- 10.5 &11.0 & 0.1\\
- 10.6 &10.8 & 0.2\\
- 10.6 &11.2 & 0.1\\
- 10.6 &11.3 & 0.1\\
- 10.6 &11.4 & 0.1\\
- 10.6 &11.5 & 0.1\\
- 10.6 &11.6 & 0.1\\
- 10.6 &11.7 & 0.1\\
- 10.7 &11.0 & 0.2\\
- 10.8 &11.2 & 0.2\\
- 10.8 &11.3 & 0.2\\
- 10.8 &11.4 & 0.2\\
- 10.9 &11.3 & 0.3\\
- 10.9 &11.7 & 0.2\\
- 10.9 &11.8 & 0.2\\
- 10.9 &11.9 & 0.2\\
- 10.9 &12.0 & 0.2\\
- 10.9 &12.1 & 0.2\\
- 10.9 &12.2 & 0.2\\
- 10.9 &12.3 & 0.2\\
- 10.9 &12.6 & 0.2\\
- 10.9 &12.8 & 0.2\\\hline
+ 10.4 &10.7 & 0.1& 0.3 \\
+ 10.5 &10.9 & 0.1& 0.4 \\
+ 10.5 &11.0 & 0.1& 0.5 \\
+ 10.6 &10.8 & 0.2& 0.2 \\
+ 10.6 &11.2 & 0.1& 0.6 \\
+ 10.6 &11.3 & 0.1& 0.7 \\
+ 10.6 &11.4 & 0.1& 0.8 \\
+ 10.6 &11.5 & 0.1& 0.9 \\
+ 10.6 &11.6 & 0.1& 1 \\
+ 10.6 &11.7 & 0.1& 1.1 \\
+ 10.7 &11.0 & 0.2& 0.3 \\
+ 10.8 &11.2 & 0.2& 0.4 \\
+ 10.8 &11.3 & 0.2& 0.5 \\
+ 10.8 &11.4 & 0.2& 0.6 \\
+ 10.9 &11.7 & 0.2& 0.8 \\
+ 10.9 &11.8 & 0.2& 0.9 \\
+ 10.9 &11.9 & 0.2& 1 \\
+ 10.9 &12.0 & 0.2& 1.1 \\
+ 10.9 &12.1 & 0.2& 1.2 \\
+ 10.9 &12.2 & 0.2& 1.3 \\
+ 10.9 &12.3 & 0.2& 1.4 \\
+ 10.9 &12.6 & 0.2& 1.7 \\
+ 10.9 &12.8 & 0.2& 1.9 \\\hline
 \end{tabular}
@@
 $\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
-10.6 &10.700 & 0.4\\
- 10.7 &10.8 & 0.5\\
- 10.8 &10.9 & 0.6\\
- 10.8 &11.0 & 0.4\\
- 10.9 &11.0 & 0.8\\
- 10.9 &11.0 & 0.9\\
- 10.9 &11.1 & 0.5\\
- 11.0 &11.1 & 1.0\\
- 11.0 &11.2 & 0.6\\
- 11.0 &11.4 & 0.4\\
- 11.1 &11.3 & 0.7\\
- 11.1 &11.3 & 0.8\\
- 11.1 &11.4 & 0.6\\
- 11.2 &11.4 & 0.9\\
- 11.2 &11.4 & 1.0\\\hline
+ 10.5 &10.6 & 0.3 & 0.1 \\
+ 10.6 &10.7 & 0.4 & 0.1 \\
+ 10.7 &10.8 & 0.5 & 0.1 \\
+ 10.8 &10.9 & 0.6 & 0.1 \\
+ 10.8 &11.0 & 0.4 & 0.2 \\
+ 10.9 &11.0 & 0.8 & 0.1 \\
+ 10.9 &11.0 & 0.9 & 0.1 \\
+ 10.9 &11.1 & 0.5 & 0.2 \\
+ 10.9 &11.3 & 0.3 & 0.4 \\
+ 11.0 &11.1 & 1.0 & 0.1 \\
+ 11.0 &11.2 & 0.6 & 0.2 \\
+ 11.0 &11.4 & 0.4 & 0.4 \\
+ 11.1 &11.3 & 0.7 & 0.2 \\
+ 11.1 &11.3 & 0.8 & 0.2 \\
+ 11.1 &11.4 & 0.6 & 0.3 \\
+ 11.2 &11.4 & 0.9 & 0.2 \\
+ 11.2 &11.4 & 1.0 & 0.2 \\\hline
 \end{tabular}
@@
 \caption{\label{table:secondfamily}List of parameters for the second
-  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and high occupation fraction $f_{\rm occ}>0.3$.}
+  family of models. Narrow mass range $\Delta M\leq 0.4 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
 \end{table}

### 2013-12-11 paper/ms.tex
new small changes

@@
 Figure \ref{fig:correlation_parameters} shows the main results for the
-best estimates of $\theta_{0}-\beta$ in the parameterization of the
-ACF. Blue circles with error bars represent the results from the mocks
-and the horizontal line the result from observations reported by
-\cite{Ouchi2010} over a field with average number density. The
-observational result does not have an uncertainty associated with
-$\beta$ because the parameter was fixed in the fit. Only $40$ models
-are consistent with the new constraints.
+best estimates of $\theta_{0}-\beta$  used in the ACF parameterization. 
+Blue circles with error bars represent the theoretical results
+and the horizontal line the observations by \cite{Ouchi2010} over a
+field with average number density. The  observational result does not
+have an uncertainty associated with $\beta$ because the parameter was
+fixed in the fit.
 
@@
 overlap between both the correlation length $\theta_0$ and the power
-$\beta$. Comparing this Figure
-\ref{fig:restriction_mock_and_f_occ_corr} with the results shown in Figure
+$\beta$.  We find that $40$ models are consistent with the ACF
+constraints.
+
+Comparing Figure
+\ref{fig:restriction_mock_and_f_occ_corr} with Figure
 \ref{fig:restriction_mock} we see that the new constraint disfavors
-practically all models with $M_{\rm max}>10^{12}$.
-
-Our main conclusions after this comparison is that clustering
-information is able to put meaningful constraints on the values of
-$M_{\rm max}$. However, the possible values for the occupation
-fraction, despite having a strong correlation with $M_{\rm min}$
-remain unconstrained.
+almost all models with $M_{\rm max}>10^{12}$. The only exception is 
+a narrow range of models with $M_{\rm min}=10^{10.9}$, however, we
+have verified that these models are only marginally consistent witht
+the ACF constraints in the $\theta_0$-$\beta$ plane.
+
+From this comparison we conclude that clustering  information is able
+to put meaningful constraints on the values of $M_{\rm max}$, but not
+on he occupation fraction.
 

### 2013-12-11 paper/ms.tex
updated discussion

@@
 correlation function. Blue dots correspond to simulations and the
-green cross to observations by \citet{Ouchi2010} . The error
+green line to observations by \citet{Ouchi2010}. The error
 bars in the theoretical data correspond to the quadratic average of
@@
 
-We end up with $XX$ models, out of $9000$ initial guesses, consistent
-with observations. In order to discuss these results we now
-define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
-\log_{10}M_{\rm  min}$, to use it together with the occupation
-fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ to
-classify all the successful models into two families:
+We end up with $40$ consistent models, out of the initial set of
+$9000$. To facilitate the discussion of these results we define a new
+quantity, the halo mass range $\Delta M=\log_{10}M_{\rm max} -
+\log_{10}M_{\rm  min}$. This quantity together with the occupation
+fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ allows us
+to clasify all the successful models into three families:
 
 \begin{itemize}
-\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
-  dex: XX models. 
-\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
-  low $\Delta M\leq 1.0$: XX models 
+\item[(1)] Low $f_{\rm occ}\leq 0.2$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
+  dex: 16 models. 
+\item[(2)] High $f_{\rm occ}> 0.2$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
+  low $\Delta M\leq 1.0$: 17 models
+
+\item[(3)] Models with low occupation $f_{\rm occ}\leq 0.2$ fraction
+  and high $\Delta M>1.0$: 7 models
 \end{itemize}
-%
-A complete parameter list is presented in Table
-\ref{table:firstfamily} and Table \ref{table:secondfamily}. There are
-two interesting feature in these families. First, the occupation
-fraction can take any value from $0.1$ to $1.0$. Second, the halos
-hosting LAEs all have a narrow mass range $\Delta M\leq 1.0$.
+
+{\bf The models in the third family are barely consistent with the
+  constraints from the ACF. They have mean values of $\theta_0$
+  outside the observational uncertainties in that parameter, but have
+  been included as consistent because their error bars overlap. These
+models they have another particular feature: their minimum mass is
+$M_{\rm min}=10^{10.9}\hMsun$. In what follows we exclude these models
+from the discussion.}
+
+A complete parameter list for the three families is presented in Table
+\ref{table:firstfamily}, Table \ref{table:secondfamily} and Table
+\ref{table:thirdfamily}. There are two interesting feature in these
+families. First, the occupation fraction can take any value from $0.1$
+to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
+$\Delta M\leq 1.0$.
 
@@
  10.6 &11.6 & 0.1& 1 \\
- 10.6 &11.7 & 0.1& 1.1 \\
  10.7 &11.0 & 0.2& 0.3 \\
@@
  10.8 &11.4 & 0.2& 0.6 \\
+ 10.9 &11.9 & 0.2& 1.0 \\
  10.9 &11.7 & 0.2& 0.8 \\
- 10.9 &11.8 & 0.2& 0.9 \\
- 10.9 &11.9 & 0.2& 1 \\
- 10.9 &12.0 & 0.2& 1.1 \\
- 10.9 &12.1 & 0.2& 1.2 \\
- 10.9 &12.2 & 0.2& 1.3 \\
- 10.9 &12.3 & 0.2& 1.4 \\
- 10.9 &12.6 & 0.2& 1.7 \\
- 10.9 &12.8 & 0.2& 1.9 \\\hline
+ 10.9 &11.8 & 0.2& 0.9 \\\hline
 \end{tabular}
 \end{center}
-\caption{\label{table:firstfamily}List of parameters for the first
+\caption{\label{table:firstfamily}
+List of parameters for the first
   family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{cccc}\hline\hline
+$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
+ 10.6 &11.7 & 0.1& 1.1 \\
+ 10.9 &12.0 & 0.2& 1.1 \\
+ 10.9 &12.1 & 0.2& 1.2 \\
+ 10.9 &12.2 & 0.2& 1.3 \\
+ 10.9 &12.3 & 0.2& 1.4 \\
+ 10.9 &12.6 & 0.2& 1.7 \\
+ 10.9 &12.8 & 0.2& 1.9 \\\hline
+\end{tabular}
+\end{center}
+\caption{\label{table:thirdfamily}List of parameters for the third
+  family of models. Wide mass range $\Delta M> 1.0$ dex and low
+  occupation fraction $f_{\rm occ}\leq 0.2$.} 
+\end{table}
+
 \subsection{In the context of abundance matching models}

### 2013-12-29 paper/ms.tex
minor edits

@@
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.95\linewidth,angle=0]{Fig4_match_P5.pdf}
-%\end{center} 
-%\caption{ Number of models with at least $N_{\rm high-P}$ mock surveys
-%  consistent with the observed surface number density
-%  distribution in terms of the KS-test values $P>0.05$. Only $\sim
-%  100$ models have all their mocks consistent with observations. 
-%  \label{fig:high_success_rate}.}  
-%\end{figure}
-
 \subsection{Models with the largest number of consistent mock surveys}
@@
 
-%Figure \ref{fig:high_success_rate} shows the number of models that
-%have at least $N_{\rm high-P}$ mocks with $P>0.05$. For each model
-%${\mathcal M}$ there are 15 different mock surveys.  We discard the
-%models that have 14 mocks or less consistent with observations.
-
 With
@@
 
-Figure \ref{fig:correlation_parameters} shows the main results for the
-best estimates of $\theta_{0}-\beta$  used in the ACF parameterization. 
-Blue circles with error bars represent the theoretical results
-and the horizontal line the observations by \cite{Ouchi2010} over a
-field with average number density. The  observational result does not
-have an uncertainty associated with $\beta$ because the parameter was
-fixed in the fit.
-
-Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the selected models
-models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm
-  min}$-$f_{\rm occ}$. To make this selection we consider that
-a model is consistent with observations if there is a $1$-$\sigma$
-overlap between both the correlation length $\theta_0$ and the power
-$\beta$.  We find that $40$ models are consistent with the ACF
-constraints.
+Figure \ref{fig:correlation_parameters} shows the results for the
+best estimates of $\theta_{0}$-$\beta$  used in the ACF
+parameterization.  Blue circles with error bars represent the results
+from the mocks and the horizontal line the obsrvational results of
+\cite{Ouchi2010} over a field with average number density where the
+$\beta$ parameter was fiexed in the fit. From this Figure we observe
+that there are models that can be ruled out as inconsistent with the
+angular correlation function.
+
+Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
+remainingn consistent models in the planes $M_{\rm min}$-$M_{\rm
+  max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
+observations if there is a $1$-$\sigma$ overlap between both the
+correlation length $\theta_0$ and the power $\beta$.  We find that
+we end up with $40$ models consistent with the ACF constraints.
 
@@
 almost all models with $M_{\rm max}>10^{12}$. The only exception is 
-a narrow range of models with $M_{\rm min}=10^{10.9}$, however, we
-have verified that these models are only marginally consistent witht
+a narrow range of models with $M_{\rm min}=10^{10.9}$. However, we
+have verified that these models are only marginally consistent with
 the ACF constraints in the $\theta_0$-$\beta$ plane.
 
-From this comparison we conclude that clustering  information is able
-to put meaningful constraints on the values of $M_{\rm max}$, but not
-on he occupation fraction.
+From this comparison we conclude that clustering information can
+constraint the values of $M_{\rm max}$, but not the occupation
+fraction.
 

### 2013-12-29 paper/ms.tex
discussion section edited

@@
 
-We end up with $40$ consistent models, out of the initial set of
-$9000$. To facilitate the discussion of these results we define a new
-quantity, the halo mass range $\Delta M=\log_{10}M_{\rm max} -
-\log_{10}M_{\rm  min}$. This quantity together with the occupation
-fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ allows us
-to clasify all the successful models into three families:
+Out of the initial set of $9000$ models we end up with $40$ that are
+consistent with the observational constraints. To facilitate the
+discussion of these models we define a new quantity, the halo mass
+range $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
+together with the occupation fraction, $f_{\rm occ}$, and the minimum
+mass $M_{\rm min}$ allows us to clasify all the successful models into
+three families:
 
 \begin{itemize}
-\item[(1)] Low $f_{\rm occ}\leq 0.2$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
+\item[(1)] Low occupation fraction $f_{\rm occ}\leq 0.2$ and narrow
+  mass range $\Delta M\leq 1.0$ 
   dex: 16 models. 
-\item[(2)] High $f_{\rm occ}> 0.2$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
-  low $\Delta M\leq 1.0$: 17 models
-
-\item[(3)] Models with low occupation $f_{\rm occ}\leq 0.2$ fraction
-  and high $\Delta M>1.0$: 7 models
+\item[(2)] High occupation fraction $f_{\rm occ}> 0.2$ and
+  narrow mass range $\Delta M\leq 1.0$: 17 models 
+\item[(3)] Low occupation fraction $f_{\rm occ}\leq 0.2$ 
+  and wide mass range $\Delta M>1.0$: 7 models
 \end{itemize}
+
+A complete parameter list for the three families is presented in Tables
+\ref{table:firstfamily}, \ref{table:secondfamily}  and 
+\ref{table:thirdfamily}.
 
@@
   constraints from the ACF. They have mean values of $\theta_0$
-  outside the observational uncertainties in that parameter, but have
-  been included as consistent because their error bars overlap. These
+  outside the observational uncertainties, but have
+  are considered as consistent because their error bars overlap. These
   models they have another particular feature: their minimum mass is
-$M_{\rm min}=10^{10.9}\hMsun$. In what follows we exclude these models
-from the discussion.}
-
-A complete parameter list for the three families is presented in Table
-\ref{table:firstfamily}, Table \ref{table:secondfamily} and Table
-\ref{table:thirdfamily}. There are two interesting feature in these
+  exactly $M_{\rm min}=10^{10.9}\hMsun$. Because these models are
+  are barely compatible with observations and are a minority of the
+  consisten models, we exclude them now from the discussion.}
+
+There are two interesting feature in the remaining two first
 families. First, the occupation fraction can take any value from $0.1$
@@
 {\bf The existence of models with high occupation fractions $f_{\rm
-    occ}>0.3$ is unexpected from previous clustering analysis that do
+    occ}>0.2$ is unexpected from previous clustering analysis that do
   not take  account the effect of cosmic variance in the same way we
-  propose in this \documentname. It seems that taking explicitly into
-  account  effect hinders the possibility of constraining the LAEs
+  propose in this \documentname. This suggests that taking explicitly
+  cosmic variance into account hinders the possibility of constraining the LAEs
   occupation fraction.}
 
-{\bf This challenge can be tracked to the uncertainty in the minimum
-  halo mass. Within out framework, high occupation fraction are
-  allowed because there are models where the minimum mass for hosting
-  observable LAEs is larger than $10^{10.8}$\hMsun, which are fully
-  consistent with the observational constraints.}
-
-{\bf On the other hand, a robust conclusion is that all
-possible models have narrow mass range regardless of the occupation
-fraction.}
-
-...A cut at the low mass end, $M_{\rm min}$, can be
+\subsection{Physical interpretations}
+
+{\bf The occupation fraction is midly correlated with a model's
+  minimum mass. As can be observed in the right panel of Figure 6, the
+  majority of  models with a high occupation fraction have  a minimum
+  mass $M_{\rm  min}> 10^{10.7}$\hMsun. Therefore, low values for the
+  occupation fraction would be favored if one could rule out models
+  with a minimum mass above that threshold.}
+
+{\bf On the other hand, a robust conclusion from the two first families
+  is that the possible models have a narrow halo mass range $\Delta M
+  <1.0$. How can we give a physical interpretation to the existence of
+a narrow mass range? We can start with a reasonable assumption of star
+formation rate increases with halo's mass. In this way a narrow
+$\Delta M$ implies a cut both at the low and high mass end. }
+
+A cut at the low mass end, $M_{\rm min}$, can be
 interpreted in terms of the minimal halo star formation rate needed to
 produce the \ly luminosity needed to be above a given detection
-threshold.  However, under the reasonable assumption of star formation
-rate increasing with halo mass, the cut at higher halo masses $M_{\rm
-  max}$requires a different justification. There are two complementary physical
+threshold.   A cut at higher halo masses $M_{\rm  max}$ requires a
+different justification. There are two complementary physical
 scenarios that could provide it.
@@
 
-\subsection{Comparison against results from galaxy surveys}
-
-Theoretical interpretations of blind galaxy surveys at $z=2.2$ find a
-volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
-\cite{Hayes2010}, similar results are obtained in a recent theoretical
-study of observational data in a wide redshift range $0<z<6$
-\citep{Dijkstra2013}.
-
-\cite{Hayes2010} showed that the luminosity function for
-LAEs at $z=2.2$ is consistent with the escape fraction being constant
-for every galaxy regardless of its luminosity. From this results they
-derive that almost $90\%$ of the star forming galaxies emit insufficient
-Lyman $\alpha$ to be detected, effectively setting the occupation
-fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} use similar
-methods to find an average \ly escape fraction in high-z galaxies,
-they conclude that there is a range in \ly luminosity where the escape
-fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
-be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$. We
-consider a success that our model indeed includes such low occupation
-fraction models. The observational evidence from galaxy surveys seem
-to disfavor the second family of models with high occupation
-fractions.
-
 \subsection{Comparison to other clustering estimates}
@@
 also required consistency with ACF measurements. These expectations
-are matched by the first family of models, also summarized in Table
-\ref{table:firstfamily}. These models, which favor only the very
+are {\bf mostly} matched by the first family of models, also summarized in Table
+\ref{table:firstfamily}. These models, which favor only the 
 low occupations fractions, are also consistent in that regards with
@@
 host halo mass range together with the escape fraction. This allows us
-to demonstrate that the halo mass range can in some cases be narrow $\Delta M <
+to show that the halo mass range can, in some cases, be narrow $\Delta M <
 0.3$dex, something that cannot be inferred from ACF analysis alone.
@@
   family of models. Wide mass range $\Delta M> 1.0$ dex and low
-  occupation fraction $f_{\rm occ}\leq 0.2$.} 
+  occupation fraction $f_{\rm occ}\leq 0.2$. {\bf These models are barely
+  consistent with the constraints from the Angular Correlation
+  Function and have been excluded from the main discussion.}} 
 \end{table}

### 2013-12-31 paper/ms.tex
new full version

@@
 $M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
-10^{11.5}\hMsun$.  We also find that all models have a narrow mass
+10^{11.5}\hMsun$.  We also find that the consistent models have a narrow mass
 range $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$
@@
 
-With
-this cut we find $\sim 100$ models with all the 15 mock survey
+With this cut we find $\sim 100$ models with all the 15 mock survey
 realizations with $P>0.05$.  This cut represents a reduction by a
@@
 in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
-  min}-f_{\rm occ}$. With this constraints the number of consistent
+  min}-f_{\rm occ}$. With this constraint the number of consistent
 models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are reduced. This 
@@
 consistent mock surveys. On the other hand, from the right panel in
-Figure \ref{fig:restriction_mock} one can see that the favored
-occupation fraction  values are still in a range $0\leq f_{\rm
-  occ}\leq 1.0$.
+Figure \ref{fig:restriction_mock} we see that the favored occupation
+fraction  still remain unconstrained $0\leq f_{\rm  occ}\leq 1.0$.
 
@@
 \cite{Ouchi2010} over a field with average number density where the
-$\beta$ parameter was fiexed in the fit. From this Figure we observe
-that there are models that can be ruled out as inconsistent with the
-angular correlation function.
+$\beta$ parameter was fixed in the fit. From this Figure we observe
+that there are models with too large values of $\theta_0$ and $\beta$
+that can be ruled out as inconsistent with the angular correlation
+function.
 
 Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
-remainingn consistent models in the planes $M_{\rm min}$-$M_{\rm
+remaining consistent models in the planes $M_{\rm min}$-$M_{\rm
   max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
 observations if there is a $1$-$\sigma$ overlap between both the
-correlation length $\theta_0$ and the power $\beta$.  We find that
+correlation length $\theta_0$ and the exponent $\beta$.  We find that
 we end up with $40$ models consistent with the ACF constraints.
@@
 \section{Discussion}
+\label{sec:discussion}
 
@@
   outside the observational uncertainties, but have
-  are considered as consistent because their error bars overlap. These
+  are considered as consistent because their large error barsoverlap. These
   models they have another particular feature: their minimum mass is
@@
   are barely compatible with observations and are a minority of the
-  consisten models, we exclude them now from the discussion.}
-
-There are two interesting feature in the remaining two first
+  consistent models, we exclude them from the rest of the discussion.}
+
+\subsection{Two relevant features}
+There are two interesting features in the remaining two first
 families. First, the occupation fraction can take any value from $0.1$
@@
   not take  account the effect of cosmic variance in the same way we
-  propose in this \documentname. This suggests that taking explicitly
-  cosmic variance into account hinders the possibility of constraining the LAEs
-  occupation fraction.}
-
-\subsection{Physical interpretations}
-
-{\bf The occupation fraction is midly correlated with a model's
-  minimum mass. As can be observed in the right panel of Figure 6, the
-  majority of  models with a high occupation fraction have  a minimum
-  mass $M_{\rm  min}> 10^{10.7}$\hMsun. Therefore, low values for the
-  occupation fraction would be favored if one could rule out models
-  with a minimum mass above that threshold.}
-
-{\bf On the other hand, a robust conclusion from the two first families
-  is that the possible models have a narrow halo mass range $\Delta M
-  <1.0$. How can we give a physical interpretation to the existence of
-a narrow mass range? We can start with a reasonable assumption of star
-formation rate increases with halo's mass. In this way a narrow
-$\Delta M$ implies a cut both at the low and high mass end. }
-
-A cut at the low mass end, $M_{\rm min}$, can be
-interpreted in terms of the minimal halo star formation rate needed to
-produce the \ly luminosity needed to be above a given detection
-threshold.   A cut at higher halo masses $M_{\rm  max}$ requires a
+  propose in this \documentname. Nevertheless, the mass range
+  predicted by our models is consistent with already published
+  observational results. This suggests that taking explicitly cosmic
+  variance into account hinders the possibility of constraining the
+  LAEs occupation fraction.}
+
+{\bf Concerning the narrow mass range $\Delta M
+  <1.0$ the question arises of how can we give a physical
+  interpretation for the existence of such  a narrow mass range. We
+  can start with a reasonable   assumption. Namely that star formation
+  rate increases with halo's  mass.}
+
+Under this assumption the cut at the low mass end, $M_{\rm min}$, can be
+interpreted in terms of the minimal star formation rate required to
+produce a \ly luminosity above observational detection thresholds.  
+A cut at higher halo masses $M_{\rm  max}$ requires a
 different justification. There are two complementary physical
-scenarios that could provide it.
+scenarios that could provide
 
@@
 support the idea that massive galaxies with higher metallicities have
-larger dust contents and less concentrated ISM than lower mass
+larger dust contents and a less concentrated ISM than lower mass
 systems. Due to the resonant nature of the \ly line the probability of
@@
 approximation a reasonable one. Therefore we conclude that including
-the effect of satellite galaxies won't change the main results
+the effect of satellite galaxies does not change the main results
 reported in this \documentname.
@@
 The second caveat are the precise values for the mass intervals. These
-values are defined from the halos defined in using the FOF halo
+values are quoted from halos defined using a FOF halo
 finder. Different halo finders and definitions for the detection
-density threshold can yield different masses up to a factor. For
+density threshold can yield different masses up to a factor $\sim 2$\citep{More2011}. For 
 instance a Friends-of-Friends algorithm with linking length $l=0.20$
@@
 following a simple recipe to assign a single LAE to each halo. Only
-a fraction $f_{\rm occ}$ of halos with a mass range  $M_{\rm
-  min}<M_{\rm h}<M_{\rm   max}$ can host a LAE. We proceed with a
+a fraction $f_{\rm occ}$ of halos within a mass range  $M_{\rm
+  min}<M_{\rm h}<M_{\rm   max}$ can host a LAE.
+
+We then proceed with a
 thorough exploration of the space of free parameters $M_{\rm min},
@@
 angular correlation function. Out of the initial $9000$ 
-combinations of parameters in the model we find $23$ arrangements
+combinations of parameters in the model we find $40$ combination of parameters
 consistent with observations.
 
-We find that the observational information we use is insufficient to
-impose a tight constraint on the escape fraction. On the other hand
-the minimum mass and maximum mass are tightly constrained as follows
-$M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
-10^{11.5}\hMsun$. Furthermore, we find that the mass range defined as
+We find that {\bf the information for the number density constrains
+  the minium mass to the range
+  $10^{10}\hMsun < M_{\rm min} < 10^{11.5}\hMsun$ while the clustering
+  constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
+  this is insufficient to impose a tight constraint  on the escape
+  fraction.} Furthermore, we find that the mass range defined as
 $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is always
@@
 
-The wide range in solutions is facilitated by the large dispersion in
-the statistics derived from the mocks. Nevertheless, all the halo mass
-ranges and occupation fractions deduced previous analysis
-\citep[i.e.][]{Gawiser2007,Ouchi2010} are a subset of the models we
-find in this \documentname. All of our models support the notion that
-the most massive halos at $z=3.1$ do not host the brightest LAEs.
-
-The existence of a narrow mass range for halos hosting LAEs, $\Delta
-M\leq 1.0$ dex, has two different explanations at least. The
-first is having LAEs with a decreasing \ly escape fraction with
-increasing mass, the second is having larger screening effects by
-neutral Hydrogen around the most massive systems
-\citep{Laursen2009,ForeroRomero2011}.
-
-However, there are extreme cases with a very narrow $\Delta M<0.3$, meaning that
+The wide range in values for the escape fraction is allowed by the
+large dispersion in the statistics derived from the
+mocks. This uncertainty is unexpected from previous studies that
+unanimously favor low values for the occupation
+fractions \citep[i.e.][]{Gawiser2007,Ouchi2010}. Nevertheless, all the
+halo mass ranges and occupation fractions deduced previous analysis
+are a subset of the models we find in this \documentname.
+
+All of our preferred models support the notion that the most massive
+halos at $z=3.1$ do not host detectable LAEs. The existence of a
+narrow mass range for halos hosting LAEs, $\Delta  M\leq 1.0$ dex, has
+two different explanations at least. The first is having LAEs with a
+decreasing \ly escape fraction with increasing mass, the second is
+having larger screening effects by neutral Hydrogen around the most
+massive systems \citep{Laursen2009,ForeroRomero2011}.
+
+We also find extreme cases with a very narrow $\Delta M<0.3$, meaning that
 there is barely a factor of $\sim 2$ between the minimum and halo
-mass. If these models turn out to be confirmed, this would be a great
+mass. If these models can be confirmed, it would mean a great
 challenge for galaxy formation models to explain how is that LAEs can
@@
 
-In summary, we show how spatial information of LAEs cannot
-put a tight constraint on their host halos and occupation fraction. We
-foresee that the new observations with new instruments (such as MUSE,
-Hyper SuprimeCam and HETDEX) covering larger fields and a wider range
-of luminosities will be key in imposing tighter constraints on the
-properties of dark matter halos hosting LAEs. At the same time,
-additional modeling for \ly radiation transfer , is needed to put a
+In summary, we show that {\bf the currently available spatial information of LAEs cannot
+put a tight constraint on their occupation fraction of dark matter
+halos}. This information can confidently be used to stablish that
+these galaxies are hosted in low mass halos with masses within a range
+spanning less than a factor of ten. We foresee that the new
+observations with new instruments (such as MUSE, Hyper SuprimeCam and
+HETDEX) covering larger fields and a wider range of luminosities will
+be key in reducing cosmic variance and imposing tighter constraints on
+the properties of dark matter halos hosting LAEs. At the same time,
+additional modeling for \ly radiation transfer is needed to put a
 tighter constrain on the \ly escape fraction in high redshift
-galaxies, also paying attention to newly framed physical phenomena, such as the
-stochasticity \citep{ForeroRomero2013} in the star formation process,
-which might play a role in inducing detection biases in high redshift LAEs.
+galaxies, also paying attention to newly framed physical phenomena,
+such as the stochasticity \citep{ForeroRomero2013} in the star
+formation process, which might play a role in inducing detection
+biases in high redshift LAEs.
 

### 2013-12-31 paper/ms.tex
fixed typos

@@
   emitters at $z\sim 3$}      
-\author[~J.~E. Forero-Romero and ~J.~E. Mejia-Restreo]{
+\author[~J.~E. Forero-Romero and ~J.~E. Mejia-Restrepo]{
 \parbox[t]{\textwidth}{\raggedright 
@@
 the connection between dark matter, star formation and the escape of
-\ly radiation. That kind of modelling should also be able to provide a
+\ly radiation. That kind of modeling should also be able to provide a
 plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
@@
 Capitalizing LAEs observations requires an understanding of
-their place in the context of a given structure formarion model in a
+their place in the context of a given structure formation model in a
 cosmological context. Under the current paradigm the dominant matter
@@
   who reported the ACF in the SSA22 region, including its densest
-  subfield.}
+  sub-field.}
 
@@
   galaxy overdensity. \cite{Yamada2012} estimates that the densest
-  subfield is likely to be a rare density peak with $3-4\sigma$
+  sub-field is likely to be a rare density peak with $3-4\sigma$
   significance on the scale of $\sim 60$\hMpc. }
@@
   outlier in the distribution (it corresponds to  the densest field in
-  SSA22). All the other fields form a continous  distribution in
+  SSA22). All the other fields form a continuous  distribution in
   number density.}
@@
 surface number density lower than the observational constrain, making
-them incompatible with observations; there are simply to few halos compared to observed
+them incompatible with observations; there are simply too few halos compared to observed
 LAEs. The opposite is true in models with $M_{\rm
@@
 parameterization.  Blue circles with error bars represent the results
-from the mocks and the horizontal line the obsrvational results of
+from the mocks and the horizontal line the observational results of
 \cite{Ouchi2010} over a field with average number density where the
@@
    constraints on the maximal number of consistent mocks and the
-  angular correlation function. The observational data correspods to
+  angular correlation function. The observational data corresponds to
   \citet{Ouchi2010}.   
@@
 together with the occupation fraction, $f_{\rm occ}$, and the minimum
-mass $M_{\rm min}$ allows us to clasify all the successful models into
+mass $M_{\rm min}$ allows us to classify all the successful models into
 three families:
@@
   outside the observational uncertainties, but have
-  are considered as consistent because their large error barsoverlap. These
+  are considered as consistent because their large error bars overlap. These
   models they have another particular feature: their minimum mass is
@@
 put a tight constraint on their occupation fraction of dark matter
-halos}. This information can confidently be used to stablish that
+halos}. This information can confidently be used to establish that
 these galaxies are hosted in low mass halos with masses within a range

### 2014-01-02 paper/ms.tex
seed for two new paragraphs in the caveat section

@@
   occ}<0.1$, which are not considered in this \documentname.  {\bf In
-  turn exploring occupation fractions on the order of $f_{\rm occ}=0.01$ requires
+  turn exploring occupation fractions on the order of $f_{\rm occ}=0.01$ 
   only makes sense for halo populations in the mass range of
   $10^{9}$\hMsun which are abundant enough to fit observations with a
-  low occupation fraction. In our case that mass range is not resolved
-  by the Bolshoi simulation an are not considered here.}
+  very low occupation fraction. In our case, this is a mass range unresolved
+  by the Bolshoi simulation and therefore cannot be considered in the
+  present study.}
 
@@
 galaxies are not a dominant population, making our initial
-approximation a reasonable one. Therefore we conclude that including
+approximation a reasonable one. {\bf The lack of close pairs }Therefore we conclude that including
 the effect of satellite galaxies does not change the main results
@@
 less than $\sim 0.2$ dex.
+
+{\bf Turning filter values into cosmological volumes.}
+
+{\bf Comparing results for the clustering and the ACF from surveys with different EW cuts.}
 
@@
 Alvaro Orsi and Mark Dijkstra for helpful comments on the physical
-interpretation and presentation of our results. J.E.F-R was
+interpretation and presentation of our results. We would
+also like to thank the referee for their helpful comments.
+
+J.E.F-R was
 supported by the FAPA grant by Vicerrector\'ia de Investigaciones at
-Universidad de los Andes.
-
-The MultiDark Database used in this paper and the web application
-providing online access to it were constructed as part of the
+Universidad de los Andes. The MultiDark Database used in this paper and the web application providing online access to it were constructed as part of the
 activities of the German Astrophysical Virtual Observatory as result

### 2014-01-03 paper/ms.tex
new paragraphs in the caveats sectionm, minor modifs in the conclusions

@@
 
-There are two important caveats for the work presented here. The first is the
+There are four caveats for the work presented here that are important
+to keep in mind. The first is the  
 assumption of a single LAE per dark matter halo. This contradicts the
@@
 galaxies are not a dominant population, making our initial
-approximation a reasonable one. {\bf The lack of close pairs }Therefore we conclude that including
+approximation a reasonable one. {\bf The lack of close pairs in
+  observations is another hint that the observed LAE population matches}
+Therefore we conclude that including
 the effect of satellite galaxies does not change the main results
@@
 
-The second caveat are the precise values for the mass intervals. These
+The second caveat is the precise values for the mass intervals. These
 values are quoted from halos defined using a FOF halo
@@
 
-{\bf Turning filter values into cosmological volumes.}
-
-{\bf Comparing results for the clustering and the ACF from surveys with different EW cuts.}
+{\bf The third caveat is the exact value that was used to turn
+  filter values into cosmological volumes. Strictly speaking the
+  volume probed is a function of the \ly luminosity. Brighter LAEs
+  probe a larger volume than fainter ones \citep{Gronwall07}. A proper
+way to account for this effect would require to assign luminosities to
+each mock LAE and process them in a similar way as mock
+observations. However, we can estimate that under the considerations
+presented in \citep{Gronwall07}, one could expect the survey depth to
+change at most by a factor of $\sim2$. Considering the dependence
+of the number density on halo mass (right panel of Figure 1), such
+change in volume could be compensated by different values for the
+favored model parameters $M_{\rm  min}$ and $M_{\rm max}$ by about the
+same factor of $\sim2$. }
+
+{\bf A fourth caveat is the comparing results for the number density
+  statistics and the ACF from surveys with different EW cuts. In this
+  sense we highlight againt that the two filters and selection
+  criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
+  slightly different. The number densities in the general fields by
+  \citep{Yamada2012} is $0.083\pm0.004$ arcmin$^{-2}$, while in
+  \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
+  confidence that the two different samples can give a self-consistent
+  picture for our studies.}
 
@@
 
-We find that {\bf the information for the number density constrains
+{\bf We find that the information for the number density constrains
   the minium mass to the range
@@
 
-The wide range in values for the escape fraction is allowed by the
-large dispersion in the statistics derived from the
-mocks. This uncertainty is unexpected from previous studies that
+{\bf Our approach has allowed the discovery of possible models that have
+been overloooked so far in the literature. A central role in these new
+models is played by the wide range of escape fraction values. A wide
+range in the escape fraction is unexpected from previous studies that
 unanimously favor low values for the occupation
-fractions \citep[i.e.][]{Gawiser2007,Ouchi2010}. Nevertheless, all the
-halo mass ranges and occupation fractions deduced previous analysis
-are a subset of the models we find in this \documentname.
-
-All of our preferred models support the notion that the most massive
-halos at $z=3.1$ do not host detectable LAEs. The existence of a
-narrow mass range for halos hosting LAEs, $\Delta  M\leq 1.0$ dex, has
-two different explanations at least. The first is having LAEs with a
+fractions \citep[i.e.][]{Gawiser2007,Ouchi2010}. The larges
+innnovation in our analysis is the construction of mock obsevations
+that directly explore the impact of cosmic variance, which seems to be
+at the root of the large uncertainties in the escape fraction.}
+
+Nevertheless, all the halo mass ranges deduced previous analysis are a
+subset of the models we find in this \documentname.  All of our
+preferred models support the notion that the most massive halos at
+$z=3.1$ do not host detectable LAEs. The existence of a narrow mass
+range for halos hosting LAEs, $\Delta  M\leq 1.0$ dex, has two
+different explanations at least. The first is having LAEs with a
 decreasing \ly escape fraction with increasing mass, the second is
@@
 
-In summary, we show that {\bf the currently available spatial information of LAEs cannot
-put a tight constraint on their occupation fraction of dark matter
-halos}. This information can confidently be used to establish that
-these galaxies are hosted in low mass halos with masses within a range
-spanning less than a factor of ten. We foresee that the new
-observations with new instruments (such as MUSE, Hyper SuprimeCam and
-HETDEX) covering larger fields and a wider range of luminosities will
-be key in reducing cosmic variance and imposing tighter constraints on
+In summary, we show that {\bf the currently available spatial
+  information of LAEs cannot put a tight constraint on their
+  occupation fraction of dark matter halos}. This information can
+confidently be used to establish that these galaxies are hosted in low
+mass halos with masses within a range spanning less than a factor of
+ten. {\bf From the point of view of Dark Energy surveys such as
+  HETDEX, the narrow mass range for LAEs can be seen as an advantage,
+  due to its simplicity, for their modeling aiming at recovering
+  cosmological parameters.} We foresee that the new observations with
+new instruments (such as MUSE, Hyper SuprimeCam and HETDEX) covering
+larger fields and a wider range of luminosities will be key in reducing cosmic variance and imposing tighter constraints on
 the properties of dark matter halos hosting LAEs. At the same time,

### 2014-01-03 paper/ms.tex
updated references, removed Hayashino 2004

@@
 field has been known to harbor a region with a large density excess of
-galaxies. {\bf The first sub-field of is taken around the same region
-  observed in \cite{Hayashino2004}.}
+galaxies.
 
@@
   reported the ACF is over a region of $1$ deg$^2$ over the SXDS
-  field.  We also keep track of the results by \cite{Hayashino2004}
-  who reported the ACF in the SSA22 region, including its densest
-  sub-field.}
+  field.  }
 
@@
   corresponding limiting luminosities and EW thresholds are different
-  in these references. The average LAEs number density inferred by
-  \cite{Hayashino2004} is  $0.37$ arcmin$^{-2}$, which is $30\%$
-  higher than the new measurement by \cite{Yamada2012}. In the case of
-  \cite{Ouchi2008} the number density is $0.10$ arcmin$^{-2}$, which
-  is $\sim 50\%$ lower than the value inferred by \cite{Yamada2012}
-  for a portion of the same region.}
+  in these references. In the case of
+  \cite{Ouchi2008} the number density is $0.099\pm0.005$ arcmin$^{-2}$, which
+  is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
+  the general fields in \cite{Yamada2012}}
 
@@
   compare mock distributions   against   observations does not require
-  such a perfect match.
-
-  In terms of the ACF the results that include the densest
-  field in SSA22 \citep{Hayashino2004} are consistent, within 
-  uncertainties, with the results of other fields
-  \citep{Ouchi2008}. In spite of this consistency we will focus on the
-  results from \citep{Ouchi2008}.}
+  such a perfect match. }
 
@@
 represent the average values in the fields observed by
-\citep{Hayashino2004,Ouchi08}.
+\citep{Ouchi2008}.
 
@@
   criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
-  slightly different. The number densities in the general fields by
-  \citep{Yamada2012} is $0.083\pm0.004$ arcmin$^{-2}$, while in
+  slightly different. The median number density in the general fields by
+  \citep{Yamada2012} is $0.20$ arcmin$^{-2}$, while in
   \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
-  confidence that the two different samples can give a self-consistent
-  picture for our studies.}
+  confidence that the two different samples can give a self-consistent picture
+  within a factor of $\sim2$ for our studies.}
 

### 2014-01-03 paper/reply.tex
referee reply

\documentclass[12pts]{article}
\begin{document}
Dear Editor, \\

We wish to thank the referee for a detailed report on our paper. \\

The referee expressed 5 major points of concern. Some of them were due
to unclearly written sections, other made reference to issues with the
observational data and choices to perform the comparison against the
simulated data.\\

In this new version we respond to all these concerns. We have
clarified the text where it was needed and performed new tests on the
data. We have also corrected an error in the computation of the
angular correlation function, strenghtening our conclusions. Therefore
we resubmit this draft to be considered for publication in the MNRAS.\\

We wish to emphasize that our paper uses a new method in the context
of the study of LAE galaxies. Correspondingly, the results are novel
with respect to the already published literature.\\

In what follows we reply to each one of the major points raised by the
referee. The comments by the referee are in boldface. Our reply
follows to each of these comments.\\

Best regards,\\

Jaime E. Forero-Romero and Julian Mejia-Restrepo\\

{\large \bf Major points}\\

\begin{enumerate}
\item {\bf As the authors are aware, each observational survey for LAEs has
  different selection effects, and some use very different thresholds
  in equivalent width.  Hence you need to use the number density and
  autocorrelation function (ACF) of LAEs from the *same* survey for an
  investigation like this.  You could try to get Yamada's LAE
  positions to calculate the ACF, since you appear to prefer that
  survey for number density estimation.  Or you could pursue joint
  analysis of number density and ACF for smaller surveys e.g.,
  Ouchi's. }\\

  We agree with the referee that the two statistical tests should be
  performed on the same data set. Unfortunately neither the galaxy catalog
  nor the ACF from Yamada et al. 2012 are available. We contacted
  Dr. Yamada asking for information about the ACF, but we didn't get
  any reply.

  The currrent version of the draft features a comparison with the ACF
  from a survey with an average number density from Hayashino et al
  2004.

  On the other hand, Using a small field as Ouchi's for our analysis
  is not feasible, given that our method is based on the analysis of
  the surface density \emph{distribution among different}
  fields. Having the distribution data is central to discard a large
  fraction of models (Section 3.3).

\item {\bf 
  The major result claimed that all models have a narrow mass range
  of halos hosting LAEs is guaranteed by the choice of a minimum
  value of $f_{\rm occ}$ of 0.1.  This should be obvious to the authors, as
  there is a degeneracy between $f_{\rm occ}$ and the mass range of halos
  that you have hidden by forcing $f_{\rm occ}$ to values larger than those
  previously claimed in the literature. }

  As the referee highlights, we have found a new set of acceptable
  parameters for the escape fraction than those that have been
  previously claimed by the literature.

  However, we do not find a clear evidence for a degeneracy between
  the occupation fraction $f_{\rm occ}$ and the mass range $\Delta
  M$. There is, however, a clear degeneracy between the minium halo
  mass $M_{\rm min}$ and the occupation fraction.

  The reason for that trend is easy to understand. In LCDM the halo
  number density $n$ is verysensitive to the mass. The dependency is
  roughly $n\propto  M_{h}^{-1}$. Therefore, at a fixed minimum halo
  mass, increasing the mass range by 1.0 dex barely raises the number
  density by  
  $0.10$. Increasing the mass range by 2.0 dex  raises the number
  density by $0.11$. This explains that we cannot find any clear
  dependence between $\Delta M$ and the $f_{\rm occ}$. On the other
  hand, decreasing the minium mass by 1.0 dex would increas the number
  density by a factor of {\bf $10$} (!). Requiring that models with
  small values for the minium mass to have a small occupation
  fraction.

  This trend is clearly seen on the right panel of Figure 3,4 and
  6. This implies that exploring very low escape fractions values of
  $0.01$ would require the exploration of halo masses aroud the range
  of $10^{9}$ Msun or   below, which is lower than the minimum halo
  masss of $10^{9.5}$ Msun   that is confidently resolved in the
  simulation.

  \item {\bf 
The authors cite similar work by Walker Soler et al. 2012 but fail
   to mention in the introduction how the current paper has the same
   goals as that earlier work.  If applied more carefully, their
   approach should be able to improve on the earlier work, but it is
   important to be clear about how similar the papers are and how the
   current one hopes to improve on the previous one. 
}

The work of Walker-Soler 2012 actually does not pursue a similar goal
as our paper. They take a fixed set of results of a semi-analytical
model to infer the mass of the \emph{descendants} from LAEs at
$z=3.1$. We have removed the reference to that work that might show
that we are improving work they have been done, because that's not the case.

\item {\bf 
Comparing the most heavily clustered of 15 mocks against SSA22 is
  unfair. SSA22 is a ~5 sigma overdensity, which is much rarer than
  1/15. 
  }

We agree with the referee that a comparison of a $\sim 5 $ overdensity
with an average field would not be fair. Therefore we have removed
that constraint from the results in the new version of the paper. Now
we only include the ACF comparison against the results of an average
density field from Ouchi 2008.

Related to this point we have added the left panel in Figure 1 and
subsection 2.2 to discuss the adequacy of including SSA22 as an
observational benchmark in the number density tests.

\item {\bf 
  There seems to be significant confusion between halo occupation
   fraction and Lyman alpha escape fraction.  Only in an incredibly
   simplified model where 100\% of Ly alpha photons escape from LAEs
   and 0\% escape from non-LAEs would the comparison in section 4.1
   make sense.  In a more realistic model, it is not clear how this
   investigation could hope to comment on the escape fraction of Ly
   alpha photons. 
}\\

We agree with the referee in this point.

We have corrected all the mistakes where we meant occupation
fraction but wrote escape fraction. We have alsoremoved the discussion
comparing our results to escape fraction estimates, in spite of the
effort of other authors to link these two different quantities.

\end{enumerate}

Additional suggestions:
\begin{itemize}
\item{\bf Only allowing one LAE per dark matter halo is a simplistic model.  You
could try more complicated HOD models where $f_occ(M)$ is not constant
to see if they make a significant difference in the results.  But
arguing against this by citing the Jose et al. 2013 paper seems
reasonable.  You could also note the lack of close-proximity LAE pairs
noted in papers led by Nick Bond as further evidence against multiple
LAEs occurring in the same halo. }

We would like to add a reference to the work of Nick Bond, but failed
to fine what exact paper makes reference to the lack of
close-proximity LAE pairs.

\item{\bf You could explore a wide range of $f_occ$ down to properly tiny values
such as 0.001 without increasing the run time by indexing it
logarithmically.}

As we mentioned before in the Reply to Major Point 2, tiny values of
0.001 can only produce reasonable models for very low mass halos. This
is due to the contraint on the number density. An occupation fraction
of 0.001 requires models with a minimum mass on the order of $M_{\rm
  min}=10^{9}$ solar masses, which is well below the mass resolution
of the simulation we use. This comment has been added to the paper.

\item {\bf Be careful when turning filters into cosmological volumes - you should
not simply use the FWHM.  See Gronwall et al. 2007 for a detailed
discussion of this.}

We have included a paragraph about this point in Section 4.4.

\item {\bf Be careful when comparing results for halo occupation fraction for
LAEs from a survey with a 190A observed EW threshold to the more
typical 20 A EW rest-frame, which equals 80A observed at z=3. }

We have included a paragraph about this point in Section 4.4

\item {\bf SSA22 is known to be an extraordinary overdensity, as you note.  The
overdense region, and possibly the entire field, will bias the
measured number density of z=3.1 LAEs upwards.  So one should be very
cautious including this field in a study like this one. }

We have included subsection 2.2 to comment on this point.

\item {\bf When using a constant value for $f_{\rm occ}$, you could use just
  $M_{\rm min}$, $M_{\rm max}$ as parameters, choose the value of
  $f_{\rm occ}$ that fits the observed number density (propagating
  uncertainties) and then test the resulting ACF versus data.  This
  would be accurate because a random sub-sample of halos has the same
  clustering as the full sample. }

  We agree that this is a feasible approach. The emphasis we meant in
  our approach was the effect of cosmic variance on the size of
  observed fields. This is why we include the tests on all sub-samples
  and not just one.

\end{itemize}

\end{document}

### 2014-01-06 paper/ms.tex
reviewed abstract

@@
 matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
-$z=3.1$ by matching the number density and the angular
+$z=3.1$ by matching the number density distribution and the angular
 correlation function between mock and observed fields. We explicitly
@@
 size by constructing mock fields from a large cosmological N-body
-simulation matching the geometries of observed fields. To populate the
+simulation with the same geometry of observed fields. To populate the
 halos in the simulation we use a model where a dark matter halo with
 mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
-one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
-build such a model is to avoid the large uncertainties in the
-estimation of \ly luminosities. Our main result is that the clustering
-and number density information are insufficient to impose a tight
-constraint on the {\bf occupation} fraction. On the other hand the
-minimum mass and maximum mass can be tightly constrained to the range
-$M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
+one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
+1.0$. We avoid the large uncertainties in the estimation of \ly
+luminosities with this approach. Our main result is that the
+clustering and number density information are insufficient to impose a
+tight constraint on the {\bf   occupation} fraction. On the other hand
+the minimum mass and maximum mass can be constrained to the range $M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
 10^{11.5}\hMsun$.  We also find that the consistent models have a narrow mass
-range $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$
-smaller than $1.0$ dex, with the vast majority in the range $\Delta
-M<0.5$ dex. Already published constraints on the mass range and
-occupation fraction are a sub-set of the models we report in this
-\documentname. Our results present an inconclusive response as to
+range, $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$,
+smaller than $1.0$ dex, with a vast majority in the range $\Delta
+M<0.5$ dex. {\bf These mass ranges are a sub-set of already published
+constraints, while the wide range of values for the escape fraction
+  are a novel result}. There is an inconclusive response as to
 which is the occupation fraction for LAEs at $z=3.1$. A precise answer

### 2014-01-06 paper/ms.tex
revised conclusions

@@
 In this \documentname we look for constraints on the preferred mass
-and occupation fraction of dark matter halos hosting Lyman Alpha Emitters at
+and occupation fraction of dark matter halos hosting Lyman $\alpha$ Emitters at
 redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform this study
@@
 observational geometries. The mocks are constructed from a N-body simulation
-following a simple recipe to assign a single LAE to each halo. Only
+following a simple recipe to assign a single LAE to each halo whereby only
 a fraction $f_{\rm occ}$ of halos within a mass range  $M_{\rm
-  min}<M_{\rm h}<M_{\rm   max}$ can host a LAE.
+  min}\leq M_{\rm h}\leq M_{\rm   max}$ can host a LAE.
 
@@
 M_{\rm max}$ and $f_{\rm occ}$ to find mocks that are consistent with
-two observational constraints: the surface number density and the
-angular correlation function. Out of the initial $9000$ 
+two observational constraints: the surface number density distribution
+and the angular correlation function. Out of the initial $9000$ 
 combinations of parameters in the model we find $40$ combination of parameters
@@
   constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
-  this is insufficient to impose a tight constraint  on the escape
-  fraction.} Furthermore, we find that the mass range defined as
-$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is always
-$\Delta M\leq 1.0$.
+  this information insufficient to impose a tight constraint  on the escape
+  fraction. Additionaly, we find that the mass range defined as
+$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is $\Delta
+M\leq 1.0$, with a large fraction of models with $\Delta M\leq 0.5$.}
 
@@
 been overloooked so far in the literature. A central role in these new
-models is played by the wide range of escape fraction values. A wide
-range in the escape fraction is unexpected from previous studies that
-unanimously favor low values for the occupation
-fractions \citep[i.e.][]{Gawiser2007,Ouchi2010}. The larges
-innnovation in our analysis is the construction of mock obsevations
-that directly explore the impact of cosmic variance, which seems to be
-at the root of the large uncertainties in the escape fraction.}
+models is played by the wide range of escape fraction values,
+something unexpected from previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that unanimously favor low values on the range of $10^{-2}$. The largest
+innovation in our analysis is the construction of mock obsevations
+that directly explore the impact of cosmic variance.}
 
 Nevertheless, all the halo mass ranges deduced previous analysis are a
-subset of the models we find in this \documentname.  All of our
+subset of the models we find in this paper.  All of our
 preferred models support the notion that the most massive halos at
-$z=3.1$ do not host detectable LAEs. The existence of a narrow mass
-range for halos hosting LAEs, $\Delta  M\leq 1.0$ dex, has two
-different explanations at least. The first is having LAEs with a
-decreasing \ly escape fraction with increasing mass, the second is
-having larger screening effects by neutral Hydrogen around the most
-massive systems \citep{Laursen2009,ForeroRomero2011}.
+$z=3.1$ do not host detectable LAEs. {\bf Furthermore, we claim that the
+mass range for halos hosting LAEs is narrow, $\Delta M\leq 1.0$, with
+a majority of models with $\Delta M\leq 0.5$.}
+
+The existence of models with narrow mass ranges has at least two
+different explanations. The first is having LAEs with a decreasing \ly
+escape fraction with increasing mass, the second is having larger
+screening effects by neutral Hydrogen around the most massive systems
+\citep{Laursen2009,ForeroRomero2011}.
 
@@
 there is barely a factor of $\sim 2$ between the minimum and halo
-mass. If these models can be confirmed, it would mean a great
+mass. If this can be confirmed, it would mean a great
 challenge for galaxy formation models to explain how is that LAEs can
@@
 confidently be used to establish that these galaxies are hosted in low
-mass halos with masses within a range spanning less than a factor of
-ten. {\bf From the point of view of Dark Energy surveys such as
-  HETDEX, the narrow mass range for LAEs can be seen as an advantage,
-  due to its simplicity, for their modeling aiming at recovering
-  cosmological parameters.} We foresee that the new observations with
-new instruments (such as MUSE, Hyper SuprimeCam and HETDEX) covering
-larger fields and a wider range of luminosities will be key in reducing cosmic variance and imposing tighter constraints on
-the properties of dark matter halos hosting LAEs. At the same time,
-additional modeling for \ly radiation transfer is needed to put a
-tighter constrain on the \ly escape fraction in high redshift
-galaxies, also paying attention to newly framed physical phenomena,
+mass halos with masses spanning less than one order of magnitude. {\bf
+  From the point of view of Dark Energy surveys such as the Hobby-Eberly
+  Telescope Dark Enery Experiment (HETDEX) the
+  narrow mass range for LAEs can be seen as an advantage because its
+  simplicity in their modeling aiming at recoverin cosmological
+  parameters.} We foresee that the observations with new instruments
+(such as the Multi Unit Spectroscopic Explorer (MUSE), Hyper
+SuprimeCam and HETDEX) covering larger fields and a wider range of
+luminosities will be key in reducing cosmic variance and imposing
+tighter constraints on the properties of dark matter halos hosting
+LAEs. At the same time, additional modeling for \ly radiation transfer
+is needed to put tighter constraints on  occupation fraction in high
+redshift halos, also paying attention to other physical phenomena,
 such as the stochasticity \citep{ForeroRomero2013} in the star

### 2014-01-06 paper/ms.tex
reviewed captions

@@
   sub-field in the SSA22 field. Right panel. Surface density of dark 
-  matter halos as a function of a minimum halo mass to count the
-  total number of elements in a volume. Each line represents one of the
-  $210$ volumes of dimensions $46\times 35\times 41$ $h^{-3}$ Mpc$^{3}$
-  in the Bolshoi simulation. The horizontal gray band represents the
-  range of surface densities observed for LAEs at $z=3.1$ as reported
-  by \citep{Yamada2012}.}
+  matter halos as a function of a minimum halo mass. Each line
+  represents one of the $210$ volumes of dimensions $46\times 35\times
+  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
+  gray band represents the range of surface densities observed for
+  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
+  line the observational results by \citet{Ouchi2008}.}
 \end{center} 
@@
 \includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
-\caption{ \label{fig:distros} Spatial distribution of a LAEs mock
-  survey for a model with parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
+\caption{ \label{fig:distros} Spatial distribution of a LAEs in a mock
+  survey with model parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
     max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
@@
   $P>0.05$. The color code corresponds to the number of mock surveys
-  compatible with observations. Only regions of parameter  space with
+  compatible with observations. Only regions in the parameter space with
   at least one consistent mock survey are
@@
 correlation function. Blue dots correspond to simulations and the
-green line to observations by \citet{Ouchi2010}. The error
+green line to observations by \citet{Ouchi2008,Ouchi2010}. The error
 bars in the theoretical data correspond to the quadratic average of
-the fitting errors for each mock
+the fitting uncertainties for each mock
 survey \label{fig:correlation_parameters}}  
@@
    constraints on the maximal number of consistent mocks and the
-  angular correlation function. The observational data corresponds to
-  \citet{Ouchi2010}.   
+  angular correlation function. The observational data for the ACF
+  corresponds to 
+  \citet{Ouchi2008,Ouchi2010}.   
   \label{fig:restriction_mock_and_f_occ_corr}} 
@@
 \caption{\label{table:secondfamily}List of parameters for the second
-  family of models. Narrow mass range $\Delta M\leq 0.4 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
+  family of models. Narrow mass range $\Delta M\leq 1.0 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
 \end{table}

### 2014-01-06 paper/ms.tex
reviewed discussion

@@
 discussion of these models we define a new quantity, the halo mass
-range $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
+range $\Delta M\equiv \log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
 together with the occupation fraction, $f_{\rm occ}$, and the minimum
@@
 {\bf The models in the third family are barely consistent with the
-  constraints from the ACF. They have mean values of $\theta_0$
-  outside the observational uncertainties, but have
-  are considered as consistent because their large error bars overlap. These
+  constraints from the ACF. They have values of $\beta$ close to $1.0$
+  (instead of the observational value of $0.8$) and $\theta_0$ on the
+  range of $13^{\prime}$ (the mean observational value is close to
+  $8^{\prime}$) but are considered
+  consistent because their large error bars barely overlap with the
+  observational expectation. These 
   models they have another particular feature: their minimum mass is
@@
 
-\subsection{Two relevant features}
+\subsection{Two relevant features in the preferred models}
 There are two interesting features in the remaining two first
@@
   predicted by our models is consistent with already published
-  observational results. This suggests that taking explicitly cosmic
-  variance into account hinders the possibility of constraining the
-  LAEs occupation fraction.}
+  observational results \citep{Gawiser07,Ouchi2010}. This suggests
+  that explicitly taking cosmic variance of the observed fields into
+  account (the only point not included in the analysis already cited)
+  hinders the possibility of constraining the LAEs occupation
+  fraction.}
 
@@
   can start with a reasonable   assumption. Namely that star formation
-  rate increases with halo's  mass.}
-
-Under this assumption the cut at the low mass end, $M_{\rm min}$, can be
-interpreted in terms of the minimal star formation rate required to
-produce a \ly luminosity above observational detection thresholds.  
-A cut at higher halo masses $M_{\rm  max}$ requires a
-different justification. There are two complementary physical
-scenarios that could provide
+  rate increases with halo's  mass. Under this assumption the cut at
+  the low mass end, $M_{\rm min}$, can be interpreted in terms of the
+  minimal star formation rate required to produce a \ly luminosity
+  above observational detection thresholds.   A cut at higher halo
+  masses $M_{\rm  max}$ requires a different justification. There are
+  two complementary physical scenarios that could provide it.}
 
@@
 
-\subsection{Comparison to other clustering estimates}
+\subsection{Comparison to previous clustering estimates}
 
@@
 \ref{table:firstfamily}. These models, which favor only the 
-low occupations fractions, are also consistent in that regards with
-the observational expectations.
+low ($\sim 10\%$) occupations fractions, are also consistent in that
+       regards with the observational expectations by \cite{Gawiser07}.
 
@@
 to show that the halo mass range can, in some cases, be narrow $\Delta M <
-0.3$dex, something that cannot be inferred from ACF analysis alone.
-Furthermore, In contrast to \citep{Gawiser07} and \citep{Ouchi2010} we
-find that an ACF analysis on a single data-set is not enough to rule
+0.3$ dex, something that cannot be inferred from ACF analysis alone.
+Furthermore, In contrast to \cite{Gawiser07} and \cite{Ouchi2010} we
+find that an ACF analysis is not enough to rule
 out models with a high occupation fraction $f_{\rm occ}>0.3$, which
@@
   observations is another hint that the observed LAE population matches}
-Therefore we conclude that including
-the effect of satellite galaxies does not change the main results
-reported in this \documentname.
+Therefore we conclude that including the effect of satellite galaxies
+should not significantly change the main results reported in this
+\documentname.
 

### 2014-01-16 code/correlation_statistic.py
correlation plot updated

@@ -23,7 +23,7 @@ pinit = [12.0]
 n_models=101
 n_mocks=15
 theta_bins=11
-pro_path="/home/margoly/CosmicVarianceLAES/"
+pro_path="/Users/jemejia/CosmicVarianceLAES/"
 
 obs_correlation_file=pro_path + "data/obs/hayashino_whole_SSA22_field.txt"
 obs=np.loadtxt(obs_correlation_file,skiprows=4)
@@ -159,7 +159,7 @@ ro_plot=fig2.add_subplot(111)
 ro_index=np.where(slope_err<2.0)
 ro_plot.errorbar(ro[ro_index],-1*slope[ro_index], yerr=slope_err[ro_index], xerr=ro_err[ro_index], label="Models",elinewidth=1.5,fmt="o")
 ro_plot.errorbar(ro_obs,-1*slope_obs, yerr=slope_err_obs, xerr=ro_err_obs, label="Ouchi et al 2008",elinewidth=4.5)
-ro_plot.set_xlabel(r'$\theta_{0}$', fontsize=20)
+ro_plot.set_xlabel(r'$\theta_{0}(arcsec)$', fontsize=20)
 ro_plot.set_ylabel(r"$\beta$",fontsize=20)
 #ro_plot.set_title("Angular Correlation parameters. Full SSA22 field",fontsize=20)
 #ro_plot.set_title("Angular Correlation parameters. Match survey",fontsize=20)

### 2014-01-17 paper/ms.tex
paper updated. New plot added to give support to the exclusion of the third family of models whre deltaM>1.0

@@
   Jaime E. Forero-Romero$^{1}$ and
-  Julian E. Mej\'ia-Restrepo$^{2}$ 
+  Julian E. Mej\'ia-Restrepo$^{2,3}$ 
 }
@@
 $^{2}$ Departamento de Astronom\'{i}a, Universidad de Chile, Camino el
-Observatorio 1515, Santiago, Chile}
+Observatorio 1515, Santiago, Chile\\
+$^3$FACom-Instituto de Física-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medellín, Colombia}
 
@@
 set is constructed from 12 different sub-fields that allows us to use
-clustering statistics and cosmic variance to constraint the mass and
+clustering statistics and cosmic variance to constrain the mass and
 occupation fraction of halos hosting LAEs.
@@
 
-Figure \ref{fig:correlation_parameters} shows the results for the
+The left panel of the figure \ref{fig:correlation_parameters} shows the results for the
 best estimates of $\theta_{0}$-$\beta$  used in the ACF
@@
 almost all models with $M_{\rm max}>10^{12}$. The only exception is 
-a narrow range of models with $M_{\rm min}=10^{10.9}$. However, we
-have verified that these models are only marginally consistent with
-the ACF constraints in the $\theta_0$-$\beta$ plane.
+a narrow range of models with $M_{\rm min}=10^{10.9}$. However, in the right panel of figure  \ref{fig:correlation_parameters}   we can observe that these models are only 
+marginally consistent with the ACF constraints in  $\theta_0$.
 
 From this comparison we conclude that clustering information can
-constraint the values of $M_{\rm max}$, but not the occupation
+constrain the values of $M_{\rm max}$, but not the occupation
 fraction.
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
+\includegraphics[width=0.46\linewidth,angle=0]{Fig7_corr_params.pdf}  
+\includegraphics[width=0.46\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
 \end{center}
-\caption{Values for the free parameters $\theta_{0}$ and $\beta$
+\caption{Left panel. Values for the free parameters $\theta_{0}$ and $\beta$
 in the fitting formula (Eq. \ref{eq:fitting}) for the angular
@@
 bars in the theoretical data correspond to the quadratic average of
-the fitting uncertainties for each mock
-survey \label{fig:correlation_parameters}}  
-\end{figure}
+the fitting uncertainties for each mock survey.
+Right panel.
+Values of $\theta_{0}$  and $\log_{10}(M_{min}/M_{\odot} h^{-1})$.
+Blue and green point represents the models where  $\log_{10}(M_{max}/M_{\odot} h^{-1})<12.0$ and  $\log_{10}(M_{min}/M_{\odot} h^{-1})>12.0$ respectively.
+.
+The horizontal gray band represents the observational contraints on $theta_{0}$ stablished by   \citet{Ouchi2008,Ouchi2010}.
+Green points has been displaced by $0.01dex$ of its original value to avoid overlapping between blue and green points.} \label{fig:correlation_parameters}
+\end{figure*}
 
@@
 \label{sec:discussion}
+
+Out of the initial set of $9000$ models we end up with $40$ that are
+consistent with the observational constraints. To facilitate the
+discussion of these models we define a new quantity, the halo mass
+range $\Delta M\equiv \log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
+together with the occupation fraction, $f_{\rm occ}$, and the minimum
+mass $M_{\rm min}$ allows us to classify all the successful models into
+three families:
+
+\begin{itemize}
+\item[(1)] Low occupation fraction $f_{\rm occ}\leq 0.2$ and narrow
+  mass range $\Delta M\leq 1.0$ 
+  dex: 16 models. 
+\item[(2)] High occupation fraction $f_{\rm occ}> 0.2$ and
+  narrow mass range $\Delta M\leq 1.0$: 17 models 
+\item[(3)] Low occupation fraction $f_{\rm occ}\leq 0.2$ 
+  and wide mass range $\Delta M>1.0$: 7 models
+\end{itemize}
+
+A complete parameter list for the three families is presented in Tables
+\ref{table:firstfamily}, \ref{table:secondfamily}  and 
+\ref{table:thirdfamily}.
+
+{\bf The models in the third family are barely consistent with the
+  constraints from the ACF. These 
+  models they have another particular feature: their minimum mass is
+  exactly $M_{\rm min}=10^{10.9}\hMsun$ m and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$ close to $1.0$
+  (instead of the observational value of $0.8$) and $\theta_0$ on the
+  range of $13^{\prime}$ (the mean observational value is close to
+  $8^{\prime}$) but are considered
+  consistent because their large error bars barely overlap with the
+  observational expectation (see figure \ref{fig:correlation_parameters})  .  Because these models are
+  are barely compatible with observations and are a minority of the
+  consistent models, we exclude them from the rest of the discussion.}
 
@@
 \end{figure*}
-
-Out of the initial set of $9000$ models we end up with $40$ that are
-consistent with the observational constraints. To facilitate the
-discussion of these models we define a new quantity, the halo mass
-range $\Delta M\equiv \log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
-together with the occupation fraction, $f_{\rm occ}$, and the minimum
-mass $M_{\rm min}$ allows us to classify all the successful models into
-three families:
-
-\begin{itemize}
-\item[(1)] Low occupation fraction $f_{\rm occ}\leq 0.2$ and narrow
-  mass range $\Delta M\leq 1.0$ 
-  dex: 16 models. 
-\item[(2)] High occupation fraction $f_{\rm occ}> 0.2$ and
-  narrow mass range $\Delta M\leq 1.0$: 17 models 
-\item[(3)] Low occupation fraction $f_{\rm occ}\leq 0.2$ 
-  and wide mass range $\Delta M>1.0$: 7 models
-\end{itemize}
-
-A complete parameter list for the three families is presented in Tables
-\ref{table:firstfamily}, \ref{table:secondfamily}  and 
-\ref{table:thirdfamily}.
-
-{\bf The models in the third family are barely consistent with the
-  constraints from the ACF. They have values of $\beta$ close to $1.0$
-  (instead of the observational value of $0.8$) and $\theta_0$ on the
-  range of $13^{\prime}$ (the mean observational value is close to
-  $8^{\prime}$) but are considered
-  consistent because their large error bars barely overlap with the
-  observational expectation. These 
-  models they have another particular feature: their minimum mass is
-  exactly $M_{\rm min}=10^{10.9}\hMsun$. Because these models are
-  are barely compatible with observations and are a minority of the
-  consistent models, we exclude them from the rest of the discussion.}
 
@@
   statistics and the ACF from surveys with different EW cuts. In this
-  sense we highlight againt that the two filters and selection
+  sense we highlight again that the two filters and selection
   criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
@@
   constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
-  this information insufficient to impose a tight constraint  on the escape
+  this information is insufficient to impose a tight constraint  on the escape
   fraction. Additionaly, we find that the mass range defined as
@@
 {\bf Our approach has allowed the discovery of possible models that have
-been overloooked so far in the literature. A central role in these new
+been overlooked so far in the literature. A central role in these new
 models is played by the wide range of escape fraction values,
@@
 
-Nevertheless, all the halo mass ranges deduced previous analysis are a
+Nevertheless, all the halo mass ranges deduced in previous analysis are a
 subset of the models we find in this paper.  All of our
@@
   narrow mass range for LAEs can be seen as an advantage because its
-  simplicity in their modeling aiming at recoverin cosmological
+  simplicity in their modeling aiming at recovering cosmological
   parameters.} We foresee that the observations with new instruments

### 2014-01-17 code/correlation_statistic.py

@@ -176,15 +176,16 @@ mmax_index=np.where(m_max_m<12.0) #and ro<ro_max) #and slope_min<slope<slope_max
 mmin_plot.errorbar(m_min_m[mmax_index],ro[mmax_index], yerr=ro_err[mmax_index],label=r"$\log M_{max}<12.0$",elinewidth=1.5,fmt="s")
 mmax_index=np.where(m_max_m>12.0) #and ro<ro_max) #and slope_min<slope<slope_max)
 mmin_plot.errorbar(m_min_m[mmax_index]+0.01,ro[mmax_index], yerr=ro_err[mmax_index],label=r"$\log M_{max}>12.0$",elinewidth=1.5,fmt="o")
-mmin_plot.set_ylabel(r'$\theta_{0}$', fontsize=20)
-mmin_plot.set_xlabel(r"$M_{min}$",fontsize=20)
-mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Full SSA22 Field",fontsize=20)
-mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Match Survey",fontsize=20)
+mmin_plot.set_ylabel(r'$\theta_{0}(arcsec)$', fontsize=20)
+mmin_plot.set_xlabel(r"$\log_{10}(M_{min}/M_{\odot} h^{-1} )$",fontsize=20)
+#mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Full SSA22 Field",fontsize=20)
+#mmin_plot.set_title(r"$M_{min}$ vs $\theta_{0}$. Match Survey",fontsize=20)
 
 plot_name=plot_dir +"mmin_vs_correlation_" +sys.argv[1] + ".pdf"
 mmin_plot.legend(shadow=False,loc=2)
-collection = collections.BrokenBarHCollection.span_where(m_min_m, ymin=5.55, ymax=11.71, where=ro>0,  facecolor='red', alpha=0.5)
+collection = collections.BrokenBarHCollection.span_where(np.append([9.98,11.5,11.6],m_min_m) + 0.02, ymin=ro_obs-ro_err_obs, ymax=ro_obs+ro_err_obs, where=ro>0,  facecolor='gray', alpha=0.5)
 mmin_plot.add_collection(collection)
+P.xlim(xmin=10.0,xmax=11.42)
 fig3.savefig(plot_name,format="pdf")
 
 

### 2014-01-20 paper/reply.tex
new reply

@@
 The referee expressed 5 major points of concern. Some of them were due
-to unclearly written sections, other made reference to issues with the
-observational data and choices to perform the comparison against the
-simulated data.\\
+to unclear written sections, other made reference to issues with the
+choice of observational data used to compare against the mocks.\\
 
@@
 clarified the text where it was needed and performed new tests on the
-data. We have also corrected an error in the computation of the
-angular correlation function, strenghtening our conclusions. Therefore
-we resubmit this draft to be considered for publication in the MNRAS.\\
+data. We have also corrected a small error in the presentation of the
+results for the angular correlation function. All these modifications
+and improvements strengthen the conclusions already
+presented. Therefore we resubmit this draft to be considered for
+publication in the MNRAS.\\
 
-We wish to emphasize that our paper uses a new method in the context
-of the study of LAE galaxies. Correspondingly, the results are novel
-with respect to the already published literature.\\
+We wish to emphasize that our paper presents a new method in the context
+of the study of LAE at high redshift. Correspondingly, the results are
+novel with respect to the already published literature.\\
 
@@
 referee. The comments by the referee are in boldface. Our reply
-follows to each of these comments.\\
+follows to each one of the comments.\\
 
@@
 
-  We agree with the referee that the two statistical tests should be
-  performed on the same data set. Unfortunately neither the galaxy catalog
+  We follow the referee's suggestion and perform the ACF analysis
+  using Ouchi's data.
+
+  We made this choice because neither the galaxy catalog
   nor the ACF from Yamada et al. 2012 are available. We contacted
@@
   any reply.
-
-  The currrent version of the draft features a comparison with the ACF
-  from a survey with an average number density from Hayashino et al
-  2004.
-
-  On the other hand, Using a small field as Ouchi's for our analysis
-  is not feasible, given that our method is based on the analysis of
-  the surface density \emph{distribution among different}
-  fields. Having the distribution data is central to discard a large
-  fraction of models (Section 3.3).
 
@@
   As the referee highlights, we have found a new set of acceptable
-  parameters for the escape fraction than those that have been
-  previously claimed by the literature.
+  parameters for the escape fraction $f_{\rm occ}>0.1$. We stress that
+  an occupation fraction of $0.1$ is on the upper end of the accepted
+  values by Gawiser et al. 2007. At the same time all the mass ranges
+  we find acceptable are within the wide mass range already published
+  by observers. All this seems to be good news rather a caveat.
 
-  However, we do not find a clear evidence for a degeneracy between
-  the occupation fraction $f_{\rm occ}$ and the mass range $\Delta
-  M$. There is, however, a clear degeneracy between the minium halo
-  mass $M_{\rm min}$ and the occupation fraction.
+  The reason for a narrow mass range $\Delta M$ does not
+  seem to be a consequence from the constraint on the occupation
+  fraction to be larger than $0.1$. We do not find a clear evidence
+  for a degeneracy between the occupation fraction $f_{\rm occ}$ and
+  the mass range $\Delta M$. However we would appreciaty a pointer to
+  any reference presenting evidence for the opossite.
 
-  The reason for that trend is easy to understand. In LCDM the halo
-  number density $n$ is verysensitive to the mass. The dependency is
-  roughly $n\propto  M_{h}^{-1}$. Therefore, at a fixed minimum halo
-  mass, increasing the mass range by 1.0 dex barely raises the number
-  density by  
-  $0.10$. Increasing the mass range by 2.0 dex  raises the number
-  density by $0.11$. This explains that we cannot find any clear
-  dependence between $\Delta M$ and the $f_{\rm occ}$. On the other
-  hand, decreasing the minium mass by 1.0 dex would increas the number
-  density by a factor of {\bf $10$} (!). Requiring that models with
-  small values for the minium mass to have a small occupation
-  fraction.
+  However, there is a clear degeneracy between the minimum halo mass
+  $M_{\rm min}$ and the occupation fraction.This trend is clearly
+  seen on the right panel of Figure 3,4 and 6. This implies that
+  exploring very low escape fractions values of the range $0.01$ would
+  require building mock catalogs with a minimum mass around the range
+  $10^{9.5}$Msun or below which is precisely the minimum halo mass of
+  that is resolved in the simulation. This intrinsic limitation on the
+  range of values that can be explored is now explicit in the paper.
 
-  This trend is clearly seen on the right panel of Figure 3,4 and
-  6. This implies that exploring very low escape fractions values of
-  $0.01$ would require the exploration of halo masses aroud the range
-  of $10^{9}$ Msun or   below, which is lower than the minimum halo
-  masss of $10^{9.5}$ Msun   that is confidently resolved in the
-  simulation.
+  All in all, we consider this result for a narrow
+  mass range $\Delta M<1.0$ (in many cases $\Delta M<0.5$) a novel
+  one, since it has not been mentioned in the literature before.
 
@@
 with an average field would not be fair. Therefore we have removed
-that constraint from the results in the new version of the paper. Now
-we only include the ACF comparison against the results of an average
-density field from Ouchi 2008.
+the comparison from the ACF in the SSA22 field in the new version of
+the paper. We only include the ACF comparison against the results of
+an average density field from Ouchi 2008.
 
 Related to this point we have added the left panel in Figure 1 and
-subsection 2.2 to discuss the adequacy of including SSA22 as an
+subsection 2.2.1 to discuss the adequacy of including SSA22 as an
 observational benchmark in the number density tests.
+
+In that subsection we emphasize that it is only one of the subfields
+in SSA22 that represents at 3-$\sigma$ overdensity. The whole field
+has an average density compared to other blank fields.
 
@@
 We have corrected all the mistakes where we meant occupation
-fraction but wrote escape fraction. We have alsoremoved the discussion
+fraction but wrote escape fraction. We have also removed the discussion
 comparing our results to escape fraction estimates, in spite of the
@@
 
-As we mentioned before in the Reply to Major Point 2, tiny values of
+As we mentioned before in the reply to Major Point 2, tiny values of
 0.001 can only produce reasonable models for very low mass halos. This
-is due to the contraint on the number density. An occupation fraction
-of 0.001 requires models with a minimum mass on the order of $M_{\rm
-  min}=10^{9}$ solar masses, which is well below the mass resolution
-of the simulation we use. This comment has been added to the paper.
+is due to the constraint on the number density distribution. An
+occupation fraction of 0.001 requires models with a minimum mass on
+the order of $M_{\rm min}=10^{9}$ solar masses, which is well below
+the mass resolution of the simulation we use. This comment has been
+added to the paper.
 
-\item {\bf Be careful when turning filters into cosmological volumes - you should
-not simply use the FWHM.  See Gronwall et al. 2007 for a detailed
+\item {\bf Be careful when turning filters into cosmological volumes -
+  you should not simply use the FWHM.  See Gronwall et al. 2007 for a detailed
 discussion of this.}

### 2014-01-20 paper/ms.tex
revised abstract

@@
 Observatorio 1515, Santiago, Chile\\
-$^3$FACom-Instituto de Física-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medellín, Colombia}
+$^3$ FACom-Instituto de F\'isica-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medell\'in, Colombia}
 
@@
 size by constructing mock fields from a large cosmological N-body
-simulation with the same geometry of observed fields. To populate the
+simulation. To populate the
 halos in the simulation we use a model where a dark matter halo with
@@
 one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
-1.0$. We avoid the large uncertainties in the estimation of \ly
-luminosities with this approach. Our main result is that the
-clustering and number density information are insufficient to impose a
-tight constraint on the {\bf   occupation} fraction. On the other hand
-the minimum mass and maximum mass can be constrained to the range $M_{\rm max}<10^{12}$\hMsun and $10^{10}\hMsun\leq M_{\rm min}\leq
-10^{11.5}\hMsun$.  We also find that the consistent models have a narrow mass
-range, $\Delta M \equiv \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$,
-smaller than $1.0$ dex, with a vast majority in the range $\Delta
-M<0.5$ dex. {\bf These mass ranges are a sub-set of already published
-constraints, while the wide range of values for the escape fraction
-  are a novel result}. There is an inconclusive response as to
-which is the occupation fraction for LAEs at $z=3.1$. A precise answer
-requires observations on larger fields and robust physical models for
-the connection between dark matter, star formation and the escape of
-\ly radiation. That kind of modeling should also be able to provide a
-plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
-derived here for the halos hosting LAEs at $z=3.1$.
-
+1.0$. {\bf We use this approach to avoid the uncertainties associated
+  to the estimation of \ly luminosities in each halo.} Our analysis
+shows that the clustering and number density information are
+insufficient to impose a tight constraint on the {\bf   occupation}
+fraction. On the other hand, the minimum mass and maximum mass can be
+constrained to the range $M_{\rm  max}<10^{12}$\hMsun and
+$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
+that the consistent models have a narrow mass range, $\Delta M \equiv
+\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
+with a majority in the range $\Delta M<0.5$ dex. {\bf These results
+  broadly reproduce some constraints   already presented in the
+  literature. However, the wide range of  values for the escape
+  fraction and the narrow mass ranges are novel results from
+  the approach presented here}. We conclude that achieving a constraint on the
+occupation fraction for LAEs at $z=3.1$ will require observations on
+larger fields to reduced cosmic variance and robust physical models
+for the connection between dark matter, star formation and the escape
+of \ly radiation. That kind of modeling should also be able to provide
+a plausible explanation for the narrow mass range derived here for the
+halos hosting LAEs at $z=3.1$. 
 \end{abstract}

### 2014-01-20 paper/ms.tex
final corrections on ms

@@
 fraction. On the other hand, the minimum mass and maximum mass can be
-constrained to the range $M_{\rm  max}<10^{12}$\hMsun and
+constrained to the range $M_{\rm  max}<10^{12}$\hMsun\ and
 $10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$. We also find
@@
   broadly reproduce some constraints   already presented in the
-  literature. However, the wide range of  values for the escape
-  fraction and the narrow mass ranges are novel results from
+  literature. However, the wide range of values for the occupation
+  fraction and the narrow mass range $\Delta M$ are novel results from
   the approach presented here}. We conclude that achieving a constraint on the
@@
 
-Our method first populates DM halos in cosmological simulations with
-LAEs. We only consider whether a DM can host a detectable LAE or not
-without predicting a \ly  luminosity. This bypasses all the physical
-uncertainties involved in the estimation of observed \ly luminosities.
-Once we have the mock LAE catalogs, we compare them against
-observations in terms of the  statistics on the number density
-distribution derived from the observations over the 12 fields of
-\cite{Yamada2012}. We also use measurements of the angular
-correlation function to improve these constraints. This method allows
-us to constraint the preferred mass range and occupation fraction of DM
-halos hosting LAEs.
+The method we use here firstly populates DM halos in cosmological
+simulations with LAEs. We only consider whether a DM can host a
+detectable LAE or not without predicting a \ly  luminosity. This
+bypasses all the physical uncertainties involved in the estimation of
+observed \ly luminosities. Once we have the halos hosting a LAE, we
+build mock surveys following the geometry of the observed fields by
+\cite{Yamada2012}. This allows us to take explicitly into account the
+effect of cosmic variance. We used this mock surveys to compared them
+against observations in terms of the number density distribution and
+the angular correlation function. This allows us to constraint the
+preferred mass range and occupation fraction of DM halos hosting LAEs.
 
@@
 observations. In \S \ref{sec:results} we present the main results for
-the halo mass and occupation fraction. We continue with a discussion
-of these results under the light of other observational and
-theoretical results. Finally, we present our conclusions in \S
-\ref{sec:conclusions}.
+the halo mass and occupation fraction. We continue in \S
+\ref{sec:discussion} with a discussion under the light of other
+constraints already presented in the literature and theoretical
+considerations of galaxy formation studies. Finally, we present our
+conclusions in \S \ref{sec:conclusions}.
 
@@
 \includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
-\caption{ \label{fig:halos} Left panel. Distribution of LAE number
+\caption{ \label{fig:halos} Left panel. Cumulative distribution of LAE number
   densities in all the fields observed by \citet{Yamada2012}. The
@@
 \AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
-sub-fields,  this corresponds to average surface number density of
+sub-fields,  this corresponds to an average surface number density of
 $0.24\pm 0.01$ arcmin$^{-2}$.
@@
   is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
-  the general fields in \cite{Yamada2012}}
-
-\subsection{The adequacy of including SSA22 as an observational benchmark}
+  the general fields in \cite{Yamada2012}. In spite of these
+  differences \cite{Ouchi2008} provides the most similar conditions
+  to \cite{Yamada2012}.}
+
+\subsubsection{The adequacy of including SSA22 as an observational benchmark}
 
@@
   evident that there is only one sub-field  that stands out as an
-  outlier in the distribution (it corresponds to  the densest field in
-  SSA22). All the other fields form a continuous  distribution in
+  outlier in the distribution, corresponding to  the densest field in
+  SSA22. All the other fields form a continuous  distribution in
   number density.}
@@
   density distribution from a simulation will include a very dense
-  field. We do not require the presence of such field to judge a mock
-  distribution as successful. The statistical test we perform to
-  compare mock distributions   against   observations does not require
-  such a perfect match. }
+  field. For this reason we do not require the presence of a very
+  dense field such as SSA22-1 to judge a mock distribution as
+  successful. The statistical test we use o compare mock
+  distributions against observations does not require such a perfect
+  match. }
 
@@
 \includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
-\caption{ \label{fig:distros} Spatial distribution of a LAEs in a mock
+\caption{ \label{fig:distros} Example of the spatial distribution of a LAEs in a mock
   survey with model parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
-    max}=10.5$ and $f_{\rm occ}=0.1$ for the {\texttt{match}}
-  method. The larger panel shows $7$ mock
-  fields together mimicking the SSA22 region. The intermediate panel
-  shows $3$ mock fields corresponding to the SXDS region. The lower
-  panels represent the SDF and GOODS-North fields. The same model has
-  another 14 associated mock surveys build from different regions in
-  the simulation, but constructed following the same pattern.}
+    max}=10.5$ and $f_{\rm occ}=0.1$. The large panel shows $7$ mock
+  fields together mimicking the geometry of the SSA22 region. The
+  intermediate panel shows $3$ mock fields corresponding to the SXDS
+  region. The lower panels represent the SDF and GOODS-North
+  fields. The same model has another 14 associated mock surveys build
+  from different regions in the simulation, but constructed following
+  the same pattern.} 
 \end{center} 
@@
 decide whether a halo host a LAE: the lower and upper bounds for the
-mass range, $M_{\rm min}< M_{\rm h} < M_{\rm max}$, where LAEs reside and the fraction $f_{\rm occ}$ of such halos that host a detectable LAE. The reader
-must keep in mind that the physical interpretation of the occupation
-fraction $f_{\rm occ}$ convolves two phenomena: the actual presence of a star
-forming galaxy in a halo and its detectability as a LAE.
+mass range ($M_{\rm min}< M_{\rm h} < M_{\rm max}$) where LAEs reside
+and the fraction ($f_{\rm occ}$) of such halos that host a detectable
+LAE. The reader must keep in mind that the physical interpretation of
+the occupation fraction $f_{\rm occ}$ convolves two phenomena: the
+actual presence of a star forming galaxy in a halo and its
+detectability as a LAE.
 
@@
 mass range hosting detectable LAEs commonly used in photometric
-narrow-band surveys. We also want to explore a wide range of
+narrow-band surveys. We want to explore a wide range of
 possible masses for the host halos without any strong theoretical
@@
 mock fields into a mock catalog is done in two different ways. The
-first is called {\texttt{match}}, it follows the clustering of the
+first is called {\texttt{match}} because it follows the clustering of the
 observational fields. From the $12$ mock fields, $7$ are constructed
@@
 contiguous. In this \documentname we only report the results obtained
-by the {\texttt{match}} method and mention explicitly differences
-observed with the {\texttt{random}} selection.
+by the {\texttt{match}} method since we do not find any significant
+difference with respect to the {\texttt{random}} method.
 
@@
 to build the mock are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
-  max}=10^{0.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
+  max}=10^{10.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
 one out of the $15$ different mock surveys that are constructed for
@@
 ${\mathcal M}$ where $\log_{10} M_{\rm min}$ takes $30$ values from $10.0$ up
-to $12.9$ with an even spacing of $0.1$ dex. $\log_{10} M_{\rm max}$
-takes values in the same range as $\log_{10}M_{\rm min}$ only with a
+to $12.9$ with an even spacing of $0.1$ dex, $\log_{10} M_{\rm max}$
+takes values in the same range as $\log_{10}M_{\rm min}$ with a
 displacement of $0.1$ dex in the whole range. The occupation fraction
@@
 consistent with observations if the two parameters $\beta$ and
-$\theta_0$ are equal within a $1$-$\sigma$ range.}
+$\theta_0$ are equal within a $1$-$\sigma$ range. We perform this
+comparison only with the fields constructed using the {\texttt{match}}
+method.}
 
@@
 \caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
-    occ}$ (right) planes for all models with  KS test values
-  $P>0.05$. The color code corresponds to the number of mock surveys
-  compatible with observations. Only regions in the parameter space with
-  at least one consistent mock survey are
-  included. \label{fig:landscape}}      
+    occ}$ (right) planes for all models consistent with the
+  observational number density (KS test values
+  $P>0.05$.) The color code corresponds to the number of mock surveys
+  compatible with observations. Only regions in the parameter space
+  with at least one consistent mock survey are
+  shown. \label{fig:landscape}}      
 \end{figure*}
 
-The main purpose of this section is to show how different
+The main purpose of this section is to show how the different
 observational constraints narrow down the parameters space of allowed
@@
 surface number density lower than the observational constrain, making
-them incompatible with observations; there are simply too few halos compared to observed
-LAEs. The opposite is true in models with $M_{\rm
-  min}<10^{11.0}$\hMsun that have a surface number density larger
+them incompatible with observations; there are simply too few halos
+compared to observed LAEs. The opposite is true in models with $M_{\rm
+  min}<10^{11.0}$\hMsun, which have a surface number density larger
 observations. In those cases the maximum mass $M_{\rm max}$ and the
@@
 in the number density abundance, which is of the same order of
-magnitude as the scatter in the observational data.  As a consequence, the variation in
-the number density in mocks for models with the same mass range and occupation
-fraction can be by factors of $\sim 2-5$.  This scatter induced by
-cosmic variance is naturally included in the mock construction
-process. This variance will explain that very different models can be
-made compatible with observations.
+magnitude as the scatter in the observational data.  As a consequence,
+the variation in the number density in mocks for models with the same
+mass range and occupation fraction can be by factors of $\sim 2-5$.
+This scatter induced by cosmic variance is naturally included in the
+mock construction process.
 
@@
 between the mocks and observations yields values of $P>0.05$ for at
-least one mock survey in each model. For those models it
-is not possible reject the hypothesis that the simulated and observed
-data for the surface number density come from the same parent
-distribution.
-
-In total, there are between $550$ to $600$ models out of the original
+least one mock survey.
+
+There are between $550$ to $600$ models out of the original
 $9000$ models that have at least one mock survey consistent with
@@
 \end{center}  
-\caption{Favored regions in parameter space when the constraints on
-  the maximal number of consistent mocks is imposed. Only the results
-  for the {\texttt{match}} method are shown.
-  \label{fig:restriction_mock}}  
+\caption{Favored regions in parameter space when we impose the
+  condition of having all the mock surveys consistent with the
+  observed number density distribution. Only the results for the
+  {\texttt{match}} method are shown. \label{fig:restriction_mock}}  
 \end{figure*}
@@
 Figure \ref{fig:restriction_mock} presents the locii of these models
-in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
-  min}-f_{\rm occ}$. With this constraint the number of consistent
+in the parameter space $M_{\rm min}$-$M_{\rm max}$ and $M_{\rm
+  min}$-$f_{\rm occ}$. With this constraint the number of consistent
 models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are reduced. This 
@@
 
-The left panel of the figure \ref{fig:correlation_parameters} shows the results for the
-best estimates of $\theta_{0}$-$\beta$  used in the ACF
-parameterization.  Blue circles with error bars represent the results
-from the mocks and the horizontal line the observational results of
-\cite{Ouchi2010} over a field with average number density where the
-$\beta$ parameter was fixed in the fit. From this Figure we observe
-that there are models with too large values of $\theta_0$ and $\beta$
-that can be ruled out as inconsistent with the angular correlation
-function.
+The left panel in Figure \ref{fig:correlation_parameters} shows the
+results for the best estimates of $\theta_{0}$-$\beta$  used in the
+ACF parameterization on the best models previously selected.  Blue
+circles with error bars represent the results from the mocks and the
+horizontal line the observational results of \cite{Ouchi2008} over a
+field with average number density where the $\beta$ parameter was
+fixed in the fit. From this Figure we observe that there are models
+with too large values of $\theta_0$ and/or $\beta$ that can be ruled
+out as inconsistent.
 
@@
 correlation length $\theta_0$ and the exponent $\beta$.  We find that
-we end up with $40$ models consistent with the ACF constraints.
-
-Comparing Figure
-\ref{fig:restriction_mock_and_f_occ_corr} with Figure
+we end up with $40$ models consistent with the ACF constraints.  This
+is a reduction of a factor of $\sim 2$ with respect to the number of
+models consistent with the number density distribution.
+
+Comparing Figure \ref{fig:restriction_mock_and_f_occ_corr} with Figure
 \ref{fig:restriction_mock} we see that the new constraint disfavors
-almost all models with $M_{\rm max}>10^{12}$. The only exception is 
-a narrow range of models with $M_{\rm min}=10^{10.9}$. However, in the right panel of figure  \ref{fig:correlation_parameters}   we can observe that these models are only 
-marginally consistent with the ACF constraints in  $\theta_0$.
+almost all models with $M_{\rm max}>10^{12}$. The only exception is a
+narrow range of models with $M_{\rm min}=10^{10.9}$. However, in the
+right panel of figure  \ref{fig:correlation_parameters}   we can
+observe that these models are only  marginally consistent with the ACF
+constraints in  $\theta_0$.
 
 From this comparison we conclude that clustering information can
-constrain the values of $M_{\rm max}$, but not the occupation
-fraction.
+constrain the values of $M_{\rm max}$. We emphasize that the
+occupation fraction continues to be unconstrained.
 
@@
 bars in the theoretical data correspond to the quadratic average of
-the fitting uncertainties for each mock survey.
-Right panel.
-Values of $\theta_{0}$  and $\log_{10}(M_{min}/M_{\odot} h^{-1})$.
-Blue and green point represents the models where  $\log_{10}(M_{max}/M_{\odot} h^{-1})<12.0$ and  $\log_{10}(M_{min}/M_{\odot} h^{-1})>12.0$ respectively.
-.
-The horizontal gray band represents the observational contraints on $theta_{0}$ stablished by   \citet{Ouchi2008,Ouchi2010}.
-Green points has been displaced by $0.01dex$ of its original value to avoid overlapping between blue and green points.} \label{fig:correlation_parameters}
+the fitting uncertainties for each mock survey. Right panel. Values of
+$\theta_{0}$  and $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})$. Blue and
+green point represents the models where  $\log_{10}(M_{\rm max}/M_{\odot}
+h^{-1})<12.0$ and  $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})>12.0$
+respectively. .  The horizontal gray band represents the observational
+constraints on $theta_{0}$ established by
+\citet{Ouchi2008,Ouchi2010}. Green points has been displaced by
+$0.01$ dex of its original value to avoid overlapping between blue and
+green points.} \label{fig:correlation_parameters}   
 \end{figure*}
@@
 {\bf The models in the third family are barely consistent with the
-  constraints from the ACF. These 
-  models they have another particular feature: their minimum mass is
-  exactly $M_{\rm min}=10^{10.9}\hMsun$ m and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$ close to $1.0$
-  (instead of the observational value of $0.8$) and $\theta_0$ on the
-  range of $13^{\prime}$ (the mean observational value is close to
-  $8^{\prime}$) but are considered
-  consistent because their large error bars barely overlap with the
-  observational expectation (see figure \ref{fig:correlation_parameters})  .  Because these models are
-  are barely compatible with observations and are a minority of the
-  consistent models, we exclude them from the rest of the discussion.}
+  constraints from the ACF. These models they have another particular
+  feature: their minimum mass is exactly $M_{\rm min}=10^{10.9}\hMsun$
+  and $M_{\rm max}>10^{12.0}\hMsun$ . They have values of $\beta$
+  close to $1.0$ (instead of the observational value of $0.8$) and
+  $\theta_0$ on the range of $13^{\prime}$ (the mean observational
+  value is close to $8^{\prime}$) but are considered consistent
+  because their large error bars barely overlap with the observational
+  expectation (see figure \ref{fig:correlation_parameters}).
+  Because these models are are barely compatible with observations and
+  are a minority of the consistent models, we exclude them from the
+  discussion.}
 
@@
 \end{center}
-\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
-    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
+\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
+    min}$-$f_{\rm occ}$ (right) planes showing the models fulfilling both
    constraints on the maximal number of consistent mocks and the
-  angular correlation function. The observational data for the ACF
-  corresponds to 
-  \citet{Ouchi2008,Ouchi2010}.   
+  angular correlation function from \citet{Ouchi2008,Ouchi2010}.   
   \label{fig:restriction_mock_and_f_occ_corr}} 
@@
 to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
-$\Delta M\leq 1.0$.
+$\Delta M\leq 1.0$, {\bf half of them $\Delta M\leq 0.5$}.
 
@@
   not take  account the effect of cosmic variance in the same way we
-  propose in this \documentname. Nevertheless, the mass range
-  predicted by our models is consistent with already published
+  propose in this \documentname. Nevertheless, values of an occupation
+  fraction $f_{\rm occ}=0.1$ and the mass range
+  predicted by all of our models is consistent with already published
   observational results \citep{Gawiser07,Ouchi2010}. This suggests
@@
   interpretation for the existence of such  a narrow mass range. We
-  can start with a reasonable   assumption. Namely that star formation
+  can start with a reasonable   assumption. Namely, that star formation
   rate increases with halo's  mass. Under this assumption the cut at
@@
 Our results are in a general good agreement with those estimates for
-the host mass. This is not completely unexpected given that we have
-also required consistency with ACF measurements. These expectations
-are {\bf mostly} matched by the first family of models, also summarized in Table
-\ref{table:firstfamily}. These models, which favor only the 
-low ($\sim 10\%$) occupations fractions, are also consistent in that
-       regards with the observational expectations by \cite{Gawiser07}.
+the host mass and the upper limit of the occupation fraction. This is
+not completely unexpected given that we have also required consistency
+with ACF measurements. These expectations are {\bf mostly} matched by
+the first family of models, also summarized in Table
+\ref{table:firstfamily}. These models, which favor only the  low
+($\sim 10\%$) occupations fractions, are also consistent in that
+regard with the observational expectations by \cite{Gawiser07}.
 
 The novelty in our results is that we have a detailed estimate for 
-host halo mass range together with the escape fraction. This allows us
+host halo mass range together with the occupation fraction. This allows us
 to show that the halo mass range can, in some cases, be narrow $\Delta M <
@@
 find that an ACF analysis is not enough to rule
-out models with a high occupation fraction $f_{\rm occ}>0.3$, which
-represent half of our best models.
+out models with a high occupation fraction $f_{\rm occ}>0.2$.
 
@@
 $M_{\rm min}$ and $M_{\rm max}$ should not be considered exact within
-less than $\sim 0.2$ dex.
+less than $\sim 0.2$ dex. However, this represents a systematic change
+in the mass values and the mass interval $\Delta M$ quoted here should
+remain unchanged.
 
@@
 favored model parameters $M_{\rm  min}$ and $M_{\rm max}$ by about the
-same factor of $\sim2$. }
+same factor of $\sim2$ or $0.3$ dex. }
 
@@
   \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
-  confidence that the two different samples can give a self-consistent picture
-  within a factor of $\sim2$ for our studies.}
+  confidence that the two different samples can give a self-consistent picture.}
 
@@
 In this \documentname we look for constraints on the preferred mass
-and occupation fraction of dark matter halos hosting Lyman $\alpha$ Emitters at
-redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform this study
-paying special attention to the impact of cosmic variance on these
-results. To this end we build a large number of mock catalogs matching
-observational geometries. The mocks are constructed from a N-body simulation
-following a simple recipe to assign a single LAE to each halo whereby only
-a fraction $f_{\rm occ}$ of halos within a mass range  $M_{\rm
-  min}\leq M_{\rm h}\leq M_{\rm   max}$ can host a LAE.
-
-We then proceed with a
-thorough exploration of the space of free parameters $M_{\rm min},
-M_{\rm max}$ and $f_{\rm occ}$ to find mocks that are consistent with
-two observational constraints: the surface number density distribution
-and the angular correlation function. Out of the initial $9000$ 
-combinations of parameters in the model we find $40$ combination of parameters
-consistent with observations.
-
-{\bf We find that the information for the number density constrains
-  the minium mass to the range
+and occupation fraction of dark matter halos hosting Lyman $\alpha$
+Emitters at redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform
+this study paying special attention to the impact of cosmic variance
+on these results. To this end we build a large number of mock catalogs
+matching observational geometries. The mocks are constructed from a
+N-body simulation following a simple recipe to assign a single LAE to
+each halo whereby only a fraction $f_{\rm occ}$ of halos within a mass
+range  $M_{\rm min}\leq M_{\rm h}\leq M_{\rm   max}$ can host a
+LAE. The main motivation to implement this kind of model is to avoid
+all the uncertainties in the estimation of \ly luminosities.
+
+We then proceed with a thorough exploration of the space of free
+parameters $M_{\rm min}, M_{\rm max}$ and $f_{\rm occ}$ to find mocks
+that are consistent with two observational constraints: the surface
+number density distribution and the angular correlation function. Out
+of the initial $9000$  combinations of parameters in the model we find
+$40$ combination of parameters consistent with observations.
+
+{\bf We find that the number density can constrain the minimum mass to the range
   $10^{10}\hMsun < M_{\rm min} < 10^{11.5}\hMsun$ while the clustering
   constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
-  this information is insufficient to impose a tight constraint  on the escape
-  fraction. Additionaly, we find that the mass range defined as
+  this information is insufficient to impose a tight constraint on the
+  occupation fraction. Additionally, we find that the mass range defined as
 $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is $\Delta
@@
 
-{\bf Our approach has allowed the discovery of possible models that have
+{\bf This approach the discovery of consistent models that have
 been overlooked so far in the literature. A central role in these new
-models is played by the wide range of escape fraction values,
+models is played by the wide range of occupation fraction values,
 something unexpected from previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that unanimously favor low values on the range of $10^{-2}$. The largest
-innovation in our analysis is the construction of mock obsevations
+innovation in our analysis is the construction of mock observations
 that directly explore the impact of cosmic variance.}
@@
 preferred models support the notion that the most massive halos at
-$z=3.1$ do not host detectable LAEs. {\bf Furthermore, we claim that the
-mass range for halos hosting LAEs is narrow, $\Delta M\leq 1.0$, with
-a majority of models with $\Delta M\leq 0.5$.}
-
-The existence of models with narrow mass ranges has at least two
-different explanations. The first is having LAEs with a decreasing \ly
-escape fraction with increasing mass, the second is having larger
-screening effects by neutral Hydrogen around the most massive systems
-\citep{Laursen2009,ForeroRomero2011}.
-
-We also find extreme cases with a very narrow $\Delta M<0.3$, meaning that
-there is barely a factor of $\sim 2$ between the minimum and halo
-mass. If this can be confirmed, it would mean a great
-challenge for galaxy formation models to explain how is that LAEs can
-be hosted in such a narrow range of halo mass.
+$z=3.1$ do not host detectable LAEs.
 
 In summary, we show that {\bf the currently available spatial
-  information of LAEs cannot put a tight constraint on their
-  occupation fraction of dark matter halos}. This information can
+  information of LAEs can put a tight constraint on the halo mass
+  range but not on the occupation fraction}. This information can
 confidently be used to establish that these galaxies are hosted in low

### 2014-01-20 paper/reply.tex
new reply

@@
   exploring very low escape fractions values of the range $0.01$ would
-  require building mock catalogs with a minimum mass around the range
-  $10^{9.5}$Msun or below which is precisely the minimum halo mass of
+  require building mock catalogs with a minimum mass below the range of
+  $10^{9.5}$Msun which is precisely the minimum halo mass of
   that is resolved in the simulation. This intrinsic limitation on the

### 2014-01-20 paper/ms.tex
submitted version

@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+%\bibliography{references} 
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
+  et~al.}{2013a}]{Behroozi2013b}
+{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013a, \apjl, 762, L31
+
+\bibitem[\protect\citeauthoryear{{Behroozi}, {Wechsler} \& {Conroy}}{{Behroozi}
+  et~al.}{2013b}]{Behroozi2013a}
+{Behroozi} P.~S.,  {Wechsler} R.~H.,    {Conroy} C.,  2013b, \apj, 770, 57
+
+\bibitem[\protect\citeauthoryear{{Colberg}, {White}, {Yoshida}, {MacFarland},
+  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
+  {Thomas} \& {Virgo Consortium}}{{Colberg} et~al.}{2000}]{Colberg00}
+{Colberg} J.~M.,  {White} S.~D.~M.,  {Yoshida} N.,  {MacFarland} T.~J.,
+  {Jenkins} A.,  {Frenk} C.~S.,  {Pearce} F.~R.,  {Evrard} A.~E.,  {Couchman}
+  H.~M.~P.,  {Efstathiou} G.,  {Peacock} J.~A.,  {Thomas} P.~A.,    {Virgo
+  Consortium} 2000, \mnras, 319, 209
+
+\bibitem[\protect\citeauthoryear{{Dayal}, {Ferrara}, {Saro}, {Salvaterra},
+  {Borgani} \& {Tornatore}}{{Dayal} et~al.}{2009}]{Dayal2009}
+{Dayal} P.,  {Ferrara} A.,  {Saro} A.,  {Salvaterra} R.,  {Borgani} S.,
+  {Tornatore} L.,  2009, \mnras, 400, 2000
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
+  {Kramer}}{2012}]{Dijkstra2012}
+{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Mesinger} \& {Wyithe}}{{Dijkstra}
+  et~al.}{2011}]{Dijkstra11}
+{Dijkstra} M.,  {Mesinger} A.,    {Wyithe} J.~S.~B.,  2011, \mnras, 414, 2139
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero} \& {Dijkstra}}{{Forero-Romero}
+  \& {Dijkstra}}{2013}]{ForeroRomero2013}
+{Forero-Romero} J.~E.,  {Dijkstra} M.,  2013, \mnras, 428, 2163
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero}
+  et~al.}{2011}]{ForeroRomero2011}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber} \&
+  {Prada}}{{Forero-Romero} et~al.}{2012}]{ForeroRomero2012}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,    {Prada} F.,  2012,
+  \mnras, 419, 952
+
+\bibitem[\protect\citeauthoryear{{Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
+  {Verhamme} \& {Hayes}}{{Garel} et~al.}{2012}]{Garel2012}
+{Garel} T.,  {Blaizot} J.,  {Guiderdoni} B.,  {Schaerer} D.,  {Verhamme} A.,
+  {Hayes} M.,  2012, \mnras, 422, 310
+
+\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
+  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio} \&
+  {Feldmeier}}{{Gawiser} et~al.}{2007}]{Gawiser2007}
+{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
+  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
+  G.~A.,  {Fazio} G.,    {Feldmeier} J.~J.,  2007, \apj, 671, 278
+
+\bibitem[\protect\citeauthoryear{{Gawiser}, {Francke}, {Lai}, {Schawinski},
+  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio},
+  {Feldmeier}, {Huang}, {Infante}, {Lira} \& {Padilla}}{{Gawiser}
+  et~al.}{2007}]{Gawiser07}
+{Gawiser} E.,  {Francke} H.,  {Lai} K.,  {Schawinski} K.,  {Gronwall} C.,
+  {Ciardullo} R.,  {Quadri} R.,  {Orsi} A.,  {Barrientos} L.~F.,  {Blanc}
+  G.~A.,  {Fazio} G.,  {Feldmeier} J.~J.,  {Huang} J.-s.,  {Infante} L.,
+  {Lira} P.,    {Padilla} N.,  2007, \apj, 671, 278
+
+\bibitem[\protect\citeauthoryear{{Gronwall}, {Ciardullo}, {Hickey}, {Gawiser},
+  {Feldmeier}, {van Dokkum}, {Urry}, {Herrera}, {Lehmer}, {Infante}, {Orsi},
+  {Marchesini}, {Blanc}, {Francke}, {Lira} \& {Treister}}{{Gronwall}
+  et~al.}{2007}]{Gronwall07}
+{Gronwall} C.,  {Ciardullo} R.,  {Hickey} T.,  {Gawiser} E.,  {Feldmeier}
+  J.~J.,  {van Dokkum} P.~G.,  {Urry} C.~M.,  {Herrera} D.,  {Lehmer} B.~D.,
+  {Infante} L.,  {Orsi} A.,  {Marchesini} D.,  {Blanc} G.~A.,  {Francke} H.,
+  {Lira} P.,    {Treister} E.,  2007, \apj, 667, 79
+
+\bibitem[\protect\citeauthoryear{{Guaita}, {Francke}, {Gawiser}, {Bauer},
+  {Hayes}, {{\"O}stlin} \& {Padilla}}{{Guaita} et~al.}{2013}]{Guaita2013}
+{Guaita} L.,  {Francke} H.,  {Gawiser} E.,  {Bauer} F.~E.,  {Hayes} M.,
+  {{\"O}stlin} G.,    {Padilla} N.,  2013, \aap, 551, A93
+
+\bibitem[\protect\citeauthoryear{{Hayashino}, {Matsuda}, {Tamura}, {Yamauchi},
+  {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi},
+  {Shimasaku}, {Shioya} \& {Taniguchi}}{{Hayashino}
+  et~al.}{2004}]{Hayashino2004}
+{Hayashino} T.,  {Matsuda} Y.,  {Tamura} H.,  {Yamauchi} R.,  {Yamada} T.,
+  {Ajiki} M.,  {Fujita} S.~S.,  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,
+  {Okamura} S.,  {Ouchi} M.,  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,
+  2004, \aj, 128, 2073
+
+\bibitem[\protect\citeauthoryear{{Jarosik}, {Bennett}, {Dunkley}, {Gold},
+  {Greason}, {Halpern}, {Hill}, {Hinshaw}, {Kogut}, {Komatsu}, {Larson} \&
+  {Limon}}{{Jarosik} et~al.}{2011}]{Jarosik2011}
+{Jarosik} N.,  {Bennett} C.~L.,  {Dunkley} J.,  {Gold} B.,  {Greason} M.~R.,
+  {Halpern} M.,  {Hill} R.~S.,  {Hinshaw} G.,  {Kogut} A.,  {Komatsu} E.,
+  {Larson} D.,    {Limon} M.,  2011, \apjs, 192, 14
+
+\bibitem[\protect\citeauthoryear{{Jose}, {Srianand} \& {Subramanian}}{{Jose}
+  et~al.}{2013}]{Jose2013b}
+{Jose} C.,  {Srianand} R.,    {Subramanian} K.,  2013, ArXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
+  {Primack}}{{Klypin} et~al.}{2011}]{Bolshoi}
+{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102
+
+\bibitem[\protect\citeauthoryear{{Koehler}, {Schuecker} \&
+  {Gebhardt}}{{Koehler} et~al.}{2007}]{Koehler2007}
+{Koehler} R.~S.,  {Schuecker} P.,    {Gebhardt} K.,  2007, \aap, 462, 7
+
+\bibitem[\protect\citeauthoryear{{Komatsu}, {Dunkley}, {Nolta}, {Bennett},
+  {Gold}, {Hinshaw}, {Jarosik}, {Larson}, {Limon}, {Page}, {Spergel} \&
+  {Halpern}}{{Komatsu} et~al.}{2009}]{Komatsu2009}
+{Komatsu} E.,  {Dunkley} J.,  {Nolta} M.~R.,  {Bennett} C.~L.,  {Gold} B.,
+  {Hinshaw} G.,  {Jarosik} N.,  {Larson} D.,  {Limon} M.,  {Page} L.,
+  {Spergel} D.~N.,    {Halpern} M.,  2009, \apjs, 180, 330
+
+\bibitem[\protect\citeauthoryear{{Kudritzki}, {M{\'e}ndez}, {Feldmeier},
+  {Ciardullo}, {Jacoby}, {Freeman}, {Arnaboldi}, {Capaccioli}, {Gerhard} \&
+  {Ford}}{{Kudritzki} et~al.}{2000}]{Kudritzki2000}
+{Kudritzki} R.-P.,  {M{\'e}ndez} R.~H.,  {Feldmeier} J.~J.,  {Ciardullo} R.,
+  {Jacoby} G.~H.,  {Freeman} K.~C.,  {Arnaboldi} M.,  {Capaccioli} M.,
+  {Gerhard} O.,    {Ford} H.~C.,  2000, \apj, 536, 19
+
+\bibitem[\protect\citeauthoryear{{Landy} \& {Szalay}}{{Landy} \&
+  {Szalay}}{1993}]{Landy1993}
+{Landy} S.~D.,  {Szalay} A.~S.,  1993, \apj, 412, 64
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013}
+{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Razoumov} \&
+  {Sommer-Larsen}}{{Laursen} et~al.}{2009}]{Laursen2009}
+{Laursen} P.,  {Razoumov} A.~O.,    {Sommer-Larsen} J.,  2009, \apj, 696, 853
+
+\bibitem[\protect\citeauthoryear{{Laursen} \& {Sommer-Larsen}}{{Laursen} \&
+  {Sommer-Larsen}}{2007}]{Laursen2007}
+{Laursen} P.,  {Sommer-Larsen} J.,  2007, \apjl, 657, L69
+
+\bibitem[\protect\citeauthoryear{{Matsuda}, {Yamada}, {Hayashino}, {Tamura},
+  {Yamauchi}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi}, {Shimasaku},
+  {Shioya} \& {Taniguchi}}{{Matsuda} et~al.}{2005}]{Matsuda2005}
+{Matsuda} Y.,  {Yamada} T.,  {Hayashino} T.,  {Tamura} H.,  {Yamauchi} R.,
+  {Murayama} T.,  {Nagao} T.,  {Ohta} K.,  {Okamura} S.,  {Ouchi} M.,
+  {Shimasaku} K.,  {Shioya} Y.,    {Taniguchi} Y.,  2005, \apjl, 634, L125
+
+\bibitem[\protect\citeauthoryear{{More}, {Kravtsov}, {Dalal} \&
+  {Gottl{\"o}ber}}{{More} et~al.}{2011}]{More2011}
+{More} S.,  {Kravtsov} A.~V.,  {Dalal} N.,    {Gottl{\"o}ber} S.,  2011, \apjs,
+  195, 4
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{Neufeld1991}
+{Neufeld} D.~A.,  1991, \apjl, 370, L85
+
+\bibitem[\protect\citeauthoryear{{Nilsson}, {M{\o}ller}, {M{\"o}ller}, {Fynbo},
+  {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen} \&
+  {Grove}}{{Nilsson} et~al.}{2007}]{Nilsson2007}
+{Nilsson} K.~K.,  {M{\o}ller} P.,  {M{\"o}ller} O.,  {Fynbo} J.~P.~U.,
+  {Micha{\l}owski} M.~J.,  {Watson} D.,  {Ledoux} C.,  {Rosati} P.,  {Pedersen}
+  K.,    {Grove} L.~F.,  2007, \aap, 471, 71
+
+\bibitem[\protect\citeauthoryear{{Nilsson}, {Tapken}, {M{\o}ller}, {Freudling},
+  {Fynbo}, {Meisenheimer}, {Laursen} \& {{\"O}stlin}}{{Nilsson}
+  et~al.}{2009}]{Nilsson2009}
+{Nilsson} K.~K.,  {Tapken} C.,  {M{\o}ller} P.,  {Freudling} W.,  {Fynbo}
+  J.~P.~U.,  {Meisenheimer} K.,  {Laursen} P.,    {{\"O}stlin} G.,  2009, \aap,
+  498, 13
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
+  et~al.}{2012}]{Orsi2012}
+{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87
+
+\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
+  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
+  {Okamura}, {Iye}, {Takata}, {Yoshida} \& {Yoshida}}{{Ouchi}
+  et~al.}{2008}]{Ouchi2008}
+{Ouchi} M.,  {Shimasaku} K.,  {Akiyama} M.,  {Simpson} C.,  {Saito} T.,  {Ueda}
+  Y.,  {Furusawa} H.,  {Sekiguchi} K.,  {Yamada} T.,  {Kodama} T.,  {Kashikawa}
+  N.,  {Okamura} S.,  {Iye} M.,  {Takata} T.,  {Yoshida} M.,    {Yoshida} M.,
+  2008, \apjs, 176, 301
+
+\bibitem[\protect\citeauthoryear{{Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
+  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
+  {Okamura}, {Simpson} \& {Yoshida}}{{Ouchi} et~al.}{2010}]{Ouchi2010}
+{Ouchi} M.,  {Shimasaku} K.,  {Furusawa} H.,  {Saito} T.,  {Yoshida} M.,
+  {Akiyama} M.,  {Ono} Y.,  {Yamada} T.,  {Ota} K.,  {Kashikawa} N.,  {Iye} M.,
+   {Kodama} T.,  {Okamura} S.,  {Simpson} C.,    {Yoshida} M.,  2010, \apj,
+  723, 869
+
+\bibitem[\protect\citeauthoryear{{Peebles}}{{Peebles}}{1980}]{Peebles1980}
+{Peebles} P.~J.~E.,  1980, {The large-scale structure of the universe}
+
+\bibitem[\protect\citeauthoryear{{Pentericci}, {Grazian}, {Fontana},
+  {Castellano}, {Giallongo}, {Salimbeni} \& {Santini}}{{Pentericci}
+  et~al.}{2009}]{Pentericci2009}
+{Pentericci} L.,  {Grazian} A.,  {Fontana} A.,  {Castellano} M.,  {Giallongo}
+  E.,  {Salimbeni} S.,    {Santini} P.,  2009, \aap, 494, 553
+
+\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
+  Granger}{2007}]{IPython}
+P\'erez F.,  Granger B.~E.,  2007, {C}omput. {S}ci. {E}ng., 9, 21
+
+\bibitem[\protect\citeauthoryear{Riebe, Partl, Enke, Forero-Romero, Gottlöber,
+  Klypin, Lemson, Prada, Primack, Steinmetz \& Turchaninov}{Riebe
+  et~al.}{2013}]{MultiDark}
+Riebe K.,  Partl A.~M.,  Enke H.,  Forero-Romero J.,  Gottlöber S.,  Klypin
+  A.,  Lemson G.,  Prada F.,  Primack J.~R.,  Steinmetz M.,    Turchaninov V.,
+  2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[\protect\citeauthoryear{{Springel}, {White}, {Jenkins}, {Frenk},
+  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
+  {Thomas}, {Couchman}, {Evrard}, {Colberg} \& {Pearce}}{{Springel}
+  et~al.}{2005}]{SpringelNature05}
+{Springel} V.,  {White} S.~D.~M.,  {Jenkins} A.,  {Frenk} C.~S.,  {Yoshida} N.,
+   {Gao} L.,  {Navarro} J.,  {Thacker} R.,  {Croton} D.,  {Helly} J.,
+  {Peacock} J.~A.,  {Cole} S.,  {Thomas} P.,  {Couchman} H.,  {Evrard} A.,
+  {Colberg} J.,    {Pearce} F.,  2005, \nat, 435, 629
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
+  {Maselli}}{{Verhamme} et~al.}{2006}]{Verhamme2006}
+{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397
+
+\bibitem[\protect\citeauthoryear{{Walker-Soler}, {Gawiser}, {Bond}, {Padilla}
+  \& {Francke}}{{Walker-Soler} et~al.}{2012}]{Soler2012}
+{Walker-Soler} J.~P.,  {Gawiser} E.,  {Bond} N.~A.,  {Padilla} N.,    {Francke}
+  H.,  2012, \apj, 752, 160
+
+\bibitem[\protect\citeauthoryear{{Yajima}, {Choi} \& {Nagamine}}{{Yajima}
+  et~al.}{2012}]{Yajima2012}
+{Yajima} H.,  {Choi} J.-H.,    {Nagamine} K.,  2012, \mnras, 427, 2889
+
+\bibitem[\protect\citeauthoryear{{Yamada}, {Nakamura}, {Matsuda}, {Hayashino},
+  {Yamauchi}, {Morimoto}, {Kousai} \& {Umemura}}{{Yamada}
+  et~al.}{2012}]{Yamada2012}
+{Yamada} T.,  {Nakamura} Y.,  {Matsuda} Y.,  {Hayashino} T.,  {Yamauchi} R.,
+  {Morimoto} N.,  {Kousai} K.,    {Umemura} M.,  2012, \aj, 143, 79
+
+\bibitem[\protect\citeauthoryear{{Zheng}, {Cen}, {Trac} \&
+  {Miralda-Escud{\'e}}}{{Zheng} et~al.}{2010}]{Zheng2010}
+{Zheng} Z.,  {Cen} R.,  {Trac} H.,    {Miralda-Escud{\'e}} J.,  2010, \apj,
+  716, 574
+
+\end{thebibliography}
 

### 2014-03-27 paper/ms.tex
shorter

--- 2014-01-20 paper/ms.tex
@@
-\documentclass[usenatbib]{mn2e}
+\documentclass{emulateapj}
+%\documentclass{aastex}
+\submitted{{\it Submitted for publication in ApJL}}
+\usepackage {graphicx}
+
 \usepackage{amsmath}
@@
 \usepackage{graphics}
-\usepackage{graphicx}
 \usepackage{epsfig}
+\usepackage{float}
+\bibliographystyle{apj}
 \def\be{\begin{equation}}
@@
 \newcommand{\match}{{\tt match}~}
-\newcommand{\apj}{ApJ}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}
-
 \newcommand{\kms}{\,km~s$^{-1}$}
@@
 
-\title[Halo mass and occupation fraction of LAEs at$z=3.1$]{Mass and
+\title{The impact of cosmic variance on constraining the mass and
   occupation fraction of dark matter halos hosting Lyman-$\alpha$
-  emitters at $z\sim 3$}      
-\author[~J.~E. Forero-Romero and ~J.~E. Mejia-Restrepo]{
-\parbox[t]{\textwidth}{\raggedright 
+  emitters at $z \sim 3$}      
+\author{
   Jaime E. Forero-Romero$^{1}$ and
@@
 }
-\vspace*{6pt}\\
+
+\affil{
 $^{1}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
@@
 Observatorio 1515, Santiago, Chile\\
-$^3$ FACom-Instituto de F\'isica-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medell\'in, Colombia}
-
-\maketitle
+$^{3}$ FACom-Instituto de F\'isica-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medell\'in, Colombia
+}
 
@@
 one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
-1.0$. {\bf We use this approach to avoid the uncertainties associated
-  to the estimation of \ly luminosities in each halo.} Our analysis
+1.0$. We use this approach to avoid the uncertainties associated
+  to the estimation of \ly luminosities in each halo. Our analysis
 shows that the clustering and number density information are
-insufficient to impose a tight constraint on the {\bf   occupation}
+insufficient to impose a tight constraint on the occupation
 fraction. On the other hand, the minimum mass and maximum mass can be
@@
 \log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
-with a majority in the range $\Delta M<0.5$ dex. {\bf These results
+with a majority in the range $\Delta M<0.5$ dex. These results
   broadly reproduce some constraints   already presented in the
@@
   fraction and the narrow mass range $\Delta M$ are novel results from
-  the approach presented here}. We conclude that achieving a constraint on the
+  the approach presented here. We conclude that achieving a constraint on the
 occupation fraction for LAEs at $z=3.1$ will require observations on
@@
 
-\begin{keywords}
-{cosmology: theory – cosmology: large-scale structure of universe –
+\keywords{cosmology: theory – cosmology: large-scale structure of universe –
   galaxies: formation – galaxies: high-redshift – galaxies: statistics
   – galaxy: haloes}
-\end{keywords}
 
@@
 
-{\bf A secondary benchmark is the angular correlation function
+A secondary benchmark is the angular correlation function
 (ACF). \cite{Yamada2012} does not report an ACF measurement for
@@
   reported the ACF is over a region of $1$ deg$^2$ over the SXDS
-  field.  }
+  field.
 
-{\bf There are some differences between \cite{Ouchi2008} observations
+There are some differences between \cite{Ouchi2008} observations
   and those by \cite{Yamada2012}. The details in the color selection,
@@
   differences \cite{Ouchi2008} provides the most similar conditions
-  to \cite{Yamada2012}.}
+  to \cite{Yamada2012}.
 
@@
 
-{\bf The field SSA22 has been known to harbor a significant
+The field SSA22 has been known to harbor a significant
   galaxy overdensity. \cite{Yamada2012} estimates that the densest
   sub-field is likely to be a rare density peak with $3-4\sigma$
-  significance on the scale of $\sim 60$\hMpc. }
+  significance on the scale of $\sim 60$\hMpc.
 
-{\bf All the other sub-fields in SSA22 are average. They have a similar
+All the other sub-fields in SSA22 are average. They have a similar
   number density as other blank fields. The left panel in Figure
@@
   SSA22. All the other fields form a continuous  distribution in
-  number density.}
+  number density.
 
-{\bf Therefore, using the whole SSA22 region as a benchmark in the
+Therefore, using the whole SSA22 region as a benchmark in the
   number density distribution does not impose any bias. However, on
@@
   distributions against observations does not require such a perfect
-  match. }
+  match.
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.8\linewidth,angle=0]{Figure0.pdf}
-\caption{ \label{fig:distros} Example of the spatial distribution of a LAEs in a mock
-  survey with model parameters $\log_{10}M_{\rm min}=10.4$, $\log_{10}M_{\rm
-    max}=10.5$ and $f_{\rm occ}=0.1$. The large panel shows $7$ mock
-  fields together mimicking the geometry of the SSA22 region. The
-  intermediate panel shows $3$ mock fields corresponding to the SXDS
-  region. The lower panels represent the SDF and GOODS-North
-  fields. The same model has another 14 associated mock surveys build
-  from different regions in the simulation, but constructed following
-  the same pattern.} 
-\end{center} 
-\end{figure*}
-
 We assume that a dark matter halo can only host one
@@
 
-{\bf We recall that we do not perform a explicit modeling for LAE
+We recall that we do not perform a explicit modeling for LAE
 detectability. Our model does not assign a luminosity or escape
@@
 prejudice regarding the details of star formation in high-redshift
-galaxies. }
+galaxies.
 
@@
 observations. Lower values for $M_{\rm min}$ require $f_{\rm
-  occ}<0.1$, which are not considered in this \documentname.  {\bf In
+  occ}<0.1$, which are not considered in this \documentname.  In
   turn exploring occupation fractions on the order of $f_{\rm occ}=0.01$ 
@@
   by the Bolshoi simulation and therefore cannot be considered in the
-  present study.}
+  present study.
 
@@
 
-{\bf The ACF is computed using  the Landy \&  Szalay estimator
+The ACF is computed using  the Landy \&  Szalay estimator
   \citep{Landy1993}  on fields of size $1$ deg$^2$ to be compared
-  against the results reported by \cite{Ouchi2010}.}
+  against the results reported by \cite{Ouchi2010}.
 
@@
 obtain a covariance matrix that gives us the uncertainty in the
-parameters $\beta$ and $\theta_0$. {\bf We consider that a mock field is
+parameters $\beta$ and $\theta_0$.  We consider that a mock field is
 consistent with observations if the two parameters $\beta$ and
@@
 comparison only with the fields constructed using the {\texttt{match}}
-method.}
+method.
 
@@
 \label{sec:results}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig2_match_P5.pdf}
-\vspace{5mm}
-\includegraphics[width=0.49\linewidth,angle=0]{Fig3_match_P5.pdf}
-\end{center} 
-\caption{$M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm    min}$-$f_{\rm
-    occ}$ (right) planes for all models consistent with the
-  observational number density (KS test values
-  $P>0.05$.) The color code corresponds to the number of mock surveys
-  compatible with observations. Only regions in the parameter space
-  with at least one consistent mock survey are
-  shown. \label{fig:landscape}}      
-\end{figure*}
 
@@
 
-\subsection{Models consistent with the surface density distributions}
+\subsection{Maximally Consistent Models}
 
-Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
-min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test
-between the mocks and observations yields values of $P>0.05$ for at
-least one mock survey.
-
-There are between $550$ to $600$ models out of the original
-$9000$ models that have at least one mock survey consistent with
-observations. By inspection of Figure \ref{fig:landscape} we see that
-the halo number abundance is able to constraint the minimum mass
-$M_{\rm min}$ to a narrow range, while $M_{\rm max}$ and $f_{\rm occ}$
-remain largely unconstrained.
-
-In Figure \ref{fig:landscape} there are three regions of parameter
-space that can be clearly distinguished. The first corresponds to
-models where the minimum mass is high $M_{\rm min}>
-10^{11.5}\hMsun$.  For these models the number density of LAEs is too low
-to be compatible with observations.
-
-The second region corresponds to an intermediate range for the minimum
-mass $10^{10.5}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ where,
-regardless of the value of the maximum mass $M_{\rm max}$, it is
-possible to tune the occupation fraction $f_{\rm occ}$ to bring some
-of the mock surveys into good agreement with observations. In this
-region we find two extreme kinds of models. One extreme are models
-with a narrow mass interval $\Delta M\equiv \log_{10} M_{\rm max}
-- \log_{10}M_{\rm  min} <1.0$ dex. The other extreme are models with a
-large mass interval $\Delta M>1.0$ dex going up to the maximum halo
-mass present in the simulation at that redshift, with $\Delta M = 2.5$
-dex in some cases.
-
-The third region in parameter space corresponds to $M_{\rm
-  min}<10^{10.5}\hMsun$. In this case only models with a very narrow
-mass interval of at most $0.5$ dex ($M_{\rm max}<10^{11.0}\hMsun$) and low
-occupation fractions $f_{\rm occ}\leq 0.3$ are allowed.
-
-Without any additional information our method allows us to infer that
-most of the successful models are found in the second and third regions of
-parameter space. This result was expected from halo
-abundance calculations shown in Figure \ref{fig:halos} and discussed
-in the previous subsection.
-
-However, the additional information we gain with this test is the
-relative abundance of models in the parameter space. Not all 
-models in the second region have an equal abundance. By inspection of
-Figure \ref{fig:landscape} it seems that models with $\log_{10}M_{\rm
-  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}\leq 0.3$
-are preferred.  In the next sub-sections we explore in detail the
-models in this region, imposing tighter constraints on the KS test
-results and exploring the mocks' consistency with the angular correlation
-function.
-
-\subsection{Models with the largest number of consistent mock surveys}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_mass_mock.pdf} 
-\hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig5_match_f_occ_mock.pdf}
-\end{center}  
-\caption{Favored regions in parameter space when we impose the
-  condition of having all the mock surveys consistent with the
-  observed number density distribution. Only the results for the
-  {\texttt{match}} method are shown. \label{fig:restriction_mock}}  
-\end{figure*}
-
-In the previous sub-section we use a conservative criterion of
-agreement by selecting the models that had at least one mock survey
-with $P>0.05$ in the KS test. Now we turn to a more strict selection
-by requiring all the 15 constructed mock surveys to be consistent with
-observations.
-
-With this cut we find $\sim 100$ models with all the 15 mock survey
-realizations with $P>0.05$.  This cut represents a reduction by a
-factor of $\sim 6$ with respect to the total number of models with at
-least one consistent mock.
-
-Figure \ref{fig:restriction_mock} presents the locii of these models
-in the parameter space $M_{\rm min}$-$M_{\rm max}$ and $M_{\rm
-  min}$-$f_{\rm occ}$. With this constraint the number of consistent
-models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are reduced. This 
-corresponds to the regions in the parameter space in
-Figure \ref{fig:landscape} that already had a low number of 
-consistent mock surveys. On the other hand, from the right panel in
-Figure \ref{fig:restriction_mock} we see that the favored occupation
-fraction  still remain unconstrained $0\leq f_{\rm  occ}\leq 1.0$.
-
-We conclude that conditions on the number density statistics, even if they are
-very strict, only put strong constraints on the minimum mass $M_{\rm
-  min}$ but not on the other two parameter of the model $M_{\rm max}$
-and $f_{\rm occ}$.
-
-\subsection{Consistency with the Angular Correlation Function}
+We impose two major constraints in our models. First, we require a 
+models to have all its 15 mocks with a number density distribution
+consistent with observations. Second, we require that the average
+values among all mocks for the $\theta_{0}$-$\beta$ values in the
+correlation function fit to be consistent with observations
+\citep{Ouchi2008}.
 
@@
 Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
-remaining consistent models in the planes $M_{\rm min}$-$M_{\rm
+consistent models in the planes $M_{\rm min}$-$M_{\rm
   max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
@@
 models consistent with the number density distribution.
-
-Comparing Figure \ref{fig:restriction_mock_and_f_occ_corr} with Figure
-\ref{fig:restriction_mock} we see that the new constraint disfavors
-almost all models with $M_{\rm max}>10^{12}$. The only exception is a
-narrow range of models with $M_{\rm min}=10^{10.9}$. However, in the
-right panel of figure  \ref{fig:correlation_parameters}   we can
-observe that these models are only  marginally consistent with the ACF
-constraints in  $\theta_0$.
-
-From this comparison we conclude that clustering information can
-constrain the values of $M_{\rm max}$. We emphasize that the
-occupation fraction continues to be unconstrained.
 
@@
 
-{\bf The models in the third family are barely consistent with the
+The models in the third family are barely consistent with the
   constraints from the ACF. These models they have another particular
@@
   are a minority of the consistent models, we exclude them from the
-  discussion.}
+  discussion.
 
@@
 to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
-$\Delta M\leq 1.0$, {\bf half of them $\Delta M\leq 0.5$}.
+$\Delta M\leq 1.0$, half of them $\Delta M\leq 0.5$.
 
-{\bf The existence of models with high occupation fractions $f_{\rm
+The existence of models with high occupation fractions $f_{\rm
     occ}>0.2$ is unexpected from previous clustering analysis that do
@@
   hinders the possibility of constraining the LAEs occupation
-  fraction.}
+  fraction.
 
-{\bf Concerning the narrow mass range $\Delta M
+Concerning the narrow mass range $\Delta M
   <1.0$ the question arises of how can we give a physical
@@
   masses $M_{\rm  max}$ requires a different justification. There are
-  two complementary physical scenarios that could provide it.}
+  two complementary physical scenarios that could provide it.
 
@@
 not completely unexpected given that we have also required consistency
-with ACF measurements. These expectations are {\bf mostly} matched by
+with ACF measurements. These expectations are mostly matched by
 the first family of models, also summarized in Table
@@
   family of models. Wide mass range $\Delta M> 1.0$ dex and low
-  occupation fraction $f_{\rm occ}\leq 0.2$. {\bf These models are barely
+  occupation fraction $f_{\rm occ}\leq 0.2$. These models are barely
   consistent with the constraints from the Angular Correlation
-  Function and have been excluded from the main discussion.}} 
+  Function and have been excluded from the main discussion.}
 \end{table}
@@
 galaxies are not a dominant population, making our initial
-approximation a reasonable one. {\bf The lack of close pairs in
-  observations is another hint that the observed LAE population matches}
+approximation a reasonable one. The lack of close pairs in
+  observations \citep{Bond2009}is another hint that the observed LAE
+  population agrees with our approximation.
 Therefore we conclude that including the effect of satellite galaxies
@@
 
-{\bf The third caveat is the exact value that was used to turn
+The third caveat is the exact value that was used to turn
   filter values into cosmological volumes. Strictly speaking the
@@
 favored model parameters $M_{\rm  min}$ and $M_{\rm max}$ by about the
-same factor of $\sim2$ or $0.3$ dex. }
+same factor of $\sim2$ or $0.3$ dex.
 
-{\bf A fourth caveat is the comparing results for the number density
+A fourth caveat is the comparison of results for the number density
   statistics and the ACF from surveys with different EW cuts. In this
@@
   \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
-  confidence that the two different samples can give a self-consistent picture.}
+  confidence that the two different samples can give a self-consistent
+  picture.
 
@@
 
-{\bf We find that the number density can constrain the minimum mass to the range
-  $10^{10}\hMsun < M_{\rm min} < 10^{11.5}\hMsun$ while the clustering
-  constrains the upper mass $M_{\rm    max} < 10^{12}\hMsun$. However,
-  this information is insufficient to impose a tight constraint on the
-  occupation fraction. Additionally, we find that the mass range defined as
-$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ is $\Delta
-M\leq 1.0$, with a large fraction of models with $\Delta M\leq 0.5$.}
-
-{\bf This approach the discovery of consistent models that have
+In these models the occupation fraction remains unconstrained, while 
+many modelshave a narrow mass range models with $\Delta M\leq 0.5$. 
+This approach the discovery of consistent models that have
 been overlooked so far in the literature. A central role in these new
 models is played by the wide range of occupation fraction values,
-something unexpected from previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that unanimously favor low values on the range of $10^{-2}$. The largest
-innovation in our analysis is the construction of mock observations
-that directly explore the impact of cosmic variance.}
+something unexpected from previous studies
+\citep[i.e.][]{Gawiser2007,Ouchi2010}  that unanimously favor low
+values on the range of $10^{-2}$. The biggest innovation in our
+analysis is the construction of mock observations that directly
+explore the impact of cosmic variance.
 
 Nevertheless, all the halo mass ranges deduced in previous analysis are a
-subset of the models we find in this paper.  All of our
-preferred models support the notion that the most massive halos at
-$z=3.1$ do not host detectable LAEs.
+subset of the models we find in this paper.  All of our preferred
+models support the notion that the most massive halos at $z=3.1$ do
+not host detectable LAEs.
 
-In summary, we show that {\bf the currently available spatial
+In summary, we show that the currently available spatial
   information of LAEs can put a tight constraint on the halo mass
-  range but not on the occupation fraction}. This information can
+  range but not on the occupation fraction. This information can
 confidently be used to establish that these galaxies are hosted in low
-mass halos with masses spanning less than one order of magnitude. {\bf
+mass halos with masses spanning less than one order of magnitude. 
   From the point of view of Dark Energy surveys such as the Hobby-Eberly
@@
   simplicity in their modeling aiming at recovering cosmological
-  parameters.} We foresee that the observations with new instruments
+  parameters We foresee that the observations with new instruments
 (such as the Multi Unit Spectroscopic Explorer (MUSE), Hyper
@@
 Alvaro Orsi and Mark Dijkstra for helpful comments on the physical
-interpretation and presentation of our results. We would
-also like to thank the referee for their helpful comments.
+interpretation and presentation of our results.
 
@@
 
-\bibliographystyle{mn2e}
+\bibliographystyle{apj}
 \bibliography{references}

### 2014-03-28 paper/ms.tex
shorter
new abstract

@@
 %
-We derive constraints on the mass and occupation fraction of dark
-matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
-$z=3.1$ by matching the number density distribution and the angular
-correlation function between mock and observed fields. We explicitly
-take into account the cosmic variance on the typical observed field
-size by constructing mock fields from a large cosmological N-body
-simulation. To populate the
-halos in the simulation we use a model where a dark matter halo with
-mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm max}$ can only host
-one detectable LAE with a probability $0.1 \leq f_{\rm occ}\leq
-1.0$. We use this approach to avoid the uncertainties associated
-  to the estimation of \ly luminosities in each halo. Our analysis
-shows that the clustering and number density information are
-insufficient to impose a tight constraint on the occupation
-fraction. On the other hand, the minimum mass and maximum mass can be
-constrained to the range $M_{\rm  max}<10^{12}$\hMsun\ and
-$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$. We also find
-that the consistent models have a narrow mass range, $\Delta M \equiv
-\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$, smaller than $1.0$ dex,
-with a majority in the range $\Delta M<0.5$ dex. These results
-  broadly reproduce some constraints   already presented in the
+  We study the impact of cosmic variance in constrainng the mass and
+  occupation fraction of dark matter halos hosting \ly Emitting
+  Galaxies at high redshift. We use and N-body simulation to construct
+  mock fields with the same typical size of observed fields at
+  $z=3.1$. As a benchmark we match the observed number density
+  distribution across fields and the angular correlation function. To
+  populate the halos in the simulation we use a model where a dark
+  matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm
+    max}$ can only host one detectable LAE with a probability $0.1
+  \leq f_{\rm occ}\leq 1.0$.  Our analysis shows that the clustering
+  and number density information are insufficient to impose a tight
+  constraint on the occupation fraction. On the other hand, the
+  minimum mass and maximum mass can be constrained to the range
+  $M_{\rm  max}<10^{12}$\hMsun\ and $10^{10.2}\hMsun\leq M_{\rm
+    min}\leq 10^{11.5}\hMsun$. We also find that the consistent models
+  have a narrow mass range, $\Delta M \equiv \log_{10}M_{\rm max} -
+  \log_{10} M_{\rm min}$, smaller than $1.0$ dex, with a majority in the range $\Delta M<0.5$ dex. These results
+  fall into constraints   already presented in the
   literature. However, the wide range of values for the occupation
@@
   for the connection between dark matter, star formation and the escape
-of \ly radiation. That kind of modeling should also be able to provide
-a plausible explanation for the narrow mass range derived here for the
-halos hosting LAEs at $z=3.1$. 
+  of \ly radiation. 
 \end{abstract}
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.46\linewidth,angle=0]{Fig7_corr_params.pdf}  
+\includegraphics[width=0.46\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
+\end{center}
+\caption{Left panel. Values for the free parameters $\theta_{0}$ and $\beta$
+in the fitting formula (Eq. \ref{eq:fitting}) for the angular
+correlation function. Blue dots correspond to simulations and the
+green line to observations by \citet{Ouchi2008,Ouchi2010}. The error
+bars in the theoretical data correspond to the quadratic average of
+the fitting uncertainties for each mock survey. Right panel. Values of
+$\theta_{0}$  and $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})$. Blue and
+green point represents the models where  $\log_{10}(M_{\rm max}/M_{\odot}
+h^{-1})<12.0$ and  $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})>12.0$
+respectively. .  The horizontal gray band represents the observational
+constraints on $theta_{0}$ established by
+\citet{Ouchi2008,Ouchi2010}. Green points has been displaced by
+$0.01$ dex of its original value to avoid overlapping between blue and
+green points.} \label{fig:correlation_parameters}   
+\end{figure*}
+
 The main purpose of this section is to show how the different
@@
 models consistent with the number density distribution.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig7_corr_params.pdf}  
-\includegraphics[width=0.46\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
-\end{center}
-\caption{Left panel. Values for the free parameters $\theta_{0}$ and $\beta$
-in the fitting formula (Eq. \ref{eq:fitting}) for the angular
-correlation function. Blue dots correspond to simulations and the
-green line to observations by \citet{Ouchi2008,Ouchi2010}. The error
-bars in the theoretical data correspond to the quadratic average of
-the fitting uncertainties for each mock survey. Right panel. Values of
-$\theta_{0}$  and $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})$. Blue and
-green point represents the models where  $\log_{10}(M_{\rm max}/M_{\odot}
-h^{-1})<12.0$ and  $\log_{10}(M_{\rm min}/M_{\odot} h^{-1})>12.0$
-respectively. .  The horizontal gray band represents the observational
-constraints on $theta_{0}$ established by
-\citet{Ouchi2008,Ouchi2010}. Green points has been displaced by
-$0.01$ dex of its original value to avoid overlapping between blue and
-green points.} \label{fig:correlation_parameters}   
-\end{figure*}
 

### 2014-03-28 paper/ms.tex
conclusions and caveats

@@
 \begin{enumerate}
-\item The first is the SSA22
-field of $1.38$ deg$^2$ with $1394$ detected LAEs (7 sub-fields), this
-field has been known to harbor a region with a large density excess of
-galaxies.
+\item The SSA22
+field of $1.38$ deg$^2$ with $1394$ detected LAEs. This large field is
+composed by 7 sub-fields.
 
-\item The second observed region is composed by the fields Subaru/{\it
-  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South, with a
+\item The Subaru/{\it
+  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South fields , with a
 total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).
 
-\item The third  field is the Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
+\item The Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
 $196$ LAEs (1 sub-field), and
 
-\item The fourth one is the field around the Great Observatory
-Optical Deep Survey  (GOODS-N) with $0.24$ deg$^2$ and $185$ LAEs (1
-sub-field).  
+\item The Great Observatory Optical Deep Survey  (GOODS-N) field with
+  $0.24$ deg$^2$ and $185$ LAEs (1 sub-field).   
 \end{enumerate}
@@
 We assume that a dark matter halo can only host one
-detectable LAE at most.  There are three parameters that
-decide whether a halo host a LAE: the lower and upper bounds for the
-mass range ($M_{\rm min}< M_{\rm h} < M_{\rm max}$) where LAEs reside
+detectable LAE at most.  This is consistent with theoretical analysis
+of the correlation function \citep{Jose2013b} and obsevations that
+confirm a lack of class pairs in LAEs \cite{Bond2009}.
+
+There are three parameters that decide whether a halo host a LAE: the
+lower and upper bounds for the mass range ($M_{\rm min}< M_{\rm h} < M_{\rm max}$) 
 and the fraction ($f_{\rm occ}$) of such halos that host a detectable
-LAE. The reader must keep in mind that the physical interpretation of
-the occupation fraction $f_{\rm occ}$ convolves two phenomena: the
-actual presence of a star forming galaxy in a halo and its
-detectability as a LAE.
+LAE. A physical interpretation of the occupation fraction $f_{\rm
+  occ}$ convolves two phenomena: the actual presence of a star forming
+galaxy in a halo and its detectability as a LAE.
 
-We recall that we do not perform a explicit modeling for LAE
-detectability. Our model does not assign a luminosity or escape
-fraction for each LAE. We are interested in constraining the halo
-mass range hosting detectable LAEs commonly used in photometric
-narrow-band surveys. We want to explore a wide range of
-possible masses for the host halos without any strong theoretical
-prejudice regarding the details of star formation in high-redshift
+Our model does not assign a luminosity or escape fraction for each
+LAE in order to maintain theoretical uncertainties to a minimum. With
+this flexibility we can explore a wide range of possible masses for
+the host halos without any strong theoretical prejudice regarding the
+details of star formation and \ly escape fraction in high-redshift
 galaxies.
@@
 
-There are four caveats for the work presented here that are important
-to keep in mind. The first is the  
-assumption of a single LAE per dark matter halo. This contradicts the
-general expectation of dark matter sub-halos in the simulation to host
-satellite galaxies. However, it has been found in analysis based on
-the shape of the correlation function \citep{Jose2013b} that satellite
-galaxies are not a dominant population, making our initial
-approximation a reasonable one. The lack of close pairs in
-  observations \citep{Bond2009}is another hint that the observed LAE
-  population agrees with our approximation.
-Therefore we conclude that including the effect of satellite galaxies
-should not significantly change the main results reported in this
-\documentname.
+There are three minor caveats for the work presented here that are important
+to keep in mind.
 
-The second caveat is the precise values for the mass intervals. These
+The first caveat is the precise values for the mass intervals. These
 values are quoted from halos defined using a FOF halo
@@
 
-The third caveat is the exact value that was used to turn
+The second caveat is the exact value that was used to turn
   filter values into cosmological volumes. Strictly speaking the
@@
 
-A fourth caveat is the comparison of results for the number density
+A third caveat is the comparison of results for the number density
   statistics and the ACF from surveys with different EW cuts. In this
@@
 
-In this \documentname we look for constraints on the preferred mass
-and occupation fraction of dark matter halos hosting Lyman $\alpha$
-Emitters at redshift $z=3.1$ in a $\Lambda$CDM cosmology. We perform
-this study paying special attention to the impact of cosmic variance
-on these results. To this end we build a large number of mock catalogs
+In this \documentname we quantify the impact of cosmic variance in
+constraining the  mass and occupation fraction of dark matter halos
+hosting Lyman $\alpha$ Emitters at redshift $z=3.1$ in a $\Lambda$CDM
+cosmology.  To this end we build a large number of mock catalogs
 matching observational geometries. The mocks are constructed from a
-N-body simulation following a simple recipe to assign a single LAE to
-each halo whereby only a fraction $f_{\rm occ}$ of halos within a mass
-range  $M_{\rm min}\leq M_{\rm h}\leq M_{\rm   max}$ can host a
-LAE. The main motivation to implement this kind of model is to avoid
-all the uncertainties in the estimation of \ly luminosities.
+N-body simulation by assigning a single LAE to a DM halo.
 
 We then proceed with a thorough exploration of the space of free
-parameters $M_{\rm min}, M_{\rm max}$ and $f_{\rm occ}$ to find mocks
-that are consistent with two observational constraints: the surface
-number density distribution and the angular correlation function. Out
-of the initial $9000$  combinations of parameters in the model we find
-$40$ combination of parameters consistent with observations.
+parameters $M_{\rm min}, M_{\rm max}$ and $f_{\rm occ}$ describing the
+model. We look for consistency with two observational constraints: the
+surface number density distribution and the angular correlation
+function. Out of the initial $9000$  combinations of parameters in the
+model we find $40$ combination of parameters consistent with
+observations.
 
-In these models the occupation fraction remains unconstrained, while 
-many modelshave a narrow mass range models with $\Delta M\leq 0.5$. 
-This approach the discovery of consistent models that have
-been overlooked so far in the literature. A central role in these new
-models is played by the wide range of occupation fraction values,
-something unexpected from previous studies
-\citep[i.e.][]{Gawiser2007,Ouchi2010}  that unanimously favor low
-values on the range of $10^{-2}$. The biggest innovation in our
-analysis is the construction of mock observations that directly
-explore the impact of cosmic variance.
+We find two interesting features in these models. First, the
+occupation fraction remains unconstrained; second, many models have a
+narrow mass range models with $\Delta M \leq 0.5$.
 
-Nevertheless, all the halo mass ranges deduced in previous analysis are a
-subset of the models we find in this paper.  All of our preferred
-models support the notion that the most massive halos at $z=3.1$ do
-not host detectable LAEs.
+The wide range of occupation fraction values is unexpected from
+previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that
+unanimously favor low values on the range of $10^{-2}$. Nevertheless,
+all the halo mass ranges deduced in previous analysis are a subset of
+the models we find in this paper, all of the best models support the
+notion that the most massive halos at $z=3.1$ do not host detectable
+LAEs.
 
-In summary, we show that the currently available spatial
-  information of LAEs can put a tight constraint on the halo mass
-  range but not on the occupation fraction. This information can
-confidently be used to establish that these galaxies are hosted in low
-mass halos with masses spanning less than one order of magnitude. 
   From the point of view of Dark Energy surveys such as the Hobby-Eberly
@@
 tighter constraints on the properties of dark matter halos hosting
-LAEs. At the same time, additional modeling for \ly radiation transfer
-is needed to put tighter constraints on  occupation fraction in high
-redshift halos, also paying attention to other physical phenomena,
-such as the stochasticity \citep{ForeroRomero2013} in the star
-formation process, which might play a role in inducing detection
-biases in high redshift LAEs.
+LAEs.
+
+Finally, additional modeling for \ly radiation transfer is needed to
+put tighter constraints on  occupation fraction in high redshift
+halos, also paying attention to other physical phenomena, such as the
+stochasticity \citep{ForeroRomero2013} in the star formation process,
+which might play a role in introducting detection biases in high redshift
+LAEs.
 
 \section*{Acknowledgments}
+
+J.E.F-R was supported by the FAPA grant by Vicerrector\'ia de
+Investigaciones at Universidad de los Andes.
+
 J.E.F-R thanks the hospitality of Changbom Park and the Korea
@@
 
-J.E.F-R was
-supported by the FAPA grant by Vicerrector\'ia de Investigaciones at
-Universidad de los Andes. The MultiDark Database used in this paper and the web application providing online access to it were constructed as part of the
+The MultiDark Database used in this paper and the web application providing online access to it were constructed as part of the
 activities of the German Astrophysical Virtual Observatory as result

### 2014-04-01 paper/ms.tex
introduction

@@
 %
-  We study the impact of cosmic variance in constrainng the mass and
+  We study the impact of cosmic variance in constraining the mass and
   occupation fraction of dark matter halos hosting \ly Emitting
-  Galaxies at high redshift. We use and N-body simulation to construct
+  Galaxies at high redshift. We use an N-body simulation to construct
   mock fields with the same typical size of observed fields at
-  $z=3.1$. As a benchmark we match the observed number density
-  distribution across fields and the angular correlation function. To
-  populate the halos in the simulation we use a model where a dark
+  $z=3.1$ to match the observed number density distribution across
+  fields and the angular correlation function. In our model a dark
   matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm
@@
   $M_{\rm  max}<10^{12}$\hMsun\ and $10^{10.2}\hMsun\leq M_{\rm
-    min}\leq 10^{11.5}\hMsun$. We also find that the consistent models
-  have a narrow mass range, $\Delta M \equiv \log_{10}M_{\rm max} -
-  \log_{10} M_{\rm min}$, smaller than $1.0$ dex, with a majority in the range $\Delta M<0.5$ dex. These results
-  fall into constraints   already presented in the
-  literature. However, the wide range of values for the occupation
-  fraction and the narrow mass range $\Delta M$ are novel results from
-  the approach presented here. We conclude that achieving a constraint on the
-  occupation fraction for LAEs at $z=3.1$ will require observations on
-  larger fields to reduced cosmic variance and robust physical models
-  for the connection between dark matter, star formation and the escape
-  of \ly radiation. 
+    min}\leq 10^{11.5}\hMsun$. Additionally, we find that the
+  consistent models have a narrow mass range, $\Delta M \equiv \log_{10}M_{\rm max} -
+  \log_{10} M_{\rm min}$, smaller than $1.0$ dex, with a majority in
+  the range $\Delta M<0.5$ dex. These results fall into constraints
+  already presented in the literature. However, the wide range of
+  values for the occupation fraction and the narrow mass range $\Delta
+  M$ are novel results allowed by takinf into account the influence of
+  cosmic variance on the statistics derived from observations.  
 \end{abstract}
@@
 distributions. Such modelling has been implemented in semi-analytic
-models \citep{Garel2012,Orsi2012,Soler2012} and  full N-body
+models \citep{Garel2012,Orsi2012} and  full N-body
 hydrodynamical simulations \citep{Laursen2007, Dayal2009,
@@
 
-These calculations involve many uncertain steps, such as the treatment
-of astrophysical processes describing star formation. However, in the
-context of LAEs, the dominant uncertainty is the estimation of the
-escape fraction, that is the fraction of \ly photons that escape the
-galaxy to the observer. Given the resonant nature of the \ly line, the escape
-fraction is sensitive to  the dust contents, density, temperature, topology and
-kinematics of the neutral Hydrogen in the interstellar medium
-(ISM). Solving the radiative transfer of \ly photons in the ISM requires Monte
-Carlo simulations. The process of finding a consensus on the expected
-value for the \ly escape fraction in high redshift galaxies is still
-matter of ongoing research
+However, these calculations involve many uncertain steps such as 
+the estimation of the escape fraction, that is the fraction of \ly
+photons that escape the galaxy to the observer. Given the resonant
+nature of the \ly line, the escape fraction is sensitive to  the dust
+contents, density, temperature, topology and kinematics of the neutral
+Hydrogen in the interstellar medium (ISM). Solving the radiative
+transfer of \ly photons in the ISM requires Monte Carlo
+simulations. The process of finding a consensus on the expected value
+for the \ly escape fraction in high redshift galaxies is still matter
+of ongoing research
 \citep{Neufeld1991,Verhamme2006,ForeroRomero2011,Dijkstra2012,Laursen2013,Orsi2012}.
@@
 set is constructed from 12 different sub-fields that allows us to use
-clustering statistics and cosmic variance to constrain the mass and
-occupation fraction of halos hosting LAEs.
+clustering statistics and the cosmic variance among fields to
+constrain the mass and occupation fraction of halos hosting LAEs.
 
-The method we use here firstly populates DM halos in cosmological
-simulations with LAEs. We only consider whether a DM can host a
-detectable LAE or not without predicting a \ly  luminosity. This
-bypasses all the physical uncertainties involved in the estimation of
-observed \ly luminosities. Once we have the halos hosting a LAE, we
-build mock surveys following the geometry of the observed fields by
-\cite{Yamada2012}. This allows us to take explicitly into account the
-effect of cosmic variance. We used this mock surveys to compared them
-against observations in terms of the number density distribution and
-the angular correlation function. This allows us to constraint the
-preferred mass range and occupation fraction of DM halos hosting LAEs.
+In this paper we investigate the impact of cosmic variance in
+constraining the mass and occupation fraction of halos hosting LAEs.
+We do this by constructing mock catalogs from cosmological simulations.
+Our method populates each halo in the simulation with a LAE without
+predicting a \ly  luminosity. This bypasses all the physical
+uncertainties associated to star formation and radiative transfer.
+We build mock surveys following the geometry of the observed fields by
+\cite{Yamada2012} to compared them  against observations in terms of
+the number density distribution and the angular correlation
+function. This allows us to find a range of parameters of our model
+that are consistent with observations while taking into account
+cosmic variance.
 
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
+\includegraphics[width=0.45\linewidth,angle=0]{Fig6_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
+\includegraphics[width=0.45\linewidth,angle=0]{Fig6_f_occ.pdf}
 \end{center}

### 2014-04-03 paper/ms.tex
observational constraints

@@
 Our method is based on the comparison of observations and mock
-catalogs. We use two different kinds of statistics to perform the
-comparison: (i) the distribution of the surface number density
-across fields and (ii) the angular correlation function.
+catalogs that take into account cosmic variance. Our benchmarks are the
+distribution of the surface number density across fields and the
+angular correlation function.
 
 In the next subsections we describe in detail the four key
-elements int our work-flow. First we present (in two sub-sections) the
+elements int our work-flow. First, we present the 
 observations we take as a benchmark. Second, we describe the main
 characteristics of the N-body simulation and the halo catalogs we
-use. Third, we recount the important parameters of the simplified
+use. Third, we list the important parameters of the simplified
 model that we use to populate the halo catalogs with LAEs. Finally, we
-describe some of the statistical tests we adopt to compare
-observations and mocks .
+describe the statistical tests we adopt to compare observations and mocks.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
-\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
-\caption{ \label{fig:halos} Left panel. Cumulative distribution of LAE number
+\includegraphics[width=0.95\linewidth,angle=0]{Fig1b.pdf}
+\caption{ \label{fig:number_density} Cumulative distribution of LAE number
   densities in all the fields observed by \citet{Yamada2012}. The
   point with the highest surface density corresponds to the densest
-  sub-field in the SSA22 field. Right panel. Surface density of dark 
-  matter halos as a function of a minimum halo mass. Each line
-  represents one of the $210$ volumes of dimensions $46\times 35\times
-  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
-  gray band represents the range of surface densities observed for
-  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
-  line the observational results by \citet{Ouchi2008}.}
+  sub-field in the SSA22 field.}
 \end{center} 
-\end{figure*}
+\end{figure}
 
-The primary observational constraint we use in this paper is the LAE number
-density information at $z=3.1$ obtained by the panoramic narrow-band
-survey presented by \cite{Yamada2012} from a survey
-conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
-which has a field of view covering $34\times 27$ arc-min, corresponding to a
-comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
-band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
-corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
-centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
-an observed equivalent width, in the observer frame, larger than $190$
-\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
-sub-fields,  this corresponds to an average surface number density of
-$0.24\pm 0.01$ arcmin$^{-2}$.
+The first observational constraint we use in this paper is the LAE number
+density information at $z=3.1$ obtained by \cite{Yamada2012} from a survey
+conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera.
+The camera has a field of view covering $34\times 27$ arc-min,
+corresponding approximately to a comoving scale of $46\times35$ Mpc
+$h^{-1}$ at $z=3.09$.
+
+The narrow band filter used in the survey is
+centered at $4977$ \AA~with  $77$ \AA~width, corresponding to the
+redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the
+detection of the Lyman-$\alpha$ line centered at $z=3.09$. The authors
+reported a total  $2161$  LAEs with an observed equivalent width, in
+the observer frame, larger than $190$ \AA~over a total survey area of
+$2.42$ deg$^{2}$ that includes 12 sub-fields,  this corresponds to an
+average surface number density of $0.24\pm 0.01$ arcmin$^{-2}$.  The
+distribution of the surface number densities is shown in Figure
+\ref{fig:number_density}.
 
@@
 \item The Subaru/{\it
-  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South fields , with a
+  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South fields, with a
 total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).
@@
 \item The Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
-$196$ LAEs (1 sub-field), and
+$196$ LAEs (1 sub-field).
 
@@
 
+The surface number density distribution for these fields is shown in
+Figure \ref{fig:number_density}.
+
 There is abundant observational work done on LAEs at redshift $z=3.1$
 \citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
-However, we decide to focus on the data from \cite{Yamada2012} because
+However, we use the data from \cite{Yamada2012} because
 it has the largest covered area with homogeneous instrumentation
@@
 and conditions to construct the LAE catalog. This ensures that the
-number density variations among fields are \emph{not} due to different
+number density variations among fields are not due to different
 observational conditions or criteria to construct the catalogs.
 
-A secondary benchmark is the angular correlation function
-(ACF). \cite{Yamada2012} does not report an ACF measurement for
-  their fields. Instead we use the results by   \cite{Ouchi2008} who
+The second benchmark is the angular correlation function
+(ACF). Unfortunately, \cite{Yamada2012} do  not report an ACF measurement for
+their fields. Instead, we use the results by   \cite{Ouchi2008} who
 reported the ACF is over a region of $1$ deg$^2$ over the SXDS
@@
 differences \cite{Ouchi2008} provides the most similar conditions
-  to \cite{Yamada2012}.
+to the observations presented by \cite{Yamada2012}.
 
-\subsubsection{The adequacy of including SSA22 as an observational benchmark}
-
-The field SSA22 has been known to harbor a significant
+We note that the field SSA22-1 has been known to harbor a significant
 galaxy overdensity. \cite{Yamada2012} estimates that the densest
 sub-field is likely to be a rare density peak with $3-4\sigma$
-  significance on the scale of $\sim 60$\hMpc.
+significance on the scale of $\sim 60$\hMpc.  All the other sub-fields
+in SSA22 are average with similar number density as other blank fields.
 
-All the other sub-fields in SSA22 are average. They have a similar
-  number density as other blank fields. The left panel in Figure
-  \ref{fig:halos} shows the integrated distribution of LAEs number
-  density in all the fields reported in  \cite{Yamada2012}. It is
-  evident that there is only one sub-field  that stands out as an
-  outlier in the distribution, corresponding to  the densest field in
-  SSA22. All the other fields form a continuous  distribution in
-  number density.
-
-Therefore, using the whole SSA22 region as a benchmark in the
-  number density distribution does not impose any bias. However, on
-  has to  keep in mind that is not plausible that the full number
-  density distribution from a simulation will include a very dense
-  field. For this reason we do not require the presence of a very
-  dense field such as SSA22-1 to judge a mock distribution as
-  successful. The statistical test we use o compare mock
-  distributions against observations does not require such a perfect
-  match.
+From Figure \ref{fig:number_density}  it is evident that there is only
+one sub-field  that stands out as an outlier in the distribution,
+corresponding to SSA22-1. All the other fields form a continous
+distribution in number density. Therefore, using the whole SSA22
+region as a benchmark in the number density distribution does not
+impose any bias. The statistical test we use o compare mock
+distributions against observations does not require a perfect match
+with observations, i.e. the presence of a mock fields as dense as
+SSA22-1 (which is very unlikely) is not required to consider that we
+have a good match with observations.
 
@@
 \label{sec:results}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\linewidth,angle=0]{Fig1.pdf}
+\caption{ \label{fig:halos} Surface density of dark 
+  matter halos as a function of a minimum halo mass. Each line
+  represents one of the $210$ volumes of dimensions $46\times 35\times
+  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
+  gray band represents the range of surface densities observed for
+  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
+  line the observational results by \citet{Ouchi2008}.}
+\end{center} 
+\end{figure}
 

### 2014-04-03 paper/ms.tex
new reference + simulation section

@@
 
-The Bolshoi simulation \citep{Bolshoi} we use in this paper was
-performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. The
-dark matter distribution is sampled using $2048^{3}$ particles, which
+We use results form the Bolshoi simulation \citep{Bolshoi} which
+was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. The
+dark matter distribution is sampled using $2048^{3}$ particles. The
+cosmological parameters are consistent with a Wilkinson Microwave
+Anisotropy Probe (WMAP) ninth year data with a matter density
+$\Omega_{\rm m} = 0.27$, cosmological constant
+$\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope
+of the power spectrum $n=0.95$ and normalization of the power
+spectrum$\sigma_{8}=0.82$ \citep{hinshaw_etal13}.   This
 translates into a particle mass of $m_{\rm p}=1.35\times 10^{8}$
-$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
-a WMAP5 and WMAP7 data with a matter density $\Omega_{\rm m} = 0.27$,
-cosmological constant $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
-$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
-power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.
+$h^{-1}$ M$_{\odot}$.
 
@@
 Multidark database \footnote{{\tt
-    http://www.multidark.org/MultiDark/}}
-\citep{MultiDark}. For each halo in the box we store its
-comoving position in the box (3-D coordinates) and FOF mass. We focus our work
-on halos more massive than $1\times 10^{10}$\hMsun that are resolved
-with at least $70$ particles, the reasons for this choice are
-explained in the next sub-section.
+    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
+halo in the box we store its comoving position in the box (3-D
+coordinates) and FOF mass. We focus our work on halos more massive
+than $1\times 10^{10}$\hMsun resolved with at least $70$ particles.
+%the reasons for this choice are explained in the next sub-section.
 

### 2014-04-03 paper/ms.tex
removed tables

@@
 
-We assume that a dark matter halo can only host one
-detectable LAE at most.  This is consistent with theoretical analysis
-of the correlation function \citep{Jose2013b} and obsevations that
-confirm a lack of class pairs in LAEs \cite{Bond2009}.
+We assume that a dark matter halo can only host one detectable LAE at
+most.  This is consistent with theoretical analysis of the correlation
+function \citep{Jose2013b} and obsevations that confirm a lack of
+class pairs in LAEs \cite{Bond2009}.
 
-There are three parameters that decide whether a halo host a LAE: the
+There are three parameters that decide whether a halo host a LAE. The
 lower and upper bounds for the mass range ($M_{\rm min}< M_{\rm h} < M_{\rm max}$) 
@@
 
-Our model does not assign a luminosity or escape fraction for each
+Our model does not assign a luminosity or escape fraction to each
 LAE in order to maintain theoretical uncertainties to a minimum. With
@@
 In what follows we note by the letter ${\mathcal M}$ a model
-defined by a particular choice of the three scalar parameters $M_{\rm
+defined by a particular choice of the three parameters $M_{\rm
   min}$, $M_{\rm  max}$ and $f_{\rm occ}$. For each model ${\mathcal
@@
 in the redshift direction. This corresponds to a total area of $880$
-arcmin$^{2}$ in each mock field. We construct a total $5\times 7
-\times 6=210$ of such volumes from a snapshot in the Bolshoi
+arcmin$^{2}$ in each mock field.
+
+Strictly speaking the volume probed is a function of the \ly
+luminosity. Under the considerations presented in \citep{Gronwall07}
+we expect the survey depth and the true number density to change at
+most by a factor of $\sim2$, increasing the scatter on the
+number density by a similar same factor. This implies that the models we
+find in this paper can be considered as a minimal set of all models
+that could be found if one takes this minor effect into account.
+
+We construct a total $5\times 7 \times 6=210$ sub-volumes from a snapshot in the Bolshoi
 simulation. In each mock field a LAE is assigned to the position of a
 dark matter halo if the halo mass is in the range allowed by the model
-$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from
-an homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
+$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from n
+homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
 fraction $\xi<f_{\rm occ}$.
 
-Next we construct mock surveys by making groups of $12$ mock fields
-out of the $210$ available volumes. In total $15$ mock surveys are
-constructed for each model $\mathcal{M}$. The grouping of the $12$
-mock fields into a mock catalog is done in two different ways. The
-first is called {\texttt{match}} because it follows the clustering of the
+We construct mock surveys by making groups of $12$ mock fields
+out of the $210$ available volumes.  The grouping of the $12$
+mock fields into a mock catalog is done following the clustering of the
 observational fields. From the $12$ mock fields, $7$ are constructed
@@
 to mimic the SXDS fields and finally $2$ non-contiguous fields to
-imitate the SDF and GOODS-North field.   The second way to group the
-mock fields is called {\texttt{random}}, whereby all the $12$ fields
-are selected in such a way as to avoid that any two volumes are
-contiguous. In this \documentname we only report the results obtained
-by the {\texttt{match}} method since we do not find any significant
-difference with respect to the {\texttt{random}} method.
+imitate the SDF and GOODS-North field.   In total $15$ mock surveys are
+constructed for each model $\mathcal{M}$ after taking into account the
+spatial restrictions due to the grouping we have just described.
 
-Figure \ref{fig:distros} shows the spatial distribution for one mock
-survey constructed using the {\texttt{match}} method. Each field
-corresponds to one of the observational fields. The model parameters
-to build the mock are $M_{\rm min}=10^{10.4}$\hMsun, $M_{\rm
-  max}=10^{10.5}$\hMsun and $f_{\rm occ}=0.1$. The figure shows only
-one out of the $15$ different mock surveys that are constructed for
-each model. We note that we only use $15\times 12=180$ mock fields out of the
-total of $210$ available sub-volumes. The reason is that the {\texttt{match}}
-method imposes constraints on the way the $7$ fields mimicking the
-SSA22 can be distributed. This restriction makes unable some of the
-sub-volumes in the box. We decide to keep the number of mock surveys
-fixed to $15$ also for the {\texttt{random}} method in order to allow a
-fair comparison between the two methods.
-
-\subsection{Exploring and selecting good models}
+\subsection{Exploring and selecting consistente models}
 
@@
 is $\sim 10$ times higher than the observational constraints
-for LAEs. This means that models in that mass range and an occupation fraction $f_{\rm  occ}=0.1$ have the possibility to be compatible with
-observations. Lower values for $M_{\rm min}$ require $f_{\rm
-  occ}<0.1$, which are not considered in this \documentname.  In
-  turn exploring occupation fractions on the order of $f_{\rm occ}=0.01$ 
-  only makes sense for halo populations in the mass range of
-  $10^{9}$\hMsun which are abundant enough to fit observations with a
-  very low occupation fraction. In our case, this is a mass range unresolved
-  by the Bolshoi simulation and therefore cannot be considered in the
-  present study.
+for LAEs. This means that models in that mass range and an occupation
+fraction $f_{\rm  occ}=0.1$ have the possibility to be compatible with
+observations.  Similarly, wxploring occupation fractions on the order
+of $f_{\rm occ}=0.01$ only makes sense for halo populations in the
+mass range of $10^{9}$\hMsun which are abundant enough to reproduce
+the observational constraint on the number density. In our case, this
+is a mass range unresolved by the Bolshoi simulation and therefore
+is not considered in the present study.
 
-For each mock survey generated in a given model ${\mathcal M}$ we
+For each mock survey generated with a given model ${\mathcal M}$ we
 compute the surface density in its $12$ mock fields. We perform a
 Kolmogorov-Smirnov (KS) to compare these values against the $12$
-observational values. This tests gives us a value $0<P<1$ to
+observational values. The test gives a value $0<P<1$ to
 reject the null hypothesis, namely that two data sets come from the
@@
 the two distributions can be thought as coming from the same
-distribution.
+distribution. We require that a model ${\mathcal M}$ must have all the 15 mock
+surveys with $P>0.05$ to be considered consistent with observations.
 
-We begin by considering that  a model ${\mathcal M}$ with at least one
-mock survey (out of 15) consistent with observations has viable
-parameters to host LAEs. From that we consider a stronger constraints
-to reduce the number of models by asking that all the 15 mocks  to be
-consistent with observations and analyze again the properties of the
-resulting models. Finally we add the ACF as an additional constraint
-and consider all the models having their $15$ mocks consistent with
-observations.
-
-The ACF is computed using  the Landy \&  Szalay estimator
+We add the Angular Correlation Function (ACF) as an additional
+constraint. The ACF is computed using  the Landy \&  Szalay estimator
   \citep{Landy1993}  on fields of size $1$ deg$^2$ to be compared
@@
 \end{equation}
+%
 where $\theta_0$ and $\beta$ are free parameters. The fit is done
@@
 obtain a covariance matrix that gives us the uncertainty in the
-parameters $\beta$ and $\theta_0$.  We consider that a mock field is
-consistent with observations if the two parameters $\beta$ and
-$\theta_0$ are equal within a $1$-$\sigma$ range. We perform this
-comparison only with the fields constructed using the {\texttt{match}}
-method.
+parameters $\beta$ and $\theta_0$.  For a model we derive a mean
+value and a dispersion computed from the fit of all mock fields. We
+consider that a mocdel is consistent with observations if the two
+parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
+range.
 
@@
 
-A complete parameter list for the three families is presented in Tables
-\ref{table:firstfamily}, \ref{table:secondfamily}  and 
-\ref{table:thirdfamily}.
-
 The models in the third family are barely consistent with the
@@
 
-\begin{table}
-\begin{center}
-\begin{tabular}{cccc}\hline\hline
-$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
- 10.4 &10.7 & 0.1& 0.3 \\
- 10.5 &10.9 & 0.1& 0.4 \\
- 10.5 &11.0 & 0.1& 0.5 \\
- 10.6 &10.8 & 0.2& 0.2 \\
- 10.6 &11.2 & 0.1& 0.6 \\
- 10.6 &11.3 & 0.1& 0.7 \\
- 10.6 &11.4 & 0.1& 0.8 \\
- 10.6 &11.5 & 0.1& 0.9 \\
- 10.6 &11.6 & 0.1& 1 \\
- 10.7 &11.0 & 0.2& 0.3 \\
- 10.8 &11.2 & 0.2& 0.4 \\
- 10.8 &11.3 & 0.2& 0.5 \\
- 10.8 &11.4 & 0.2& 0.6 \\
- 10.9 &11.9 & 0.2& 1.0 \\
- 10.9 &11.7 & 0.2& 0.8 \\
- 10.9 &11.8 & 0.2& 0.9 \\\hline
-\end{tabular}
-\end{center}
-\caption{\label{table:firstfamily}
-List of parameters for the first
-  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
-  occupation fraction $f_{\rm occ}\leq 0.3$.} 
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{cccc}\hline\hline
-$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
- 10.5 &10.6 & 0.3 & 0.1 \\
- 10.6 &10.7 & 0.4 & 0.1 \\
- 10.7 &10.8 & 0.5 & 0.1 \\
- 10.8 &10.9 & 0.6 & 0.1 \\
- 10.8 &11.0 & 0.4 & 0.2 \\
- 10.9 &11.0 & 0.8 & 0.1 \\
- 10.9 &11.0 & 0.9 & 0.1 \\
- 10.9 &11.1 & 0.5 & 0.2 \\
- 10.9 &11.3 & 0.3 & 0.4 \\
- 11.0 &11.1 & 1.0 & 0.1 \\
- 11.0 &11.2 & 0.6 & 0.2 \\
- 11.0 &11.4 & 0.4 & 0.4 \\
- 11.1 &11.3 & 0.7 & 0.2 \\
- 11.1 &11.3 & 0.8 & 0.2 \\
- 11.1 &11.4 & 0.6 & 0.3 \\
- 11.2 &11.4 & 0.9 & 0.2 \\
- 11.2 &11.4 & 1.0 & 0.2 \\\hline
-\end{tabular}
-\end{center}
-\caption{\label{table:secondfamily}List of parameters for the second
-  family of models. Narrow mass range $\Delta M\leq 1.0 $ dex and high occupation fraction $f_{\rm occ}>0.2$.}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{cccc}\hline\hline
-$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
- 10.6 &11.7 & 0.1& 1.1 \\
- 10.9 &12.0 & 0.2& 1.1 \\
- 10.9 &12.1 & 0.2& 1.2 \\
- 10.9 &12.2 & 0.2& 1.3 \\
- 10.9 &12.3 & 0.2& 1.4 \\
- 10.9 &12.6 & 0.2& 1.7 \\
- 10.9 &12.8 & 0.2& 1.9 \\\hline
-\end{tabular}
-\end{center}
-\caption{\label{table:thirdfamily}List of parameters for the third
-  family of models. Wide mass range $\Delta M> 1.0$ dex and low
-  occupation fraction $f_{\rm occ}\leq 0.2$. These models are barely
-  consistent with the constraints from the Angular Correlation
-  Function and have been excluded from the main discussion.}
-\end{table}
-
 \subsection{In the context of abundance matching models}
@@
 remain unchanged.
-
-The second caveat is the exact value that was used to turn
-  filter values into cosmological volumes. Strictly speaking the
-  volume probed is a function of the \ly luminosity. Brighter LAEs
-  probe a larger volume than fainter ones \citep{Gronwall07}. A proper
-way to account for this effect would require to assign luminosities to
-each mock LAE and process them in a similar way as mock
-observations. However, we can estimate that under the considerations
-presented in \citep{Gronwall07}, one could expect the survey depth to
-change at most by a factor of $\sim2$. Considering the dependence
-of the number density on halo mass (right panel of Figure 1), such
-change in volume could be compensated by different values for the
-favored model parameters $M_{\rm  min}$ and $M_{\rm max}$ by about the
-same factor of $\sim2$ or $0.3$ dex.
 

### 2014-04-03 paper/ms.tex
results - caveats

@@
 
-The main purpose of this section is to show how the different
-observational constraints narrow down the parameters space of allowed
-models. Each sub-section presents the effect of adding a new piece of 
-observational or statistical evidence.
-
 \subsection{Dark Matter Halo Number Density}
 
-The right panel in Figure \ref{fig:halos} shows the  integrated dark matter halo surface
+Figure \ref{fig:halos} shows the  integrated dark matter halo surface
 density as a function of  minimum halo mass $M_{\rm min}$. Each line
@@
 LAEs allowed by observations \citep{Yamada2012}. The dashed lines
-represent the average values in the fields observed by
+represent the values in the field observed by
 \citep{Ouchi2008}.
 
-This plot allows us to understand why only a specific range of
+Figure \ref{fig:halos} illustrates the impact of cosmic variance. At a
+fixed minimum mass there is an scatter of $0.3-0.6$ dex in the number
+density abundance, which is of the same order of magnitude as the
+scatter in the observational data. As a consequence the variation in
+the number density in mocks for models with the same mass range and
+occupation fraction can be by factors of $\sim 2-5$.
+
+Figure \ref{fig:halos} allows us to understand why only a specific range of
 models ${\mathcal M}$ can be expected to be consistent with
 observations. From Figure \ref{fig:halos} we can read that models with
-a minimum mass $M_{\rm min}>10^{12}$\hMsun always have a
-surface number density lower than the observational constrain, making
-them incompatible with observations; there are simply too few halos
+a minimum mass $M_{\rm min}>10^{12}$\hMsun always have a surface
+number density lower than the observational constrain, making them
+incompatible with observations; there are simply too few halos
 compared to observed LAEs. The opposite is true in models with $M_{\rm
@@
 
-Figure \ref{fig:halos} also illustrates the impact of cosmic
-variance. At fixed minimum mass there is an scatter of $0.3-0.6$ dex
-in the number density abundance, which is of the same order of
-magnitude as the scatter in the observational data.  As a consequence,
-the variation in the number density in mocks for models with the same
-mass range and occupation fraction can be by factors of $\sim 2-5$.
-This scatter induced by cosmic variance is naturally included in the
-mock construction process.
-
 \subsection{Maximally Consistent Models}
-
-We impose two major constraints in our models. First, we require a 
-models to have all its 15 mocks with a number density distribution
-consistent with observations. Second, we require that the average
-values among all mocks for the $\theta_{0}$-$\beta$ values in the
-correlation function fit to be consistent with observations
-\citep{Ouchi2008}.
 
@@
 results for the best estimates of $\theta_{0}$-$\beta$  used in the
-ACF parameterization on the best models previously selected.  Blue
-circles with error bars represent the results from the mocks and the
-horizontal line the observational results of \cite{Ouchi2008} over a
-field with average number density where the $\beta$ parameter was
-fixed in the fit. From this Figure we observe that there are models
-with too large values of $\theta_0$ and/or $\beta$ that can be ruled
-out as inconsistent.
+ACF parameterization on the models that are already consistent with
+the surface number density distribution.  Blue circles with error bars
+represent the results from the mocks and the horizontal line the
+observational results of \cite{Ouchi2008} over a field with average
+number density where the $\beta$ parameter was fixed in the fit. From
+this Figure we observe that there are models with too large values of
+$\theta_0$ and/or $\beta$ that can be ruled out as inconsistent.
 
-Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the
-consistent models in the planes $M_{\rm min}$-$M_{\rm
-  max}$ and $M_{\rm   min}$-$f_{\rm occ}$. A model is consistent with
-observations if there is a $1$-$\sigma$ overlap between both the
-correlation length $\theta_0$ and the exponent $\beta$.  We find that
-we end up with $40$ models consistent with the ACF constraints.  This
-is a reduction of a factor of $\sim 2$ with respect to the number of
-models consistent with the number density distribution.
+Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the final
+seletion consistent models in the planes $M_{\rm min}$-$M_{\rm
+  max}$ and $M_{\rm   min}$-$f_{\rm occ}$. We find that
+we end up with $40$ models consistent with both the surface number
+density constraints and the ACF.  This is a reduction of two orders of
+magnitude with respecto to the initial set of $9000$ models.
+
+In the next section we review in detail these models and their
+implications from the point of galaxy formation.
 
@@
 
-\subsection{Caveats of our method}
-
-There are three minor caveats for the work presented here that are important
-to keep in mind.
-
-The first caveat is the precise values for the mass intervals. These
-values are quoted from halos defined using a FOF halo
-finder. Different halo finders and definitions for the detection
-density threshold can yield different masses up to a factor $\sim 2$\citep{More2011}. For 
-instance a Friends-of-Friends algorithm with linking length $l=0.20$
-times the average inter-particle distance finds halos on average $1.4$
-times less massive than halos defined  with an spherical overdensity
-algorithm halos \citep{Bolshoi}. Therefore, the mass values for
-$M_{\rm min}$ and $M_{\rm max}$ should not be considered exact within
-less than $\sim 0.2$ dex. However, this represents a systematic change
-in the mass values and the mass interval $\Delta M$ quoted here should
-remain unchanged.
-
-A third caveat is the comparison of results for the number density
-  statistics and the ACF from surveys with different EW cuts. In this
-  sense we highlight again that the two filters and selection
-  criteria used by \citep{Ouchi2008} and \citep{Yamada2012} are only
-  slightly different. The median number density in the general fields by
-  \citep{Yamada2012} is $0.20$ arcmin$^{-2}$, while in
-  \citep{Ouchi2008} is $0.099\pm0.005$ arcmin$^{-2}$. This gives us
-  confidence that the two different samples can give a self-consistent
-  picture.
-
 \subsection{On the reproducibility of our results}

### 2014-04-03 paper/ms.tex
discussion

@@
 In the next section we review in detail these models and their
-implications from the point of galaxy formation.
+implications from the point of galaxy formation and other
+constraints reported in the literature.
 
@@
 The models in the third family are barely consistent with the
-  constraints from the ACF. These models they have another particular
+constraints from the ACF. These models have another particular
 feature: their minimum mass is exactly $M_{\rm min}=10^{10.9}\hMsun$
@@
 \subsection{Two relevant features in the preferred models}
+
 There are two interesting features in the remaining two first
@@
 propose in this \documentname. Nevertheless, values of an occupation
-  fraction $f_{\rm occ}=0.1$ and the mass range
-  predicted by all of our models is consistent with already published
-  observational results \citep{Gawiser07,Ouchi2010}. This suggests
-  that explicitly taking cosmic variance of the observed fields into
-  account (the only point not included in the analysis already cited)
-  hinders the possibility of constraining the LAEs occupation
-  fraction.
+fraction $f_{\rm occ}=0.1$ and the mass range predicted by all of our
+models are consistent with already published observational results
+\citep{Gawiser07,Ouchi2010}. This suggests that explicitly taking
+cosmic variance of the observed fields into account (the only point
+not included in the analysis already cited) hinders the possibility of
+constraining the LAEs occupation fraction.
 
-Concerning the narrow mass range $\Delta M
-  <1.0$ the question arises of how can we give a physical
-  interpretation for the existence of such  a narrow mass range. We
-  can start with a reasonable   assumption. Namely, that star formation
-  rate increases with halo's  mass. Under this assumption the cut at
-  the low mass end, $M_{\rm min}$, can be interpreted in terms of the
-  minimal star formation rate required to produce a \ly luminosity
-  above observational detection thresholds.   A cut at higher halo
-  masses $M_{\rm  max}$ requires a different justification. There are
-  two complementary physical scenarios that could provide it.
+Concerning the narrow mass range $\Delta M <1.0$ the question arises
+of how can we give a physical interpretation for the existence of such
+a narrow mass range. We can start with a reasonable
+assumption. Namely, that the star formation rate increases with halo's
+mass. Under this assumption the cut at the low mass end, $M_{\rm
+  min}$, can be interpreted in terms of the minimal star formation
+rate required to produce a \ly luminosity above observational
+detection thresholds.   A cut at higher halo masses $M_{\rm  max}$
+requires a different justification. There are two complementary
+physical scenarios that could provide it.
 
@@
 
-\subsection{In the context of abundance matching models}
-
-The abundance matching methods are based on observational results for
-Lyman Break Galaxies (LBGs) \citep{Behroozi2013a,Behroozi2013b}.  In
-the case of \cite{Behroozi2013a} the minimum halo mass considered to
-be relevant in their analysis is $10^{11.4}$\hMsun. They report
-stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
-their star formation rate is in the range $0.6\pm 0.2$ \Msun yr$^{-1}$,
-which nevertheless are close to the lower bound of values inferred for
-LAEs at high redshift \citep{Gawiser2007,Nilsson2009,Pentericci2009}.
-
-In our results, all the preferred models have a halo mass range lower
-than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considered in
-abundance matching at $z=3$. Our results confirm the expectations
-that most of  LAEs are to be found in less massive halos LBG hosts. A
-detailed analysis of the spectral and photometric properties of LAEs
-coupled to the kind of analysis performed in this paper can be a guide
-in the study of the properties of low mass dark matter halos at
-$z=3.1$, extending the capabilities of abundance matching methods.
-
 \subsection{On the reproducibility of our results}
@@
 
-In this \documentname we quantify the impact of cosmic variance in
+In this \documentname we quantified the impact of cosmic variance in
 constraining the  mass and occupation fraction of dark matter halos
 hosting Lyman $\alpha$ Emitters at redshift $z=3.1$ in a $\Lambda$CDM
-cosmology.  To this end we build a large number of mock catalogs
-matching observational geometries. The mocks are constructed from a
+cosmology.  To this end we built a large number of mock catalogs
+matching observational geometries. The mocks were constructed from a
 N-body simulation by assigning a single LAE to a DM halo.

### 2014-04-03 paper/ms.tex
conclusions

@@
 
-We then proceed with a thorough exploration of the space of free
-parameters $M_{\rm min}, M_{\rm max}$ and $f_{\rm occ}$ describing the
+We proceeded with a thorough exploration of the space of 
+parameters ($M_{\rm min}$, $M_{\rm max}$, $f_{\rm occ}$) describing the
 model. We look for consistency with two observational constraints: the
@@
 previous studies \citep[i.e.][]{Gawiser2007,Ouchi2010}  that
-unanimously favor low values on the range of $10^{-2}$. Nevertheless,
-all the halo mass ranges deduced in previous analysis are a subset of
-the models we find in this paper, all of the best models support the
-notion that the most massive halos at $z=3.1$ do not host detectable
+unanimously favor low values on the range of $10^{-2}$ and only
+consider values of $0.1$ as an upper limit. Nevertheless, all the halo
+mass ranges deduced in previous analysis are a subset of the models we
+find in this paper. All our the best models support the notion that the
+most massive halos at $z=3.1$ do not host detectable LAEs.
+
+Additional modeling for \ly radiation transfer is needed to
+put tighter constraints on  occupation fraction in high redshift
+halos, also paying attention to other physical phenomena, such as the
+stochasticity \citep{ForeroRomero2013} in the star formation process,
+which might play a role in introducing detection biases in high redshift
 LAEs.
@@
 From the point of view of Dark Energy surveys such as the Hobby-Eberly
-  Telescope Dark Enery Experiment (HETDEX) the
-  narrow mass range for LAEs can be seen as an advantage because its
-  simplicity in their modeling aiming at recovering cosmological
-  parameters We foresee that the observations with new instruments
-(such as the Multi Unit Spectroscopic Explorer (MUSE), Hyper
-SuprimeCam and HETDEX) covering larger fields and a wider range of
-luminosities will be key in reducing cosmic variance and imposing
-tighter constraints on the properties of dark matter halos hosting
-LAEs.
-
-Finally, additional modeling for \ly radiation transfer is needed to
-put tighter constraints on  occupation fraction in high redshift
-halos, also paying attention to other physical phenomena, such as the
-stochasticity \citep{ForeroRomero2013} in the star formation process,
-which might play a role in introducting detection biases in high redshift
-LAEs.
+Telescope Dark Enery Experiment (HETDEX) the narrow mass range for
+LAEs can be seen as an advantage because its simplicity in their
+modeling aiming at recovering cosmological parameters. We foresee that
+the observations with new instruments (such as the Multi Unit
+Spectroscopic Explorer (MUSE), Hyper SuprimeCam and HETDEX) covering
+more fields and a wider range of luminosities will be key in fully
+understanding the effects of cosmic variance  and imposing tighter
+constraints on the properties of dark matter halos hosting LAEs.
 
@@
 
-The MultiDark Database used in this paper and the web application providing online access to it were constructed as part of the
+The MultiDark Database used in this paper and the web application
+providing online access to it were constructed as part of the
 activities of the German Astrophysical Virtual Observatory as result

### 2014-04-15 paper/ms.tex
correcting typos and small changes to paper

@@
   values for the occupation fraction and the narrow mass range $\Delta
-  M$ are novel results allowed by takinf into account the influence of
+  M$ are novel results allowed by taking into account the influence of
   cosmic variance on the statistics derived from observations.  
@@
 content of the Universe is to be found in dark matter (DM) and each
-galaxy is thought to be hosted by larger dark matter structure known
+galaxy is thought to be hosted by a larger dark matter structure known
 as a halo. \citep{Peebles1980,SpringelNature05}.
@@
 approach. They start from the DM halo population to infer the
-intrinsic star formation rates and \ly a luminosities. From these
+intrinsic star formation rates and \ly  luminosities. From these
 values they estimate the amount of \ly photons that
@@
 We build mock surveys following the geometry of the observed fields by
-\cite{Yamada2012} to compared them  against observations in terms of
+\cite{Yamada2012} to compare them  against observations in terms of
 the number density distribution and the angular correlation
@@
 In the next subsections we describe in detail the four key
-elements int our work-flow. First, we present the 
+elements in our work-flow. First, we present the 
 observations we take as a benchmark. Second, we describe the main
@@
 detection of the Lyman-$\alpha$ line centered at $z=3.09$. The authors
-reported a total  $2161$  LAEs with an observed equivalent width, in
+reported a total of $2161$  LAEs with an observed equivalent width, in
 the observer frame, larger than $190$ \AA~over a total survey area of
@@
 their fields. Instead, we use the results by   \cite{Ouchi2008} who
-reported the ACF is over a region of $1$ deg$^2$ over the SXDS
+reported the ACF  over a region of $1$ deg$^2$ over the SXDS
 field.
@@
 dark matter halo if the halo mass is in the range allowed by the model
-$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from n
+$M_{\rm min}<M_{\rm h}<M_{\rm max}$ and a random variable taken from a
 homogeneous distribution $0\leq \xi<1$ is smaller than the occupation
@@
 fraction $f_{\rm  occ}=0.1$ have the possibility to be compatible with
-observations.  Similarly, wxploring occupation fractions on the order
+observations.  Similarly, exploring occupation fractions on the order
 of $f_{\rm occ}=0.01$ only makes sense for halo populations in the
@@
 the observational constraint on the number density. In our case, this
-is a mass range unresolved by the Bolshoi simulation and therefore
+ mass range is unresolved by the Bolshoi simulation and therefore
 is not considered in the present study.
@@
 value and a dispersion computed from the fit of all mock fields. We
-consider that a mocdel is consistent with observations if the two
+consider that a model is consistent with observations if the two
 parameters $\beta$ and $\theta_0$ are equal within a $1$-$\sigma$
@@
 respectively. .  The horizontal gray band represents the observational
-constraints on $theta_{0}$ established by
+constraints on $\theta_{0}$ established by
 \citet{Ouchi2008,Ouchi2010}. Green points has been displaced by
@@
   min}<10^{11.0}$\hMsun, which have a surface number density larger
-observations. In those cases the maximum mass $M_{\rm max}$ and the
+than observations. In those cases the maximum mass $M_{\rm max}$ and the
 occupation fraction $f_{\rm occ}<1.0$  can be tuned in order to lower
@@
 expectation (see figure \ref{fig:correlation_parameters}).
-Because these models are are barely compatible with observations and
+Because these models are barely compatible with observations and
 are a minority of the consistent models, we exclude them from the
@@
 \begin{center}
-\includegraphics[width=0.45\linewidth,angle=0]{Fig6_mass.pdf}
+\includegraphics[width=0.35\linewidth,angle=0]{Fig6_mass.pdf}
 \hspace{5mm}
-\includegraphics[width=0.45\linewidth,angle=0]{Fig6_f_occ.pdf}
+\includegraphics[width=0.35\linewidth,angle=0]{Fig6_f_occ.pdf}
 \end{center} 
@@
 families. First, the occupation fraction can take any value from $0.1$
-to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
-$\Delta M\leq 1.0$, half of them $\Delta M\leq 0.5$.
+to $1.0$. Second, all constrained models of halos hosting LAEs 
+ have a narrow mass range $\Delta M\leq 1.0$, and half of them 
+ have $\Delta M\leq 0.5$.
 
@@
   occ}>0.2$ is unexpected from previous clustering analysis that do
-not take  account the effect of cosmic variance in the same way we
+not take  into account the effect of cosmic variance in the same way we
 propose in this \documentname. Nevertheless, values of an occupation
@@
 model we find $40$ combination of parameters consistent with
-observations.
+observations.  The minimum mass and maximum mass of these consistent
+ models are found to be in the ranges:   $M_{\rm  max}<10^{12}$\hMsun\ 
+ and $10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.
 
@@
 mass ranges deduced in previous analysis are a subset of the models we
-find in this paper. All our the best models support the notion that the
+find in this paper. All our  best models support the notion that the
 most massive halos at $z=3.1$ do not host detectable LAEs.

### 2014-04-17 paper/ms.tex
version to submit

@@
   minimum mass and maximum mass can be constrained to the range
-  $M_{\rm  max}<10^{12}$\hMsun\ and $10^{10.2}\hMsun\leq M_{\rm
-    min}\leq 10^{11.5}\hMsun$. Additionally, we find that the
+$10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$ and $M_{\rm  max}<10^{12}$\hMsun.
+Additionally, we find that the
   consistent models have a narrow mass range, $\Delta M \equiv \log_{10}M_{\rm max} -
@@
 Capitalizing LAEs observations requires an understanding of
-their place in the context of a given structure formation model in a
-cosmological context. Under the current paradigm the dominant matter
-content of the Universe is to be found in dark matter (DM) and each
-galaxy is thought to be hosted by a larger dark matter structure known
-as a halo. \citep{Peebles1980,SpringelNature05}.
+their place in structure formation model in an explicit cosmological
+context. Under the current paradigm the dominant matter content of the
+Universe is to be found in dark matter (DM) and each galaxy is thought
+to be hosted by a larger dark matter structure known as a
+halo. \citep{Peebles1980,SpringelNature05}.
 
@@
 
-Some theoretical attempts to solve this problem using an  ab-initio
+There are theoretical attempts to solve this problem using an  ab-initio
 approach. They start from the DM halo population to infer the
@@
 However, these calculations involve many uncertain steps such as 
-the estimation of the escape fraction, that is the fraction of \ly
-photons that escape the galaxy to the observer. Given the resonant
+the estimation of the escape fraction of \ly photons. Given the resonant
 nature of the \ly line, the escape fraction is sensitive to  the dust
@@
 the conclusions derived on the halo host mass do not delve too deeply
-into the possible impact of cosmic variance.
+into the possible impact of cosmic variance in their estimates.
 
@@
 the number density distribution and the angular correlation
-function. This allows us to find a range of parameters of our model
-that are consistent with observations while taking into account
-cosmic variance.
+function. This allows us to find the range of parameters in our model
+that are consistent with observations while taking explicitly into
+account cosmic variance.
 
@@
 the halo mass and occupation fraction. We continue in \S
-\ref{sec:discussion} with a discussion under the light of other
-constraints already presented in the literature and theoretical
-considerations of galaxy formation studies. Finally, we present our
-conclusions in \S \ref{sec:conclusions}.
+\ref{sec:discussion} with a discussion of other constraints already
+presented in the literature and theoretical considerations. Finally,
+we present our conclusions in \S \ref{sec:conclusions}.
 
@@
 Our method is based on the comparison of observations and mock
-catalogs that take into account cosmic variance. Our benchmarks are the
-distribution of the surface number density across fields and the
-angular correlation function.
+catalogs. This approach explicitly takes into account cosmic
+variance. Our benchmarks are the distribution of the surface number
+density across fields and the angular correlation function.
 
@@
 centered at $4977$ \AA~with  $77$ \AA~width, corresponding to the
-redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the
-detection of the Lyman-$\alpha$ line centered at $z=3.09$. The authors
-reported a total of $2161$  LAEs with an observed equivalent width, in
-the observer frame, larger than $190$ \AA~over a total survey area of
-$2.42$ deg$^{2}$ that includes 12 sub-fields,  this corresponds to an
-average surface number density of $0.24\pm 0.01$ arcmin$^{-2}$.  The
-distribution of the surface number densities is shown in Figure
-\ref{fig:number_density}.
+redshift range $z=3.062$-$3.125$ and approximately $41$ \hMpc comoving scale for the
+detection of the Lyman-$\alpha$ line centered at
+$z=3.09$. The authors reported a total of $2161$  LAEs with an
+observed equivalent width, in the observer frame, larger than $190$
+\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
+sub-fields,  this corresponds to an average surface number density of
+$0.24\pm 0.01$ arcmin$^{-2}$.  The distribution of the surface number
+densities is shown in Figure \ref{fig:number_density}.
 
@@
 one sub-field  that stands out as an outlier in the distribution,
-corresponding to SSA22-1. All the other fields form a continous
+corresponding to SSA22-1. All the other fields form a continuous
 distribution in number density. Therefore, using the whole SSA22
@@
 most.  This is consistent with theoretical analysis of the correlation
-function \citep{Jose2013b} and obsevations that confirm a lack of
+function \citep{Jose2013b} and observations that confirm a lack of
 class pairs in LAEs \cite{Bond2009}.
@@
 in the redshift direction. This corresponds to a total area of $880$
-arcmin$^{2}$ in each mock field.
+arcmin$^{2}$ in each mock field. The exact value for the comoving size
+in the redshift direction is only accurate within a factor of $\sim 2$
+at most, given the luminosity dependence of this quantity
+\citep{Gronwall07}. In this \documentname we do not model the impact
+of the uncertainty from this quantity on our results.
 
@@
 
-\subsection{Exploring and selecting consistente models}
+\subsection{Exploring and selecting consistent models}
 
@@
 \begin{center}
-\includegraphics[width=0.46\linewidth,angle=0]{Fig7_corr_params.pdf}  
-\includegraphics[width=0.46\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
+\includegraphics[width=0.49\linewidth,angle=0]{Fig7_corr_params.pdf}  
+\includegraphics[width=0.49\linewidth,angle=0]{Fig7_mmin_vs_theta.pdf} 
 \end{center}
@@
 
-Figure \ref{fig:halos} allows us to understand why only a specific range of
+Figure \ref{fig:halos} help us to understand why only a specific range of
 models ${\mathcal M}$ can be expected to be consistent with
@@
 results for the best estimates of $\theta_{0}$-$\beta$  used in the
-ACF parameterization on the models that are already consistent with
+ACF parametrization on the models that are already consistent with
 the surface number density distribution.  Blue circles with error bars
@@
 Figure \ref{fig:restriction_mock_and_f_occ_corr} presents the final
-seletion consistent models in the planes $M_{\rm min}$-$M_{\rm
+selection consistent models in the planes $M_{\rm min}$-$M_{\rm
   max}$ and $M_{\rm   min}$-$f_{\rm occ}$. We find that
@@
 density constraints and the ACF.  This is a reduction of two orders of
-magnitude with respecto to the initial set of $9000$ models.
+magnitude with respect to the initial set of $9000$ models.
 
@@
 \begin{center}
-\includegraphics[width=0.35\linewidth,angle=0]{Fig6_mass.pdf}
-\hspace{5mm}
-\includegraphics[width=0.35\linewidth,angle=0]{Fig6_f_occ.pdf}
+\includegraphics[width=0.49\linewidth,angle=0]{Fig6_mass.pdf}
+\includegraphics[width=0.49\linewidth,angle=0]{Fig6_f_occ.pdf}
 \end{center} 
@@
 with ACF measurements. These expectations are mostly matched by
-the first family of models, also summarized in Table
-\ref{table:firstfamily}. These models, which favor only the  low
+the first family of models which favor only the  low
 ($\sim 10\%$) occupations fractions, are also consistent in that
@@
 Furthermore, In contrast to \cite{Gawiser07} and \cite{Ouchi2010} we
-find that an ACF analysis is not enough to rule
-out models with a high occupation fraction $f_{\rm occ}>0.2$.
-
-\subsection{On the reproducibility of our results}
-
-All the software, raw and processed data to produce the results
-and plots in this paper are publicly available in a github
-repository \footnote{https://github.com/forero/CosmicVarianceLAES}. Most
-of the code to produce the plots can be found as an Ipython notebook
-\citep{IPython} in the same repository.
+find that an ACF analysis is not enough to rule out models with a high
+occupation fraction $f_{\rm occ}>0.1$.
 
@@
 
-In this \documentname we quantified the impact of cosmic variance in
-constraining the  mass and occupation fraction of dark matter halos
-hosting Lyman $\alpha$ Emitters at redshift $z=3.1$ in a $\Lambda$CDM
-cosmology.  To this end we built a large number of mock catalogs
+In this \documentname constrained the  mass and occupation fraction of dark matter halos
+hosting Lyman $\alpha$ Emitters at redshift $z=3.1$ taking into
+account cosmic variance in a $\Lambda$CDM cosmology.  To this end we built a large number of mock catalogs
 matching observational geometries. The mocks were constructed from a
@@
 
-We proceeded with a thorough exploration of the space of 
-parameters ($M_{\rm min}$, $M_{\rm max}$, $f_{\rm occ}$) describing the
-model. We look for consistency with two observational constraints: the
+We proceeded with a thorough exploration of the parameter space
+($M_{\rm min}$, $M_{\rm max}$, $f_{\rm occ}$) describing our
+model. We looked for consistency with two observational constraints: the
 surface number density distribution and the angular correlation
 function. Out of the initial $9000$  combinations of parameters in the
-model we find $40$ combination of parameters consistent with
-observations.  The minimum mass and maximum mass of these consistent
- models are found to be in the ranges:   $M_{\rm  max}<10^{12}$\hMsun\ 
- and $10^{10.2}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.
+model we found $40$ consistent with observations.  The minimum mass and
+maximum mass of these consistent models were found to be in the
+ranges:   $M_{\rm  max}<10^{12}$\hMsun\ and $10^{10.2}\hMsun\leq
+M_{\rm min}\leq 10^{11.5}\hMsun$.  This supports the notion that the
+most massive halos at $z=3.1$ do not host detectable LAEs.
 
-We find two interesting features in these models. First, the
+We found two interesting features in these models. First, the
 occupation fraction remains unconstrained; second, many models have a
@@
 mass ranges deduced in previous analysis are a subset of the models we
-find in this paper. All our  best models support the notion that the
-most massive halos at $z=3.1$ do not host detectable LAEs.
+found with our method.
 
-Additional modeling for \ly radiation transfer is needed to
-put tighter constraints on  occupation fraction in high redshift
-halos, also paying attention to other physical phenomena, such as the
-stochasticity \citep{ForeroRomero2013} in the star formation process,
-which might play a role in introducing detection biases in high redshift
-LAEs.
+We consider that putting tight constraints on the occupation cannot be
+done from spatial information only. This requires additional modeling and
+larger observed fields to narrow down the link between halo mass, star
+formation and escaping \ly radiation. Additionally, the narrow halo
+mass range for halos hosting LAEs can be seen as an additional
+constraint for galaxy formation models that hope to address these
+questions.
 

### 2014-04-17 paper/ms.tex
submitted version

@@
 %\documentclass{aastex}
-\submitted{{\it Submitted for publication in ApJL}}
+\submitted{{\it Submitted for publication in ApJ}}
 \usepackage {graphicx}
@@
 
-\keywords{cosmology: theory – cosmology: large-scale structure of universe –
-  galaxies: formation – galaxies: high-redshift – galaxies: statistics
-  – galaxy: haloes}
+\keywords{cosmology: theory, dark matter --- methods: numerical --- galaxies: formation --- galaxies: high-redshift}
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{36}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Behroozi} {et~al.}(2013){Behroozi}, {Wechsler}, \&
+  {Conroy}}]{Behroozi2013a}
+{Behroozi}, P.~S., {Wechsler}, R.~H., \& {Conroy}, C. 2013, \apj, 770, 57
+
+\bibitem[{{Bond} {et~al.}(2009){Bond}, {Gawiser}, {Gronwall}, {Ciardullo},
+  {Altmann}, \& {Schawinski}}]{Bond2009}
+{Bond}, N.~A., {Gawiser}, E., {Gronwall}, C., {Ciardullo}, R., {Altmann}, M.,
+  \& {Schawinski}, K. 2009, \apj, 705, 639
+
+\bibitem[{{Colberg} {et~al.}(2000){Colberg}, {White}, {Yoshida}, {MacFarland},
+  {Jenkins}, {Frenk}, {Pearce}, {Evrard}, {Couchman}, {Efstathiou}, {Peacock},
+  {Thomas}, \& {Virgo Consortium}}]{Colberg00}
+{Colberg}, J.~M., {White}, S.~D.~M., {Yoshida}, N., {MacFarland}, T.~J.,
+  {Jenkins}, A., {Frenk}, C.~S., {Pearce}, F.~R., {Evrard}, A.~E., {Couchman},
+  H.~M.~P., {Efstathiou}, G., {Peacock}, J.~A., {Thomas}, P.~A., \& {Virgo
+  Consortium}. 2000, \mnras, 319, 209
+
+\bibitem[{{Dayal} {et~al.}(2009){Dayal}, {Ferrara}, {Saro}, {Salvaterra},
+  {Borgani}, \& {Tornatore}}]{Dayal2009}
+{Dayal}, P., {Ferrara}, A., {Saro}, A., {Salvaterra}, R., {Borgani}, S., \&
+  {Tornatore}, L. 2009, \mnras, 400, 2000
+
+\bibitem[{{Dijkstra} \& {Kramer}(2012)}]{Dijkstra2012}
+{Dijkstra}, M., \& {Kramer}, R. 2012, \mnras, 424, 1672
+
+\bibitem[{{Dijkstra} {et~al.}(2011){Dijkstra}, {Mesinger}, \&
+  {Wyithe}}]{Dijkstra11}
+{Dijkstra}, M., {Mesinger}, A., \& {Wyithe}, J.~S.~B. 2011, \mnras, 414, 2139
+
+\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
+  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{ForeroRomero2011}
+{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
+  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666
+
+\bibitem[{{Forero-Romero} {et~al.}(2012){Forero-Romero}, {Yepes},
+  {Gottl{\"o}ber}, \& {Prada}}]{ForeroRomero2012}
+{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., \& {Prada}, F. 2012,
+  \mnras, 419, 952
+
+\bibitem[{{Garel} {et~al.}(2012){Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
+  {Verhamme}, \& {Hayes}}]{Garel2012}
+{Garel}, T., {Blaizot}, J., {Guiderdoni}, B., {Schaerer}, D., {Verhamme}, A.,
+  \& {Hayes}, M. 2012, \mnras, 422, 310
+
+\bibitem[{{Gawiser} {et~al.}(2007{\natexlab{a}}){Gawiser}, {Francke}, {Lai},
+  {Schawinski}, {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos},
+  {Blanc}, {Fazio}, \& {Feldmeier}}]{Gawiser2007}
+{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
+  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
+  G.~A., {Fazio}, G., \& {Feldmeier}, J.~J. 2007{\natexlab{a}}, \apj, 671, 278
+
+\bibitem[{{Gawiser} {et~al.}(2007{\natexlab{b}}){Gawiser}, {Francke}, {Lai},
+  {Schawinski}, {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos},
+  {Blanc}, {Fazio}, {Feldmeier}, {Huang}, {Infante}, {Lira}, \&
+  {Padilla}}]{Gawiser07}
+{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
+  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
+  G.~A., {Fazio}, G., {Feldmeier}, J.~J., {Huang}, J.-s., {Infante}, L.,
+  {Lira}, P., \& {Padilla}, N. 2007{\natexlab{b}}, \apj, 671, 278
+
+\bibitem[{{Gronwall} {et~al.}(2007){Gronwall}, {Ciardullo}, {Hickey},
+  {Gawiser}, {Feldmeier}, {van Dokkum}, {Urry}, {Herrera}, {Lehmer}, {Infante},
+  {Orsi}, {Marchesini}, {Blanc}, {Francke}, {Lira}, \& {Treister}}]{Gronwall07}
+{Gronwall}, C., {Ciardullo}, R., {Hickey}, T., {Gawiser}, E., {Feldmeier},
+  J.~J., {van Dokkum}, P.~G., {Urry}, C.~M., {Herrera}, D., {Lehmer}, B.~D.,
+  {Infante}, L., {Orsi}, A., {Marchesini}, D., {Blanc}, G.~A., {Francke}, H.,
+  {Lira}, P., \& {Treister}, E. 2007, \apj, 667, 79
+
+\bibitem[{{Guaita} {et~al.}(2013){Guaita}, {Francke}, {Gawiser}, {Bauer},
+  {Hayes}, {{\"O}stlin}, \& {Padilla}}]{Guaita2013}
+{Guaita}, L., {Francke}, H., {Gawiser}, E., {Bauer}, F.~E., {Hayes}, M.,
+  {{\"O}stlin}, G., \& {Padilla}, N. 2013, \aap, 551, A93
+
+\bibitem[{{Hayashino} {et~al.}(2004){Hayashino}, {Matsuda}, {Tamura},
+  {Yamauchi}, {Yamada}, {Ajiki}, {Fujita}, {Murayama}, {Nagao}, {Ohta},
+  {Okamura}, {Ouchi}, {Shimasaku}, {Shioya}, \& {Taniguchi}}]{Hayashino2004}
+{Hayashino}, T., {Matsuda}, Y., {Tamura}, H., {Yamauchi}, R., {Yamada}, T.,
+  {Ajiki}, M., {Fujita}, S.~S., {Murayama}, T., {Nagao}, T., {Ohta}, K.,
+  {Okamura}, S., {Ouchi}, M., {Shimasaku}, K., {Shioya}, Y., \& {Taniguchi}, Y.
+  2004, \aj, 128, 2073
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{hinshaw_etal13}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
+  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
+  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
+  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
+  {Wright}, E.~L. 2013, \apjs, 208, 19
+
+\bibitem[{{Jose} {et~al.}(2013){Jose}, {Srianand}, \&
+  {Subramanian}}]{Jose2013b}
+{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, ArXiv e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{Bolshoi}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Koehler} {et~al.}(2007){Koehler}, {Schuecker}, \&
+  {Gebhardt}}]{Koehler2007}
+{Koehler}, R.~S., {Schuecker}, P., \& {Gebhardt}, K. 2007, \aap, 462, 7
+
+\bibitem[{{Kudritzki} {et~al.}(2000){Kudritzki}, {M{\'e}ndez}, {Feldmeier},
+  {Ciardullo}, {Jacoby}, {Freeman}, {Arnaboldi}, {Capaccioli}, {Gerhard}, \&
+  {Ford}}]{Kudritzki2000}
+{Kudritzki}, R.-P., {M{\'e}ndez}, R.~H., {Feldmeier}, J.~J., {Ciardullo}, R.,
+  {Jacoby}, G.~H., {Freeman}, K.~C., {Arnaboldi}, M., {Capaccioli}, M.,
+  {Gerhard}, O., \& {Ford}, H.~C. 2000, \apj, 536, 19
+
+\bibitem[{{Landy} \& {Szalay}(1993)}]{Landy1993}
+{Landy}, S.~D., \& {Szalay}, A.~S. 1993, \apj, 412, 64
+
+\bibitem[{{Laursen} {et~al.}(2013){Laursen}, {Duval}, \&
+  {{\"O}stlin}}]{Laursen2013}
+{Laursen}, P., {Duval}, F., \& {{\"O}stlin}, G. 2013, \apj, 766, 124
+
+\bibitem[{{Laursen} {et~al.}(2009){Laursen}, {Razoumov}, \&
+  {Sommer-Larsen}}]{Laursen2009}
+{Laursen}, P., {Razoumov}, A.~O., \& {Sommer-Larsen}, J. 2009, \apj, 696, 853
+
+\bibitem[{{Laursen} \& {Sommer-Larsen}(2007)}]{Laursen2007}
+{Laursen}, P., \& {Sommer-Larsen}, J. 2007, \apjl, 657, L69
+
+\bibitem[{{Matsuda} {et~al.}(2005){Matsuda}, {Yamada}, {Hayashino}, {Tamura},
+  {Yamauchi}, {Murayama}, {Nagao}, {Ohta}, {Okamura}, {Ouchi}, {Shimasaku},
+  {Shioya}, \& {Taniguchi}}]{Matsuda2005}
+{Matsuda}, Y., {Yamada}, T., {Hayashino}, T., {Tamura}, H., {Yamauchi}, R.,
+  {Murayama}, T., {Nagao}, T., {Ohta}, K., {Okamura}, S., {Ouchi}, M.,
+  {Shimasaku}, K., {Shioya}, Y., \& {Taniguchi}, Y. 2005, \apjl, 634, L125
+
+\bibitem[{{Neufeld}(1991)}]{Neufeld1991}
+{Neufeld}, D.~A. 1991, \apjl, 370, L85
+
+\bibitem[{{Nilsson} {et~al.}(2007){Nilsson}, {M{\o}ller}, {M{\"o}ller},
+  {Fynbo}, {Micha{\l}owski}, {Watson}, {Ledoux}, {Rosati}, {Pedersen}, \&
+  {Grove}}]{Nilsson2007}
+{Nilsson}, K.~K., {M{\o}ller}, P., {M{\"o}ller}, O., {Fynbo}, J.~P.~U.,
+  {Micha{\l}owski}, M.~J., {Watson}, D., {Ledoux}, C., {Rosati}, P.,
+  {Pedersen}, K., \& {Grove}, L.~F. 2007, \aap, 471, 71
+
+\bibitem[{{Orsi} {et~al.}(2012){Orsi}, {Lacey}, \& {Baugh}}]{Orsi2012}
+{Orsi}, A., {Lacey}, C.~G., \& {Baugh}, C.~M. 2012, \mnras, 425, 87
+
+\bibitem[{{Ouchi} {et~al.}(2008){Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
+  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
+  {Okamura}, {Iye}, {Takata}, {Yoshida}, \& {Yoshida}}]{Ouchi2008}
+{Ouchi}, M., {Shimasaku}, K., {Akiyama}, M., {Simpson}, C., {Saito}, T.,
+  {Ueda}, Y., {Furusawa}, H., {Sekiguchi}, K., {Yamada}, T., {Kodama}, T.,
+  {Kashikawa}, N., {Okamura}, S., {Iye}, M., {Takata}, T., {Yoshida}, M., \&
+  {Yoshida}, M. 2008, \apjs, 176, 301
+
+\bibitem[{{Ouchi} {et~al.}(2010){Ouchi}, {Shimasaku}, {Furusawa}, {Saito},
+  {Yoshida}, {Akiyama}, {Ono}, {Yamada}, {Ota}, {Kashikawa}, {Iye}, {Kodama},
+  {Okamura}, {Simpson}, \& {Yoshida}}]{Ouchi2010}
+{Ouchi}, M., {Shimasaku}, K., {Furusawa}, H., {Saito}, T., {Yoshida}, M.,
+  {Akiyama}, M., {Ono}, Y., {Yamada}, T., {Ota}, K., {Kashikawa}, N., {Iye},
+  M., {Kodama}, T., {Okamura}, S., {Simpson}, C., \& {Yoshida}, M. 2010, \apj,
+  723, 869
+
+\bibitem[{{Peebles}(1980)}]{Peebles1980}
+{Peebles}, P.~J.~E. 1980, {The large-scale structure of the universe}
+
+\bibitem[{Riebe {et~al.}(2013)Riebe, Partl, Enke, Forero-Romero, Gottlöber,
+  Klypin, Lemson, Prada, Primack, Steinmetz, \& Turchaninov}]{MultiDark}
+Riebe, K., Partl, A.~M., Enke, H., Forero-Romero, J., Gottlöber, S., Klypin,
+  A., Lemson, G., Prada, F., Primack, J.~R., Steinmetz, M., \& Turchaninov, V.
+  2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Springel} {et~al.}(2005){Springel}, {White}, {Jenkins}, {Frenk},
+  {Yoshida}, {Gao}, {Navarro}, {Thacker}, {Croton}, {Helly}, {Peacock}, {Cole},
+  {Thomas}, {Couchman}, {Evrard}, {Colberg}, \& {Pearce}}]{SpringelNature05}
+{Springel}, V., {White}, S.~D.~M., {Jenkins}, A., {Frenk}, C.~S., {Yoshida},
+  N., {Gao}, L., {Navarro}, J., {Thacker}, R., {Croton}, D., {Helly}, J.,
+  {Peacock}, J.~A., {Cole}, S., {Thomas}, P., {Couchman}, H., {Evrard}, A.,
+  {Colberg}, J., \& {Pearce}, F. 2005, \nat, 435, 629
+
+\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
+  {Maselli}}]{Verhamme2006}
+{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397
+
+\bibitem[{{Yajima} {et~al.}(2012){Yajima}, {Choi}, \& {Nagamine}}]{Yajima2012}
+{Yajima}, H., {Choi}, J.-H., \& {Nagamine}, K. 2012, \mnras, 427, 2889
+
+\bibitem[{{Yamada} {et~al.}(2012){Yamada}, {Nakamura}, {Matsuda}, {Hayashino},
+  {Yamauchi}, {Morimoto}, {Kousai}, \& {Umemura}}]{Yamada2012}
+{Yamada}, T., {Nakamura}, Y., {Matsuda}, Y., {Hayashino}, T., {Yamauchi}, R.,
+  {Morimoto}, N., {Kousai}, K., \& {Umemura}, M. 2012, \aj, 143, 79
+
+\bibitem[{{Zheng} {et~al.}(2010){Zheng}, {Cen}, {Trac}, \&
+  {Miralda-Escud{\'e}}}]{Zheng2010}
+{Zheng}, Z., {Cen}, R., {Trac}, H., \& {Miralda-Escud{\'e}}, J. 2010, \apj,
+  716, 574
+
+\end{thebibliography}
 
